### 2023-03-30 manuscript.Rmd
creating manuscript

---
title             : "Visualizing and Interpreting Multi-Group Confirmatory Factor Analysis"
shorttitle        : "VISUAL MGCFA"

author: 
  - name          : "Erin M. Buchanan"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "326 Market St., Harrisburg, PA, USA"
    email         : "ebuchanan@harrisburgu.edu"
    role: # Contributorship roles (e.g., CRediT, https://credit.niso.org/)
      - "Conceptualization"
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"

affiliation:
  - id            : "1"
    institution   : "Harrisburg University of Science and Technology"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  Latent variable modeling as a lens for psychometric theory is a popular tool for social scientists to examine measurement of constructs [@beaujean2014]. Journals such as *Assessment* regularly publish articles supporting new or previously established measures of latent constructs (e.g., depression, anxiety) wherein a measurement model is established for the scale in question. These measurement models designate the relationship between the measured, observed variables, and the underlying construct, with the assumption that these relations hold in many samples. Confirmatory factor analysis can be used to investigate the replicability and generalizability of the measurement model in new samples, while multi-group confirmatory factor analysis is used to examine the measurement model across groups within samples [@brown2015]. With the rise of the replication crisis and "psychology's renaissance" [@nelson2018], interest in divergence in measurement has increased, often focused on small parameter differences within the latent model. While the statistical procedure for examining measurement invariance is moderately well established, it is clear that the toolkit for inspecting these results is lacking. This manuscript will outline ways to visualize potential non-invariance, to supplement large numbers of tables that often overwhelm a reader within these published reports. Further, given these visualizations, readers will learn how to interpret the impact and size of the proposed non-invariance in models. While it is tempting to suggest that problems with replication and generalizability are simply issues with measurement, it is crucial to remember that all models have variability and error, even those models estimating the differences between item functioning, such as multi-group confirmatory factor analysis. This manuscript will help provide a framework for researchers interested in registered reports in this area.

keywords          : "multigroup confirmatory factor analysis, measurement invariance, visualization, effect size"

floatsintext      : no
linenumbers       : yes
draft             : no
mask              : no

figurelist        : no
tablelist         : no
footnotelist      : no

classoption       : "man"
output            : papaja::apa6_pdf
bibliography: references.bib
---

```{r setup, include = FALSE}
library(papaja)
library(lavaan)
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(84393)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

Outline

-   talk about LVM

-   talk about cfa

-   talk about mgcfa

-   how are measurement and replication/crisis related

-   why it is a bad idea to say that replication/crisis are *because* bad measurement

-   how can we visualize and interpret MGCFA to help us understand the impact of measurement differences

Research Questions:

By the end of this tutorial manuscript, readers will: 1. Be able to create visualizations for common steps to multi-group confirmatory factor analysis. 2. Be able to interpret the impact and size of potential non-invariance on measurement. 3. Understand the impact of measurement variability on replication and generalizability.

# Methods

## Design

Data will be simulated based on a multivariate normal distribution using R. The data will include two groups of individuals for multi-group confirmatory factor analysis (ns = 250; N = 500). The latent variables will be assumed to be continuous normal, and the measured items will be simulated using a traditional 1-7 Likert-type scale, matching many of the types of scales published in psychology and Assessment. Each item will be assumed to be related to the latent variable with loadings approximately equal to .60 to .80 (minus scenarios in which configural non-invariance is simulated).

## Variables

- Number of factors: one and two latent variable models will be simulated with five measured items for each latent variable. 
- Area of invariance: a model with non-invariance at each stage will be simulated including configural, metric, scalar, and strict non-invariance. One model with complete invariance will be used for comparison purposes. 
- Size of invariance: the size of the invariance will be simulated at three levels.

none, small, medium, large 
two models
metric (loadings), scalar (intercepts), strict (residuals)

4X2X3

since these are normally tested sequentially, we will only do one at a time

https://stats.stackexchange.com/questions/593243/data-simulation-in-r-for-measurement-invariance

```{r}
model.1 <- "lv =~ q1 + q2 + q3 + q4 + q5"

model.2 <- "lv =~ q1 + q2 + q3 + q4 + q5
lv2 =~ q6 + q7 + q8 + q9 + q10
"

# Packages
library(lavaan)

# specify population model for group 1 and group 2
population_model_g1 <-'f1=~x1+.6*x2+.7*x3+0.5*x4'
population_model_g2 <-'f1=~x1+.6*x2+.7*x3+0.4*x4'

# Sumulate data
set.seed(1234)
model_data_g1<-lavaan::simulateData(population_model_g1,sample.nobs=500)
model_data_g2<-lavaan::simulateData(population_model_g2,sample.nobs=500)

# Add group label
model_data_g1$group <- "Group1"
model_data_g2$group <- "Group2"

# put data into one data frame
model_data_all <- cbind(model_data_g1,model_data_g2)

```

#### delete this 
Across all studies, results indicated that the majority of the standardized factor loading differ-
ences were below .10, and few were greater than .50. Given these results, small, medium, and large
differences in factor loadings were operationalized as .10, .20, and .30, respectively. In other words,
the factor loadings in the focal group were increased by .10, .20, or .30 to simulate MNE in various
conditions. In contrast, intercept differences in the literature were larger than the factor loading
differences, and the majority of these differences were below .20, but very few were above 1.00.
Therefore, intercept differences across groups were operationalized as .25, .50, and .75. Figures A1
and A2 in the online supplemental material show the distributions of differences between the
standardized factor loadings and intercepts in the reference and focal groups.

## Data analysis

Multi-group confirmatory factor analysis will be examined across the simulated two groups of individuals using lavaan (Rosseel, 2012) focusing on the most common procedure outlined in Brown (2015). Each stage of measurement invariance (i.e., configural, metric, scalar, and strict) will be examined in the simulated data demonstrating how to visualize results using common tools, such as ggplot2 (Wickham et al., 2021). These visualizations will be compared across differences in non-invariance size to illustrate how to interpret the size of the non-invariance. Last, these effects will be examined on total score measurement (i.e., latent means) to explore the potential impacts on replication. Finally, suggestions will be provided for framing registered reports using multi-group confirmatory factor analysis.

# Results

# Discussion

Conclusions:

-   framework for submitted/interpreting reports

\newpage

# References

::: {#refs custom-style="Bibliography"}
:::

Visualizing Measurement Model Parameters for Tests of (Non)Invariance/DIF: 
Purpose, Presentation, and a New R Package

Type: Tutorial

Authors: John K. Sakaluk, Brenton M. Wiernik, Flavio Azevedo, Alex J. Denison, and Erin M. Buchanan

Email: jsakaluk@uwo.ca

300 Word Summary: 
Latent variable psychometric theory remains psychology’s most popular framework for conceptualizing and studying psychological entities across its many subdisciplines. Indeed, psychologists regularly use latent variable analysis frameworks to generate a “measurement model”: a statistical statement of the relations between a given set of observed variables and their construct(s) when attempting to describe and quantify the substance of the theoretical entities that they study. A core--and tacit--assumption, however of latent variables is that the measurement parameters are consistent between groups or across a given continuous covariate, as divergent measurement model parameters otherwise threaten the validity of the estimation, testing, and comparison of structural parameters. Psychologists therefore are often tasked with testing to establish “measurement invariance” (or equivalently, to rule out “differential item functioning”) for their latent variables of interest. But whereas the estimation, testing, and comparison of measurement model parameters is commonplace, the visualization of these parameters is virtually nonexistent, largely owing to a dearth of any standardized manner by which these parameters ought to be depicted. Without any compelling visualization techniques, the process of evaluating measurement (non)invariance seems likely to persist in facilitating relatively uninformative all-or-none omnibus testing, without any possibility of researchers identifying meaningful patterns. We therefore propose to describe, apply, and develop supporting analytic materials (e.g., R functions and tutorials) to visualize measurement modeling parameters. Our approach will be amenable to either multi-group comparisons or continuous covariate examinations of measurement modeling parameters and will enable emphasizing particular parameters and/or variables, while also providing visual information about the model as a whole. Finally, our approach will emphasize accessibility, in terms of: 1) creating easy-to-use functions for interested users to adopt in their own work, which will create 2) publication-ready greyscale figures and/or; 3) figures in a colorblind-friendly palette.  
Prior Req’d Knowledge:
R coding
Regression
Latent variable theory and measurement modeling

What: 
Rationale
Easy-to-use functionality/package for visualizations of measurement modeling output for DIF/Noninvariance-Testing, including:
Scale of measuremen-friendly for source of noninvariance
Multi-Group
Continuous-Covariate
Multilevel(s) Targeting
Measurement parameter (loading, intercept, residuals(?))
Item level (e.g., noninvariance/DIF effect sizes?)
Test level
Application/didactic example
Existing data sets? And/or?
Simulated data sets?

Guiding Programming Values
Easy to use
Should use df and fitted lavaan object and little else
Easy to incorporate into pubs
Should have a template option for APA-compliant figures (i.e., greyscale)
Accessibility
Should have a template(s) option for beautiful and colourblind-friendly palette(s)
Modifiable
Should return ggplot2::ggplot objects that the user can modify as desired; perhaps a “basic” template option that returns the geoms_ with little else?

March 24 Meeting

Introductions

Rehash of project goals/features + Discussion
Visualization of measurement model parameters for noninvariance/DIF testing
Visualization types
Response curves (latent score X, predicted item score on Y)
IRT Sigmoidal curves
CFA item “curves” 
“Common” visualization style (simple intercepts/slopes) for MCCFA/RFA
Error variance could be a band 
Faceted by items
Test level observed score and latent score distributions
Densities with grouped observed + grouped latent scores
Variance decomposition signal:noise (communality to uniqueness) “candybar plots”
R Functions (take selection of items and group/covariate and/or MGCFA lavaan object)
Return ggplot object
Options for “canned” style (e.g., APA compliant) 
Didactic example
learnr tutorial(s)

Preferred workflow/systems
lavaan:: focused
Github repo for package
Brenton with commit access on master branch
Others suggest changes with pull requests
Github issues for communication
Use Brown terminology
Configural
Metric
Scalar
Strict

Preferred roles
Toy examples for dev (two group multiple groups, continuous mimic, categorical mimic, sparse groups at different levels)
Erin’s examples 
Install the package examples if you want: devtools::install_github(“doomlab/learnSEM”) (I have a few more too, I’ll dig them up)
John: lavaan::HolzingerSwineford1939 and psych::bfi as preexisting/often used exemplar sets
Plot design in ggplot
Alex and Brenton and Flavio
Function writing
Alex and Brenton and John
Package dev/maintenance
Brenton
learnr tutorial(s)
Erin and John
Writing
John is happy to lead

Prefered timeline

Submission targets
AMPPS
BRM

### 2023-03-30 manuscript.Rmd
WHEW GRAPHS

@@
 library(lavaan)
+library(broom)
+library(dplyr)
+library(ggplot2)
+# devtools::install_github("psyteachr/introdataviz")
+library(introdataviz)
+
+# CFA function
+mgcfa <- function(data, group, model){
+
+  group_names <- unique(data[ , group])
+
+  model.overall <- cfa(model = model, data = data)
+  model.group1 <- cfa(model = model, data = subset(data, group == group_names[1]))
+  model.group2 <- cfa(model = model, data = subset(data, group == group_names[2]))
+  model.configural <- cfa(model = model, data = data, group = group, meanstructure = T)
+  model.metric <- cfa(model = model, data = data, group = group, group.equal = "loadings")
+  model.scalar <- cfa(model = model, data = data, group = group, group.equal = c("loadings", "intercepts"))
+  model.strict <- cfa(model = model, data = data, group = group, group.equal =  c("loadings", "intercepts", "residuals"))
+
+  model_coef <- bind_rows(
+    tidy(model.overall, conf.level = .95) %>% mutate(model = "overall"), 
+    tidy(model.group1, conf.level = .95) %>% mutate(model = "group1"), 
+    tidy(model.group2, conf.level = .95) %>% mutate(model = "group2"), 
+    tidy(model.configural, conf.level = .95) %>% mutate(model = "configural"), 
+    tidy(model.metric, conf.level = .95) %>% mutate(model = "metric"), 
+    tidy(model.scalar, conf.level = .95) %>% mutate(model = "scalar"), 
+    tidy(model.strict, conf.level = .95) %>% mutate(model = "strict")
+  )
+
+  model_fit <- bind_rows(
+    glance(model.overall) %>% mutate(model = "overall"), 
+    glance(model.group1) %>% mutate(model = "group1"), 
+    glance(model.group2) %>% mutate(model = "group2"), 
+    glance(model.configural) %>% mutate(model = "configural"), 
+    glance(model.metric) %>% mutate(model = "metric"), 
+    glance(model.scalar) %>% mutate(model = "scalar"), 
+    glance(model.strict) %>% mutate(model = "strict")
+    )
+
+  return(list(
+    "model_coef" = model_coef,
+    "model_fit" = model_fit
+  ))
+
+}
 ```
@@
 
+```{r create-data}
+library(lavaan)
+
+# build invariant model one factor
+model.invariant.g1 <- "lv =~ .9*q1 + .4*q2 + .6*q3 + .3*q4 + .6*q5"
+model.invariant.g2 <- "lv =~ .87*q1 + .43*q2 + .54*q3 + .4*q4 + .61*q5"
+model.overall <- "lv =~ q1 + q2 + q3 + q4 + q5"
+
+# simulate data
+df.invariant <- bind_rows(
+  simulateData(model.invariant.g1, sample.nobs = 250, 
+               meanstructure = T, model.type = "cfa") %>% 
+    mutate(group = "Group 1"), 
+  simulateData(model.invariant.g2, sample.nobs = 250, 
+               meanstructure = T, model.type = "cfa") %>% 
+    mutate(group = "Group 2") 
+)
+
+```
+
+```{r run-cfa}
+# invariant CFA
+results.invariant <- mgcfa(df.invariant, "group", model.overall)
+```
+
+```{r invariant-picture}
+graph.data <- results.invariant$model_coef %>% # put in tidy coefficients
+  filter(model == "configural") %>% # pick a model
+  filter(grepl("q4", term)) %>%  # pick a question
+  mutate(group = factor(group, levels = c(1,2), labels = c("Group 1", "Group 2")))
+
+graph.data$low <- graph.data$estimate - 2*graph.data$estimate
+graph.data$high <- graph.data$estimate + 2*graph.data$estimate
+
+# X = latent variable (so interpretation is z-score)
+# Y = observed variable
+# set x and y limits
+x_limits <- c(-1,1)
+y_limits <- c(min(df.invariant$q4), max(df.invariant$q4))
+
+# make ribbon data y = slope*x + intercept
+ribbondata <- bind_rows(
+  data.frame(
+  x = seq(from = x_limits[1] - 1,  
+          to = x_limits[2] + 1, 
+          by = .05), 
+  group = unique(graph.data$group)[1]
+) %>% 
+  mutate(ymin = (graph.data %>% filter(op == "=~") %>% 
+               slice_head() %>% pull(estimate) * x) - 
+           (2*graph.data %>% filter(op == "=~") %>% 
+                  slice_head() %>% pull(std.error)) +
+           graph.data %>% filter(op == "~1") %>% 
+               slice_head() %>% pull(estimate), 
+         ymax = (graph.data %>% filter(op == "=~") %>% 
+               slice_head() %>% pull(estimate) * x) + 
+           (2*graph.data %>% filter(op == "=~") %>% 
+                  slice_head() %>% pull(std.error)) +
+           graph.data %>% filter(op == "~1") %>% 
+               slice_head() %>% pull(estimate)), 
+  data.frame(
+    x = seq(from = x_limits[1] - 1,  
+            to = x_limits[2] + 1, 
+            by = .05), 
+    group = unique(graph.data$group)[2]
+  ) %>% 
+    mutate(ymin = (graph.data %>% filter(op == "=~") %>% 
+                 slice_tail() %>% pull(estimate) * x) - 
+             (2*graph.data %>% filter(op == "=~") %>% 
+                    slice_tail() %>% pull(std.error)) +
+             graph.data %>% filter(op == "~1") %>% 
+                 slice_tail() %>% pull(estimate), 
+           ymax = (graph.data %>% filter(op == "=~") %>% 
+                 slice_tail() %>% pull(estimate) * x) + 
+             (2*graph.data %>% filter(op == "=~") %>% 
+                    slice_tail() %>% pull(std.error)) +
+             graph.data %>% filter(op == "~1") %>% 
+                 slice_tail() %>% pull(estimate))
+)
+
+pointdata <- data.frame(
+  x = c(0,0),
+  y = graph.data %>% filter(op == "~1") %>% pull(estimate), 
+  group = graph.data %>% filter(op == "~1") %>% pull(group),
+  ymin = graph.data %>% filter(op == "~1") %>% pull(estimate) - 
+    2 * graph.data %>% filter(op == "~1") %>% pull(std.error), 
+  ymax = graph.data %>% filter(op == "~1") %>% pull(estimate) + 
+    2 * graph.data %>% filter(op == "~1") %>% pull(std.error)
+)
+
+linedata <- data.frame(
+  slope = graph.data %>% filter(op == "=~") %>% pull(estimate), 
+  intercept = graph.data %>% filter(op == "~1") %>% pull(estimate), 
+  group = graph.data %>% filter(op == "~1") %>% pull(group)
+)
+
+violindata <- data.frame(
+  y = c(rnorm(n = 1000, 
+            mean = graph.data %>% filter(op == "~~") %>% 
+              slice_head() %>% pull(estimate), 
+            sd = graph.data %>% filter(op == "~~") %>% 
+              slice_head() %>% pull(std.error)), 
+        rnorm(n = 1000, 
+            mean = graph.data %>% filter(op == "~~") %>% 
+              slice_tail() %>% pull(estimate), 
+            sd = graph.data %>% filter(op == "~~") %>% 
+              slice_tail() %>% pull(std.error))),
+  group = c(rep(graph.data %>% filter(op == "~~") %>% 
+              slice_head() %>% pull(group), 100),
+            rep(graph.data %>% filter(op == "~~") %>% 
+              slice_tail() %>% pull(group), 100)), 
+  x = 1
+)
+
+latent_means <- data.frame(
+  predict(model.overall.model), 
+  group = df.invariant$group
+)
+
+variance_plot <- 
+  ggplot(violindata, aes(x = 1, y = y, color = group, fill = group)) + 
+  geom_split_violin() + 
+  theme_void() + 
+  theme(legend.position = "none") + 
+  stat_summary(fun = "mean",
+               geom = "crossbar", 
+               width = 0.5,
+               colour = "black")
+
+intercept_plot <- 
+  ggplot() + 
+  # basic set up
+  theme_classic() + 
+  xlab("Latent Variable") + 
+  ylab("Observed Variable") + 
+  coord_cartesian(xlim = x_limits, ylim = y_limits) + 
+  # plot the intercepts 
+  geom_point(data = pointdata, 
+             aes(x = x, y = y, color = group), 
+             inherit.aes = FALSE) + 
+  geom_errorbar(data = pointdata,
+                aes(x = x, ymin = ymin, ymax = ymax, color = group), 
+                inherit.aes = FALSE, width = .10) + 
+  # plot the slopes
+  geom_abline(data = linedata,
+              aes(slope = slope, intercept = intercept, color = group)) + 
+  geom_ribbon(data = ribbondata, 
+              aes(x = x, ymin = ymin, ymax = ymax, fill = group), 
+              inherit.aes = FALSE, alpha = .2) + 
+  scale_color_discrete(name = "Group") + 
+  scale_fill_discrete(name = "Group") + 
+  geom_vline(xintercept = 0)
+
+# latent means
+mean_plot <- ggplot(latent_means, aes(x = lv, fill = group)) + 
+  geom_density(alpha = .2) + 
+  theme_classic() + 
+  xlab("Latent Variable") + 
+  ylab("Density") + 
+  geom_vline(data = latent_means %>% group_by(group) %>% summarize(mean = mean(lv)), 
+             aes(xintercept = mean, color = group)) + 
+  theme(legend.position = "none") 
+```
+
 ```{r}
-model.1 <- "lv =~ q1 + q2 + q3 + q4 + q5"
 

### 2023-03-30 manuscript.Rmd
so many pictures

--- 2023-03-30 manuscript.Rmd
@@
 
-```{r setup, include = FALSE}
+```{r libraries, include = FALSE}
 library(papaja)
 library(lavaan)
+library(broom)
+library(dplyr)
+library(ggplot2)
+# devtools::install_github("psyteachr/introdataviz")
+# devtools::install_github("ddueber/dmacs")
+library(introdataviz)
+library(dmacs)
+library(cowplot)
+```
+
+```{r cfa-function, include = FALSE}
+# CFA function
+mgcfa <- function(data, group, model){
+
+  group_names <- unique(data[ , group])
+
+  model.overall <- cfa(model = model, data = data)
+  model.group1 <- cfa(model = model, data = subset(data, group == group_names[1]))
+  model.group2 <- cfa(model = model, data = subset(data, group == group_names[2]))
+  model.configural <- cfa(model = model, data = data, group = group, meanstructure = T)
+  model.metric <- cfa(model = model, data = data, group = group, group.equal = "loadings")
+  model.scalar <- cfa(model = model, data = data, group = group, group.equal = c("loadings", "intercepts"))
+  model.strict <- cfa(model = model, data = data, group = group, group.equal =  c("loadings", "intercepts", "residuals"))
+
+  model_coef <- bind_rows(
+    tidy(model.overall, conf.level = .95) %>% mutate(model = "overall"), 
+    tidy(model.group1, conf.level = .95) %>% mutate(model = "group1"), 
+    tidy(model.group2, conf.level = .95) %>% mutate(model = "group2"), 
+    tidy(model.configural, conf.level = .95) %>% mutate(model = "configural"), 
+    tidy(model.metric, conf.level = .95) %>% mutate(model = "metric"), 
+    tidy(model.scalar, conf.level = .95) %>% mutate(model = "scalar"), 
+    tidy(model.strict, conf.level = .95) %>% mutate(model = "strict")
+  )
+
+  model_fit <- bind_rows(
+    glance(model.overall) %>% mutate(model = "overall"), 
+    glance(model.group1) %>% mutate(model = "group1"), 
+    glance(model.group2) %>% mutate(model = "group2"), 
+    glance(model.configural) %>% mutate(model = "configural"), 
+    glance(model.metric) %>% mutate(model = "metric"), 
+    glance(model.scalar) %>% mutate(model = "scalar"), 
+    glance(model.strict) %>% mutate(model = "strict")
+    )
+
+  return(list(
+    "model_coef" = model_coef,
+    "model_fit" = model_fit,
+    "model.overall" = model.overall,
+    "model.group1" = model.group1,
+    "model.group2" = model.group2,
+    "model.configural" = model.configural,
+    "model.metric" = model.metric,
+    "model.scalar" = model.scalar,
+    "model.strict" = model.strict
+  ))
+
+}
+```
+
+```{r test-function, eval = F, include = F}
+# temp test
+data_coef = results.large.res$model_coef
+model_step = "configural" 
+item_name = "q4"
+x_limits = c(-1,1)
+y_limits = c(min(df.large.res$q4), max(df.large.res$q4))
+ci_level = .95
+model_results = results.invariant$model.configural
+lv_name = "lv"
+```
+
+```{r plot-function, include = FALSE}
+plot_mgcfa <- function(data_coef, # output from model_coef
+                       model_step, # which model
+                       item_name, # name of observed item
+                       x_limits = c(-1,1), # LV limits to graph
+                       y_limits, # Y min and max in data 
+                       ci_level, # what ci do you want
+                       model_results, # what model results do you want 
+                       lv_name # which latent is the observed variable on
+                       ){
+
+  # calculate cutoff
+  cutoff <- qt(p = (1-ci_level)/2, 
+               df = sum(unlist(model_results@Data@nobs)), 
+               lower.tail = F)
+
+  # first get the data
+  graph.data <- data_coef %>% # put in tidy coefficients
+  filter(model == model_step) %>% # pick a model
+  filter(grepl(item_name, term)) %>%  # pick a question
+  mutate(group = factor(group, levels = names(table(data_coef$group)), labels = c("Group 1", "Group 2")))
+
+  # make ribbon data y = slope*x + intercept for ci for slopes 
+  ribbondata <- bind_rows(
+    data.frame(
+    x = seq(from = x_limits[1] - 1,  
+            to = x_limits[2] + 1, 
+            by = .05), 
+    group = unique(graph.data$group)[1]
+  ) %>% 
+    mutate(ymin = (graph.data %>% filter(op == "=~") %>% 
+                 slice_head() %>% pull(estimate) * x) - 
+             (cutoff*graph.data %>% filter(op == "=~") %>% 
+                    slice_head() %>% pull(std.error)) +
+             graph.data %>% filter(op == "~1") %>% 
+                 slice_head() %>% pull(estimate), 
+           ymax = (graph.data %>% filter(op == "=~") %>% 
+                 slice_head() %>% pull(estimate) * x) + 
+             (cutoff*graph.data %>% filter(op == "=~") %>% 
+                    slice_head() %>% pull(std.error)) +
+             graph.data %>% filter(op == "~1") %>% 
+                 slice_head() %>% pull(estimate)), 
+    data.frame(
+      x = seq(from = x_limits[1] - 1,  
+              to = x_limits[2] + 1, 
+              by = .05), 
+      group = unique(graph.data$group)[2]
+    ) %>% 
+      mutate(ymin = (graph.data %>% filter(op == "=~") %>% 
+                   slice_tail() %>% pull(estimate) * x) - 
+               (cutoff*graph.data %>% filter(op == "=~") %>% 
+                      slice_tail() %>% pull(std.error)) +
+               graph.data %>% filter(op == "~1") %>% 
+                   slice_tail() %>% pull(estimate), 
+             ymax = (graph.data %>% filter(op == "=~") %>% 
+                   slice_tail() %>% pull(estimate) * x) + 
+               (cutoff*graph.data %>% filter(op == "=~") %>% 
+                      slice_tail() %>% pull(std.error)) +
+               graph.data %>% filter(op == "~1") %>% 
+                   slice_tail() %>% pull(estimate))
+  )
+
+  # make point data to draw on the intercepts 
+  pointdata <- data.frame(
+  x = c(0,0),
+  y = graph.data %>% filter(op == "~1") %>% pull(estimate), 
+  group = graph.data %>% filter(op == "~1") %>% pull(group),
+  ymin = graph.data %>% filter(op == "~1") %>% pull(estimate) - 
+    cutoff * graph.data %>% filter(op == "~1") %>% pull(std.error), 
+  ymax = graph.data %>% filter(op == "~1") %>% pull(estimate) + 
+    cutoff * graph.data %>% filter(op == "~1") %>% pull(std.error)
+  )
+
+  # make the line data to draw on the slopes
+  linedata <- data.frame(
+  slope = graph.data %>% filter(op == "=~") %>% pull(estimate), 
+  intercept = graph.data %>% filter(op == "~1") %>% pull(estimate), 
+  group = graph.data %>% filter(op == "~1") %>% pull(group)
+  )
+
+  # make the distributions for the residuals 
+  violindata <- data.frame(
+  y = c(rnorm(n = 1000, 
+            mean = graph.data %>% filter(op == "~~") %>% 
+              slice_head() %>% pull(estimate), 
+            sd = graph.data %>% filter(op == "~~") %>% 
+              slice_head() %>% pull(std.error)), 
+        rnorm(n = 1000, 
+            mean = graph.data %>% filter(op == "~~") %>% 
+              slice_tail() %>% pull(estimate), 
+            sd = graph.data %>% filter(op == "~~") %>% 
+              slice_tail() %>% pull(std.error))),
+  group = c(rep(graph.data %>% filter(op == "~~") %>% 
+              slice_head() %>% pull(group), 1000),
+            rep(graph.data %>% filter(op == "~~") %>% 
+              slice_tail() %>% pull(group), 1000)), 
+  x = 1
+  )
+
+  # make the latent mean data for right panel
+  latent_predict <- predict(model_results)
+  latent_means <- data.frame(
+    c(latent_predict[[1]], latent_predict[[2]])
+    )
+  colnames(latent_means) <- colnames(latent_predict[[1]])
+  latent_means$group <- rep(names(latent_predict), 
+                  times = c(length(latent_predict[[1]]), 
+                           length(latent_predict[[2]])))
+
+  latent_means$lv <- latent_means[ , lv_name]
+
+  # make a plot of the variance
+  variance_plot <- 
+  ggplot(violindata, aes(x = 1, y = y, color = group, fill = group)) + 
+  geom_split_violin() + 
+  theme_void() + 
+  theme(legend.position = "none") + 
+  stat_summary(fun = "mean",
+               geom = "crossbar", 
+               width = 0.5,
+               colour = "black")
+
+  # make the plot with intercepts and slopes
+  intercept_plot <- 
+  ggplot() + 
+  # basic set up
+  theme_classic() + 
+  xlab("Latent Variable") + 
+  ylab("Observed Variable") + 
+  coord_cartesian(xlim = x_limits, ylim = y_limits) + 
+  # plot the intercepts 
+  geom_point(data = pointdata, 
+             aes(x = x, y = y, color = group), 
+             inherit.aes = FALSE) + 
+  geom_errorbar(data = pointdata,
+                aes(x = x, ymin = ymin, ymax = ymax, color = group), 
+                inherit.aes = FALSE, width = .10) + 
+  # plot the slopes
+  geom_abline(data = linedata,
+              aes(slope = slope, intercept = intercept, color = group)) + 
+  geom_ribbon(data = ribbondata, 
+              aes(x = x, ymin = ymin, ymax = ymax, fill = group), 
+              inherit.aes = FALSE, alpha = .2) + 
+  scale_color_discrete(name = "Group") + 
+  scale_fill_discrete(name = "Group") + 
+  geom_vline(xintercept = 0) + 
+  theme(axis.line.y = element_blank())
+
+  # make the latent means plot
+  mean_plot <- ggplot(latent_means, aes(x = lv, fill = group)) + 
+    geom_density(alpha = .2) + 
+    theme_classic() + 
+    xlab("Latent Variable") + 
+    ylab("Density") + 
+    geom_vline(data = latent_means %>% group_by(group) %>% summarize(mean = mean(lv)), 
+               aes(xintercept = mean, color = group)) + 
+    theme(legend.position = "none")
+
+  y_range = abs(y_limits[2] - y_limits[1])
+
+  # line up the two plots 
+  prow <- plot_grid(
+    intercept_plot + 
+      theme(legend.position = "none") + 
+      annotation_custom(ggplotGrob(variance_plot), 
+                        xmin = .25, xmax = 1, 
+                        ymin = y_limits[1], ymax = y_limits[2]-y_range/1.8),
+    mean_plot + 
+      theme(legend.position = "none"),
+    align = 'vh',
+    hjust = -1,
+    nrow = 1
+  )
+
+  # get the lengend
+  legend_b <- get_legend(
+    intercept_plot + 
+      guides(color = guide_legend(nrow = 1)) +
+      theme(legend.position = "bottom")
+  )
+
+  # send out the plot 
+  plot_grid(prow, legend_b, ncol = 1, rel_heights = c(1, .1))
+
+}
 ```
@@
 
-Research Questions:
+By the end of this tutorial manuscript, readers will:
 
-By the end of this tutorial manuscript, readers will: 1.
-Be able to create visualizations for common steps to multi-group confirmatory factor analysis.
-2.
-Be able to interpret the impact and size of potential non-invariance on measurement.
-3.
-Understand the impact of measurement variability on replication and generalizability.
+1.  Be able to create visualizations for common steps to multi-group confirmatory factor analysis.
+2.  Be able to interpret the impact and size of potential non-invariance on measurement.
+3.  Understand the impact of measurement variability on replication and generalizability.
 
-# Methods
+# Method
 
-## Design
+## Design and Analysis
 
-Data will be simulated based on a multivariate normal distribution using R.
-The data will include two groups of individuals for multi-group confirmatory factor analysis (ns = 250; N = 500).
-The latent variables will be assumed to be continuous normal, and the measured items will be simulated using a traditional 1-7 Likert-type scale, matching many of the types of scales published in psychology and Assessment.
-Each item will be assumed to be related to the latent variable with loadings approximately equal to .60 to .80 (minus scenarios in which configural non-invariance is simulated).
+Data was simulated using the `simulateData` function in the *R* package `lavaan` [@rosseel2012] assuming multivariate normality using a $\mu$ of 0 and $\sigma$ of 1 for the data.
+This function allows you to write `lavaan` syntax for your model with estimated values to generate data for observed variables.
+The data included two groups of individuals ("Group 1", "Group 2") for a multi-group confirmatory factor analysis (\$n\_{group}\$ = 250, *N* = 500).
+The latent variables were assumed to be continuous normal.
+The model consisted of five observed items predicted by one latent variable (`lv =~ q1 + q2 + q3 + q4 + q5`); however, the demonstration in this manuscript extends to multiple latent variables and other combinations of observed variables.
+Each item was assumed to be related to the latent variable with loadings approximately equal to .40 to .80, except when cases of non-invariance on the loadings was assumed.
 
-## Variables
+The @brown2015 steps of testing measurement invariance are demonstrated in this manuscript for illustration purposes, but in line with @stark2006 suggestions, the visualizations show the impact of loadings and intercepts together.
+The configural model was analyzed nesting both groups into the same CFA model requiring that both groups show the same model structure, but all other parameters are free to vary between groups.
+The metric model constrained the factor loadings of each group to be equal within the model.
+The scalar model then constrained the item intercepts (i.e., item mean) to be equal across groups.
+Finally, the strict model constrained the item variances (i.e., error variances) to be equal for each item across groups.
+These models are normally tested sequentially, and a convenience function `mgcfa` is provided in the supplemental documents for this manuscript.
 
-- Number of factors: one and two latent variable models will be simulated with five measured items for each latent variable. 
-- Area of invariance: a model with non-invariance at each stage will be simulated including configural, metric, scalar, and strict non-invariance.
-One model with complete invariance will be used for comparison purposes.
-- Size of invariance: the size of the invariance will be simulated at three levels.
+The data was then simulated to represent invariance across all model steps, small, medium, and large invariance using $d_{MACS}$ estimated sizes from @nye2019.
+While $d_{MACS}$ is used primarily for an effect size of the (non)-invariance for intercepts and loadings together, a similar approach was taken for the estimation of small, medium, and large effects on the residuals.
+The effect size is presented for all models, calculated from the *dmacs* package [@dueber2023, @nye2011].
+Only one item in each model was manipulated from the invariant model to create the non-invariant models.
 
-none, small, medium, large 
-two models
-metric (loadings), scalar (intercepts), strict (residuals)
+```{r create-models}
+# overall model
+model.overall <- "lv =~ q1 + q2 + q3 + q4 + q5"
 
-4X2X3
+# build invariant model one factor
+model.invariant.g1 <- "lv =~ .8*q1 + .4*q2 + .6*q3 + .3*q4 + .6*q5 
+q4 ~~ 1*q4
+q4 ~ 0*1"
+model.invariant.g2 <- "lv =~ .77*q1 + .43*q2 + .58*q3 + .3*q4 + .61*q5
+q4 ~~ 1*q4
+q4 ~ 0*1"
 
-since these are normally tested sequentially, we will only do one at a time
+# loadings
+model.small.load.g2 <- "lv =~ .77*q1 + .43*q2 + .58*q3 + .5*q4 + .61*q5"
+model.med.load.g2 <- "lv =~ .77*q1 + .43*q2 + .58*q3 + .6*q4 + .61*q5"
+model.large.load.g2 <- "lv =~ .77*q1 + .43*q2 + .58*q3 + 1.1*q4 + .61*q5"
 
-https://stats.stackexchange.com/questions/593243/data-simulation-in-r-for-measurement-invariance
+# build invariance on intercepts .25, .50, and .75
+model.small.int.g2 <- "lv =~ .77*q1 + .43*q2 + .58*q3 + .34*q4 + .61*q5
+q4 ~ .25*1"
+model.med.int.g2 <- "lv =~ .77*q1 + .43*q2 + .58*q3 + .34*q4 + .61*q5
+q4 ~ .5*1"
+model.large.int.g2 <- "lv =~ .77*q1 + .43*q2 + .58*q3 + .34*q4 + .61*q5
+q4 ~ .75*1"
 
-```{r}
-model.1 <- "lv =~ q1 + q2 + q3 + q4 + q5"
-
-model.2 <- "lv =~ q1 + q2 + q3 + q4 + q5
-lv2 =~ q6 + q7 + q8 + q9 + q10
-"
-
-# Packages
-library(lavaan)
-
-# specify population model for group 1 and group 2
-population_model_g1 <-'f1=~x1+.6*x2+.7*x3+0.5*x4'
-population_model_g2 <-'f1=~x1+.6*x2+.7*x3+0.4*x4'
-
-# Sumulate data
-set.seed(1234)
-model_data_g1<-lavaan::simulateData(population_model_g1,sample.nobs=500)
-model_data_g2<-lavaan::simulateData(population_model_g2,sample.nobs=500)
-
-# Add group label
-model_data_g1$group <- "Group1"
-model_data_g2$group <- "Group2"
-
-# put data into one data frame
-model_data_all <- cbind(model_data_g1,model_data_g2)
-
+# build invariance on residuals .25, .50, and .75
+model.small.res.g2 <- "lv =~ .77*q1 + .43*q2 + .58*q3 + .34*q4 + .61*q5
+q4 ~~ .75*q4"
+model.med.res.g2 <- "lv =~ .77*q1 + .43*q2 + .58*q3 + .34*q4 + .61*q5
+q4 ~~ .5*q4"
+model.large.res.g2 <- "lv =~ .77*q1 + .43*q2 + .58*q3 + .34*q4 + .61*q5
+q4 ~~ .25*q4"
 ```
 
-#### delete this 
-Across all studies, results indicated that the majority of the standardized factor loading differ-
-ences were below .10, and few were greater than .50. Given these results, small, medium, and large
-differences in factor loadings were operationalized as .10, .20, and .30, respectively. In other words,
-the factor loadings in the focal group were increased by .10, .20, or .30 to simulate MNE in various
-conditions. In contrast, intercept differences in the literature were larger than the factor loading
-differences, and the majority of these differences were below .20, but very few were above 1.00.
-Therefore, intercept differences across groups were operationalized as .25, .50, and .75. Figures A1
-and A2 in the online supplemental material show the distributions of differences between the
-standardized factor loadings and intercepts in the reference and focal groups.
+```{r create-data}
+# simulate data invariant
+df.invariant <- bind_rows(
+  simulateData(model.invariant.g1, sample.nobs = 250, 
+               meanstructure = T, model.type = "cfa",
+               seed = 1234) %>% 
+    mutate(group = "Group 1"), 
+  simulateData(model.invariant.g2, sample.nobs = 250, 
+               meanstructure = T, model.type = "cfa",
+               seed = 1234) %>% 
+    mutate(group = "Group 2") 
+)
 
-## Data analysis
+# simulate data small load
+df.small.load <- bind_rows(
+  simulateData(model.invariant.g1, sample.nobs = 250, 
+               meanstructure = T, model.type = "cfa",
+               seed = 1234) %>% 
+    mutate(group = "Group 1"), 
+  simulateData(model.small.load.g2, sample.nobs = 250, 
+               meanstructure = T, model.type = "cfa",
+               seed = 1234) %>% 
+    mutate(group = "Group 2") 
+)
 
-Multi-group confirmatory factor analysis will be examined across the simulated two groups of individuals using lavaan (Rosseel, 2012) focusing on the most common procedure outlined in Brown (2015).
-Each stage of measurement invariance (i.e., configural, metric, scalar, and strict) will be examined in the simulated data demonstrating how to visualize results using common tools, such as ggplot2 (Wickham et al., 2021).
-These visualizations will be compared across differences in non-invariance size to illustrate how to interpret the size of the non-invariance.
-Last, these effects will be examined on total score measurement (i.e., latent means) to explore the potential impacts on replication.
-Finally, suggestions will be provided for framing registered reports using multi-group confirmatory factor analysis.
+# simulate data med load
+df.med.load <- bind_rows(
+  simulateData(model.invariant.g1, sample.nobs = 250, 
+               meanstructure = T, model.type = "cfa",
+               seed = 1234) %>% 
+    mutate(group = "Group 1"), 
+  simulateData(model.med.load.g2, sample.nobs = 250, 
+               meanstructure = T, model.type = "cfa",
+               seed = 1234) %>% 
+    mutate(group = "Group 2") 
+)
+
+# simulate data large load
+df.large.load <- bind_rows(
+  simulateData(model.invariant.g1, sample.nobs = 250, 
+               meanstructure = T, model.type = "cfa",
+               seed = 1234) %>% 
+    mutate(group = "Group 1"), 
+  simulateData(model.large.load.g2, sample.nobs = 250, 
+               meanstructure = T, model.type = "cfa",
+               seed = 1234) %>% 
+    mutate(group = "Group 2") 
+)
+
+# simulate data small int
+df.small.int <- bind_rows(
+  simulateData(model.invariant.g1, sample.nobs = 250, 
+               meanstructure = T, model.type = "cfa",
+               seed = 1234) %>% 
+    mutate(group = "Group 1"), 
+  simulateData(model.small.int.g2, sample.nobs = 250, 
+               meanstructure = T, model.type = "cfa",
+               seed = 1234) %>% 
+    mutate(group = "Group 2") 
+)
+
+# simulate data med int
+df.med.int <- bind_rows(
+  simulateData(model.invariant.g1, sample.nobs = 250, 
+               meanstructure = T, model.type = "cfa",
+               seed = 1234) %>% 
+    mutate(group = "Group 1"), 
+  simulateData(model.med.int.g2, sample.nobs = 250, 
+               meanstructure = T, model.type = "cfa",
+               seed = 1234) %>% 
+    mutate(group = "Group 2") 
+)
+
+# simulate data large int
+df.large.int <- bind_rows(
+  simulateData(model.invariant.g1, sample.nobs = 250, 
+               meanstructure = T, model.type = "cfa",
+               seed = 1234) %>% 
+    mutate(group = "Group 1"), 
+  simulateData(model.large.int.g2, sample.nobs = 250, 
+               meanstructure = T, model.type = "cfa",
+               seed = 1234) %>% 
+    mutate(group = "Group 2") 
+)
+
+# simulate data small res
+df.small.res <- bind_rows(
+  simulateData(model.invariant.g1, sample.nobs = 250, 
+               meanstructure = T, model.type = "cfa",
+               seed = 1234) %>% 
+    mutate(group = "Group 1"), 
+  simulateData(model.small.res.g2, sample.nobs = 250, 
+               meanstructure = T, model.type = "cfa",
+               seed = 1234) %>% 
+    mutate(group = "Group 2") 
+)
+
+# simulate data med res
+df.med.res <- bind_rows(
+  simulateData(model.invariant.g1, sample.nobs = 250, 
+               meanstructure = T, model.type = "cfa",
+               seed = 1234) %>% 
+    mutate(group = "Group 1"), 
+  simulateData(model.med.res.g2, sample.nobs = 250, 
+               meanstructure = T, model.type = "cfa",
+               seed = 1234) %>% 
+    mutate(group = "Group 2") 
+)
+
+# simulate data large res
+df.large.res <- bind_rows(
+  simulateData(model.invariant.g1, sample.nobs = 250, 
+               meanstructure = T, model.type = "cfa",
+               seed = 1234) %>% 
+    mutate(group = "Group 1"), 
+  simulateData(model.large.res.g2, sample.nobs = 250, 
+               meanstructure = T, model.type = "cfa",
+               seed = 1234) %>% 
+    mutate(group = "Group 2") 
+)
+```
+
+```{r run-cfa}
+# invariant CFA
+results.invariant <- mgcfa(df.invariant, "group", model.overall)
+d_invariant <- lavaan_dmacs(results.invariant$model.configural, RefGroup = "Group 1")
+
+# loadings
+results.small.load <- mgcfa(df.small.load, "group", model.overall)
+results.med.load <- mgcfa(df.med.load, "group", model.overall)
+results.large.load <- mgcfa(df.large.load, "group", model.overall)
+
+d_small_load <- lavaan_dmacs(results.small.load$model.configural, RefGroup = "Group 1")
+d_med_load <- lavaan_dmacs(results.med.load$model.configural, RefGroup = "Group 1")
+d_large_load <- lavaan_dmacs(results.large.load$model.configural, RefGroup = "Group 1")
+
+# intercepts
+results.small.int <- mgcfa(df.small.int, "group", model.overall)
+results.med.int <- mgcfa(df.med.int, "group", model.overall)
+results.large.int <- mgcfa(df.large.int, "group", model.overall)
+
+d_small_int <- lavaan_dmacs(results.small.int$model.configural, RefGroup = "Group 1")
+d_med_int <- lavaan_dmacs(results.med.int$model.configural, RefGroup = "Group 1")
+d_large_int <- lavaan_dmacs(results.large.int$model.configural, RefGroup = "Group 1")
+
+# residuals
+results.small.res <- mgcfa(df.small.res, "group", model.overall)
+results.med.res <- mgcfa(df.med.res, "group", model.overall)
+results.large.res <- mgcfa(df.large.res, "group", model.overall)
+
+d_small_res <- lavaan_dmacs(results.small.res$model.configural, RefGroup = "Group 1")
+d_med_res <- lavaan_dmacs(results.med.res$model.configural, RefGroup = "Group 1")
+d_large_res <- lavaan_dmacs(results.large.res$model.configural, RefGroup = "Group 1")
+```
+
+```{r invariant-pic, include = T, fig.cap = "Invariant Model Visualization"}
+plot_mgcfa(
+  data_coef = results.invariant$model_coef, # output from model_coef
+  model_step = "configural", # which model
+  item_name = "q4", # name of observed item
+  x_limits = c(-1,1), # LV limits to graph
+  y_limits = c(min(df.invariant$q4), max(df.invariant$q4)), # Y min and max in data 
+  ci_level = .95, # what ci do you want
+  model_results = results.invariant$model.configural, # what model results do you want 
+  lv_name = "lv"
+)
+```
+
+```{r small-load-pic, include = T, fig.cap = "Small Loadings Model Visualization"}
+plot_mgcfa(
+  data_coef = results.small.load$model_coef, # output from model_coef
+  model_step = "configural", # which model
+  item_name = "q4", # name of observed item
+  x_limits = c(-1,1), # LV limits to graph
+  y_limits = c(min(df.small.load$q4), max(df.small.load$q4)), # Y min and max in data 
+  ci_level = .95, # what ci do you want
+  model_results = results.small.load$model.configural, # what model results do you want 
+  lv_name = "lv"
+)
+```
+
+```{r med-load-pic, include = T, fig.cap = "Medium Loadings Model Visualization"}
+plot_mgcfa(
+  data_coef = results.med.load$model_coef, # output from model_coef
+  model_step = "configural", # which model
+  item_name = "q4", # name of observed item
+  x_limits = c(-1,1), # LV limits to graph
+  y_limits = c(min(df.med.load$q4), max(df.med.load$q4)), # Y min and max in data 
+  ci_level = .95, # what ci do you want
+  model_results = results.med.load$model.configural, # what model results do you want 
+  lv_name = "lv"
+)
+```
+
+```{r large-load-pic, include = T, fig.cap = "Large Loadings Model Visualization"}
+plot_mgcfa(
+  data_coef = results.large.load$model_coef, # output from model_coef
+  model_step = "configural", # which model
+  item_name = "q4", # name of observed item
+  x_limits = c(-1,1), # LV limits to graph
+  y_limits = c(min(df.large.load$q4), max(df.large.load$q4)), # Y min and max in data 
+  ci_level = .95, # what ci do you want
+  model_results = results.large.load$model.configural, # what model results do you want 
+  lv_name = "lv"
+)
+```
+
+```{r small-int-pic, include = T, fig.cap = "Small Intercepts Model Visualization"}
+plot_mgcfa(
+  data_coef = results.small.int$model_coef, # output from model_coef
+  model_step = "metric", # which model
+  item_name = "q4", # name of observed item
+  x_limits = c(-1,1), # LV limits to graph
+  y_limits = c(min(df.small.int$q4), max(df.small.int$q4)), # Y min and max in data 
+  ci_level = .95, # what ci do you want
+  model_results = results.small.int$model.metric, # what model results do you want 
+  lv_name = "lv"
+)
+```
+
+```{r med-int-pic, include = T, fig.cap = "Medium Intercepts Model Visualization"}
+plot_mgcfa(
+  data_coef = results.med.int$model_coef, # output from model_coef
+  model_step = "metric", # which model
+  item_name = "q4", # name of observed item
+  x_limits = c(-1,1), # LV limits to graph
+  y_limits = c(min(df.med.int$q4), max(df.med.int$q4)), # Y min and max in data 
+  ci_level = .95, # what ci do you want
+  model_results = results.med.int$model.metric, # what model results do you want 
+  lv_name = "lv"
+)
+```
+
+```{r large-int-pic, include = T, fig.cap = "Large Intercepts Model Visualization"}
+plot_mgcfa(
+  data_coef = results.large.int$model_coef, # output from model_coef
+  model_step = "metric", # which model
+  item_name = "q4", # name of observed item
+  x_limits = c(-1,1), # LV limits to graph
+  y_limits = c(min(df.large.int$q4), max(df.large.int$q4)), # Y min and max in data 
+  ci_level = .95, # what ci do you want
+  model_results = results.large.int$model.metric, # what model results do you want 
+  lv_name = "lv"
+)
+```
+
+```{r small-res-pic, include = T, fig.cap = "Small Residuals Model Visualization"}
+plot_mgcfa(
+  data_coef = results.small.res$model_coef, # output from model_coef
+  model_step = "scalar", # which model
+  item_name = "q4", # name of observed item
+  x_limits = c(-1,1), # LV limits to graph
+  y_limits = c(min(df.small.res$q4), max(df.small.res$q4)), # Y min and max in data 
+  ci_level = .95, # what ci do you want
+  model_results = results.small.res$model.scalar, # what model results do you want 
+  lv_name = "lv"
+)
+```
+
+```{r med-res-pic, include = T, fig.cap = "Medium Residuals Model Visualization"}
+plot_mgcfa(
+  data_coef = results.med.res$model_coef, # output from model_coef
+  model_step = "scalar", # which model
+  item_name = "q4", # name of observed item
+  x_limits = c(-1,1), # LV limits to graph
+  y_limits = c(min(df.med.res$q4), max(df.med.res$q4)), # Y min and max in data 
+  ci_level = .95, # what ci do you want
+  model_results = results.med.res$model.scalar, # what model results do you want 
+  lv_name = "lv"
+)
+```
+
+```{r large-res-pic, include = T, fig.cap = "Large Residuals Model Visualization"}
+plot_mgcfa(
+  data_coef = results.large.res$model_coef, # output from model_coef
+  model_step = "scalar", # which model
+  item_name = "q4", # name of observed item
+  x_limits = c(-1,1), # LV limits to graph
+  y_limits = c(min(df.large.res$q4), max(df.large.res$q4)), # Y min and max in data 
+  ci_level = .95, # what ci do you want
+  model_results = results.large.res$model.scalar, # what model results do you want 
+  lv_name = "lv"
+)
+```
 
@@
 
-Visualizing Measurement Model Parameters for Tests of (Non)Invariance/DIF: 
-Purpose, Presentation, and a New R Package
+\newpage
 
-Type: Tutorial
+# Appendix
 
-Authors: John K. Sakaluk, Brenton M. Wiernik, Flavio Azevedo, Alex J. Denison, and Erin M. Buchanan
+```{r}
+apa_table(results.invariant$model_fit %>% 
+            select(model, AIC, BIC, cfi, tli, rmsea, srmr), 
+          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
+          caption = "Model Fit for Invariant Model")
+```
 
-Email: jsakaluk@uwo.ca
+```{r}
+apa_table(results.small.load$model_fit %>% 
+            select(model, AIC, BIC, cfi, tli, rmsea, srmr), 
+          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
+          caption = "Model Fit for Small Differences in Loadings")
+```
 
-300 Word Summary: 
-Latent variable psychometric theory remains psychology’s most popular framework for conceptualizing and studying psychological entities across its many subdisciplines.
-Indeed, psychologists regularly use latent variable analysis frameworks to generate a “measurement model”: a statistical statement of the relations between a given set of observed variables and their construct(s) when attempting to describe and quantify the substance of the theoretical entities that they study.
-A core--and tacit--assumption, however of latent variables is that the measurement parameters are consistent between groups or across a given continuous covariate, as divergent measurement model parameters otherwise threaten the validity of the estimation, testing, and comparison of structural parameters.
-Psychologists therefore are often tasked with testing to establish “measurement invariance” (or equivalently, to rule out “differential item functioning”) for their latent variables of interest.
-But whereas the estimation, testing, and comparison of measurement model parameters is commonplace, the visualization of these parameters is virtually nonexistent, largely owing to a dearth of any standardized manner by which these parameters ought to be depicted.
-Without any compelling visualization techniques, the process of evaluating measurement (non)invariance seems likely to persist in facilitating relatively uninformative all-or-none omnibus testing, without any possibility of researchers identifying meaningful patterns.
-We therefore propose to describe, apply, and develop supporting analytic materials (e.g., R functions and tutorials) to visualize measurement modeling parameters.
-Our approach will be amenable to either multi-group comparisons or continuous covariate examinations of measurement modeling parameters and will enable emphasizing particular parameters and/or variables, while also providing visual information about the model as a whole.
-Finally, our approach will emphasize accessibility, in terms of: 1) creating easy-to-use functions for interested users to adopt in their own work, which will create 2) publication-ready greyscale figures and/or; 3) figures in a colorblind-friendly palette.
-Prior Req’d Knowledge:
-R coding
-Regression
-Latent variable theory and measurement modeling
+```{r}
+apa_table(results.med.load$model_fit %>% 
+            select(model, AIC, BIC, cfi, tli, rmsea, srmr), 
+          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
+          caption = "Model Fit for Medium Differences in Loadings")
+```
 
-What: 
-Rationale
-Easy-to-use functionality/package for visualizations of measurement modeling output for DIF/Noninvariance-Testing, including:
-Scale of measuremen-friendly for source of noninvariance
-Multi-Group
-Continuous-Covariate
-Multilevel(s) Targeting
-Measurement parameter (loading, intercept, residuals(?))
-Item level (e.g., noninvariance/DIF effect sizes?)
-Test level
-Application/didactic example
-Existing data sets? And/or?
-Simulated data sets?
+```{r}
+apa_table(results.large.load$model_fit %>% 
+            select(model, AIC, BIC, cfi, tli, rmsea, srmr), 
+          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
+          caption = "Model Fit for Large Differences in Loadings")
+```
 
-Guiding Programming Values
-Easy to use
-Should use df and fitted lavaan object and little else
-Easy to incorporate into pubs
-Should have a template option for APA-compliant figures (i.e., greyscale)
-Accessibility
-Should have a template(s) option for beautiful and colourblind-friendly palette(s)
-Modifiable
-Should return ggplot2::ggplot objects that the user can modify as desired; perhaps a “basic” template option that returns the geoms_ with little else?
+```{r}
+apa_table(results.small.int$model_fit %>% 
+            select(model, AIC, BIC, cfi, tli, rmsea, srmr), 
+          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
+          caption = "Model Fit for Small Differences in Intercepts")
+```
 
-March 24 Meeting
+```{r}
+apa_table(results.med.int$model_fit %>% 
+            select(model, AIC, BIC, cfi, tli, rmsea, srmr), 
+          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
+          caption = "Model Fit for Medium Differences in Intercepts")
+```
 
-Introductions
+```{r}
+apa_table(results.large.int$model_fit %>% 
+            select(model, AIC, BIC, cfi, tli, rmsea, srmr), 
+          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
+          caption = "Model Fit for Large Differences in Intercepts")
+```
 
-Rehash of project goals/features + Discussion
-Visualization of measurement model parameters for noninvariance/DIF testing
-Visualization types
-Response curves (latent score X, predicted item score on Y)
-IRT Sigmoidal curves
-CFA item “curves” 
-“Common” visualization style (simple intercepts/slopes) for MCCFA/RFA
-Error variance could be a band 
-Faceted by items
-Test level observed score and latent score distributions
-Densities with grouped observed + grouped latent scores
-Variance decomposition signal:noise (communality to uniqueness) “candybar plots”
-R Functions (take selection of items and group/covariate and/or MGCFA lavaan object)
-Return ggplot object
-Options for “canned” style (e.g., APA compliant) 
-Didactic example
-learnr tutorial(s)
+```{r}
+apa_table(results.small.res$model_fit %>% 
+            select(model, AIC, BIC, cfi, tli, rmsea, srmr), 
+          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
+          caption = "Model Fit for Small Differences in Residuals")
+```
 
-Preferred workflow/systems
-lavaan:: focused
-Github repo for package
-Brenton with commit access on master branch
-Others suggest changes with pull requests
-Github issues for communication
-Use Brown terminology
-Configural
-Metric
-Scalar
-Strict
+```{r}
+apa_table(results.med.res$model_fit %>% 
+            select(model, AIC, BIC, cfi, tli, rmsea, srmr), 
+          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
+          caption = "Model Fit for Medium Differences in Residuals")
+```
 
-Preferred roles
-Toy examples for dev (two group multiple groups, continuous mimic, categorical mimic, sparse groups at different levels)
-Erin’s examples 
-Install the package examples if you want: devtools::install_github(“doomlab/learnSEM”) (I have a few more too, I’ll dig them up)
-John: lavaan::HolzingerSwineford1939 and psych::bfi as preexisting/often used exemplar sets
-Plot design in ggplot
-Alex and Brenton and Flavio
-Function writing
-Alex and Brenton and John
-Package dev/maintenance
-Brenton
-learnr tutorial(s)
-Erin and John
-Writing
-John is happy to lead
-
-Prefered timeline
-
-Submission targets
-AMPPS
-BRM
+```{r}
+apa_table(results.large.res$model_fit %>% 
+            select(model, AIC, BIC, cfi, tli, rmsea, srmr), 
+          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
+          caption = "Model Fit for Large Differences in Residuals")
+```

### 2023-03-30 manuscript.tex
so many pictures

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

% Table formatting
\usepackage{longtable}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\centering\begin{threeparttable}}
%   {\end{threeparttable}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\centering\begin{ThreePartTable}}{\end{ThreePartTable}\end{landscape}}

% Enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

% \setlength{\parindent}{0.5in}
% \setlength{\parskip}{0pt plus 0pt minus 0pt}

% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
% See https://github.com/crsh/papaja/issues/292
\makeatletter
\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-1em}%
  {\normalfont\normalsize\bfseries\itshape\typesectitle}}

\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-\z@\relax}%
  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
\makeatother

\makeatletter
\usepackage{etoolbox}
\patchcmd{\maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{multigroup confirmatory factor analysis, measurement invariance, visualization, effect size}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Visualizing and Interpreting Multi-Group Confirmatory Factor Analysis},
  pdfauthor={Erin M. Buchanan1},
  pdflang={en-EN},
  pdfkeywords={multigroup confirmatory factor analysis, measurement invariance, visualization, effect size},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Visualizing and Interpreting Multi-Group Confirmatory Factor Analysis}
\author{Erin M. Buchanan\textsuperscript{1}}
\date{}

\shorttitle{VISUAL MGCFA}

\authornote{

Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

Enter author note here.

The authors made the following contributions. Erin M. Buchanan: Conceptualization, Writing - Original Draft Preparation, Writing - Review \& Editing.

Correspondence concerning this article should be addressed to Erin M. Buchanan, 326 Market St., Harrisburg, PA, USA. E-mail: \href{mailto:ebuchanan@harrisburgu.edu}{\nolinkurl{ebuchanan@harrisburgu.edu}}

}

\affiliation{\vspace{0.5cm}\textsuperscript{1} Harrisburg University of Science and Technology}

\abstract{%
Latent variable modeling as a lens for psychometric theory is a popular tool for social scientists to examine measurement of constructs (Beaujean, 2014). Journals such as \emph{Assessment} regularly publish articles supporting new or previously established measures of latent constructs (e.g., depression, anxiety) wherein a measurement model is established for the scale in question. These measurement models designate the relationship between the measured, observed variables, and the underlying construct, with the assumption that these relations hold in many samples. Confirmatory factor analysis can be used to investigate the replicability and generalizability of the measurement model in new samples, while multi-group confirmatory factor analysis is used to examine the measurement model across groups within samples (Brown, 2015). With the rise of the replication crisis and ``psychology's renaissance'' (Nelson, Simmons, \& Simonsohn, 2018), interest in divergence in measurement has increased, often focused on small parameter differences within the latent model. While the statistical procedure for examining measurement invariance is moderately well established, it is clear that the toolkit for inspecting these results is lacking. This manuscript will outline ways to visualize potential non-invariance, to supplement large numbers of tables that often overwhelm a reader within these published reports. Further, given these visualizations, readers will learn how to interpret the impact and size of the proposed non-invariance in models. While it is tempting to suggest that problems with replication and generalizability are simply issues with measurement, it is crucial to remember that all models have variability and error, even those models estimating the differences between item functioning, such as multi-group confirmatory factor analysis. This manuscript will help provide a framework for researchers interested in registered reports in this area.
}

\begin{document}
\maketitle

Outline

\begin{itemize}
\item
  talk about LVM
\item
  talk about cfa
\item
  talk about mgcfa
\item
  how are measurement and replication/crisis related
\item
  why it is a bad idea to say that replication/crisis are \emph{because} bad measurement
\item
  how can we visualize and interpret MGCFA to help us understand the impact of measurement differences
\end{itemize}

By the end of this tutorial manuscript, readers will:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Be able to create visualizations for common steps to multi-group confirmatory factor analysis.
\item
  Be able to interpret the impact and size of potential non-invariance on measurement.
\item
  Understand the impact of measurement variability on replication and generalizability.
\end{enumerate}

\hypertarget{method}{%
\section{Method}\label{method}}

\hypertarget{design-and-analysis}{%
\subsection{Design and Analysis}\label{design-and-analysis}}

Data was simulated using the \texttt{simulateData} function in the \emph{R} package \texttt{lavaan} (Rosseel, 2012) assuming multivariate normality using a \(\mu\) of 0 and \(\sigma\) of 1 for the data. This function allows you to write \texttt{lavaan} syntax for your model with estimated values to generate data for observed variables. The data included two groups of individuals (``Group 1'', ``Group 2'') for a multi-group confirmatory factor analysis (\$n\_\{group\}\$ = 250, \emph{N} = 500). The latent variables were assumed to be continuous normal. The model consisted of five observed items predicted by one latent variable (\texttt{lv\ =\textasciitilde{}\ q1\ +\ q2\ +\ q3\ +\ q4\ +\ q5}); however, the demonstration in this manuscript extends to multiple latent variables and other combinations of observed variables. Each item was assumed to be related to the latent variable with loadings approximately equal to .40 to .80, except when cases of non-invariance on the loadings was assumed.

The Brown (2015) steps of testing measurement invariance are demonstrated in this manuscript for illustration purposes, but in line with Stark, Chernyshenko, and Drasgow (2006) suggestions, the visualizations show the impact of loadings and intercepts together. The configural model was analyzed nesting both groups into the same CFA model requiring that both groups show the same model structure, but all other parameters are free to vary between groups. The metric model constrained the factor loadings of each group to be equal within the model. The scalar model then constrained the item intercepts (i.e., item mean) to be equal across groups. Finally, the strict model constrained the item variances (i.e., error variances) to be equal for each item across groups. These models are normally tested sequentially, and a convenience function \texttt{mgcfa} is provided in the supplemental documents for this manuscript.

The data was then simulated to represent invariance across all model steps, small, medium, and large invariance using \(d_{MACS}\) estimated sizes from Nye, Bradburn, Olenick, Bialko, and Drasgow (2019). While \(d_{MACS}\) is used primarily for an effect size of the (non)-invariance for intercepts and loadings together, a similar approach was taken for the estimation of small, medium, and large effects on the residuals. The effect size is presented for all models, calculated from the \emph{dmacs} package Nye \& Drasgow (2011). Only one item in each model was manipulated from the invariant model to create the non-invariant models.

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/invariant-pic-1.pdf}
\caption{\label{fig:invariant-pic}Invariant Model Visualization}
\end{figure}

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/small-load-pic-1.pdf}
\caption{\label{fig:small-load-pic}Small Loadings Model Visualization}
\end{figure}

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/med-load-pic-1.pdf}
\caption{\label{fig:med-load-pic}Medium Loadings Model Visualization}
\end{figure}

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/large-load-pic-1.pdf}
\caption{\label{fig:large-load-pic}Large Loadings Model Visualization}
\end{figure}

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/small-int-pic-1.pdf}
\caption{\label{fig:small-int-pic}Small Intercepts Model Visualization}
\end{figure}

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/med-int-pic-1.pdf}
\caption{\label{fig:med-int-pic}Medium Intercepts Model Visualization}
\end{figure}

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/large-int-pic-1.pdf}
\caption{\label{fig:large-int-pic}Large Intercepts Model Visualization}
\end{figure}

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/small-res-pic-1.pdf}
\caption{\label{fig:small-res-pic}Small Residuals Model Visualization}
\end{figure}

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/med-res-pic-1.pdf}
\caption{\label{fig:med-res-pic}Medium Residuals Model Visualization}
\end{figure}

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/large-res-pic-1.pdf}
\caption{\label{fig:large-res-pic}Large Residuals Model Visualization}
\end{figure}

\hypertarget{results}{%
\section{Results}\label{results}}

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

Conclusions:

\begin{itemize}
\tightlist
\item
  framework for submitted/interpreting reports
\end{itemize}

\newpage

\hypertarget{references}{%
\section{References}\label{references}}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-beaujean2014}{}}%
Beaujean, A. A. (2014). \emph{Latent variable modeling using r: A step by step guide}. New York: Routledge/Taylor \& Francis Group.

\leavevmode\vadjust pre{\hypertarget{ref-brown2015}{}}%
Brown, T. A. (2015). \emph{Confirmatory factor analysis for applied research} (Second edition). New York ; London: The Guilford Press.

\leavevmode\vadjust pre{\hypertarget{ref-dueber2023}{}}%
Dueber, D. (2023). \emph{Dmacs}. Retrieved from \url{https://github.com/ddueber/dmacs}

\leavevmode\vadjust pre{\hypertarget{ref-nelson2018}{}}%
Nelson, L. D., Simmons, J., \& Simonsohn, U. (2018). Psychology's renaissance. \emph{Annual Review of Psychology}, \emph{69}(1), 511--534. \url{https://doi.org/10.1146/annurev-psych-122216-011836}

\leavevmode\vadjust pre{\hypertarget{ref-nye2019}{}}%
Nye, C. D., Bradburn, J., Olenick, J., Bialko, C., \& Drasgow, F. (2019). How Big Are My Effects? Examining the Magnitude of Effect Sizes in Studies of Measurement Equivalence. \emph{Organizational Research Methods}, \emph{22}(3), 678--709. \url{https://doi.org/10.1177/1094428118761122}

\leavevmode\vadjust pre{\hypertarget{ref-nye2011}{}}%
Nye, C. D., \& Drasgow, F. (2011). Effect size indices for analyses of measurement equivalence: Understanding the practical importance of differences between groups. \emph{Journal of Applied Psychology}, \emph{96}(5), 966--980. \url{https://doi.org/10.1037/a0022955}

\leavevmode\vadjust pre{\hypertarget{ref-rosseel2012}{}}%
Rosseel, Y. (2012). Lavaan: An r package for structural equation modeling. \emph{Journal of Statistical Software}, \emph{48}(1), 1--36. \url{https://doi.org/10.18637/jss.v048.i02}

\leavevmode\vadjust pre{\hypertarget{ref-stark2006}{}}%
Stark, S., Chernyshenko, O. S., \& Drasgow, F. (2006). Detecting differential item functioning with confirmatory factor analysis and item response theory: Toward a unified strategy. \emph{Journal of Applied Psychology}, \emph{91}(6), 1292--1306. \url{https://doi.org/10.1037/0021-9010.91.6.1292}

\end{CSLReferences}

\newpage

\hypertarget{appendix}{%
\section{Appendix}\label{appendix}}

\begin{table}[tbp]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:unnamed-chunk-1}Model Fit for Invariant Model}

\begin{tabular}{lllllll}
\toprule
Model & AIC & BIC & CFI & TLI & RMSEA & SRMR\\
\midrule
overall & 7,505.72 & 7,547.87 & 0.99 & 0.99 & 0.02 & 0.02\\
group1 & 3,755.75 & 3,790.96 & 0.98 & 0.95 & 0.05 & 0.04\\
group2 & 3,751.95 & 3,787.17 & 0.98 & 0.96 & 0.04 & 0.04\\
configural & 7,527.70 & 7,654.14 & 0.98 & 0.96 & 0.04 & 0.03\\
metric & 7,529.39 & 7,638.97 & 0.95 & 0.93 & 0.06 & 0.05\\
scalar & 7,522.90 & 7,615.62 & 0.96 & 0.96 & 0.04 & 0.05\\
strict & 7,519.51 & 7,591.16 & 0.96 & 0.96 & 0.04 & 0.06\\
\bottomrule
\end{tabular}

\end{threeparttable}
\end{center}

\end{table}

\begin{table}[tbp]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:unnamed-chunk-2}Model Fit for Small Differences in Loadings}

\begin{tabular}{lllllll}
\toprule
Model & AIC & BIC & CFI & TLI & RMSEA & SRMR\\
\midrule
overall & 7,527.67 & 7,569.81 & 0.98 & 0.96 & 0.04 & 0.03\\
group1 & 3,755.75 & 3,790.96 & 0.98 & 0.95 & 0.05 & 0.04\\
group2 & 3,767.83 & 3,803.05 & 0.98 & 0.96 & 0.05 & 0.04\\
configural & 7,543.58 & 7,670.02 & 0.98 & 0.95 & 0.05 & 0.03\\
metric & 7,548.90 & 7,658.48 & 0.94 & 0.92 & 0.07 & 0.06\\
scalar & 7,541.81 & 7,634.53 & 0.95 & 0.95 & 0.05 & 0.06\\
strict & 7,541.66 & 7,613.31 & 0.93 & 0.94 & 0.05 & 0.07\\
\bottomrule
\end{tabular}

\end{threeparttable}
\end{center}

\end{table}

\begin{table}[tbp]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:unnamed-chunk-3}Model Fit for Medium Differences in Loadings}

\begin{tabular}{lllllll}
\toprule
Model & AIC & BIC & CFI & TLI & RMSEA & SRMR\\
\midrule
overall & 7,544.55 & 7,586.70 & 0.97 & 0.94 & 0.05 & 0.03\\
group1 & 3,755.75 & 3,790.96 & 0.98 & 0.95 & 0.05 & 0.04\\
group2 & 3,774.92 & 3,810.14 & 1.00 & 1.00 & 0.02 & 0.03\\
configural & 7,550.67 & 7,677.11 & 0.99 & 0.98 & 0.04 & 0.03\\
metric & 7,562.71 & 7,672.29 & 0.93 & 0.89 & 0.07 & 0.06\\
scalar & 7,556.86 & 7,649.58 & 0.93 & 0.93 & 0.06 & 0.06\\
strict & 7,558.05 & 7,629.70 & 0.91 & 0.92 & 0.06 & 0.08\\
\bottomrule
\end{tabular}

\end{threeparttable}
\end{center}

\end{table}

\begin{table}[tbp]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:unnamed-chunk-4}Model Fit for Large Differences in Loadings}

\begin{tabular}{lllllll}
\toprule
Model & AIC & BIC & CFI & TLI & RMSEA & SRMR\\
\midrule
overall & 7,652.99 & 7,695.14 & 0.98 & 0.97 & 0.04 & 0.03\\
group1 & 3,755.75 & 3,790.96 & 0.98 & 0.95 & 0.05 & 0.04\\
group2 & 3,847.21 & 3,882.42 & 0.97 & 0.94 & 0.08 & 0.04\\
configural & 7,622.96 & 7,749.40 & 0.97 & 0.94 & 0.06 & 0.03\\
metric & 7,659.19 & 7,768.77 & 0.85 & 0.79 & 0.12 & 0.08\\
scalar & 7,652.60 & 7,745.32 & 0.86 & 0.85 & 0.10 & 0.09\\
strict & 7,660.63 & 7,732.27 & 0.82 & 0.85 & 0.10 & 0.12\\
\bottomrule
\end{tabular}

\end{threeparttable}
\end{center}

\end{table}

\begin{table}[tbp]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:unnamed-chunk-5}Model Fit for Small Differences in Intercepts}

\begin{tabular}{lllllll}
\toprule
Model & AIC & BIC & CFI & TLI & RMSEA & SRMR\\
\midrule
overall & 7,509.69 & 7,551.83 & 1.00 & 0.99 & 0.02 & 0.02\\
group1 & 3,755.75 & 3,790.96 & 0.98 & 0.95 & 0.05 & 0.04\\
group2 & 3,760.41 & 3,795.63 & 0.93 & 0.86 & 0.08 & 0.05\\
configural & 7,536.16 & 7,662.60 & 0.95 & 0.91 & 0.07 & 0.04\\
metric & 7,531.36 & 7,640.94 & 0.96 & 0.94 & 0.05 & 0.04\\
scalar & 7,531.34 & 7,624.06 & 0.94 & 0.93 & 0.06 & 0.05\\
strict & 7,523.54 & 7,595.18 & 0.95 & 0.96 & 0.04 & 0.05\\
\bottomrule
\end{tabular}

\end{threeparttable}
\end{center}

\end{table}

\begin{table}[tbp]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:unnamed-chunk-6}Model Fit for Medium Differences in Intercepts}

\begin{tabular}{lllllll}
\toprule
Model & AIC & BIC & CFI & TLI & RMSEA & SRMR\\
\midrule
overall & 7,532.77 & 7,574.92 & 1.00 & 1.00 & 0.01 & 0.02\\
group1 & 3,755.75 & 3,790.96 & 0.98 & 0.95 & 0.05 & 0.04\\
group2 & 3,760.41 & 3,795.63 & 0.93 & 0.86 & 0.08 & 0.05\\
configural & 7,536.16 & 7,662.60 & 0.95 & 0.91 & 0.07 & 0.04\\
metric & 7,531.36 & 7,640.94 & 0.96 & 0.94 & 0.05 & 0.04\\
scalar & 7,554.20 & 7,646.92 & 0.85 & 0.83 & 0.09 & 0.07\\
strict & 7,546.38 & 7,618.03 & 0.86 & 0.88 & 0.08 & 0.07\\
\bottomrule
\end{tabular}

\end{threeparttable}
\end{center}

\end{table}

\begin{table}[tbp]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:unnamed-chunk-7}Model Fit for Large Differences in Intercepts}

\begin{tabular}{lllllll}
\toprule
Model & AIC & BIC & CFI & TLI & RMSEA & SRMR\\
\midrule
overall & 7,569.17 & 7,611.31 & 1.00 & 1.00 & 0.00 & 0.02\\
group1 & 3,755.75 & 3,790.96 & 0.98 & 0.95 & 0.05 & 0.04\\
group2 & 3,760.41 & 3,795.63 & 0.93 & 0.86 & 0.08 & 0.05\\
configural & 7,536.16 & 7,662.60 & 0.95 & 0.91 & 0.07 & 0.04\\
metric & 7,531.36 & 7,640.94 & 0.96 & 0.94 & 0.05 & 0.04\\
scalar & 7,590.29 & 7,683.01 & 0.70 & 0.66 & 0.13 & 0.10\\
strict & 7,582.47 & 7,654.12 & 0.71 & 0.75 & 0.11 & 0.10\\
\bottomrule
\end{tabular}

\end{threeparttable}
\end{center}

\end{table}

\begin{table}[tbp]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:unnamed-chunk-8}Model Fit for Small Differences in Residuals}

\begin{tabular}{lllllll}
\toprule
Model & AIC & BIC & CFI & TLI & RMSEA & SRMR\\
\midrule
overall & 7,439.49 & 7,481.64 & 1.00 & 1.01 & 0.00 & 0.02\\
group1 & 3,755.75 & 3,790.96 & 0.98 & 0.95 & 0.05 & 0.04\\
group2 & 3,683.32 & 3,718.53 & 1.00 & 1.01 & 0.00 & 0.02\\
configural & 7,459.07 & 7,585.51 & 0.99 & 0.98 & 0.03 & 0.03\\
metric & 7,461.41 & 7,570.99 & 0.97 & 0.95 & 0.05 & 0.05\\
scalar & 7,455.85 & 7,548.58 & 0.97 & 0.97 & 0.04 & 0.05\\
strict & 7,453.48 & 7,525.12 & 0.96 & 0.97 & 0.04 & 0.05\\
\bottomrule
\end{tabular}

\end{threeparttable}
\end{center}

\end{table}

\begin{table}[tbp]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:unnamed-chunk-9}Model Fit for Medium Differences in Residuals}

\begin{tabular}{lllllll}
\toprule
Model & AIC & BIC & CFI & TLI & RMSEA & SRMR\\
\midrule
overall & 7,368.57 & 7,410.71 & 1.00 & 1.00 & 0.00 & 0.02\\
group1 & 3,755.75 & 3,790.96 & 0.98 & 0.95 & 0.05 & 0.04\\
group2 & 3,587.77 & 3,622.99 & 1.00 & 1.03 & 0.00 & 0.02\\
configural & 7,363.52 & 7,489.96 & 1.00 & 0.99 & 0.02 & 0.02\\
metric & 7,366.63 & 7,476.21 & 0.97 & 0.96 & 0.05 & 0.05\\
scalar & 7,360.15 & 7,452.87 & 0.98 & 0.98 & 0.03 & 0.05\\
strict & 7,382.53 & 7,454.18 & 0.88 & 0.90 & 0.08 & 0.07\\
\bottomrule
\end{tabular}

\end{threeparttable}
\end{center}

\end{table}

\begin{table}[tbp]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:unnamed-chunk-10}Model Fit for Large Differences in Residuals}

\begin{tabular}{lllllll}
\toprule
Model & AIC & BIC & CFI & TLI & RMSEA & SRMR\\
\midrule
overall & 7,284.21 & 7,326.36 & 1.00 & 1.01 & 0.00 & 0.02\\
group1 & 3,755.75 & 3,790.96 & 0.98 & 0.95 & 0.05 & 0.04\\
group2 & 3,443.47 & 3,478.69 & 0.95 & 0.90 & 0.07 & 0.04\\
configural & 7,219.22 & 7,345.66 & 0.96 & 0.92 & 0.06 & 0.03\\
metric & 7,216.38 & 7,325.96 & 0.96 & 0.94 & 0.05 & 0.04\\
scalar & 7,210.65 & 7,303.37 & 0.96 & 0.96 & 0.04 & 0.05\\
strict & 7,297.89 & 7,369.54 & 0.59 & 0.65 & 0.13 & 0.18\\
\bottomrule
\end{tabular}

\end{threeparttable}
\end{center}

\end{table}

\end{document}

### 2023-03-31 manuscript.Rmd
update

@@
 authornote: |
-  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
-
-  Enter author note here.
+  Thank you to K.D. Valentine and Chelsea Parlett-Pelleriti for feedback on some ugly graphs.
 
@@
 library(cowplot)
+
+# make smaller outputs
+def.source.hook  <- knitr::knit_hooks$get("source")
+knitr::knit_hooks$set(source = function(x, options) {
+  x <- def.source.hook(x, options)
+  x <- ifelse(!is.null(options$size), 
+         paste0("\\", options$size,"\n\n", x, "\n\n \\normalsize"), 
+         x)
+})
 ```
@@
   model.configural <- cfa(model = model, data = data, group = group, meanstructure = T)
-  model.metric <- cfa(model = model, data = data, group = group, group.equal = "loadings")
-  model.scalar <- cfa(model = model, data = data, group = group, group.equal = c("loadings", "intercepts"))
-  model.strict <- cfa(model = model, data = data, group = group, group.equal =  c("loadings", "intercepts", "residuals"))
+  model.metric <- cfa(model = model, data = data, 
+                      group = group, meanstructure = T,
+                      group.equal = "loadings")
+  model.scalar <- cfa(model = model, data = data, 
+                      group = group, meanstructure = T, 
+                      group.equal = c("loadings", "intercepts"))
+  model.strict <- cfa(model = model, data = data, 
+                      group = group, meanstructure = T, 
+                      group.equal =  c("loadings", "intercepts", "residuals"))
 
@@
 lv_name = "lv"
+
+  data_coef = partial.coef
+  model_step = "intercepts"
+  item_name = "RS6"
+  x_limits = c(-1,1)
+  y_limits = c(min(DF$RS7), max(DF$RS7))
+  model_results = partial.rs.2.picture
+  ci_level = .95
+  lv_name = "RS"
 ```
@@
 
+  # get group variable
+  group_var <- model_results@Data@group
+  group_labels <- model_results@Data@group.label
+
   # first get the data
@@
   filter(grepl(item_name, term)) %>%  # pick a question
-  mutate(group = factor(group, levels = names(table(data_coef$group)), labels = c("Group 1", "Group 2")))
+  mutate(group = factor(group, levels = names(table(data_coef$group)), labels = group_labels))
 
@@
   # make the latent mean data for right panel
-  latent_predict <- predict(model_results)
-  latent_means <- data.frame(
-    c(latent_predict[[1]], latent_predict[[2]])
-    )
-  colnames(latent_means) <- colnames(latent_predict[[1]])
-  latent_means$group <- rep(names(latent_predict), 
-                  times = c(length(latent_predict[[1]]), 
-                           length(latent_predict[[2]])))
+  latent_means <- lavPredict(model_results, 
+                               type = "lv", 
+                               label = TRUE,
+                               assemble = TRUE, 
+                               append.data = TRUE)
 
   latent_means$lv <- latent_means[ , lv_name]
+  latent_means$group <- latent_means[ , group_var]
 
@@
                aes(xintercept = mean, color = group)) + 
-    theme(legend.position = "none")
+    theme(legend.position = "none") + 
+    coord_cartesian(xlim = x_limits)
 
@@
     intercept_plot + 
+      ggtitle("Item Invariance") + 
       theme(legend.position = "none") + 
@@
     mean_plot + 
+      ggtitle("Latent Mean Distribution") + 
       theme(legend.position = "none"),
@@
 
-Outline
-
--   talk about LVM
-
--   talk about cfa
-
--   talk about mgcfa
-
--   how are measurement and replication/crisis related
-
--   why it is a bad idea to say that replication/crisis are *because* bad measurement
-
--   how can we visualize and interpret MGCFA to help us understand the impact of measurement differences
-
-By the end of this tutorial manuscript, readers will:
+Psychological assessments play a critical role in our ability to measure and analyze constructs to support theories and experimental hypotheses.
+Defining and creating assessments to validly and reliability measure constructs is often difficult because phenomenon, such as anxiety, are often not directly observable.
+Instead, we use surveys and questionnaires to indirectly assess the underlying construct [@devellis2022].
+Latent variable modeling (i.e., structural equation modeling) is a popular tool for the validation of developed survey instruments to verify scale dimensionalality, structure, and model fit.
+A simple search for scale development reveals thousands of articles in psychology that examine new and previously published work, thus, illustrating the interest in both measurement and the use of validation techniques.
+Unfortunately, except in specialty journals, much of the validity evidence and/or development for measures used in empirical studies is not reported within the journal article [@barry2014, @weidman2017].
+Without this information, it is difficult to interpret individual study conclusions, as validity information allows for judgment of usefulness of the measured values [@flake2020].
+Further, the current focus on replication [@makel2012, @makel2014, @zwaan2018], reproducibility [@nelson2018], and the credibility of our results [@vazire2022] has demonstrated questionable measurement practices - decisions that researchers make like survey selection and scoring that impact the results of the study [@flake2020].
+Transparent reporting of the use and creation of scales can improve both interpretation and reproducibility when using surveys developed to measure latent constructs [@shadish2001].
+
+A secondary concern for developed measures is the potential for differential responding and assessment within target populations.
+For example, @trent2013 examined for potential variability in the Revised Child Anxiety and Depression Scale in White and Black youths [@chorpita2000].
+They found that the scale mostly functioned the same for both White and Black individuals but differences in averages on individual items could potentially affect the scoring and interpretation of the scale results.
+This comparison of sub-populations is the test of measurement invariance [@meredith1993].
+Invariance or equivalence implies that the scale operates in the same fashion for each sub-group, and thus, differences in the final latent variable scores can interpretated as differences in populations.
+Non-invariance suggests that individuals respond or interpret items differently, and thus, differences in scores may represent different scores on the latent variable in the population or differences in measurement.
+Non-invariant measurement may lead to misleading results when making group comparisons, and assessing invariance has become a popular technique in scale development [@vandeschoot2015].
+
+Measurement invariance is typically analyzed using confirmatory factor analysis, specifically, multi-group confirmatory factor analysis (MGCFA) or less often, with item response theory [@stark2006, @tay2015].
+First, the model is examined with the factor structure proposed for the latent and observed variables, and then often these models are assessed for each group separately.
+The two models are then combined together into one nested CFA in order to determine configural invariance [@brown2015, @byrne2001, @kline2016].
+Configural invariance tests if the proposed factor structure is the same between groups.
+In this model, all other estimated parameters are allowed to vary between groups.
+The general approach is to use this model as a baseline for starting a sequential analysis of further restrictions between group parameters (i.e., more restrictive with each step).
+However, models without configural invariance can occur and often point to misspecification for the observed and latent variables within one group (i.e., cross loadings of items onto other latent variables or correlated error terms for one group only).
+
+Next, the estimated parameter between each observed variable and its latent variable are constrained to be equal between groups for metric invariance.
+For example, item 1's factor loading must be equal to item 1's factor loading for each group.
+This test examines if the items represent the same relationship to the latent variable, or if specific items have weaker or stronger relationships in specific groups.
+Finding non-invariance at this stage generally points to items that have different functioning or interpretation for one group.
+At the third model, the item intercepts (i.e., item averages) are restricted across groups for scalar invariance.
+Scalar non-invariance would indicate that items have the same strength of relationship with their latent variable, just one group has a higher overall average on that item.
+Last (although sometimes not used), we may consider constraining error variances for each observed variable to be equal across groups for strict invariance.
+Strict non-invariance can occur when one group has a higher range of values on the observed variable, thus showing a larger variance.
+For example, if using a Likert scale, one group may use the full 1 to 7 range (creating a flatter distribution and larger variance), while the other group shows a ceiling effect of only using 5 to 7.
+
+These concepts have been explored and implemented for the last fifty years [@jöreskog1971, @sörbom1978] and implemented in the most popular structural equation modeling programs [@jöreskog2001, @rosseel2012, @boker2011].
+@byrne1989 extended the ideas of multi-group testing by suggesting partial invariance [followed by @meredith1993].
+Partial invariance occurs when non-invariance is found but can be attributed to only a few parameter estimate differences between groups (i.e., items 1 and 2 have different factor loadings but all others are the same).
+This testing provided an advantage to understand where the potential non-invariance may occur for further study and interpretation guidelines.
+To determine when non-invariance and partial invariance occurred, each model is sequentially compared to the previous model using some form of a difference test.
+Traditionally, since models were nested, a chi-square difference test was used [@meade2008, @cheung2002]; however, given the known issues with chi-square [@thompson1996], people have favored empirical cutoffs for differences in fit indices.
+As the field pushes back against favoring cutoff criteria and rules of thumb [@marsh2004, @putnick2016], an effect size measure for translating "how much" non-invariance was developed $d_{MACS}$ [@nye2011].
+This effect size examines the differences in observed variables between the two groups for both the factor loading and the item intercept; thus, any differences in either or both will increase the effect size for non-invariance [@stark2006].
+
+With $d_{MACS}$ and measurement invariance testing, researchers can begin to quantify how and where their construct measurement may vary between groups.
+However, given the large number of studies that show non-invariance, it is clear that equivalence can be hard to meet.
+It is difficult to know if non-invariance occurs because of random sampling error, true population differences, or differences in replication and reproducibility of the construct in a new sample.
+Further, it is important to remember that the parameter estimates that we are testing are just that - estimates.
+All the parameter estimates have measures of standard error to indicate that they are more than likely variable with a new sample or population.
+Given that this information is generally ignored during the examination of measurement invariance, it may be that we are claiming that many scales are non-invariant, when in reality, the differences between loadings or item intercepts are small and unimportant.
+$d_{MACS}$ provides the opportunity to begin to think about the smallest effect size of interest or the smallest meaningful effect size [@lakens2017, @anvari2021].
+As mentioned, $d_{MACS}$ has only really been explored for a combined intercept and loadings, and while useful, does not necessarily allow a researcher to pinpoint specific issues within an observed variable.
+The purpose of this manuscript is provide readers with a framework for visualization of differences in loadings, intercepts, and variances for each item, and the impact of those differences on the distribution of the latent mean.
+No known visualization techniques have been proposed for measurement invariance.
+By creating panel visualizations, we can supplement a researchers ability to judge the strength of the non-invariance differences and effect size for each item.
+Coupled with other indicators (i.e., fit indice differences, $d_{MACS}$), we can move toward a better understanding of how much measurement non-invariance is meaningful.
+
+By the end of this manuscript, readers will:
 
@@
 These models are normally tested sequentially, and a convenience function `mgcfa` is provided in the supplemental documents for this manuscript.
+Fit indices for the steps for multi-group models are presented in the appendix for comparison of cutoff rules of thumb [@cheung2002] to effect sizes and visualizations presented in this manuscript.
+Fit indices include Akaike Information Criterion [AIC, @akaike1998], Bayesian Information Criterion [BIC, @schwarz1978], Comparative Fit Index [CFI, @bentler1990], Tucker Lewis Index [TLI, @tucker1973], root mean squared error of approximation RMSEA [@steiger1990], and standardized root mean squar residual [SRMR, @bentler1995].
 
@@
 
+# Results
+
 ```{r create-models}
 # overall model
-model.overall <- "lv =~ q1 + q2 + q3 + q4 + q5"
+model.overall <- "lv =~ q1 + q2 + q3 + q4 + q5
+q1 ~ 0*1
+lv ~ 1"
 
@@
 q4 ~~ 1*q4
-q4 ~ 0*1"
+q4 ~ 0*1
+q1 ~ 0*1
+lv ~ 1"
 model.invariant.g2 <- "lv =~ .77*q1 + .43*q2 + .58*q3 + .3*q4 + .61*q5
 q4 ~~ 1*q4
-q4 ~ 0*1"
+q4 ~ 0*1
+q1 ~ 0*1
+lv ~ 1"
 
 # loadings
-model.small.load.g2 <- "lv =~ .77*q1 + .43*q2 + .58*q3 + .5*q4 + .61*q5"
-model.med.load.g2 <- "lv =~ .77*q1 + .43*q2 + .58*q3 + .6*q4 + .61*q5"
-model.large.load.g2 <- "lv =~ .77*q1 + .43*q2 + .58*q3 + 1.1*q4 + .61*q5"
+model.small.load.g2 <- "lv =~ .77*q1 + .43*q2 + .58*q3 + .5*q4 + .61*q5
+q1 ~ 0*1
+lv ~ 1"
+model.med.load.g2 <- "lv =~ .77*q1 + .43*q2 + .58*q3 + .6*q4 + .61*q5
+q1 ~ 0*1
+lv ~ 1"
+model.large.load.g2 <- "lv =~ .77*q1 + .43*q2 + .58*q3 + 1.1*q4 + .61*q5
+q1 ~ 0*1
+lv ~ 1"
 
@@
 model.small.int.g2 <- "lv =~ .77*q1 + .43*q2 + .58*q3 + .34*q4 + .61*q5
-q4 ~ .25*1"
+q4 ~ .25*1
+q1 ~ 0*1
+lv ~ 1"
 model.med.int.g2 <- "lv =~ .77*q1 + .43*q2 + .58*q3 + .34*q4 + .61*q5
-q4 ~ .5*1"
+q4 ~ .5*1
+q1 ~ 0*1
+lv ~ 1"
 model.large.int.g2 <- "lv =~ .77*q1 + .43*q2 + .58*q3 + .34*q4 + .61*q5
-q4 ~ .75*1"
+q4 ~ .75*1
+q1 ~ 0*1
+lv ~ 1"
 
@@
 model.small.res.g2 <- "lv =~ .77*q1 + .43*q2 + .58*q3 + .34*q4 + .61*q5
-q4 ~~ .75*q4"
+q4 ~~ .75*q4
+q1 ~ 0*1
+lv ~ 1"
 model.med.res.g2 <- "lv =~ .77*q1 + .43*q2 + .58*q3 + .34*q4 + .61*q5
-q4 ~~ .5*q4"
+q4 ~~ .5*q4
+q1 ~ 0*1
+lv ~ 1"
 model.large.res.g2 <- "lv =~ .77*q1 + .43*q2 + .58*q3 + .34*q4 + .61*q5
-q4 ~~ .25*q4"
+q4 ~~ .25*q4
+q1 ~ 0*1
+lv ~ 1"
 ```
@@
 ```
+
+## Code Examples
+
+The complete code for this manuscript can be found at <https://osf.io/wev5f/>, and the function code for the convenience function for multi-group models and plots is found in the appendix.
+First, we would create our model code in `lavaan` syntax.
+The `lv` latent variable predicts the five measured variables, which are present as columns in our `df.invariant` dataset.
+You would include the dataframe in the `data` argument of our function, the name of the grouping variable in quotes for `group`, and the `lavaan` model syntax in the `model` argument.
+The `mgcfa` function code runs an overall model with all data, regardless of group, each group separately on the model, then the steps described above: configural, metric, scalar, and strict invariance.
+
+`lavaan` automatically sets the mean (i.e., the intercept) for latent variables to zero.
+If we wish to visualize the impact of the changes in parameter estimates across groups on the latent means, we need to allow the latent mean estimation with `lv ~ 1`.
+However, adding this estimation into our model will create a non-identified model.
+To solve this problem, you can set one of the intercepts of another variable to a value to scale the model.
+Here we will set the scale of the model by using `q1 ~ 0*1`, thus, scaling the expected means to zero.
+With simulation, this step is easy to know which variable to pick - we set the intercept on the variable we know did not show differences.
+In real data, you may wish to run the model steps *without* setting this option, examine the results of a configural or separate models, and then add the option for the values most similar.
+Additionally, you could complete partial invariance steps to determine which value appears most consistent to fix.
+
+```{r eval = T, include = T, echo = T, size = "small"}
+# create lavaan model
+model.overall <- "
+# overall one-factor model
+lv =~ q1 + q2 + q3 + q4 + q5
+# set the intercept (mean) of q1 to zero
+q1 ~ 0*1
+# allow the lv intercept to be freely estimated
+lv ~ 1"
+# look at the data
+head(df.invariant)
+# run our mgcfa function to run all models
+results.invariant <- mgcfa(data = df.invariant, #dataframe
+                           group = "group", 
+                           model = model.overall)
+# what is saved for you
+names(results.invariant)
+```
+
+The results are saved as a list and include the following:
+
+1)  `model_coef`: a tidy dataframe with *all* model's coefficients saved from the `lavaan` outputs.
+Note that we can see that the intercept `~1` is set for question 1 but freely estimated for the latent variable.
+
+```{r echo = T, include = T, size = "small"}
+results.invariant$model_coef[1:10 , ]
+```
+
+2)  `model_fit`: a tidy dataframe with *all* model's fit indices saved from the `lavaan` outputs.
+
+```{r echo = T, include = T, size = "small"}
+head(results.invariant$model_fit)
+```
+
+3)  Saved `lavaan` fitted objects that you can use the `summary()`, `parameterEstimates()`, `fitIndices()`, etc.
+on.
+Overall model indicates the model without grouping variables testing all data on the proposed model structure.
+This model is then tested separately for each group (`model.group1`, `model.group2`).
+The final models follow the @brown2015 naming convention for sequential steps for testing MGCFA for measurement invariance (`model.configural`, `model.metric`, `model.scalar`, `model.strict`).
+
+The results from the `model_coef` table can then be used directly in the suggested plotting function. The plot outputs will be described below. First, here are the arguments for the function:
+
+1)  `data_coef`: A tidy dataframe of the parameter estimates from the models.
+This function assumes you have used `broom::tidy()` on the saved model from `lavaan` and added a column called "model" with the name of the model step.
+This function will only run for models that have used the grouping function (i.e., configural, metric, scalar, and strict or other combinations/steps you wish to examine).
+
+2)  `model_step`: Which model do you want to plot? You should match this name to the one you want to extract from your model column in the `data_coef`.
+
+3)  `item_name`: Which observed variable from your model syntax do you want to plot? Please list this variable name exactly how it appears in the model.
+
+4)  `x_limits`: What do you want the x-axits limits to be for your invariance plot?
+The default option is to assume the latent variable is standardized, and therefore, -1 to 1 is recommended.
+Use only two numbers, a lower and upper limit.
+This value also constrains the latent mean diagram to help zoom in on group differences because the scale of latent means is usually centered over zero.
+You can use this parameter to zoom out to a more traditional histogram using `c(-2, 2)`.
+
+5)  `y_limits`: What do you want the y-axits limits to be for your invariance plot?
+Given that the latent variable is used to predict the observed values in the data, you could use the minimum and maximum values found in the data.
+If that range is large, consider reducing this value to be able to visualize the results (i.e., otherwise it may be too zoomed out to judge group differences).
+Use only two numbers, a lower and upper limit.
+
+6)  `ci_level`: What confidence limit do you want to plot? Use 1 - $\alpha$.
+
+7)  `model_results`: In this argument, include the saved `lavaan` output for the model listed in the `model_step` argument.
+
+8)  `lv_name`: Include the name of the latent variable, exactly how it is listed in your `lavaan` syntax.
+You should plot the latent variable that the `item_name` is linked to.
+If you have items that load onto multiple latent variables, you will need to make multiple plots.
+
+```{r eval = F, echo = T, include = T, size = "small"}
+plot_mgcfa(
+  data_coef = results.invariant$model_coef, # output from model_coef
+  model_step = "configural", # which model do you want to plot
+  item_name = "q4", # name of observed item
+  x_limits = c(-1,1), # latent variable limits to graph
+  y_limits = c(min(df.invariant$q4), max(df.invariant$q4)), # Y min and max in data 
+  ci_level = .95, # what ci do you want
+  model_results = results.invariant$model.configural, # what model results do you want 
+  lv_name = "lv" # which latent variable do you want 
+)
+```
+
+## Visualization of Invariance
+
+The output from this model can be found in Figure \@ref(fig:invariant-pic).
+On the left hand side, the item invariance is plotted, and on the right hand side, the latent mean distributions for the two groups are plotted.
+In the item invariance sub-plot, the visualization includes all three components traditionally seen in MGCFA testing steps: loadings, intercepts, and residuals.
+Each visualization element was designed to match the traditional visualization for that type of output.
+All parameter estimates are plotted on the unstandardized estimates and their confidence interval based on the standard error of the estimate.
+
+### Loadings
+
+Factor loadings represent the slope of the regression equation for the latent variable predicting the scores on the observed variable ($\hat{Y} \sim b_0 + b_1X + \epsilon$).
+Therefore, the latent variable is shown on the x-axis using standardized values (i.e., *z*-scores) where -1 indicates one standard deviation below the mean for the latent variable, 0 indicates the mean for the latent variable and so on.
+The y-axis indicates the observed variable scores, and here, the plot includes the entire range of the scale of the data for item four.
+The coefficient ($b_1$) for group 1 was `r apa_num(results.invariant$model_coef %>% filter(model == "configural") %>% filter(grepl("q4", term)) %>% filter(op == "=~") %>% slice_head() %>% pull(estimate))`, while the coefficient for group 2 was `r apa_num(results.invariant$model_coef %>% filter(model == "configural") %>% filter(grepl("q4", term)) %>% filter(op == "=~") %>% slice_tail() %>% pull(estimate))`.
+The ribbon bands around the plotted slopes indicate the confidence interval for that estimate.
+In this plot, while the coefficients for each group are not literally equal, the overlapping and parallel slope bands indicate they are not different practically.
+
+### Intercepts
+
+The item intercepts ($b_0$) are plotted on the middle line where they would cross the y-axis at a latent variable score of zero.
+These are represented by a dot with a set of confidence error bars around the point.
+The intercept for group 1 was `r apa_num(results.invariant$model_coef %>% filter(model == "configural") %>% filter(grepl("q4", term)) %>% filter(op == "~1") %>% slice_head() %>% pull(estimate))`, while the coefficient for group 2 was `r apa_num(results.invariant$model_coef %>% filter(model == "configural") %>% filter(grepl("q4", term)) %>% filter(op == "~1") %>% slice_tail() %>% pull(estimate))`.
+In this invariant depiction, the overlap in the intercepts is clear, indicating they are not different.
+You can use `y_limits` to zoom in on the graph if these are too small to be distinguishable.
+
+### Residuals
+
+Residuals are trickier to plot, as they are the left over error when predicting the observed variables $\epsilon$.
+It is tempting to plot this value as the confidence band around the slope, however, that defeats the purpose of understanding that the slopes are estimated separately from the residuals, and both have an associated variability around their parameter estimate.
+Therefore, residuals are represented in the inset picture at the bottom right of the item invariance plot.
+The black bars represent the estimated residual for each group (group 1: `r apa_num(results.invariant$model_coef %>% filter(model == "configural") %>% filter(grepl("q4", term)) %>% filter(op == "~~") %>% slice_head() %>% pull(estimate))`, group 2: `r apa_num(results.invariant$model_coef %>% filter(model == "configural") %>% filter(grepl("q4", term)) %>% filter(op == "~~") %>% slice_tail() %>% pull(estimate))`).
+The distributions are plotted to represent the normal spread of values using the standard error of the residuals.
+The violin plot allows for direct comparison of those residuals and their potential distributions.
+Note that the placement has nothing to do with the x or y-axis and is designed to always show in the same location, regardless of size/value.
+
+### Latent Means
+
+The overall impact of differences on the latent means can be found in the right hand visualization.
+The latent means are calculated by using the `lavPredict` function and then plotted as overlapping histograms.
+The vertical colored lines represent the mean for each group, and the spread of the distribution can be examined using the density coloring.
+Finally, group labels are represented in the figure caption on the bottom.
+Group 1 is usually the group that is alphabetically first in the dataset or whichever group is the first that appears when using the `levels()` command.
 
@@
 
+### Graphing Effect Size
+
+The $d_{MACS}$ value for item 4 in the invariant model was `r apa_num(d_invariant)$DMACS[4]`, representing a nil or unimportant difference in this manuscript.
+It is important to note that while @nye2019 suggests specific sizes for small, medium, and large, each researcher should determine for themselves what effects represent.
+Figure \@ref(fig:small-load-pic) displays the results from the small ($d_{MACS}$ = `r apa_num(d_small_load)$DMACS[4]`) difference in loadings, while Figure \@ref(fig:med-load-pic) displays the results from the medium ($d_{MACS}$ = `r apa_num(d_med_load)$DMACS[4]`) difference in loadings, and Figure \@ref(fig:large-load-pic) shows the large ($d_{MACS}$ = `r apa_num(d_large_load)$DMACS[4]`) differences.
+When investigating the slope values, we can clearly see the change in the loading for the second group (the only manipulated variable, although random dataset generation may also change intercepts and residuals slightly).
+At the medium effect size, we see that the confidence bands do not overlap (at the edges), and at the large effect size, we can see a clear separation of two lines.
+Note that the intercepts in this model are estimated as equal so the loading representation will not literally separate, but the steepness of the lines is the indicator of the difference between the slopes.
+You can imagine these lines are interpreted like a simple slopes analysis for interactions in regression [@cohen2003].
+When simple slopes for interactions are plotted, if they are parallel, there is no interaction, and if they cross, then there is an interaction.
+Here, we can use this same logic.
+If they are parallel, there is likely invariance (they are the same), and the further from parallel they become, the larger the effect size for the differences between group loadings.
+
+The latent means in Figure \@ref(fig:large-load-pic) do appear to show differences, albeit visually small.
+The latent means diagram shows the impact of any group differences that aren't constrained, and this image shows the configural model (as the metric model would force them to be equal).
+In the simulated model, the *only* manipulated parameter is question 4's loading.
+In real models, the differences may be larger due to other variation found in the parameter estimates.
+Therefore, once you discover items you believe would make a model "partially" invariant, you may wish to estimate that model and graph the item again using the partially invariant model to see only the effect of the non-invariant items.
+Additionally, consider that we set the scaling of the model to 0.
+The estimate for the lv mean in the large loading model was group 1: `r apa_num(results.invariant$model_coef %>% filter(model == "configural") %>% filter(grepl("lv", term)) %>% filter(op == "~1") %>% slice_head() %>% pull(estimate))`, and group 2: `r apa_num(results.invariant$model_coef %>% filter(model == "configural") %>% filter(grepl("lv", term)) %>% filter(op == "~1") %>% slice_tail() %>% pull(estimate))`, which results in `r apa_num(results.invariant$model_coef %>% filter(model == "configural") %>% filter(grepl("lv", term)) %>% filter(op == "~1") %>% slice_head() %>% pull(estimate) - results.invariant$model_coef %>% filter(model == "configural") %>% filter(grepl("lv", term)) %>% filter(op == "~1") %>% slice_tail() %>% pull(estimate))` difference in group means.
+The practical implications of this difference will depend on the research and interpretations of the researcher.
+
 ```{r small-load-pic, include = T, fig.cap = "Small Loadings Model Visualization"}
@@
 
+For intercepts, the small (Figure \@ref(fig:small-int-pic)), medium (Figure \@ref(fig:med-int-pic)), and large (Figure \@ref(fig:large-int-pic)) depictions represent $d_{MACS}$ values of `r apa_num(d_small_int)$DMACS[4]`, `r apa_num(d_med_int)$DMACS[4]`, and `r apa_num(d_large_int)$DMACS[4]`, respectively.
+Intercept differences can be clearly seen represented by the spacing out of the intercept locations (and thus, the overall line as well).
+Note how little the intercept differences appear to influence the latent variable means and distributions.
+
 ```{r small-int-pic, include = T, fig.cap = "Small Intercepts Model Visualization"}
@@
 
+Last, the effect of the residuals is plotted in small (Figure \@ref(fig:small-res-pic)), medium (Figure \@ref(fig:med-res-pic)), and large (Figure \@ref(fig:large-res-pic)) formats.
+While $d_{MACS}$ values are not technically avaliable for the residuals, our models showed `r apa_num(d_small_res)$DMACS[4]`, `r apa_num(d_med_res)$DMACS[4]`, and `r apa_num(d_large_res)$DMACS[4]`, respectively.
+These differences in values are variable due to the random generation of datasets for each measurement invariance manipulation.
+At first glance, the differences in the small chart may seem large, because the black lines are not touching, but notice that the distributions overlap, indicating a likely small difference.
+The medium and large differences better illustrate differences in residuals across groups.
+Further, the impact of the residuals on the shape of the latent mean distribution can also been seen (and unintentionally, in the first figures as well due to random variation).
+The impact is due to the standard error of the residuals, as smaller standard errors represent lepokurtic distributions (taller), and larger standard errors represent platykurtic distributions (flatter).
+The effect size difference of the residuals does not appear to change the effects in the latent means.
+
 ```{r small-res-pic, include = T, fig.cap = "Small Residuals Model Visualization"}
@@
 
-# Results
+## An Example Analysis
+
+```{r eval = F, include = F}
+library(rio)
+
+DF <- bind_rows(
+  import("data/Adult CFA.sav") %>% select(-Age) %>% 
+    mutate(sample = "Clinical"),
+  import("data/Adult EFA.sav") %>% select(-Age) %>% 
+    mutate(sample = "Clinical"),
+  import("data/Student CFA.sav") %>% select(-Age) %>% 
+    mutate(sample = "Student"),
+  import("data/Student EFA.sav") %>% select(-Age) %>% 
+    mutate(sample = "Student")
+) %>% select(RS1:RS14, sample)
+
+save(DF, file = "RS14.Rdata")
+```
+
+@aiena2014 examined the RS-14 [@wagnild2009] exploring the factor structure of the Resiliency Scale in a clinical sample receiving treatment services and a college student sample.
+Measurement invariance was calculated for differences separately for these samples for gender and race finding a partially invariant models with a few item intercepts or residuals that differed between groups.
+@aiena2014 did not compare the clinical to the student sample for measurement invariance, and it is reasonable to expect potential differences in these two populations.
+
+```{r echo = T, include = T, size = "small"}
+load("RS14.Rdata")
+model.rs <- "RS =~ RS1+RS2+RS3+RS4+RS5+RS6+RS7+RS8+RS9+RS10+RS11+RS12+RS13+RS14"
+results.rs <- mgcfa(data = DF, 
+                    group = "sample", 
+                    model = model.rs)
+
+results.rs$model_fit %>% select(model, AIC, BIC, cfi, tli, rmsea, srmr)
+
+##write out partial codes
+partial_syntax <- paste(colnames(DF)[1:14], "~1") #all columns again 
+partial_syntax
+
+CFI_list  <- 1:length(partial_syntax)
+names(CFI_list) <- partial_syntax
+
+for (i in 1:length(partial_syntax)){
+
+  temp <- cfa(model = model.rs, 
+              data = DF,
+              meanstructure = TRUE,
+              group = "sample",
+              group.equal = c("loadings", "intercepts"),
+              group.partial = partial_syntax[i])
+
+  CFI_list[i] <- fitmeasures(temp, "cfi")
+}
+
+CFI_list
+
+partial.rs <- cfa(model = model.rs, 
+                  data = DF, 
+                  meanstructure = TRUE,
+                  group = "sample", 
+                  meanstructure = T, 
+                  group.equal = c("loadings", "intercepts"),
+                  group.partial = c("RS7~1")
+)
+
+tidy(partial.rs)
+glance(partial.rs)
+results.rs$model_fit
+
+partial.rs.2 <- cfa(model = model.rs, 
+                  data = DF, 
+                  meanstructure = TRUE,
+                  group = "sample", 
+                  meanstructure = T, 
+                  group.equal = c("loadings", "intercepts"),
+                  group.partial = c("RS7~1", "RS6~1")
+)
+
+tidy(partial.rs.2)
+glance(partial.rs.2)
+
+partial.rs.2.strict <- cfa(model = model.rs, 
+                  data = DF, 
+                  meanstructure = TRUE,
+                  group = "sample", 
+                  meanstructure = T, 
+                  group.equal = c("loadings", "intercepts", "residuals"),
+                  group.partial = c("RS7~1", "RS6~1")
+)
+
+tidy(partial.rs.2.strict)
+glance(partial.rs.2.strict)
+
+model.rs.picture <- "RS =~ RS1+RS2+RS3+RS4+RS5+RS6+RS7+RS8+RS9+RS10+RS11+RS12+RS13+RS14
+RS~1
+RS1~0*1"
+
+partial.rs.2.picture <- cfa(model = model.rs, 
+                  data = DF, 
+                  meanstructure = TRUE,
+                  group = "sample", 
+                  meanstructure = T, 
+                  group.equal = c("loadings", "intercepts"),
+                  group.partial = c("RS7~1", "RS6~1"))
+
+partial.coef <- tidy(partial.rs.2.picture) %>% 
+  mutate(model = "intercepts")
+
+plot_mgcfa(
+  data_coef = partial.coef,
+  model_step = "intercepts", 
+  item_name = "RS6",
+  x_limits = c(-1,1),
+  y_limits = c(min(DF$RS7), max(DF$RS7)),
+  model_results = partial.rs.2.picture, 
+  ci_level = .95,
+  lv_name = "RS"
+)
+
+```
+
+```{r echo = T, include = T, size = "small"}
+
+```
 
@@
 
-```{r}
+## Model Fit Statistics
+
+Model fit statistics are provided for each of the ten model combinations (invariant, three sizes for each ladings, intercepts, and residuals).
+These tables could be used to examine the traditional change in fit statistics cutoff rules of thumb [@cheung2002], such as $\Delta$ CFI or $\Delta$ RMSEA, to the visualizations presented in the manuscript.
+
+```{r tab1, results='asis'}
 apa_table(results.invariant$model_fit %>% 
@@
 
-```{r}
+```{r tab2, results='asis'}
 apa_table(results.small.load$model_fit %>% 
@@
 
-```{r}
+```{r tab3, results='asis'}
 apa_table(results.med.load$model_fit %>% 
@@
 
-```{r}
+```{r tab4, results='asis'}
 apa_table(results.large.load$model_fit %>% 
@@
 
-```{r}
+```{r tab5, results='asis'}
 apa_table(results.small.int$model_fit %>% 
@@
 
-```{r}
+```{r tab6, results='asis'}
 apa_table(results.med.int$model_fit %>% 
@@
 
-```{r}
+```{r tab7, results='asis'}
 apa_table(results.large.int$model_fit %>% 
@@
 
-```{r}
+```{r tab8, results='asis'}
 apa_table(results.small.res$model_fit %>% 
@@
 
-```{r}
+```{r tab9, results='asis'}
 apa_table(results.med.res$model_fit %>% 
@@
 
-```{r}
+```{r tab10, results='asis'}
 apa_table(results.large.res$model_fit %>% 
@@
 ```
+
+## MGCFA Convenience Function
+
+Please note that any partial invariance is not automatically included in this function.
+This function returns a list with all model summaries, the model coefficients in a tidy dataframe, and the model fit statistics in a tidy dataframe.
+You will need the libraries listed below for this function to work properly.
+
+```{r cfa-append, include = T, echo = T, size = "small"}
+library(lavaan)
+library(dplyr)
+library(broom)
+# CFA function
+mgcfa <- function(data, group, model){
+
+  group_names <- unique(data[ , group])
+
+  model.overall <- cfa(model = model, data = data)
+  model.group1 <- cfa(model = model, 
+                      data = subset(data, group == group_names[1]))
+  model.group2 <- cfa(model = model, 
+                      data = subset(data, group == group_names[2]))
+  model.configural <- cfa(model = model, data = data, 
+                          group = group, meanstructure = T)
+  model.metric <- cfa(model = model, data = data, 
+                      group = group, meanstructure = T,
+                      group.equal = "loadings")
+  model.scalar <- cfa(model = model, data = data, 
+                      group = group, meanstructure = T, 
+                      group.equal = c("loadings", "intercepts"))
+  model.strict <- cfa(model = model, data = data, 
+                      group = group, meanstructure = T, 
+                      group.equal =  c("loadings", "intercepts", "residuals"))
+
+  model_coef <- bind_rows(
+    tidy(model.overall, conf.level = .95) %>% 
+      mutate(model = "overall"), 
+    tidy(model.group1, conf.level = .95) %>% 
+      mutate(model = "group1"), 
+    tidy(model.group2, conf.level = .95) %>% 
+      mutate(model = "group2"), 
+    tidy(model.configural, conf.level = .95) %>% 
+      mutate(model = "configural"), 
+    tidy(model.metric, conf.level = .95) %>% 
+      mutate(model = "metric"), 
+    tidy(model.scalar, conf.level = .95) %>% 
+      mutate(model = "scalar"), 
+    tidy(model.strict, conf.level = .95) %>% 
+      mutate(model = "strict")
+  )
+
+  model_fit <- bind_rows(
+    glance(model.overall) %>% mutate(model = "overall"), 
+    glance(model.group1) %>% mutate(model = "group1"), 
+    glance(model.group2) %>% mutate(model = "group2"), 
+    glance(model.configural) %>% mutate(model = "configural"), 
+    glance(model.metric) %>% mutate(model = "metric"), 
+    glance(model.scalar) %>% mutate(model = "scalar"), 
+    glance(model.strict) %>% mutate(model = "strict")
+    )
+
+  return(list(
+    "model_coef" = model_coef,
+    "model_fit" = model_fit,
+    "model.overall" = model.overall,
+    "model.group1" = model.group1,
+    "model.group2" = model.group2,
+    "model.configural" = model.configural,
+    "model.metric" = model.metric,
+    "model.scalar" = model.scalar,
+    "model.strict" = model.strict
+  ))
+
+}
+```
+
+## Measurement Invariance Plot Function
+
+This function creates the plots shown in the manuscript.
+You will need the libraries listed for this function to work.
+Plots may be modified to rearrange for those who are familiar with `ggplot2`.
+Please note that the function assumes you will use the outputs from the previous `mgcfa` function or a tidy dataframe that includes the coefficients from the model with a column `model` that indicates which step of the MGCFA you are wanting to plot.
+If you have more than two groups, you should first filter the dataframe model coefficient outputs to only include to the two groups you want to compare.
+This code does not plot more than two groups (although, it could be modified for this, but the assumption here is that you only have two, as this is how you would normally proceed in a MGCFA using pairwise comparisons to find where the invariance occurs).
+
+```{r plot-append, include = T, echo = T, size = "small"}
+library(dplyr)
+library(ggplot2)
+library(cowplot)
+library(lavaan)
+# devtools::install_github("psyteachr/introdataviz")
+library(introdataviz)
+# Plot MI MGCFA
+plot_mgcfa <- function(data_coef, # output from model_coef
+                       model_step, # which model
+                       item_name, # name of observed item
+                       x_limits = c(-1,1), # LV limits to graph
+                       y_limits, # Y min and max in data 
+                       ci_level, # what ci do you want
+                       model_results, # what model results do you want 
+                       lv_name # which latent is the observed variable on
+                       ){
+
+  # calculate cutoff
+  cutoff <- qt(p = (1-ci_level)/2, 
+               df = sum(unlist(model_results@Data@nobs)), 
+               lower.tail = F)
+
+  # get group variable
+  group_var <- model_results@Data@group
+  group_labels <- model_results@Data@group.label
+
+  # first get the data
+  graph.data <- data_coef %>% # put in tidy coefficients
+  filter(model == model_step) %>% # pick a model
+  filter(grepl(item_name, term)) %>%  # pick a question
+  mutate(group = factor(group, levels = names(table(data_coef$group)), labels = group_labels))
+
+  # make ribbon data y = slope*x + intercept for ci for slopes 
+  ribbondata <- bind_rows(
+    data.frame(
+    x = seq(from = x_limits[1] - 1,  
+            to = x_limits[2] + 1, 
+            by = .05), 
+    group = unique(graph.data$group)[1]
+  ) %>% 
+    mutate(ymin = (graph.data %>% filter(op == "=~") %>% 
+                 slice_head() %>% pull(estimate) * x) - 
+             (cutoff*graph.data %>% filter(op == "=~") %>% 
+                    slice_head() %>% pull(std.error)) +
+             graph.data %>% filter(op == "~1") %>% 
+                 slice_head() %>% pull(estimate), 
+           ymax = (graph.data %>% filter(op == "=~") %>% 
+                 slice_head() %>% pull(estimate) * x) + 
+             (cutoff*graph.data %>% filter(op == "=~") %>% 
+                    slice_head() %>% pull(std.error)) +
+             graph.data %>% filter(op == "~1") %>% 
+                 slice_head() %>% pull(estimate)), 
+    data.frame(
+      x = seq(from = x_limits[1] - 1,  
+              to = x_limits[2] + 1, 
+              by = .05), 
+      group = unique(graph.data$group)[2]
+    ) %>% 
+      mutate(ymin = (graph.data %>% filter(op == "=~") %>% 
+                   slice_tail() %>% pull(estimate) * x) - 
+               (cutoff*graph.data %>% filter(op == "=~") %>% 
+                      slice_tail() %>% pull(std.error)) +
+               graph.data %>% filter(op == "~1") %>% 
+                   slice_tail() %>% pull(estimate), 
+             ymax = (graph.data %>% filter(op == "=~") %>% 
+                   slice_tail() %>% pull(estimate) * x) + 
+               (cutoff*graph.data %>% filter(op == "=~") %>% 
+                      slice_tail() %>% pull(std.error)) +
+               graph.data %>% filter(op == "~1") %>% 
+                   slice_tail() %>% pull(estimate))
+  )
+
+  # make point data to draw on the intercepts 
+  pointdata <- data.frame(
+  x = c(0,0),
+  y = graph.data %>% filter(op == "~1") %>% pull(estimate), 
+  group = graph.data %>% filter(op == "~1") %>% pull(group),
+  ymin = graph.data %>% filter(op == "~1") %>% pull(estimate) - 
+    cutoff * graph.data %>% filter(op == "~1") %>% pull(std.error), 
+  ymax = graph.data %>% filter(op == "~1") %>% pull(estimate) + 
+    cutoff * graph.data %>% filter(op == "~1") %>% pull(std.error)
+  )
+
+  # make the line data to draw on the slopes
+  linedata <- data.frame(
+  slope = graph.data %>% filter(op == "=~") %>% pull(estimate), 
+  intercept = graph.data %>% filter(op == "~1") %>% pull(estimate), 
+  group = graph.data %>% filter(op == "~1") %>% pull(group)
+  )
+
+  # make the distributions for the residuals 
+  violindata <- data.frame(
+  y = c(rnorm(n = 1000, 
+            mean = graph.data %>% filter(op == "~~") %>% 
+              slice_head() %>% pull(estimate), 
+            sd = graph.data %>% filter(op == "~~") %>% 
+              slice_head() %>% pull(std.error)), 
+        rnorm(n = 1000, 
+            mean = graph.data %>% filter(op == "~~") %>% 
+              slice_tail() %>% pull(estimate), 
+            sd = graph.data %>% filter(op == "~~") %>% 
+              slice_tail() %>% pull(std.error))),
+  group = c(rep(graph.data %>% filter(op == "~~") %>% 
+              slice_head() %>% pull(group), 1000),
+            rep(graph.data %>% filter(op == "~~") %>% 
+              slice_tail() %>% pull(group), 1000)), 
+  x = 1
+  )
+
+  # make the latent mean data for right panel
+  latent_means <- lavPredict(model_results, 
+                               type = "lv", 
+                               label = TRUE,
+                               assemble = TRUE, 
+                               append.data = TRUE)
+
+  latent_means$lv <- latent_means[ , lv_name]
+  latent_means$group <- latent_means[ , group_var]
+
+  # make a plot of the variance
+  variance_plot <- 
+  ggplot(violindata, aes(x = 1, y = y, color = group, fill = group)) + 
+  geom_split_violin() + 
+  theme_void() + 
+  theme(legend.position = "none") + 
+  stat_summary(fun = "mean",
+               geom = "crossbar", 
+               width = 0.5,
+               colour = "black")
+
+  # make the plot with intercepts and slopes
+  intercept_plot <- 
+  ggplot() + 
+  # basic set up
+  theme_classic() + 
+  xlab("Latent Variable") + 
+  ylab("Observed Variable") + 
+  coord_cartesian(xlim = x_limits, ylim = y_limits) + 
+  # plot the intercepts 
+  geom_point(data = pointdata, 
+             aes(x = x, y = y, color = group), 
+             inherit.aes = FALSE) + 
+  geom_errorbar(data = pointdata,
+                aes(x = x, ymin = ymin, ymax = ymax, color = group), 
+                inherit.aes = FALSE, width = .10) + 
+  # plot the slopes
+  geom_abline(data = linedata,
+              aes(slope = slope, intercept = intercept, color = group)) + 
+  geom_ribbon(data = ribbondata, 
+              aes(x = x, ymin = ymin, ymax = ymax, fill = group), 
+              inherit.aes = FALSE, alpha = .2) + 
+  scale_color_discrete(name = "Group") + 
+  scale_fill_discrete(name = "Group") + 
+  geom_vline(xintercept = 0) + 
+  theme(axis.line.y = element_blank())
+
+  # make the latent means plot
+  mean_plot <- ggplot(latent_means, aes(x = lv, fill = group)) + 
+    geom_density(alpha = .2) + 
+    theme_classic() + 
+    xlab("Latent Variable") + 
+    ylab("Density") + 
+    geom_vline(data = latent_means %>% group_by(group) %>% summarize(mean = mean(lv)), 
+               aes(xintercept = mean, color = group)) + 
+    theme(legend.position = "none") + 
+    coord_cartesian(xlim = x_limits)
+
+  y_range = abs(y_limits[2] - y_limits[1])
+
+  # line up the two plots 
+  prow <- plot_grid(
+    intercept_plot + 
+      ggtitle("Item Invariance") + 
+      theme(legend.position = "none") + 
+      annotation_custom(ggplotGrob(variance_plot), 
+                        xmin = .25, xmax = 1, 
+                        ymin = y_limits[1], ymax = y_limits[2]-y_range/1.8),
+    mean_plot + 
+      ggtitle("Latent Mean Distribution") + 
+      theme(legend.position = "none"),
+    align = 'vh',
+    hjust = -1,
+    nrow = 1
+  )
+
+  # get the lengend
+  legend_b <- get_legend(
+    intercept_plot + 
+      guides(color = guide_legend(nrow = 1)) +
+      theme(legend.position = "bottom")
+  )
+
+  # send out the plot 
+  plot_grid(prow, legend_b, ncol = 1, rel_heights = c(1, .1))
+
+}
+```

### 2023-03-31 manuscript.tex
update

@@
 \usepackage{xcolor}
+\usepackage{color}
+\usepackage{fancyvrb}
+\newcommand{\VerbBar}{|}
+\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
+\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
+% Add ',fontsize=\small' for more characters per line
+\usepackage{framed}
+\definecolor{shadecolor}{RGB}{248,248,248}
+\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
+\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
+\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
+\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
+\newcommand{\BuiltInTok}[1]{#1}
+\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
+\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
+\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
+\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
+\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
+\newcommand{\ExtensionTok}[1]{#1}
+\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
+\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\ImportTok}[1]{#1}
+\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
+\newcommand{\NormalTok}[1]{#1}
+\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
+\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
+\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
+\newcommand{\RegionMarkerTok}[1]{#1}
+\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
 \usepackage{graphicx}
@@
 
-Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
-
-Enter author note here.
+Thank you to K.D. Valentine and Chelsea Parlett-Pelleriti for feedback on some ugly graphs.
 
@@
 
-Outline
-
-\begin{itemize}
-\item
-  talk about LVM
-\item
-  talk about cfa
-\item
-  talk about mgcfa
-\item
-  how are measurement and replication/crisis related
-\item
-  why it is a bad idea to say that replication/crisis are \emph{because} bad measurement
-\item
-  how can we visualize and interpret MGCFA to help us understand the impact of measurement differences
-\end{itemize}
-
-By the end of this tutorial manuscript, readers will:
+Psychological assessments play a critical role in our ability to measure and analyze constructs to support theories and experimental hypotheses.
+Defining and creating assessments to validly and reliability measure constructs is often difficult because phenomenon, such as anxiety, are often not directly observable.
+Instead, we use surveys and questionnaires to indirectly assess the underlying construct (DeVellis \& Thorpe, 2022).
+Latent variable modeling (i.e., structural equation modeling) is a popular tool for the validation of developed survey instruments to verify scale dimensionalality, structure, and model fit.
+A simple search for scale development reveals thousands of articles in psychology that examine new and previously published work, thus, illustrating the interest in both measurement and the use of validation techniques.
+Unfortunately, except in specialty journals, much of the validity evidence and/or development for measures used in empirical studies is not reported within the journal article Weidman, Steckler, \& Tracy (2017).
+Without this information, it is difficult to interpret individual study conclusions, as validity information allows for judgment of usefulness of the measured values (Flake \& Fried, 2020).
+Further, the current focus on replication Zwaan, Etz, Lucas, \& Donnellan (2018), reproducibility (Nelson et al., 2018), and the credibility of our results (Vazire, Schiavone, \& Bottesini, 2022) has demonstrated questionable measurement practices - decisions that researchers make like survey selection and scoring that impact the results of the study (Flake \& Fried, 2020).
+Transparent reporting of the use and creation of scales can improve both interpretation and reproducibility when using surveys developed to measure latent constructs (Shadish, Cook, \& Campbell, 2001).
+
+A secondary concern for developed measures is the potential for differential responding and assessment within target populations.
+For example, Trent et al.
+(2013) examined for potential variability in the Revised Child Anxiety and Depression Scale in White and Black youths (Chorpita, Yim, Moffitt, Umemoto, \& Francis, 2000).
+They found that the scale mostly functioned the same for both White and Black individuals but differences in averages on individual items could potentially affect the scoring and interpretation of the scale results.
+This comparison of sub-populations is the test of measurement invariance (Meredith, 1993).
+Invariance or equivalence implies that the scale operates in the same fashion for each sub-group, and thus, differences in the final latent variable scores can interpretated as differences in populations.
+Non-invariance suggests that individuals respond or interpret items differently, and thus, differences in scores may represent different scores on the latent variable in the population or differences in measurement.
+Non-invariant measurement may lead to misleading results when making group comparisons, and assessing invariance has become a popular technique in scale development (Van De Schoot, Schmidt, De Beuckelaer, Lek, \& Zondervan-Zwijnenburg, 2015).
+
+Measurement invariance is typically analyzed using confirmatory factor analysis, specifically, multi-group confirmatory factor analysis (MGCFA) or less often, with item response theory Tay, Meade, \& Cao (2015).
+First, the model is examined with the factor structure proposed for the latent and observed variables, and then often these models are assessed for each group separately.
+The two models are then combined together into one nested CFA in order to determine configural invariance Kline (2016).
+Configural invariance tests if the proposed factor structure is the same between groups.
+In this model, all other estimated parameters are allowed to vary between groups.
+The general approach is to use this model as a baseline for starting a sequential analysis of further restrictions between group parameters (i.e., more restrictive with each step).
+However, models without configural invariance can occur and often point to misspecification for the observed and latent variables within one group (i.e., cross loadings of items onto other latent variables or correlated error terms for one group only).
+
+Next, the estimated parameter between each observed variable and its latent variable are constrained to be equal between groups for metric invariance.
+For example, item 1's factor loading must be equal to item 1's factor loading for each group.
+This test examines if the items represent the same relationship to the latent variable, or if specific items have weaker or stronger relationships in specific groups.
+Finding non-invariance at this stage generally points to items that have different functioning or interpretation for one group.
+At the third model, the item intercepts (i.e., item averages) are restricted across groups for scalar invariance.
+Scalar non-invariance would indicate that items have the same strength of relationship with their latent variable, just one group has a higher overall average on that item.
+Last (although sometimes not used), we may consider constraining error variances for each observed variable to be equal across groups for strict invariance.
+Strict non-invariance can occur when one group has a higher range of values on the observed variable, thus showing a larger variance.
+For example, if using a Likert scale, one group may use the full 1 to 7 range (creating a flatter distribution and larger variance), while the other group shows a ceiling effect of only using 5 to 7.
+
+These concepts have been explored and implemented for the last fifty years Sörbom (1978) and implemented in the most popular structural equation modeling programs Boker et al.
+(2011).
+Byrne, Shavelson, and Muthén (1989) extended the ideas of multi-group testing by suggesting partial invariance (followed by Meredith, 1993).
+Partial invariance occurs when non-invariance is found but can be attributed to only a few parameter estimate differences between groups (i.e., items 1 and 2 have different factor loadings but all others are the same).
+This testing provided an advantage to understand where the potential non-invariance may occur for further study and interpretation guidelines.
+To determine when non-invariance and partial invariance occurred, each model is sequentially compared to the previous model using some form of a difference test.
+Traditionally, since models were nested, a chi-square difference test was used Cheung \& Rensvold (2002); however, given the known issues with chi-square (Thompson \& Daniel, 1996), people have favored empirical cutoffs for differences in fit indices.
+As the field pushes back against favoring cutoff criteria and rules of thumb Putnick \& Bornstein (2016), an effect size measure for translating ``how much'' non-invariance was developed \(d_{MACS}\) (Nye \& Drasgow, 2011).
+This effect size examines the differences in observed variables between the two groups for both the factor loading and the item intercept; thus, any differences in either or both will increase the effect size for non-invariance (Stark et al., 2006).
+
+With \(d_{MACS}\) and measurement invariance testing, researchers can begin to quantify how and where their construct measurement may vary between groups.
+However, given the large number of studies that show non-invariance, it is clear that equivalence can be hard to meet.
+It is difficult to know if non-invariance occurs because of random sampling error, true population differences, or differences in replication and reproducibility of the construct in a new sample.
+Further, it is important to remember that the parameter estimates that we are testing are just that - estimates.
+All the parameter estimates have measures of standard error to indicate that they are more than likely variable with a new sample or population.
+Given that this information is generally ignored during the examination of measurement invariance, it may be that we are claiming that many scales are non-invariant, when in reality, the differences between loadings or item intercepts are small and unimportant.
+\(d_{MACS}\) provides the opportunity to begin to think about the smallest effect size of interest or the smallest meaningful effect size Anvari \& Lakens (2021).
+As mentioned, \(d_{MACS}\) has only really been explored for a combined intercept and loadings, and while useful, does not necessarily allow a researcher to pinpoint specific issues within an observed variable.
+The purpose of this manuscript is provide readers with a framework for visualization of differences in loadings, intercepts, and variances for each item, and the impact of those differences on the distribution of the latent mean.
+No known visualization techniques have been proposed for measurement invariance.
+By creating panel visualizations, we can supplement a researchers ability to judge the strength of the non-invariance differences and effect size for each item.
+Coupled with other indicators (i.e., fit indice differences, \(d_{MACS}\)), we can move toward a better understanding of how much measurement non-invariance is meaningful.
+
+By the end of this manuscript, readers will:
 
@@
 
-The Brown (2015) steps of testing measurement invariance are demonstrated in this manuscript for illustration purposes, but in line with Stark, Chernyshenko, and Drasgow (2006) suggestions, the visualizations show the impact of loadings and intercepts together.
+The Brown (2015) steps of testing measurement invariance are demonstrated in this manuscript for illustration purposes, but in line with Stark et al.
+(2006) suggestions, the visualizations show the impact of loadings and intercepts together.
 The configural model was analyzed nesting both groups into the same CFA model requiring that both groups show the same model structure, but all other parameters are free to vary between groups.
@@
 These models are normally tested sequentially, and a convenience function \texttt{mgcfa} is provided in the supplemental documents for this manuscript.
+Fit indices for the steps for multi-group models are presented in the appendix for comparison of cutoff rules of thumb (Cheung \& Rensvold, 2002) to effect sizes and visualizations presented in this manuscript.
+Fit indices include Akaike Information Criterion (AIC, Akaike, 1998), Bayesian Information Criterion (BIC, Schwarz, 1978), Comparative Fit Index (CFI, Bentler, 1990), Tucker Lewis Index (TLI, Tucker \& Lewis, 1973), root mean squared error of approximation RMSEA (Steiger, 1990), and standardized root mean squar residual (SRMR, Bentler, 1995).
 
@@
 Only one item in each model was manipulated from the invariant model to create the non-invariant models.
+
+\hypertarget{results}{%
+\section{Results}\label{results}}
+
+\hypertarget{code-examples}{%
+\subsection{Code Examples}\label{code-examples}}
+
+The complete code for this manuscript can be found at \url{https://osf.io/wev5f/}, and the function code for the convenience function for multi-group models and plots is found in the appendix.
+First, we would create our model code in \texttt{lavaan} syntax.
+The \texttt{lv} latent variable predicts the five measured variables, which are present as columns in our \texttt{df.invariant} dataset.
+You would include the dataframe in the \texttt{data} argument of our function, the name of the grouping variable in quotes for \texttt{group}, and the \texttt{lavaan} model syntax in the \texttt{model} argument.
+The \texttt{mgcfa} function code runs an overall model with all data, regardless of group, each group separately on the model, then the steps described above: configural, metric, scalar, and strict invariance.
+
+\small
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\# create lavaan model}
+\NormalTok{model.overall }\OtherTok{\textless{}{-}} \StringTok{"lv =\textasciitilde{} q1 + q2 + q3 + q4 + q5}
+\StringTok{q1 \textasciitilde{} 0*1}
+\StringTok{lv \textasciitilde{} 1"}
+\CommentTok{\# look at the data}
+\FunctionTok{head}\NormalTok{(df.invariant)}
+\end{Highlighting}
+\end{Shaded}
+
+\normalsize
+
+\begin{verbatim}
+##           q1          q2          q3         q4         q5   group
+## 1 -0.8903542 -0.81707530  0.06137292 -1.3236407 -1.7916418 Group 1
+## 2  1.1054521 -0.03540948 -0.81299606  1.0028340 -0.1909127 Group 1
+## 3  1.4555852  1.54083484  1.59084213 -0.3345967 -0.6865496 Group 1
+## 4 -1.8745187 -1.27880245 -2.53565792 -1.0024193 -1.6253249 Group 1
+## 5 -0.4449517 -0.17782974  1.05507079 -1.2615705  1.7536428 Group 1
+## 6  0.2278813  0.71348845  1.63251893  0.6449847 -1.0055700 Group 1
+\end{verbatim}
+
+\small
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\# run our mgcfa function to run all models}
+\NormalTok{results.invariant }\OtherTok{\textless{}{-}} \FunctionTok{mgcfa}\NormalTok{(}\AttributeTok{data =}\NormalTok{ df.invariant, }\CommentTok{\#dataframe}
+                           \AttributeTok{group =} \StringTok{"group"}\NormalTok{, }
+                           \AttributeTok{model =}\NormalTok{ model.overall)}
+\CommentTok{\# what is saved for you}
+\FunctionTok{names}\NormalTok{(results.invariant)}
+\end{Highlighting}
+\end{Shaded}
+
+\normalsize
+
+\begin{verbatim}
+## [1] "model_coef"       "model_fit"        "model.overall"    "model.group1"    
+## [5] "model.group2"     "model.configural" "model.metric"     "model.scalar"    
+## [9] "model.strict"
+\end{verbatim}
+
+The results are saved as a list and include the following:
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi})}
+\tightlist
+\item
+  \texttt{model\_coef}: a tidy dataframe with \emph{all} model's coefficients saved from the \texttt{lavaan} outputs.
+\end{enumerate}
+
+\small
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{head}\NormalTok{(results.invariant}\SpecialCharTok{$}\NormalTok{model\_coef)}
+\end{Highlighting}
+\end{Shaded}
+
+\normalsize
+
+\begin{verbatim}
+## # A tibble: 6 x 13
+##   term       op    estimate std.error statistic   p.value std.lv std.all std.nox
+##   <chr>      <chr>    <dbl>     <dbl>     <dbl>     <dbl>  <dbl>   <dbl>   <dbl>
+## 1 "lv =~ q1" =~       1        0          NA    NA         0.780   0.598   0.598
+## 2 "lv =~ q2" =~       0.564    0.0864      6.52  6.99e-11  0.440   0.435   0.435
+## 3 "lv =~ q3" =~       0.748    0.105       7.12  1.09e-12  0.583   0.505   0.505
+## 4 "lv =~ q4" =~       0.338    0.0804      4.20  2.62e- 5  0.264   0.250   0.250
+## 5 "lv =~ q5" =~       0.904    0.120       7.52  5.48e-14  0.705   0.613   0.613
+## 6 "q1 ~1 "   ~1       0        0          NA    NA         0       0       0    
+## # i 4 more variables: model <chr>, block <int>, group <int>, label <chr>
+\end{verbatim}
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi})}
+\setcounter{enumi}{1}
+\tightlist
+\item
+  \texttt{model\_fit}: a tidy dataframe with \emph{all} model's fit indices saved from the \texttt{lavaan} outputs.
+\end{enumerate}
+
+\small
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{head}\NormalTok{(results.invariant}\SpecialCharTok{$}\NormalTok{model\_fit)}
+\end{Highlighting}
+\end{Shaded}
+
+\normalsize
+
+\begin{verbatim}
+## # A tibble: 6 x 18
+##    agfi   AIC   BIC   cfi chisq  npar  rmsea rmsea.conf.high   srmr   tli
+##   <dbl> <dbl> <dbl> <dbl> <dbl> <dbl>  <dbl>           <dbl>  <dbl> <dbl>
+## 1 0.979 7516. 7579. 0.994  6.37    15 0.0234          0.0697 0.0211 0.988
+## 2 0.948 3766. 3819. 0.976  7.79    15 0.0473          0.108  0.0312 0.953
+## 3 0.952 3762. 3815. 0.980  7.25    15 0.0424          0.104  0.0322 0.960
+## 4 0.950 7528. 7654. 0.978 15.0     30 0.0449          0.0886 0.0317 0.956
+## 5 0.942 7529. 7639. 0.954 24.7     26 0.0554          0.0905 0.0476 0.934
+## 6 0.952 7523. 7616. 0.964 26.2     22 0.0428          0.0760 0.0488 0.960
+## # i 8 more variables: converged <lgl>, estimator <chr>, ngroups <int>,
+## #   missing_method <chr>, nobs <int>, norig <int>, nexcluded <int>, model <chr>
+\end{verbatim}
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi})}
+\setcounter{enumi}{2}
+\tightlist
+\item
+  Saved \texttt{lavaan} fitted objects that you can use the \texttt{summary()}, \texttt{parameterEstimates()}, \texttt{fitIndices()}, etc.
+on.
+Overall model indicates the model without grouping variables testing all data on the proposed model structure.
+This model is then tested separately for each group (\texttt{model.group1}, \texttt{model.group2}).
+The final models follow the Brown (2015) naming convention for sequential steps for testing MGCFA for measurement invariance (\texttt{model.configural}, \texttt{model.metric}, \texttt{model.scalar}, \texttt{model.strict}).
+\end{enumerate}
+
+The results from the \texttt{model\_coef} table can then be used directly in the suggested plotting function. The plot outputs will be described below. First, here are the arguments for the function:
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi})}
+\item
+  \texttt{data\_coef}: A tidy dataframe of the parameter estimates from the models.
+This function assumes you have used \texttt{broom::tidy()} on the saved model from \texttt{lavaan} and added a column called ``model'' with the name of the model step.
+This function will only run for models that have used the grouping function (i.e., configural, metric, scalar, and strict or other combinations/steps you wish to examine).
+\item
+  \texttt{model\_step}: Which model do you want to plot? You should match this name to the one you want to extract from your model column in the \texttt{data\_coef}.
+\item
+  \texttt{item\_name}: Which observed variable from your model syntax do you want to plot? Please list this variable name exactly how it appears in the model.
+\item
+  \texttt{x\_limits}: What do you want the x-axits limits to be for your invariance plot?
+The default option is to assume the latent variable is standardized, and therefore, -1 to 1 is recommended.
+Use only two numbers, a lower and upper limit.
+\item
+  \texttt{y\_limits}: What do you want the y-axits limits to be for your invariance plot?
+Given that the latent variable is used to predict the observed values in the data, you could use the minimum and maximum values found in the data.
+If that range is large, consider reducing this value to be able to visualize the results (i.e., otherwise it may be too zoomed out to judge group differences).
+Use only two numbers, a lower and upper limit.
+\item
+  \texttt{ci\_level}: What confidence limit do you want to plot? Use 1 - \(\alpha\).
+\item
+  \texttt{model\_results}: In this argument, include the saved \texttt{lavaan} output for the model listed in the \texttt{model\_step} argument.
+\item
+  \texttt{lv\_name}: Include the name of the latent variable, exactly how it is listed in your \texttt{lavaan} syntax.
+You should plot the latent variable that the \texttt{item\_name} is linked to.
+If you have items that load onto multiple latent variables, you will need to make multiple plots.
+\end{enumerate}
+
+\small
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{plot\_mgcfa}\NormalTok{(}
+  \AttributeTok{data\_coef =}\NormalTok{ results.invariant}\SpecialCharTok{$}\NormalTok{model\_coef, }\CommentTok{\# output from model\_coef}
+  \AttributeTok{model\_step =} \StringTok{"configural"}\NormalTok{, }\CommentTok{\# which model do you want to plot}
+  \AttributeTok{item\_name =} \StringTok{"q4"}\NormalTok{, }\CommentTok{\# name of observed item}
+  \AttributeTok{x\_limits =} \FunctionTok{c}\NormalTok{(}\SpecialCharTok{{-}}\DecValTok{1}\NormalTok{,}\DecValTok{1}\NormalTok{), }\CommentTok{\# latent variable limits to graph}
+  \AttributeTok{y\_limits =} \FunctionTok{c}\NormalTok{(}\FunctionTok{min}\NormalTok{(df.invariant}\SpecialCharTok{$}\NormalTok{q4), }\FunctionTok{max}\NormalTok{(df.invariant}\SpecialCharTok{$}\NormalTok{q4)), }\CommentTok{\# Y min and max in data }
+  \AttributeTok{ci\_level =}\NormalTok{ .}\DecValTok{95}\NormalTok{, }\CommentTok{\# what ci do you want}
+  \AttributeTok{model\_results =}\NormalTok{ results.invariant}\SpecialCharTok{$}\NormalTok{model.configural, }\CommentTok{\# what model results do you want }
+  \AttributeTok{lv\_name =} \StringTok{"lv"} \CommentTok{\# which latent variable do you want }
+\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\normalsize
+
+\hypertarget{visualization-of-invariance}{%
+\subsection{Visualization of Invariance}\label{visualization-of-invariance}}
+
+The output from this model can be found in Figure \ref{fig:invariant-pic}.
+On the left hand side, the item invariance is plotted, and on the right hand side, the latent mean distributions for the two groups are plotted.
+In the item invariance sub-plot, the visualization includes all three components traditionally seen in MGCFA testing steps: loadings, intercepts, and residuals.
+Each visualization element was designed to match the traditional visualization for that type of output.
+All parameter estimates are plotted on the unstandardized estimates and their confidence interval based on the standard error of the estimate.
+
+\hypertarget{loadings}{%
+\subsubsection{Loadings}\label{loadings}}
+
+Factor loadings represent the slope of the regression equation for the latent variable predicting the scores on the observed variable (\(\hat{Y} \sim b_0 + b_1X + \epsilon\)).
+Therefore, the latent variable is shown on the x-axis using standardized values (i.e., \emph{z}-scores) where -1 indicates one standard deviation below the mean for the latent variable, 0 indicates the mean for the latent variable and so on.
+The y-axis indicates the observed variable scores, and here, the plot includes the entire range of the scale of the data for item four.
+The coefficient (\(b_1\)) for group 1 was 0.40, while the coefficient for group 2 was 0.34.
+The ribbon bands around the plotted slopes indicate the confidence interval for that estimate.
+In this plot, while the coefficients for each group are not literally equal, the overlapping and parallel slope bands indicate they are not different practically.
+
+\hypertarget{intercepts}{%
+\subsubsection{Intercepts}\label{intercepts}}
+
+The item intercepts (\(b_0\)) are plotted on the middle line where they would cross the y-axis at a latent variable score of zero.
+These are represented by a dot with a set of confidence error bars around the point.
+The intercept for group 1 was 0.07, while the coefficient for group 2 was 0.03.
+In this invariant depiction, the overlap in the intercepts is clear, indicating they are not different.
+You can use \texttt{y\_limits} to zoom in on the graph if these are too small to be distinguishable.
+
+\hypertarget{residuals}{%
+\subsubsection{Residuals}\label{residuals}}
+
+Residuals are trickier to plot, as they are the left over error when predicting the observed variables \(\epsilon\).
+It is tempting to plot this value as the confidence band around the slope, however, that defeats the purpose of understanding that the slopes are estimated separately from the residuals, and both have an associated variability around their parameter estimate.
+Therefore, residuals are represented in the inset picture at the bottom right of the item invariance plot.
+The black bars represent the estimated residual for each group (group 1: 0.91, group 2: 1.16).
+The distributions are plotted to represent the normal spread of values using the standard error of the residuals.
+The violin plot allows for direct comparison of those residuals and their potential distributions.
+Note that the placement has nothing to do with the x or y-axis and is designed to always show in the same location, regardless of size/value.
+
+\hypertarget{latent-means}{%
+\subsubsection{Latent Means}\label{latent-means}}
+
+The overall impact of differences on the latent means can be found in the right hand visualization.
+The latent means are calculated by using the \texttt{predict} function and then plotted as overlapping histograms.
+The vertical colored lines represent the mean for each group, and the spread of the distribution can be examined using the density coloring.
+Finally, group labels are represented in the figure caption on the bottom.
+Group 1 is usually the group that is alphabetically first in the dataset or whichever group is the first that appears when using the \texttt{levels()} command.
 
@@
 
+\hypertarget{graphing-effect-size}{%
+\subsubsection{Graphing Effect Size}\label{graphing-effect-size}}
+
+The \(d_{MACS}\) value for item 4 in the invariant model was 0.06, representing a nil or unimportant difference in this manuscript.
+It is important to note that while Nye et al.
+(2019) suggests specific sizes for small, medium, and large, each researcher should determine for themselves what effects represent.
+Figure \ref{fig:small-load-pic} displays the results from the small (\(d_{MACS}\) = 0.12) difference in loadings, while Figure \ref{fig:med-load-pic} displays the results from the medium (\(d_{MACS}\) = 0.43) difference in loadings, and Figure \ref{fig:large-load-pic} shows the large (\(d_{MACS}\) = 0.63) differences.
+When investigating the slope values, we can clearly see the change in the loading for the second group (the only manipulated variable, although random dataset generation may also change intercepts and residuals slightly).
+At the medium effect size, we see that the confidence bands do not overlap (at the edges), and at the large effect size, we can see a clear separation of two lines.
+Note that the intercepts are still fixed so the loading representation will not literally separate, but the steepness of the lines is the indicator of the difference between the slopes.
+You can imagine these lines are interpreted like a simple slopes analysis for interactions in regression (Cohen, Cohen, West, \& Aiken, 2003).
+When simple slopes for interactions are plotted, if they are parallel, there is no interaction, and if they cross, then there is an interaction.
+Here, we can use this same logic.
+If they are parallel, there is likely invariance (they are the same), and the further from parallel they become, the larger the effect size for the differences between group loadings.
+
 \begin{figure}
@@
 
+For intercepts, the small (Figure \ref{fig:small-int-pic}), medium (Figure \ref{fig:med-int-pic}), and large (Figure \ref{fig:large-int-pic}) depictions represent \(d_{MACS}\) values of 0.29, 0.52, and 0.76, respectively.
+Intercept differences can be clearly seen represented by the spacing out of the intercept locations (and thus, the overall line as well).
+Note how little the intercept differences appear to influence the latent variable means and distributions.
+
 \begin{figure}
@@
 
+Last, the effect of the residuals is plotted in small (Figure \ref{fig:small-res-pic}), medium (Figure \ref{fig:med-res-pic}), and large (Figure \ref{fig:large-res-pic}) formats.
+While \(d_{MACS}\) values are not technically avaliable for the residuals, our models showed 0.20, 0.14, and 0.11, respectively.
+These differences in values are variable due to the random generation of datasets for each measurement invariance manipulation.
+At first glance, the differences in the small chart may seem large, because the black lines are not touching, but notice that the distributions overlap, indicating a likely small difference.
+The medium and large differences better illustrate differences in residuals across groups.
+Further, the impact of the residuals on the shape of the latent mean distribution can also been seen (and unintentionally, in the first figures as well due to random variation).
+The impact is due to the standard error of the residuals, as smaller standard errors represent lepokurtic distributions (taller), and larger standard errors represent platykurtic distributions (flatter).
+The effect size difference of the residuals does not appear to change the effects in the latent means.
+
 \begin{figure}
@@
 
-\hypertarget{results}{%
-\section{Results}\label{results}}
-
 \hypertarget{discussion}{%
@@
 \begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-akaike1998}{}}%
+Akaike, H.
+(1998).
+\emph{Information theory and an extension of the maximum likelihood principle} (E.
+Parzen, K.
+Tanabe, \& G.
+Kitagawa, Eds.).
+New York, NY: Springer New York.
+Retrieved from \url{http://link.springer.com/10.1007/978-1-4612-1694-0_15}
+
+\leavevmode\vadjust pre{\hypertarget{ref-anvari2021}{}}%
+Anvari, F., \& Lakens, D.
+(2021).
+Using anchor-based methods to determine the smallest effect size of interest.
+\emph{Journal of Experimental Social Psychology}, \emph{96}, 104159.
+\url{https://doi.org/10.1016/j.jesp.2021.104159}
+
+\leavevmode\vadjust pre{\hypertarget{ref-barry2014}{}}%
+Barry, A.
+E., Chaney, B., Piazza-Gardner, A.
+K., \& Chavarria, E.
+A.
+(2014).
+Validity and Reliability Reporting Practices in the Field of Health Education and Behavior: A Review of Seven Journals.
+\emph{Health Education \& Behavior}, \emph{41}(1), 12--18.
+\url{https://doi.org/10.1177/1090198113483139}
+
 \leavevmode\vadjust pre{\hypertarget{ref-beaujean2014}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-bentler1990}{}}%
+Bentler, P. M. (1990). Comparative fit indexes in structural models. \emph{Psychological Bulletin}, \emph{107}(2), 238--246. \url{https://doi.org/10.1037/0033-2909.107.2.238}
+
+\leavevmode\vadjust pre{\hypertarget{ref-bentler1995}{}}%
+Bentler, P. M. (1995). \emph{EQS structural equations program manual}. Encino, CA.
+
+\leavevmode\vadjust pre{\hypertarget{ref-boker2011}{}}%
+Boker, S., Neale, M., Maes, H., Wilde, M., Spiegel, M., Brick, T., \ldots{} Fox, J.
+(2011).
+OpenMx: An Open Source Extended Structural Equation Modeling Framework.
+\emph{Psychometrika}, \emph{76}(2), 306--317.
+\url{https://doi.org/10.1007/s11336-010-9200-6}
+
 \leavevmode\vadjust pre{\hypertarget{ref-brown2015}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-byrne2001}{}}%
+Byrne, B.
+M.
+(2001).
+Structural Equation Modeling With AMOS, EQS, and LISREL: Comparative Approaches to Testing for the Factorial Validity of a Measuring Instrument.
+\emph{International Journal of Testing}, \emph{1}(1), 55--86.
+\url{https://doi.org/10.1207/S15327574IJT0101_4}
+
+\leavevmode\vadjust pre{\hypertarget{ref-byrne1989}{}}%
+Byrne, B.
+M., Shavelson, R.
+J., \& Muthén, B.
+(1989).
+Testing for the equivalence of factor covariance and mean structures: The issue of partial measurement invariance.
+\emph{Psychological Bulletin}, \emph{105}(3), 456--466.
+\url{https://doi.org/10.1037/0033-2909.105.3.456}
+
+\leavevmode\vadjust pre{\hypertarget{ref-cheung2002}{}}%
+Cheung, G.
+W., \& Rensvold, R.
+B.
+(2002).
+Evaluating Goodness-of-Fit Indexes for Testing Measurement Invariance.
+\emph{Structural Equation Modeling: A Multidisciplinary Journal}, \emph{9}(2), 233--255.
+\url{https://doi.org/10.1207/s15328007sem0902_5}
+
+\leavevmode\vadjust pre{\hypertarget{ref-chorpita2000}{}}%
+Chorpita, B.
+F., Yim, L., Moffitt, C., Umemoto, L.
+A., \& Francis, S.
+E.
+(2000).
+Assessment of symptoms of DSM-IV anxiety and depression in children: a revised child anxiety and depression scale.
+\emph{Behaviour Research and Therapy}, \emph{38}(8), 835--855.
+\url{https://doi.org/10.1016/S0005-7967(99)00130-8}
+
+\leavevmode\vadjust pre{\hypertarget{ref-cohen2003}{}}%
+Cohen, J., Cohen, P., West, S. G., \& Aiken, L. (2003). \emph{Applied multiple regression / correlation analysis for the behavioral sciences} (3rd ed.). Lawrence Erlbaum Associates.
+
+\leavevmode\vadjust pre{\hypertarget{ref-devellis2022}{}}%
+DeVellis, R. F., \& Thorpe, C. T. (2022). \emph{Scale development: Theory and applications} (Fifth edition). Thousand Oaks, California: SAGE Publications, Inc.
+
 \leavevmode\vadjust pre{\hypertarget{ref-dueber2023}{}}%
 Dueber, D. (2023). \emph{Dmacs}. Retrieved from \url{https://github.com/ddueber/dmacs}
+
+\leavevmode\vadjust pre{\hypertarget{ref-flake2020}{}}%
+Flake, J.
+K., \& Fried, E.
+I.
+(2020).
+Measurement Schmeasurement: Questionable Measurement Practices and How to Avoid Them.
+\emph{Advances in Methods and Practices in Psychological Science}, \emph{3}(4), 456--465.
+\url{https://doi.org/10.1177/2515245920952393}
+
+\leavevmode\vadjust pre{\hypertarget{ref-juxf6reskog1971}{}}%
+Jöreskog, K. G. (1971). Simultaneous factor analysis in several populations. \emph{Psychometrika}, \emph{36}(4), 409--426. \url{https://doi.org/10.1007/BF02291366}
+
+\leavevmode\vadjust pre{\hypertarget{ref-juxf6reskog2001}{}}%
+Jöreskog, Karl G., \& Sörbom, D. (2001). \emph{LISREL 8: user's reference guide} (2. ed., updated to LISREL 8). Lincolnwood, Ill: SSI Scientific Software Internat.
+
+\leavevmode\vadjust pre{\hypertarget{ref-kline2016}{}}%
+Kline, R. B. (2016). \emph{Principles and practice of structural equation modeling} (Fourth edition). New York: The Guilford Press.
+
+\leavevmode\vadjust pre{\hypertarget{ref-lakens2017}{}}%
+Lakens, D. (2017). Equivalence Tests. \emph{Social Psychological and Personality Science}, \emph{8}(4), 355--362. \url{https://doi.org/10.1177/1948550617697177}
+
+\leavevmode\vadjust pre{\hypertarget{ref-makel2014}{}}%
+Makel, M.
+C., \& Plucker, J.
+A.
+(2014).
+Facts Are More Important Than Novelty: Replication in the Education Sciences.
+\emph{Educational Researcher}, \emph{43}(6), 304--316.
+\url{https://doi.org/10.3102/0013189X14545513}
+
+\leavevmode\vadjust pre{\hypertarget{ref-makel2012}{}}%
+Makel, M.
+C., Plucker, J.
+A., \& Hegarty, B.
+(2012).
+Replications in Psychology Research: How Often Do They Really Occur?
+\emph{Perspectives on Psychological Science}, \emph{7}(6), 537--542.
+\url{https://doi.org/10.1177/1745691612460688}
+
+\leavevmode\vadjust pre{\hypertarget{ref-marsh2004}{}}%
+Marsh, H.
+W., Hau, K.-T., \& Wen, Z.
+(2004).
+In search of golden rules: Comment on hypothesis-testing approaches to setting cutoff values for fit indexes and dangers in overgeneralizing hu and bentler's (1999) findings.
+\emph{Structural Equation Modeling: A Multidisciplinary Journal}, \emph{11}(3), 320--341.
+\url{https://doi.org/10.1207/s15328007sem1103_2}
+
+\leavevmode\vadjust pre{\hypertarget{ref-meade2008}{}}%
+Meade, A.
+W., Johnson, E.
+C., \& Braddy, P.
+W.
+(2008).
+Power and sensitivity of alternative fit indices in tests of measurement invariance.
+\emph{Journal of Applied Psychology}, \emph{93}(3), 568--592.
+\url{https://doi.org/10.1037/0021-9010.93.3.568}
+
+\leavevmode\vadjust pre{\hypertarget{ref-meredith1993}{}}%
+Meredith, W. (1993). Measurement invariance, factor analysis and factorial invariance. \emph{Psychometrika}, \emph{58}(4), 525--543. \url{https://doi.org/10.1007/BF02294825}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-putnick2016}{}}%
+Putnick, D.
+L., \& Bornstein, M.
+H.
+(2016).
+Measurement invariance conventions and reporting: The state of the art and future directions for psychological research.
+\emph{Developmental Review}, \emph{41}, 71--90.
+\url{https://doi.org/10.1016/j.dr.2016.06.004}
+
 \leavevmode\vadjust pre{\hypertarget{ref-rosseel2012}{}}%
 Rosseel, Y. (2012). Lavaan: An r package for structural equation modeling. \emph{Journal of Statistical Software}, \emph{48}(1), 1--36. \url{https://doi.org/10.18637/jss.v048.i02}
+
+\leavevmode\vadjust pre{\hypertarget{ref-schwarz1978}{}}%
+Schwarz, G. (1978). Estimating the dimension of a model. \emph{The Annals of Statistics}, \emph{6}(2), 461--464. Retrieved from \url{https://www.jstor.org/stable/2958889}
+
+\leavevmode\vadjust pre{\hypertarget{ref-shadish2001}{}}%
+Shadish, W. R., Cook, T. D., \& Campbell, D. T. (2001). \emph{Experimental and quasi-experimental designs for generalized causal inference}. Boston: Houghton Mifflin.
+
+\leavevmode\vadjust pre{\hypertarget{ref-suxf6rbom1978}{}}%
+Sörbom, D. (1978). An alternative to the methodology for analysis of covariance. \emph{Psychometrika}, \emph{43}(3), 381--396. \url{https://doi.org/10.1007/BF02293647}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-steiger1990}{}}%
+Steiger, J.
+H.
+(1990).
+Structural model evaluation and modification: An interval estimation approach.
+\emph{Multivariate Behavioral Research}, \emph{25}(2), 173--180.
+\url{https://doi.org/10.1207/s15327906mbr2502_4}
+
+\leavevmode\vadjust pre{\hypertarget{ref-tay2015}{}}%
+Tay, L., Meade, A.
+W., \& Cao, M.
+(2015).
+An Overview and Practical Guide to IRT Measurement Equivalence Analysis.
+\emph{Organizational Research Methods}, \emph{18}(1), 3--46.
+\url{https://doi.org/10.1177/1094428114553062}
+
+\leavevmode\vadjust pre{\hypertarget{ref-thompson1996}{}}%
+Thompson, B., \& Daniel, L.
+G.
+(1996).
+Factor Analytic Evidence for the Construct Validity of Scores: A Historical Overview and Some Guidelines.
+\emph{Educational and Psychological Measurement}, \emph{56}(2), 197--208.
+\url{https://doi.org/10.1177/0013164496056002001}
+
+\leavevmode\vadjust pre{\hypertarget{ref-trent2013}{}}%
+Trent, L.
+R., Buchanan, E., Ebesutani, C., Ale, C.
+M., Heiden, L., Hight, T.
+L., \ldots{} Young, J.
+(2013).
+A measurement invariance examination of the revised child anxiety and depression scale in a southern sample: Differential item functioning between african american and caucasian youth.
+\emph{Assessment}, \emph{20}(2), 175--187.
+\url{https://doi.org/10.1177/1073191112450907}
+
+\leavevmode\vadjust pre{\hypertarget{ref-tucker1973}{}}%
+Tucker, L. R., \& Lewis, C. (1973). A reliability coefficient for maximum likelihood factor analysis. \emph{Psychometrika}, \emph{38}(1), 1--10. \url{https://doi.org/10.1007/BF02291170}
+
+\leavevmode\vadjust pre{\hypertarget{ref-vandeschoot2015}{}}%
+Van De Schoot, R., Schmidt, P., De Beuckelaer, A., Lek, K., \& Zondervan-Zwijnenburg, M.
+(2015).
+Editorial: Measurement invariance.
+\emph{Frontiers in Psychology}, \emph{6}.
+Retrieved from \url{https://www.frontiersin.org/articles/10.3389/fpsyg.2015.01064}
+
+\leavevmode\vadjust pre{\hypertarget{ref-vazire2022}{}}%
+Vazire, S., Schiavone, S.
+R., \& Bottesini, J.
+G.
+(2022).
+Credibility Beyond Replicability: Improving the Four Validities in Psychological Science.
+\emph{Current Directions in Psychological Science}, \emph{31}(2), 162--168.
+\url{https://doi.org/10.1177/09637214211067779}
+
+\leavevmode\vadjust pre{\hypertarget{ref-weidman2017}{}}%
+Weidman, A.
+C., Steckler, C.
+M., \& Tracy, J.
+L.
+(2017).
+The jingle and jangle of emotion assessment: Imprecise measurement, casual scale usage, and conceptual fuzziness in emotion research.
+\emph{Emotion}, \emph{17}(2), 267--295.
+\url{https://doi.org/10.1037/emo0000226}
+
+\leavevmode\vadjust pre{\hypertarget{ref-zwaan2018}{}}%
+Zwaan, R. A., Etz, A., Lucas, R. E., \& Donnellan, M. B. (2018). Making replication mainstream. \emph{Behavioral and Brain Sciences}, \emph{41}, e120. \url{https://doi.org/10.1017/S0140525X17001972}
+
 \end{CSLReferences}
@@
 
+\hypertarget{model-fit-statistics}{%
+\subsection{Model Fit Statistics}\label{model-fit-statistics}}
+
+Model fit statistics are provided for each of the ten model combinations (invariant, three sizes for each ladings, intercepts, and residuals).
+These tables could be used to examine the traditional change in fit statistics cutoff rules of thumb (Cheung \& Rensvold, 2002), such as \(\Delta\) CFI or \(\Delta\) RMSEA, to the visualizations presented in the manuscript.
+
 \begin{table}[tbp]
@@
 
-\caption{\label{tab:unnamed-chunk-1}Model Fit for Invariant Model}
+\caption{\label{tab:tab1}Model Fit for Invariant Model}
 
@@
 \midrule
-overall & 7,505.72 & 7,547.87 & 0.99 & 0.99 & 0.02 & 0.02\\
-group1 & 3,755.75 & 3,790.96 & 0.98 & 0.95 & 0.05 & 0.04\\
-group2 & 3,751.95 & 3,787.17 & 0.98 & 0.96 & 0.04 & 0.04\\
+overall & 7,515.72 & 7,578.94 & 0.99 & 0.99 & 0.02 & 0.02\\
+group1 & 3,765.75 & 3,818.57 & 0.98 & 0.95 & 0.05 & 0.03\\
+group2 & 3,761.95 & 3,814.77 & 0.98 & 0.96 & 0.04 & 0.03\\
 configural & 7,527.70 & 7,654.14 & 0.98 & 0.96 & 0.04 & 0.03\\
@@
 
-\caption{\label{tab:unnamed-chunk-2}Model Fit for Small Differences in Loadings}
+\caption{\label{tab:tab2}Model Fit for Small Differences in Loadings}
 
@@
 \midrule
-overall & 7,527.67 & 7,569.81 & 0.98 & 0.96 & 0.04 & 0.03\\
-group1 & 3,755.75 & 3,790.96 & 0.98 & 0.95 & 0.05 & 0.04\\
-group2 & 3,767.83 & 3,803.05 & 0.98 & 0.96 & 0.05 & 0.04\\
+overall & 7,537.67 & 7,600.89 & 0.98 & 0.96 & 0.04 & 0.02\\
+group1 & 3,765.75 & 3,818.57 & 0.98 & 0.95 & 0.05 & 0.03\\
+group2 & 3,777.83 & 3,830.66 & 0.98 & 0.96 & 0.05 & 0.03\\
 configural & 7,543.58 & 7,670.02 & 0.98 & 0.95 & 0.05 & 0.03\\
@@
 
-\caption{\label{tab:unnamed-chunk-3}Model Fit for Medium Differences in Loadings}
+\caption{\label{tab:tab3}Model Fit for Medium Differences in Loadings}
 
@@
 \midrule
-overall & 7,544.55 & 7,586.70 & 0.97 & 0.94 & 0.05 & 0.03\\
-group1 & 3,755.75 & 3,790.96 & 0.98 & 0.95 & 0.05 & 0.04\\
-group2 & 3,774.92 & 3,810.14 & 1.00 & 1.00 & 0.02 & 0.03\\
+overall & 7,554.55 & 7,617.77 & 0.97 & 0.94 & 0.05 & 0.03\\
+group1 & 3,765.75 & 3,818.57 & 0.98 & 0.95 & 0.05 & 0.03\\
+group2 & 3,784.92 & 3,837.74 & 1.00 & 1.00 & 0.02 & 0.02\\
 configural & 7,550.67 & 7,677.11 & 0.99 & 0.98 & 0.04 & 0.03\\
@@
 
-\caption{\label{tab:unnamed-chunk-4}Model Fit for Large Differences in Loadings}
+\caption{\label{tab:tab4}Model Fit for Large Differences in Loadings}
 
@@
 \midrule
-overall & 7,652.99 & 7,695.14 & 0.98 & 0.97 & 0.04 & 0.03\\
-group1 & 3,755.75 & 3,790.96 & 0.98 & 0.95 & 0.05 & 0.04\\
-group2 & 3,847.21 & 3,882.42 & 0.97 & 0.94 & 0.08 & 0.04\\
+overall & 7,662.99 & 7,726.21 & 0.98 & 0.97 & 0.04 & 0.02\\
+group1 & 3,765.75 & 3,818.57 & 0.98 & 0.95 & 0.05 & 0.03\\
+group2 & 3,857.21 & 3,910.03 & 0.97 & 0.94 & 0.08 & 0.03\\
 configural & 7,622.96 & 7,749.40 & 0.97 & 0.94 & 0.06 & 0.03\\
@@
 
-\caption{\label{tab:unnamed-chunk-5}Model Fit for Small Differences in Intercepts}
+\caption{\label{tab:tab5}Model Fit for Small Differences in Intercepts}
 
@@
 \midrule
-overall & 7,509.69 & 7,551.83 & 1.00 & 0.99 & 0.02 & 0.02\\
-group1 & 3,755.75 & 3,790.96 & 0.98 & 0.95 & 0.05 & 0.04\\
-group2 & 3,760.41 & 3,795.63 & 0.93 & 0.86 & 0.08 & 0.05\\
+overall & 7,519.69 & 7,582.91 & 1.00 & 0.99 & 0.02 & 0.02\\
+group1 & 3,765.75 & 3,818.57 & 0.98 & 0.95 & 0.05 & 0.03\\
+group2 & 3,770.41 & 3,823.23 & 0.93 & 0.86 & 0.08 & 0.04\\
 configural & 7,536.16 & 7,662.60 & 0.95 & 0.91 & 0.07 & 0.04\\
@@
 
-\caption{\label{tab:unnamed-chunk-6}Model Fit for Medium Differences in Intercepts}
+\caption{\label{tab:tab6}Model Fit for Medium Differences in Intercepts}
 
@@
 \midrule
-overall & 7,532.77 & 7,574.92 & 1.00 & 1.00 & 0.01 & 0.02\\
-group1 & 3,755.75 & 3,790.96 & 0.98 & 0.95 & 0.05 & 0.04\\
-group2 & 3,760.41 & 3,795.63 & 0.93 & 0.86 & 0.08 & 0.05\\
+overall & 7,542.77 & 7,605.99 & 1.00 & 1.00 & 0.01 & 0.02\\
+group1 & 3,765.75 & 3,818.57 & 0.98 & 0.95 & 0.05 & 0.03\\
+group2 & 3,770.41 & 3,823.23 & 0.93 & 0.86 & 0.08 & 0.04\\
 configural & 7,536.16 & 7,662.60 & 0.95 & 0.91 & 0.07 & 0.04\\
@@
 
-\caption{\label{tab:unnamed-chunk-7}Model Fit for Large Differences in Intercepts}
+\caption{\label{tab:tab7}Model Fit for Large Differences in Intercepts}
 
@@
 \midrule
-overall & 7,569.17 & 7,611.31 & 1.00 & 1.00 & 0.00 & 0.02\\
-group1 & 3,755.75 & 3,790.96 & 0.98 & 0.95 & 0.05 & 0.04\\
-group2 & 3,760.41 & 3,795.63 & 0.93 & 0.86 & 0.08 & 0.05\\
+overall & 7,579.17 & 7,642.39 & 1.00 & 1.00 & 0.00 & 0.02\\
+group1 & 3,765.75 & 3,818.57 & 0.98 & 0.95 & 0.05 & 0.03\\
+group2 & 3,770.41 & 3,823.23 & 0.93 & 0.86 & 0.08 & 0.04\\
 configural & 7,536.16 & 7,662.60 & 0.95 & 0.91 & 0.07 & 0.04\\
@@
 
-\caption{\label{tab:unnamed-chunk-8}Model Fit for Small Differences in Residuals}
+\caption{\label{tab:tab8}Model Fit for Small Differences in Residuals}
 
@@
 \midrule
-overall & 7,439.49 & 7,481.64 & 1.00 & 1.01 & 0.00 & 0.02\\
-group1 & 3,755.75 & 3,790.96 & 0.98 & 0.95 & 0.05 & 0.04\\
-group2 & 3,683.32 & 3,718.53 & 1.00 & 1.01 & 0.00 & 0.02\\
+overall & 7,449.49 & 7,512.71 & 1.00 & 1.01 & 0.00 & 0.01\\
+group1 & 3,765.75 & 3,818.57 & 0.98 & 0.95 & 0.05 & 0.03\\
+group2 & 3,693.32 & 3,746.14 & 1.00 & 1.01 & 0.00 & 0.02\\
 configural & 7,459.07 & 7,585.51 & 0.99 & 0.98 & 0.03 & 0.03\\
@@
 
-\caption{\label{tab:unnamed-chunk-9}Model Fit for Medium Differences in Residuals}
+\caption{\label{tab:tab9}Model Fit for Medium Differences in Residuals}
 
@@
 \midrule
-overall & 7,368.57 & 7,410.71 & 1.00 & 1.00 & 0.00 & 0.02\\
-group1 & 3,755.75 & 3,790.96 & 0.98 & 0.95 & 0.05 & 0.04\\
-group2 & 3,587.77 & 3,622.99 & 1.00 & 1.03 & 0.00 & 0.02\\
+overall & 7,378.57 & 7,441.79 & 1.00 & 1.00 & 0.00 & 0.02\\
+group1 & 3,765.75 & 3,818.57 & 0.98 & 0.95 & 0.05 & 0.03\\
+group2 & 3,597.77 & 3,650.60 & 1.00 & 1.03 & 0.00 & 0.02\\
 configural & 7,363.52 & 7,489.96 & 1.00 & 0.99 & 0.02 & 0.02\\
@@
 
-\caption{\label{tab:unnamed-chunk-10}Model Fit for Large Differences in Residuals}
+\caption{\label{tab:tab10}Model Fit for Large Differences in Residuals}
 
@@
 \midrule
-overall & 7,284.21 & 7,326.36 & 1.00 & 1.01 & 0.00 & 0.02\\
-group1 & 3,755.75 & 3,790.96 & 0.98 & 0.95 & 0.05 & 0.04\\
-group2 & 3,443.47 & 3,478.69 & 0.95 & 0.90 & 0.07 & 0.04\\
+overall & 7,294.21 & 7,357.43 & 1.00 & 1.01 & 0.00 & 0.01\\
+group1 & 3,765.75 & 3,818.57 & 0.98 & 0.95 & 0.05 & 0.03\\
+group2 & 3,453.47 & 3,506.29 & 0.95 & 0.90 & 0.07 & 0.03\\
 configural & 7,219.22 & 7,345.66 & 0.96 & 0.92 & 0.06 & 0.03\\
@@
 
+\hypertarget{mgcfa-convenience-function}{%
+\subsection{MGCFA Convenience Function}\label{mgcfa-convenience-function}}
+
+Please note that any partial invariance is not automatically included in this function.
+This function returns a list with all model summaries, the model coefficients in a tidy dataframe, and the model fit statistics in a tidy dataframe.
+You will need the libraries listed below for this function to work properly.
+
+\small
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{library}\NormalTok{(lavaan)}
+\FunctionTok{library}\NormalTok{(dplyr)}
+\FunctionTok{library}\NormalTok{(broom)}
+\CommentTok{\# CFA function}
+\NormalTok{mgcfa }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(data, group, model)\{}
+
+\NormalTok{  group\_names }\OtherTok{\textless{}{-}} \FunctionTok{unique}\NormalTok{(data[ , group])}
+
+\NormalTok{  model.overall }\OtherTok{\textless{}{-}} \FunctionTok{cfa}\NormalTok{(}\AttributeTok{model =}\NormalTok{ model, }\AttributeTok{data =}\NormalTok{ data)}
+\NormalTok{  model.group1 }\OtherTok{\textless{}{-}} \FunctionTok{cfa}\NormalTok{(}\AttributeTok{model =}\NormalTok{ model, }
+                      \AttributeTok{data =} \FunctionTok{subset}\NormalTok{(data, group }\SpecialCharTok{==}\NormalTok{ group\_names[}\DecValTok{1}\NormalTok{]))}
+\NormalTok{  model.group2 }\OtherTok{\textless{}{-}} \FunctionTok{cfa}\NormalTok{(}\AttributeTok{model =}\NormalTok{ model, }
+                      \AttributeTok{data =} \FunctionTok{subset}\NormalTok{(data, group }\SpecialCharTok{==}\NormalTok{ group\_names[}\DecValTok{2}\NormalTok{]))}
+\NormalTok{  model.configural }\OtherTok{\textless{}{-}} \FunctionTok{cfa}\NormalTok{(}\AttributeTok{model =}\NormalTok{ model, }\AttributeTok{data =}\NormalTok{ data, }
+                          \AttributeTok{group =}\NormalTok{ group, }\AttributeTok{meanstructure =}\NormalTok{ T)}
+\NormalTok{  model.metric }\OtherTok{\textless{}{-}} \FunctionTok{cfa}\NormalTok{(}\AttributeTok{model =}\NormalTok{ model, }\AttributeTok{data =}\NormalTok{ data, }
+                      \AttributeTok{group =}\NormalTok{ group, }\AttributeTok{meanstructure =}\NormalTok{ T,}
+                      \AttributeTok{group.equal =} \StringTok{"loadings"}\NormalTok{)}
+\NormalTok{  model.scalar }\OtherTok{\textless{}{-}} \FunctionTok{cfa}\NormalTok{(}\AttributeTok{model =}\NormalTok{ model, }\AttributeTok{data =}\NormalTok{ data, }
+                      \AttributeTok{group =}\NormalTok{ group, }\AttributeTok{meanstructure =}\NormalTok{ T, }
+                      \AttributeTok{group.equal =} \FunctionTok{c}\NormalTok{(}\StringTok{"loadings"}\NormalTok{, }\StringTok{"intercepts"}\NormalTok{))}
+\NormalTok{  model.strict }\OtherTok{\textless{}{-}} \FunctionTok{cfa}\NormalTok{(}\AttributeTok{model =}\NormalTok{ model, }\AttributeTok{data =}\NormalTok{ data, }
+                      \AttributeTok{group =}\NormalTok{ group, }\AttributeTok{meanstructure =}\NormalTok{ T, }
+                      \AttributeTok{group.equal =}  \FunctionTok{c}\NormalTok{(}\StringTok{"loadings"}\NormalTok{, }\StringTok{"intercepts"}\NormalTok{, }\StringTok{"residuals"}\NormalTok{))}
+
+\NormalTok{  model\_coef }\OtherTok{\textless{}{-}} \FunctionTok{bind\_rows}\NormalTok{(}
+    \FunctionTok{tidy}\NormalTok{(model.overall, }\AttributeTok{conf.level =}\NormalTok{ .}\DecValTok{95}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
+      \FunctionTok{mutate}\NormalTok{(}\AttributeTok{model =} \StringTok{"overall"}\NormalTok{), }
+    \FunctionTok{tidy}\NormalTok{(model.group1, }\AttributeTok{conf.level =}\NormalTok{ .}\DecValTok{95}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
+      \FunctionTok{mutate}\NormalTok{(}\AttributeTok{model =} \StringTok{"group1"}\NormalTok{), }
+    \FunctionTok{tidy}\NormalTok{(model.group2, }\AttributeTok{conf.level =}\NormalTok{ .}\DecValTok{95}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
+      \FunctionTok{mutate}\NormalTok{(}\AttributeTok{model =} \StringTok{"group2"}\NormalTok{), }
+    \FunctionTok{tidy}\NormalTok{(model.configural, }\AttributeTok{conf.level =}\NormalTok{ .}\DecValTok{95}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
+      \FunctionTok{mutate}\NormalTok{(}\AttributeTok{model =} \StringTok{"configural"}\NormalTok{), }
+    \FunctionTok{tidy}\NormalTok{(model.metric, }\AttributeTok{conf.level =}\NormalTok{ .}\DecValTok{95}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
+      \FunctionTok{mutate}\NormalTok{(}\AttributeTok{model =} \StringTok{"metric"}\NormalTok{), }
+    \FunctionTok{tidy}\NormalTok{(model.scalar, }\AttributeTok{conf.level =}\NormalTok{ .}\DecValTok{95}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
+      \FunctionTok{mutate}\NormalTok{(}\AttributeTok{model =} \StringTok{"scalar"}\NormalTok{), }
+    \FunctionTok{tidy}\NormalTok{(model.strict, }\AttributeTok{conf.level =}\NormalTok{ .}\DecValTok{95}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
+      \FunctionTok{mutate}\NormalTok{(}\AttributeTok{model =} \StringTok{"strict"}\NormalTok{)}
+\NormalTok{  )}
+
+\NormalTok{  model\_fit }\OtherTok{\textless{}{-}} \FunctionTok{bind\_rows}\NormalTok{(}
+    \FunctionTok{glance}\NormalTok{(model.overall) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{mutate}\NormalTok{(}\AttributeTok{model =} \StringTok{"overall"}\NormalTok{), }
+    \FunctionTok{glance}\NormalTok{(model.group1) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{mutate}\NormalTok{(}\AttributeTok{model =} \StringTok{"group1"}\NormalTok{), }
+    \FunctionTok{glance}\NormalTok{(model.group2) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{mutate}\NormalTok{(}\AttributeTok{model =} \StringTok{"group2"}\NormalTok{), }
+    \FunctionTok{glance}\NormalTok{(model.configural) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{mutate}\NormalTok{(}\AttributeTok{model =} \StringTok{"configural"}\NormalTok{), }
+    \FunctionTok{glance}\NormalTok{(model.metric) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{mutate}\NormalTok{(}\AttributeTok{model =} \StringTok{"metric"}\NormalTok{), }
+    \FunctionTok{glance}\NormalTok{(model.scalar) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{mutate}\NormalTok{(}\AttributeTok{model =} \StringTok{"scalar"}\NormalTok{), }
+    \FunctionTok{glance}\NormalTok{(model.strict) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{mutate}\NormalTok{(}\AttributeTok{model =} \StringTok{"strict"}\NormalTok{)}
+\NormalTok{    )}
+
+  \FunctionTok{return}\NormalTok{(}\FunctionTok{list}\NormalTok{(}
+    \StringTok{"model\_coef"} \OtherTok{=}\NormalTok{ model\_coef,}
+    \StringTok{"model\_fit"} \OtherTok{=}\NormalTok{ model\_fit,}
+    \StringTok{"model.overall"} \OtherTok{=}\NormalTok{ model.overall,}
+    \StringTok{"model.group1"} \OtherTok{=}\NormalTok{ model.group1,}
+    \StringTok{"model.group2"} \OtherTok{=}\NormalTok{ model.group2,}
+    \StringTok{"model.configural"} \OtherTok{=}\NormalTok{ model.configural,}
+    \StringTok{"model.metric"} \OtherTok{=}\NormalTok{ model.metric,}
+    \StringTok{"model.scalar"} \OtherTok{=}\NormalTok{ model.scalar,}
+    \StringTok{"model.strict"} \OtherTok{=}\NormalTok{ model.strict}
+\NormalTok{  ))}
+
+\NormalTok{\}}
+\end{Highlighting}
+\end{Shaded}
+
+\normalsize
+
+\hypertarget{measurement-invariance-plot-function}{%
+\subsection{Measurement Invariance Plot Function}\label{measurement-invariance-plot-function}}
+
+This function creates the plots shown in the manuscript.
+You will need the libraries listed for this function to work.
+Plots may be modified to rearrange for those who are familiar with \texttt{ggplot2}.
+Please note that the function assumes you will use the outputs from the previous \texttt{mgcfa} function or a tidy dataframe that includes the coefficients from the model with a column \texttt{model} that indicates which step of the MGCFA you are wanting to plot.
+If you have more than two groups, you should first filter the dataframe model coefficient outputs to only include to the two groups you want to compare.
+This code does not plot more than two groups (although, it could be modified for this, but the assumption here is that you only have two, as this is how you would normally proceed in a MGCFA using pairwise comparisons to find where the invariance occurs).
+
+\small
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{library}\NormalTok{(dplyr)}
+\FunctionTok{library}\NormalTok{(ggplot2)}
+\FunctionTok{library}\NormalTok{(cowplot)}
+\FunctionTok{library}\NormalTok{(lavaan)}
+\CommentTok{\# devtools::install\_github("psyteachr/introdataviz")}
+\FunctionTok{library}\NormalTok{(introdataviz)}
+\CommentTok{\# Plot MI MGCFA}
+\NormalTok{plot\_mgcfa }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(data\_coef, }\CommentTok{\# output from model\_coef}
+\NormalTok{                       model\_step, }\CommentTok{\# which model}
+\NormalTok{                       item\_name, }\CommentTok{\# name of observed item}
+                       \AttributeTok{x\_limits =} \FunctionTok{c}\NormalTok{(}\SpecialCharTok{{-}}\DecValTok{1}\NormalTok{,}\DecValTok{1}\NormalTok{), }\CommentTok{\# LV limits to graph}
+\NormalTok{                       y\_limits, }\CommentTok{\# Y min and max in data }
+\NormalTok{                       ci\_level, }\CommentTok{\# what ci do you want}
+\NormalTok{                       model\_results, }\CommentTok{\# what model results do you want }
+\NormalTok{                       lv\_name }\CommentTok{\# which latent is the observed variable on}
+\NormalTok{                       )\{}
+
+  \CommentTok{\# calculate cutoff}
+\NormalTok{  cutoff }\OtherTok{\textless{}{-}} \FunctionTok{qt}\NormalTok{(}\AttributeTok{p =}\NormalTok{ (}\DecValTok{1}\SpecialCharTok{{-}}\NormalTok{ci\_level)}\SpecialCharTok{/}\DecValTok{2}\NormalTok{, }
+               \AttributeTok{df =} \FunctionTok{sum}\NormalTok{(}\FunctionTok{unlist}\NormalTok{(model\_results}\SpecialCharTok{@}\NormalTok{Data}\SpecialCharTok{@}\NormalTok{nobs)), }
+               \AttributeTok{lower.tail =}\NormalTok{ F)}
+
+  \CommentTok{\# first get the data}
+\NormalTok{  graph.data }\OtherTok{\textless{}{-}}\NormalTok{ data\_coef }\SpecialCharTok{\%\textgreater{}\%} \CommentTok{\# put in tidy coefficients}
+  \FunctionTok{filter}\NormalTok{(model }\SpecialCharTok{==}\NormalTok{ model\_step) }\SpecialCharTok{\%\textgreater{}\%} \CommentTok{\# pick a model}
+  \FunctionTok{filter}\NormalTok{(}\FunctionTok{grepl}\NormalTok{(item\_name, term)) }\SpecialCharTok{\%\textgreater{}\%}  \CommentTok{\# pick a question}
+  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{group =} \FunctionTok{factor}\NormalTok{(group, }\AttributeTok{levels =} \FunctionTok{names}\NormalTok{(}\FunctionTok{table}\NormalTok{(data\_coef}\SpecialCharTok{$}\NormalTok{group)), }
+                        \AttributeTok{labels =} \FunctionTok{c}\NormalTok{(}\StringTok{"Group 1"}\NormalTok{, }\StringTok{"Group 2"}\NormalTok{))) }
+
+  \CommentTok{\# make ribbon data y = slope*x + intercept for ci for slopes }
+\NormalTok{  ribbondata }\OtherTok{\textless{}{-}} \FunctionTok{bind\_rows}\NormalTok{(}
+    \FunctionTok{data.frame}\NormalTok{(}
+    \AttributeTok{x =} \FunctionTok{seq}\NormalTok{(}\AttributeTok{from =}\NormalTok{ x\_limits[}\DecValTok{1}\NormalTok{] }\SpecialCharTok{{-}} \DecValTok{1}\NormalTok{,  }
+            \AttributeTok{to =}\NormalTok{ x\_limits[}\DecValTok{2}\NormalTok{] }\SpecialCharTok{+} \DecValTok{1}\NormalTok{, }
+            \AttributeTok{by =}\NormalTok{ .}\DecValTok{05}\NormalTok{), }
+    \AttributeTok{group =} \FunctionTok{unique}\NormalTok{(graph.data}\SpecialCharTok{$}\NormalTok{group)[}\DecValTok{1}\NormalTok{]}
+\NormalTok{  ) }\SpecialCharTok{\%\textgreater{}\%} 
+    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{ymin =}\NormalTok{ (graph.data }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(op }\SpecialCharTok{==} \StringTok{"=\textasciitilde{}"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
+                 \FunctionTok{slice\_head}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{pull}\NormalTok{(estimate) }\SpecialCharTok{*}\NormalTok{ x) }\SpecialCharTok{{-}} 
+\NormalTok{             (cutoff}\SpecialCharTok{*}\NormalTok{graph.data }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(op }\SpecialCharTok{==} \StringTok{"=\textasciitilde{}"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
+                    \FunctionTok{slice\_head}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{pull}\NormalTok{(std.error)) }\SpecialCharTok{+}
+\NormalTok{             graph.data }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(op }\SpecialCharTok{==} \StringTok{"\textasciitilde{}1"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
+                 \FunctionTok{slice\_head}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{pull}\NormalTok{(estimate), }
+           \AttributeTok{ymax =}\NormalTok{ (graph.data }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(op }\SpecialCharTok{==} \StringTok{"=\textasciitilde{}"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
+                 \FunctionTok{slice\_head}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{pull}\NormalTok{(estimate) }\SpecialCharTok{*}\NormalTok{ x) }\SpecialCharTok{+} 
+\NormalTok{             (cutoff}\SpecialCharTok{*}\NormalTok{graph.data }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(op }\SpecialCharTok{==} \StringTok{"=\textasciitilde{}"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
+                    \FunctionTok{slice\_head}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{pull}\NormalTok{(std.error)) }\SpecialCharTok{+}
+\NormalTok{             graph.data }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(op }\SpecialCharTok{==} \StringTok{"\textasciitilde{}1"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
+                 \FunctionTok{slice\_head}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{pull}\NormalTok{(estimate)), }
+    \FunctionTok{data.frame}\NormalTok{(}
+      \AttributeTok{x =} \FunctionTok{seq}\NormalTok{(}\AttributeTok{from =}\NormalTok{ x\_limits[}\DecValTok{1}\NormalTok{] }\SpecialCharTok{{-}} \DecValTok{1}\NormalTok{,  }
+              \AttributeTok{to =}\NormalTok{ x\_limits[}\DecValTok{2}\NormalTok{] }\SpecialCharTok{+} \DecValTok{1}\NormalTok{, }
+              \AttributeTok{by =}\NormalTok{ .}\DecValTok{05}\NormalTok{), }
+      \AttributeTok{group =} \FunctionTok{unique}\NormalTok{(graph.data}\SpecialCharTok{$}\NormalTok{group)[}\DecValTok{2}\NormalTok{]}
+\NormalTok{    ) }\SpecialCharTok{\%\textgreater{}\%} 
+      \FunctionTok{mutate}\NormalTok{(}\AttributeTok{ymin =}\NormalTok{ (graph.data }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(op }\SpecialCharTok{==} \StringTok{"=\textasciitilde{}"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
+                   \FunctionTok{slice\_tail}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{pull}\NormalTok{(estimate) }\SpecialCharTok{*}\NormalTok{ x) }\SpecialCharTok{{-}} 
+\NormalTok{               (cutoff}\SpecialCharTok{*}\NormalTok{graph.data }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(op }\SpecialCharTok{==} \StringTok{"=\textasciitilde{}"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
+                      \FunctionTok{slice\_tail}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{pull}\NormalTok{(std.error)) }\SpecialCharTok{+}
+\NormalTok{               graph.data }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(op }\SpecialCharTok{==} \StringTok{"\textasciitilde{}1"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
+                   \FunctionTok{slice\_tail}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{pull}\NormalTok{(estimate), }
+             \AttributeTok{ymax =}\NormalTok{ (graph.data }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(op }\SpecialCharTok{==} \StringTok{"=\textasciitilde{}"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
+                   \FunctionTok{slice\_tail}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{pull}\NormalTok{(estimate) }\SpecialCharTok{*}\NormalTok{ x) }\SpecialCharTok{+} 
+\NormalTok{               (cutoff}\SpecialCharTok{*}\NormalTok{graph.data }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(op }\SpecialCharTok{==} \StringTok{"=\textasciitilde{}"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
+                      \FunctionTok{slice\_tail}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{pull}\NormalTok{(std.error)) }\SpecialCharTok{+}
+\NormalTok{               graph.data }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(op }\SpecialCharTok{==} \StringTok{"\textasciitilde{}1"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
+                   \FunctionTok{slice\_tail}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{pull}\NormalTok{(estimate))}
+\NormalTok{  )}
+
+  \CommentTok{\# make point data to draw on the intercepts }
+\NormalTok{  pointdata }\OtherTok{\textless{}{-}} \FunctionTok{data.frame}\NormalTok{(}
+  \AttributeTok{x =} \FunctionTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{,}\DecValTok{0}\NormalTok{),}
+  \AttributeTok{y =}\NormalTok{ graph.data }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(op }\SpecialCharTok{==} \StringTok{"\textasciitilde{}1"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{pull}\NormalTok{(estimate), }
+  \AttributeTok{group =}\NormalTok{ graph.data }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(op }\SpecialCharTok{==} \StringTok{"\textasciitilde{}1"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{pull}\NormalTok{(group),}
+  \AttributeTok{ymin =}\NormalTok{ graph.data }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(op }\SpecialCharTok{==} \StringTok{"\textasciitilde{}1"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{pull}\NormalTok{(estimate) }\SpecialCharTok{{-}}
+\NormalTok{    cutoff }\SpecialCharTok{*}\NormalTok{ graph.data }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(op }\SpecialCharTok{==} \StringTok{"\textasciitilde{}1"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{pull}\NormalTok{(std.error), }
+  \AttributeTok{ymax =}\NormalTok{ graph.data }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(op }\SpecialCharTok{==} \StringTok{"\textasciitilde{}1"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{pull}\NormalTok{(estimate) }\SpecialCharTok{+}
+\NormalTok{    cutoff }\SpecialCharTok{*}\NormalTok{ graph.data }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(op }\SpecialCharTok{==} \StringTok{"\textasciitilde{}1"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{pull}\NormalTok{(std.error)}
+\NormalTok{  )}
+
+  \CommentTok{\# make the line data to draw on the slopes}
+\NormalTok{  linedata }\OtherTok{\textless{}{-}} \FunctionTok{data.frame}\NormalTok{(}
+  \AttributeTok{slope =}\NormalTok{ graph.data }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(op }\SpecialCharTok{==} \StringTok{"=\textasciitilde{}"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{pull}\NormalTok{(estimate), }
+  \AttributeTok{intercept =}\NormalTok{ graph.data }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(op }\SpecialCharTok{==} \StringTok{"\textasciitilde{}1"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{pull}\NormalTok{(estimate), }
+  \AttributeTok{group =}\NormalTok{ graph.data }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(op }\SpecialCharTok{==} \StringTok{"\textasciitilde{}1"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{pull}\NormalTok{(group)}
+\NormalTok{  )}
+
+  \CommentTok{\# make the distributions for the residuals }
+\NormalTok{  violindata }\OtherTok{\textless{}{-}} \FunctionTok{data.frame}\NormalTok{(}
+  \AttributeTok{y =} \FunctionTok{c}\NormalTok{(}\FunctionTok{rnorm}\NormalTok{(}\AttributeTok{n =} \DecValTok{1000}\NormalTok{, }
+            \AttributeTok{mean =}\NormalTok{ graph.data }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(op }\SpecialCharTok{==} \StringTok{"\textasciitilde{}\textasciitilde{}"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
+              \FunctionTok{slice\_head}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{pull}\NormalTok{(estimate), }
+            \AttributeTok{sd =}\NormalTok{ graph.data }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(op }\SpecialCharTok{==} \StringTok{"\textasciitilde{}\textasciitilde{}"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
+              \FunctionTok{slice\_head}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{pull}\NormalTok{(std.error)), }
+        \FunctionTok{rnorm}\NormalTok{(}\AttributeTok{n =} \DecValTok{1000}\NormalTok{, }
+            \AttributeTok{mean =}\NormalTok{ graph.data }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(op }\SpecialCharTok{==} \StringTok{"\textasciitilde{}\textasciitilde{}"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
+              \FunctionTok{slice\_tail}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{pull}\NormalTok{(estimate), }
+            \AttributeTok{sd =}\NormalTok{ graph.data }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(op }\SpecialCharTok{==} \StringTok{"\textasciitilde{}\textasciitilde{}"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
+              \FunctionTok{slice\_tail}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{pull}\NormalTok{(std.error))),}
+  \AttributeTok{group =} \FunctionTok{c}\NormalTok{(}\FunctionTok{rep}\NormalTok{(graph.data }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(op }\SpecialCharTok{==} \StringTok{"\textasciitilde{}\textasciitilde{}"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
+              \FunctionTok{slice\_head}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{pull}\NormalTok{(group), }\DecValTok{1000}\NormalTok{),}
+            \FunctionTok{rep}\NormalTok{(graph.data }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(op }\SpecialCharTok{==} \StringTok{"\textasciitilde{}\textasciitilde{}"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
+              \FunctionTok{slice\_tail}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{pull}\NormalTok{(group), }\DecValTok{1000}\NormalTok{)), }
+  \AttributeTok{x =} \DecValTok{1}
+\NormalTok{  )}
+
+  \CommentTok{\# make the latent mean data for right panel}
+\NormalTok{  latent\_means }\OtherTok{\textless{}{-}} \FunctionTok{lavPredict}\NormalTok{(model\_results, }
+                               \AttributeTok{type =} \StringTok{"lv"}\NormalTok{, }
+                               \AttributeTok{label =} \ConstantTok{TRUE}\NormalTok{,}
+                               \AttributeTok{assemble =} \ConstantTok{TRUE}\NormalTok{, }
+                               \AttributeTok{append.data =} \ConstantTok{TRUE}\NormalTok{)}
+
+\NormalTok{  latent\_means}\SpecialCharTok{$}\NormalTok{lv }\OtherTok{\textless{}{-}}\NormalTok{ latent\_means[ , lv\_name]}
+
+  \CommentTok{\# make a plot of the variance}
+\NormalTok{  variance\_plot }\OtherTok{\textless{}{-}} 
+  \FunctionTok{ggplot}\NormalTok{(violindata, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =} \DecValTok{1}\NormalTok{, }\AttributeTok{y =}\NormalTok{ y, }\AttributeTok{color =}\NormalTok{ group, }\AttributeTok{fill =}\NormalTok{ group)) }\SpecialCharTok{+}
+  \FunctionTok{geom\_split\_violin}\NormalTok{() }\SpecialCharTok{+} 
+  \FunctionTok{theme\_void}\NormalTok{() }\SpecialCharTok{+} 
+  \FunctionTok{theme}\NormalTok{(}\AttributeTok{legend.position =} \StringTok{"none"}\NormalTok{) }\SpecialCharTok{+} 
+  \FunctionTok{stat\_summary}\NormalTok{(}\AttributeTok{fun =} \StringTok{"mean"}\NormalTok{,}
+               \AttributeTok{geom =} \StringTok{"crossbar"}\NormalTok{, }
+               \AttributeTok{width =} \FloatTok{0.5}\NormalTok{,}
+               \AttributeTok{colour =} \StringTok{"black"}\NormalTok{)}
+
+  \CommentTok{\# make the plot with intercepts and slopes}
+\NormalTok{  intercept\_plot }\OtherTok{\textless{}{-}} 
+  \FunctionTok{ggplot}\NormalTok{() }\SpecialCharTok{+} 
+  \CommentTok{\# basic set up}
+  \FunctionTok{theme\_classic}\NormalTok{() }\SpecialCharTok{+} 
+  \FunctionTok{xlab}\NormalTok{(}\StringTok{"Latent Variable"}\NormalTok{) }\SpecialCharTok{+} 
+  \FunctionTok{ylab}\NormalTok{(}\StringTok{"Observed Variable"}\NormalTok{) }\SpecialCharTok{+} 
+  \FunctionTok{coord\_cartesian}\NormalTok{(}\AttributeTok{xlim =}\NormalTok{ x\_limits, }\AttributeTok{ylim =}\NormalTok{ y\_limits) }\SpecialCharTok{+} 
+  \CommentTok{\# plot the intercepts }
+  \FunctionTok{geom\_point}\NormalTok{(}\AttributeTok{data =}\NormalTok{ pointdata, }
+             \FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ x, }\AttributeTok{y =}\NormalTok{ y, }\AttributeTok{color =}\NormalTok{ group), }
+             \AttributeTok{inherit.aes =} \ConstantTok{FALSE}\NormalTok{) }\SpecialCharTok{+} 
+  \FunctionTok{geom\_errorbar}\NormalTok{(}\AttributeTok{data =}\NormalTok{ pointdata,}
+                \FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ x, }\AttributeTok{ymin =}\NormalTok{ ymin, }\AttributeTok{ymax =}\NormalTok{ ymax, }\AttributeTok{color =}\NormalTok{ group), }
+                \AttributeTok{inherit.aes =} \ConstantTok{FALSE}\NormalTok{, }\AttributeTok{width =}\NormalTok{ .}\DecValTok{10}\NormalTok{) }\SpecialCharTok{+} 
+  \CommentTok{\# plot the slopes}
+  \FunctionTok{geom\_abline}\NormalTok{(}\AttributeTok{data =}\NormalTok{ linedata,}
+              \FunctionTok{aes}\NormalTok{(}\AttributeTok{slope =}\NormalTok{ slope, }\AttributeTok{intercept =}\NormalTok{ intercept, }\AttributeTok{color =}\NormalTok{ group)) }\SpecialCharTok{+} 
+  \FunctionTok{geom\_ribbon}\NormalTok{(}\AttributeTok{data =}\NormalTok{ ribbondata, }
+              \FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ x, }\AttributeTok{ymin =}\NormalTok{ ymin, }\AttributeTok{ymax =}\NormalTok{ ymax, }\AttributeTok{fill =}\NormalTok{ group), }
+              \AttributeTok{inherit.aes =} \ConstantTok{FALSE}\NormalTok{, }\AttributeTok{alpha =}\NormalTok{ .}\DecValTok{2}\NormalTok{) }\SpecialCharTok{+} 
+  \FunctionTok{scale\_color\_discrete}\NormalTok{(}\AttributeTok{name =} \StringTok{"Group"}\NormalTok{) }\SpecialCharTok{+} 
+  \FunctionTok{scale\_fill\_discrete}\NormalTok{(}\AttributeTok{name =} \StringTok{"Group"}\NormalTok{) }\SpecialCharTok{+} 
+  \FunctionTok{geom\_vline}\NormalTok{(}\AttributeTok{xintercept =} \DecValTok{0}\NormalTok{) }\SpecialCharTok{+} 
+  \FunctionTok{theme}\NormalTok{(}\AttributeTok{axis.line.y =} \FunctionTok{element\_blank}\NormalTok{())}
+
+  \CommentTok{\# make the latent means plot}
+\NormalTok{  mean\_plot }\OtherTok{\textless{}{-}} \FunctionTok{ggplot}\NormalTok{(latent\_means, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ lv, }\AttributeTok{fill =}\NormalTok{ group)) }\SpecialCharTok{+}
+    \FunctionTok{geom\_density}\NormalTok{(}\AttributeTok{alpha =}\NormalTok{ .}\DecValTok{2}\NormalTok{) }\SpecialCharTok{+} 
+    \FunctionTok{theme\_classic}\NormalTok{() }\SpecialCharTok{+} 
+    \FunctionTok{xlab}\NormalTok{(}\StringTok{"Latent Variable"}\NormalTok{) }\SpecialCharTok{+} 
+    \FunctionTok{ylab}\NormalTok{(}\StringTok{"Density"}\NormalTok{) }\SpecialCharTok{+} 
+    \FunctionTok{geom\_vline}\NormalTok{(}\AttributeTok{data =}\NormalTok{ latent\_means }\SpecialCharTok{\%\textgreater{}\%}
+                 \FunctionTok{group\_by}\NormalTok{(group) }\SpecialCharTok{\%\textgreater{}\%} 
+                 \FunctionTok{summarize}\NormalTok{(}\AttributeTok{mean =} \FunctionTok{mean}\NormalTok{(lv)), }
+               \FunctionTok{aes}\NormalTok{(}\AttributeTok{xintercept =}\NormalTok{ mean, }\AttributeTok{color =}\NormalTok{ group)) }\SpecialCharTok{+} 
+    \FunctionTok{theme}\NormalTok{(}\AttributeTok{legend.position =} \StringTok{"none"}\NormalTok{) }\SpecialCharTok{+} 
+    \FunctionTok{coord\_cartesian}\NormalTok{(}\AttributeTok{xlim =}\NormalTok{ x\_limits)}
+
+\NormalTok{  y\_range }\OtherTok{=} \FunctionTok{abs}\NormalTok{(y\_limits[}\DecValTok{2}\NormalTok{] }\SpecialCharTok{{-}}\NormalTok{ y\_limits[}\DecValTok{1}\NormalTok{])}
+
+  \CommentTok{\# line up the two plots }
+\NormalTok{  prow }\OtherTok{\textless{}{-}} \FunctionTok{plot\_grid}\NormalTok{(}
+\NormalTok{    intercept\_plot }\SpecialCharTok{+} 
+      \FunctionTok{ggtitle}\NormalTok{(}\StringTok{"Item Invariance"}\NormalTok{) }\SpecialCharTok{+} 
+      \FunctionTok{theme}\NormalTok{(}\AttributeTok{legend.position =} \StringTok{"none"}\NormalTok{) }\SpecialCharTok{+} 
+      \FunctionTok{annotation\_custom}\NormalTok{(}\FunctionTok{ggplotGrob}\NormalTok{(variance\_plot), }
+                        \AttributeTok{xmin =}\NormalTok{ .}\DecValTok{25}\NormalTok{, }\AttributeTok{xmax =} \DecValTok{1}\NormalTok{, }
+                        \AttributeTok{ymin =}\NormalTok{ y\_limits[}\DecValTok{1}\NormalTok{], }
+                        \AttributeTok{ymax =}\NormalTok{ y\_limits[}\DecValTok{2}\NormalTok{]}\SpecialCharTok{{-}}\NormalTok{y\_range}\SpecialCharTok{/}\FloatTok{1.8}\NormalTok{),}
+\NormalTok{    mean\_plot }\SpecialCharTok{+} 
+      \FunctionTok{ggtitle}\NormalTok{(}\StringTok{"Latent Mean Distribution"}\NormalTok{) }\SpecialCharTok{+} 
+      \FunctionTok{theme}\NormalTok{(}\AttributeTok{legend.position =} \StringTok{"none"}\NormalTok{),}
+    \AttributeTok{align =} \StringTok{\textquotesingle{}vh\textquotesingle{}}\NormalTok{,}
+    \AttributeTok{hjust =} \SpecialCharTok{{-}}\DecValTok{1}\NormalTok{,}
+    \AttributeTok{nrow =} \DecValTok{1}
+\NormalTok{  )}
+
+  \CommentTok{\# get the lengend}
+\NormalTok{  legend\_b }\OtherTok{\textless{}{-}} \FunctionTok{get\_legend}\NormalTok{(}
+\NormalTok{    intercept\_plot }\SpecialCharTok{+} 
+      \FunctionTok{guides}\NormalTok{(}\AttributeTok{color =} \FunctionTok{guide\_legend}\NormalTok{(}\AttributeTok{nrow =} \DecValTok{1}\NormalTok{)) }\SpecialCharTok{+}
+      \FunctionTok{theme}\NormalTok{(}\AttributeTok{legend.position =} \StringTok{"bottom"}\NormalTok{)}
+\NormalTok{  )}
+
+  \CommentTok{\# send out the plot }
+  \FunctionTok{plot\_grid}\NormalTok{(prow, legend\_b, }\AttributeTok{ncol =} \DecValTok{1}\NormalTok{, }\AttributeTok{rel\_heights =} \FunctionTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{, .}\DecValTok{1}\NormalTok{))}
+
+\NormalTok{\}}
+\end{Highlighting}
+\end{Shaded}
+
+\normalsize
+
 \end{document}

### 2023-03-31 manuscript.Rmd
do the paper

@@
   group_names <- unique(data[ , group])
+  data$group <- data[ , group]
 
@@
   model_coef <- bind_rows(
-    tidy(model.overall, conf.level = .95) %>% mutate(model = "overall"), 
-    tidy(model.group1, conf.level = .95) %>% mutate(model = "group1"), 
-    tidy(model.group2, conf.level = .95) %>% mutate(model = "group2"), 
-    tidy(model.configural, conf.level = .95) %>% mutate(model = "configural"), 
-    tidy(model.metric, conf.level = .95) %>% mutate(model = "metric"), 
-    tidy(model.scalar, conf.level = .95) %>% mutate(model = "scalar"), 
-    tidy(model.strict, conf.level = .95) %>% mutate(model = "strict")
+    tidy(model.overall, conf.level = .95) %>% mutate(model = "Overall"), 
+    tidy(model.group1, conf.level = .95) %>% mutate(model = "Group 1"), 
+    tidy(model.group2, conf.level = .95) %>% mutate(model = "Group 2"), 
+    tidy(model.configural, conf.level = .95) %>% mutate(model = "Configural"), 
+    tidy(model.metric, conf.level = .95) %>% mutate(model = "Metric"), 
+    tidy(model.scalar, conf.level = .95) %>% mutate(model = "Scalar"), 
+    tidy(model.strict, conf.level = .95) %>% mutate(model = "Strict")
   )
@@
   model_fit <- bind_rows(
-    glance(model.overall) %>% mutate(model = "overall"), 
-    glance(model.group1) %>% mutate(model = "group1"), 
-    glance(model.group2) %>% mutate(model = "group2"), 
-    glance(model.configural) %>% mutate(model = "configural"), 
-    glance(model.metric) %>% mutate(model = "metric"), 
-    glance(model.scalar) %>% mutate(model = "scalar"), 
-    glance(model.strict) %>% mutate(model = "strict")
+    glance(model.overall) %>% mutate(model = "Overall"), 
+    glance(model.group1) %>% mutate(model = "Group 1"), 
+    glance(model.group2) %>% mutate(model = "Group 2"), 
+    glance(model.configural) %>% mutate(model = "Configural"), 
+    glance(model.metric) %>% mutate(model = "Metric"), 
+    glance(model.scalar) %>% mutate(model = "Scalar"), 
+    glance(model.strict) %>% mutate(model = "Strict")
     )
@@
 data_coef = results.large.res$model_coef
-model_step = "configural" 
+model_step = "Configural" 
 item_name = "q4"
@@
   data_coef = results.invariant$model_coef, # output from model_coef
-  model_step = "configural", # which model do you want to plot
+  model_step = "Configural", # which model do you want to plot
   item_name = "q4", # name of observed item
@@
 The y-axis indicates the observed variable scores, and here, the plot includes the entire range of the scale of the data for item four.
-The coefficient ($b_1$) for group 1 was `r apa_num(results.invariant$model_coef %>% filter(model == "configural") %>% filter(grepl("q4", term)) %>% filter(op == "=~") %>% slice_head() %>% pull(estimate))`, while the coefficient for group 2 was `r apa_num(results.invariant$model_coef %>% filter(model == "configural") %>% filter(grepl("q4", term)) %>% filter(op == "=~") %>% slice_tail() %>% pull(estimate))`.
+The coefficient ($b_1$) for group 1 was `r apa_num(results.invariant$model_coef %>% filter(model == "Configural") %>% filter(grepl("q4", term)) %>% filter(op == "=~") %>% slice_head() %>% pull(estimate))`, while the coefficient for group 2 was `r apa_num(results.invariant$model_coef %>% filter(model == "Configural") %>% filter(grepl("q4", term)) %>% filter(op == "=~") %>% slice_tail() %>% pull(estimate))`.
 The ribbon bands around the plotted slopes indicate the confidence interval for that estimate.
@@
 These are represented by a dot with a set of confidence error bars around the point.
-The intercept for group 1 was `r apa_num(results.invariant$model_coef %>% filter(model == "configural") %>% filter(grepl("q4", term)) %>% filter(op == "~1") %>% slice_head() %>% pull(estimate))`, while the coefficient for group 2 was `r apa_num(results.invariant$model_coef %>% filter(model == "configural") %>% filter(grepl("q4", term)) %>% filter(op == "~1") %>% slice_tail() %>% pull(estimate))`.
+The intercept for group 1 was `r apa_num(results.invariant$model_coef %>% filter(model == "Configural") %>% filter(grepl("q4", term)) %>% filter(op == "~1") %>% slice_head() %>% pull(estimate))`, while the coefficient for group 2 was `r apa_num(results.invariant$model_coef %>% filter(model == "Configural") %>% filter(grepl("q4", term)) %>% filter(op == "~1") %>% slice_tail() %>% pull(estimate))`.
 In this invariant depiction, the overlap in the intercepts is clear, indicating they are not different.
@@
 Therefore, residuals are represented in the inset picture at the bottom right of the item invariance plot.
-The black bars represent the estimated residual for each group (group 1: `r apa_num(results.invariant$model_coef %>% filter(model == "configural") %>% filter(grepl("q4", term)) %>% filter(op == "~~") %>% slice_head() %>% pull(estimate))`, group 2: `r apa_num(results.invariant$model_coef %>% filter(model == "configural") %>% filter(grepl("q4", term)) %>% filter(op == "~~") %>% slice_tail() %>% pull(estimate))`).
+The black bars represent the estimated residual for each group (group 1: `r apa_num(results.invariant$model_coef %>% filter(model == "Configural") %>% filter(grepl("q4", term)) %>% filter(op == "~~") %>% slice_head() %>% pull(estimate))`, group 2: `r apa_num(results.invariant$model_coef %>% filter(model == "Configural") %>% filter(grepl("q4", term)) %>% filter(op == "~~") %>% slice_tail() %>% pull(estimate))`).
 The distributions are plotted to represent the normal spread of values using the standard error of the residuals.
@@
   data_coef = results.invariant$model_coef, # output from model_coef
-  model_step = "configural", # which model
+  model_step = "Configural", # which model
   item_name = "q4", # name of observed item
@@
 Additionally, consider that we set the scaling of the model to 0.
-The estimate for the lv mean in the large loading model was group 1: `r apa_num(results.invariant$model_coef %>% filter(model == "configural") %>% filter(grepl("lv", term)) %>% filter(op == "~1") %>% slice_head() %>% pull(estimate))`, and group 2: `r apa_num(results.invariant$model_coef %>% filter(model == "configural") %>% filter(grepl("lv", term)) %>% filter(op == "~1") %>% slice_tail() %>% pull(estimate))`, which results in `r apa_num(results.invariant$model_coef %>% filter(model == "configural") %>% filter(grepl("lv", term)) %>% filter(op == "~1") %>% slice_head() %>% pull(estimate) - results.invariant$model_coef %>% filter(model == "configural") %>% filter(grepl("lv", term)) %>% filter(op == "~1") %>% slice_tail() %>% pull(estimate))` difference in group means.
+The estimate for the lv mean in the large loading model was group 1: `r apa_num(results.invariant$model_coef %>% filter(model == "Configural") %>% filter(grepl("lv", term)) %>% filter(op == "~1") %>% slice_head() %>% pull(estimate))`, and group 2: `r apa_num(results.invariant$model_coef %>% filter(model == "Configural") %>% filter(grepl("lv", term)) %>% filter(op == "~1") %>% slice_tail() %>% pull(estimate))`, which results in `r apa_num(results.invariant$model_coef %>% filter(model == "Configural") %>% filter(grepl("lv", term)) %>% filter(op == "~1") %>% slice_head() %>% pull(estimate) - results.invariant$model_coef %>% filter(model == "Configural") %>% filter(grepl("lv", term)) %>% filter(op == "~1") %>% slice_tail() %>% pull(estimate))` difference in group means.
 The practical implications of this difference will depend on the research and interpretations of the researcher.
@@
   data_coef = results.small.load$model_coef, # output from model_coef
-  model_step = "configural", # which model
+  model_step = "Configural", # which model
   item_name = "q4", # name of observed item
@@
   data_coef = results.med.load$model_coef, # output from model_coef
-  model_step = "configural", # which model
+  model_step = "Configural", # which model
   item_name = "q4", # name of observed item
@@
   data_coef = results.large.load$model_coef, # output from model_coef
-  model_step = "configural", # which model
+  model_step = "Configural", # which model
   item_name = "q4", # name of observed item
@@
 Intercept differences can be clearly seen represented by the spacing out of the intercept locations (and thus, the overall line as well).
-Note how little the intercept differences appear to influence the latent variable means and distributions.
+While the changes in intercept do not appear to change the latent means, the cavaet to this simulation is that only item four was manipulated.
+An example is provided below that demonstrates large changes in latent means.
 
@@
   data_coef = results.small.int$model_coef, # output from model_coef
-  model_step = "metric", # which model
+  model_step = "Metric", # which model
   item_name = "q4", # name of observed item
@@
   data_coef = results.med.int$model_coef, # output from model_coef
-  model_step = "metric", # which model
+  model_step = "Metric", # which model
   item_name = "q4", # name of observed item
@@
   data_coef = results.large.int$model_coef, # output from model_coef
-  model_step = "metric", # which model
+  model_step = "Metric", # which model
   item_name = "q4", # name of observed item
@@
   data_coef = results.small.res$model_coef, # output from model_coef
-  model_step = "scalar", # which model
+  model_step = "Scalar", # which model
   item_name = "q4", # name of observed item
@@
   data_coef = results.med.res$model_coef, # output from model_coef
-  model_step = "scalar", # which model
+  model_step = "Scalar", # which model
   item_name = "q4", # name of observed item
@@
   data_coef = results.large.res$model_coef, # output from model_coef
-  model_step = "scalar", # which model
+  model_step = "Scalar", # which model
   item_name = "q4", # name of observed item
@@
 @aiena2014 did not compare the clinical to the student sample for measurement invariance, and it is reasonable to expect potential differences in these two populations.
+This example will demonstrate the procedure for researchers who wish to use partial invariance steps and how to interpret real, messy data.
 
 ```{r echo = T, include = T, size = "small"}
+# load the data
 load("RS14.Rdata")
+# build the one-factor model 
 model.rs <- "RS =~ RS1+RS2+RS3+RS4+RS5+RS6+RS7+RS8+RS9+RS10+RS11+RS12+RS13+RS14"
+# run the multi-group CFA
 results.rs <- mgcfa(data = DF, 
@@
                     model = model.rs)
-
-results.rs$model_fit %>% select(model, AIC, BIC, cfi, tli, rmsea, srmr)
-
+```
+
+```{r eval = F, echo = T, include = T, size = "small"}
+# how to get results in table 
+results.rs$model_fit %>% 
+        select(model, AIC, BIC, cfi, tli, rmsea, srmr)
+```
+
+```{r rs-table, results = 'asis'}
+apa_table(results.rs$model_fit %>% 
+        select(model, AIC, BIC, cfi, tli, rmsea, srmr), 
+        col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
+          caption = "Model Fit for RS-14 Example")
+```
+
+Table \@ref(fig:invariant-pic) indicates the results after running the one-factor model. There are several guidelines for assessing assessing a degradation in model fit [@cheung]
+
+```{r}
 ##write out partial codes
@@
   item_name = "RS6",
-  x_limits = c(-1,1),
+  x_limits = c(-2,2),
   y_limits = c(min(DF$RS7), max(DF$RS7)),
@@
 
-```
+plot_mgcfa(
+  data_coef = partial.coef,
+  model_step = "intercepts", 
+  item_name = "RS7",
+  x_limits = c(-2,2),
+  y_limits = c(min(DF$RS7), max(DF$RS7)),
+  model_results = partial.rs.2.picture, 
+  ci_level = .95,
+  lv_name = "RS"
+)
+
+SD <- tapply(DF$RS6, DF$sample, sd)
+M <- tapply(DF$RS6, DF$sample, mean)
+N <- tapply(DF$RS6, DF$sample, length)
+
+SD2 <- tapply(DF$RS7, DF$sample, sd)
+M2 <- tapply(DF$RS7, DF$sample, mean)
+N2 <- tapply(DF$RS7, DF$sample, length)
+
+library(MOTE)
+d.ind.t(M[1], M[2], SD[1], SD[2], N[1], N[2])
+d.ind.t(M2[1], M2[2], SD2[1], SD2[2], N2[1], N2[2])
+lavaan_dmacs(partial.rs.2.picture, "Clinical")
+lavaan_dmacs(results.rs$model.configural, "Clinical")
+```
+
+6: Drive
+
+7: Perseverance
+
+I1tems for the RS–14 are described in the measure’s manual (Wagnild, 2009a)
+and can be viewed at www.resiliencecenter.com.
 
@@
     tidy(model.overall, conf.level = .95) %>% 
-      mutate(model = "overall"), 
+      mutate(model = "Overall"), 
     tidy(model.group1, conf.level = .95) %>% 
-      mutate(model = "group1"), 
+      mutate(model = "Group 1"), 
     tidy(model.group2, conf.level = .95) %>% 
-      mutate(model = "group2"), 
+      mutate(model = "Group 2"), 
     tidy(model.configural, conf.level = .95) %>% 
-      mutate(model = "configural"), 
+      mutate(model = "Configural"), 
     tidy(model.metric, conf.level = .95) %>% 
-      mutate(model = "metric"), 
+      mutate(model = "Metric"), 
     tidy(model.scalar, conf.level = .95) %>% 
-      mutate(model = "scalar"), 
+      mutate(model = "Scalar"), 
     tidy(model.strict, conf.level = .95) %>% 
-      mutate(model = "strict")
+      mutate(model = "Strict")
   )

### 2023-03-31 manuscript.tex
do the paper

@@
 
+\texttt{lavaan} automatically sets the mean (i.e., the intercept) for latent variables to zero.
+If we wish to visualize the impact of the changes in parameter estimates across groups on the latent means, we need to allow the latent mean estimation with \texttt{lv\ \textasciitilde{}\ 1}.
+However, adding this estimation into our model will create a non-identified model.
+To solve this problem, you can set one of the intercepts of another variable to a value to scale the model.
+Here we will set the scale of the model by using \texttt{q1\ \textasciitilde{}\ 0*1}, thus, scaling the expected means to zero.
+With simulation, this step is easy to know which variable to pick - we set the intercept on the variable we know did not show differences.
+In real data, you may wish to run the model steps \emph{without} setting this option, examine the results of a configural or separate models, and then add the option for the values most similar.
+Additionally, you could complete partial invariance steps to determine which value appears most consistent to fix.
+
 \small
@@
 \CommentTok{\# create lavaan model}
-\NormalTok{model.overall }\OtherTok{\textless{}{-}} \StringTok{"lv =\textasciitilde{} q1 + q2 + q3 + q4 + q5}
+\NormalTok{model.overall }\OtherTok{\textless{}{-}} \StringTok{"}
+\StringTok{\# overall one{-}factor model}
+\StringTok{lv =\textasciitilde{} q1 + q2 + q3 + q4 + q5}
+\StringTok{\# set the intercept (mean) of q1 to zero}
 \StringTok{q1 \textasciitilde{} 0*1}
+\StringTok{\# allow the lv intercept to be freely estimated}
 \StringTok{lv \textasciitilde{} 1"}
@@
   \texttt{model\_coef}: a tidy dataframe with \emph{all} model's coefficients saved from the \texttt{lavaan} outputs.
+Note that we can see that the intercept \texttt{\textasciitilde{}1} is set for question 1 but freely estimated for the latent variable.
 \end{enumerate}
@@
 \begin{Highlighting}[]
-\FunctionTok{head}\NormalTok{(results.invariant}\SpecialCharTok{$}\NormalTok{model\_coef)}
+\NormalTok{results.invariant}\SpecialCharTok{$}\NormalTok{model\_coef[}\DecValTok{1}\SpecialCharTok{:}\DecValTok{10}\NormalTok{ , ]}
 \end{Highlighting}
@@
 \begin{verbatim}
-## # A tibble: 6 x 13
+## # A tibble: 10 x 13
 ##    term     op    estimate std.error statistic   p.value  std.lv std.all std.nox
 ##    <chr>    <chr>    <dbl>     <dbl>     <dbl>     <dbl>   <dbl>   <dbl>   <dbl>
-## 1 "lv =~ q1" =~       1        0          NA    NA         0.780   0.598   0.598
-## 2 "lv =~ q2" =~       0.564    0.0864      6.52  6.99e-11  0.440   0.435   0.435
-## 3 "lv =~ q3" =~       0.748    0.105       7.12  1.09e-12  0.583   0.505   0.505
-## 4 "lv =~ q4" =~       0.338    0.0804      4.20  2.62e- 5  0.264   0.250   0.250
-## 5 "lv =~ q5" =~       0.904    0.120       7.52  5.48e-14  0.705   0.613   0.613
+##  1 "lv =~ ~ =~      1         0         NA     NA         0.780   0.598   0.598 
+##  2 "lv =~ ~ =~      0.564     0.0864     6.52   6.99e-11  0.440   0.435   0.435 
+##  3 "lv =~ ~ =~      0.748     0.105      7.12   1.09e-12  0.583   0.505   0.505 
+##  4 "lv =~ ~ =~      0.338     0.0804     4.20   2.62e- 5  0.264   0.250   0.250 
+##  5 "lv =~ ~ =~      0.904     0.120      7.52   5.48e-14  0.705   0.613   0.613 
 ##  6 "q1 ~1 " ~1      0         0         NA     NA         0       0       0     
+##  7 "lv ~1 " ~1     -0.0187    0.0584    -0.320  7.49e- 1 -0.0239 -0.0239 -0.0239
+##  8 "q1 ~~ ~ ~~      1.09      0.103     10.6    0         1.09    0.643   0.643 
+##  9 "q2 ~~ ~ ~~      0.828     0.0604    13.7    0         0.828   0.811   0.811 
+## 10 "q3 ~~ ~ ~~      0.997     0.0786    12.7    0         0.997   0.745   0.745 
 ## # i 4 more variables: model <chr>, block <int>, group <int>, label <chr>
@@
 Use only two numbers, a lower and upper limit.
+This value also constrains the latent mean diagram to help zoom in on group differences because the scale of latent means is usually centered over zero.
+You can use this parameter to zoom out to a more traditional histogram using \texttt{c(-2,\ 2)}.
 \item
@@
   \AttributeTok{data\_coef =}\NormalTok{ results.invariant}\SpecialCharTok{$}\NormalTok{model\_coef, }\CommentTok{\# output from model\_coef}
-  \AttributeTok{model\_step =} \StringTok{"configural"}\NormalTok{, }\CommentTok{\# which model do you want to plot}
+  \AttributeTok{model\_step =} \StringTok{"Configural"}\NormalTok{, }\CommentTok{\# which model do you want to plot}
   \AttributeTok{item\_name =} \StringTok{"q4"}\NormalTok{, }\CommentTok{\# name of observed item}
@@
 The overall impact of differences on the latent means can be found in the right hand visualization.
-The latent means are calculated by using the \texttt{predict} function and then plotted as overlapping histograms.
+The latent means are calculated by using the \texttt{lavPredict} function and then plotted as overlapping histograms.
 The vertical colored lines represent the mean for each group, and the spread of the distribution can be examined using the density coloring.
@@
 At the medium effect size, we see that the confidence bands do not overlap (at the edges), and at the large effect size, we can see a clear separation of two lines.
-Note that the intercepts are still fixed so the loading representation will not literally separate, but the steepness of the lines is the indicator of the difference between the slopes.
+Note that the intercepts in this model are estimated as equal so the loading representation will not literally separate, but the steepness of the lines is the indicator of the difference between the slopes.
 You can imagine these lines are interpreted like a simple slopes analysis for interactions in regression (Cohen, Cohen, West, \& Aiken, 2003).
@@
 If they are parallel, there is likely invariance (they are the same), and the further from parallel they become, the larger the effect size for the differences between group loadings.
+
+The latent means in Figure \ref{fig:large-load-pic} do appear to show differences, albeit visually small.
+The latent means diagram shows the impact of any group differences that aren't constrained, and this image shows the configural model (as the metric model would force them to be equal).
+In the simulated model, the \emph{only} manipulated parameter is question 4's loading.
+In real models, the differences may be larger due to other variation found in the parameter estimates.
+Therefore, once you discover items you believe would make a model ``partially'' invariant, you may wish to estimate that model and graph the item again using the partially invariant model to see only the effect of the non-invariant items.
+Additionally, consider that we set the scaling of the model to 0.
+The estimate for the lv mean in the large loading model was group 1: 0.00, and group 2: -0.04, which results in 0.04 difference in group means.
+The practical implications of this difference will depend on the research and interpretations of the researcher.
 
@@
 
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
-
-Conclusions:
-
-\begin{itemize}
-\tightlist
-\item
-  framework for submitted/interpreting reports
-\end{itemize}
-
-\newpage
-
-\hypertarget{references}{%
-\section{References}\label{references}}
-
-\hypertarget{refs}{}
-\begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-akaike1998}{}}%
-Akaike, H.
-(1998).
-\emph{Information theory and an extension of the maximum likelihood principle} (E.
-Parzen, K.
-Tanabe, \& G.
-Kitagawa, Eds.).
-New York, NY: Springer New York.
-Retrieved from \url{http://link.springer.com/10.1007/978-1-4612-1694-0_15}
-
-\leavevmode\vadjust pre{\hypertarget{ref-anvari2021}{}}%
-Anvari, F., \& Lakens, D.
-(2021).
-Using anchor-based methods to determine the smallest effect size of interest.
-\emph{Journal of Experimental Social Psychology}, \emph{96}, 104159.
-\url{https://doi.org/10.1016/j.jesp.2021.104159}
-
-\leavevmode\vadjust pre{\hypertarget{ref-barry2014}{}}%
-Barry, A.
-E., Chaney, B., Piazza-Gardner, A.
-K., \& Chavarria, E.
-A.
-(2014).
-Validity and Reliability Reporting Practices in the Field of Health Education and Behavior: A Review of Seven Journals.
-\emph{Health Education \& Behavior}, \emph{41}(1), 12--18.
-\url{https://doi.org/10.1177/1090198113483139}
-
-\leavevmode\vadjust pre{\hypertarget{ref-beaujean2014}{}}%
-Beaujean, A. A. (2014). \emph{Latent variable modeling using r: A step by step guide}. New York: Routledge/Taylor \& Francis Group.
-
-\leavevmode\vadjust pre{\hypertarget{ref-bentler1990}{}}%
-Bentler, P. M. (1990). Comparative fit indexes in structural models. \emph{Psychological Bulletin}, \emph{107}(2), 238--246. \url{https://doi.org/10.1037/0033-2909.107.2.238}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bentler1995}{}}%
-Bentler, P. M. (1995). \emph{EQS structural equations program manual}. Encino, CA.
-
-\leavevmode\vadjust pre{\hypertarget{ref-boker2011}{}}%
-Boker, S., Neale, M., Maes, H., Wilde, M., Spiegel, M., Brick, T., \ldots{} Fox, J.
-(2011).
-OpenMx: An Open Source Extended Structural Equation Modeling Framework.
-\emph{Psychometrika}, \emph{76}(2), 306--317.
-\url{https://doi.org/10.1007/s11336-010-9200-6}
-
-\leavevmode\vadjust pre{\hypertarget{ref-brown2015}{}}%
-Brown, T. A. (2015). \emph{Confirmatory factor analysis for applied research} (Second edition). New York ; London: The Guilford Press.
-
-\leavevmode\vadjust pre{\hypertarget{ref-byrne2001}{}}%
-Byrne, B.
-M.
-(2001).
-Structural Equation Modeling With AMOS, EQS, and LISREL: Comparative Approaches to Testing for the Factorial Validity of a Measuring Instrument.
-\emph{International Journal of Testing}, \emph{1}(1), 55--86.
-\url{https://doi.org/10.1207/S15327574IJT0101_4}
-
-\leavevmode\vadjust pre{\hypertarget{ref-byrne1989}{}}%
-Byrne, B.
-M., Shavelson, R.
-J., \& Muthén, B.
-(1989).
-Testing for the equivalence of factor covariance and mean structures: The issue of partial measurement invariance.
-\emph{Psychological Bulletin}, \emph{105}(3), 456--466.
-\url{https://doi.org/10.1037/0033-2909.105.3.456}
-
-\leavevmode\vadjust pre{\hypertarget{ref-cheung2002}{}}%
-Cheung, G.
-W., \& Rensvold, R.
-B.
-(2002).
-Evaluating Goodness-of-Fit Indexes for Testing Measurement Invariance.
-\emph{Structural Equation Modeling: A Multidisciplinary Journal}, \emph{9}(2), 233--255.
-\url{https://doi.org/10.1207/s15328007sem0902_5}
-
-\leavevmode\vadjust pre{\hypertarget{ref-chorpita2000}{}}%
-Chorpita, B.
-F., Yim, L., Moffitt, C., Umemoto, L.
-A., \& Francis, S.
-E.
-(2000).
-Assessment of symptoms of DSM-IV anxiety and depression in children: a revised child anxiety and depression scale.
-\emph{Behaviour Research and Therapy}, \emph{38}(8), 835--855.
-\url{https://doi.org/10.1016/S0005-7967(99)00130-8}
-
-\leavevmode\vadjust pre{\hypertarget{ref-cohen2003}{}}%
-Cohen, J., Cohen, P., West, S. G., \& Aiken, L. (2003). \emph{Applied multiple regression / correlation analysis for the behavioral sciences} (3rd ed.). Lawrence Erlbaum Associates.
-
-\leavevmode\vadjust pre{\hypertarget{ref-devellis2022}{}}%
-DeVellis, R. F., \& Thorpe, C. T. (2022). \emph{Scale development: Theory and applications} (Fifth edition). Thousand Oaks, California: SAGE Publications, Inc.
-
-\leavevmode\vadjust pre{\hypertarget{ref-dueber2023}{}}%
-Dueber, D. (2023). \emph{Dmacs}. Retrieved from \url{https://github.com/ddueber/dmacs}
-
-\leavevmode\vadjust pre{\hypertarget{ref-flake2020}{}}%
-Flake, J.
-K., \& Fried, E.
-I.
-(2020).
-Measurement Schmeasurement: Questionable Measurement Practices and How to Avoid Them.
-\emph{Advances in Methods and Practices in Psychological Science}, \emph{3}(4), 456--465.
-\url{https://doi.org/10.1177/2515245920952393}
-
-\leavevmode\vadjust pre{\hypertarget{ref-juxf6reskog1971}{}}%
-Jöreskog, K. G. (1971). Simultaneous factor analysis in several populations. \emph{Psychometrika}, \emph{36}(4), 409--426. \url{https://doi.org/10.1007/BF02291366}
-
-\leavevmode\vadjust pre{\hypertarget{ref-juxf6reskog2001}{}}%
-Jöreskog, Karl G., \& Sörbom, D. (2001). \emph{LISREL 8: user's reference guide} (2. ed., updated to LISREL 8). Lincolnwood, Ill: SSI Scientific Software Internat.
-
-\leavevmode\vadjust pre{\hypertarget{ref-kline2016}{}}%
-Kline, R. B. (2016). \emph{Principles and practice of structural equation modeling} (Fourth edition). New York: The Guilford Press.
-
-\leavevmode\vadjust pre{\hypertarget{ref-lakens2017}{}}%
-Lakens, D. (2017). Equivalence Tests. \emph{Social Psychological and Personality Science}, \emph{8}(4), 355--362. \url{https://doi.org/10.1177/1948550617697177}
-
-\leavevmode\vadjust pre{\hypertarget{ref-makel2014}{}}%
-Makel, M.
-C., \& Plucker, J.
-A.
-(2014).
-Facts Are More Important Than Novelty: Replication in the Education Sciences.
-\emph{Educational Researcher}, \emph{43}(6), 304--316.
-\url{https://doi.org/10.3102/0013189X14545513}
-
-\leavevmode\vadjust pre{\hypertarget{ref-makel2012}{}}%
-Makel, M.
-C., Plucker, J.
-A., \& Hegarty, B.
-(2012).
-Replications in Psychology Research: How Often Do They Really Occur?
-\emph{Perspectives on Psychological Science}, \emph{7}(6), 537--542.
-\url{https://doi.org/10.1177/1745691612460688}
-
-\leavevmode\vadjust pre{\hypertarget{ref-marsh2004}{}}%
-Marsh, H.
-W., Hau, K.-T., \& Wen, Z.
-(2004).
-In search of golden rules: Comment on hypothesis-testing approaches to setting cutoff values for fit indexes and dangers in overgeneralizing hu and bentler's (1999) findings.
-\emph{Structural Equation Modeling: A Multidisciplinary Journal}, \emph{11}(3), 320--341.
-\url{https://doi.org/10.1207/s15328007sem1103_2}
-
-\leavevmode\vadjust pre{\hypertarget{ref-meade2008}{}}%
-Meade, A.
-W., Johnson, E.
-C., \& Braddy, P.
-W.
-(2008).
-Power and sensitivity of alternative fit indices in tests of measurement invariance.
-\emph{Journal of Applied Psychology}, \emph{93}(3), 568--592.
-\url{https://doi.org/10.1037/0021-9010.93.3.568}
-
-\leavevmode\vadjust pre{\hypertarget{ref-meredith1993}{}}%
-Meredith, W. (1993). Measurement invariance, factor analysis and factorial invariance. \emph{Psychometrika}, \emph{58}(4), 525--543. \url{https://doi.org/10.1007/BF02294825}
-
-\leavevmode\vadjust pre{\hypertarget{ref-nelson2018}{}}%
-Nelson, L. D., Simmons, J., \& Simonsohn, U. (2018). Psychology's renaissance. \emph{Annual Review of Psychology}, \emph{69}(1), 511--534. \url{https://doi.org/10.1146/annurev-psych-122216-011836}
-
-\leavevmode\vadjust pre{\hypertarget{ref-nye2019}{}}%
-Nye, C.
-D., Bradburn, J., Olenick, J., Bialko, C., \& Drasgow, F.
-(2019).
-How Big Are My Effects?
-Examining the Magnitude of Effect Sizes in Studies of Measurement Equivalence.
-\emph{Organizational Research Methods}, \emph{22}(3), 678--709.
-\url{https://doi.org/10.1177/1094428118761122}
-
-\leavevmode\vadjust pre{\hypertarget{ref-nye2011}{}}%
-Nye, C.
-D., \& Drasgow, F.
-(2011).
-Effect size indices for analyses of measurement equivalence: Understanding the practical importance of differences between groups.
-\emph{Journal of Applied Psychology}, \emph{96}(5), 966--980.
-\url{https://doi.org/10.1037/a0022955}
-
-\leavevmode\vadjust pre{\hypertarget{ref-putnick2016}{}}%
-Putnick, D.
-L., \& Bornstein, M.
-H.
-(2016).
-Measurement invariance conventions and reporting: The state of the art and future directions for psychological research.
-\emph{Developmental Review}, \emph{41}, 71--90.
-\url{https://doi.org/10.1016/j.dr.2016.06.004}
-
-\leavevmode\vadjust pre{\hypertarget{ref-rosseel2012}{}}%
-Rosseel, Y. (2012). Lavaan: An r package for structural equation modeling. \emph{Journal of Statistical Software}, \emph{48}(1), 1--36. \url{https://doi.org/10.18637/jss.v048.i02}
-
-\leavevmode\vadjust pre{\hypertarget{ref-schwarz1978}{}}%
-Schwarz, G. (1978). Estimating the dimension of a model. \emph{The Annals of Statistics}, \emph{6}(2), 461--464. Retrieved from \url{https://www.jstor.org/stable/2958889}
-
-\leavevmode\vadjust pre{\hypertarget{ref-shadish2001}{}}%
-Shadish, W. R., Cook, T. D., \& Campbell, D. T. (2001). \emph{Experimental and quasi-experimental designs for generalized causal inference}. Boston: Houghton Mifflin.
-
-\leavevmode\vadjust pre{\hypertarget{ref-suxf6rbom1978}{}}%
-Sörbom, D. (1978). An alternative to the methodology for analysis of covariance. \emph{Psychometrika}, \emph{43}(3), 381--396. \url{https://doi.org/10.1007/BF02293647}
-
-\leavevmode\vadjust pre{\hypertarget{ref-stark2006}{}}%
-Stark, S., Chernyshenko, O.
-S., \& Drasgow, F.
-(2006).
-Detecting differential item functioning with confirmatory factor analysis and item response theory: Toward a unified strategy.
-\emph{Journal of Applied Psychology}, \emph{91}(6), 1292--1306.
-\url{https://doi.org/10.1037/0021-9010.91.6.1292}
-
-\leavevmode\vadjust pre{\hypertarget{ref-steiger1990}{}}%
-Steiger, J.
-H.
-(1990).
-Structural model evaluation and modification: An interval estimation approach.
-\emph{Multivariate Behavioral Research}, \emph{25}(2), 173--180.
-\url{https://doi.org/10.1207/s15327906mbr2502_4}
-
-\leavevmode\vadjust pre{\hypertarget{ref-tay2015}{}}%
-Tay, L., Meade, A.
-W., \& Cao, M.
-(2015).
-An Overview and Practical Guide to IRT Measurement Equivalence Analysis.
-\emph{Organizational Research Methods}, \emph{18}(1), 3--46.
-\url{https://doi.org/10.1177/1094428114553062}
-
-\leavevmode\vadjust pre{\hypertarget{ref-thompson1996}{}}%
-Thompson, B., \& Daniel, L.
-G.
-(1996).
-Factor Analytic Evidence for the Construct Validity of Scores: A Historical Overview and Some Guidelines.
-\emph{Educational and Psychological Measurement}, \emph{56}(2), 197--208.
-\url{https://doi.org/10.1177/0013164496056002001}
-
-\leavevmode\vadjust pre{\hypertarget{ref-trent2013}{}}%
-Trent, L.
-R., Buchanan, E., Ebesutani, C., Ale, C.
-M., Heiden, L., Hight, T.
-L., \ldots{} Young, J.
-(2013).
-A measurement invariance examination of the revised child anxiety and depression scale in a southern sample: Differential item functioning between african american and caucasian youth.
-\emph{Assessment}, \emph{20}(2), 175--187.
-\url{https://doi.org/10.1177/1073191112450907}
-
-\leavevmode\vadjust pre{\hypertarget{ref-tucker1973}{}}%
-Tucker, L. R., \& Lewis, C. (1973). A reliability coefficient for maximum likelihood factor analysis. \emph{Psychometrika}, \emph{38}(1), 1--10. \url{https://doi.org/10.1007/BF02291170}
-
-\leavevmode\vadjust pre{\hypertarget{ref-vandeschoot2015}{}}%
-Van De Schoot, R., Schmidt, P., De Beuckelaer, A., Lek, K., \& Zondervan-Zwijnenburg, M.
-(2015).
-Editorial: Measurement invariance.
-\emph{Frontiers in Psychology}, \emph{6}.
-Retrieved from \url{https://www.frontiersin.org/articles/10.3389/fpsyg.2015.01064}
-
-\leavevmode\vadjust pre{\hypertarget{ref-vazire2022}{}}%
-Vazire, S., Schiavone, S.
-R., \& Bottesini, J.
-G.
-(2022).
-Credibility Beyond Replicability: Improving the Four Validities in Psychological Science.
-\emph{Current Directions in Psychological Science}, \emph{31}(2), 162--168.
-\url{https://doi.org/10.1177/09637214211067779}
-
-\leavevmode\vadjust pre{\hypertarget{ref-weidman2017}{}}%
-Weidman, A.
-C., Steckler, C.
-M., \& Tracy, J.
-L.
-(2017).
-The jingle and jangle of emotion assessment: Imprecise measurement, casual scale usage, and conceptual fuzziness in emotion research.
-\emph{Emotion}, \emph{17}(2), 267--295.
-\url{https://doi.org/10.1037/emo0000226}
-
-\leavevmode\vadjust pre{\hypertarget{ref-zwaan2018}{}}%
-Zwaan, R. A., Etz, A., Lucas, R. E., \& Donnellan, M. B. (2018). Making replication mainstream. \emph{Behavioral and Brain Sciences}, \emph{41}, e120. \url{https://doi.org/10.1017/S0140525X17001972}
-
-\end{CSLReferences}
-
-\newpage
-
-\hypertarget{appendix}{%
-\section{Appendix}\label{appendix}}
-
-\hypertarget{model-fit-statistics}{%
-\subsection{Model Fit Statistics}\label{model-fit-statistics}}
-
-Model fit statistics are provided for each of the ten model combinations (invariant, three sizes for each ladings, intercepts, and residuals).
-These tables could be used to examine the traditional change in fit statistics cutoff rules of thumb (Cheung \& Rensvold, 2002), such as \(\Delta\) CFI or \(\Delta\) RMSEA, to the visualizations presented in the manuscript.
+\hypertarget{an-example-analysis}{%
+\subsection{An Example Analysis}\label{an-example-analysis}}
+
+Aiena, Baczwaski, Schulenberg, and Buchanan (2014) examined the RS-14 (Wagnild, 2009) exploring the factor structure of the Resiliency Scale in a clinical sample receiving treatment services and a college student sample.
+Measurement invariance was calculated for differences separately for these samples for gender and race finding a partially invariant models with a few item intercepts or residuals that differed between groups.
+Aiena et al.
+(2014) did not compare the clinical to the student sample for measurement invariance, and it is reasonable to expect potential differences in these two populations.
+This example will demonstrate the procedure for researchers who wish to use partial invariance steps and how to interpret real, messy data.
+
+\small
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\# load the data}
+\FunctionTok{load}\NormalTok{(}\StringTok{"RS14.Rdata"}\NormalTok{)}
+\CommentTok{\# build the one{-}factor model }
+\NormalTok{model.rs }\OtherTok{\textless{}{-}} \StringTok{"RS =\textasciitilde{} RS1+RS2+RS3+RS4+RS5+RS6+RS7+RS8+RS9+RS10+RS11+RS12+RS13+RS14"}
+\CommentTok{\# run the multi{-}group CFA}
+\NormalTok{results.rs }\OtherTok{\textless{}{-}} \FunctionTok{mgcfa}\NormalTok{(}\AttributeTok{data =}\NormalTok{ DF, }
+                    \AttributeTok{group =} \StringTok{"sample"}\NormalTok{, }
+                    \AttributeTok{model =}\NormalTok{ model.rs)}
+\end{Highlighting}
+\end{Shaded}
+
+\normalsize
+
+\small
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\# how to get results in table }
+\NormalTok{results.rs}\SpecialCharTok{$}\NormalTok{model\_fit }\SpecialCharTok{\%\textgreater{}\%} 
+        \FunctionTok{select}\NormalTok{(model, AIC, BIC, cfi, tli, rmsea, srmr)}
+\end{Highlighting}
+\end{Shaded}
+
+\normalsize
 
@@
 
-\caption{\label{tab:tab1}Model Fit for Invariant Model}
+\caption{\label{tab:rs-table}Model Fit for RS-14 Example}
 
@@
 \midrule
-overall & 7,515.72 & 7,578.94 & 0.99 & 0.99 & 0.02 & 0.02\\
-group1 & 3,765.75 & 3,818.57 & 0.98 & 0.95 & 0.05 & 0.03\\
-group2 & 3,761.95 & 3,814.77 & 0.98 & 0.96 & 0.04 & 0.03\\
-configural & 7,527.70 & 7,654.14 & 0.98 & 0.96 & 0.04 & 0.03\\
-metric & 7,529.39 & 7,638.97 & 0.95 & 0.93 & 0.06 & 0.05\\
-scalar & 7,522.90 & 7,615.62 & 0.96 & 0.96 & 0.04 & 0.05\\
-strict & 7,519.51 & 7,591.16 & 0.96 & 0.96 & 0.04 & 0.06\\
+Overall & 126,722.49 & 126,888.71 & 0.93 & 0.92 & 0.09 & 0.04\\
+Group 1 & 52,961.42 & 53,099.72 & 0.92 & 0.90 & 0.09 & 0.04\\
+Group 2 & 69,100.98 & 69,254.31 & 0.93 & 0.92 & 0.11 & 0.04\\
+Configural & 122,118.41 & 122,617.06 & 0.93 & 0.91 & 0.10 & 0.04\\
+Metric & 122,144.53 & 122,566.01 & 0.92 & 0.92 & 0.10 & 0.04\\
+Scalar & 122,544.11 & 122,888.42 & 0.91 & 0.91 & 0.10 & 0.05\\
+Strict & 126,466.24 & 126,727.44 & 0.78 & 0.79 & 0.16 & 0.09\\
 \bottomrule
@@
 
+Table \ref{fig:invariant-pic} indicates the results after running the one-factor model. There are several guidelines for assessing assessing a degradation in model fit (\textbf{cheung?})
+
+\#\#write out partial codes
+partial\_syntax \textless- paste(colnames(DF){[}1:14{]}, ``\textasciitilde1'') \#all columns again
+partial\_syntax
+
+CFI\_list \textless- 1:length(partial\_syntax)
+names(CFI\_list) \textless- partial\_syntax
+
+for (i in 1:length(partial\_syntax))\{
+
+temp \textless- cfa(model = model.rs,
+data = DF,
+meanstructure = TRUE,
+group = ``sample'',
+group.equal = c(``loadings'', ``intercepts''),
+group.partial = partial\_syntax{[}i{]})
+
+CFI\_list{[}i{]} \textless- fitmeasures(temp, ``cfi'')
+\}
+
+CFI\_list
+
+partial.rs \textless- cfa(model = model.rs,
+data = DF,
+meanstructure = TRUE,
+group = ``sample'',
+meanstructure = T,
+group.equal = c(``loadings'', ``intercepts''),
+group.partial = c(``RS7\textasciitilde1'')
+)
+
+tidy(partial.rs)
+glance(partial.rs)
+results.rs\$model\_fit
+
+partial.rs.2 \textless- cfa(model = model.rs,
+data = DF,
+meanstructure = TRUE,
+group = ``sample'',
+meanstructure = T,
+group.equal = c(``loadings'', ``intercepts''),
+group.partial = c(``RS7\textasciitilde1'', ``RS6\textasciitilde1'')
+)
+
+tidy(partial.rs.2)
+glance(partial.rs.2)
+
+partial.rs.2.strict \textless- cfa(model = model.rs,
+data = DF,
+meanstructure = TRUE,
+group = ``sample'',
+meanstructure = T,
+group.equal = c(``loadings'', ``intercepts'', ``residuals''),
+group.partial = c(``RS7\textasciitilde1'', ``RS6\textasciitilde1'')
+)
+
+tidy(partial.rs.2.strict)
+glance(partial.rs.2.strict)
+
+model.rs.picture \textless- ``RS =\textasciitilde{} RS1+RS2+RS3+RS4+RS5+RS6+RS7+RS8+RS9+RS10+RS11+RS12+RS13+RS14
+RS\textasciitilde1
+RS1\textasciitilde0*1''
+
+partial.rs.2.picture \textless- cfa(model = model.rs,
+data = DF,
+meanstructure = TRUE,
+group = ``sample'',
+meanstructure = T,
+group.equal = c(``loadings'', ``intercepts''),
+group.partial = c(``RS7\textasciitilde1'', ``RS6\textasciitilde1''))
+
+partial.coef \textless- tidy(partial.rs.2.picture) \%\textgreater\%
+mutate(model = ``intercepts'')
+
+plot\_mgcfa(
+data\_coef = partial.coef,
+model\_step = ``intercepts'',
+item\_name = ``RS6'',
+x\_limits = c(-2,2),
+y\_limits = c(min(DF\(RS7), max(DF\)RS7)),
+model\_results = partial.rs.2.picture,
+ci\_level = .95,
+lv\_name = ``RS''
+)
+
+plot\_mgcfa(
+data\_coef = partial.coef,
+model\_step = ``intercepts'',
+item\_name = ``RS7'',
+x\_limits = c(-2,2),
+y\_limits = c(min(DF\(RS7), max(DF\)RS7)),
+model\_results = partial.rs.2.picture,
+ci\_level = .95,
+lv\_name = ``RS''
+)
+
+SD \textless- tapply(DF\(RS6, DF\)sample, sd)
+M \textless- tapply(DF\(RS6, DF\)sample, mean)
+N \textless- tapply(DF\(RS6, DF\)sample, length)
+
+SD2 \textless- tapply(DF\(RS7, DF\)sample, sd)
+M2 \textless- tapply(DF\(RS7, DF\)sample, mean)
+N2 \textless- tapply(DF\(RS7, DF\)sample, length)
+
+library(MOTE)
+d.ind.t(M{[}1{]}, M{[}2{]}, SD{[}1{]}, SD{[}2{]}, N{[}1{]}, N{[}2{]})
+d.ind.t(M2{[}1{]}, M2{[}2{]}, SD2{[}1{]}, SD2{[}2{]}, N2{[}1{]}, N2{[}2{]})
+lavaan\_dmacs(partial.rs.2.picture, ``Clinical'')
+lavaan\_dmacs(results.rs\$model.configural, ``Clinical'')
+
+\begin{verbatim}
+
+6: Drive
+
+7: Perseverance
+
+I1tems for the RS–14 are described in the measure’s manual (Wagnild, 2009a)
+and can be viewed at www.resiliencecenter.com.
+
+# Discussion
+
+Conclusions:
+
+-   framework for submitted/interpreting reports
+
+\newpage
+
+# References
+
+::: {#refs custom-style="Bibliography"}
+:::
+
+\newpage
+
+# Appendix
+
+## Model Fit Statistics
+
+Model fit statistics are provided for each of the ten model combinations (invariant, three sizes for each ladings, intercepts, and residuals).
+These tables could be used to examine the traditional change in fit statistics cutoff rules of thumb [@cheung2002], such as $\Delta$ CFI or $\Delta$ RMSEA, to the visualizations presented in the manuscript.
+
 \begin{table}[tbp]
@@
 
-\caption{\label{tab:tab2}Model Fit for Small Differences in Loadings}
+\caption{\label{tab:tab1}Model Fit for Invariant Model}
 
@@
 \midrule
-overall & 7,537.67 & 7,600.89 & 0.98 & 0.96 & 0.04 & 0.02\\
-group1 & 3,765.75 & 3,818.57 & 0.98 & 0.95 & 0.05 & 0.03\\
-group2 & 3,777.83 & 3,830.66 & 0.98 & 0.96 & 0.05 & 0.03\\
-configural & 7,543.58 & 7,670.02 & 0.98 & 0.95 & 0.05 & 0.03\\
-metric & 7,548.90 & 7,658.48 & 0.94 & 0.92 & 0.07 & 0.06\\
-scalar & 7,541.81 & 7,634.53 & 0.95 & 0.95 & 0.05 & 0.06\\
-strict & 7,541.66 & 7,613.31 & 0.93 & 0.94 & 0.05 & 0.07\\
+Overall & 7,515.72 & 7,578.94 & 0.99 & 0.99 & 0.02 & 0.02\\
+Group 1 & 3,765.75 & 3,818.57 & 0.98 & 0.95 & 0.05 & 0.03\\
+Group 2 & 3,761.95 & 3,814.77 & 0.98 & 0.96 & 0.04 & 0.03\\
+Configural & 7,527.70 & 7,654.14 & 0.98 & 0.96 & 0.04 & 0.03\\
+Metric & 7,529.39 & 7,638.97 & 0.95 & 0.93 & 0.06 & 0.05\\
+Scalar & 7,522.90 & 7,615.62 & 0.96 & 0.96 & 0.04 & 0.05\\
+Strict & 7,519.51 & 7,591.16 & 0.96 & 0.96 & 0.04 & 0.06\\
 \bottomrule
@@
 
-\caption{\label{tab:tab3}Model Fit for Medium Differences in Loadings}
+\caption{\label{tab:tab2}Model Fit for Small Differences in Loadings}
 
@@
 \midrule
-overall & 7,554.55 & 7,617.77 & 0.97 & 0.94 & 0.05 & 0.03\\
-group1 & 3,765.75 & 3,818.57 & 0.98 & 0.95 & 0.05 & 0.03\\
-group2 & 3,784.92 & 3,837.74 & 1.00 & 1.00 & 0.02 & 0.02\\
-configural & 7,550.67 & 7,677.11 & 0.99 & 0.98 & 0.04 & 0.03\\
-metric & 7,562.71 & 7,672.29 & 0.93 & 0.89 & 0.07 & 0.06\\
-scalar & 7,556.86 & 7,649.58 & 0.93 & 0.93 & 0.06 & 0.06\\
-strict & 7,558.05 & 7,629.70 & 0.91 & 0.92 & 0.06 & 0.08\\
+Overall & 7,537.67 & 7,600.89 & 0.98 & 0.96 & 0.04 & 0.02\\
+Group 1 & 3,765.75 & 3,818.57 & 0.98 & 0.95 & 0.05 & 0.03\\
+Group 2 & 3,777.83 & 3,830.66 & 0.98 & 0.96 & 0.05 & 0.03\\
+Configural & 7,543.58 & 7,670.02 & 0.98 & 0.95 & 0.05 & 0.03\\
+Metric & 7,548.90 & 7,658.48 & 0.94 & 0.92 & 0.07 & 0.06\\
+Scalar & 7,541.81 & 7,634.53 & 0.95 & 0.95 & 0.05 & 0.06\\
+Strict & 7,541.66 & 7,613.31 & 0.93 & 0.94 & 0.05 & 0.07\\
 \bottomrule
@@
 
-\caption{\label{tab:tab4}Model Fit for Large Differences in Loadings}
+\caption{\label{tab:tab3}Model Fit for Medium Differences in Loadings}
 
@@
 \midrule
-overall & 7,662.99 & 7,726.21 & 0.98 & 0.97 & 0.04 & 0.02\\
-group1 & 3,765.75 & 3,818.57 & 0.98 & 0.95 & 0.05 & 0.03\\
-group2 & 3,857.21 & 3,910.03 & 0.97 & 0.94 & 0.08 & 0.03\\
-configural & 7,622.96 & 7,749.40 & 0.97 & 0.94 & 0.06 & 0.03\\
-metric & 7,659.19 & 7,768.77 & 0.85 & 0.79 & 0.12 & 0.08\\
-scalar & 7,652.60 & 7,745.32 & 0.86 & 0.85 & 0.10 & 0.09\\
-strict & 7,660.63 & 7,732.27 & 0.82 & 0.85 & 0.10 & 0.12\\
+Overall & 7,554.55 & 7,617.77 & 0.97 & 0.94 & 0.05 & 0.03\\
+Group 1 & 3,765.75 & 3,818.57 & 0.98 & 0.95 & 0.05 & 0.03\\
+Group 2 & 3,784.92 & 3,837.74 & 1.00 & 1.00 & 0.02 & 0.02\\
+Configural & 7,550.67 & 7,677.11 & 0.99 & 0.98 & 0.04 & 0.03\\
+Metric & 7,562.71 & 7,672.29 & 0.93 & 0.89 & 0.07 & 0.06\\
+Scalar & 7,556.86 & 7,649.58 & 0.93 & 0.93 & 0.06 & 0.06\\
+Strict & 7,558.05 & 7,629.70 & 0.91 & 0.92 & 0.06 & 0.08\\
 \bottomrule
@@
 
-\caption{\label{tab:tab5}Model Fit for Small Differences in Intercepts}
+\caption{\label{tab:tab4}Model Fit for Large Differences in Loadings}
 
@@
 \midrule
-overall & 7,519.69 & 7,582.91 & 1.00 & 0.99 & 0.02 & 0.02\\
-group1 & 3,765.75 & 3,818.57 & 0.98 & 0.95 & 0.05 & 0.03\\
-group2 & 3,770.41 & 3,823.23 & 0.93 & 0.86 & 0.08 & 0.04\\
-configural & 7,536.16 & 7,662.60 & 0.95 & 0.91 & 0.07 & 0.04\\
-metric & 7,531.36 & 7,640.94 & 0.96 & 0.94 & 0.05 & 0.04\\
-scalar & 7,531.34 & 7,624.06 & 0.94 & 0.93 & 0.06 & 0.05\\
-strict & 7,523.54 & 7,595.18 & 0.95 & 0.96 & 0.04 & 0.05\\
+Overall & 7,662.99 & 7,726.21 & 0.98 & 0.97 & 0.04 & 0.02\\
+Group 1 & 3,765.75 & 3,818.57 & 0.98 & 0.95 & 0.05 & 0.03\\
+Group 2 & 3,857.21 & 3,910.03 & 0.97 & 0.94 & 0.08 & 0.03\\
+Configural & 7,622.96 & 7,749.40 & 0.97 & 0.94 & 0.06 & 0.03\\
+Metric & 7,659.19 & 7,768.77 & 0.85 & 0.79 & 0.12 & 0.08\\
+Scalar & 7,652.60 & 7,745.32 & 0.86 & 0.85 & 0.10 & 0.09\\
+Strict & 7,660.63 & 7,732.27 & 0.82 & 0.85 & 0.10 & 0.12\\
 \bottomrule
@@
 
-\caption{\label{tab:tab6}Model Fit for Medium Differences in Intercepts}
+\caption{\label{tab:tab5}Model Fit for Small Differences in Intercepts}
 
@@
 \midrule
-overall & 7,542.77 & 7,605.99 & 1.00 & 1.00 & 0.01 & 0.02\\
-group1 & 3,765.75 & 3,818.57 & 0.98 & 0.95 & 0.05 & 0.03\\
-group2 & 3,770.41 & 3,823.23 & 0.93 & 0.86 & 0.08 & 0.04\\
-configural & 7,536.16 & 7,662.60 & 0.95 & 0.91 & 0.07 & 0.04\\
-metric & 7,531.36 & 7,640.94 & 0.96 & 0.94 & 0.05 & 0.04\\
-scalar & 7,554.20 & 7,646.92 & 0.85 & 0.83 & 0.09 & 0.07\\
-strict & 7,546.38 & 7,618.03 & 0.86 & 0.88 & 0.08 & 0.07\\
+Overall & 7,519.69 & 7,582.91 & 1.00 & 0.99 & 0.02 & 0.02\\
+Group 1 & 3,765.75 & 3,818.57 & 0.98 & 0.95 & 0.05 & 0.03\\
+Group 2 & 3,770.41 & 3,823.23 & 0.93 & 0.86 & 0.08 & 0.04\\
+Configural & 7,536.16 & 7,662.60 & 0.95 & 0.91 & 0.07 & 0.04\\
+Metric & 7,531.36 & 7,640.94 & 0.96 & 0.94 & 0.05 & 0.04\\
+Scalar & 7,531.34 & 7,624.06 & 0.94 & 0.93 & 0.06 & 0.05\\
+Strict & 7,523.54 & 7,595.18 & 0.95 & 0.96 & 0.04 & 0.05\\
 \bottomrule
@@
 
-\caption{\label{tab:tab7}Model Fit for Large Differences in Intercepts}
+\caption{\label{tab:tab6}Model Fit for Medium Differences in Intercepts}
 
@@
 \midrule
-overall & 7,579.17 & 7,642.39 & 1.00 & 1.00 & 0.00 & 0.02\\
-group1 & 3,765.75 & 3,818.57 & 0.98 & 0.95 & 0.05 & 0.03\\
-group2 & 3,770.41 & 3,823.23 & 0.93 & 0.86 & 0.08 & 0.04\\
-configural & 7,536.16 & 7,662.60 & 0.95 & 0.91 & 0.07 & 0.04\\
-metric & 7,531.36 & 7,640.94 & 0.96 & 0.94 & 0.05 & 0.04\\
-scalar & 7,590.29 & 7,683.01 & 0.70 & 0.66 & 0.13 & 0.10\\
-strict & 7,582.47 & 7,654.12 & 0.71 & 0.75 & 0.11 & 0.10\\
+Overall & 7,542.77 & 7,605.99 & 1.00 & 1.00 & 0.01 & 0.02\\
+Group 1 & 3,765.75 & 3,818.57 & 0.98 & 0.95 & 0.05 & 0.03\\
+Group 2 & 3,770.41 & 3,823.23 & 0.93 & 0.86 & 0.08 & 0.04\\
+Configural & 7,536.16 & 7,662.60 & 0.95 & 0.91 & 0.07 & 0.04\\
+Metric & 7,531.36 & 7,640.94 & 0.96 & 0.94 & 0.05 & 0.04\\
+Scalar & 7,554.20 & 7,646.92 & 0.85 & 0.83 & 0.09 & 0.07\\
+Strict & 7,546.38 & 7,618.03 & 0.86 & 0.88 & 0.08 & 0.07\\
 \bottomrule
@@
 
-\caption{\label{tab:tab8}Model Fit for Small Differences in Residuals}
+\caption{\label{tab:tab7}Model Fit for Large Differences in Intercepts}
 
@@
 \midrule
-overall & 7,449.49 & 7,512.71 & 1.00 & 1.01 & 0.00 & 0.01\\
-group1 & 3,765.75 & 3,818.57 & 0.98 & 0.95 & 0.05 & 0.03\\
-group2 & 3,693.32 & 3,746.14 & 1.00 & 1.01 & 0.00 & 0.02\\
-configural & 7,459.07 & 7,585.51 & 0.99 & 0.98 & 0.03 & 0.03\\
-metric & 7,461.41 & 7,570.99 & 0.97 & 0.95 & 0.05 & 0.05\\
-scalar & 7,455.85 & 7,548.58 & 0.97 & 0.97 & 0.04 & 0.05\\
-strict & 7,453.48 & 7,525.12 & 0.96 & 0.97 & 0.04 & 0.05\\
+Overall & 7,579.17 & 7,642.39 & 1.00 & 1.00 & 0.00 & 0.02\\
+Group 1 & 3,765.75 & 3,818.57 & 0.98 & 0.95 & 0.05 & 0.03\\
+Group 2 & 3,770.41 & 3,823.23 & 0.93 & 0.86 & 0.08 & 0.04\\
+Configural & 7,536.16 & 7,662.60 & 0.95 & 0.91 & 0.07 & 0.04\\
+Metric & 7,531.36 & 7,640.94 & 0.96 & 0.94 & 0.05 & 0.04\\
+Scalar & 7,590.29 & 7,683.01 & 0.70 & 0.66 & 0.13 & 0.10\\
+Strict & 7,582.47 & 7,654.12 & 0.71 & 0.75 & 0.11 & 0.10\\
 \bottomrule
@@
 
-\caption{\label{tab:tab9}Model Fit for Medium Differences in Residuals}
+\caption{\label{tab:tab8}Model Fit for Small Differences in Residuals}
 
@@
 \midrule
-overall & 7,378.57 & 7,441.79 & 1.00 & 1.00 & 0.00 & 0.02\\
-group1 & 3,765.75 & 3,818.57 & 0.98 & 0.95 & 0.05 & 0.03\\
-group2 & 3,597.77 & 3,650.60 & 1.00 & 1.03 & 0.00 & 0.02\\
-configural & 7,363.52 & 7,489.96 & 1.00 & 0.99 & 0.02 & 0.02\\
-metric & 7,366.63 & 7,476.21 & 0.97 & 0.96 & 0.05 & 0.05\\
-scalar & 7,360.15 & 7,452.87 & 0.98 & 0.98 & 0.03 & 0.05\\
-strict & 7,382.53 & 7,454.18 & 0.88 & 0.90 & 0.08 & 0.07\\
+Overall & 7,449.49 & 7,512.71 & 1.00 & 1.01 & 0.00 & 0.01\\
+Group 1 & 3,765.75 & 3,818.57 & 0.98 & 0.95 & 0.05 & 0.03\\
+Group 2 & 3,693.32 & 3,746.14 & 1.00 & 1.01 & 0.00 & 0.02\\
+Configural & 7,459.07 & 7,585.51 & 0.99 & 0.98 & 0.03 & 0.03\\
+Metric & 7,461.41 & 7,570.99 & 0.97 & 0.95 & 0.05 & 0.05\\
+Scalar & 7,455.85 & 7,548.58 & 0.97 & 0.97 & 0.04 & 0.05\\
+Strict & 7,453.48 & 7,525.12 & 0.96 & 0.97 & 0.04 & 0.05\\
 \bottomrule
@@
 
-\caption{\label{tab:tab10}Model Fit for Large Differences in Residuals}
+\caption{\label{tab:tab9}Model Fit for Medium Differences in Residuals}
 
@@
 \midrule
-overall & 7,294.21 & 7,357.43 & 1.00 & 1.01 & 0.00 & 0.01\\
-group1 & 3,765.75 & 3,818.57 & 0.98 & 0.95 & 0.05 & 0.03\\
-group2 & 3,453.47 & 3,506.29 & 0.95 & 0.90 & 0.07 & 0.03\\
-configural & 7,219.22 & 7,345.66 & 0.96 & 0.92 & 0.06 & 0.03\\
-metric & 7,216.38 & 7,325.96 & 0.96 & 0.94 & 0.05 & 0.04\\
-scalar & 7,210.65 & 7,303.37 & 0.96 & 0.96 & 0.04 & 0.05\\
-strict & 7,297.89 & 7,369.54 & 0.59 & 0.65 & 0.13 & 0.18\\
+Overall & 7,378.57 & 7,441.79 & 1.00 & 1.00 & 0.00 & 0.02\\
+Group 1 & 3,765.75 & 3,818.57 & 0.98 & 0.95 & 0.05 & 0.03\\
+Group 2 & 3,597.77 & 3,650.60 & 1.00 & 1.03 & 0.00 & 0.02\\
+Configural & 7,363.52 & 7,489.96 & 1.00 & 0.99 & 0.02 & 0.02\\
+Metric & 7,366.63 & 7,476.21 & 0.97 & 0.96 & 0.05 & 0.05\\
+Scalar & 7,360.15 & 7,452.87 & 0.98 & 0.98 & 0.03 & 0.05\\
+Strict & 7,382.53 & 7,454.18 & 0.88 & 0.90 & 0.08 & 0.07\\
 \bottomrule
@@
 
-\hypertarget{mgcfa-convenience-function}{%
-\subsection{MGCFA Convenience Function}\label{mgcfa-convenience-function}}
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:tab10}Model Fit for Large Differences in Residuals}
+
+\begin{tabular}{lllllll}
+\toprule
+Model & AIC & BIC & CFI & TLI & RMSEA & SRMR\\
+\midrule
+Overall & 7,294.21 & 7,357.43 & 1.00 & 1.01 & 0.00 & 0.01\\
+Group 1 & 3,765.75 & 3,818.57 & 0.98 & 0.95 & 0.05 & 0.03\\
+Group 2 & 3,453.47 & 3,506.29 & 0.95 & 0.90 & 0.07 & 0.03\\
+Configural & 7,219.22 & 7,345.66 & 0.96 & 0.92 & 0.06 & 0.03\\
+Metric & 7,216.38 & 7,325.96 & 0.96 & 0.94 & 0.05 & 0.04\\
+Scalar & 7,210.65 & 7,303.37 & 0.96 & 0.96 & 0.04 & 0.05\\
+Strict & 7,297.89 & 7,369.54 & 0.59 & 0.65 & 0.13 & 0.18\\
+\bottomrule
+\end{tabular}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+## MGCFA Convenience Function
 
@@
 
-\begin{Shaded}
-\begin{Highlighting}[]
-\FunctionTok{library}\NormalTok{(lavaan)}
-\FunctionTok{library}\NormalTok{(dplyr)}
-\FunctionTok{library}\NormalTok{(broom)}
-\CommentTok{\# CFA function}
-\NormalTok{mgcfa }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(data, group, model)\{}
-
-\NormalTok{  group\_names }\OtherTok{\textless{}{-}} \FunctionTok{unique}\NormalTok{(data[ , group])}
-
-\NormalTok{  model.overall }\OtherTok{\textless{}{-}} \FunctionTok{cfa}\NormalTok{(}\AttributeTok{model =}\NormalTok{ model, }\AttributeTok{data =}\NormalTok{ data)}
-\NormalTok{  model.group1 }\OtherTok{\textless{}{-}} \FunctionTok{cfa}\NormalTok{(}\AttributeTok{model =}\NormalTok{ model, }
-                      \AttributeTok{data =} \FunctionTok{subset}\NormalTok{(data, group }\SpecialCharTok{==}\NormalTok{ group\_names[}\DecValTok{1}\NormalTok{]))}
-\NormalTok{  model.group2 }\OtherTok{\textless{}{-}} \FunctionTok{cfa}\NormalTok{(}\AttributeTok{model =}\NormalTok{ model, }
-                      \AttributeTok{data =} \FunctionTok{subset}\NormalTok{(data, group }\SpecialCharTok{==}\NormalTok{ group\_names[}\DecValTok{2}\NormalTok{]))}
-\NormalTok{  model.configural }\OtherTok{\textless{}{-}} \FunctionTok{cfa}\NormalTok{(}\AttributeTok{model =}\NormalTok{ model, }\AttributeTok{data =}\NormalTok{ data, }
-                          \AttributeTok{group =}\NormalTok{ group, }\AttributeTok{meanstructure =}\NormalTok{ T)}
-\NormalTok{  model.metric }\OtherTok{\textless{}{-}} \FunctionTok{cfa}\NormalTok{(}\AttributeTok{model =}\NormalTok{ model, }\AttributeTok{data =}\NormalTok{ data, }
-                      \AttributeTok{group =}\NormalTok{ group, }\AttributeTok{meanstructure =}\NormalTok{ T,}
-                      \AttributeTok{group.equal =} \StringTok{"loadings"}\NormalTok{)}
-\NormalTok{  model.scalar }\OtherTok{\textless{}{-}} \FunctionTok{cfa}\NormalTok{(}\AttributeTok{model =}\NormalTok{ model, }\AttributeTok{data =}\NormalTok{ data, }
-                      \AttributeTok{group =}\NormalTok{ group, }\AttributeTok{meanstructure =}\NormalTok{ T, }
-                      \AttributeTok{group.equal =} \FunctionTok{c}\NormalTok{(}\StringTok{"loadings"}\NormalTok{, }\StringTok{"intercepts"}\NormalTok{))}
-\NormalTok{  model.strict }\OtherTok{\textless{}{-}} \FunctionTok{cfa}\NormalTok{(}\AttributeTok{model =}\NormalTok{ model, }\AttributeTok{data =}\NormalTok{ data, }
-                      \AttributeTok{group =}\NormalTok{ group, }\AttributeTok{meanstructure =}\NormalTok{ T, }
-                      \AttributeTok{group.equal =}  \FunctionTok{c}\NormalTok{(}\StringTok{"loadings"}\NormalTok{, }\StringTok{"intercepts"}\NormalTok{, }\StringTok{"residuals"}\NormalTok{))}
-
-\NormalTok{  model\_coef }\OtherTok{\textless{}{-}} \FunctionTok{bind\_rows}\NormalTok{(}
-    \FunctionTok{tidy}\NormalTok{(model.overall, }\AttributeTok{conf.level =}\NormalTok{ .}\DecValTok{95}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
-      \FunctionTok{mutate}\NormalTok{(}\AttributeTok{model =} \StringTok{"overall"}\NormalTok{), }
-    \FunctionTok{tidy}\NormalTok{(model.group1, }\AttributeTok{conf.level =}\NormalTok{ .}\DecValTok{95}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
-      \FunctionTok{mutate}\NormalTok{(}\AttributeTok{model =} \StringTok{"group1"}\NormalTok{), }
-    \FunctionTok{tidy}\NormalTok{(model.group2, }\AttributeTok{conf.level =}\NormalTok{ .}\DecValTok{95}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
-      \FunctionTok{mutate}\NormalTok{(}\AttributeTok{model =} \StringTok{"group2"}\NormalTok{), }
-    \FunctionTok{tidy}\NormalTok{(model.configural, }\AttributeTok{conf.level =}\NormalTok{ .}\DecValTok{95}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
-      \FunctionTok{mutate}\NormalTok{(}\AttributeTok{model =} \StringTok{"configural"}\NormalTok{), }
-    \FunctionTok{tidy}\NormalTok{(model.metric, }\AttributeTok{conf.level =}\NormalTok{ .}\DecValTok{95}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
-      \FunctionTok{mutate}\NormalTok{(}\AttributeTok{model =} \StringTok{"metric"}\NormalTok{), }
-    \FunctionTok{tidy}\NormalTok{(model.scalar, }\AttributeTok{conf.level =}\NormalTok{ .}\DecValTok{95}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
-      \FunctionTok{mutate}\NormalTok{(}\AttributeTok{model =} \StringTok{"scalar"}\NormalTok{), }
-    \FunctionTok{tidy}\NormalTok{(model.strict, }\AttributeTok{conf.level =}\NormalTok{ .}\DecValTok{95}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
-      \FunctionTok{mutate}\NormalTok{(}\AttributeTok{model =} \StringTok{"strict"}\NormalTok{)}
-\NormalTok{  )}
-
-\NormalTok{  model\_fit }\OtherTok{\textless{}{-}} \FunctionTok{bind\_rows}\NormalTok{(}
-    \FunctionTok{glance}\NormalTok{(model.overall) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{mutate}\NormalTok{(}\AttributeTok{model =} \StringTok{"overall"}\NormalTok{), }
-    \FunctionTok{glance}\NormalTok{(model.group1) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{mutate}\NormalTok{(}\AttributeTok{model =} \StringTok{"group1"}\NormalTok{), }
-    \FunctionTok{glance}\NormalTok{(model.group2) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{mutate}\NormalTok{(}\AttributeTok{model =} \StringTok{"group2"}\NormalTok{), }
-    \FunctionTok{glance}\NormalTok{(model.configural) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{mutate}\NormalTok{(}\AttributeTok{model =} \StringTok{"configural"}\NormalTok{), }
-    \FunctionTok{glance}\NormalTok{(model.metric) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{mutate}\NormalTok{(}\AttributeTok{model =} \StringTok{"metric"}\NormalTok{), }
-    \FunctionTok{glance}\NormalTok{(model.scalar) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{mutate}\NormalTok{(}\AttributeTok{model =} \StringTok{"scalar"}\NormalTok{), }
-    \FunctionTok{glance}\NormalTok{(model.strict) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{mutate}\NormalTok{(}\AttributeTok{model =} \StringTok{"strict"}\NormalTok{)}
-\NormalTok{    )}
-
-  \FunctionTok{return}\NormalTok{(}\FunctionTok{list}\NormalTok{(}
-    \StringTok{"model\_coef"} \OtherTok{=}\NormalTok{ model\_coef,}
-    \StringTok{"model\_fit"} \OtherTok{=}\NormalTok{ model\_fit,}
-    \StringTok{"model.overall"} \OtherTok{=}\NormalTok{ model.overall,}
-    \StringTok{"model.group1"} \OtherTok{=}\NormalTok{ model.group1,}
-    \StringTok{"model.group2"} \OtherTok{=}\NormalTok{ model.group2,}
-    \StringTok{"model.configural"} \OtherTok{=}\NormalTok{ model.configural,}
-    \StringTok{"model.metric"} \OtherTok{=}\NormalTok{ model.metric,}
-    \StringTok{"model.scalar"} \OtherTok{=}\NormalTok{ model.scalar,}
-    \StringTok{"model.strict"} \OtherTok{=}\NormalTok{ model.strict}
-\NormalTok{  ))}
-
-\NormalTok{\}}
-\end{Highlighting}
-\end{Shaded}
+```r
+library(lavaan)
+library(dplyr)
+library(broom)
+# CFA function
+mgcfa <- function(data, group, model){
+
+  group_names <- unique(data[ , group])
+  data$group <- data[ , group]
+
+  model.overall <- cfa(model = model, data = data)
+  model.group1 <- cfa(model = model, 
+                      data = subset(data, group == group_names[1]))
+  model.group2 <- cfa(model = model, 
+                      data = subset(data, group == group_names[2]))
+  model.configural <- cfa(model = model, data = data, 
+                          group = group, meanstructure = T)
+  model.metric <- cfa(model = model, data = data, 
+                      group = group, meanstructure = T,
+                      group.equal = "loadings")
+  model.scalar <- cfa(model = model, data = data, 
+                      group = group, meanstructure = T, 
+                      group.equal = c("loadings", "intercepts"))
+  model.strict <- cfa(model = model, data = data, 
+                      group = group, meanstructure = T, 
+                      group.equal =  c("loadings", "intercepts", "residuals"))
+
+  model_coef <- bind_rows(
+    tidy(model.overall, conf.level = .95) %>% 
+      mutate(model = "Overall"), 
+    tidy(model.group1, conf.level = .95) %>% 
+      mutate(model = "Group 1"), 
+    tidy(model.group2, conf.level = .95) %>% 
+      mutate(model = "Group 2"), 
+    tidy(model.configural, conf.level = .95) %>% 
+      mutate(model = "Configural"), 
+    tidy(model.metric, conf.level = .95) %>% 
+      mutate(model = "Metric"), 
+    tidy(model.scalar, conf.level = .95) %>% 
+      mutate(model = "Scalar"), 
+    tidy(model.strict, conf.level = .95) %>% 
+      mutate(model = "Strict")
+  )
+
+  model_fit <- bind_rows(
+    glance(model.overall) %>% mutate(model = "Overall"), 
+    glance(model.group1) %>% mutate(model = "Group 1"), 
+    glance(model.group2) %>% mutate(model = "Group 2"), 
+    glance(model.configural) %>% mutate(model = "Configural"), 
+    glance(model.metric) %>% mutate(model = "Metric"), 
+    glance(model.scalar) %>% mutate(model = "Scalar"), 
+    glance(model.strict) %>% mutate(model = "Strict")
+    )
+
+  return(list(
+    "model_coef" = model_coef,
+    "model_fit" = model_fit,
+    "model.overall" = model.overall,
+    "model.group1" = model.group1,
+    "model.group2" = model.group2,
+    "model.configural" = model.configural,
+    "model.metric" = model.metric,
+    "model.scalar" = model.scalar,
+    "model.strict" = model.strict
+  ))
+
+}
+\end{verbatim}
 
@@
 
+  \CommentTok{\# get group variable}
+\NormalTok{  group\_var }\OtherTok{\textless{}{-}}\NormalTok{ model\_results}\SpecialCharTok{@}\NormalTok{Data}\SpecialCharTok{@}\NormalTok{group}
+\NormalTok{  group\_labels }\OtherTok{\textless{}{-}}\NormalTok{ model\_results}\SpecialCharTok{@}\NormalTok{Data}\SpecialCharTok{@}\NormalTok{group.label}
+
   \CommentTok{\# first get the data}
@@
   \FunctionTok{filter}\NormalTok{(}\FunctionTok{grepl}\NormalTok{(item\_name, term)) }\SpecialCharTok{\%\textgreater{}\%}  \CommentTok{\# pick a question}
-  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{group =} \FunctionTok{factor}\NormalTok{(group, }\AttributeTok{levels =} \FunctionTok{names}\NormalTok{(}\FunctionTok{table}\NormalTok{(data\_coef}\SpecialCharTok{$}\NormalTok{group)), }
-                        \AttributeTok{labels =} \FunctionTok{c}\NormalTok{(}\StringTok{"Group 1"}\NormalTok{, }\StringTok{"Group 2"}\NormalTok{))) }
+  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{group =} \FunctionTok{factor}\NormalTok{(group, }\AttributeTok{levels =} \FunctionTok{names}\NormalTok{(}\FunctionTok{table}\NormalTok{(data\_coef}\SpecialCharTok{$}\NormalTok{group)), }\AttributeTok{labels =}\NormalTok{ group\_labels)) }
 
@@
 \NormalTok{  latent\_means}\SpecialCharTok{$}\NormalTok{lv }\OtherTok{\textless{}{-}}\NormalTok{ latent\_means[ , lv\_name]}
+\NormalTok{  latent\_means}\SpecialCharTok{$}\NormalTok{group }\OtherTok{\textless{}{-}}\NormalTok{ latent\_means[ , group\_var]}
 
@@
     \FunctionTok{ylab}\NormalTok{(}\StringTok{"Density"}\NormalTok{) }\SpecialCharTok{+} 
-    \FunctionTok{geom\_vline}\NormalTok{(}\AttributeTok{data =}\NormalTok{ latent\_means }\SpecialCharTok{\%\textgreater{}\%}
-                 \FunctionTok{group\_by}\NormalTok{(group) }\SpecialCharTok{\%\textgreater{}\%} 
-                 \FunctionTok{summarize}\NormalTok{(}\AttributeTok{mean =} \FunctionTok{mean}\NormalTok{(lv)), }
+    \FunctionTok{geom\_vline}\NormalTok{(}\AttributeTok{data =}\NormalTok{ latent\_means }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{group\_by}\NormalTok{(group) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{summarize}\NormalTok{(}\AttributeTok{mean =} \FunctionTok{mean}\NormalTok{(lv)), }
                \FunctionTok{aes}\NormalTok{(}\AttributeTok{xintercept =}\NormalTok{ mean, }\AttributeTok{color =}\NormalTok{ group)) }\SpecialCharTok{+} 
@@
                         \AttributeTok{xmin =}\NormalTok{ .}\DecValTok{25}\NormalTok{, }\AttributeTok{xmax =} \DecValTok{1}\NormalTok{, }
-                        \AttributeTok{ymin =}\NormalTok{ y\_limits[}\DecValTok{1}\NormalTok{], }
-                        \AttributeTok{ymax =}\NormalTok{ y\_limits[}\DecValTok{2}\NormalTok{]}\SpecialCharTok{{-}}\NormalTok{y\_range}\SpecialCharTok{/}\FloatTok{1.8}\NormalTok{),}
+                        \AttributeTok{ymin =}\NormalTok{ y\_limits[}\DecValTok{1}\NormalTok{], }\AttributeTok{ymax =}\NormalTok{ y\_limits[}\DecValTok{2}\NormalTok{]}\SpecialCharTok{{-}}\NormalTok{y\_range}\SpecialCharTok{/}\FloatTok{1.8}\NormalTok{),}
 \NormalTok{    mean\_plot }\SpecialCharTok{+} 
@@
 
+\hypertarget{refs}{}
+\begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-aiena2014}{}}%
+Aiena, B.
+J., Baczwaski, B.
+J., Schulenberg, S.
+E., \& Buchanan, E.
+M.
+(2014).
+Measuring Resilience With the RS{\textendash}14: A Tale of Two Samples.
+\emph{Journal of Personality Assessment}, \emph{97}(3), 291--300.
+\url{https://doi.org/10.1080/00223891.2014.951445}
+
+\leavevmode\vadjust pre{\hypertarget{ref-akaike1998}{}}%
+Akaike, H.
+(1998).
+\emph{Information theory and an extension of the maximum likelihood principle} (E.
+Parzen, K.
+Tanabe, \& G.
+Kitagawa, Eds.).
+New York, NY: Springer New York.
+Retrieved from \url{http://link.springer.com/10.1007/978-1-4612-1694-0_15}
+
+\leavevmode\vadjust pre{\hypertarget{ref-anvari2021}{}}%
+Anvari, F., \& Lakens, D.
+(2021).
+Using anchor-based methods to determine the smallest effect size of interest.
+\emph{Journal of Experimental Social Psychology}, \emph{96}, 104159.
+\url{https://doi.org/10.1016/j.jesp.2021.104159}
+
+\leavevmode\vadjust pre{\hypertarget{ref-barry2014}{}}%
+Barry, A.
+E., Chaney, B., Piazza-Gardner, A.
+K., \& Chavarria, E.
+A.
+(2014).
+Validity and Reliability Reporting Practices in the Field of Health Education and Behavior: A Review of Seven Journals.
+\emph{Health Education \& Behavior}, \emph{41}(1), 12--18.
+\url{https://doi.org/10.1177/1090198113483139}
+
+\leavevmode\vadjust pre{\hypertarget{ref-beaujean2014}{}}%
+Beaujean, A. A. (2014). \emph{Latent variable modeling using r: A step by step guide}. New York: Routledge/Taylor \& Francis Group.
+
+\leavevmode\vadjust pre{\hypertarget{ref-bentler1990}{}}%
+Bentler, P. M. (1990). Comparative fit indexes in structural models. \emph{Psychological Bulletin}, \emph{107}(2), 238--246. \url{https://doi.org/10.1037/0033-2909.107.2.238}
+
+\leavevmode\vadjust pre{\hypertarget{ref-bentler1995}{}}%
+Bentler, P. M. (1995). \emph{EQS structural equations program manual}. Encino, CA.
+
+\leavevmode\vadjust pre{\hypertarget{ref-boker2011}{}}%
+Boker, S., Neale, M., Maes, H., Wilde, M., Spiegel, M., Brick, T., \ldots{} Fox, J.
+(2011).
+OpenMx: An Open Source Extended Structural Equation Modeling Framework.
+\emph{Psychometrika}, \emph{76}(2), 306--317.
+\url{https://doi.org/10.1007/s11336-010-9200-6}
+
+\leavevmode\vadjust pre{\hypertarget{ref-brown2015}{}}%
+Brown, T. A. (2015). \emph{Confirmatory factor analysis for applied research} (Second edition). New York ; London: The Guilford Press.
+
+\leavevmode\vadjust pre{\hypertarget{ref-byrne2001}{}}%
+Byrne, B.
+M.
+(2001).
+Structural Equation Modeling With AMOS, EQS, and LISREL: Comparative Approaches to Testing for the Factorial Validity of a Measuring Instrument.
+\emph{International Journal of Testing}, \emph{1}(1), 55--86.
+\url{https://doi.org/10.1207/S15327574IJT0101_4}
+
+\leavevmode\vadjust pre{\hypertarget{ref-byrne1989}{}}%
+Byrne, B.
+M., Shavelson, R.
+J., \& Muthén, B.
+(1989).
+Testing for the equivalence of factor covariance and mean structures: The issue of partial measurement invariance.
+\emph{Psychological Bulletin}, \emph{105}(3), 456--466.
+\url{https://doi.org/10.1037/0033-2909.105.3.456}
+
+\leavevmode\vadjust pre{\hypertarget{ref-cheung2002}{}}%
+Cheung, G.
+W., \& Rensvold, R.
+B.
+(2002).
+Evaluating Goodness-of-Fit Indexes for Testing Measurement Invariance.
+\emph{Structural Equation Modeling: A Multidisciplinary Journal}, \emph{9}(2), 233--255.
+\url{https://doi.org/10.1207/s15328007sem0902_5}
+
+\leavevmode\vadjust pre{\hypertarget{ref-chorpita2000}{}}%
+Chorpita, B.
+F., Yim, L., Moffitt, C., Umemoto, L.
+A., \& Francis, S.
+E.
+(2000).
+Assessment of symptoms of DSM-IV anxiety and depression in children: a revised child anxiety and depression scale.
+\emph{Behaviour Research and Therapy}, \emph{38}(8), 835--855.
+\url{https://doi.org/10.1016/S0005-7967(99)00130-8}
+
+\leavevmode\vadjust pre{\hypertarget{ref-cohen2003}{}}%
+Cohen, J., Cohen, P., West, S. G., \& Aiken, L. (2003). \emph{Applied multiple regression / correlation analysis for the behavioral sciences} (3rd ed.). Lawrence Erlbaum Associates.
+
+\leavevmode\vadjust pre{\hypertarget{ref-devellis2022}{}}%
+DeVellis, R. F., \& Thorpe, C. T. (2022). \emph{Scale development: Theory and applications} (Fifth edition). Thousand Oaks, California: SAGE Publications, Inc.
+
+\leavevmode\vadjust pre{\hypertarget{ref-dueber2023}{}}%
+Dueber, D. (2023). \emph{Dmacs}. Retrieved from \url{https://github.com/ddueber/dmacs}
+
+\leavevmode\vadjust pre{\hypertarget{ref-flake2020}{}}%
+Flake, J.
+K., \& Fried, E.
+I.
+(2020).
+Measurement Schmeasurement: Questionable Measurement Practices and How to Avoid Them.
+\emph{Advances in Methods and Practices in Psychological Science}, \emph{3}(4), 456--465.
+\url{https://doi.org/10.1177/2515245920952393}
+
+\leavevmode\vadjust pre{\hypertarget{ref-juxf6reskog1971}{}}%
+Jöreskog, K. G. (1971). Simultaneous factor analysis in several populations. \emph{Psychometrika}, \emph{36}(4), 409--426. \url{https://doi.org/10.1007/BF02291366}
+
+\leavevmode\vadjust pre{\hypertarget{ref-juxf6reskog2001}{}}%
+Jöreskog, Karl G., \& Sörbom, D. (2001). \emph{LISREL 8: user's reference guide} (2. ed., updated to LISREL 8). Lincolnwood, Ill: SSI Scientific Software Internat.
+
+\leavevmode\vadjust pre{\hypertarget{ref-kline2016}{}}%
+Kline, R. B. (2016). \emph{Principles and practice of structural equation modeling} (Fourth edition). New York: The Guilford Press.
+
+\leavevmode\vadjust pre{\hypertarget{ref-lakens2017}{}}%
+Lakens, D. (2017). Equivalence Tests. \emph{Social Psychological and Personality Science}, \emph{8}(4), 355--362. \url{https://doi.org/10.1177/1948550617697177}
+
+\leavevmode\vadjust pre{\hypertarget{ref-makel2014}{}}%
+Makel, M.
+C., \& Plucker, J.
+A.
+(2014).
+Facts Are More Important Than Novelty: Replication in the Education Sciences.
+\emph{Educational Researcher}, \emph{43}(6), 304--316.
+\url{https://doi.org/10.3102/0013189X14545513}
+
+\leavevmode\vadjust pre{\hypertarget{ref-makel2012}{}}%
+Makel, M.
+C., Plucker, J.
+A., \& Hegarty, B.
+(2012).
+Replications in Psychology Research: How Often Do They Really Occur?
+\emph{Perspectives on Psychological Science}, \emph{7}(6), 537--542.
+\url{https://doi.org/10.1177/1745691612460688}
+
+\leavevmode\vadjust pre{\hypertarget{ref-marsh2004}{}}%
+Marsh, H.
+W., Hau, K.-T., \& Wen, Z.
+(2004).
+In search of golden rules: Comment on hypothesis-testing approaches to setting cutoff values for fit indexes and dangers in overgeneralizing hu and bentler's (1999) findings.
+\emph{Structural Equation Modeling: A Multidisciplinary Journal}, \emph{11}(3), 320--341.
+\url{https://doi.org/10.1207/s15328007sem1103_2}
+
+\leavevmode\vadjust pre{\hypertarget{ref-meade2008}{}}%
+Meade, A.
+W., Johnson, E.
+C., \& Braddy, P.
+W.
+(2008).
+Power and sensitivity of alternative fit indices in tests of measurement invariance.
+\emph{Journal of Applied Psychology}, \emph{93}(3), 568--592.
+\url{https://doi.org/10.1037/0021-9010.93.3.568}
+
+\leavevmode\vadjust pre{\hypertarget{ref-meredith1993}{}}%
+Meredith, W. (1993). Measurement invariance, factor analysis and factorial invariance. \emph{Psychometrika}, \emph{58}(4), 525--543. \url{https://doi.org/10.1007/BF02294825}
+
+\leavevmode\vadjust pre{\hypertarget{ref-nelson2018}{}}%
+Nelson, L. D., Simmons, J., \& Simonsohn, U. (2018). Psychology's renaissance. \emph{Annual Review of Psychology}, \emph{69}(1), 511--534. \url{https://doi.org/10.1146/annurev-psych-122216-011836}
+
+\leavevmode\vadjust pre{\hypertarget{ref-nye2019}{}}%
+Nye, C.
+D., Bradburn, J., Olenick, J., Bialko, C., \& Drasgow, F.
+(2019).
+How Big Are My Effects?
+Examining the Magnitude of Effect Sizes in Studies of Measurement Equivalence.
+\emph{Organizational Research Methods}, \emph{22}(3), 678--709.
+\url{https://doi.org/10.1177/1094428118761122}
+
+\leavevmode\vadjust pre{\hypertarget{ref-nye2011}{}}%
+Nye, C.
+D., \& Drasgow, F.
+(2011).
+Effect size indices for analyses of measurement equivalence: Understanding the practical importance of differences between groups.
+\emph{Journal of Applied Psychology}, \emph{96}(5), 966--980.
+\url{https://doi.org/10.1037/a0022955}
+
+\leavevmode\vadjust pre{\hypertarget{ref-putnick2016}{}}%
+Putnick, D.
+L., \& Bornstein, M.
+H.
+(2016).
+Measurement invariance conventions and reporting: The state of the art and future directions for psychological research.
+\emph{Developmental Review}, \emph{41}, 71--90.
+\url{https://doi.org/10.1016/j.dr.2016.06.004}
+
+\leavevmode\vadjust pre{\hypertarget{ref-rosseel2012}{}}%
+Rosseel, Y. (2012). Lavaan: An r package for structural equation modeling. \emph{Journal of Statistical Software}, \emph{48}(1), 1--36. \url{https://doi.org/10.18637/jss.v048.i02}
+
+\leavevmode\vadjust pre{\hypertarget{ref-schwarz1978}{}}%
+Schwarz, G. (1978). Estimating the dimension of a model. \emph{The Annals of Statistics}, \emph{6}(2), 461--464. Retrieved from \url{https://www.jstor.org/stable/2958889}
+
+\leavevmode\vadjust pre{\hypertarget{ref-shadish2001}{}}%
+Shadish, W. R., Cook, T. D., \& Campbell, D. T. (2001). \emph{Experimental and quasi-experimental designs for generalized causal inference}. Boston: Houghton Mifflin.
+
+\leavevmode\vadjust pre{\hypertarget{ref-suxf6rbom1978}{}}%
+Sörbom, D. (1978). An alternative to the methodology for analysis of covariance. \emph{Psychometrika}, \emph{43}(3), 381--396. \url{https://doi.org/10.1007/BF02293647}
+
+\leavevmode\vadjust pre{\hypertarget{ref-stark2006}{}}%
+Stark, S., Chernyshenko, O.
+S., \& Drasgow, F.
+(2006).
+Detecting differential item functioning with confirmatory factor analysis and item response theory: Toward a unified strategy.
+\emph{Journal of Applied Psychology}, \emph{91}(6), 1292--1306.
+\url{https://doi.org/10.1037/0021-9010.91.6.1292}
+
+\leavevmode\vadjust pre{\hypertarget{ref-steiger1990}{}}%
+Steiger, J.
+H.
+(1990).
+Structural model evaluation and modification: An interval estimation approach.
+\emph{Multivariate Behavioral Research}, \emph{25}(2), 173--180.
+\url{https://doi.org/10.1207/s15327906mbr2502_4}
+
+\leavevmode\vadjust pre{\hypertarget{ref-tay2015}{}}%
+Tay, L., Meade, A.
+W., \& Cao, M.
+(2015).
+An Overview and Practical Guide to IRT Measurement Equivalence Analysis.
+\emph{Organizational Research Methods}, \emph{18}(1), 3--46.
+\url{https://doi.org/10.1177/1094428114553062}
+
+\leavevmode\vadjust pre{\hypertarget{ref-thompson1996}{}}%
+Thompson, B., \& Daniel, L.
+G.
+(1996).
+Factor Analytic Evidence for the Construct Validity of Scores: A Historical Overview and Some Guidelines.
+\emph{Educational and Psychological Measurement}, \emph{56}(2), 197--208.
+\url{https://doi.org/10.1177/0013164496056002001}
+
+\leavevmode\vadjust pre{\hypertarget{ref-trent2013}{}}%
+Trent, L.
+R., Buchanan, E., Ebesutani, C., Ale, C.
+M., Heiden, L., Hight, T.
+L., \ldots{} Young, J.
+(2013).
+A measurement invariance examination of the revised child anxiety and depression scale in a southern sample: Differential item functioning between african american and caucasian youth.
+\emph{Assessment}, \emph{20}(2), 175--187.
+\url{https://doi.org/10.1177/1073191112450907}
+
+\leavevmode\vadjust pre{\hypertarget{ref-tucker1973}{}}%
+Tucker, L. R., \& Lewis, C. (1973). A reliability coefficient for maximum likelihood factor analysis. \emph{Psychometrika}, \emph{38}(1), 1--10. \url{https://doi.org/10.1007/BF02291170}
+
+\leavevmode\vadjust pre{\hypertarget{ref-vandeschoot2015}{}}%
+Van De Schoot, R., Schmidt, P., De Beuckelaer, A., Lek, K., \& Zondervan-Zwijnenburg, M.
+(2015).
+Editorial: Measurement invariance.
+\emph{Frontiers in Psychology}, \emph{6}.
+Retrieved from \url{https://www.frontiersin.org/articles/10.3389/fpsyg.2015.01064}
+
+\leavevmode\vadjust pre{\hypertarget{ref-vazire2022}{}}%
+Vazire, S., Schiavone, S.
+R., \& Bottesini, J.
+G.
+(2022).
+Credibility Beyond Replicability: Improving the Four Validities in Psychological Science.
+\emph{Current Directions in Psychological Science}, \emph{31}(2), 162--168.
+\url{https://doi.org/10.1177/09637214211067779}
+
+\leavevmode\vadjust pre{\hypertarget{ref-wagnild2009}{}}%
+Wagnild, G. (2009). A review of the resilience scale. \emph{Journal of Nursing Measurement}, \emph{17}(2), 105--113. \url{https://doi.org/10.1891/1061-3749.17.2.105}
+
+\leavevmode\vadjust pre{\hypertarget{ref-weidman2017}{}}%
+Weidman, A.
+C., Steckler, C.
+M., \& Tracy, J.
+L.
+(2017).
+The jingle and jangle of emotion assessment: Imprecise measurement, casual scale usage, and conceptual fuzziness in emotion research.
+\emph{Emotion}, \emph{17}(2), 267--295.
+\url{https://doi.org/10.1037/emo0000226}
+
+\leavevmode\vadjust pre{\hypertarget{ref-zwaan2018}{}}%
+Zwaan, R. A., Etz, A., Lucas, R. E., \& Donnellan, M. B. (2018). Making replication mainstream. \emph{Behavioral and Brain Sciences}, \emph{41}, e120. \url{https://doi.org/10.1017/S0140525X17001972}
+
+\end{CSLReferences}
+
 \end{document}

### 2023-03-31 manuscript.Rmd
almost there

@@
     email         : "ebuchanan@harrisburgu.edu"
-    role: # Contributorship roles (e.g., CRediT, https://credit.niso.org/)
-      - "Conceptualization"
-      - "Writing - Original Draft Preparation"
-      - "Writing - Review & Editing"
 
@@
   Latent variable modeling as a lens for psychometric theory is a popular tool for social scientists to examine measurement of constructs [@beaujean2014].
-Journals such as *Assessment* regularly publish articles supporting new or previously established measures of latent constructs (e.g., depression, anxiety) wherein a measurement model is established for the scale in question.
-These measurement models designate the relationship between the measured, observed variables, and the underlying construct, with the assumption that these relations hold in many samples.
+Journals such as *Assessment* regularly publish articles supporting measures of latent constructs wherein a measurement model is established.
 Confirmatory factor analysis can be used to investigate the replicability and generalizability of the measurement model in new samples, while multi-group confirmatory factor analysis is used to examine the measurement model across groups within samples [@brown2015].
 With the rise of the replication crisis and "psychology's renaissance" [@nelson2018], interest in divergence in measurement has increased, often focused on small parameter differences within the latent model.
-While the statistical procedure for examining measurement invariance is moderately well established, it is clear that the toolkit for inspecting these results is lacking.
-This manuscript will outline ways to visualize potential non-invariance, to supplement large numbers of tables that often overwhelm a reader within these published reports.
-Further, given these visualizations, readers will learn how to interpret the impact and size of the proposed non-invariance in models.
+This manuscript outlines ways to visualize potential non-invariance, to supplement large numbers of tables that often overwhelm a reader within these published reports.
+Readers will learn how to interpret the impact and size of the proposed non-invariance in models.
 While it is tempting to suggest that problems with replication and generalizability are simply issues with measurement, it is crucial to remember that all models have variability and error, even those models estimating the differences between item functioning, such as multi-group confirmatory factor analysis.
-This manuscript will help provide a framework for researchers interested in registered reports in this area.
 
@@
 classoption       : "man"
+bibliography: references.bib
+
+header-includes:
+  - |
+    \makeatletter
+    \renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
+      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+      {-1em}%
+      {\normalfont\normalsize\bfseries\typesectitle}}
+
+    \renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
+      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+      {-\z@\relax}%
+      {\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
+    \makeatother
+
+csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
+documentclass     : "apa7"
 output            : papaja::apa6_pdf
-bibliography: references.bib
 ---
@@
 
-  model.overall <- cfa(model = model, data = data)
-  model.group1 <- cfa(model = model, data = subset(data, group == group_names[1]))
-  model.group2 <- cfa(model = model, data = subset(data, group == group_names[2]))
-  model.configural <- cfa(model = model, data = data, group = group, meanstructure = T)
+  model.overall <- cfa(model = model, data = data, 
+                       meanstructure = T)
+  model.group1 <- cfa(model = model, 
+                      data = subset(data, group == group_names[1]),
+                      meanstructure = T)
+  model.group2 <- cfa(model = model, 
+                      data = subset(data, group == group_names[2]),
+                      meanstructure = T)
+  model.configural <- cfa(model = model, data = data, 
+                          group = group, meanstructure = T)
   model.metric <- cfa(model = model, data = data, 
@@
   filter(grepl(item_name, term)) %>%  # pick a question
-  mutate(group = factor(group, levels = names(table(data_coef$group)), labels = group_labels))
+  mutate(group = factor(group, levels = names(table(data_coef$group)), 
+                        labels = group_labels))
 
@@
 
-  # get the lengend
+  # get the legend
   legend_b <- get_legend(
@@
 Instead, we use surveys and questionnaires to indirectly assess the underlying construct [@devellis2022].
-Latent variable modeling (i.e., structural equation modeling) is a popular tool for the validation of developed survey instruments to verify scale dimensionalality, structure, and model fit.
+Latent variable modeling (i.e., structural equation modeling) is a popular tool for the validation of developed survey instruments to verify scale dimensionality, structure, and model fit.
 A simple search for scale development reveals thousands of articles in psychology that examine new and previously published work, thus, illustrating the interest in both measurement and the use of validation techniques.
-Unfortunately, except in specialty journals, much of the validity evidence and/or development for measures used in empirical studies is not reported within the journal article [@barry2014, @weidman2017].
+Unfortunately, except in specialty journals, much of the validity evidence and/or development for measures used in empirical studies is not reported within the journal article [@barry2014; @weidman2017].
 Without this information, it is difficult to interpret individual study conclusions, as validity information allows for judgment of usefulness of the measured values [@flake2020].
-Further, the current focus on replication [@makel2012, @makel2014, @zwaan2018], reproducibility [@nelson2018], and the credibility of our results [@vazire2022] has demonstrated questionable measurement practices - decisions that researchers make like survey selection and scoring that impact the results of the study [@flake2020].
+Further, the current focus on replication [@makel2012; @makel2014; @zwaan2018], reproducibility [@nelson2018], and the credibility of our results [@vazire2022] has demonstrated questionable measurement practices - decisions that researchers make like survey selection and scoring that impact the results of the study [@flake2020].
 Transparent reporting of the use and creation of scales can improve both interpretation and reproducibility when using surveys developed to measure latent constructs [@shadish2001].
@@
 This comparison of sub-populations is the test of measurement invariance [@meredith1993].
-Invariance or equivalence implies that the scale operates in the same fashion for each sub-group, and thus, differences in the final latent variable scores can interpretated as differences in populations.
+Invariance or equivalence implies that the scale operates in the same fashion for each sub-group, and thus, differences in the final latent variable scores can interpreted as differences in populations.
 Non-invariance suggests that individuals respond or interpret items differently, and thus, differences in scores may represent different scores on the latent variable in the population or differences in measurement.
@@
 
-Measurement invariance is typically analyzed using confirmatory factor analysis, specifically, multi-group confirmatory factor analysis (MGCFA) or less often, with item response theory [@stark2006, @tay2015].
+Measurement invariance is typically analyzed using confirmatory factor analysis, specifically, multi-group confirmatory factor analysis (MGCFA) or less often, with item response theory [@stark2006; @tay2015].
 First, the model is examined with the factor structure proposed for the latent and observed variables, and then often these models are assessed for each group separately.
-The two models are then combined together into one nested CFA in order to determine configural invariance [@brown2015, @byrne2001, @kline2016].
+The two models are then combined together into one nested CFA in order to determine configural invariance [@brown2015; @byrne2001; @kline2016].
 Configural invariance tests if the proposed factor structure is the same between groups.
@@
 
-These concepts have been explored and implemented for the last fifty years [@jöreskog1971, @sörbom1978] and implemented in the most popular structural equation modeling programs [@jöreskog2001, @rosseel2012, @boker2011].
+These concepts have been explored and implemented for the last fifty years [@jöreskog1971; @sörbom1978] and implemented in the most popular structural equation modeling programs [@jöreskog2001; @rosseel2012; @boker2011].
 @byrne1989 extended the ideas of multi-group testing by suggesting partial invariance [followed by @meredith1993].
@@
 To determine when non-invariance and partial invariance occurred, each model is sequentially compared to the previous model using some form of a difference test.
-Traditionally, since models were nested, a chi-square difference test was used [@meade2008, @cheung2002]; however, given the known issues with chi-square [@thompson1996], people have favored empirical cutoffs for differences in fit indices.
-As the field pushes back against favoring cutoff criteria and rules of thumb [@marsh2004, @putnick2016], an effect size measure for translating "how much" non-invariance was developed $d_{MACS}$ [@nye2011].
+Traditionally, since models were nested, a chi-square difference test was used [@meade2008; @cheung2002]; however, given the known issues with chi-square [@thompson1996], people have favored empirical cutoffs for differences in fit indices.
+As the field pushes back against favoring cutoff criteria and rules of thumb [@marsh2004; @putnick2016], an effect size measure for translating "how much" non-invariance was developed $d_{MACS}$ [@nye2011].
 This effect size examines the differences in observed variables between the two groups for both the factor loading and the item intercept; thus, any differences in either or both will increase the effect size for non-invariance [@stark2006].
@@
 Given that this information is generally ignored during the examination of measurement invariance, it may be that we are claiming that many scales are non-invariant, when in reality, the differences between loadings or item intercepts are small and unimportant.
-$d_{MACS}$ provides the opportunity to begin to think about the smallest effect size of interest or the smallest meaningful effect size [@lakens2017, @anvari2021].
+$d_{MACS}$ provides the opportunity to begin to think about the smallest effect size of interest or the smallest meaningful effect size [@lakens2017; @anvari2021].
 As mentioned, $d_{MACS}$ has only really been explored for a combined intercept and loadings, and while useful, does not necessarily allow a researcher to pinpoint specific issues within an observed variable.
@@
 By creating panel visualizations, we can supplement a researchers ability to judge the strength of the non-invariance differences and effect size for each item.
-Coupled with other indicators (i.e., fit indice differences, $d_{MACS}$), we can move toward a better understanding of how much measurement non-invariance is meaningful.
-
-By the end of this manuscript, readers will:
+Coupled with other indicators (i.e., fit indices differences, $d_{MACS}$), we can move toward a better understanding of how much measurement non-invariance is meaningful.
+
+By the end of this tutorial manuscript, readers will:
 
@@
 
-Data was simulated using the `simulateData` function in the *R* package `lavaan` [@rosseel2012] assuming multivariate normality using a $\mu$ of 0 and $\sigma$ of 1 for the data.
-This function allows you to write `lavaan` syntax for your model with estimated values to generate data for observed variables.
-The data included two groups of individuals ("Group 1", "Group 2") for a multi-group confirmatory factor analysis (\$n\_{group}\$ = 250, *N* = 500).
+Data was simulated using the `simulateData` function in the *R* package *lavaan* [@rosseel2012] assuming multivariate normality using a $\mu$ of 0 and $\sigma$ of 1 for the data.
+This function allows you to write *lavaan* syntax for your model with estimated values to generate data for observed variables.
+The data included two groups of individuals ("Group 1", "Group 2") for a multi-group confirmatory factor analysis ($n_{group}$ = 250, *N* = 500).
 The latent variables were assumed to be continuous normal.
@@
 The metric model constrained the factor loadings of each group to be equal within the model.
-The scalar model then constrained the item intercepts (i.e., item mean) to be equal across groups.
+The scalar model then constrained the item intercepts (i.e., item means) to be equal across groups.
 Finally, the strict model constrained the item variances (i.e., error variances) to be equal for each item across groups.
@@
 Fit indices for the steps for multi-group models are presented in the appendix for comparison of cutoff rules of thumb [@cheung2002] to effect sizes and visualizations presented in this manuscript.
-Fit indices include Akaike Information Criterion [AIC, @akaike1998], Bayesian Information Criterion [BIC, @schwarz1978], Comparative Fit Index [CFI, @bentler1990], Tucker Lewis Index [TLI, @tucker1973], root mean squared error of approximation RMSEA [@steiger1990], and standardized root mean squar residual [SRMR, @bentler1995].
+Fit indices include Akaike Information Criterion [AIC, @akaike1998], Bayesian Information Criterion [BIC, @schwarz1978], Comparative Fit Index [CFI, @bentler1990], Tucker Lewis Index [TLI, @tucker1973], root mean squared error of approximation RMSEA [@steiger1990], and standardized root mean square residual [SRMR, @bentler1995].
 
@@
 While $d_{MACS}$ is used primarily for an effect size of the (non)-invariance for intercepts and loadings together, a similar approach was taken for the estimation of small, medium, and large effects on the residuals.
-The effect size is presented for all models, calculated from the *dmacs* package [@dueber2023, @nye2011].
+The effect size is presented for all models, calculated from the *dmacs* package [@dueber2023; @nye2011].
 Only one item in each model was manipulated from the invariant model to create the non-invariant models.
@@
 The complete code for this manuscript can be found at <https://osf.io/wev5f/>, and the function code for the convenience function for multi-group models and plots is found in the appendix.
-First, we would create our model code in `lavaan` syntax.
-The `lv` latent variable predicts the five measured variables, which are present as columns in our `df.invariant` dataset.
-You would include the dataframe in the `data` argument of our function, the name of the grouping variable in quotes for `group`, and the `lavaan` model syntax in the `model` argument.
+This tutorial was registered at <https://osf.io/vwf4d>, and the example provided at the end of the manuscript was added after that registration.
+First, we would create our model code in *lavaan* syntax [@rosseel2012].
+The `lv` latent variable predicts the five measured variables, which are present as columns in our `df.invariant` data set.
+You would include the dataframe in the `data` argument of our function, the name of the grouping variable in quotes for `group`, and the *lavaan* model syntax in the `model` argument.
 The `mgcfa` function code runs an overall model with all data, regardless of group, each group separately on the model, then the steps described above: configural, metric, scalar, and strict invariance.
 
-`lavaan` automatically sets the mean (i.e., the intercept) for latent variables to zero.
+*lavaan* automatically sets the mean (i.e., the intercept) for latent variables to zero.
 If we wish to visualize the impact of the changes in parameter estimates across groups on the latent means, we need to allow the latent mean estimation with `lv ~ 1`.
@@
 
-1)  `model_coef`: a tidy dataframe with *all* model's coefficients saved from the `lavaan` outputs.
+1)  `model_coef`: a tidy dataframe with *all* model's coefficients saved from the *lavaan* outputs.
 Note that we can see that the intercept `~1` is set for question 1 but freely estimated for the latent variable.
@@
 
-2)  `model_fit`: a tidy dataframe with *all* model's fit indices saved from the `lavaan` outputs.
+2)  `model_fit`: a tidy dataframe with *all* model's fit indices saved from the *lavaan* outputs.
 
@@
 
-3)  Saved `lavaan` fitted objects that you can use the `summary()`, `parameterEstimates()`, `fitIndices()`, etc.
+3)  Saved *lavaan* fitted objects that you can use the `summary()`, `parameterEstimates()`, `fitIndices()`, etc.
 on.
@@
 1)  `data_coef`: A tidy dataframe of the parameter estimates from the models.
-This function assumes you have used `broom::tidy()` on the saved model from `lavaan` and added a column called "model" with the name of the model step.
+This function assumes you have used `broom::tidy()` on the saved model from *lavaan* and added a column called "model" with the name of the model step [@robinson2023].
 This function will only run for models that have used the grouping function (i.e., configural, metric, scalar, and strict or other combinations/steps you wish to examine).
@@
 
-4)  `x_limits`: What do you want the x-axits limits to be for your invariance plot?
+4)  `x_limits`: What do you want the x-axis limits to be for your invariance plot?
 The default option is to assume the latent variable is standardized, and therefore, -1 to 1 is recommended.
@@
 
-5)  `y_limits`: What do you want the y-axits limits to be for your invariance plot?
+5)  `y_limits`: What do you want the y-axis limits to be for your invariance plot?
 Given that the latent variable is used to predict the observed values in the data, you could use the minimum and maximum values found in the data.
@@
 
-7)  `model_results`: In this argument, include the saved `lavaan` output for the model listed in the `model_step` argument.
-
-8)  `lv_name`: Include the name of the latent variable, exactly how it is listed in your `lavaan` syntax.
+7)  `model_results`: In this argument, include the saved *lavaan* output for the model listed in the `model_step` argument.
+
+8)  `lv_name`: Include the name of the latent variable, exactly how it is listed in your *lavaan* syntax.
 You should plot the latent variable that the `item_name` is linked to.
@@
 All parameter estimates are plotted on the unstandardized estimates and their confidence interval based on the standard error of the estimate.
+All plots are made with *ggplot2* [@R-ggplot2] and *cowplot* [@wilke2020].
 
@@
 Finally, group labels are represented in the figure caption on the bottom.
-Group 1 is usually the group that is alphabetically first in the dataset or whichever group is the first that appears when using the `levels()` command.
+Group 1 is usually the group that is alphabetically first in the data set or whichever group is the first that appears when using the `levels()` command.
 
@@
 Figure \@ref(fig:small-load-pic) displays the results from the small ($d_{MACS}$ = `r apa_num(d_small_load)$DMACS[4]`) difference in loadings, while Figure \@ref(fig:med-load-pic) displays the results from the medium ($d_{MACS}$ = `r apa_num(d_med_load)$DMACS[4]`) difference in loadings, and Figure \@ref(fig:large-load-pic) shows the large ($d_{MACS}$ = `r apa_num(d_large_load)$DMACS[4]`) differences.
-When investigating the slope values, we can clearly see the change in the loading for the second group (the only manipulated variable, although random dataset generation may also change intercepts and residuals slightly).
+When investigating the slope values, we can clearly see the change in the loading for the second group (the only manipulated variable, although random data set generation may also change intercepts and residuals slightly).
 At the medium effect size, we see that the confidence bands do not overlap (at the edges), and at the large effect size, we can see a clear separation of two lines.
@@
 Intercept differences can be clearly seen represented by the spacing out of the intercept locations (and thus, the overall line as well).
-While the changes in intercept do not appear to change the latent means, the cavaet to this simulation is that only item four was manipulated.
+While the changes in intercept do not appear to change the latent means, the caveat to this simulation is that only item four was manipulated.
 An example is provided below that demonstrates large changes in latent means.
@@
 Last, the effect of the residuals is plotted in small (Figure \@ref(fig:small-res-pic)), medium (Figure \@ref(fig:med-res-pic)), and large (Figure \@ref(fig:large-res-pic)) formats.
-While $d_{MACS}$ values are not technically avaliable for the residuals, our models showed `r apa_num(d_small_res)$DMACS[4]`, `r apa_num(d_med_res)$DMACS[4]`, and `r apa_num(d_large_res)$DMACS[4]`, respectively.
-These differences in values are variable due to the random generation of datasets for each measurement invariance manipulation.
+While $d_{MACS}$ values are not technically available for the residuals, our models showed `r apa_num(d_small_res)$DMACS[4]`, `r apa_num(d_med_res)$DMACS[4]`, and `r apa_num(d_large_res)$DMACS[4]`, respectively.
+These differences in values are variable due to the random generation of data sets for each measurement invariance manipulation.
 At first glance, the differences in the small chart may seem large, because the black lines are not touching, but notice that the distributions overlap, indicating a likely small difference.
@@
 load("RS14.Rdata")
+
 # build the one-factor model 
@@
         select(model, AIC, BIC, cfi, tli, rmsea, srmr), 
+        digits = 3, 
         col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
@@
 
-Table \@ref(fig:invariant-pic) indicates the results after running the one-factor model. There are several guidelines for assessing assessing a degradation in model fit [@cheung]
-
-```{r}
-##write out partial codes
-partial_syntax <- paste(colnames(DF)[1:14], "~1") #all columns again 
+Table \@ref(fig:invariant-pic) indicates the results after running the one-factor model.
+There are several guidelines for assessing assessing a degradation in model fit [@cheung2002; @jin2020; @putnick2016; @counsell2020; @cao2022] but for the purposes of this illustration $\Delta$CFI \> .01 will be used.
+Table \@ref(fig:invariant-pic) indicates that fit was degraded when the constraint on equal item intercepts was added.
+The code below provides an example of testing each item individually by relaxing the constraints and recalculating the CFI.
+If these Items bring the CFI value back up to $\Delta$CFI \<= .01 from the metric model, then the model would be considering partially invariant at the scalar level.
+It seems unlikely that the residuals will show invariance, if partial scalar invariance can be found, as the drop in fit is quite large.
+
+```{r echo = T, include = T, size = "small"}
+# write out the partial invariance codes for intercepts ~1
+partial_syntax <- paste(colnames(DF)[1:14], "~1") 
 partial_syntax
-
+# create a place to save the CFIs for each item separately
 CFI_list  <- 1:length(partial_syntax)
 names(CFI_list) <- partial_syntax
-
+# loop over the items and calculate CFI 
+# with that item freely estimated
 for (i in 1:length(partial_syntax)){
@@
 }
-
+# look at the new CFIs
 CFI_list
-
+```
+
+The output indicates that RS6 and RS7 are potential items that could be relaxed to improve model fit and create a partial scalar invariant model.
+The code below show to check the addition of these items, which are added one at a time.
+You use the `group.partial` open to "relax" or freely estimate that parameter for each group separately.
+Once that model is saved, you can use the `tidy` function from *broom* to arrange the estimates from the model, which is used in our plotting function.
+The `glance` function will create a tidy dataframe of the fit indices for easy review.
+
+```{r echo = T, include = T, size = "small"}
+# run the partially invariant model with group.partial
 partial.rs <- cfa(model = model.rs, 
@@
                   group.equal = c("loadings", "intercepts"),
-                  group.partial = c("RS7~1")
-)
-
-tidy(partial.rs)
-glance(partial.rs)
-results.rs$model_fit
-
+                  group.partial = c("RS7~1"))
+
+# examine the loadings 
+tidy(partial.rs) %>% 
+  filter(term == "RS7 ~1 ") %>% 
+  select(term, group, estimate, std.error)
+# examine the fit indices 
+glance(partial.rs) %>% 
+  select(AIC, BIC, cfi, tli, rmsea, srmr)
+
+# effect size model 
+lavaan_dmacs(partial.rs, "Clinical")$DMACS[7]
+```
+
+By examining our estimates, we can see that item seven on the RS-14 is estimated at nearly 5 points for the clinical sample, while the student sample has a lower mean around 4.5 points.
+Generally, students show higher means on the items of the RS14, but when all loadings and other intercepts are constrained to be equal, and this one item is relaxed, this pattern flips so that clinical groups show higher item intercepts.
+Given the scale is a 1-7 Likert type scale, .5 a point represents a potentially sizable change on the scale.
+Item seven covers perseverance after hardship, and all items can be found in the user manual for the scale at www.resiliencecenter.com.
+The effect size from $d_{DMACS}$ suggests a small to medium effect, `r apa_num(lavaan_dmacs(partial.rs, "Clinical")$DMACS[7])`.
+In this next code section, we repeat this process for the RS6, as the CFI for our model with only RS7 does not achieve the levels of partial invariance for our $\Delta$CFI criterion (i.e., \<= .01 downward change in fit: metric CFI = `r apa_p(results.rs$model_fit$cfi[5])`, partial scalar CFI = `r apa_p(glance(partial.rs)$cfi)`).
+
+```{r echo = T, include = T, size = "small"}
+# add the second intercept
 partial.rs.2 <- cfa(model = model.rs, 
@@
                   group.equal = c("loadings", "intercepts"),
-                  group.partial = c("RS7~1", "RS6~1")
-)
-
-tidy(partial.rs.2)
-glance(partial.rs.2)
-
-partial.rs.2.strict <- cfa(model = model.rs, 
-                  data = DF, 
-                  meanstructure = TRUE,
-                  group = "sample", 
-                  meanstructure = T, 
-                  group.equal = c("loadings", "intercepts", "residuals"),
-                  group.partial = c("RS7~1", "RS6~1")
-)
-
-tidy(partial.rs.2.strict)
-glance(partial.rs.2.strict)
-
+                  group.partial = c("RS7~1", "RS6~1"))
+
+# examine the loadings 
+tidy(partial.rs.2) %>% 
+  filter(term == "RS6 ~1 ") %>% 
+  select(term, group, estimate, std.error)
+# examine the fit indices 
+glance(partial.rs.2) %>% 
+  select(AIC, BIC, cfi, tli, rmsea, srmr)
+# the effect size is 
+lavaan_dmacs(partial.rs.2, "Clinical")$DMACS[6]
+```
+
+Again, we see about a half-point difference between our clinical and student samples for item 6, which is about drive to achieve.
+The CFI for this model does meet the requirements for partial invariance, `r apa_p(glance(partial.rs.2)$cfi)`.
+The effect size is approximately the same at `r apa_num(lavaan_dmacs(partial.rs.2, "Clinical")$DMACS[6])`.
+Last, we can create our images to view the item non-invariance and the latent means in Figures \@ref(fig:rs6-img) and \@ref(fig:rs7-img).
+
+```{r echo = T, include = T, size = "small"}
+# rebuild the model by constraining item 1 intercept
+# allow the latent variable to be estimated
 model.rs.picture <- "RS =~ RS1+RS2+RS3+RS4+RS5+RS6+RS7+RS8+RS9+RS10+RS11+RS12+RS13+RS14
@@
 
+# rerun the partial invariance model 
 partial.rs.2.picture <- cfa(model = model.rs, 
@@
 
+# save the coefficients to use in our picture function 
 partial.coef <- tidy(partial.rs.2.picture) %>% 
-  mutate(model = "intercepts")
-
+  mutate(model = "Scalar")
+```
+
+```{r include = T, echo = T, results = "small", eval = F}
+# plot the image for RS6
 plot_mgcfa(
   data_coef = partial.coef,
-  model_step = "intercepts", 
+  model_step = "Scalar", 
   item_name = "RS6",
@@
 )
-
+```
+
+```{r rs6-img, echo = F, include = T, size = "small", fig.cap="RS6 Item Invariance Visualization"}
+# plot the image for RS6
 plot_mgcfa(
   data_coef = partial.coef,
-  model_step = "intercepts", 
+  model_step = "Scalar", 
+  item_name = "RS6",
+  x_limits = c(-2,2),
+  y_limits = c(min(DF$RS7), max(DF$RS7)),
+  model_results = partial.rs.2.picture, 
+  ci_level = .95,
+  lv_name = "RS"
+)
+```
+
+```{r include = T, echo = T, results = "small", eval = F}
+# plot the image for RS7
+plot_mgcfa(
+  data_coef = partial.coef,
+  model_step = "Scalar", 
   item_name = "RS7",
@@
 )
-
-SD <- tapply(DF$RS6, DF$sample, sd)
-M <- tapply(DF$RS6, DF$sample, mean)
-N <- tapply(DF$RS6, DF$sample, length)
-
-SD2 <- tapply(DF$RS7, DF$sample, sd)
-M2 <- tapply(DF$RS7, DF$sample, mean)
-N2 <- tapply(DF$RS7, DF$sample, length)
-
-library(MOTE)
-d.ind.t(M[1], M[2], SD[1], SD[2], N[1], N[2])
-d.ind.t(M2[1], M2[2], SD2[1], SD2[2], N2[1], N2[2])
-lavaan_dmacs(partial.rs.2.picture, "Clinical")
-lavaan_dmacs(results.rs$model.configural, "Clinical")
-```
-
-6: Drive
-
-7: Perseverance
-
-I1tems for the RS–14 are described in the measure’s manual (Wagnild, 2009a)
-and can be viewed at www.resiliencecenter.com.
-
-```{r echo = T, include = T, size = "small"}
-
-```
+```
+
+```{r rs7-img, echo = F, include = T, size = "small", fig.cap="RS7 Item Invariance Visualization"}
+# plot the image for RS7
+plot_mgcfa(
+  data_coef = partial.coef,
+  model_step = "Scalar", 
+  item_name = "RS7",
+  x_limits = c(-2,2),
+  y_limits = c(min(DF$RS7), max(DF$RS7)),
+  model_results = partial.rs.2.picture, 
+  ci_level = .95,
+  lv_name = "RS"
+)
+```
+
+The latent mean is calculated "separately" for each group, insomuch as the first group is considered the comparison group, while the second is the difference between groups, like how dummy coded variables in regression are examined.
+Here we see a difference of `r apa_num(partial.coef %>% filter(term == "RS ~1 ") %>% slice_tail() %>% pull(estimate))`, and students show a higher resiliency score.
+However, when all other things are held equivalent, the intercepts on items 6 and 7 show higher scores for clinical populations.
+Additionally, we may see an indication in our student population of a bimodal distribution that may be related to this effect.
 
@@
 
-Conclusions:
-
--   framework for submitted/interpreting reports
+In this tutorial, we examined how to use multiple tools to examine measurement invariance.
+Model fit comparisons and statistics can be paired with newly developed effect size measures, and finally a visualization to examine individual items and the overall latent mean scores.
+This visualization was designed with common graphing elements that researchers often use to display those statistics - intercepts were graphed on the intercept line, slopes were represented as lines of fit, and error terms were represented as distributions.
+Each component can impact the overall model and the eventual latent mean scores, as shown in the simulations holding all other things equal.
+Using real data, the effect of two non-invariant item intercepts was examined and visualized.
+How should one interpret the "discrepancy" between the results (these effect visually appear large) from effect sizes (.30 was proposed as small to medium in @nye2019)?
+
+Effect sizes are notoriously difficult to interpret, which is why we love guidelines, even if @cohen1990 declared we probably shouldn't use his suggestions.
+Others have begun to discuss the importance of focusing on effects in the scale of the data and their practical importance [@cumming2012; @anvari2021].
+Our interpretation may be that the difference between groups is large, as a `r apa_num(partial.coef %>% filter(term == "RS ~1 ") %>% slice_tail() %>% pull(estimate))` change on a 7 point scale is approximately 10% more resiliency for students when compared to the clinical sample.
+Practically, 10% in resiliency for an area of the United States (Mississippi) often hit with natural disasters (hurricanes, tornadoes, floods) and high levels of poverty would be very important.
+Even the smaller difference of .5 point on each individual item could translate into increases in resiliency, and these results may elucidate avenues for further exploration into areas of focus within resiliency, given the items.
+
+What do the results of a study on measurement invariance with these results tell us about replication, generalizability, and validity?
+If a researcher decides their effects are large, they should likely caution against suggesting that these scores are directly comparable without weighting or other adjustment.
+Let's consider a scenario wherein the change metric between models picked (i.e., $\Delta$CFI, $\Delta$RMSEA) indicates a "significant" change in model fit.
+However, if both the effect size and a visual inspection of the invariance indicates a small difference, we may decide to lessen the practical importance of those results, much like "just significant" *p*-values with small effect sizes are treated now.
+Given that the goal of measurement invariance is to compare *estimates*, we should expect some differences across samples due to the nature of sampling and estimation.
+It may be that many of the published models presented represent these effects - small variations between groups due to sampling error or other small crud - but do not represent a fundamental problem with the measurement or generalizability of the results.
 
@@
 # Appendix
-
-## Model Fit Statistics
-
-Model fit statistics are provided for each of the ten model combinations (invariant, three sizes for each ladings, intercepts, and residuals).
-These tables could be used to examine the traditional change in fit statistics cutoff rules of thumb [@cheung2002], such as $\Delta$ CFI or $\Delta$ RMSEA, to the visualizations presented in the manuscript.
-
-```{r tab1, results='asis'}
-apa_table(results.invariant$model_fit %>% 
-            select(model, AIC, BIC, cfi, tli, rmsea, srmr), 
-          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
-          caption = "Model Fit for Invariant Model")
-```
-
-```{r tab2, results='asis'}
-apa_table(results.small.load$model_fit %>% 
-            select(model, AIC, BIC, cfi, tli, rmsea, srmr), 
-          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
-          caption = "Model Fit for Small Differences in Loadings")
-```
-
-```{r tab3, results='asis'}
-apa_table(results.med.load$model_fit %>% 
-            select(model, AIC, BIC, cfi, tli, rmsea, srmr), 
-          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
-          caption = "Model Fit for Medium Differences in Loadings")
-```
-
-```{r tab4, results='asis'}
-apa_table(results.large.load$model_fit %>% 
-            select(model, AIC, BIC, cfi, tli, rmsea, srmr), 
-          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
-          caption = "Model Fit for Large Differences in Loadings")
-```
-
-```{r tab5, results='asis'}
-apa_table(results.small.int$model_fit %>% 
-            select(model, AIC, BIC, cfi, tli, rmsea, srmr), 
-          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
-          caption = "Model Fit for Small Differences in Intercepts")
-```
-
-```{r tab6, results='asis'}
-apa_table(results.med.int$model_fit %>% 
-            select(model, AIC, BIC, cfi, tli, rmsea, srmr), 
-          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
-          caption = "Model Fit for Medium Differences in Intercepts")
-```
-
-```{r tab7, results='asis'}
-apa_table(results.large.int$model_fit %>% 
-            select(model, AIC, BIC, cfi, tli, rmsea, srmr), 
-          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
-          caption = "Model Fit for Large Differences in Intercepts")
-```
-
-```{r tab8, results='asis'}
-apa_table(results.small.res$model_fit %>% 
-            select(model, AIC, BIC, cfi, tli, rmsea, srmr), 
-          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
-          caption = "Model Fit for Small Differences in Residuals")
-```
-
-```{r tab9, results='asis'}
-apa_table(results.med.res$model_fit %>% 
-            select(model, AIC, BIC, cfi, tli, rmsea, srmr), 
-          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
-          caption = "Model Fit for Medium Differences in Residuals")
-```
-
-```{r tab10, results='asis'}
-apa_table(results.large.res$model_fit %>% 
-            select(model, AIC, BIC, cfi, tli, rmsea, srmr), 
-          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
-          caption = "Model Fit for Large Differences in Residuals")
-```
 
@@
 
-  model.overall <- cfa(model = model, data = data)
+  model.overall <- cfa(model = model, data = data, 
+                       meanstructure = T)
   model.group1 <- cfa(model = model, 
-                      data = subset(data, group == group_names[1]))
+                      data = subset(data, group == group_names[1]),
+                      meanstructure = T)
   model.group2 <- cfa(model = model, 
-                      data = subset(data, group == group_names[2]))
+                      data = subset(data, group == group_names[2]),
+                      meanstructure = T)
   model.configural <- cfa(model = model, data = data, 
@@
 ```
+
+## Model Fit Statistics
+
+Model fit statistics are provided for each of the ten model combinations (invariant, three sizes for each ladings, intercepts, and residuals).
+These tables could be used to examine the traditional change in fit statistics cutoff rules of thumb [@cheung2002], such as $\Delta$ CFI or $\Delta$ RMSEA, to the visualizations presented in the manuscript.
+
+```{r tab1, results='asis'}
+apa_table(results.invariant$model_fit %>% 
+            select(model, AIC, BIC, cfi, tli, rmsea, srmr),
+          digits = 3, 
+          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
+          caption = "Model Fit for Invariant Model")
+```
+
+```{r tab2, results='asis'}
+apa_table(results.small.load$model_fit %>% 
+            select(model, AIC, BIC, cfi, tli, rmsea, srmr), 
+          digits = 3, 
+          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
+          caption = "Model Fit for Small Differences in Loadings")
+```
+
+```{r tab3, results='asis'}
+apa_table(results.med.load$model_fit %>% 
+            select(model, AIC, BIC, cfi, tli, rmsea, srmr), 
+          digits = 3, 
+          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
+          caption = "Model Fit for Medium Differences in Loadings")
+```
+
+```{r tab4, results='asis'}
+apa_table(results.large.load$model_fit %>% 
+            select(model, AIC, BIC, cfi, tli, rmsea, srmr),
+          digits = 3, 
+          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
+          caption = "Model Fit for Large Differences in Loadings")
+```
+
+```{r tab5, results='asis'}
+apa_table(results.small.int$model_fit %>% 
+            select(model, AIC, BIC, cfi, tli, rmsea, srmr), 
+          digits = 3, 
+          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
+          caption = "Model Fit for Small Differences in Intercepts")
+```
+
+```{r tab6, results='asis'}
+apa_table(results.med.int$model_fit %>% 
+            select(model, AIC, BIC, cfi, tli, rmsea, srmr),
+          digits = 3, 
+          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
+          caption = "Model Fit for Medium Differences in Intercepts")
+```
+
+```{r tab7, results='asis'}
+apa_table(results.large.int$model_fit %>% 
+            select(model, AIC, BIC, cfi, tli, rmsea, srmr),
+          digits = 3, 
+          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
+          caption = "Model Fit for Large Differences in Intercepts")
+```
+
+```{r tab8, results='asis'}
+apa_table(results.small.res$model_fit %>% 
+            select(model, AIC, BIC, cfi, tli, rmsea, srmr), 
+          digits = 3, 
+          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
+          caption = "Model Fit for Small Differences in Residuals")
+```
+
+```{r tab9, results='asis'}
+apa_table(results.med.res$model_fit %>% 
+            select(model, AIC, BIC, cfi, tli, rmsea, srmr), 
+          digits = 3, 
+          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
+          caption = "Model Fit for Medium Differences in Residuals")
+```
+
+```{r tab10, results='asis'}
+apa_table(results.large.res$model_fit %>% 
+            select(model, AIC, BIC, cfi, tli, rmsea, srmr), 
+          digits = 3, 
+          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
+          caption = "Model Fit for Large Differences in Residuals")
+```

### 2023-03-31 manuscript.tex
almost there

@@
 \documentclass[
-  man]{apa6}
+  man]{apa7}
 \usepackage{amsmath,amssymb}
@@
 \usepackage{csquotes}
+\makeatletter
+\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
+  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+  {-1em}%
+  {\normalfont\normalsize\bfseries\typesectitle}}
+
+\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
+  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+  {-\z@\relax}%
+  {\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
+\makeatother
+
 \ifLuaTeX
@@
 
-The authors made the following contributions. Erin M. Buchanan: Conceptualization, Writing - Original Draft Preparation, Writing - Review \& Editing.
-
 Correspondence concerning this article should be addressed to Erin M.
@@
 Latent variable modeling as a lens for psychometric theory is a popular tool for social scientists to examine measurement of constructs (Beaujean, 2014).
-Journals such as \emph{Assessment} regularly publish articles supporting new or previously established measures of latent constructs (e.g., depression, anxiety) wherein a measurement model is established for the scale in question.
-These measurement models designate the relationship between the measured, observed variables, and the underlying construct, with the assumption that these relations hold in many samples.
+Journals such as \emph{Assessment} regularly publish articles supporting measures of latent constructs wherein a measurement model is established.
 Confirmatory factor analysis can be used to investigate the replicability and generalizability of the measurement model in new samples, while multi-group confirmatory factor analysis is used to examine the measurement model across groups within samples (Brown, 2015).
-With the rise of the replication crisis and ``psychology's renaissance'' (Nelson, Simmons, \& Simonsohn, 2018), interest in divergence in measurement has increased, often focused on small parameter differences within the latent model.
-While the statistical procedure for examining measurement invariance is moderately well established, it is clear that the toolkit for inspecting these results is lacking.
-This manuscript will outline ways to visualize potential non-invariance, to supplement large numbers of tables that often overwhelm a reader within these published reports.
-Further, given these visualizations, readers will learn how to interpret the impact and size of the proposed non-invariance in models.
+With the rise of the replication crisis and ``psychology's renaissance'' (Nelson et al., 2018), interest in divergence in measurement has increased, often focused on small parameter differences within the latent model.
+This manuscript outlines ways to visualize potential non-invariance, to supplement large numbers of tables that often overwhelm a reader within these published reports.
+Readers will learn how to interpret the impact and size of the proposed non-invariance in models.
 While it is tempting to suggest that problems with replication and generalizability are simply issues with measurement, it is crucial to remember that all models have variability and error, even those models estimating the differences between item functioning, such as multi-group confirmatory factor analysis.
-This manuscript will help provide a framework for researchers interested in registered reports in this area.
 }
@@
 Instead, we use surveys and questionnaires to indirectly assess the underlying construct (DeVellis \& Thorpe, 2022).
-Latent variable modeling (i.e., structural equation modeling) is a popular tool for the validation of developed survey instruments to verify scale dimensionalality, structure, and model fit.
+Latent variable modeling (i.e., structural equation modeling) is a popular tool for the validation of developed survey instruments to verify scale dimensionality, structure, and model fit.
 A simple search for scale development reveals thousands of articles in psychology that examine new and previously published work, thus, illustrating the interest in both measurement and the use of validation techniques.
-Unfortunately, except in specialty journals, much of the validity evidence and/or development for measures used in empirical studies is not reported within the journal article Weidman, Steckler, \& Tracy (2017).
+Unfortunately, except in specialty journals, much of the validity evidence and/or development for measures used in empirical studies is not reported within the journal article (Barry et al., 2014; Weidman et al., 2017).
 Without this information, it is difficult to interpret individual study conclusions, as validity information allows for judgment of usefulness of the measured values (Flake \& Fried, 2020).
-Further, the current focus on replication Zwaan, Etz, Lucas, \& Donnellan (2018), reproducibility (Nelson et al., 2018), and the credibility of our results (Vazire, Schiavone, \& Bottesini, 2022) has demonstrated questionable measurement practices - decisions that researchers make like survey selection and scoring that impact the results of the study (Flake \& Fried, 2020).
-Transparent reporting of the use and creation of scales can improve both interpretation and reproducibility when using surveys developed to measure latent constructs (Shadish, Cook, \& Campbell, 2001).
+Further, the current focus on replication (Makel et al., 2012; Makel \& Plucker, 2014; Zwaan et al., 2018), reproducibility (Nelson et al., 2018), and the credibility of our results (Vazire et al., 2022) has demonstrated questionable measurement practices - decisions that researchers make like survey selection and scoring that impact the results of the study (Flake \& Fried, 2020).
+Transparent reporting of the use and creation of scales can improve both interpretation and reproducibility when using surveys developed to measure latent constructs (Shadish et al., 2001).
 
@@
 For example, Trent et al.
-(2013) examined for potential variability in the Revised Child Anxiety and Depression Scale in White and Black youths (Chorpita, Yim, Moffitt, Umemoto, \& Francis, 2000).
+(2013) examined for potential variability in the Revised Child Anxiety and Depression Scale in White and Black youths (Chorpita et al., 2000).
 They found that the scale mostly functioned the same for both White and Black individuals but differences in averages on individual items could potentially affect the scoring and interpretation of the scale results.
 This comparison of sub-populations is the test of measurement invariance (Meredith, 1993).
-Invariance or equivalence implies that the scale operates in the same fashion for each sub-group, and thus, differences in the final latent variable scores can interpretated as differences in populations.
+Invariance or equivalence implies that the scale operates in the same fashion for each sub-group, and thus, differences in the final latent variable scores can interpreted as differences in populations.
 Non-invariance suggests that individuals respond or interpret items differently, and thus, differences in scores may represent different scores on the latent variable in the population or differences in measurement.
-Non-invariant measurement may lead to misleading results when making group comparisons, and assessing invariance has become a popular technique in scale development (Van De Schoot, Schmidt, De Beuckelaer, Lek, \& Zondervan-Zwijnenburg, 2015).
-
-Measurement invariance is typically analyzed using confirmatory factor analysis, specifically, multi-group confirmatory factor analysis (MGCFA) or less often, with item response theory Tay, Meade, \& Cao (2015).
+Non-invariant measurement may lead to misleading results when making group comparisons, and assessing invariance has become a popular technique in scale development (Van De Schoot et al., 2015).
+
+Measurement invariance is typically analyzed using confirmatory factor analysis, specifically, multi-group confirmatory factor analysis (MGCFA) or less often, with item response theory (Stark et al., 2006; Tay et al., 2015).
 First, the model is examined with the factor structure proposed for the latent and observed variables, and then often these models are assessed for each group separately.
-The two models are then combined together into one nested CFA in order to determine configural invariance Kline (2016).
+The two models are then combined together into one nested CFA in order to determine configural invariance (Brown, 2015; Byrne, 2001; Kline, 2016).
 Configural invariance tests if the proposed factor structure is the same between groups.
@@
 
-These concepts have been explored and implemented for the last fifty years Sörbom (1978) and implemented in the most popular structural equation modeling programs Boker et al.
-(2011).
-Byrne, Shavelson, and Muthén (1989) extended the ideas of multi-group testing by suggesting partial invariance (followed by Meredith, 1993).
+These concepts have been explored and implemented for the last fifty years (Jöreskog, 1971; Sörbom, 1978) and implemented in the most popular structural equation modeling programs (Boker et al., 2011; Jöreskog \& Sörbom, 2001; Rosseel, 2012).
+Byrne et al.
+(1989) extended the ideas of multi-group testing by suggesting partial invariance (followed by Meredith, 1993).
 Partial invariance occurs when non-invariance is found but can be attributed to only a few parameter estimate differences between groups (i.e., items 1 and 2 have different factor loadings but all others are the same).
@@
 To determine when non-invariance and partial invariance occurred, each model is sequentially compared to the previous model using some form of a difference test.
-Traditionally, since models were nested, a chi-square difference test was used Cheung \& Rensvold (2002); however, given the known issues with chi-square (Thompson \& Daniel, 1996), people have favored empirical cutoffs for differences in fit indices.
-As the field pushes back against favoring cutoff criteria and rules of thumb Putnick \& Bornstein (2016), an effect size measure for translating ``how much'' non-invariance was developed \(d_{MACS}\) (Nye \& Drasgow, 2011).
+Traditionally, since models were nested, a chi-square difference test was used (Cheung \& Rensvold, 2002; Meade et al., 2008); however, given the known issues with chi-square (Thompson \& Daniel, 1996), people have favored empirical cutoffs for differences in fit indices.
+As the field pushes back against favoring cutoff criteria and rules of thumb (Marsh et al., 2004; Putnick \& Bornstein, 2016), an effect size measure for translating ``how much'' non-invariance was developed \(d_{MACS}\) (Nye \& Drasgow, 2011).
 This effect size examines the differences in observed variables between the two groups for both the factor loading and the item intercept; thus, any differences in either or both will increase the effect size for non-invariance (Stark et al., 2006).
@@
 Given that this information is generally ignored during the examination of measurement invariance, it may be that we are claiming that many scales are non-invariant, when in reality, the differences between loadings or item intercepts are small and unimportant.
-\(d_{MACS}\) provides the opportunity to begin to think about the smallest effect size of interest or the smallest meaningful effect size Anvari \& Lakens (2021).
+\(d_{MACS}\) provides the opportunity to begin to think about the smallest effect size of interest or the smallest meaningful effect size (Anvari \& Lakens, 2021; Lakens, 2017).
 As mentioned, \(d_{MACS}\) has only really been explored for a combined intercept and loadings, and while useful, does not necessarily allow a researcher to pinpoint specific issues within an observed variable.
@@
 By creating panel visualizations, we can supplement a researchers ability to judge the strength of the non-invariance differences and effect size for each item.
-Coupled with other indicators (i.e., fit indice differences, \(d_{MACS}\)), we can move toward a better understanding of how much measurement non-invariance is meaningful.
-
-By the end of this manuscript, readers will:
+Coupled with other indicators (i.e., fit indices differences, \(d_{MACS}\)), we can move toward a better understanding of how much measurement non-invariance is meaningful.
+
+By the end of this tutorial manuscript, readers will:
 
@@
 
-Data was simulated using the \texttt{simulateData} function in the \emph{R} package \texttt{lavaan} (Rosseel, 2012) assuming multivariate normality using a \(\mu\) of 0 and \(\sigma\) of 1 for the data.
-This function allows you to write \texttt{lavaan} syntax for your model with estimated values to generate data for observed variables.
-The data included two groups of individuals (``Group 1'', ``Group 2'') for a multi-group confirmatory factor analysis (\$n\_\{group\}\$ = 250, \emph{N} = 500).
+Data was simulated using the \texttt{simulateData} function in the \emph{R} package \emph{lavaan} (Rosseel, 2012) assuming multivariate normality using a \(\mu\) of 0 and \(\sigma\) of 1 for the data.
+This function allows you to write \emph{lavaan} syntax for your model with estimated values to generate data for observed variables.
+The data included two groups of individuals (``Group 1'', ``Group 2'') for a multi-group confirmatory factor analysis (\(n_{group}\) = 250, \emph{N} = 500).
 The latent variables were assumed to be continuous normal.
@@
 Fit indices for the steps for multi-group models are presented in the appendix for comparison of cutoff rules of thumb (Cheung \& Rensvold, 2002) to effect sizes and visualizations presented in this manuscript.
-Fit indices include Akaike Information Criterion (AIC, Akaike, 1998), Bayesian Information Criterion (BIC, Schwarz, 1978), Comparative Fit Index (CFI, Bentler, 1990), Tucker Lewis Index (TLI, Tucker \& Lewis, 1973), root mean squared error of approximation RMSEA (Steiger, 1990), and standardized root mean squar residual (SRMR, Bentler, 1995).
-
-The data was then simulated to represent invariance across all model steps, small, medium, and large invariance using \(d_{MACS}\) estimated sizes from Nye, Bradburn, Olenick, Bialko, and Drasgow (2019).
+Fit indices include Akaike Information Criterion (AIC, Akaike, 1998), Bayesian Information Criterion (BIC, Schwarz, 1978), Comparative Fit Index (CFI, Bentler, 1990), Tucker Lewis Index (TLI, Tucker \& Lewis, 1973), root mean squared error of approximation RMSEA (Steiger, 1990), and standardized root mean square residual (SRMR, Bentler, 1995).
+
+The data was then simulated to represent invariance across all model steps, small, medium, and large invariance using \(d_{MACS}\) estimated sizes from Nye et al.
+(2019).
 While \(d_{MACS}\) is used primarily for an effect size of the (non)-invariance for intercepts and loadings together, a similar approach was taken for the estimation of small, medium, and large effects on the residuals.
-The effect size is presented for all models, calculated from the \emph{dmacs} package Nye \& Drasgow (2011).
+The effect size is presented for all models, calculated from the \emph{dmacs} package (Dueber, 2023; Nye \& Drasgow, 2011).
 Only one item in each model was manipulated from the invariant model to create the non-invariant models.
@@
 The complete code for this manuscript can be found at \url{https://osf.io/wev5f/}, and the function code for the convenience function for multi-group models and plots is found in the appendix.
-First, we would create our model code in \texttt{lavaan} syntax.
-The \texttt{lv} latent variable predicts the five measured variables, which are present as columns in our \texttt{df.invariant} dataset.
-You would include the dataframe in the \texttt{data} argument of our function, the name of the grouping variable in quotes for \texttt{group}, and the \texttt{lavaan} model syntax in the \texttt{model} argument.
+This tutorial was registered at \url{https://osf.io/vwf4d}, and the example provided at the end of the manuscript was added after that registration.
+First, we would create our model code in \emph{lavaan} syntax (Rosseel, 2012).
+The \texttt{lv} latent variable predicts the five measured variables, which are present as columns in our \texttt{df.invariant} data set.
+You would include the dataframe in the \texttt{data} argument of our function, the name of the grouping variable in quotes for \texttt{group}, and the \emph{lavaan} model syntax in the \texttt{model} argument.
 The \texttt{mgcfa} function code runs an overall model with all data, regardless of group, each group separately on the model, then the steps described above: configural, metric, scalar, and strict invariance.
 
-\texttt{lavaan} automatically sets the mean (i.e., the intercept) for latent variables to zero.
+\emph{lavaan} automatically sets the mean (i.e., the intercept) for latent variables to zero.
 If we wish to visualize the impact of the changes in parameter estimates across groups on the latent means, we need to allow the latent mean estimation with \texttt{lv\ \textasciitilde{}\ 1}.
@@
 \item
-  \texttt{model\_coef}: a tidy dataframe with \emph{all} model's coefficients saved from the \texttt{lavaan} outputs.
+  \texttt{model\_coef}: a tidy dataframe with \emph{all} model's coefficients saved from the \emph{lavaan} outputs.
 Note that we can see that the intercept \texttt{\textasciitilde{}1} is set for question 1 but freely estimated for the latent variable.
@@
 \item
-  \texttt{model\_fit}: a tidy dataframe with \emph{all} model's fit indices saved from the \texttt{lavaan} outputs.
+  \texttt{model\_fit}: a tidy dataframe with \emph{all} model's fit indices saved from the \emph{lavaan} outputs.
 \end{enumerate}
@@
 \item
-  Saved \texttt{lavaan} fitted objects that you can use the \texttt{summary()}, \texttt{parameterEstimates()}, \texttt{fitIndices()}, etc.
+  Saved \emph{lavaan} fitted objects that you can use the \texttt{summary()}, \texttt{parameterEstimates()}, \texttt{fitIndices()}, etc.
 on.
@@
   \texttt{data\_coef}: A tidy dataframe of the parameter estimates from the models.
-This function assumes you have used \texttt{broom::tidy()} on the saved model from \texttt{lavaan} and added a column called ``model'' with the name of the model step.
+This function assumes you have used \texttt{broom::tidy()} on the saved model from \emph{lavaan} and added a column called ``model'' with the name of the model step (Robinson et al., 2023).
 This function will only run for models that have used the grouping function (i.e., configural, metric, scalar, and strict or other combinations/steps you wish to examine).
@@
 \item
-  \texttt{x\_limits}: What do you want the x-axits limits to be for your invariance plot?
+  \texttt{x\_limits}: What do you want the x-axis limits to be for your invariance plot?
 The default option is to assume the latent variable is standardized, and therefore, -1 to 1 is recommended.
@@
 \item
-  \texttt{y\_limits}: What do you want the y-axits limits to be for your invariance plot?
+  \texttt{y\_limits}: What do you want the y-axis limits to be for your invariance plot?
 Given that the latent variable is used to predict the observed values in the data, you could use the minimum and maximum values found in the data.
@@
 \item
-  \texttt{model\_results}: In this argument, include the saved \texttt{lavaan} output for the model listed in the \texttt{model\_step} argument.
+  \texttt{model\_results}: In this argument, include the saved \emph{lavaan} output for the model listed in the \texttt{model\_step} argument.
 \item
-  \texttt{lv\_name}: Include the name of the latent variable, exactly how it is listed in your \texttt{lavaan} syntax.
+  \texttt{lv\_name}: Include the name of the latent variable, exactly how it is listed in your \emph{lavaan} syntax.
 You should plot the latent variable that the \texttt{item\_name} is linked to.
@@
 All parameter estimates are plotted on the unstandardized estimates and their confidence interval based on the standard error of the estimate.
+All plots are made with \emph{ggplot2} (Wickham, 2016) and \emph{cowplot} (Wilke, 2020).
 
@@
 Finally, group labels are represented in the figure caption on the bottom.
-Group 1 is usually the group that is alphabetically first in the dataset or whichever group is the first that appears when using the \texttt{levels()} command.
+Group 1 is usually the group that is alphabetically first in the data set or whichever group is the first that appears when using the \texttt{levels()} command.
 
@@
 Figure \ref{fig:small-load-pic} displays the results from the small (\(d_{MACS}\) = 0.12) difference in loadings, while Figure \ref{fig:med-load-pic} displays the results from the medium (\(d_{MACS}\) = 0.43) difference in loadings, and Figure \ref{fig:large-load-pic} shows the large (\(d_{MACS}\) = 0.63) differences.
-When investigating the slope values, we can clearly see the change in the loading for the second group (the only manipulated variable, although random dataset generation may also change intercepts and residuals slightly).
+When investigating the slope values, we can clearly see the change in the loading for the second group (the only manipulated variable, although random data set generation may also change intercepts and residuals slightly).
 At the medium effect size, we see that the confidence bands do not overlap (at the edges), and at the large effect size, we can see a clear separation of two lines.
 Note that the intercepts in this model are estimated as equal so the loading representation will not literally separate, but the steepness of the lines is the indicator of the difference between the slopes.
-You can imagine these lines are interpreted like a simple slopes analysis for interactions in regression (Cohen, Cohen, West, \& Aiken, 2003).
+You can imagine these lines are interpreted like a simple slopes analysis for interactions in regression (Cohen et al., 2003).
 When simple slopes for interactions are plotted, if they are parallel, there is no interaction, and if they cross, then there is an interaction.
@@
 Last, the effect of the residuals is plotted in small (Figure \ref{fig:small-res-pic}), medium (Figure \ref{fig:med-res-pic}), and large (Figure \ref{fig:large-res-pic}) formats.
-While \(d_{MACS}\) values are not technically avaliable for the residuals, our models showed 0.20, 0.14, and 0.11, respectively.
-These differences in values are variable due to the random generation of datasets for each measurement invariance manipulation.
+While \(d_{MACS}\) values are not technically available for the residuals, our models showed 0.20, 0.14, and 0.11, respectively.
+These differences in values are variable due to the random generation of data sets for each measurement invariance manipulation.
 At first glance, the differences in the small chart may seem large, because the black lines are not touching, but notice that the distributions overlap, indicating a likely small difference.
@@
 
-Aiena, Baczwaski, Schulenberg, and Buchanan (2014) examined the RS-14 (Wagnild, 2009) exploring the factor structure of the Resiliency Scale in a clinical sample receiving treatment services and a college student sample.
+Aiena et al.
+(2014) examined the RS-14 (Wagnild, 2009) exploring the factor structure of the Resiliency Scale in a clinical sample receiving treatment services and a college student sample.
 Measurement invariance was calculated for differences separately for these samples for gender and race finding a partially invariant models with a few item intercepts or residuals that differed between groups.
@@
 \FunctionTok{load}\NormalTok{(}\StringTok{"RS14.Rdata"}\NormalTok{)}
+
 \CommentTok{\# build the one{-}factor model }
@@
 \midrule
-Overall & 126,722.49 & 126,888.71 & 0.93 & 0.92 & 0.09 & 0.04\\
-Group 1 & 52,961.42 & 53,099.72 & 0.92 & 0.90 & 0.09 & 0.04\\
-Group 2 & 69,100.98 & 69,254.31 & 0.93 & 0.92 & 0.11 & 0.04\\
-Configural & 122,118.41 & 122,617.06 & 0.93 & 0.91 & 0.10 & 0.04\\
-Metric & 122,144.53 & 122,566.01 & 0.92 & 0.92 & 0.10 & 0.04\\
-Scalar & 122,544.11 & 122,888.42 & 0.91 & 0.91 & 0.10 & 0.05\\
-Strict & 126,466.24 & 126,727.44 & 0.78 & 0.79 & 0.16 & 0.09\\
+Overall & 126,750.491 & 126,999.816 & 0.934 & 0.923 & 0.094 & 0.033\\
+Group 1 & 52,989.421 & 53,196.870 & 0.919 & 0.904 & 0.090 & 0.041\\
+Group 2 & 69,128.985 & 69,358.973 & 0.928 & 0.915 & 0.108 & 0.033\\
+Configural & 122,118.406 & 122,617.055 & 0.926 & 0.912 & 0.102 & 0.036\\
+Metric & 122,144.532 & 122,566.010 & 0.925 & 0.918 & 0.098 & 0.043\\
+Scalar & 122,544.109 & 122,888.415 & 0.911 & 0.910 & 0.103 & 0.052\\
+Strict & 126,466.241 & 126,727.438 & 0.780 & 0.793 & 0.156 & 0.086\\
 \bottomrule
@@
 
-Table \ref{fig:invariant-pic} indicates the results after running the one-factor model. There are several guidelines for assessing assessing a degradation in model fit (\textbf{cheung?})
-
-\#\#write out partial codes
-partial\_syntax \textless- paste(colnames(DF){[}1:14{]}, ``\textasciitilde1'') \#all columns again
-partial\_syntax
-
-CFI\_list \textless- 1:length(partial\_syntax)
-names(CFI\_list) \textless- partial\_syntax
-
-for (i in 1:length(partial\_syntax))\{
-
-temp \textless- cfa(model = model.rs,
-data = DF,
-meanstructure = TRUE,
-group = ``sample'',
-group.equal = c(``loadings'', ``intercepts''),
-group.partial = partial\_syntax{[}i{]})
-
-CFI\_list{[}i{]} \textless- fitmeasures(temp, ``cfi'')
-\}
-
-CFI\_list
-
-partial.rs \textless- cfa(model = model.rs,
-data = DF,
-meanstructure = TRUE,
-group = ``sample'',
-meanstructure = T,
-group.equal = c(``loadings'', ``intercepts''),
-group.partial = c(``RS7\textasciitilde1'')
-)
-
-tidy(partial.rs)
-glance(partial.rs)
-results.rs\$model\_fit
-
-partial.rs.2 \textless- cfa(model = model.rs,
-data = DF,
-meanstructure = TRUE,
-group = ``sample'',
-meanstructure = T,
-group.equal = c(``loadings'', ``intercepts''),
-group.partial = c(``RS7\textasciitilde1'', ``RS6\textasciitilde1'')
-)
-
-tidy(partial.rs.2)
-glance(partial.rs.2)
-
-partial.rs.2.strict \textless- cfa(model = model.rs,
-data = DF,
-meanstructure = TRUE,
-group = ``sample'',
-meanstructure = T,
-group.equal = c(``loadings'', ``intercepts'', ``residuals''),
-group.partial = c(``RS7\textasciitilde1'', ``RS6\textasciitilde1'')
-)
-
-tidy(partial.rs.2.strict)
-glance(partial.rs.2.strict)
-
-model.rs.picture \textless- ``RS =\textasciitilde{} RS1+RS2+RS3+RS4+RS5+RS6+RS7+RS8+RS9+RS10+RS11+RS12+RS13+RS14
-RS\textasciitilde1
-RS1\textasciitilde0*1''
-
-partial.rs.2.picture \textless- cfa(model = model.rs,
-data = DF,
-meanstructure = TRUE,
-group = ``sample'',
-meanstructure = T,
-group.equal = c(``loadings'', ``intercepts''),
-group.partial = c(``RS7\textasciitilde1'', ``RS6\textasciitilde1''))
-
-partial.coef \textless- tidy(partial.rs.2.picture) \%\textgreater\%
-mutate(model = ``intercepts'')
-
-plot\_mgcfa(
-data\_coef = partial.coef,
-model\_step = ``intercepts'',
-item\_name = ``RS6'',
-x\_limits = c(-2,2),
-y\_limits = c(min(DF\(RS7), max(DF\)RS7)),
-model\_results = partial.rs.2.picture,
-ci\_level = .95,
-lv\_name = ``RS''
-)
-
-plot\_mgcfa(
-data\_coef = partial.coef,
-model\_step = ``intercepts'',
-item\_name = ``RS7'',
-x\_limits = c(-2,2),
-y\_limits = c(min(DF\(RS7), max(DF\)RS7)),
-model\_results = partial.rs.2.picture,
-ci\_level = .95,
-lv\_name = ``RS''
-)
-
-SD \textless- tapply(DF\(RS6, DF\)sample, sd)
-M \textless- tapply(DF\(RS6, DF\)sample, mean)
-N \textless- tapply(DF\(RS6, DF\)sample, length)
-
-SD2 \textless- tapply(DF\(RS7, DF\)sample, sd)
-M2 \textless- tapply(DF\(RS7, DF\)sample, mean)
-N2 \textless- tapply(DF\(RS7, DF\)sample, length)
-
-library(MOTE)
-d.ind.t(M{[}1{]}, M{[}2{]}, SD{[}1{]}, SD{[}2{]}, N{[}1{]}, N{[}2{]})
-d.ind.t(M2{[}1{]}, M2{[}2{]}, SD2{[}1{]}, SD2{[}2{]}, N2{[}1{]}, N2{[}2{]})
-lavaan\_dmacs(partial.rs.2.picture, ``Clinical'')
-lavaan\_dmacs(results.rs\$model.configural, ``Clinical'')
+Table \ref{fig:invariant-pic} indicates the results after running the one-factor model.
+There are several guidelines for assessing assessing a degradation in model fit (Cao \& Liang, 2022; Cheung \& Rensvold, 2002; Counsell et al., 2020; Jin, 2020; Putnick \& Bornstein, 2016) but for the purposes of this illustration \(\Delta\)CFI \textgreater{} .01 will be used.
+Table \ref{fig:invariant-pic} indicates that fit was degraded when the constraint on equal item intercepts was added.
+The code below provides an example of testing each item individually by relaxing the constraints and recalculating the CFI.
+If these Items bring the CFI value back up to \(\Delta\)CFI \textless= .01 from the metric model, then the model would be considering partially invariant at the scalar level.
+It seems unlikely that the residuals will show invariance, if partial scalar invariance can be found, as the drop in fit is quite large.
+
+\small
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\# write out the partial invariance codes for intercepts \textasciitilde{}1}
+\NormalTok{partial\_syntax }\OtherTok{\textless{}{-}} \FunctionTok{paste}\NormalTok{(}\FunctionTok{colnames}\NormalTok{(DF)[}\DecValTok{1}\SpecialCharTok{:}\DecValTok{14}\NormalTok{], }\StringTok{"\textasciitilde{}1"}\NormalTok{) }
+\NormalTok{partial\_syntax}
+\end{Highlighting}
+\end{Shaded}
+
+\normalsize
 
 \begin{verbatim}
-
-6: Drive
-
-7: Perseverance
-
-I1tems for the RS–14 are described in the measure’s manual (Wagnild, 2009a)
-and can be viewed at www.resiliencecenter.com.
-
-# Discussion
-
-Conclusions:
-
--   framework for submitted/interpreting reports
+##  [1] "RS1 ~1"  "RS2 ~1"  "RS3 ~1"  "RS4 ~1"  "RS5 ~1"  "RS6 ~1"  "RS7 ~1" 
+##  [8] "RS8 ~1"  "RS9 ~1"  "RS10 ~1" "RS11 ~1" "RS12 ~1" "RS13 ~1" "RS14 ~1"
+\end{verbatim}
+
+\small
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\# create a place to save the CFIs for each item separately}
+\NormalTok{CFI\_list  }\OtherTok{\textless{}{-}} \DecValTok{1}\SpecialCharTok{:}\FunctionTok{length}\NormalTok{(partial\_syntax)}
+\FunctionTok{names}\NormalTok{(CFI\_list) }\OtherTok{\textless{}{-}}\NormalTok{ partial\_syntax}
+\CommentTok{\# loop over the items and calculate CFI }
+\CommentTok{\# with that item freely estimated}
+\ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{1}\SpecialCharTok{:}\FunctionTok{length}\NormalTok{(partial\_syntax))\{}
+
+\NormalTok{  temp }\OtherTok{\textless{}{-}} \FunctionTok{cfa}\NormalTok{(}\AttributeTok{model =}\NormalTok{ model.rs, }
+              \AttributeTok{data =}\NormalTok{ DF,}
+              \AttributeTok{meanstructure =} \ConstantTok{TRUE}\NormalTok{,}
+              \AttributeTok{group =} \StringTok{"sample"}\NormalTok{,}
+              \AttributeTok{group.equal =} \FunctionTok{c}\NormalTok{(}\StringTok{"loadings"}\NormalTok{, }\StringTok{"intercepts"}\NormalTok{),}
+              \AttributeTok{group.partial =}\NormalTok{ partial\_syntax[i])}
+
+\NormalTok{  CFI\_list[i] }\OtherTok{\textless{}{-}} \FunctionTok{fitmeasures}\NormalTok{(temp, }\StringTok{"cfi"}\NormalTok{)}
+\NormalTok{\}}
+\CommentTok{\# look at the new CFIs}
+\NormalTok{CFI\_list}
+\end{Highlighting}
+\end{Shaded}
+
+\normalsize
+
+\begin{verbatim}
+##    RS1 ~1    RS2 ~1    RS3 ~1    RS4 ~1    RS5 ~1    RS6 ~1    RS7 ~1    RS8 ~1 
+## 0.9116914 0.9129976 0.9117235 0.9111212 0.9126742 0.9133618 0.9139287 0.9111397 
+##    RS9 ~1   RS10 ~1   RS11 ~1   RS12 ~1   RS13 ~1   RS14 ~1 
+## 0.9119702 0.9118309 0.9110574 0.9112309 0.9112367 0.9112015
+\end{verbatim}
+
+The output indicates that RS6 and RS7 are potential items that could be relaxed to improve model fit and create a partial scalar invariant model.
+The code below show to check the addition of these items, which are added one at a time.
+You use the \texttt{group.partial} open to ``relax'' or freely estimate that parameter for each group separately.
+Once that model is saved, you can use the \texttt{tidy} function from \emph{broom} to arrange the estimates from the model, which is used in our plotting function.
+The \texttt{glance} function will create a tidy dataframe of the fit indices for easy review.
+
+\small
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\# run the partially invariant model with group.partial}
+\NormalTok{partial.rs }\OtherTok{\textless{}{-}} \FunctionTok{cfa}\NormalTok{(}\AttributeTok{model =}\NormalTok{ model.rs, }
+                  \AttributeTok{data =}\NormalTok{ DF, }
+                  \AttributeTok{meanstructure =} \ConstantTok{TRUE}\NormalTok{,}
+                  \AttributeTok{group =} \StringTok{"sample"}\NormalTok{, }
+                  \AttributeTok{meanstructure =}\NormalTok{ T, }
+                  \AttributeTok{group.equal =} \FunctionTok{c}\NormalTok{(}\StringTok{"loadings"}\NormalTok{, }\StringTok{"intercepts"}\NormalTok{),}
+                  \AttributeTok{group.partial =} \FunctionTok{c}\NormalTok{(}\StringTok{"RS7\textasciitilde{}1"}\NormalTok{))}
+
+\CommentTok{\# examine the loadings }
+\FunctionTok{tidy}\NormalTok{(partial.rs) }\SpecialCharTok{\%\textgreater{}\%} 
+  \FunctionTok{filter}\NormalTok{(term }\SpecialCharTok{==} \StringTok{"RS7 \textasciitilde{}1 "}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
+  \FunctionTok{select}\NormalTok{(term, group, estimate, std.error)}
+\end{Highlighting}
+\end{Shaded}
+
+\normalsize
+
+\begin{verbatim}
+## # A tibble: 2 x 4
+##   term      group estimate std.error
+##   <chr>     <int>    <dbl>     <dbl>
+## 1 "RS7 ~1 "     1     4.95    0.0580
+## 2 "RS7 ~1 "     2     4.49    0.0529
+\end{verbatim}
+
+\small
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\# examine the fit indices }
+\FunctionTok{glance}\NormalTok{(partial.rs) }\SpecialCharTok{\%\textgreater{}\%} 
+  \FunctionTok{select}\NormalTok{(AIC, BIC, cfi, tli, rmsea, srmr)}
+\end{Highlighting}
+\end{Shaded}
+
+\normalsize
+
+\begin{verbatim}
+## # A tibble: 1 x 6
+##       AIC     BIC   cfi   tli rmsea   srmr
+##     <dbl>   <dbl> <dbl> <dbl> <dbl>  <dbl>
+## 1 122454. 122804. 0.914 0.912 0.102 0.0502
+\end{verbatim}
+
+\small
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\# effect size model }
+\FunctionTok{lavaan\_dmacs}\NormalTok{(partial.rs, }\StringTok{"Clinical"}\NormalTok{)}\SpecialCharTok{$}\NormalTok{DMACS[}\DecValTok{7}\NormalTok{]}
+\end{Highlighting}
+\end{Shaded}
+
+\normalsize
+
+\begin{verbatim}
+##      RS7 
+## 0.282302
+\end{verbatim}
+
+By examining our estimates, we can see that item seven on the RS-14 is estimated at nearly 5 points for the clinical sample, while the student sample has a lower mean around 4.5 points.
+Generally, students show higher means on the items of the RS14, but when all loadings and other intercepts are constrained to be equal, and this one item is relaxed, this pattern flips so that clinical groups show higher item intercepts.
+Given the scale is a 1-7 Likert type scale, .5 a point represents a potentially sizable change on the scale.
+Item seven covers perseverance after hardship, and all items can be found in the user manual for the scale at www.resiliencecenter.com.
+The effect size from \(d_{DMACS}\) suggests a small to medium effect, 0.28.
+In this next code section, we repeat this process for the RS6, as the CFI for our model with only RS7 does not achieve the levels of partial invariance for our \(\Delta\)CFI criterion (i.e., \textless= .01 downward change in fit: metric CFI = .925, partial scalar CFI = .914).
+
+\small
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\# add the second intercept}
+\NormalTok{partial.rs}\FloatTok{.2} \OtherTok{\textless{}{-}} \FunctionTok{cfa}\NormalTok{(}\AttributeTok{model =}\NormalTok{ model.rs, }
+                  \AttributeTok{data =}\NormalTok{ DF, }
+                  \AttributeTok{meanstructure =} \ConstantTok{TRUE}\NormalTok{,}
+                  \AttributeTok{group =} \StringTok{"sample"}\NormalTok{, }
+                  \AttributeTok{meanstructure =}\NormalTok{ T, }
+                  \AttributeTok{group.equal =} \FunctionTok{c}\NormalTok{(}\StringTok{"loadings"}\NormalTok{, }\StringTok{"intercepts"}\NormalTok{),}
+                  \AttributeTok{group.partial =} \FunctionTok{c}\NormalTok{(}\StringTok{"RS7\textasciitilde{}1"}\NormalTok{, }\StringTok{"RS6\textasciitilde{}1"}\NormalTok{))}
+
+\CommentTok{\# examine the loadings }
+\FunctionTok{tidy}\NormalTok{(partial.rs}\FloatTok{.2}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
+  \FunctionTok{filter}\NormalTok{(term }\SpecialCharTok{==} \StringTok{"RS6 \textasciitilde{}1 "}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
+  \FunctionTok{select}\NormalTok{(term, group, estimate, std.error)}
+\end{Highlighting}
+\end{Shaded}
+
+\normalsize
+
+\begin{verbatim}
+## # A tibble: 2 x 4
+##   term      group estimate std.error
+##   <chr>     <int>    <dbl>     <dbl>
+## 1 "RS6 ~1 "     1     5.00    0.0605
+## 2 "RS6 ~1 "     2     4.54    0.0533
+\end{verbatim}
+
+\small
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\# examine the fit indices }
+\FunctionTok{glance}\NormalTok{(partial.rs}\FloatTok{.2}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
+  \FunctionTok{select}\NormalTok{(AIC, BIC, cfi, tli, rmsea, srmr)}
+\end{Highlighting}
+\end{Shaded}
+
+\normalsize
+
+\begin{verbatim}
+## # A tibble: 1 x 6
+##       AIC     BIC   cfi   tli rmsea   srmr
+##     <dbl>   <dbl> <dbl> <dbl> <dbl>  <dbl>
+## 1 122363. 122719. 0.917 0.915 0.100 0.0488
+\end{verbatim}
+
+\small
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\# the effect size is }
+\FunctionTok{lavaan\_dmacs}\NormalTok{(partial.rs}\FloatTok{.2}\NormalTok{, }\StringTok{"Clinical"}\NormalTok{)}\SpecialCharTok{$}\NormalTok{DMACS[}\DecValTok{6}\NormalTok{]}
+\end{Highlighting}
+\end{Shaded}
+
+\normalsize
+
+\begin{verbatim}
+##       RS6 
+## 0.2796334
+\end{verbatim}
+
+Again, we see about a half-point difference between our clinical and student samples for item 6, which is about drive to achieve.
+The CFI for this model does meet the requirements for partial invariance, .917.
+The effect size is approximately the same at 0.28.
+Last, we can create our images to view the item non-invariance and the latent means in Figures \ref{fig:rs6-img} and \ref{fig:rs7-img}.
+
+\small
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\# rebuild the model by constraining item 1 intercept}
+\CommentTok{\# allow the latent variable to be estimated}
+\NormalTok{model.rs.picture }\OtherTok{\textless{}{-}} \StringTok{"RS =\textasciitilde{} RS1+RS2+RS3+RS4+RS5+RS6+RS7+RS8+RS9+RS10+RS11+RS12+RS13+RS14}
+\StringTok{RS\textasciitilde{}1}
+\StringTok{RS1\textasciitilde{}0*1"}
+
+\CommentTok{\# rerun the partial invariance model }
+\NormalTok{partial.rs.}\FloatTok{2.}\NormalTok{picture }\OtherTok{\textless{}{-}} \FunctionTok{cfa}\NormalTok{(}\AttributeTok{model =}\NormalTok{ model.rs, }
+                  \AttributeTok{data =}\NormalTok{ DF, }
+                  \AttributeTok{meanstructure =} \ConstantTok{TRUE}\NormalTok{,}
+                  \AttributeTok{group =} \StringTok{"sample"}\NormalTok{, }
+                  \AttributeTok{meanstructure =}\NormalTok{ T, }
+                  \AttributeTok{group.equal =} \FunctionTok{c}\NormalTok{(}\StringTok{"loadings"}\NormalTok{, }\StringTok{"intercepts"}\NormalTok{),}
+                  \AttributeTok{group.partial =} \FunctionTok{c}\NormalTok{(}\StringTok{"RS7\textasciitilde{}1"}\NormalTok{, }\StringTok{"RS6\textasciitilde{}1"}\NormalTok{))}
+
+\CommentTok{\# save the coefficients to use in our picture function }
+\NormalTok{partial.coef }\OtherTok{\textless{}{-}} \FunctionTok{tidy}\NormalTok{(partial.rs.}\FloatTok{2.}\NormalTok{picture) }\SpecialCharTok{\%\textgreater{}\%} 
+  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{model =} \StringTok{"Scalar"}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\normalsize
+
+\normalsize
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\# plot the image for RS6}
+\FunctionTok{plot\_mgcfa}\NormalTok{(}
+  \AttributeTok{data\_coef =}\NormalTok{ partial.coef,}
+  \AttributeTok{model\_step =} \StringTok{"Scalar"}\NormalTok{, }
+  \AttributeTok{item\_name =} \StringTok{"RS6"}\NormalTok{,}
+  \AttributeTok{x\_limits =} \FunctionTok{c}\NormalTok{(}\SpecialCharTok{{-}}\DecValTok{2}\NormalTok{,}\DecValTok{2}\NormalTok{),}
+  \AttributeTok{y\_limits =} \FunctionTok{c}\NormalTok{(}\FunctionTok{min}\NormalTok{(DF}\SpecialCharTok{$}\NormalTok{RS7), }\FunctionTok{max}\NormalTok{(DF}\SpecialCharTok{$}\NormalTok{RS7)),}
+  \AttributeTok{model\_results =}\NormalTok{ partial.rs.}\FloatTok{2.}\NormalTok{picture, }
+  \AttributeTok{ci\_level =}\NormalTok{ .}\DecValTok{95}\NormalTok{,}
+  \AttributeTok{lv\_name =} \StringTok{"RS"}
+\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\normalsize
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/rs6-img-1.pdf}
+\caption{\label{fig:rs6-img}RS6 Item Invariance Visualization}
+\end{figure}
+
+\normalsize
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\# plot the image for RS7}
+\FunctionTok{plot\_mgcfa}\NormalTok{(}
+  \AttributeTok{data\_coef =}\NormalTok{ partial.coef,}
+  \AttributeTok{model\_step =} \StringTok{"Scalar"}\NormalTok{, }
+  \AttributeTok{item\_name =} \StringTok{"RS7"}\NormalTok{,}
+  \AttributeTok{x\_limits =} \FunctionTok{c}\NormalTok{(}\SpecialCharTok{{-}}\DecValTok{2}\NormalTok{,}\DecValTok{2}\NormalTok{),}
+  \AttributeTok{y\_limits =} \FunctionTok{c}\NormalTok{(}\FunctionTok{min}\NormalTok{(DF}\SpecialCharTok{$}\NormalTok{RS7), }\FunctionTok{max}\NormalTok{(DF}\SpecialCharTok{$}\NormalTok{RS7)),}
+  \AttributeTok{model\_results =}\NormalTok{ partial.rs.}\FloatTok{2.}\NormalTok{picture, }
+  \AttributeTok{ci\_level =}\NormalTok{ .}\DecValTok{95}\NormalTok{,}
+  \AttributeTok{lv\_name =} \StringTok{"RS"}
+\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\normalsize
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/rs7-img-1.pdf}
+\caption{\label{fig:rs7-img}RS7 Item Invariance Visualization}
+\end{figure}
+
+The latent mean is calculated ``separately'' for each group, insomuch as the first group is considered the comparison group, while the second is the difference between groups, like how dummy coded variables in regression are examined.
+Here we see a difference of 0.72, and students show a higher resiliency score.
+However, when all other things are held equivalent, the intercepts on items 6 and 7 show higher scores for clinical populations.
+Additionally, we may see an indication in our student population of a bimodal distribution that may be related to this effect.
+
+\hypertarget{discussion}{%
+\section{Discussion}\label{discussion}}
+
+In this tutorial, we examined how to use multiple tools to examine measurement invariance.
+Model fit comparisons and statistics can be paired with newly developed effect size measures, and finally a visualization to examine individual items and the overall latent mean scores.
+This visualization was designed with common graphing elements that researchers often use to display those statistics - intercepts were graphed on the intercept line, slopes were represented as lines of fit, and error terms were represented as distributions.
+Each component can impact the overall model and the eventual latent mean scores, as shown in the simulations holding all other things equal.
+Using real data, the effect of two non-invariant item intercepts was examined and visualized.
+How should one interpret the ``discrepancy'' between the results (these effect visually appear large) from effect sizes (.30 was proposed as small to medium in Nye et al.
+(2019))?
+
+Effect sizes are notoriously difficult to interpret, which is why we love guidelines, even if Cohen (1990) declared we probably shouldn't use his suggestions.
+Others have begun to discuss the importance of focusing on effects in the scale of the data and their practical importance (Anvari \& Lakens, 2021; Cumming, 2012).
+Our interpretation may be that the difference between groups is large, as a 0.72 change on a 7 point scale is approximately 10\% more resiliency for students when compared to the clinical sample.
+Practically, 10\% in resiliency for an area of the United States (Mississippi) often hit with natural disasters (hurricanes, tornadoes, floods) and high levels of poverty would be very important.
+Even the smaller difference of .5 point on each individual item could translate into increases in resiliency, and these results may elucidate avenues for further exploration into areas of focus within resiliency, given the items.
+
+What do the results of a study on measurement invariance with these results tell us about replication, generalizability, and validity?
+If a researcher decides their effects are large, they should likely caution against suggesting that these scores are directly comparable without weighting or other adjustment.
+Let's consider a scenario wherein the change metric between models picked (i.e., \(\Delta\)CFI, \(\Delta\)RMSEA) indicates a ``significant'' change in model fit.
+However, if both the effect size and a visual inspection of the invariance indicates a small difference, we may decide to lessen the practical importance of those results, much like ``just significant'' \emph{p}-values with small effect sizes are treated now.
+Given that the goal of measurement invariance is to compare \emph{estimates}, we should expect some differences across samples due to the nature of sampling and estimation.
+It may be that many of the published models presented represent these effects - small variations between groups due to sampling error or other small crud - but do not represent a fundamental problem with the measurement or generalizability of the results.
 
@@
 
-# References
-
-::: {#refs custom-style="Bibliography"}
-:::
+\hypertarget{references}{%
+\section{References}\label{references}}
+
+\hypertarget{refs}{}
+\begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-aiena2014}{}}%
+Aiena, B.
+J., Baczwaski, B.
+J., Schulenberg, S.
+E., \& Buchanan, E.
+M.
+(2014).
+Measuring Resilience With the RS{\textendash}14: A Tale of Two Samples.
+\emph{Journal of Personality Assessment}, \emph{97}(3), 291--300.
+\url{https://doi.org/10.1080/00223891.2014.951445}
+
+\leavevmode\vadjust pre{\hypertarget{ref-akaike1998}{}}%
+Akaike, H.
+(1998).
+\emph{Information theory and an extension of the maximum likelihood principle} (E.
+Parzen, K.
+Tanabe, \& G.
+Kitagawa, Eds.; pp.
+199--213).
+Springer New York.
+\url{http://link.springer.com/10.1007/978-1-4612-1694-0_15}
+
+\leavevmode\vadjust pre{\hypertarget{ref-anvari2021}{}}%
+Anvari, F., \& Lakens, D.
+(2021).
+Using anchor-based methods to determine the smallest effect size of interest.
+\emph{Journal of Experimental Social Psychology}, \emph{96}, 104159.
+\url{https://doi.org/10.1016/j.jesp.2021.104159}
+
+\leavevmode\vadjust pre{\hypertarget{ref-barry2014}{}}%
+Barry, A.
+E., Chaney, B., Piazza-Gardner, A.
+K., \& Chavarria, E.
+A.
+(2014).
+Validity and Reliability Reporting Practices in the Field of Health Education and Behavior: A Review of Seven Journals.
+\emph{Health Education \& Behavior}, \emph{41}(1), 12--18.
+\url{https://doi.org/10.1177/1090198113483139}
+
+\leavevmode\vadjust pre{\hypertarget{ref-beaujean2014}{}}%
+Beaujean, A. A. (2014). \emph{Latent variable modeling using r: A step by step guide}. Routledge/Taylor \& Francis Group.
+
+\leavevmode\vadjust pre{\hypertarget{ref-bentler1990}{}}%
+Bentler, P. M. (1990). Comparative fit indexes in structural models. \emph{Psychological Bulletin}, \emph{107}(2), 238--246. \url{https://doi.org/10.1037/0033-2909.107.2.238}
+
+\leavevmode\vadjust pre{\hypertarget{ref-bentler1995}{}}%
+Bentler, P. M. (1995). \emph{EQS structural equations program manual}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-boker2011}{}}%
+Boker, S., Neale, M., Maes, H., Wilde, M., Spiegel, M., Brick, T., Spies, J., Estabrook, R., Kenny, S., Bates, T., Mehta, P., \& Fox, J.
+(2011).
+OpenMx: An Open Source Extended Structural Equation Modeling Framework.
+\emph{Psychometrika}, \emph{76}(2), 306--317.
+\url{https://doi.org/10.1007/s11336-010-9200-6}
+
+\leavevmode\vadjust pre{\hypertarget{ref-brown2015}{}}%
+Brown, T. A. (2015). \emph{Confirmatory factor analysis for applied research} (Second edition). The Guilford Press.
+
+\leavevmode\vadjust pre{\hypertarget{ref-byrne2001}{}}%
+Byrne, B.
+M.
+(2001).
+Structural Equation Modeling With AMOS, EQS, and LISREL: Comparative Approaches to Testing for the Factorial Validity of a Measuring Instrument.
+\emph{International Journal of Testing}, \emph{1}(1), 55--86.
+\url{https://doi.org/10.1207/S15327574IJT0101_4}
+
+\leavevmode\vadjust pre{\hypertarget{ref-byrne1989}{}}%
+Byrne, B.
+M., Shavelson, R.
+J., \& Muthén, B.
+(1989).
+Testing for the equivalence of factor covariance and mean structures: The issue of partial measurement invariance.
+\emph{Psychological Bulletin}, \emph{105}(3), 456--466.
+\url{https://doi.org/10.1037/0033-2909.105.3.456}
+
+\leavevmode\vadjust pre{\hypertarget{ref-cao2022}{}}%
+Cao, C., \& Liang, X.
+(2022).
+The impact of model size on the sensitivity of fit measures in measurement invariance testing.
+\emph{Structural Equation Modeling: A Multidisciplinary Journal}, \emph{29}(5), 744--754.
+\url{https://doi.org/10.1080/10705511.2022.2056893}
+
+\leavevmode\vadjust pre{\hypertarget{ref-cheung2002}{}}%
+Cheung, G.
+W., \& Rensvold, R.
+B.
+(2002).
+Evaluating Goodness-of-Fit Indexes for Testing Measurement Invariance.
+\emph{Structural Equation Modeling: A Multidisciplinary Journal}, \emph{9}(2), 233--255.
+\url{https://doi.org/10.1207/s15328007sem0902_5}
+
+\leavevmode\vadjust pre{\hypertarget{ref-chorpita2000}{}}%
+Chorpita, B.
+F., Yim, L., Moffitt, C., Umemoto, L.
+A., \& Francis, S.
+E.
+(2000).
+Assessment of symptoms of DSM-IV anxiety and depression in children: a revised child anxiety and depression scale.
+\emph{Behaviour Research and Therapy}, \emph{38}(8), 835--855.
+\url{https://doi.org/10.1016/S0005-7967(99)00130-8}
+
+\leavevmode\vadjust pre{\hypertarget{ref-cohen1990}{}}%
+Cohen, J. (1990). Things I have learned (so far). \emph{American Psychologist}, \emph{45}(12), 1304--1312. \url{https://doi.org/10.1037/0003-066X.45.12.1304}
+
+\leavevmode\vadjust pre{\hypertarget{ref-cohen2003}{}}%
+Cohen, J., Cohen, P., West, S. G., \& Aiken, L. (2003). \emph{Applied multiple regression / correlation analysis for the behavioral sciences} (3rd ed.). Lawrence Erlbaum Associates.
+
+\leavevmode\vadjust pre{\hypertarget{ref-counsell2020}{}}%
+Counsell, A., Cribbie, R.
+A., \& Flora, D.
+B.
+(2020).
+Evaluating equivalence testing methods for measurement invariance.
+\emph{Multivariate Behavioral Research}, \emph{55}(2), 312--328.
+\url{https://doi.org/10.1080/00273171.2019.1633617}
+
+\leavevmode\vadjust pre{\hypertarget{ref-cumming2012}{}}%
+Cumming, G. (2012). \emph{Understanding the new statistics: Effect sizes, confidence intervals, and meta-analysis}. Routledge.
+
+\leavevmode\vadjust pre{\hypertarget{ref-devellis2022}{}}%
+DeVellis, R. F., \& Thorpe, C. T. (2022). \emph{Scale development: Theory and applications} (Fifth edition). SAGE Publications, Inc.
+
+\leavevmode\vadjust pre{\hypertarget{ref-dueber2023}{}}%
+Dueber, D. (2023). \emph{Dmacs}. \url{https://github.com/ddueber/dmacs}
+
+\leavevmode\vadjust pre{\hypertarget{ref-flake2020}{}}%
+Flake, J.
+K., \& Fried, E.
+I.
+(2020).
+Measurement Schmeasurement: Questionable Measurement Practices and How to Avoid Them.
+\emph{Advances in Methods and Practices in Psychological Science}, \emph{3}(4), 456--465.
+\url{https://doi.org/10.1177/2515245920952393}
+
+\leavevmode\vadjust pre{\hypertarget{ref-jin2020}{}}%
+Jin, Y.
+(2020).
+A note on the cutoff values of alternative fit indices to evaluate measurement invariance for ESEM models.
+\emph{International Journal of Behavioral Development}, \emph{44}(2), 166--174.
+\url{https://doi.org/10.1177/0165025419866911}
+
+\leavevmode\vadjust pre{\hypertarget{ref-juxf6reskog1971}{}}%
+Jöreskog, K. G. (1971). Simultaneous factor analysis in several populations. \emph{Psychometrika}, \emph{36}(4), 409--426. \url{https://doi.org/10.1007/BF02291366}
+
+\leavevmode\vadjust pre{\hypertarget{ref-juxf6reskog2001}{}}%
+Jöreskog, K. G., \& Sörbom, D. (2001). \emph{LISREL 8: user's reference guide} (2. ed., updated to LISREL 8). SSI Scientific Software Internat.
+
+\leavevmode\vadjust pre{\hypertarget{ref-kline2016}{}}%
+Kline, R. B. (2016). \emph{Principles and practice of structural equation modeling} (Fourth edition). The Guilford Press.
+
+\leavevmode\vadjust pre{\hypertarget{ref-lakens2017}{}}%
+Lakens, D. (2017). Equivalence Tests. \emph{Social Psychological and Personality Science}, \emph{8}(4), 355--362. \url{https://doi.org/10.1177/1948550617697177}
+
+\leavevmode\vadjust pre{\hypertarget{ref-makel2014}{}}%
+Makel, M.
+C., \& Plucker, J.
+A.
+(2014).
+Facts Are More Important Than Novelty: Replication in the Education Sciences.
+\emph{Educational Researcher}, \emph{43}(6), 304--316.
+\url{https://doi.org/10.3102/0013189X14545513}
+
+\leavevmode\vadjust pre{\hypertarget{ref-makel2012}{}}%
+Makel, M.
+C., Plucker, J.
+A., \& Hegarty, B.
+(2012).
+Replications in Psychology Research: How Often Do They Really Occur?
+\emph{Perspectives on Psychological Science}, \emph{7}(6), 537--542.
+\url{https://doi.org/10.1177/1745691612460688}
+
+\leavevmode\vadjust pre{\hypertarget{ref-marsh2004}{}}%
+Marsh, H.
+W., Hau, K.-T., \& Wen, Z.
+(2004).
+In search of golden rules: Comment on hypothesis-testing approaches to setting cutoff values for fit indexes and dangers in overgeneralizing hu and bentler's (1999) findings.
+\emph{Structural Equation Modeling: A Multidisciplinary Journal}, \emph{11}(3), 320--341.
+\url{https://doi.org/10.1207/s15328007sem1103_2}
+
+\leavevmode\vadjust pre{\hypertarget{ref-meade2008}{}}%
+Meade, A.
+W., Johnson, E.
+C., \& Braddy, P.
+W.
+(2008).
+Power and sensitivity of alternative fit indices in tests of measurement invariance.
+\emph{Journal of Applied Psychology}, \emph{93}(3), 568--592.
+\url{https://doi.org/10.1037/0021-9010.93.3.568}
+
+\leavevmode\vadjust pre{\hypertarget{ref-meredith1993}{}}%
+Meredith, W. (1993). Measurement invariance, factor analysis and factorial invariance. \emph{Psychometrika}, \emph{58}(4), 525--543. \url{https://doi.org/10.1007/BF02294825}
+
+\leavevmode\vadjust pre{\hypertarget{ref-nelson2018}{}}%
+Nelson, L. D., Simmons, J., \& Simonsohn, U. (2018). Psychology's renaissance. \emph{Annual Review of Psychology}, \emph{69}(1), 511--534. \url{https://doi.org/10.1146/annurev-psych-122216-011836}
+
+\leavevmode\vadjust pre{\hypertarget{ref-nye2019}{}}%
+Nye, C.
+D., Bradburn, J., Olenick, J., Bialko, C., \& Drasgow, F.
+(2019).
+How Big Are My Effects?
+Examining the Magnitude of Effect Sizes in Studies of Measurement Equivalence.
+\emph{Organizational Research Methods}, \emph{22}(3), 678--709.
+\url{https://doi.org/10.1177/1094428118761122}
+
+\leavevmode\vadjust pre{\hypertarget{ref-nye2011}{}}%
+Nye, C.
+D., \& Drasgow, F.
+(2011).
+Effect size indices for analyses of measurement equivalence: Understanding the practical importance of differences between groups.
+\emph{Journal of Applied Psychology}, \emph{96}(5), 966--980.
+\url{https://doi.org/10.1037/a0022955}
+
+\leavevmode\vadjust pre{\hypertarget{ref-putnick2016}{}}%
+Putnick, D.
+L., \& Bornstein, M.
+H.
+(2016).
+Measurement invariance conventions and reporting: The state of the art and future directions for psychological research.
+\emph{Developmental Review}, \emph{41}, 71--90.
+\url{https://doi.org/10.1016/j.dr.2016.06.004}
+
+\leavevmode\vadjust pre{\hypertarget{ref-robinson2023}{}}%
+Robinson, D., Hayes, A., Couch {[}aut, S., cre, Software, P., PBC, Patil, I., Chiu, D., Gomez, M., Demeshev, B., Menne, D., Nutter, B., Johnston, L., Bolker, B., Briatte, F., Arnold, J., Gabry, J., Selzer, L., Simpson, G., \ldots{} Reinhart, A.
+(2023).
+\emph{Broom: Convert statistical objects into tidy tibbles}.
+\url{https://CRAN.R-project.org/package=broom}
+
+\leavevmode\vadjust pre{\hypertarget{ref-rosseel2012}{}}%
+Rosseel, Y. (2012). Lavaan: An r package for structural equation modeling. \emph{Journal of Statistical Software}, \emph{48}(1), 1--36. \url{https://doi.org/10.18637/jss.v048.i02}
+
+\leavevmode\vadjust pre{\hypertarget{ref-schwarz1978}{}}%
+Schwarz, G. (1978). Estimating the dimension of a model. \emph{The Annals of Statistics}, \emph{6}(2), 461--464. \url{https://www.jstor.org/stable/2958889}
+
+\leavevmode\vadjust pre{\hypertarget{ref-shadish2001}{}}%
+Shadish, W. R., Cook, T. D., \& Campbell, D. T. (2001). \emph{Experimental and quasi-experimental designs for generalized causal inference}. Houghton Mifflin.
+
+\leavevmode\vadjust pre{\hypertarget{ref-suxf6rbom1978}{}}%
+Sörbom, D. (1978). An alternative to the methodology for analysis of covariance. \emph{Psychometrika}, \emph{43}(3), 381--396. \url{https://doi.org/10.1007/BF02293647}
+
+\leavevmode\vadjust pre{\hypertarget{ref-stark2006}{}}%
+Stark, S., Chernyshenko, O.
+S., \& Drasgow, F.
+(2006).
+Detecting differential item functioning with confirmatory factor analysis and item response theory: Toward a unified strategy.
+\emph{Journal of Applied Psychology}, \emph{91}(6), 1292--1306.
+\url{https://doi.org/10.1037/0021-9010.91.6.1292}
+
+\leavevmode\vadjust pre{\hypertarget{ref-steiger1990}{}}%
+Steiger, J.
+H.
+(1990).
+Structural model evaluation and modification: An interval estimation approach.
+\emph{Multivariate Behavioral Research}, \emph{25}(2), 173--180.
+\url{https://doi.org/10.1207/s15327906mbr2502_4}
+
+\leavevmode\vadjust pre{\hypertarget{ref-tay2015}{}}%
+Tay, L., Meade, A.
+W., \& Cao, M.
+(2015).
+An Overview and Practical Guide to IRT Measurement Equivalence Analysis.
+\emph{Organizational Research Methods}, \emph{18}(1), 3--46.
+\url{https://doi.org/10.1177/1094428114553062}
+
+\leavevmode\vadjust pre{\hypertarget{ref-thompson1996}{}}%
+Thompson, B., \& Daniel, L.
+G.
+(1996).
+Factor Analytic Evidence for the Construct Validity of Scores: A Historical Overview and Some Guidelines.
+\emph{Educational and Psychological Measurement}, \emph{56}(2), 197--208.
+\url{https://doi.org/10.1177/0013164496056002001}
+
+\leavevmode\vadjust pre{\hypertarget{ref-trent2013}{}}%
+Trent, L.
+R., Buchanan, E., Ebesutani, C., Ale, C.
+M., Heiden, L., Hight, T.
+L., Damon, J.
+D., \& Young, J.
+(2013).
+A measurement invariance examination of the revised child anxiety and depression scale in a southern sample: Differential item functioning between african american and caucasian youth.
+\emph{Assessment}, \emph{20}(2), 175--187.
+\url{https://doi.org/10.1177/1073191112450907}
+
+\leavevmode\vadjust pre{\hypertarget{ref-tucker1973}{}}%
+Tucker, L. R., \& Lewis, C. (1973). A reliability coefficient for maximum likelihood factor analysis. \emph{Psychometrika}, \emph{38}(1), 1--10. \url{https://doi.org/10.1007/BF02291170}
+
+\leavevmode\vadjust pre{\hypertarget{ref-vandeschoot2015}{}}%
+Van De Schoot, R., Schmidt, P., De Beuckelaer, A., Lek, K., \& Zondervan-Zwijnenburg, M.
+(2015).
+Editorial: Measurement invariance.
+\emph{Frontiers in Psychology}, \emph{6}.
+\url{https://www.frontiersin.org/articles/10.3389/fpsyg.2015.01064}
+
+\leavevmode\vadjust pre{\hypertarget{ref-vazire2022}{}}%
+Vazire, S., Schiavone, S.
+R., \& Bottesini, J.
+G.
+(2022).
+Credibility Beyond Replicability: Improving the Four Validities in Psychological Science.
+\emph{Current Directions in Psychological Science}, \emph{31}(2), 162--168.
+\url{https://doi.org/10.1177/09637214211067779}
+
+\leavevmode\vadjust pre{\hypertarget{ref-wagnild2009}{}}%
+Wagnild, G. (2009). A review of the resilience scale. \emph{Journal of Nursing Measurement}, \emph{17}(2), 105--113. \url{https://doi.org/10.1891/1061-3749.17.2.105}
+
+\leavevmode\vadjust pre{\hypertarget{ref-weidman2017}{}}%
+Weidman, A.
+C., Steckler, C.
+M., \& Tracy, J.
+L.
+(2017).
+The jingle and jangle of emotion assessment: Imprecise measurement, casual scale usage, and conceptual fuzziness in emotion research.
+\emph{Emotion}, \emph{17}(2), 267--295.
+\url{https://doi.org/10.1037/emo0000226}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-ggplot2}{}}%
+Wickham, H. (2016). \emph{ggplot2: Elegant graphics for data analysis}. Springer-Verlag New York. \url{https://ggplot2.tidyverse.org}
+
+\leavevmode\vadjust pre{\hypertarget{ref-wilke2020}{}}%
+Wilke, C. O. (2020). \emph{Cowplot: Streamlined plot theme and plot annotations for 'ggplot2'}. \url{https://CRAN.R-project.org/package=cowplot}
+
+\leavevmode\vadjust pre{\hypertarget{ref-zwaan2018}{}}%
+Zwaan, R. A., Etz, A., Lucas, R. E., \& Donnellan, M. B. (2018). Making replication mainstream. \emph{Behavioral and Brain Sciences}, \emph{41}, e120. \url{https://doi.org/10.1017/S0140525X17001972}
+
+\end{CSLReferences}
 
@@
 
-# Appendix
-
-## Model Fit Statistics
-
-Model fit statistics are provided for each of the ten model combinations (invariant, three sizes for each ladings, intercepts, and residuals).
-These tables could be used to examine the traditional change in fit statistics cutoff rules of thumb [@cheung2002], such as $\Delta$ CFI or $\Delta$ RMSEA, to the visualizations presented in the manuscript.
-
-\begin{table}[tbp]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:tab1}Model Fit for Invariant Model}
-
-\begin{tabular}{lllllll}
-\toprule
-Model & AIC & BIC & CFI & TLI & RMSEA & SRMR\\
-\midrule
-Overall & 7,515.72 & 7,578.94 & 0.99 & 0.99 & 0.02 & 0.02\\
-Group 1 & 3,765.75 & 3,818.57 & 0.98 & 0.95 & 0.05 & 0.03\\
-Group 2 & 3,761.95 & 3,814.77 & 0.98 & 0.96 & 0.04 & 0.03\\
-Configural & 7,527.70 & 7,654.14 & 0.98 & 0.96 & 0.04 & 0.03\\
-Metric & 7,529.39 & 7,638.97 & 0.95 & 0.93 & 0.06 & 0.05\\
-Scalar & 7,522.90 & 7,615.62 & 0.96 & 0.96 & 0.04 & 0.05\\
-Strict & 7,519.51 & 7,591.16 & 0.96 & 0.96 & 0.04 & 0.06\\
-\bottomrule
-\end{tabular}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-\begin{table}[tbp]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:tab2}Model Fit for Small Differences in Loadings}
-
-\begin{tabular}{lllllll}
-\toprule
-Model & AIC & BIC & CFI & TLI & RMSEA & SRMR\\
-\midrule
-Overall & 7,537.67 & 7,600.89 & 0.98 & 0.96 & 0.04 & 0.02\\
-Group 1 & 3,765.75 & 3,818.57 & 0.98 & 0.95 & 0.05 & 0.03\\
-Group 2 & 3,777.83 & 3,830.66 & 0.98 & 0.96 & 0.05 & 0.03\\
-Configural & 7,543.58 & 7,670.02 & 0.98 & 0.95 & 0.05 & 0.03\\
-Metric & 7,548.90 & 7,658.48 & 0.94 & 0.92 & 0.07 & 0.06\\
-Scalar & 7,541.81 & 7,634.53 & 0.95 & 0.95 & 0.05 & 0.06\\
-Strict & 7,541.66 & 7,613.31 & 0.93 & 0.94 & 0.05 & 0.07\\
-\bottomrule
-\end{tabular}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-\begin{table}[tbp]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:tab3}Model Fit for Medium Differences in Loadings}
-
-\begin{tabular}{lllllll}
-\toprule
-Model & AIC & BIC & CFI & TLI & RMSEA & SRMR\\
-\midrule
-Overall & 7,554.55 & 7,617.77 & 0.97 & 0.94 & 0.05 & 0.03\\
-Group 1 & 3,765.75 & 3,818.57 & 0.98 & 0.95 & 0.05 & 0.03\\
-Group 2 & 3,784.92 & 3,837.74 & 1.00 & 1.00 & 0.02 & 0.02\\
-Configural & 7,550.67 & 7,677.11 & 0.99 & 0.98 & 0.04 & 0.03\\
-Metric & 7,562.71 & 7,672.29 & 0.93 & 0.89 & 0.07 & 0.06\\
-Scalar & 7,556.86 & 7,649.58 & 0.93 & 0.93 & 0.06 & 0.06\\
-Strict & 7,558.05 & 7,629.70 & 0.91 & 0.92 & 0.06 & 0.08\\
-\bottomrule
-\end{tabular}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-\begin{table}[tbp]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:tab4}Model Fit for Large Differences in Loadings}
-
-\begin{tabular}{lllllll}
-\toprule
-Model & AIC & BIC & CFI & TLI & RMSEA & SRMR\\
-\midrule
-Overall & 7,662.99 & 7,726.21 & 0.98 & 0.97 & 0.04 & 0.02\\
-Group 1 & 3,765.75 & 3,818.57 & 0.98 & 0.95 & 0.05 & 0.03\\
-Group 2 & 3,857.21 & 3,910.03 & 0.97 & 0.94 & 0.08 & 0.03\\
-Configural & 7,622.96 & 7,749.40 & 0.97 & 0.94 & 0.06 & 0.03\\
-Metric & 7,659.19 & 7,768.77 & 0.85 & 0.79 & 0.12 & 0.08\\
-Scalar & 7,652.60 & 7,745.32 & 0.86 & 0.85 & 0.10 & 0.09\\
-Strict & 7,660.63 & 7,732.27 & 0.82 & 0.85 & 0.10 & 0.12\\
-\bottomrule
-\end{tabular}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-\begin{table}[tbp]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:tab5}Model Fit for Small Differences in Intercepts}
-
-\begin{tabular}{lllllll}
-\toprule
-Model & AIC & BIC & CFI & TLI & RMSEA & SRMR\\
-\midrule
-Overall & 7,519.69 & 7,582.91 & 1.00 & 0.99 & 0.02 & 0.02\\
-Group 1 & 3,765.75 & 3,818.57 & 0.98 & 0.95 & 0.05 & 0.03\\
-Group 2 & 3,770.41 & 3,823.23 & 0.93 & 0.86 & 0.08 & 0.04\\
-Configural & 7,536.16 & 7,662.60 & 0.95 & 0.91 & 0.07 & 0.04\\
-Metric & 7,531.36 & 7,640.94 & 0.96 & 0.94 & 0.05 & 0.04\\
-Scalar & 7,531.34 & 7,624.06 & 0.94 & 0.93 & 0.06 & 0.05\\
-Strict & 7,523.54 & 7,595.18 & 0.95 & 0.96 & 0.04 & 0.05\\
-\bottomrule
-\end{tabular}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-\begin{table}[tbp]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:tab6}Model Fit for Medium Differences in Intercepts}
-
-\begin{tabular}{lllllll}
-\toprule
-Model & AIC & BIC & CFI & TLI & RMSEA & SRMR\\
-\midrule
-Overall & 7,542.77 & 7,605.99 & 1.00 & 1.00 & 0.01 & 0.02\\
-Group 1 & 3,765.75 & 3,818.57 & 0.98 & 0.95 & 0.05 & 0.03\\
-Group 2 & 3,770.41 & 3,823.23 & 0.93 & 0.86 & 0.08 & 0.04\\
-Configural & 7,536.16 & 7,662.60 & 0.95 & 0.91 & 0.07 & 0.04\\
-Metric & 7,531.36 & 7,640.94 & 0.96 & 0.94 & 0.05 & 0.04\\
-Scalar & 7,554.20 & 7,646.92 & 0.85 & 0.83 & 0.09 & 0.07\\
-Strict & 7,546.38 & 7,618.03 & 0.86 & 0.88 & 0.08 & 0.07\\
-\bottomrule
-\end{tabular}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-\begin{table}[tbp]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:tab7}Model Fit for Large Differences in Intercepts}
-
-\begin{tabular}{lllllll}
-\toprule
-Model & AIC & BIC & CFI & TLI & RMSEA & SRMR\\
-\midrule
-Overall & 7,579.17 & 7,642.39 & 1.00 & 1.00 & 0.00 & 0.02\\
-Group 1 & 3,765.75 & 3,818.57 & 0.98 & 0.95 & 0.05 & 0.03\\
-Group 2 & 3,770.41 & 3,823.23 & 0.93 & 0.86 & 0.08 & 0.04\\
-Configural & 7,536.16 & 7,662.60 & 0.95 & 0.91 & 0.07 & 0.04\\
-Metric & 7,531.36 & 7,640.94 & 0.96 & 0.94 & 0.05 & 0.04\\
-Scalar & 7,590.29 & 7,683.01 & 0.70 & 0.66 & 0.13 & 0.10\\
-Strict & 7,582.47 & 7,654.12 & 0.71 & 0.75 & 0.11 & 0.10\\
-\bottomrule
-\end{tabular}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-\begin{table}[tbp]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:tab8}Model Fit for Small Differences in Residuals}
-
-\begin{tabular}{lllllll}
-\toprule
-Model & AIC & BIC & CFI & TLI & RMSEA & SRMR\\
-\midrule
-Overall & 7,449.49 & 7,512.71 & 1.00 & 1.01 & 0.00 & 0.01\\
-Group 1 & 3,765.75 & 3,818.57 & 0.98 & 0.95 & 0.05 & 0.03\\
-Group 2 & 3,693.32 & 3,746.14 & 1.00 & 1.01 & 0.00 & 0.02\\
-Configural & 7,459.07 & 7,585.51 & 0.99 & 0.98 & 0.03 & 0.03\\
-Metric & 7,461.41 & 7,570.99 & 0.97 & 0.95 & 0.05 & 0.05\\
-Scalar & 7,455.85 & 7,548.58 & 0.97 & 0.97 & 0.04 & 0.05\\
-Strict & 7,453.48 & 7,525.12 & 0.96 & 0.97 & 0.04 & 0.05\\
-\bottomrule
-\end{tabular}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-\begin{table}[tbp]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:tab9}Model Fit for Medium Differences in Residuals}
-
-\begin{tabular}{lllllll}
-\toprule
-Model & AIC & BIC & CFI & TLI & RMSEA & SRMR\\
-\midrule
-Overall & 7,378.57 & 7,441.79 & 1.00 & 1.00 & 0.00 & 0.02\\
-Group 1 & 3,765.75 & 3,818.57 & 0.98 & 0.95 & 0.05 & 0.03\\
-Group 2 & 3,597.77 & 3,650.60 & 1.00 & 1.03 & 0.00 & 0.02\\
-Configural & 7,363.52 & 7,489.96 & 1.00 & 0.99 & 0.02 & 0.02\\
-Metric & 7,366.63 & 7,476.21 & 0.97 & 0.96 & 0.05 & 0.05\\
-Scalar & 7,360.15 & 7,452.87 & 0.98 & 0.98 & 0.03 & 0.05\\
-Strict & 7,382.53 & 7,454.18 & 0.88 & 0.90 & 0.08 & 0.07\\
-\bottomrule
-\end{tabular}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-\begin{table}[tbp]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:tab10}Model Fit for Large Differences in Residuals}
-
-\begin{tabular}{lllllll}
-\toprule
-Model & AIC & BIC & CFI & TLI & RMSEA & SRMR\\
-\midrule
-Overall & 7,294.21 & 7,357.43 & 1.00 & 1.01 & 0.00 & 0.01\\
-Group 1 & 3,765.75 & 3,818.57 & 0.98 & 0.95 & 0.05 & 0.03\\
-Group 2 & 3,453.47 & 3,506.29 & 0.95 & 0.90 & 0.07 & 0.03\\
-Configural & 7,219.22 & 7,345.66 & 0.96 & 0.92 & 0.06 & 0.03\\
-Metric & 7,216.38 & 7,325.96 & 0.96 & 0.94 & 0.05 & 0.04\\
-Scalar & 7,210.65 & 7,303.37 & 0.96 & 0.96 & 0.04 & 0.05\\
-Strict & 7,297.89 & 7,369.54 & 0.59 & 0.65 & 0.13 & 0.18\\
-\bottomrule
-\end{tabular}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-## MGCFA Convenience Function
+\hypertarget{appendix}{%
+\section{Appendix}\label{appendix}}
+
+\hypertarget{mgcfa-convenience-function}{%
+\subsection{MGCFA Convenience Function}\label{mgcfa-convenience-function}}
 
@@
 
-```r
-library(lavaan)
-library(dplyr)
-library(broom)
-# CFA function
-mgcfa <- function(data, group, model){
-
-  group_names <- unique(data[ , group])
-  data$group <- data[ , group]
-
-  model.overall <- cfa(model = model, data = data)
-  model.group1 <- cfa(model = model, 
-                      data = subset(data, group == group_names[1]))
-  model.group2 <- cfa(model = model, 
-                      data = subset(data, group == group_names[2]))
-  model.configural <- cfa(model = model, data = data, 
-                          group = group, meanstructure = T)
-  model.metric <- cfa(model = model, data = data, 
-                      group = group, meanstructure = T,
-                      group.equal = "loadings")
-  model.scalar <- cfa(model = model, data = data, 
-                      group = group, meanstructure = T, 
-                      group.equal = c("loadings", "intercepts"))
-  model.strict <- cfa(model = model, data = data, 
-                      group = group, meanstructure = T, 
-                      group.equal =  c("loadings", "intercepts", "residuals"))
-
-  model_coef <- bind_rows(
-    tidy(model.overall, conf.level = .95) %>% 
-      mutate(model = "Overall"), 
-    tidy(model.group1, conf.level = .95) %>% 
-      mutate(model = "Group 1"), 
-    tidy(model.group2, conf.level = .95) %>% 
-      mutate(model = "Group 2"), 
-    tidy(model.configural, conf.level = .95) %>% 
-      mutate(model = "Configural"), 
-    tidy(model.metric, conf.level = .95) %>% 
-      mutate(model = "Metric"), 
-    tidy(model.scalar, conf.level = .95) %>% 
-      mutate(model = "Scalar"), 
-    tidy(model.strict, conf.level = .95) %>% 
-      mutate(model = "Strict")
-  )
-
-  model_fit <- bind_rows(
-    glance(model.overall) %>% mutate(model = "Overall"), 
-    glance(model.group1) %>% mutate(model = "Group 1"), 
-    glance(model.group2) %>% mutate(model = "Group 2"), 
-    glance(model.configural) %>% mutate(model = "Configural"), 
-    glance(model.metric) %>% mutate(model = "Metric"), 
-    glance(model.scalar) %>% mutate(model = "Scalar"), 
-    glance(model.strict) %>% mutate(model = "Strict")
-    )
-
-  return(list(
-    "model_coef" = model_coef,
-    "model_fit" = model_fit,
-    "model.overall" = model.overall,
-    "model.group1" = model.group1,
-    "model.group2" = model.group2,
-    "model.configural" = model.configural,
-    "model.metric" = model.metric,
-    "model.scalar" = model.scalar,
-    "model.strict" = model.strict
-  ))
-
-}
-\end{verbatim}
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{library}\NormalTok{(lavaan)}
+\FunctionTok{library}\NormalTok{(dplyr)}
+\FunctionTok{library}\NormalTok{(broom)}
+\CommentTok{\# CFA function}
+\NormalTok{mgcfa }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(data, group, model)\{}
+
+\NormalTok{  group\_names }\OtherTok{\textless{}{-}} \FunctionTok{unique}\NormalTok{(data[ , group])}
+\NormalTok{  data}\SpecialCharTok{$}\NormalTok{group }\OtherTok{\textless{}{-}}\NormalTok{ data[ , group]}
+
+\NormalTok{  model.overall }\OtherTok{\textless{}{-}} \FunctionTok{cfa}\NormalTok{(}\AttributeTok{model =}\NormalTok{ model, }\AttributeTok{data =}\NormalTok{ data, }
+                       \AttributeTok{meanstructure =}\NormalTok{ T)}
+\NormalTok{  model.group1 }\OtherTok{\textless{}{-}} \FunctionTok{cfa}\NormalTok{(}\AttributeTok{model =}\NormalTok{ model, }
+                      \AttributeTok{data =} \FunctionTok{subset}\NormalTok{(data, group }\SpecialCharTok{==}\NormalTok{ group\_names[}\DecValTok{1}\NormalTok{]),}
+                      \AttributeTok{meanstructure =}\NormalTok{ T)}
+\NormalTok{  model.group2 }\OtherTok{\textless{}{-}} \FunctionTok{cfa}\NormalTok{(}\AttributeTok{model =}\NormalTok{ model, }
+                      \AttributeTok{data =} \FunctionTok{subset}\NormalTok{(data, group }\SpecialCharTok{==}\NormalTok{ group\_names[}\DecValTok{2}\NormalTok{]),}
+                      \AttributeTok{meanstructure =}\NormalTok{ T)}
+\NormalTok{  model.configural }\OtherTok{\textless{}{-}} \FunctionTok{cfa}\NormalTok{(}\AttributeTok{model =}\NormalTok{ model, }\AttributeTok{data =}\NormalTok{ data, }
+                          \AttributeTok{group =}\NormalTok{ group, }\AttributeTok{meanstructure =}\NormalTok{ T)}
+\NormalTok{  model.metric }\OtherTok{\textless{}{-}} \FunctionTok{cfa}\NormalTok{(}\AttributeTok{model =}\NormalTok{ model, }\AttributeTok{data =}\NormalTok{ data, }
+                      \AttributeTok{group =}\NormalTok{ group, }\AttributeTok{meanstructure =}\NormalTok{ T,}
+                      \AttributeTok{group.equal =} \StringTok{"loadings"}\NormalTok{)}
+\NormalTok{  model.scalar }\OtherTok{\textless{}{-}} \FunctionTok{cfa}\NormalTok{(}\AttributeTok{model =}\NormalTok{ model, }\AttributeTok{data =}\NormalTok{ data, }
+                      \AttributeTok{group =}\NormalTok{ group, }\AttributeTok{meanstructure =}\NormalTok{ T, }
+                      \AttributeTok{group.equal =} \FunctionTok{c}\NormalTok{(}\StringTok{"loadings"}\NormalTok{, }\StringTok{"intercepts"}\NormalTok{))}
+\NormalTok{  model.strict }\OtherTok{\textless{}{-}} \FunctionTok{cfa}\NormalTok{(}\AttributeTok{model =}\NormalTok{ model, }\AttributeTok{data =}\NormalTok{ data, }
+                      \AttributeTok{group =}\NormalTok{ group, }\AttributeTok{meanstructure =}\NormalTok{ T, }
+                      \AttributeTok{group.equal =}  \FunctionTok{c}\NormalTok{(}\StringTok{"loadings"}\NormalTok{, }\StringTok{"intercepts"}\NormalTok{, }\StringTok{"residuals"}\NormalTok{))}
+
+\NormalTok{  model\_coef }\OtherTok{\textless{}{-}} \FunctionTok{bind\_rows}\NormalTok{(}
+    \FunctionTok{tidy}\NormalTok{(model.overall, }\AttributeTok{conf.level =}\NormalTok{ .}\DecValTok{95}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
+      \FunctionTok{mutate}\NormalTok{(}\AttributeTok{model =} \StringTok{"Overall"}\NormalTok{), }
+    \FunctionTok{tidy}\NormalTok{(model.group1, }\AttributeTok{conf.level =}\NormalTok{ .}\DecValTok{95}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
+      \FunctionTok{mutate}\NormalTok{(}\AttributeTok{model =} \StringTok{"Group 1"}\NormalTok{), }
+    \FunctionTok{tidy}\NormalTok{(model.group2, }\AttributeTok{conf.level =}\NormalTok{ .}\DecValTok{95}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
+      \FunctionTok{mutate}\NormalTok{(}\AttributeTok{model =} \StringTok{"Group 2"}\NormalTok{), }
+    \FunctionTok{tidy}\NormalTok{(model.configural, }\AttributeTok{conf.level =}\NormalTok{ .}\DecValTok{95}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
+      \FunctionTok{mutate}\NormalTok{(}\AttributeTok{model =} \StringTok{"Configural"}\NormalTok{), }
+    \FunctionTok{tidy}\NormalTok{(model.metric, }\AttributeTok{conf.level =}\NormalTok{ .}\DecValTok{95}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
+      \FunctionTok{mutate}\NormalTok{(}\AttributeTok{model =} \StringTok{"Metric"}\NormalTok{), }
+    \FunctionTok{tidy}\NormalTok{(model.scalar, }\AttributeTok{conf.level =}\NormalTok{ .}\DecValTok{95}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
+      \FunctionTok{mutate}\NormalTok{(}\AttributeTok{model =} \StringTok{"Scalar"}\NormalTok{), }
+    \FunctionTok{tidy}\NormalTok{(model.strict, }\AttributeTok{conf.level =}\NormalTok{ .}\DecValTok{95}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
+      \FunctionTok{mutate}\NormalTok{(}\AttributeTok{model =} \StringTok{"Strict"}\NormalTok{)}
+\NormalTok{  )}
+
+\NormalTok{  model\_fit }\OtherTok{\textless{}{-}} \FunctionTok{bind\_rows}\NormalTok{(}
+    \FunctionTok{glance}\NormalTok{(model.overall) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{mutate}\NormalTok{(}\AttributeTok{model =} \StringTok{"Overall"}\NormalTok{), }
+    \FunctionTok{glance}\NormalTok{(model.group1) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{mutate}\NormalTok{(}\AttributeTok{model =} \StringTok{"Group 1"}\NormalTok{), }
+    \FunctionTok{glance}\NormalTok{(model.group2) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{mutate}\NormalTok{(}\AttributeTok{model =} \StringTok{"Group 2"}\NormalTok{), }
+    \FunctionTok{glance}\NormalTok{(model.configural) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{mutate}\NormalTok{(}\AttributeTok{model =} \StringTok{"Configural"}\NormalTok{), }
+    \FunctionTok{glance}\NormalTok{(model.metric) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{mutate}\NormalTok{(}\AttributeTok{model =} \StringTok{"Metric"}\NormalTok{), }
+    \FunctionTok{glance}\NormalTok{(model.scalar) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{mutate}\NormalTok{(}\AttributeTok{model =} \StringTok{"Scalar"}\NormalTok{), }
+    \FunctionTok{glance}\NormalTok{(model.strict) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{mutate}\NormalTok{(}\AttributeTok{model =} \StringTok{"Strict"}\NormalTok{)}
+\NormalTok{    )}
+
+  \FunctionTok{return}\NormalTok{(}\FunctionTok{list}\NormalTok{(}
+    \StringTok{"model\_coef"} \OtherTok{=}\NormalTok{ model\_coef,}
+    \StringTok{"model\_fit"} \OtherTok{=}\NormalTok{ model\_fit,}
+    \StringTok{"model.overall"} \OtherTok{=}\NormalTok{ model.overall,}
+    \StringTok{"model.group1"} \OtherTok{=}\NormalTok{ model.group1,}
+    \StringTok{"model.group2"} \OtherTok{=}\NormalTok{ model.group2,}
+    \StringTok{"model.configural"} \OtherTok{=}\NormalTok{ model.configural,}
+    \StringTok{"model.metric"} \OtherTok{=}\NormalTok{ model.metric,}
+    \StringTok{"model.scalar"} \OtherTok{=}\NormalTok{ model.scalar,}
+    \StringTok{"model.strict"} \OtherTok{=}\NormalTok{ model.strict}
+\NormalTok{  ))}
+
+\NormalTok{\}}
+\end{Highlighting}
+\end{Shaded}
 
@@
   \FunctionTok{filter}\NormalTok{(}\FunctionTok{grepl}\NormalTok{(item\_name, term)) }\SpecialCharTok{\%\textgreater{}\%}  \CommentTok{\# pick a question}
-  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{group =} \FunctionTok{factor}\NormalTok{(group, }\AttributeTok{levels =} \FunctionTok{names}\NormalTok{(}\FunctionTok{table}\NormalTok{(data\_coef}\SpecialCharTok{$}\NormalTok{group)), }\AttributeTok{labels =}\NormalTok{ group\_labels)) }
+  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{group =} \FunctionTok{factor}\NormalTok{(group, }\AttributeTok{levels =} \FunctionTok{names}\NormalTok{(}\FunctionTok{table}\NormalTok{(data\_coef}\SpecialCharTok{$}\NormalTok{group)), }
+                        \AttributeTok{labels =}\NormalTok{ group\_labels)) }
 
@@
 
-  \CommentTok{\# get the lengend}
+  \CommentTok{\# get the legend}
 \NormalTok{  legend\_b }\OtherTok{\textless{}{-}} \FunctionTok{get\_legend}\NormalTok{(}
@@
 
-\hypertarget{refs}{}
-\begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-aiena2014}{}}%
-Aiena, B.
-J., Baczwaski, B.
-J., Schulenberg, S.
-E., \& Buchanan, E.
-M.
-(2014).
-Measuring Resilience With the RS{\textendash}14: A Tale of Two Samples.
-\emph{Journal of Personality Assessment}, \emph{97}(3), 291--300.
-\url{https://doi.org/10.1080/00223891.2014.951445}
-
-\leavevmode\vadjust pre{\hypertarget{ref-akaike1998}{}}%
-Akaike, H.
-(1998).
-\emph{Information theory and an extension of the maximum likelihood principle} (E.
-Parzen, K.
-Tanabe, \& G.
-Kitagawa, Eds.).
-New York, NY: Springer New York.
-Retrieved from \url{http://link.springer.com/10.1007/978-1-4612-1694-0_15}
-
-\leavevmode\vadjust pre{\hypertarget{ref-anvari2021}{}}%
-Anvari, F., \& Lakens, D.
-(2021).
-Using anchor-based methods to determine the smallest effect size of interest.
-\emph{Journal of Experimental Social Psychology}, \emph{96}, 104159.
-\url{https://doi.org/10.1016/j.jesp.2021.104159}
-
-\leavevmode\vadjust pre{\hypertarget{ref-barry2014}{}}%
-Barry, A.
-E., Chaney, B., Piazza-Gardner, A.
-K., \& Chavarria, E.
-A.
-(2014).
-Validity and Reliability Reporting Practices in the Field of Health Education and Behavior: A Review of Seven Journals.
-\emph{Health Education \& Behavior}, \emph{41}(1), 12--18.
-\url{https://doi.org/10.1177/1090198113483139}
-
-\leavevmode\vadjust pre{\hypertarget{ref-beaujean2014}{}}%
-Beaujean, A. A. (2014). \emph{Latent variable modeling using r: A step by step guide}. New York: Routledge/Taylor \& Francis Group.
-
-\leavevmode\vadjust pre{\hypertarget{ref-bentler1990}{}}%
-Bentler, P. M. (1990). Comparative fit indexes in structural models. \emph{Psychological Bulletin}, \emph{107}(2), 238--246. \url{https://doi.org/10.1037/0033-2909.107.2.238}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bentler1995}{}}%
-Bentler, P. M. (1995). \emph{EQS structural equations program manual}. Encino, CA.
-
-\leavevmode\vadjust pre{\hypertarget{ref-boker2011}{}}%
-Boker, S., Neale, M., Maes, H., Wilde, M., Spiegel, M., Brick, T., \ldots{} Fox, J.
-(2011).
-OpenMx: An Open Source Extended Structural Equation Modeling Framework.
-\emph{Psychometrika}, \emph{76}(2), 306--317.
-\url{https://doi.org/10.1007/s11336-010-9200-6}
-
-\leavevmode\vadjust pre{\hypertarget{ref-brown2015}{}}%
-Brown, T. A. (2015). \emph{Confirmatory factor analysis for applied research} (Second edition). New York ; London: The Guilford Press.
-
-\leavevmode\vadjust pre{\hypertarget{ref-byrne2001}{}}%
-Byrne, B.
-M.
-(2001).
-Structural Equation Modeling With AMOS, EQS, and LISREL: Comparative Approaches to Testing for the Factorial Validity of a Measuring Instrument.
-\emph{International Journal of Testing}, \emph{1}(1), 55--86.
-\url{https://doi.org/10.1207/S15327574IJT0101_4}
-
-\leavevmode\vadjust pre{\hypertarget{ref-byrne1989}{}}%
-Byrne, B.
-M., Shavelson, R.
-J., \& Muthén, B.
-(1989).
-Testing for the equivalence of factor covariance and mean structures: The issue of partial measurement invariance.
-\emph{Psychological Bulletin}, \emph{105}(3), 456--466.
-\url{https://doi.org/10.1037/0033-2909.105.3.456}
-
-\leavevmode\vadjust pre{\hypertarget{ref-cheung2002}{}}%
-Cheung, G.
-W., \& Rensvold, R.
-B.
-(2002).
-Evaluating Goodness-of-Fit Indexes for Testing Measurement Invariance.
-\emph{Structural Equation Modeling: A Multidisciplinary Journal}, \emph{9}(2), 233--255.
-\url{https://doi.org/10.1207/s15328007sem0902_5}
-
-\leavevmode\vadjust pre{\hypertarget{ref-chorpita2000}{}}%
-Chorpita, B.
-F., Yim, L., Moffitt, C., Umemoto, L.
-A., \& Francis, S.
-E.
-(2000).
-Assessment of symptoms of DSM-IV anxiety and depression in children: a revised child anxiety and depression scale.
-\emph{Behaviour Research and Therapy}, \emph{38}(8), 835--855.
-\url{https://doi.org/10.1016/S0005-7967(99)00130-8}
-
-\leavevmode\vadjust pre{\hypertarget{ref-cohen2003}{}}%
-Cohen, J., Cohen, P., West, S. G., \& Aiken, L. (2003). \emph{Applied multiple regression / correlation analysis for the behavioral sciences} (3rd ed.). Lawrence Erlbaum Associates.
-
-\leavevmode\vadjust pre{\hypertarget{ref-devellis2022}{}}%
-DeVellis, R. F., \& Thorpe, C. T. (2022). \emph{Scale development: Theory and applications} (Fifth edition). Thousand Oaks, California: SAGE Publications, Inc.
-
-\leavevmode\vadjust pre{\hypertarget{ref-dueber2023}{}}%
-Dueber, D. (2023). \emph{Dmacs}. Retrieved from \url{https://github.com/ddueber/dmacs}
-
-\leavevmode\vadjust pre{\hypertarget{ref-flake2020}{}}%
-Flake, J.
-K., \& Fried, E.
-I.
-(2020).
-Measurement Schmeasurement: Questionable Measurement Practices and How to Avoid Them.
-\emph{Advances in Methods and Practices in Psychological Science}, \emph{3}(4), 456--465.
-\url{https://doi.org/10.1177/2515245920952393}
-
-\leavevmode\vadjust pre{\hypertarget{ref-juxf6reskog1971}{}}%
-Jöreskog, K. G. (1971). Simultaneous factor analysis in several populations. \emph{Psychometrika}, \emph{36}(4), 409--426. \url{https://doi.org/10.1007/BF02291366}
-
-\leavevmode\vadjust pre{\hypertarget{ref-juxf6reskog2001}{}}%
-Jöreskog, Karl G., \& Sörbom, D. (2001). \emph{LISREL 8: user's reference guide} (2. ed., updated to LISREL 8). Lincolnwood, Ill: SSI Scientific Software Internat.
-
-\leavevmode\vadjust pre{\hypertarget{ref-kline2016}{}}%
-Kline, R. B. (2016). \emph{Principles and practice of structural equation modeling} (Fourth edition). New York: The Guilford Press.
-
-\leavevmode\vadjust pre{\hypertarget{ref-lakens2017}{}}%
-Lakens, D. (2017). Equivalence Tests. \emph{Social Psychological and Personality Science}, \emph{8}(4), 355--362. \url{https://doi.org/10.1177/1948550617697177}
-
-\leavevmode\vadjust pre{\hypertarget{ref-makel2014}{}}%
-Makel, M.
-C., \& Plucker, J.
-A.
-(2014).
-Facts Are More Important Than Novelty: Replication in the Education Sciences.
-\emph{Educational Researcher}, \emph{43}(6), 304--316.
-\url{https://doi.org/10.3102/0013189X14545513}
-
-\leavevmode\vadjust pre{\hypertarget{ref-makel2012}{}}%
-Makel, M.
-C., Plucker, J.
-A., \& Hegarty, B.
-(2012).
-Replications in Psychology Research: How Often Do They Really Occur?
-\emph{Perspectives on Psychological Science}, \emph{7}(6), 537--542.
-\url{https://doi.org/10.1177/1745691612460688}
-
-\leavevmode\vadjust pre{\hypertarget{ref-marsh2004}{}}%
-Marsh, H.
-W., Hau, K.-T., \& Wen, Z.
-(2004).
-In search of golden rules: Comment on hypothesis-testing approaches to setting cutoff values for fit indexes and dangers in overgeneralizing hu and bentler's (1999) findings.
-\emph{Structural Equation Modeling: A Multidisciplinary Journal}, \emph{11}(3), 320--341.
-\url{https://doi.org/10.1207/s15328007sem1103_2}
-
-\leavevmode\vadjust pre{\hypertarget{ref-meade2008}{}}%
-Meade, A.
-W., Johnson, E.
-C., \& Braddy, P.
-W.
-(2008).
-Power and sensitivity of alternative fit indices in tests of measurement invariance.
-\emph{Journal of Applied Psychology}, \emph{93}(3), 568--592.
-\url{https://doi.org/10.1037/0021-9010.93.3.568}
-
-\leavevmode\vadjust pre{\hypertarget{ref-meredith1993}{}}%
-Meredith, W. (1993). Measurement invariance, factor analysis and factorial invariance. \emph{Psychometrika}, \emph{58}(4), 525--543. \url{https://doi.org/10.1007/BF02294825}
-
-\leavevmode\vadjust pre{\hypertarget{ref-nelson2018}{}}%
-Nelson, L. D., Simmons, J., \& Simonsohn, U. (2018). Psychology's renaissance. \emph{Annual Review of Psychology}, \emph{69}(1), 511--534. \url{https://doi.org/10.1146/annurev-psych-122216-011836}
-
-\leavevmode\vadjust pre{\hypertarget{ref-nye2019}{}}%
-Nye, C.
-D., Bradburn, J., Olenick, J., Bialko, C., \& Drasgow, F.
-(2019).
-How Big Are My Effects?
-Examining the Magnitude of Effect Sizes in Studies of Measurement Equivalence.
-\emph{Organizational Research Methods}, \emph{22}(3), 678--709.
-\url{https://doi.org/10.1177/1094428118761122}
-
-\leavevmode\vadjust pre{\hypertarget{ref-nye2011}{}}%
-Nye, C.
-D., \& Drasgow, F.
-(2011).
-Effect size indices for analyses of measurement equivalence: Understanding the practical importance of differences between groups.
-\emph{Journal of Applied Psychology}, \emph{96}(5), 966--980.
-\url{https://doi.org/10.1037/a0022955}
-
-\leavevmode\vadjust pre{\hypertarget{ref-putnick2016}{}}%
-Putnick, D.
-L., \& Bornstein, M.
-H.
-(2016).
-Measurement invariance conventions and reporting: The state of the art and future directions for psychological research.
-\emph{Developmental Review}, \emph{41}, 71--90.
-\url{https://doi.org/10.1016/j.dr.2016.06.004}
-
-\leavevmode\vadjust pre{\hypertarget{ref-rosseel2012}{}}%
-Rosseel, Y. (2012). Lavaan: An r package for structural equation modeling. \emph{Journal of Statistical Software}, \emph{48}(1), 1--36. \url{https://doi.org/10.18637/jss.v048.i02}
-
-\leavevmode\vadjust pre{\hypertarget{ref-schwarz1978}{}}%
-Schwarz, G. (1978). Estimating the dimension of a model. \emph{The Annals of Statistics}, \emph{6}(2), 461--464. Retrieved from \url{https://www.jstor.org/stable/2958889}
-
-\leavevmode\vadjust pre{\hypertarget{ref-shadish2001}{}}%
-Shadish, W. R., Cook, T. D., \& Campbell, D. T. (2001). \emph{Experimental and quasi-experimental designs for generalized causal inference}. Boston: Houghton Mifflin.
-
-\leavevmode\vadjust pre{\hypertarget{ref-suxf6rbom1978}{}}%
-Sörbom, D. (1978). An alternative to the methodology for analysis of covariance. \emph{Psychometrika}, \emph{43}(3), 381--396. \url{https://doi.org/10.1007/BF02293647}
-
-\leavevmode\vadjust pre{\hypertarget{ref-stark2006}{}}%
-Stark, S., Chernyshenko, O.
-S., \& Drasgow, F.
-(2006).
-Detecting differential item functioning with confirmatory factor analysis and item response theory: Toward a unified strategy.
-\emph{Journal of Applied Psychology}, \emph{91}(6), 1292--1306.
-\url{https://doi.org/10.1037/0021-9010.91.6.1292}
-
-\leavevmode\vadjust pre{\hypertarget{ref-steiger1990}{}}%
-Steiger, J.
-H.
-(1990).
-Structural model evaluation and modification: An interval estimation approach.
-\emph{Multivariate Behavioral Research}, \emph{25}(2), 173--180.
-\url{https://doi.org/10.1207/s15327906mbr2502_4}
-
-\leavevmode\vadjust pre{\hypertarget{ref-tay2015}{}}%
-Tay, L., Meade, A.
-W., \& Cao, M.
-(2015).
-An Overview and Practical Guide to IRT Measurement Equivalence Analysis.
-\emph{Organizational Research Methods}, \emph{18}(1), 3--46.
-\url{https://doi.org/10.1177/1094428114553062}
-
-\leavevmode\vadjust pre{\hypertarget{ref-thompson1996}{}}%
-Thompson, B., \& Daniel, L.
-G.
-(1996).
-Factor Analytic Evidence for the Construct Validity of Scores: A Historical Overview and Some Guidelines.
-\emph{Educational and Psychological Measurement}, \emph{56}(2), 197--208.
-\url{https://doi.org/10.1177/0013164496056002001}
-
-\leavevmode\vadjust pre{\hypertarget{ref-trent2013}{}}%
-Trent, L.
-R., Buchanan, E., Ebesutani, C., Ale, C.
-M., Heiden, L., Hight, T.
-L., \ldots{} Young, J.
-(2013).
-A measurement invariance examination of the revised child anxiety and depression scale in a southern sample: Differential item functioning between african american and caucasian youth.
-\emph{Assessment}, \emph{20}(2), 175--187.
-\url{https://doi.org/10.1177/1073191112450907}
-
-\leavevmode\vadjust pre{\hypertarget{ref-tucker1973}{}}%
-Tucker, L. R., \& Lewis, C. (1973). A reliability coefficient for maximum likelihood factor analysis. \emph{Psychometrika}, \emph{38}(1), 1--10. \url{https://doi.org/10.1007/BF02291170}
-
-\leavevmode\vadjust pre{\hypertarget{ref-vandeschoot2015}{}}%
-Van De Schoot, R., Schmidt, P., De Beuckelaer, A., Lek, K., \& Zondervan-Zwijnenburg, M.
-(2015).
-Editorial: Measurement invariance.
-\emph{Frontiers in Psychology}, \emph{6}.
-Retrieved from \url{https://www.frontiersin.org/articles/10.3389/fpsyg.2015.01064}
-
-\leavevmode\vadjust pre{\hypertarget{ref-vazire2022}{}}%
-Vazire, S., Schiavone, S.
-R., \& Bottesini, J.
-G.
-(2022).
-Credibility Beyond Replicability: Improving the Four Validities in Psychological Science.
-\emph{Current Directions in Psychological Science}, \emph{31}(2), 162--168.
-\url{https://doi.org/10.1177/09637214211067779}
-
-\leavevmode\vadjust pre{\hypertarget{ref-wagnild2009}{}}%
-Wagnild, G. (2009). A review of the resilience scale. \emph{Journal of Nursing Measurement}, \emph{17}(2), 105--113. \url{https://doi.org/10.1891/1061-3749.17.2.105}
-
-\leavevmode\vadjust pre{\hypertarget{ref-weidman2017}{}}%
-Weidman, A.
-C., Steckler, C.
-M., \& Tracy, J.
-L.
-(2017).
-The jingle and jangle of emotion assessment: Imprecise measurement, casual scale usage, and conceptual fuzziness in emotion research.
-\emph{Emotion}, \emph{17}(2), 267--295.
-\url{https://doi.org/10.1037/emo0000226}
-
-\leavevmode\vadjust pre{\hypertarget{ref-zwaan2018}{}}%
-Zwaan, R. A., Etz, A., Lucas, R. E., \& Donnellan, M. B. (2018). Making replication mainstream. \emph{Behavioral and Brain Sciences}, \emph{41}, e120. \url{https://doi.org/10.1017/S0140525X17001972}
-
-\end{CSLReferences}
+\hypertarget{model-fit-statistics}{%
+\subsection{Model Fit Statistics}\label{model-fit-statistics}}
+
+Model fit statistics are provided for each of the ten model combinations (invariant, three sizes for each ladings, intercepts, and residuals).
+These tables could be used to examine the traditional change in fit statistics cutoff rules of thumb (Cheung \& Rensvold, 2002), such as \(\Delta\) CFI or \(\Delta\) RMSEA, to the visualizations presented in the manuscript.
+
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:tab1}Model Fit for Invariant Model}
+
+\begin{tabular}{lllllll}
+\toprule
+Model & AIC & BIC & CFI & TLI & RMSEA & SRMR\\
+\midrule
+Overall & 7,515.723 & 7,578.942 & 0.994 & 0.988 & 0.023 & 0.021\\
+Group 1 & 3,765.749 & 3,818.571 & 0.976 & 0.953 & 0.047 & 0.031\\
+Group 2 & 3,761.952 & 3,814.774 & 0.980 & 0.960 & 0.042 & 0.032\\
+Configural & 7,527.701 & 7,654.140 & 0.978 & 0.956 & 0.045 & 0.032\\
+Metric & 7,529.390 & 7,638.970 & 0.954 & 0.934 & 0.055 & 0.048\\
+Scalar & 7,522.896 & 7,615.617 & 0.964 & 0.960 & 0.043 & 0.049\\
+Strict & 7,519.512 & 7,591.160 & 0.957 & 0.963 & 0.041 & 0.059\\
+\bottomrule
+\end{tabular}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:tab2}Model Fit for Small Differences in Loadings}
+
+\begin{tabular}{lllllll}
+\toprule
+Model & AIC & BIC & CFI & TLI & RMSEA & SRMR\\
+\midrule
+Overall & 7,537.668 & 7,600.888 & 0.981 & 0.962 & 0.044 & 0.024\\
+Group 1 & 3,765.749 & 3,818.571 & 0.976 & 0.953 & 0.047 & 0.031\\
+Group 2 & 3,777.833 & 3,830.655 & 0.978 & 0.956 & 0.050 & 0.032\\
+Configural & 7,543.582 & 7,670.020 & 0.977 & 0.955 & 0.048 & 0.032\\
+Metric & 7,548.898 & 7,658.477 & 0.941 & 0.916 & 0.066 & 0.056\\
+Scalar & 7,541.810 & 7,634.531 & 0.953 & 0.948 & 0.052 & 0.056\\
+Strict & 7,541.658 & 7,613.307 & 0.935 & 0.943 & 0.054 & 0.071\\
+\bottomrule
+\end{tabular}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:tab3}Model Fit for Medium Differences in Loadings}
+
+\begin{tabular}{lllllll}
+\toprule
+Model & AIC & BIC & CFI & TLI & RMSEA & SRMR\\
+\midrule
+Overall & 7,554.550 & 7,617.769 & 0.972 & 0.945 & 0.052 & 0.027\\
+Group 1 & 3,765.749 & 3,818.571 & 0.976 & 0.953 & 0.047 & 0.031\\
+Group 2 & 3,784.923 & 3,837.745 & 0.998 & 0.996 & 0.016 & 0.025\\
+Configural & 7,550.672 & 7,677.110 & 0.988 & 0.976 & 0.035 & 0.028\\
+Metric & 7,562.714 & 7,672.294 & 0.926 & 0.894 & 0.074 & 0.063\\
+Scalar & 7,556.859 & 7,649.580 & 0.933 & 0.926 & 0.062 & 0.064\\
+Strict & 7,558.054 & 7,629.703 & 0.909 & 0.921 & 0.064 & 0.079\\
+\bottomrule
+\end{tabular}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:tab4}Model Fit for Large Differences in Loadings}
+
+\begin{tabular}{lllllll}
+\toprule
+Model & AIC & BIC & CFI & TLI & RMSEA & SRMR\\
+\midrule
+Overall & 7,662.989 & 7,726.209 & 0.984 & 0.969 & 0.045 & 0.022\\
+Group 1 & 3,765.749 & 3,818.571 & 0.976 & 0.953 & 0.047 & 0.031\\
+Group 2 & 3,857.210 & 3,910.032 & 0.968 & 0.936 & 0.076 & 0.033\\
+Configural & 7,622.959 & 7,749.397 & 0.971 & 0.942 & 0.063 & 0.032\\
+Metric & 7,659.191 & 7,768.771 & 0.854 & 0.792 & 0.120 & 0.085\\
+Scalar & 7,652.603 & 7,745.325 & 0.862 & 0.846 & 0.103 & 0.085\\
+Strict & 7,660.626 & 7,732.274 & 0.824 & 0.847 & 0.103 & 0.119\\
+\bottomrule
+\end{tabular}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:tab5}Model Fit for Small Differences in Intercepts}
+
+\begin{tabular}{lllllll}
+\toprule
+Model & AIC & BIC & CFI & TLI & RMSEA & SRMR\\
+\midrule
+Overall & 7,519.687 & 7,582.906 & 0.996 & 0.992 & 0.020 & 0.021\\
+Group 1 & 3,765.749 & 3,818.571 & 0.976 & 0.953 & 0.047 & 0.031\\
+Group 2 & 3,770.411 & 3,823.233 & 0.932 & 0.865 & 0.081 & 0.041\\
+Configural & 7,536.160 & 7,662.598 & 0.954 & 0.908 & 0.066 & 0.036\\
+Metric & 7,531.359 & 7,640.939 & 0.957 & 0.939 & 0.054 & 0.041\\
+Scalar & 7,531.343 & 7,624.064 & 0.941 & 0.934 & 0.056 & 0.049\\
+Strict & 7,523.535 & 7,595.184 & 0.952 & 0.959 & 0.045 & 0.052\\
+\bottomrule
+\end{tabular}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:tab6}Model Fit for Medium Differences in Intercepts}
+
+\begin{tabular}{lllllll}
+\toprule
+Model & AIC & BIC & CFI & TLI & RMSEA & SRMR\\
+\midrule
+Overall & 7,542.771 & 7,605.990 & 0.998 & 0.996 & 0.014 & 0.020\\
+Group 1 & 3,765.749 & 3,818.571 & 0.976 & 0.953 & 0.047 & 0.031\\
+Group 2 & 3,770.411 & 3,823.233 & 0.932 & 0.865 & 0.081 & 0.041\\
+Configural & 7,536.160 & 7,662.598 & 0.954 & 0.908 & 0.066 & 0.036\\
+Metric & 7,531.359 & 7,640.939 & 0.957 & 0.939 & 0.054 & 0.041\\
+Scalar & 7,554.199 & 7,646.920 & 0.845 & 0.828 & 0.091 & 0.070\\
+Strict & 7,546.383 & 7,618.032 & 0.857 & 0.876 & 0.077 & 0.071\\
+\bottomrule
+\end{tabular}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:tab7}Model Fit for Large Differences in Intercepts}
+
+\begin{tabular}{lllllll}
+\toprule
+Model & AIC & BIC & CFI & TLI & RMSEA & SRMR\\
+\midrule
+Overall & 7,579.167 & 7,642.386 & 1.000 & 1.000 & 0.000 & 0.019\\
+Group 1 & 3,765.749 & 3,818.571 & 0.976 & 0.953 & 0.047 & 0.031\\
+Group 2 & 3,770.411 & 3,823.233 & 0.932 & 0.865 & 0.081 & 0.041\\
+Configural & 7,536.160 & 7,662.598 & 0.954 & 0.908 & 0.066 & 0.036\\
+Metric & 7,531.359 & 7,640.939 & 0.957 & 0.939 & 0.054 & 0.041\\
+Scalar & 7,590.291 & 7,683.013 & 0.695 & 0.661 & 0.128 & 0.097\\
+Strict & 7,582.468 & 7,654.117 & 0.707 & 0.745 & 0.111 & 0.098\\
+\bottomrule
+\end{tabular}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:tab8}Model Fit for Small Differences in Residuals}
+
+\begin{tabular}{lllllll}
+\toprule
+Model & AIC & BIC & CFI & TLI & RMSEA & SRMR\\
+\midrule
+Overall & 7,449.492 & 7,512.711 & 1.000 & 1.008 & 0.000 & 0.014\\
+Group 1 & 3,765.749 & 3,818.571 & 0.976 & 0.953 & 0.047 & 0.031\\
+Group 2 & 3,693.319 & 3,746.141 & 1.000 & 1.009 & 0.000 & 0.022\\
+Configural & 7,459.068 & 7,585.507 & 0.991 & 0.983 & 0.030 & 0.026\\
+Metric & 7,461.406 & 7,570.986 & 0.966 & 0.952 & 0.049 & 0.049\\
+Scalar & 7,455.854 & 7,548.575 & 0.972 & 0.969 & 0.039 & 0.051\\
+Strict & 7,453.476 & 7,525.124 & 0.962 & 0.967 & 0.041 & 0.051\\
+\bottomrule
+\end{tabular}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:tab9}Model Fit for Medium Differences in Residuals}
+
+\begin{tabular}{lllllll}
+\toprule
+Model & AIC & BIC & CFI & TLI & RMSEA & SRMR\\
+\midrule
+Overall & 7,378.566 & 7,441.785 & 1.000 & 1.004 & 0.000 & 0.016\\
+Group 1 & 3,765.749 & 3,818.571 & 0.976 & 0.953 & 0.047 & 0.031\\
+Group 2 & 3,597.774 & 3,650.596 & 1.000 & 1.026 & 0.000 & 0.018\\
+Configural & 7,363.523 & 7,489.961 & 0.997 & 0.994 & 0.018 & 0.025\\
+Metric & 7,366.629 & 7,476.209 & 0.971 & 0.958 & 0.048 & 0.047\\
+Scalar & 7,360.147 & 7,452.869 & 0.980 & 0.978 & 0.035 & 0.048\\
+Strict & 7,382.532 & 7,454.180 & 0.879 & 0.895 & 0.076 & 0.072\\
+\bottomrule
+\end{tabular}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:tab10}Model Fit for Large Differences in Residuals}
+
+\begin{tabular}{lllllll}
+\toprule
+Model & AIC & BIC & CFI & TLI & RMSEA & SRMR\\
+\midrule
+Overall & 7,294.214 & 7,357.433 & 1.000 & 1.009 & 0.000 & 0.015\\
+Group 1 & 3,765.749 & 3,818.571 & 0.976 & 0.953 & 0.047 & 0.031\\
+Group 2 & 3,453.472 & 3,506.294 & 0.950 & 0.900 & 0.073 & 0.035\\
+Configural & 7,219.221 & 7,345.659 & 0.962 & 0.925 & 0.061 & 0.033\\
+Metric & 7,216.378 & 7,325.957 & 0.958 & 0.940 & 0.055 & 0.043\\
+Scalar & 7,210.650 & 7,303.372 & 0.965 & 0.961 & 0.044 & 0.045\\
+Strict & 7,297.887 & 7,369.535 & 0.595 & 0.648 & 0.133 & 0.176\\
+\bottomrule
+\end{tabular}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
 

### 2023-10-16 appendix_1.Rmd
all the updates

---
appendix: "appendix_1.Rmd"
---

## Simulating from models

Here's an example of how to simulate directly from a `lavaan` model:

```{r echo = T, eval = F, size = "small"}
# first build your model
# this example is separate for each group
model.invariant.g1 <- "
# loadings
lv =~ .8*q1 + .4*q2 + .6*q3 + .3*q4 + .6*q5 
# set the residual for invariance on q4
q4 ~~ 1*q4
# set the intercept for invariance on q4
q4 ~ 0*1
# set the intercept to zero for df purposes
q1 ~ 0*1
# allow the latent mean to be estimated 
lv ~ 1"
model.invariant.g2 <- "lv =~ .77*q1 + .43*q2 + .58*q3 + .3*q4 + .61*q5
q4 ~~ 1*q4
q4 ~ 0*1
q1 ~ 0*1
lv ~ 1"

# simulate data invariant separately for each group
df.invariant <- bind_rows(
  # lavaan function 
  simulateData(
    # model with estimates 
    model = model.invariant.g1, 
    # how many data points
    sample.nobs = 250, 
    # mean structure for mgcfa models 
    meanstructure = T, 
    # model type
    model.type = "cfa",
    # set seed for reproducibility 
    seed = 1234) %>% 
    # add a group label to the data 
    mutate(group = "Group 1"), 
  simulateData(
    model = model.invariant.g2, 
    sample.nobs = 250, 
    meanstructure = T, 
    model.type = "cfa",
    seed = 1234) %>% 
    mutate(group = "Group 2") 
)
```

\newpage

## Simulating from matrices

Here's an example of how to simulate using `MASS` and covariance or correlation matrices.

```{r echo = T, eval = T, size = "small"}
library(MASS)

# covariance matrix
university.cov <- lav_matrix_lower2full(
    c(169.00, 
      73.710, 182.2500,
      73.229, 88.4250, 171.6100,
      63.375, 72.5625, 127.7250, 156.2500,
      42.120, 67.4325, 122.0265, 123.1875, 182.2500,
      57.226, 63.2610, 117.1926, 154.4250, 138.0240, 201.6400,
      30.875, 32.0625, 60.9805, 62.9375, 76.9500, 79.5910, 90.2500,
      36.075, 38.9610, 61.0722, 58.2750, 65.9340, 70.9290, 81.1965, 123.2100,
      18.096, 21.1410, 26.2131, 39.1500, 44.6310, 46.9452, 48.7635, 56.0106, 75.6900))

# give it names
rownames(university.cov) <-
    colnames(university.cov) <-
    c("class", "social", "learn", "chronic", "physical", "sex", 
      "depression", "anxiety", "stress")

# means - you need standard deviation if you only have a correlation matrix 
university.means <- c(3.4, 4.3, 3.7, 3.2, 4.5, 1.2, 4.0, 3.5, 4.2)

# use mass function
DF <- mvrnorm(n = 200, mu = university.means, Sigma = university.cov)

head(DF)
```

### 2023-10-16 appendix_2.Rmd
all the updates

---
appendix: "appendix_2.Rmd"
---

## MGCFA Model Fit Statistics

Model fit statistics are provided for each of the ten model combinations (invariant, three sizes for each ladings, intercepts, and residuals). These tables could be used to examine the traditional change in fit statistics cutoff rules of thumb [@cheung2002], such as $\Delta$ CFI or $\Delta$ RMSEA, to the visualizations presented in the manuscript.

```{r tab1, results='asis'}
apa_table(results.invariant$model_fit %>% 
            dplyr::select(model, AIC, BIC, cfi, tli, rmsea, srmr),
          digits = 3, 
          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
          caption = "Model Fit for Invariant Model")
```

```{r tab2, results='asis'}
apa_table(results.small.load$model_fit %>% 
            dplyr::select(model, AIC, BIC, cfi, tli, rmsea, srmr), 
          digits = 3, 
          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
          caption = "Model Fit for Small Differences in Loadings")
```

```{r tab3, results='asis'}
apa_table(results.med.load$model_fit %>% 
            dplyr::select(model, AIC, BIC, cfi, tli, rmsea, srmr), 
          digits = 3, 
          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
          caption = "Model Fit for Medium Differences in Loadings")
```

```{r tab4, results='asis'}
apa_table(results.large.load$model_fit %>% 
            dplyr::select(model, AIC, BIC, cfi, tli, rmsea, srmr),
          digits = 3, 
          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
          caption = "Model Fit for Large Differences in Loadings")
```

```{r tab5, results='asis'}
apa_table(results.small.int$model_fit %>% 
            dplyr::select(model, AIC, BIC, cfi, tli, rmsea, srmr), 
          digits = 3, 
          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
          caption = "Model Fit for Small Differences in Intercepts")
```

```{r tab6, results='asis'}
apa_table(results.med.int$model_fit %>% 
            dplyr::select(model, AIC, BIC, cfi, tli, rmsea, srmr),
          digits = 3, 
          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
          caption = "Model Fit for Medium Differences in Intercepts")
```

```{r tab7, results='asis'}
apa_table(results.large.int$model_fit %>% 
            dplyr::select(model, AIC, BIC, cfi, tli, rmsea, srmr),
          digits = 3, 
          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
          caption = "Model Fit for Large Differences in Intercepts")
```

```{r tab8, results='asis'}
apa_table(results.small.res$model_fit %>% 
            dplyr::select(model, AIC, BIC, cfi, tli, rmsea, srmr), 
          digits = 3, 
          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
          caption = "Model Fit for Small Differences in Residuals")
```

```{r tab9, results='asis'}
apa_table(results.med.res$model_fit %>% 
            dplyr::select(model, AIC, BIC, cfi, tli, rmsea, srmr), 
          digits = 3, 
          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
          caption = "Model Fit for Medium Differences in Residuals")
```

```{r tab10, results='asis'}
apa_table(results.large.res$model_fit %>% 
            dplyr::select(model, AIC, BIC, cfi, tli, rmsea, srmr), 
          digits = 3, 
          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
          caption = "Model Fit for Large Differences in Residuals")
```

### 2023-10-16 appendix_3.Rmd
all the updates

---
appendix: "appendix_3.Rmd"
---

## Simulated Parital Invariance Results

```{r p-tab11, results = 'asis', eval = T}
partial.invariant <-
  partial_mi(
    saved_model = results.invariant$invariance_models$model.residuals,
    data = df.invariant,
    model = model.overall,
    group = "group",
    group.equal = c("loadings", "intercepts", "residuals"),
    partial_step = "residuals")

apa_table(partial.invariant$fit_table %>% 
  dplyr::select(free.parameter, cfi, rmsea), 
  digits = 3, 
  col.names = c("Estimated Parameter", "CFI", "RSMEA"),
  caption = "Fit Estimates for Partial Invariance Residuals on Invariant Data")
```

```{r p-tab12, results = 'asis', eval = T}
partial.small.load <-
  partial_mi(
    saved_model = results.small.load$invariance_models$model.loadings,
    data = df.small.load,
    model = model.overall,
    group = "group",
    group.equal = c("loadings", "intercepts", "residuals"),
    partial_step = "loadings")

apa_table(partial.small.load$fit_table %>% 
  dplyr::select(free.parameter, cfi, rmsea), 
  digits = 3, 
  col.names = c("Estimated Parameter", "CFI", "RSMEA"),
  caption = "Fit Estimates for Partial Invariance Loadings for Small Loading Data")
```

```{r p-tab13, results = 'asis', eval = T}
partial.med.load <-
  partial_mi(
    saved_model = results.med.load$invariance_models$model.loadings,
    data = df.med.load,
    model = model.overall,
    group = "group",
    group.equal = c("loadings", "intercepts", "residuals"),
    partial_step = "loadings")

apa_table(partial.med.load$fit_table %>% 
  dplyr::select(free.parameter, cfi, rmsea), 
  digits = 3, 
  col.names = c("Estimated Parameter", "CFI", "RSMEA"),
  caption = "Fit Estimates for Partial Invariance Loadings for Medium Loading Data")
```

```{r p-tab14, results = 'asis', eval = T}
partial.large.load <-
  partial_mi(
    saved_model = results.large.load$invariance_models$model.loadings,
    data = df.large.load,
    model = model.overall,
    group = "group",
    group.equal = c("loadings", "intercepts", "residuals"),
    partial_step = "loadings")

apa_table(partial.large.load$fit_table %>% 
  dplyr::select(free.parameter, cfi, rmsea), 
  digits = 3, 
  col.names = c("Estimated Parameter", "CFI", "RSMEA"),
  caption = "Fit Estimates for Partial Invariance Loadings for Large Loading Data")
```

```{r p-tab15, results = 'asis', eval = T}
partial.small.int <-
  partial_mi(
    saved_model = results.small.int$invariance_models$model.intercepts,
    data = df.small.int,
    model = model.overall,
    group = "group",
    group.equal = c("loadings", "intercepts", "residuals"),
    partial_step = "intercepts")

apa_table(partial.small.int$fit_table %>% 
  dplyr::select(free.parameter, cfi, rmsea), 
  digits = 3, 
  col.names = c("Estimated Parameter", "CFI", "RSMEA"),
  caption = "Fit Estimates for Partial Invariance Loadings for Small Intercept Data")
```

```{r p-tab16, results = 'asis', eval = T}
partial.med.int <-
  partial_mi(
    saved_model = results.med.int$invariance_models$model.intercepts,
    data = df.med.int,
    model = model.overall,
    group = "group",
    group.equal = c("loadings", "intercepts", "residuals"),
    partial_step = "intercepts")

apa_table(partial.med.int$fit_table %>% 
  dplyr::select(free.parameter, cfi, rmsea), 
  digits = 3, 
  col.names = c("Estimated Parameter", "CFI", "RSMEA"),
  caption = "Fit Estimates for Partial Invariance Loadings for Medium Intercept Data")
```

```{r p-tab17, results = 'asis', eval = T}
partial.large.int <-
  partial_mi(
    saved_model = results.large.int$invariance_models$model.intercepts,
    data = df.large.int,
    model = model.overall,
    group = "group",
    group.equal = c("loadings", "intercepts", "residuals"),
    partial_step = "intercepts")

apa_table(partial.large.int$fit_table %>% 
  dplyr::select(free.parameter, cfi, rmsea), 
  digits = 3, 
  col.names = c("Estimated Parameter", "CFI", "RSMEA"),
  caption = "Fit Estimates for Partial Invariance Loadings for Large Intercept Data")
```

```{r p-tab18, results = 'asis', eval = T}
partial.small.res <-
  partial_mi(
    saved_model = results.small.res$invariance_models$model.residuals,
    data = df.small.res,
    model = model.overall,
    group = "group",
    group.equal = c("loadings", "intercepts", "residuals"),
    partial_step = "residuals")

apa_table(partial.small.res$fit_table %>% 
  dplyr::select(free.parameter, cfi, rmsea), 
  digits = 3, 
  col.names = c("Estimated Parameter", "CFI", "RSMEA"),
  caption = "Fit Estimates for Partial Invariance Loadings for Small Residual Data")
```

```{r p-tab19, results = 'asis', eval = T}
partial.med.res <-
  partial_mi(
    saved_model = results.med.res$invariance_models$model.residuals,
    data = df.med.res,
    model = model.overall,
    group = "group",
    group.equal = c("loadings", "intercepts", "residuals"),
    partial_step = "residuals")

apa_table(partial.med.res$fit_table %>% 
  dplyr::select(free.parameter, cfi, rmsea), 
  digits = 3, 
  col.names = c("Estimated Parameter", "CFI", "RSMEA"),
  caption = "Fit Estimates for Partial Invariance Loadings for Medium Residual Data")
```

```{r p-tab20, results = 'asis', eval = T}
partial.large.res <-
  partial_mi(
    saved_model = results.large.res$invariance_models$model.residuals,
    data = df.large.res,
    model = model.overall,
    group = "group",
    group.equal = c("loadings", "intercepts", "residuals"),
    partial_step = "residuals")

apa_table(partial.large.res$fit_table %>% 
  dplyr::select(free.parameter, cfi, rmsea), 
  digits = 3, 
  col.names = c("Estimated Parameter", "CFI", "RSMEA"),
  caption = "Fit Estimates for Partial Invariance Loadings for Large Residual Data")
```

\newpage

### 2023-10-16 appendix_4.Rmd
all the updates

---
appendix: "appendix_4.Rmd"
---
## Invariance Plots Difference Scores by Condition

```{r inv-plots-condition, include = TRUE}
conditions <- unique(boot_long$type)

for (cond in conditions){
  invariance_plot <- ggplot(boot_long %>% 
                              filter(type == cond), 
                          aes(term, difference, color = type_estimate)) + 
  stat_summary(fun = mean, geom = "point", 
               position = position_dodge(width = 0.9)) + 
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", 
               position = position_dodge(width = 0.9), 
               width = 0.2) + 
  theme_classic() + 
  xlab("Estimated Item") + 
  ylab("Difference Score Between Groups") + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1), legend.position = "bottom") + 
  facet_wrap(~index_difference, labeller = as_labeller(label_graph)) + 
  scale_color_discrete(name = "Type of Estimate") + 
    coord_flip() + 
    ggtitle(paste0(cond, " Graph Results"))

print(invariance_plot)
}
```

### 2023-10-16 appendix_5.Rmd
all the updates

---
appendix: "appendix_5.Rmd"
---

## Invariance Plots Effect Sizes by Condition

```{r inv-effect-condition, include = TRUE}

for (cond in conditions){
  effect_invariance_plot <- 
  ggplot(boot_summary_long %>% 
           filter(type == cond), aes(term, d, color = type_estimate)) + 
  theme_classic() + 
  facet_wrap(~invariant, labeller = as_labeller(label_graph)) +
  scale_color_discrete(name = "Type of Estimate") + 
  geom_point(aes(size = n)) + 
  geom_errorbar(aes(ymin = d_low, ymax = d_high), width = 0.2) + 
  xlab("Estimated Item") + 
  ylab("Group Effect Size") + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1), 
        legend.position = "bottom") + 
  geom_hline(yintercept = 0) + 
  coord_flip() + 
    ggtitle(paste0(cond, " Graph Results"))

  print(effect_invariance_plot)
}
```

### 2023-10-16 manuscript.Rmd
all the updates

@@
 ---
-title             : "Visualizing and Interpreting Multi-Group Confirmatory Factor Analysis"
+title             : "visualizemi: Visualization, Effect Size, and Replication of Measurement Invariance for Registered Reports"
 shorttitle        : "VISUAL MGCFA"
@@
 With the rise of the replication crisis and "psychology's renaissance" [@nelson2018], interest in divergence in measurement has increased, often focused on small parameter differences within the latent model.
-This manuscript outlines ways to visualize potential non-invariance, to supplement large numbers of tables that often overwhelm a reader within these published reports.
-Readers will learn how to interpret the impact and size of the proposed non-invariance in models.
-While it is tempting to suggest that problems with replication and generalizability are simply issues with measurement, it is crucial to remember that all models have variability and error, even those models estimating the differences between item functioning, such as multi-group confirmatory factor analysis.
+This manuscript presents `visualizemi`, an *R* package that provides functionality to calculate multigroup models, partial invariance, visualizations for (non)-invariance, effect sizes for models and parameters, and potential replication rates compared to random models.
+Readers will learn how to interpret the impact and size of the proposed non-invariance in models with a focus on potential replication and how to plan for registered reports.
 
@@
 classoption       : "man"
-bibliography: references.bib
+bibliography: includes/references.bib
 
@@
 output            : papaja::apa6_pdf
+appendix          :
+  - "appendix_1.Rmd"
+  - "appendix_2.Rmd"
+  - "appendix_3.Rmd"
+  - "appendix_4.Rmd"
+  - "appendix_5.Rmd"
+  - "appendix_6.Rmd"
 ---
@@
 library(ggplot2)
+library(cowplot)
+library(ggridges)
+library(tidyr)
+library(rio)
+
 # devtools::install_github("psyteachr/introdataviz")
 # devtools::install_github("ddueber/dmacs")
+# devtools::install_github("doomlab/visualizemi")
 library(introdataviz)
 library(dmacs)
-library(cowplot)
+library(visualizemi)
 
@@
 
-```{r cfa-function, include = FALSE}
-# CFA function
-mgcfa <- function(data, group, model){
-
-  group_names <- unique(data[ , group])
-  data$group <- data[ , group]
-
-  model.overall <- cfa(model = model, data = data, 
-                       meanstructure = T)
-  model.group1 <- cfa(model = model, 
-                      data = subset(data, group == group_names[1]),
-                      meanstructure = T)
-  model.group2 <- cfa(model = model, 
-                      data = subset(data, group == group_names[2]),
-                      meanstructure = T)
-  model.configural <- cfa(model = model, data = data, 
-                          group = group, meanstructure = T)
-  model.metric <- cfa(model = model, data = data, 
-                      group = group, meanstructure = T,
-                      group.equal = "loadings")
-  model.scalar <- cfa(model = model, data = data, 
-                      group = group, meanstructure = T, 
-                      group.equal = c("loadings", "intercepts"))
-  model.strict <- cfa(model = model, data = data, 
-                      group = group, meanstructure = T, 
-                      group.equal =  c("loadings", "intercepts", "residuals"))
-
-  model_coef <- bind_rows(
-    tidy(model.overall, conf.level = .95) %>% mutate(model = "Overall"), 
-    tidy(model.group1, conf.level = .95) %>% mutate(model = "Group 1"), 
-    tidy(model.group2, conf.level = .95) %>% mutate(model = "Group 2"), 
-    tidy(model.configural, conf.level = .95) %>% mutate(model = "Configural"), 
-    tidy(model.metric, conf.level = .95) %>% mutate(model = "Metric"), 
-    tidy(model.scalar, conf.level = .95) %>% mutate(model = "Scalar"), 
-    tidy(model.strict, conf.level = .95) %>% mutate(model = "Strict")
-  )
-
-  model_fit <- bind_rows(
-    glance(model.overall) %>% mutate(model = "Overall"), 
-    glance(model.group1) %>% mutate(model = "Group 1"), 
-    glance(model.group2) %>% mutate(model = "Group 2"), 
-    glance(model.configural) %>% mutate(model = "Configural"), 
-    glance(model.metric) %>% mutate(model = "Metric"), 
-    glance(model.scalar) %>% mutate(model = "Scalar"), 
-    glance(model.strict) %>% mutate(model = "Strict")
-    )
-
-  return(list(
-    "model_coef" = model_coef,
-    "model_fit" = model_fit,
-    "model.overall" = model.overall,
-    "model.group1" = model.group1,
-    "model.group2" = model.group2,
-    "model.configural" = model.configural,
-    "model.metric" = model.metric,
-    "model.scalar" = model.scalar,
-    "model.strict" = model.strict
-  ))
-
-}
-```
-
-```{r test-function, eval = F, include = F}
-# temp test
-data_coef = results.large.res$model_coef
-model_step = "Configural" 
-item_name = "q4"
-x_limits = c(-1,1)
-y_limits = c(min(df.large.res$q4), max(df.large.res$q4))
-ci_level = .95
-model_results = results.invariant$model.configural
-lv_name = "lv"
-
-  data_coef = partial.coef
-  model_step = "intercepts"
-  item_name = "RS6"
-  x_limits = c(-1,1)
-  y_limits = c(min(DF$RS7), max(DF$RS7))
-  model_results = partial.rs.2.picture
-  ci_level = .95
-  lv_name = "RS"
-```
-
-```{r plot-function, include = FALSE}
-plot_mgcfa <- function(data_coef, # output from model_coef
-                       model_step, # which model
-                       item_name, # name of observed item
-                       x_limits = c(-1,1), # LV limits to graph
-                       y_limits, # Y min and max in data 
-                       ci_level, # what ci do you want
-                       model_results, # what model results do you want 
-                       lv_name # which latent is the observed variable on
-                       ){
-
-  # calculate cutoff
-  cutoff <- qt(p = (1-ci_level)/2, 
-               df = sum(unlist(model_results@Data@nobs)), 
-               lower.tail = F)
-
-  # get group variable
-  group_var <- model_results@Data@group
-  group_labels <- model_results@Data@group.label
-
-  # first get the data
-  graph.data <- data_coef %>% # put in tidy coefficients
-  filter(model == model_step) %>% # pick a model
-  filter(grepl(item_name, term)) %>%  # pick a question
-  mutate(group = factor(group, levels = names(table(data_coef$group)), 
-                        labels = group_labels))
-
-  # make ribbon data y = slope*x + intercept for ci for slopes 
-  ribbondata <- bind_rows(
-    data.frame(
-    x = seq(from = x_limits[1] - 1,  
-            to = x_limits[2] + 1, 
-            by = .05), 
-    group = unique(graph.data$group)[1]
-  ) %>% 
-    mutate(ymin = (graph.data %>% filter(op == "=~") %>% 
-                 slice_head() %>% pull(estimate) * x) - 
-             (cutoff*graph.data %>% filter(op == "=~") %>% 
-                    slice_head() %>% pull(std.error)) +
-             graph.data %>% filter(op == "~1") %>% 
-                 slice_head() %>% pull(estimate), 
-           ymax = (graph.data %>% filter(op == "=~") %>% 
-                 slice_head() %>% pull(estimate) * x) + 
-             (cutoff*graph.data %>% filter(op == "=~") %>% 
-                    slice_head() %>% pull(std.error)) +
-             graph.data %>% filter(op == "~1") %>% 
-                 slice_head() %>% pull(estimate)), 
-    data.frame(
-      x = seq(from = x_limits[1] - 1,  
-              to = x_limits[2] + 1, 
-              by = .05), 
-      group = unique(graph.data$group)[2]
-    ) %>% 
-      mutate(ymin = (graph.data %>% filter(op == "=~") %>% 
-                   slice_tail() %>% pull(estimate) * x) - 
-               (cutoff*graph.data %>% filter(op == "=~") %>% 
-                      slice_tail() %>% pull(std.error)) +
-               graph.data %>% filter(op == "~1") %>% 
-                   slice_tail() %>% pull(estimate), 
-             ymax = (graph.data %>% filter(op == "=~") %>% 
-                   slice_tail() %>% pull(estimate) * x) + 
-               (cutoff*graph.data %>% filter(op == "=~") %>% 
-                      slice_tail() %>% pull(std.error)) +
-               graph.data %>% filter(op == "~1") %>% 
-                   slice_tail() %>% pull(estimate))
-  )
-
-  # make point data to draw on the intercepts 
-  pointdata <- data.frame(
-  x = c(0,0),
-  y = graph.data %>% filter(op == "~1") %>% pull(estimate), 
-  group = graph.data %>% filter(op == "~1") %>% pull(group),
-  ymin = graph.data %>% filter(op == "~1") %>% pull(estimate) - 
-    cutoff * graph.data %>% filter(op == "~1") %>% pull(std.error), 
-  ymax = graph.data %>% filter(op == "~1") %>% pull(estimate) + 
-    cutoff * graph.data %>% filter(op == "~1") %>% pull(std.error)
-  )
-
-  # make the line data to draw on the slopes
-  linedata <- data.frame(
-  slope = graph.data %>% filter(op == "=~") %>% pull(estimate), 
-  intercept = graph.data %>% filter(op == "~1") %>% pull(estimate), 
-  group = graph.data %>% filter(op == "~1") %>% pull(group)
-  )
-
-  # make the distributions for the residuals 
-  violindata <- data.frame(
-  y = c(rnorm(n = 1000, 
-            mean = graph.data %>% filter(op == "~~") %>% 
-              slice_head() %>% pull(estimate), 
-            sd = graph.data %>% filter(op == "~~") %>% 
-              slice_head() %>% pull(std.error)), 
-        rnorm(n = 1000, 
-            mean = graph.data %>% filter(op == "~~") %>% 
-              slice_tail() %>% pull(estimate), 
-            sd = graph.data %>% filter(op == "~~") %>% 
-              slice_tail() %>% pull(std.error))),
-  group = c(rep(graph.data %>% filter(op == "~~") %>% 
-              slice_head() %>% pull(group), 1000),
-            rep(graph.data %>% filter(op == "~~") %>% 
-              slice_tail() %>% pull(group), 1000)), 
-  x = 1
-  )
-
-  # make the latent mean data for right panel
-  latent_means <- lavPredict(model_results, 
-                               type = "lv", 
-                               label = TRUE,
-                               assemble = TRUE, 
-                               append.data = TRUE)
-
-  latent_means$lv <- latent_means[ , lv_name]
-  latent_means$group <- latent_means[ , group_var]
-
-  # make a plot of the variance
-  variance_plot <- 
-  ggplot(violindata, aes(x = 1, y = y, color = group, fill = group)) + 
-  geom_split_violin() + 
-  theme_void() + 
-  theme(legend.position = "none") + 
-  stat_summary(fun = "mean",
-               geom = "crossbar", 
-               width = 0.5,
-               colour = "black")
-
-  # make the plot with intercepts and slopes
-  intercept_plot <- 
-  ggplot() + 
-  # basic set up
-  theme_classic() + 
-  xlab("Latent Variable") + 
-  ylab("Observed Variable") + 
-  coord_cartesian(xlim = x_limits, ylim = y_limits) + 
-  # plot the intercepts 
-  geom_point(data = pointdata, 
-             aes(x = x, y = y, color = group), 
-             inherit.aes = FALSE) + 
-  geom_errorbar(data = pointdata,
-                aes(x = x, ymin = ymin, ymax = ymax, color = group), 
-                inherit.aes = FALSE, width = .10) + 
-  # plot the slopes
-  geom_abline(data = linedata,
-              aes(slope = slope, intercept = intercept, color = group)) + 
-  geom_ribbon(data = ribbondata, 
-              aes(x = x, ymin = ymin, ymax = ymax, fill = group), 
-              inherit.aes = FALSE, alpha = .2) + 
-  scale_color_discrete(name = "Group") + 
-  scale_fill_discrete(name = "Group") + 
-  geom_vline(xintercept = 0) + 
-  theme(axis.line.y = element_blank())
-
-  # make the latent means plot
-  mean_plot <- ggplot(latent_means, aes(x = lv, fill = group)) + 
-    geom_density(alpha = .2) + 
-    theme_classic() + 
-    xlab("Latent Variable") + 
-    ylab("Density") + 
-    geom_vline(data = latent_means %>% group_by(group) %>% summarize(mean = mean(lv)), 
-               aes(xintercept = mean, color = group)) + 
-    theme(legend.position = "none") + 
-    coord_cartesian(xlim = x_limits)
-
-  y_range = abs(y_limits[2] - y_limits[1])
-
-  # line up the two plots 
-  prow <- plot_grid(
-    intercept_plot + 
-      ggtitle("Item Invariance") + 
-      theme(legend.position = "none") + 
-      annotation_custom(ggplotGrob(variance_plot), 
-                        xmin = .25, xmax = 1, 
-                        ymin = y_limits[1], ymax = y_limits[2]-y_range/1.8),
-    mean_plot + 
-      ggtitle("Latent Mean Distribution") + 
-      theme(legend.position = "none"),
-    align = 'vh',
-    hjust = -1,
-    nrow = 1
-  )
-
-  # get the legend
-  legend_b <- get_legend(
-    intercept_plot + 
-      guides(color = guide_legend(nrow = 1)) +
-      theme(legend.position = "bottom")
-  )
-
-  # send out the plot 
-  plot_grid(prow, legend_b, ncol = 1, rel_heights = c(1, .1))
-
-}
-```
-
 ```{r analysis-preferences}
@@
 set.seed(84393)
-knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
+knitr::opts_chunk$set(cache.extra = knitr::rand_seed, cache = TRUE, message = FALSE, warning = FALSE)
+
+boot_rr_DF <- import("manu_data/boot_rr_DF.csv")
+boot.partial.invariant <- readRDS("manu_data/boot.partial.invariant.RData")
+boot.model.rs <- readRDS("manu_data/boot.model.rs.RData")
+boot.partial.rs <- readRDS("manu_data/boot.partial.rs.RData")
+
+boot.df.full <- import("manu_data/boot_DF_full.csv")
+boot.effects.summary.full <- import("manu_data/boot_effects_summary_DF_full.csv")
+boot.partial.summary.full <- import("manu_data/boot_partial_summary_DF_full.csv")
 ```
@@
 
-Measurement invariance is typically analyzed using confirmatory factor analysis, specifically, multi-group confirmatory factor analysis (MGCFA) or less often, with item response theory [@stark2006; @tay2015].
-First, the model is examined with the factor structure proposed for the latent and observed variables, and then often these models are assessed for each group separately.
-The two models are then combined together into one nested CFA in order to determine configural invariance [@brown2015; @byrne2001; @kline2016].
-Configural invariance tests if the proposed factor structure is the same between groups.
-In this model, all other estimated parameters are allowed to vary between groups.
-The general approach is to use this model as a baseline for starting a sequential analysis of further restrictions between group parameters (i.e., more restrictive with each step).
-However, models without configural invariance can occur and often point to misspecification for the observed and latent variables within one group (i.e., cross loadings of items onto other latent variables or correlated error terms for one group only).
-
-Next, the estimated parameter between each observed variable and its latent variable are constrained to be equal between groups for metric invariance.
-For example, item 1's factor loading must be equal to item 1's factor loading for each group.
-This test examines if the items represent the same relationship to the latent variable, or if specific items have weaker or stronger relationships in specific groups.
-Finding non-invariance at this stage generally points to items that have different functioning or interpretation for one group.
-At the third model, the item intercepts (i.e., item averages) are restricted across groups for scalar invariance.
-Scalar non-invariance would indicate that items have the same strength of relationship with their latent variable, just one group has a higher overall average on that item.
-Last (although sometimes not used), we may consider constraining error variances for each observed variable to be equal across groups for strict invariance.
-Strict non-invariance can occur when one group has a higher range of values on the observed variable, thus showing a larger variance.
-For example, if using a Likert scale, one group may use the full 1 to 7 range (creating a flatter distribution and larger variance), while the other group shows a ceiling effect of only using 5 to 7.
-
-These concepts have been explored and implemented for the last fifty years [@jöreskog1971; @sörbom1978] and implemented in the most popular structural equation modeling programs [@jöreskog2001; @rosseel2012; @boker2011].
+Measurement invariance has been explored and implemented for the last fifty years [@jöreskog1971; @sörbom1978] and implemented in the most popular structural equation modeling programs [@jöreskog2001; @rosseel2012; @boker2011].
 @byrne1989 extended the ideas of multi-group testing by suggesting partial invariance [followed by @meredith1993].
@@
 This testing provided an advantage to understand where the potential non-invariance may occur for further study and interpretation guidelines.
-To determine when non-invariance and partial invariance occurred, each model is sequentially compared to the previous model using some form of a difference test.
-Traditionally, since models were nested, a chi-square difference test was used [@meade2008; @cheung2002]; however, given the known issues with chi-square [@thompson1996], people have favored empirical cutoffs for differences in fit indices.
 As the field pushes back against favoring cutoff criteria and rules of thumb [@marsh2004; @putnick2016], an effect size measure for translating "how much" non-invariance was developed $d_{MACS}$ [@nye2011].
@@
 With $d_{MACS}$ and measurement invariance testing, researchers can begin to quantify how and where their construct measurement may vary between groups.
-However, given the large number of studies that show non-invariance, it is clear that equivalence can be hard to meet.
+Yet, given the large number of studies that show non-invariance, it is clear that equivalence can be hard to meet.
 It is difficult to know if non-invariance occurs because of random sampling error, true population differences, or differences in replication and reproducibility of the construct in a new sample.
-Further, it is important to remember that the parameter estimates that we are testing are just that - estimates.
-All the parameter estimates have measures of standard error to indicate that they are more than likely variable with a new sample or population.
-Given that this information is generally ignored during the examination of measurement invariance, it may be that we are claiming that many scales are non-invariant, when in reality, the differences between loadings or item intercepts are small and unimportant.
-$d_{MACS}$ provides the opportunity to begin to think about the smallest effect size of interest or the smallest meaningful effect size [@lakens2017; @anvari2021].
+The field of psychology is increasingly interested in pre-registration [i.e., registering plans for a study before data collection, @nosek2018] and the promotion of transparency in study design, implementation, and analysis [@mayo-wilson2021], in addition to supporting replication studies [@zwaan2018].
+Registered (replication) reports provide an advantageous avenue for the pre-registration of measurement tests, as they allow a researcher the ability to have their study accepted in principle, regardless of the results of a test of construct validity, reliability, or measurement invariance [@hobson2019; @nosek2014].
+However, there are few tools that can provide effect size measures for models, individual parameters, or visualization for researchers to plan for future studies.
+$d_{MACS}$ provides the opportunity to begin to think about the smallest effect size of interest or the smallest meaningful effect size for measurement invariance and replication [i.e., two studies with overlapping confidence intervals "replicate", even if the test of measurement invariance does not, @lakens2017; @anvari2021].
 As mentioned, $d_{MACS}$ has only really been explored for a combined intercept and loadings, and while useful, does not necessarily allow a researcher to pinpoint specific issues within an observed variable.
-The purpose of this manuscript is provide readers with a framework for visualization of differences in loadings, intercepts, and variances for each item, and the impact of those differences on the distribution of the latent mean.
+
+Therefore, purpose of this manuscript is describe an *R* package, `visualizemi`, that provides functionality to calculate multi-group confirmatory factor analysis, partial invariance tests, visualizations of the size of non-invariance, and potential effect sizes for overall models and individual parameters.
 No known visualization techniques have been proposed for measurement invariance.
 By creating panel visualizations, we can supplement a researchers ability to judge the strength of the non-invariance differences and effect size for each item.
+The proposed effect sizes demonstrate the likelihood of replication with a similar sample as compared to a randomly assigned group model, thus, illustrating what type of measurement one might expect to find, and how different that is from random chance.
+Within this technique, the individual parameter effect sizes can calculated: both the group differences within a model as compared to random and the likelihood of a parameter replication compared to random groups.
 Coupled with other indicators (i.e., fit indices differences, $d_{MACS}$), we can move toward a better understanding of how much measurement non-invariance is meaningful.
+This tutorial and package will help researchers plan future studies and aid in the ability to estimate a smallest effect of interest for measurement invariance studies, rather than relying on fit indices and rules of thumb alone.
 
@@
 
-1.  Be able to create visualizations for common steps to multi-group confirmatory factor analysis.
-2.  Be able to interpret the impact and size of potential non-invariance on measurement.
-3.  Understand the impact of measurement variability on replication and generalizability.
+1.  Learn how to use *visualizemi* to analyze multi-group confirmatory factor analysis, examine partial invariance, and create visualizations of parameters.
+2.  Learn how to estimate the potential replication of multi-group models and their parameters using bootstrapping compared to a random group model.
+3.  Be able to calculate and interpret effect sizes for model and parameter replication, as well as parameter group differences.
+4.  Understand the impact of measurement variability on replication and generalizability.
+
+The tutorial will start with simulated data based on known effect sizes using $d_{MACS}$ and demonstrating the package functions for 1) running the multigroup analysis, 2) running a partial invariance analysis, 3) plotting the partial invariance, 4) estimating replication and effect sizes at the model level, and 5) estimating replication and effect sizes at the parameter level.
+Last, data from @aiena2014 examining the measurement invariance of the RS-14 [@wagnild2009] will be used to demonstrate the application of the package on real data.
+The *visualizemi* package vignette includes an additional tutorial walk through.
 
@@
 Data was simulated using the `simulateData` function in the *R* package *lavaan* [@rosseel2012] assuming multivariate normality using a $\mu$ of 0 and $\sigma$ of 1 for the data.
-This function allows you to write *lavaan* syntax for your model with estimated values to generate data for observed variables.
+This function allows you to write *lavaan* syntax for your model with estimated values to generate data for observed variables (see supplemental for examples).
 The data included two groups of individuals ("Group 1", "Group 2") for a multi-group confirmatory factor analysis ($n_{group}$ = 250, *N* = 500).
-The latent variables were assumed to be continuous normal.
+The latent variables were assumed to be continuous normal (the package functions do not require this assumption).
 The model consisted of five observed items predicted by one latent variable (`lv =~ q1 + q2 + q3 + q4 + q5`); however, the demonstration in this manuscript extends to multiple latent variables and other combinations of observed variables.
-Each item was assumed to be related to the latent variable with loadings approximately equal to .40 to .80, except when cases of non-invariance on the loadings was assumed.
+Each item was assumed to be related to the latent variable with loadings approximately equal to .40 to .80, except when cases of non-invariance on the loadings was simulated.
 
 The @brown2015 steps of testing measurement invariance are demonstrated in this manuscript for illustration purposes, but in line with @stark2006 suggestions, the visualizations show the impact of loadings and intercepts together.
-The configural model was analyzed nesting both groups into the same CFA model requiring that both groups show the same model structure, but all other parameters are free to vary between groups.
-The metric model constrained the factor loadings of each group to be equal within the model.
-The scalar model then constrained the item intercepts (i.e., item means) to be equal across groups.
-Finally, the strict model constrained the item variances (i.e., error variances) to be equal for each item across groups.
-These models are normally tested sequentially, and a convenience function `mgcfa` is provided in the supplemental documents for this manuscript.
+A convenience function `mgcfa` is used for these steps or other measurement invariance test orders and combinations.
 Fit indices for the steps for multi-group models are presented in the appendix for comparison of cutoff rules of thumb [@cheung2002] to effect sizes and visualizations presented in this manuscript.
@@
 Only one item in each model was manipulated from the invariant model to create the non-invariant models.
-
-# Results
+Given the data was simulated with a *z*-score scaling, the loading values were simulated at .30 points apart (given $d_{MACS}$ suggestions of .2, .4, .7), the intercepts at .25 points apart, and the residuals at .25 points apart.
+To plan a simulation for your own study, these values can be used to simulate small, medium, and large non-invariance effects by first converting data into *z*-score.
+
+# Package Code Examples
+
+The complete code for this manuscript can be found at <https://osf.io/wev5f/>.
+This tutorial was registered at <https://osf.io/vwf4d>, and the example provided at the end of the manuscript was added after that registration.
+The *R* package and replication/effect sizes was added after the original manuscript submission.
 
@@
 lv ~ 1"
-model.invariant.g2 <- "lv =~ .77*q1 + .43*q2 + .58*q3 + .3*q4 + .61*q5
+model.invariant.g2 <- "lv =~ .81*q1 + .41*q2 + .61*q3 + .31*q4 + .61*q5
 q4 ~~ 1*q4
@@
 
-# loadings
-model.small.load.g2 <- "lv =~ .77*q1 + .43*q2 + .58*q3 + .5*q4 + .61*q5
+# loadings .5, .8, 1.1
+model.small.load.g2 <- "lv =~ .81*q1 + .41*q2 + .61*q3 + .5*q4 + .61*q5
 q1 ~ 0*1
 lv ~ 1"
-model.med.load.g2 <- "lv =~ .77*q1 + .43*q2 + .58*q3 + .6*q4 + .61*q5
+model.med.load.g2 <- "lv =~ .81*q1 + .41*q2 + .61*q3 + .8*q4 + .61*q5
 q1 ~ 0*1
 lv ~ 1"
-model.large.load.g2 <- "lv =~ .77*q1 + .43*q2 + .58*q3 + 1.1*q4 + .61*q5
+model.large.load.g2 <- "lv =~ .81*q1 + .41*q2 + .61*q3 + 1.1*q4 + .61*q5
 q1 ~ 0*1
@@
 # build invariance on intercepts .25, .50, and .75
-model.small.int.g2 <- "lv =~ .77*q1 + .43*q2 + .58*q3 + .34*q4 + .61*q5
+model.small.int.g2 <- "lv =~ .81*q1 + .41*q2 + .61*q3 + .31*q4 + .61*q5
 q4 ~ .25*1
@@
 lv ~ 1"
-model.med.int.g2 <- "lv =~ .77*q1 + .43*q2 + .58*q3 + .34*q4 + .61*q5
+model.med.int.g2 <- "lv =~ .81*q1 + .41*q2 + .61*q3 + .31*q4 + .61*q5
 q4 ~ .5*1
@@
 lv ~ 1"
-model.large.int.g2 <- "lv =~ .77*q1 + .43*q2 + .58*q3 + .34*q4 + .61*q5
+model.large.int.g2 <- "lv =~ .81*q1 + .41*q2 + .61*q3 + .31*q4 + .61*q5
 q4 ~ .75*1
@@
 # build invariance on residuals .25, .50, and .75
-model.small.res.g2 <- "lv =~ .77*q1 + .43*q2 + .58*q3 + .34*q4 + .61*q5
+model.small.res.g2 <- "lv =~ .81*q1 + .41*q2 + .61*q3 + .31*q4 + .61*q5
 q4 ~~ .75*q4
@@
 lv ~ 1"
-model.med.res.g2 <- "lv =~ .77*q1 + .43*q2 + .58*q3 + .34*q4 + .61*q5
+model.med.res.g2 <- "lv =~ .81*q1 + .41*q2 + .61*q3 + .31*q4 + .61*q5
 q4 ~~ .5*q4
@@
 lv ~ 1"
-model.large.res.g2 <- "lv =~ .77*q1 + .43*q2 + .58*q3 + .34*q4 + .61*q5
+model.large.res.g2 <- "lv =~ .81*q1 + .41*q2 + .61*q3 + .31*q4 + .61*q5
 q4 ~~ .25*q4
@@
 # invariant CFA
-results.invariant <- mgcfa(df.invariant, "group", model.overall)
-d_invariant <- lavaan_dmacs(results.invariant$model.configural, RefGroup = "Group 1")
+results.invariant <- 
+  mgcfa(model = model.overall, 
+        data = df.invariant,
+        group = "group",
+        group.equal = c("loadings", "intercepts", "residuals"),
+        meanstructure = T)
+
+d_invariant <- lavaan_dmacs(
+  results.invariant$model_configural, 
+  RefGroup = "Group 1")
 
 # loadings
-results.small.load <- mgcfa(df.small.load, "group", model.overall)
-results.med.load <- mgcfa(df.med.load, "group", model.overall)
-results.large.load <- mgcfa(df.large.load, "group", model.overall)
-
-d_small_load <- lavaan_dmacs(results.small.load$model.configural, RefGroup = "Group 1")
-d_med_load <- lavaan_dmacs(results.med.load$model.configural, RefGroup = "Group 1")
-d_large_load <- lavaan_dmacs(results.large.load$model.configural, RefGroup = "Group 1")
+results.small.load <- 
+  mgcfa(model = model.overall, 
+        data = df.small.load,
+        group = "group",
+        group.equal = c("loadings", "intercepts", "residuals"),
+        meanstructure = T)
+
+results.med.load <- 
+  mgcfa(model = model.overall, 
+        data = df.med.load,
+        group = "group",
+        group.equal = c("loadings", "intercepts", "residuals"),
+        meanstructure = T)
+results.large.load <- 
+  mgcfa(model = model.overall, 
+        data = df.large.load,
+        group = "group",
+        group.equal = c("loadings", "intercepts", "residuals"),
+        meanstructure = T)
+
+d_small_load <- 
+  lavaan_dmacs(results.small.load$model_configural, 
+               RefGroup = "Group 1")
+d_med_load <- 
+  lavaan_dmacs(results.med.load$model_configural, 
+               RefGroup = "Group 1")
+d_large_load <- 
+  lavaan_dmacs(results.large.load$model_configural, 
+               RefGroup = "Group 1")
 
 # intercepts
-results.small.int <- mgcfa(df.small.int, "group", model.overall)
-results.med.int <- mgcfa(df.med.int, "group", model.overall)
-results.large.int <- mgcfa(df.large.int, "group", model.overall)
-
-d_small_int <- lavaan_dmacs(results.small.int$model.configural, RefGroup = "Group 1")
-d_med_int <- lavaan_dmacs(results.med.int$model.configural, RefGroup = "Group 1")
-d_large_int <- lavaan_dmacs(results.large.int$model.configural, RefGroup = "Group 1")
+results.small.int <- 
+  mgcfa(model = model.overall, 
+        data = df.small.int,
+        group = "group",
+        group.equal = c("loadings", "intercepts", "residuals"),
+        meanstructure = T)
+results.med.int <- 
+  mgcfa(model = model.overall, 
+        data = df.med.int,
+        group = "group",
+        group.equal = c("loadings", "intercepts", "residuals"),
+        meanstructure = T)
+results.large.int <- 
+  mgcfa(model = model.overall, 
+        data = df.large.int,
+        group = "group",
+        group.equal = c("loadings", "intercepts", "residuals"),
+        meanstructure = T)
+
+d_small_int <- 
+  lavaan_dmacs(results.small.int$model_configural, 
+               RefGroup = "Group 1")
+d_med_int <- 
+  lavaan_dmacs(results.med.int$model_configural, 
+               RefGroup = "Group 1")
+d_large_int <- 
+  lavaan_dmacs(results.large.int$model_configural, 
+               RefGroup = "Group 1")
 
 # residuals
-results.small.res <- mgcfa(df.small.res, "group", model.overall)
-results.med.res <- mgcfa(df.med.res, "group", model.overall)
-results.large.res <- mgcfa(df.large.res, "group", model.overall)
-
-d_small_res <- lavaan_dmacs(results.small.res$model.configural, RefGroup = "Group 1")
-d_med_res <- lavaan_dmacs(results.med.res$model.configural, RefGroup = "Group 1")
-d_large_res <- lavaan_dmacs(results.large.res$model.configural, RefGroup = "Group 1")
-```
-
-## Code Examples
-
-The complete code for this manuscript can be found at <https://osf.io/wev5f/>, and the function code for the convenience function for multi-group models and plots is found in the appendix.
-This tutorial was registered at <https://osf.io/vwf4d>, and the example provided at the end of the manuscript was added after that registration.
+results.small.res <-
+  mgcfa(model = model.overall, 
+        data = df.small.res,
+        group = "group",
+        group.equal = c("loadings", "intercepts", "residuals"),
+        meanstructure = T)
+results.med.res <- 
+  mgcfa(model = model.overall, 
+        data = df.med.res,
+        group = "group",
+        group.equal = c("loadings", "intercepts", "residuals"),
+        meanstructure = T)
+results.large.res <- 
+  mgcfa(model = model.overall, 
+        data = df.large.res,
+        group = "group",
+        group.equal = c("loadings", "intercepts", "residuals"),
+        meanstructure = T)
+
+d_small_res <- 
+  lavaan_dmacs(results.small.res$model_configural, 
+               RefGroup = "Group 1")
+d_med_res <- 
+  lavaan_dmacs(results.med.res$model_configural,
+               RefGroup = "Group 1")
+d_large_res <- 
+  lavaan_dmacs(results.large.res$model_configural, 
+               RefGroup = "Group 1")
+```
+
+## Multi-group CFA Caculation
+
 First, we would create our model code in *lavaan* syntax [@rosseel2012].
 The `lv` latent variable predicts the five measured variables, which are present as columns in our `df.invariant` data set.
-You would include the dataframe in the `data` argument of our function, the name of the grouping variable in quotes for `group`, and the *lavaan* model syntax in the `model` argument.
-The `mgcfa` function code runs an overall model with all data, regardless of group, each group separately on the model, then the steps described above: configural, metric, scalar, and strict invariance.
+The package does generally require raw data for bootstrapping purposes, and an example of how to simulate data from models and covariance/correlations tables sometimes provided in manuscripts (rather than the raw data) is provided in the supplemental documentation.
 
@@
 In real data, you may wish to run the model steps *without* setting this option, examine the results of a configural or separate models, and then add the option for the values most similar.
-Additionally, you could complete partial invariance steps to determine which value appears most consistent to fix.
-
-```{r eval = T, include = T, echo = T, size = "small"}
+Additionally, you could complete partial invariance steps to determine which value appears most consistent to fix the estimate.
+
+```{r model-example, eval = T, include = T, echo = T, size = "small"}
 # create lavaan model
@@
 head(df.invariant)
+```
+
+The `mgcfa` function is designed to flexibly allow you to leverage `lavaan`'s package functions to calculate multiple measurement steps at once. You would include:
+
+1)  the model syntax in the `model` argument
+2)  the dataframe in the `data` argument of our function
+3)  the name of the grouping variable in quotes for `group`
+4)  and the equality constraints you would like to impose in order in `group.equal`
+5)  `...` any other *lavaan* arguments you would like to use such as `meanstructure` or `estimator`.
+
+Note: you can also use `sample.cov`, `sample.mean`, `sample.nobs` in this step for estimation of multi-group models, but simulated dataframes are needed for bootstrapping replication estimates.
+
+```{r mgcfa-example, echo = T, size = "small"}
 # run our mgcfa function to run all models
-results.invariant <- mgcfa(data = df.invariant, #dataframe
+results.invariant <- 
+  # name of the saved model syntax
+  mgcfa(model = model.overall, 
+        # name of the dataframe
+        data = df.invariant,
+        # name of the grouping variable
         group = "group",
-                           model = model.overall)
+        # equality constraints to impose in order
+        group.equal = c("loadings", "intercepts", "residuals"),
+        # other options to send to lavaan cfa function
+        meanstructure = T)
+
 # what is saved for you
@@
 
-The results are saved as a list and include the following:
-
-1)  `model_coef`: a tidy dataframe with *all* model's coefficients saved from the *lavaan* outputs.
-Note that we can see that the intercept `~1` is set for question 1 but freely estimated for the latent variable.
-
-```{r echo = T, include = T, size = "small"}
+The following output is saved:
+
+1)  `model_coef`: The parameter estimates for each model with the model step included in a *model* column.
+This set of coefficients can be used for other functions.
+This dataframe is created with *broom*'s `tidy()` function if you wish to recreate this table without running the `mgcfa()` function [@robinson2023].
+
+```{r mgcfa-output1, echo = T, include = T, size = "small"}
 results.invariant$model_coef[1:10 , ]
@@
 
-2)  `model_fit`: a tidy dataframe with *all* model's fit indices saved from the *lavaan* outputs.
-
-```{r echo = T, include = T, size = "small"}
+2)  `model_fit`: The model fit indices from `fitmeasures()` to review for overall model fit and invariance judgments. The name of the model is included in a *model* column.
+
+```{r mgcfa-output2, echo = T, include = T, size = "small"}
 head(results.invariant$model_fit)
@@
 
-3)  Saved *lavaan* fitted objects that you can use the `summary()`, `parameterEstimates()`, `fitIndices()`, etc.
-on.
-Overall model indicates the model without grouping variables testing all data on the proposed model structure.
-This model is then tested separately for each group (`model.group1`, `model.group2`).
-The final models follow the @brown2015 naming convention for sequential steps for testing MGCFA for measurement invariance (`model.configural`, `model.metric`, `model.scalar`, `model.strict`).
-
-The results from the `model_coef` table can then be used directly in the suggested plotting function. The plot outputs will be described below. First, here are the arguments for the function:
+3)  `model_overall`: A saved *lavaan* fitted model of all groups together without any equality constraints or grouping variables.
+These objects can be used with any function that normally takes a saved model: `parameterEstimates()`, `modificationIndices()`, `semPlot::semPaths()`, and so on [@epskamp2022].
+4)  `group_models`: A list of saved fitted models for each group separately.
+5)  `model_configural`: A saved fitted model for the configural model that nests together each group into one model with no other constraints.
+6)  `invariance_models`: A list of saved fitted models that consecutively adds `group.equal` constraints.
+
+## Visualization of Invariance
+
+### Package Function
+
+The results from the `model_coef` table can then be used directly in `plot_mi()`. The plot outputs will be described below. First, here are the arguments for the function:
 
@@
 This function will only run for models that have used the grouping function (i.e., configural, metric, scalar, and strict or other combinations/steps you wish to examine).
-
 2)  `model_step`: Which model do you want to plot? You should match this name to the one you want to extract from your model column in the `data_coef`.
-
 3)  `item_name`: Which observed variable from your model syntax do you want to plot? Please list this variable name exactly how it appears in the model.
-
 4)  `x_limits`: What do you want the x-axis limits to be for your invariance plot?
@@
 You can use this parameter to zoom out to a more traditional histogram using `c(-2, 2)`.
-
 5)  `y_limits`: What do you want the y-axis limits to be for your invariance plot?
@@
 Use only two numbers, a lower and upper limit.
-
-6)  `ci_level`: What confidence limit do you want to plot? Use 1 - $\alpha$.
-
+6)  `conf.level`: What confidence limit do you want to plot? Use 1 - $\alpha$.
 7)  `model_results`: In this argument, include the saved *lavaan* output for the model listed in the `model_step` argument.
-
 8)  `lv_name`: Include the name of the latent variable, exactly how it is listed in your *lavaan* syntax.
@@
 If you have items that load onto multiple latent variables, you will need to make multiple plots.
-
-```{r eval = F, echo = T, include = T, size = "small"}
-plot_mgcfa(
-  data_coef = results.invariant$model_coef, # output from model_coef
-  model_step = "Configural", # which model do you want to plot
-  item_name = "q4", # name of observed item
-  x_limits = c(-1,1), # latent variable limits to graph
-  y_limits = c(min(df.invariant$q4), max(df.invariant$q4)), # Y min and max in data 
-  ci_level = .95, # what ci do you want
-  model_results = results.invariant$model.configural, # what model results do you want 
-  lv_name = "lv" # which latent variable do you want 
-)
-```
-
-## Visualization of Invariance
-
-The output from this model can be found in Figure \@ref(fig:invariant-pic).
+9) `plot_groups`: If you include more than two groups in a multi-group model, the automatic assumption is that you want the first two groups for this visualization.
+If not, include the names of the groups here to plot.
+
+```{r plot-example, eval = T, echo = T, include = T, size = "small"}
+invariant.plot <- 
+  plot_mi(
+    # output from model_coef
+    data_coef = results.invariant$model_coef, 
+    # which model do you want to plot
+    model_step = "Configural", 
+    # name of observed item
+    item_name = "q4", 
+    # latent variable limits to graph
+    x_limits = c(-1,1), 
+    # Y min and max in data 
+    y_limits = c(min(df.invariant$q4), max(df.invariant$q4)),
+    # what ci do you want
+    conf.level = .95, 
+    # what model results do you want 
+    model_results = results.invariant$model_configural,
+    # which latent variable do you want 
+    lv_name = "lv" 
+)
+
+names(invariant.plot)
+```
+
+The output from this function are several *ggplot2* objects that can be edited or saved directly using *ggplot2* functionality [@R-ggplot2].
+
+1) `complete`: The output from this model can be found in Figure \@ref(fig:invariant-pic).
 On the left hand side, the item invariance is plotted, and on the right hand side, the latent mean distributions for the two groups are plotted.
@@
 All parameter estimates are plotted on the unstandardized estimates and their confidence interval based on the standard error of the estimate.
-All plots are made with *ggplot2* [@R-ggplot2] and *cowplot* [@wilke2020].
-
-### Loadings
-
+All plots are made with *ggplot2* and *cowplot* [@wilke2020].
+
+```{r invariant-pic, include = T, fig.cap = "Invariant Model Visualization"}
+invariant.plot$complete
+```
+
+2) `intercept`: Only the left hand side of the complete plot designed to represent intercepts and factor loadings.
 Factor loadings represent the slope of the regression equation for the latent variable predicting the scores on the observed variable ($\hat{Y} \sim b_0 + b_1X + \epsilon$).
-Therefore, the latent variable is shown on the x-axis using standardized values (i.e., *z*-scores) where -1 indicates one standard deviation below the mean for the latent variable, 0 indicates the mean for the latent variable and so on.
 The y-axis indicates the observed variable scores, and here, the plot includes the entire range of the scale of the data for item four.
@@
 In this plot, while the coefficients for each group are not literally equal, the overlapping and parallel slope bands indicate they are not different practically.
-
-### Intercepts
 
@@
 
-### Residuals
-
+3) `mean`: The right hand side of the complete plot graphing the latent variable means and density from the data.
+The latent variable is shown on the x-axis using standardized values (i.e., *z*-scores) where -1 indicates one standard deviation below the mean for the latent variable, 0 indicates the mean for the latent variable and so on.
+The lines indicate the means of the latent variables from the simulated dataset.
+Group labels are represented in the figure caption on the bottom.
+Group 1 is usually the group that is alphabetically first in the data set or whichever group is the first that appears when using the `levels()` command.
+
+4) `variance`: A split geom violin plot indicating the variance distribution of the plotted item.
 Residuals are trickier to plot, as they are the left over error when predicting the observed variables $\epsilon$.
@@
 Note that the placement has nothing to do with the x or y-axis and is designed to always show in the same location, regardless of size/value.
-
-### Latent Means
-
-The overall impact of differences on the latent means can be found in the right hand visualization.
-The latent means are calculated by using the `lavPredict` function and then plotted as overlapping histograms.
-The vertical colored lines represent the mean for each group, and the spread of the distribution can be examined using the density coloring.
-Finally, group labels are represented in the figure caption on the bottom.
-Group 1 is usually the group that is alphabetically first in the data set or whichever group is the first that appears when using the `levels()` command.
-
-```{r invariant-pic, include = T, fig.cap = "Invariant Model Visualization"}
-plot_mgcfa(
-  data_coef = results.invariant$model_coef, # output from model_coef
-  model_step = "Configural", # which model
-  item_name = "q4", # name of observed item
-  x_limits = c(-1,1), # LV limits to graph
-  y_limits = c(min(df.invariant$q4), max(df.invariant$q4)), # Y min and max in data 
-  ci_level = .95, # what ci do you want
-  model_results = results.invariant$model.configural, # what model results do you want 
-  lv_name = "lv"
-)
-```
-
-### Graphing Effect Size
+The plots are included separately so they can be arranged in a different fashion if desired.
+
+### Simulated Results
 
@@
 ```{r small-load-pic, include = T, fig.cap = "Small Loadings Model Visualization"}
-plot_mgcfa(
+plot_mi(
   data_coef = results.small.load$model_coef, # output from model_coef
@@
   y_limits = c(min(df.small.load$q4), max(df.small.load$q4)), # Y min and max in data 
-  ci_level = .95, # what ci do you want
-  model_results = results.small.load$model.configural, # what model results do you want 
+  conf.level = .95, # what ci do you want
+  model_results = results.small.load$model_configural, # what model results do you want 
   lv_name = "lv"
-)
+)$complete
 ```
@@
 ```{r med-load-pic, include = T, fig.cap = "Medium Loadings Model Visualization"}
-plot_mgcfa(
+plot_mi(
   data_coef = results.med.load$model_coef, # output from model_coef
@@
   y_limits = c(min(df.med.load$q4), max(df.med.load$q4)), # Y min and max in data 
-  ci_level = .95, # what ci do you want
-  model_results = results.med.load$model.configural, # what model results do you want 
+  conf.level = .95, # what ci do you want
+  model_results = results.med.load$model_configural, # what model results do you want 
   lv_name = "lv"
-)
+)$complete
 ```
@@
 ```{r large-load-pic, include = T, fig.cap = "Large Loadings Model Visualization"}
-plot_mgcfa(
+plot_mi(
   data_coef = results.large.load$model_coef, # output from model_coef
@@
   y_limits = c(min(df.large.load$q4), max(df.large.load$q4)), # Y min and max in data 
-  ci_level = .95, # what ci do you want
-  model_results = results.large.load$model.configural, # what model results do you want 
+  conf.level = .95, # what ci do you want
+  model_results = results.large.load$model_configural, # what model results do you want 
   lv_name = "lv"
-)
+)$complete
 ```
@@
 ```{r small-int-pic, include = T, fig.cap = "Small Intercepts Model Visualization"}
-plot_mgcfa(
+plot_mi(
   data_coef = results.small.int$model_coef, # output from model_coef
-  model_step = "Metric", # which model
+  model_step = "loadings", # which model
   item_name = "q4", # name of observed item
@@
   y_limits = c(min(df.small.int$q4), max(df.small.int$q4)), # Y min and max in data 
-  ci_level = .95, # what ci do you want
-  model_results = results.small.int$model.metric, # what model results do you want 
+  conf.level = .95, # what ci do you want
+  model_results = results.small.int$invariance_models$model.loadings, # what model results do you want 
   lv_name = "lv"
-)
+)$complete
 ```
@@
 ```{r med-int-pic, include = T, fig.cap = "Medium Intercepts Model Visualization"}
-plot_mgcfa(
+plot_mi(
   data_coef = results.med.int$model_coef, # output from model_coef
-  model_step = "Metric", # which model
+  model_step = "loadings", # which model
   item_name = "q4", # name of observed item
@@
   y_limits = c(min(df.med.int$q4), max(df.med.int$q4)), # Y min and max in data 
-  ci_level = .95, # what ci do you want
-  model_results = results.med.int$model.metric, # what model results do you want 
+  conf.level = .95, # what ci do you want
+  model_results = results.med.int$invariance_models$model.loadings, # what model results do you want 
   lv_name = "lv"
-)
+)$complete
 ```
@@
 ```{r large-int-pic, include = T, fig.cap = "Large Intercepts Model Visualization"}
-plot_mgcfa(
+plot_mi(
   data_coef = results.large.int$model_coef, # output from model_coef
-  model_step = "Metric", # which model
+  model_step = "loadings", # which model
   item_name = "q4", # name of observed item
@@
   y_limits = c(min(df.large.int$q4), max(df.large.int$q4)), # Y min and max in data 
-  ci_level = .95, # what ci do you want
-  model_results = results.large.int$model.metric, # what model results do you want 
+  conf.level = .95, # what ci do you want
+  model_results = results.large.int$invariance_models$model.loadings, # what model results do you want 
   lv_name = "lv"
-)
+)$complete
 ```
@@
 ```{r small-res-pic, include = T, fig.cap = "Small Residuals Model Visualization"}
-plot_mgcfa(
+plot_mi(
   data_coef = results.small.res$model_coef, # output from model_coef
-  model_step = "Scalar", # which model
+  model_step = "intercepts", # which model
   item_name = "q4", # name of observed item
@@
   y_limits = c(min(df.small.res$q4), max(df.small.res$q4)), # Y min and max in data 
-  ci_level = .95, # what ci do you want
-  model_results = results.small.res$model.scalar, # what model results do you want 
+  conf.level = .95, # what ci do you want
+  model_results = results.small.res$invariance_models$model.intercepts, # what model results do you want 
   lv_name = "lv"
-)
+)$complete
 ```
@@
 ```{r med-res-pic, include = T, fig.cap = "Medium Residuals Model Visualization"}
-plot_mgcfa(
+plot_mi(
   data_coef = results.med.res$model_coef, # output from model_coef
-  model_step = "Scalar", # which model
+  model_step = "intercepts", # which model
   item_name = "q4", # name of observed item
@@
   y_limits = c(min(df.med.res$q4), max(df.med.res$q4)), # Y min and max in data 
-  ci_level = .95, # what ci do you want
-  model_results = results.med.res$model.scalar, # what model results do you want 
+  conf.level = .95, # what ci do you want
+  model_results = results.med.res$invariance_models$model.intercepts, # what model results do you want 
   lv_name = "lv"
-)
+)$complete
 ```
@@
 ```{r large-res-pic, include = T, fig.cap = "Large Residuals Model Visualization"}
-plot_mgcfa(
+plot_mi(
   data_coef = results.large.res$model_coef, # output from model_coef
-  model_step = "Scalar", # which model
+  model_step = "intercepts", # which model
   item_name = "q4", # name of observed item
@@
   y_limits = c(min(df.large.res$q4), max(df.large.res$q4)), # Y min and max in data 
-  ci_level = .95, # what ci do you want
-  model_results = results.large.res$model.scalar, # what model results do you want 
+  conf.level = .95, # what ci do you want
+  model_results = results.large.res$invariance_models$model.intercepts, # what model results do you want 
   lv_name = "lv"
-)
+)$complete
+```
+
+## Partial Invariance Calculation
+
+### Package Function
+
+The results of the simulated models are presented in the appendix, demonstrating that each simulated dataset shows partial invariance if item four is allowed to vary between groups.
+The function takes the following arguments:
+
+1) `saved_model`: The saved *lavaan* model with the equality constraints at the level of measurement invariance you would like to examine for partial invariance. 
+2) `data`: The dataframe where the model was estimated. 
+3) `model`: The model syntax for the overall model.
+4) `group`: The grouping variable column in the dataframe. 
+5) `group.equal`: The equality constraints including in your original multi-group tests. 
+6) `partial_step`: The level of partial invariance you wish to test.
+
+```{r partial-example, echo = T, size = "small"}
+partial.invariant <-
+  partial_mi(
+    # saved model output with constraints
+    saved_model = results.invariant$invariance_models$model.residuals,
+    # dataframe from model 
+    data = df.invariant,
+    # model syntax 
+    model = model.overall,
+    # group column name 
+    group = "group",
+    # group equality constraints from your mgcfa
+    group.equal = c("loadings", "intercepts", "residuals"),
+    # which step you want to examine for partial invariance
+    partial_step = "residuals"
+    )
+
+names(partial.invariant)
+```
+
+In this function, each parameter with the appropriate *lavaan* syntax is relaxed individually (i.e., `~1` for intercepts, `~~` for residuals, etc.).
+The fitted models are saved in the `models` output, and the `fit_table` output includes all fit indices for each model to investigate potential areas of partial invariance based on the researcher's desired criterion.
+Note: the `partial_step` function is used to determine which types of `op` or operators to freely estimate between groups.
+If one chooses residuals, you will also freely estimate the residual for the latent variable or any other residuals found in the model.
+These items may be ignored if they were not meant to be included.
+
+```{r partial-example2, echo = T, size = "small"}
+head(partial.invariant$fit_table %>% 
+       dplyr::select(free.parameter, cfi, rmsea))
+```
+
+## Replication and Effect Size: Model
+
+### Package Function
+
+The `bootstrap_rr` function in *visualizemi* was designed to estimate the likely replication of overall model invariance with the assumption that the data used for the estimation represents the larger population.
+The following arguments are used:
+
+1) `saved_configural`: a saved fitted model at the configural level with no equality constraints.
+This model should include all other *lavaan* settings you would like to use, such as `estimator` or `ordered`.
+
+```{r boot-rr, echo = T, eval = F, size = "small"}
+boot.model.invariant <- 
+  bootstrap_rr(
+    # saved configural model 
+    saved_configural = results.invariant$model_configural,
+    # dataframe
+    data = df.invariant,
+    # model syntax
+    model = model.overall, 
+    # group variable column in dataframe
+    group = "group",
+    # number of bootstraps
+    nboot = 1000, 
+    # which fit index you would like to use
+    invariance_index = "cfi",
+    # what is your criterion for that fit index
+    invariance_rule = .01,
+    # what equality constraints are you testing 
+    group.equal = c("loadings", "intercepts", "residuals")
+  )
+```
+
+The data included in this function will be sampled, with replacement, at the same size as the current dataset, and the included invariance equality constraints are estimated.
+Each step will be compared to the previous step using the invariance index and comparison rule entered.
+The output is a dataframe of the proportion of non-invariant bootstraps from the real data and the same bootstrapped dataset with the group labels randomly assigned.
+The effect size comparison of proportions, $h$, for non-invariant comparisons:
+
+$$h_{nmi} = 2 \times (asin\sqrt{p_{data}} - asin\sqrt{p_{random}})$$
+The alternative, $h_{mi}$, for effect size of measurement invariance replication would simply be the inverse sign of $h_{nmi}$ and is also included in the table.
+Two additional columns $h_{nmi_p}$ and $h_{nmi_p}$ represent the $h$ values divided by the upper bound of $h$ (i.e., $\pi$), to help with interpretation of the effect size (thus, bounding $h$ to -1 to 1).
+
+### Simulated Results
+
+Figure \@ref(fig:boot-rr-pic) portrays the $h_{nmi_p}$ values by simulated non-invariance, strength of non-invariance, and type of equality constraint.
+This image represents 100 simulations of data by 1000 bootstrapped runs (averaged) to explore the expected pattern of results.
+The bars are arranged to show what a researcher might inspect when thinking about replication possibilities and their effect sizes (i.e., only three bars for each equality constraint would be calculated).
+
+```{r boot-rr-pic, include = T, fig.cap = "Visualization of the effect size of bootstrapped replication proportions on simulated data.
+Each panel indicates the simulated data type, colors represent the differences in the strength of the non-invariance, and the bars on the x-axis represent the effect size for the equality constraint.
+"}
+
+boot_rr_DF <- boot_rr_DF %>% 
+  mutate(type_size = ifelse(
+    type == "Invariant", "None", ifelse(
+      grepl("Small", type), "Small", ifelse(
+        grepl("Medium", type), "Medium", "Large"
+      )
+    )
+  ),
+  type_type = ifelse(
+    type == "Invariant", "Invariant", ifelse(
+      grepl("Loadings", type), "Loadings", ifelse(
+        grepl("Intercepts", type), "Intercepts", "Residuals"
+      )
+    ) 
+  ),
+  model = factor(model, 
+                 levels = c("loadings", "intercepts", "residuals"),
+                 labels = c("Loadings", "Intercepts", "Residuals")),
+  type_size = factor(type_size, 
+                     levels = c("None", "Small", "Medium", "Large")),
+  type_type = factor(type_type, 
+                     levels = c("Invariant", "Loadings", "Intercepts", "Residuals")))
+
+prop_boot_rr <- ggplot(boot_rr_DF %>% 
+                         filter(type_type != "Invariant"), 
+                       aes(x = model, 
+                       y = h_nmi_p,
+                       fill = type_size)) + 
+  stat_summary(fun = "mean", 
+               position = "dodge", 
+               geom = "bar") + 
+  stat_summary(fun.data = "mean_cl_normal",
+               geom = "errorbar", 
+               position = position_dodge(width = .9),
+               width = .2) + 
+  theme_classic() + 
+  facet_grid(type_type~type_size) + 
+  scale_fill_discrete(name = "Size of Non-Invariance") + 
+  xlab("Equality Constraints") + 
+  ylab("Normalized Effect Size") + 
+  theme(legend.position = "bottom") + 
+  geom_hline(yintercept = 0) +
+  # geom_hline(yintercept = 1) + 
+  NULL
+
+prop_boot_rr
+
+means_invariant <- boot_rr_DF %>% filter(type == "Invariant") %>% group_by(model) %>% summarize(mean_h = mean(h_nmi_p))
+```
+
+In the data that was simulated to be invariant between groups, effect sizes are still non-zero (loadings $h_{nmi_p}$ = `r apa_num(means_invariant$mean_h[1])`, intercepts = $h_{nmi_p}$ = `r apa_num(means_invariant$mean_h[2])`, $h_{nmi_p}$ = `r apa_num(means_invariant$mean_h[3])`).
+This result mirrors the effects found in the literature - that often, many models fail to show invariance, and potentially not because measurement is poor but because of natural random variation in parameter estimates.
+This result also indicates the need to be able to identify if specific parameters are driving the differences, which is shown in the next section.
+
+Next, Figure \@ref(fig:boot-rr-pic) demonstrates the patterns one might find for small, medium, and large effects at each type of invariance when data is simulated with *one* difference.
+For loadings, the pattern shows a larger effect for loadings with zero or negative effect sizes for other effect sizes.
+The intercept simulations show non-zero effect sizes in the loadings and intercepts, likely for the same reasons $d_{MACS}$ is interpreted as a combined effect size.
+When intercepts are changed, loadings may naturally shift with those means.
+Last, the residual results present an unexpected pattern, wherein the effect is primarily seen in the loadings, rather than the residuals step.
+However, when distributions of error variance are different, one may expect that those effects are pushed toward the loadings as well (as values can vary more, thus potentially weakening the relationship between observed and latent variable).
+
+An example of interpretation on real data is given in a later section.
+From a research study, only one effect size for each equality constraint would be calculated.
+The interpretation will often be up to the researcher's smallest effect of interest, and this simulation gives some guidance that the values should not be interpreted with traditional rules of thumb.
+The pattern of effects is potentially the most useful information: 1) positive effects on the loadings with negative or very close to zero effects on the other parameters may indicate a non-replication in loadings, 2) equal effects on loadings and intercepts with smaller or negative effects may indicate intercepts may be an issue, and 3) residuals may be determined by the same pattern as loadings but with a smaller ratio of loadings to residuals effect (i.e., loadings $h_{nmi}$ / residuals $h_{nmi}$.
+The "size" could be determined by the ratio of effect sizes for each constraint.
+Of course, this represents one simulation study, and results from many studies in a meta-analysis would be fruitful for future work.
+
+## Replication and Effect Size: Parameters
+
+### Package Function
+
+After examining the overall model potential replication effect size, the individual parameters within a model can be bootstrapped for partial invariance to with that parameter relaxed (overall partial model statistics) and the difference in group parameter estimates (parameter effect size).
+This function uses arguments seen in other functions, so they will not be repeated here.
+The general setup consists of using the model you think could be partially invariant in the `saved_model` argument and the fit index for comparison for the model with less constraints in `invariance_compare`.
+This example examines the loadings in the invariant model, so `saved_model` uses the `mgcfa` output for equality constraints present on the loadings and compares that model to the configural model with no equality constraints on the loadings.
+The `partial_step` argument will be used to determine which operation syntax (i.e.
+`=~` for loadings) to relax for modeling.
+
+```{r boot-partial, echo = T, size = "small", eval = F}
+boot.partial.invariant <- 
+      bootstrap_partial(
+        # saved model you want to examine the partial loadings for 
+        saved_model = results.invariant$invariance_models$model.loadings,
+        # the dataset 
+        data = df.invariant, 
+        # the model 
+        model = model.overall,
+        # the group variable in the dataset
+        group = "group", 
+        # number of bootstraps
+        nboot = 1000,
+        # which fit index you would like to use to determine partial invariance
+        invariance_index = "cfi", 
+        # what is the invariance rule 
+        invariance_rule = .01, 
+        # what are we comparing the saved model fit index to 
+        invariance_compare = fitmeasures(results.invariant$model_configural, "cfi"), 
+        # what step are we using for invariance
+        partial_step = "loadings", 
+        # what equality constraints should be imposed 
+        group.equal = c("loadings")
+      )
+```
+
+```{r partial-boot-print, echo = T, size = "small"}
+names(boot.partial.invariant)
+```
+
+The saved output includes several dataframes and plots.
+The first is the `boot_DF` which the summary of each run in a dataframe for plotting or summarization.
+This dataframe includes the estimate for each paramter (`term`) separated by group and type (`boot_1`, `boot_2` are the bootstrapped estimates for group 1 and group 2, while the same `random` columns indicate the randomly assigned groups).
+The fit index used to determine invariance is included for bootstrapped and random estimates, and then the differences between groups and if they were "invariant" or not given the researcher supplied rule.
+
+```{r boot-partial-DF, echo = T, size = "small"}
+head(boot.partial.invariant$boot_DF)
+```
+
+Next, the `boot_summary` includes a summarized form of the bootstrapped results from separated by bootstrapping versus random and invariant/non-invariant.
+The $d_s$ for between groups Cohen's $d$ is shown below, and the non-central confidence interval is included.
+Effect sizes are only calculated when the number of bootstrapped estimates is at least 10% of the data - therefore, you would not receive effect sizes with almost no bootstrapped runs.
+This dataframe should be used to determine which parameter may be different and at what size between groups in a replication of the study.
+
+```{r boot-summary-DF, echo = T, size = "small"}
+boot.partial.invariant$boot_summary %>% 
+  dplyr::select(term, d_boot, d_random)
+```
+
+The `boot_effects` table creates a summary similar to the overall model replication table based on the proportion of runs that were considered invariant versus not for each parameter.
+Note that the effects match the overall results, such that simulated invariant data appears to still show the likelihood that loadings may not replicate in a similar dataset.
+
+```{r boot-effects-DF, echo = T, size = "small"}
+boot.partial.invariant$boot_effects
+```
+
+Plots of the results from dataframes can be found within the `bootstrap_partial()` function.
+Figure \@ref(fig:invariance-partial-fig) shows the difference between parameters for groups in the bootstrapped and randomly assigned group runs.
+Figure \@ref(fig:density-partial-fig) shows the density plot of the estimates for each group organized by bootstrapped and randomly assigned groups and the invariance decision for each bootstrapped run.
+Last, Figure \@ref(fig:effect-partial-fig) indicates the $d_s$ value between groups with an indication of the number of data points in each estimate (i.e., dot size).
+These visualizations should allow a researcher to understand the likelihood of replication for each parameter, as well as the potential size of the differences.
+Therefore, one could indicate a specific smallest effect size of interest, rather than a invariance cut-off rule of thumb when planning a replication or registered report.
+
+```{r invariance-partial-fig, include = T, fig.cap = "Visualization of the difference score between groups by parameter for invariant and non-invariant bootstrapped and randomly assigned group data."}
+boot.partial.invariant$invariance_plot
+```
+
+```{r density-partial-fig, include = T, fig.cap = "Visualization of the number of estimates for each group by bootstrapped and randomly assigned group runs by their invariance decision."}
+suppressMessages(boot.partial.invariant$density_plot)
+```
+
+```{r effect-partial-fig, include = T, fig.cap = "Visualization of effect size between groups by parameter for invariant and non-invariant bootstrapped and randomly assigned group data.
+The size of the dots indicate the number of data points for that estimate."}
+boot.partial.invariant$effect_invariance_plot
+```
+
+### Simulated Results
+
+```{r create-plot-partial}
+# make all the graphs boot long ----
+boot_long <- 
+  bind_rows(boot.df.full %>% 
+              dplyr::select(term, boot_difference, boot_index_difference, type) %>% 
+              rename(difference = boot_difference, index_difference = boot_index_difference) %>%
+              mutate(type_estimate = "Bootstrapped"), 
+            boot.df.full %>% 
+              dplyr::select(term, random_difference, random_index_difference, type) %>% 
+              rename(difference = random_difference, index_difference = random_index_difference) %>% 
+              mutate(type_estimate = "Random")) %>% 
+  mutate(type_together = paste0(type, " " , type_estimate ))
+
+label_graph <- c(`TRUE` = "Invariant", `FALSE` = "Non-Invariant")
+
+# make all the graps summary long ----
+# summarize the overall
+boot.partial.summary <- boot.partial.summary.full %>% 
+  dplyr::select(-run_number, computer) %>% 
+  group_by(term, invariant, type) %>% 
+  summarize_at(vars(mean_boot_1:d_random_high), mean, na.rm = TRUE)
+
+boot_summary_long <- 
+  bind_rows(boot.partial.summary %>% 
+              dplyr::select(term, invariant, n_boot, type, starts_with("d_boot")) %>% 
+              rename(n = n_boot, 
+                     d_low = d_boot_low, 
+                     d = d_boot, 
+                     d_high = d_boot_high) %>% 
+              mutate(type_estimate = "Bootstrapped"), 
+            boot.partial.summary %>% 
+              dplyr::select(term, invariant, n_random, type,
+                                    starts_with("d_random")) %>% 
+              rename(n = n_random, 
+                     d_low = d_random_low, 
+                     d = d_random, 
+                     d_high = d_random_high) %>% 
+              mutate(type_estimate = "Random"))
+
+## make all the graphs effects long ----
+# summarize the effects
+boot.effects.summary <- boot.effects.summary.full %>% 
+  dplyr::select(-run_number, -computer) %>% 
+  group_by(term, type) %>% 
+  summarize_at(vars(non_invariant:h_mi_p), mean, na.rm = TRUE)
+
+density_long <- 
+  bind_rows(
+    boot.df.full %>% 
+      dplyr::select(term, boot_index_difference, boot_1, boot_2, type) %>% 
+      pivot_longer(cols = c(boot_1, boot_2), 
+                   names_to = "group", 
+                   values_to = "estimate") %>% 
+      rename(invariant = boot_index_difference) %>% 
+      mutate(type_estimate = "Bootstrapped"), 
+    boot.df.full %>% 
+      dplyr::select(term, random_index_difference, random_1, random_2, type) %>% 
+      pivot_longer(cols = c(random_1, random_2), 
+                   names_to = "group", values_to = "estimate") %>% 
+      rename(invariant = random_index_difference) %>% 
+      mutate(type_estimate = "Random")) %>% 
+  mutate(group = gsub("boot_1|random_1", "Group 1", group), 
+         group = gsub("boot_2|random_2", "Group 2", group), 
+         invariant = factor(invariant, 
+                            levels = c("TRUE", "FALSE"), 
+                            labels = c("Invariant", "Non-Invariant")))
+
+```
+
+Figure \@ref(fig:effect-large-loading-pic) shows the effect size differences within large loadings simulations.
+The results demonstrate that most of the loadings were considered non-invariant in the bootstrapped models (while holdings all others equal).
+This result is partially due to simulating very good data, so small changes in loadings results in a drop in fit for our chosen invariance index.
+However, we can use this graph to show that question four shows a possible effect size ranging from `r boot_summary_long %>% filter(type == "Large Loadings") %>% filter(invariant == FALSE) %>% filter(term == "lv =~ q4") %>% filter(type_estimate == "Bootstrapped") %>% pull(d_low) %>% apa_num()` to `r boot_summary_long %>% filter(type == "Large Loadings") %>% filter(invariant == FALSE) %>% filter(term == "lv =~ q4") %>% filter(type_estimate == "Bootstrapped") %>% pull(d_high) %>% apa_num()`.
+The $h_{nmi_p}$ value for question four was `r boot.effects.summary %>% filter(type == "Large Loadings") %>% filter(term == "lv =~ q4") %>% pull(h_nmi_p) %>% apa_num()`, representing about a quarter of a possible total effect.
+Last, the density plot in Figure \@ref(fig:density-large-loading-pic) shows the separation of the two different groups loadings in item four, thus, illustrating group differences in the findings for their loadings.
+Each of the other combination of plots can be found in the supplemental materials.
+
+```{r effect-large-loading-pic, fig.cap="Bootstrapped and Random Group effect size differences in loadings for the Large Loading difference simulation.
+The size of the point reprensents the number of data points included in that calculation."}
+effect_invariance_plot <- 
+  ggplot(boot_summary_long %>% 
+           filter(type == "Large Loadings"), 
+         aes(term, d, color = type_estimate)) + 
+  theme_classic() + 
+  facet_wrap(~invariant, labeller = as_labeller(label_graph)) +
+  scale_color_discrete(name = "Type of Estimate") + 
+  geom_point(aes(size = n)) + 
+  geom_errorbar(aes(ymin = d_low, ymax = d_high), width = 0.2) + 
+  xlab("Estimated Item") + 
+  ylab("Group Effect Size") + 
+  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1), 
+        legend.position = "bottom") + 
+  geom_hline(yintercept = 0) + 
+  coord_flip()
+
+suppressWarnings(effect_invariance_plot)
+```
+
+```{r density-large-loading-pic, fig.cap="Bootstrapped and Random density plots for invariant and non-invariant bootstrapped partial effects examining only large loadings."}
+density_plot <- ggplot(density_long %>% 
+                        filter(type == "Large Loadings"), 
+                       aes(x = estimate, y = term, fill = group)) + 
+  geom_density_ridges(alpha = 0.7, scale = 0.9) + 
+  facet_grid(invariant ~ type_estimate) + 
+  theme_classic() + 
+  xlab("Estimated Score") + 
+  ylab("Parameter") + 
+  scale_fill_discrete(name = "Group")
+
+suppressMessages(density_plot)
 ```
@@
 
-```{r eval = F, include = F}
+```{r grab-data, eval = F, include = F}
 library(rio)
@@
 DF <- bind_rows(
-  import("data/Adult CFA.sav") %>% select(-Age) %>% 
+  import("data/Adult CFA.sav") %>% dplyr::select(-Age) %>% 
     mutate(sample = "Clinical"),
-  import("data/Adult EFA.sav") %>% select(-Age) %>% 
+  import("data/Adult EFA.sav") %>% dplyr::select(-Age) %>% 
     mutate(sample = "Clinical"),
-  import("data/Student CFA.sav") %>% select(-Age) %>% 
+  import("data/Student CFA.sav") %>% dplyr::select(-Age) %>% 
     mutate(sample = "Student"),
-  import("data/Student EFA.sav") %>% select(-Age) %>% 
+  import("data/Student EFA.sav") %>% dplyr::select(-Age) %>% 
     mutate(sample = "Student")
-) %>% select(RS1:RS14, sample)
+) %>% dplyr::select(RS1:RS14, sample)
 
@@
 
-```{r echo = T, include = T, size = "small"}
-# load the data
-load("RS14.Rdata")
+```{r load-RS, echo = T, include = T, size = "small"}
+# load the data, it is called DF
+load("manu_data/RS14.Rdata")
 
@@
 # run the multi-group CFA
-results.rs <- mgcfa(data = DF, 
+results.rs <- mgcfa(
+  model = model.rs,
+  data = DF, 
   group = "sample", 
-                    model = model.rs)
-```
-
-```{r eval = F, echo = T, include = T, size = "small"}
+  group.equal = c("loadings", "intercepts", "residuals")
+  )
+```
+
+```{r show-rs-results, eval = F, echo = T, include = T, size = "small"}
 # how to get results in table 
 results.rs$model_fit %>% 
-        select(model, AIC, BIC, cfi, tli, rmsea, srmr)
+        dplyr::select(model, AIC, BIC, cfi, tli, rmsea, srmr)
 ```
@@
 apa_table(results.rs$model_fit %>% 
-        select(model, AIC, BIC, cfi, tli, rmsea, srmr), 
+        dplyr::select(model, AIC, BIC, cfi, tli, rmsea, srmr), 
         digits = 3, 
@@
 
-Table \@ref(fig:invariant-pic) indicates the results after running the one-factor model.
+Table \@ref(tab:rs-table) indicates the results after running the one-factor model.
 There are several guidelines for assessing assessing a degradation in model fit [@cheung2002; @jin2020; @putnick2016; @counsell2020; @cao2022] but for the purposes of this illustration $\Delta$CFI \> .01 will be used.
-Table \@ref(fig:invariant-pic) indicates that fit was degraded when the constraint on equal item intercepts was added.
+Table \@ref(tab:rs-table) indicates that fit was degraded when the constraint on equal item intercepts was added.
 The code below provides an example of testing each item individually by relaxing the constraints and recalculating the CFI.
@@
 
-```{r echo = T, include = T, size = "small"}
-# write out the partial invariance codes for intercepts ~1
-partial_syntax <- paste(colnames(DF)[1:14], "~1") 
-partial_syntax
-# create a place to save the CFIs for each item separately
-CFI_list  <- 1:length(partial_syntax)
-names(CFI_list) <- partial_syntax
-# loop over the items and calculate CFI 
-# with that item freely estimated
-for (i in 1:length(partial_syntax)){
-
-  temp <- cfa(model = model.rs, 
+```{r partial-RS, echo = T, include = T, size = "small"}
+partial.rs <-
+  partial_mi(
+    saved_model = results.rs$invariance_models$model.intercepts,
     data = DF,
-              meanstructure = TRUE,
+    model = model.rs,
+    group = "sample",
+    # be sure to do only up to the step you are interested in
+    group.equal = c("loadings", "intercepts"),
+    partial_step = "intercepts")
+
+partial.rs$fit_table %>% 
+  dplyr::select(free.parameter, cfi)
+```
+
+The output indicates that RS6 and RS7 are potential items that could be relaxed to improve model fit and create a partial scalar invariant model (i.e., by picking the largest CFI values).
+The code below show to check the addition of these items, which are added one at a time.
+You use the `group.partial` open to "relax" or freely estimate that parameter for each group separately.
+
+```{r partial-RS7, echo = T, include = T, size = "small"}
+# run the partially invariant model with group.partial
+partial.rs.1 <- mgcfa(model = model.rs, 
+                  data = DF, 
                   group = "sample", 
                   group.equal = c("loadings", "intercepts"),
-              group.partial = partial_syntax[i])
-
-  CFI_list[i] <- fitmeasures(temp, "cfi")
-}
-# look at the new CFIs
-CFI_list
-```
-
-The output indicates that RS6 and RS7 are potential items that could be relaxed to improve model fit and create a partial scalar invariant model.
-The code below show to check the addition of these items, which are added one at a time.
-You use the `group.partial` open to "relax" or freely estimate that parameter for each group separately.
-Once that model is saved, you can use the `tidy` function from *broom* to arrange the estimates from the model, which is used in our plotting function.
-The `glance` function will create a tidy dataframe of the fit indices for easy review.
-
-```{r echo = T, include = T, size = "small"}
-# run the partially invariant model with group.partial
-partial.rs <- cfa(model = model.rs, 
-                  data = DF, 
-                  meanstructure = TRUE,
-                  group = "sample", 
-                  meanstructure = T, 
-                  group.equal = c("loadings", "intercepts"),
-                  group.partial = c("RS7~1"))
+                  group.partial = c("RS7~1"),
+                  meanstructure = TRUE)
 
 # examine the loadings 
-tidy(partial.rs) %>% 
+partial.rs.1$model_coef %>% 
   filter(term == "RS7 ~1 ") %>% 
-  select(term, group, estimate, std.error)
+  filter(model == "intercepts") %>% 
+  dplyr::select(term, group, estimate, std.error)
+
 # examine the fit indices 
-glance(partial.rs) %>% 
-  select(AIC, BIC, cfi, tli, rmsea, srmr)
+partial.rs.1$model_fit %>% 
+  filter(model == "intercepts") %>% 
+  dplyr::select(AIC, BIC, cfi, tli, rmsea, srmr)
 
 # effect size model 
-lavaan_dmacs(partial.rs, "Clinical")$DMACS[7]
+lavaan_dmacs(partial.rs.1$invariance_models$model.intercepts, "Clinical")$DMACS[7]
 ```
@@
 Item seven covers perseverance after hardship, and all items can be found in the user manual for the scale at www.resiliencecenter.com.
-The effect size from $d_{DMACS}$ suggests a small to medium effect, `r apa_num(lavaan_dmacs(partial.rs, "Clinical")$DMACS[7])`.
-In this next code section, we repeat this process for the RS6, as the CFI for our model with only RS7 does not achieve the levels of partial invariance for our $\Delta$CFI criterion (i.e., \<= .01 downward change in fit: metric CFI = `r apa_p(results.rs$model_fit$cfi[5])`, partial scalar CFI = `r apa_p(glance(partial.rs)$cfi)`).
-
-```{r echo = T, include = T, size = "small"}
+The effect size from $d_{MACS}$ suggests a small to medium effect, `r apa_num(lavaan_dmacs(partial.rs.1$invariance_models$model.intercepts, "Clinical")$DMACS[7])`.
+In this next code section, we repeat this process for the RS6, as the CFI for our model with only RS7 does not achieve the levels of partial invariance for our $\Delta$CFI criterion (i.e., \<= .01 downward change in fit: metric CFI = `r apa_p(results.rs$model_fit$cfi[5])`, partial scalar CFI = `r apa_p(partial.rs.1$model_fit$cfi[6])`).
+See Figure \@ref(fig:rs7-img) for the difference between item intercepts and latent means.
+
+```{r partial-RS6, echo = T, include = T, size = "small"}
 # add the second intercept
-partial.rs.2 <- cfa(model = model.rs, 
+partial.rs.2 <- mgcfa(model = model.rs, 
                   data = DF, 
-                  meanstructure = TRUE,
                   group = "sample", 
-                  meanstructure = T, 
                   group.equal = c("loadings", "intercepts"),
-                  group.partial = c("RS7~1", "RS6~1"))
+                  group.partial = c("RS7~1", "RS6~1"),
+                  meanstructure = TRUE)
 
 # examine the loadings 
-tidy(partial.rs.2) %>% 
+partial.rs.2$model_coef %>% 
   filter(term == "RS6 ~1 ") %>% 
-  select(term, group, estimate, std.error)
+  filter(model == "intercepts") %>% 
+  dplyr::select(term, group, estimate, std.error)
 # examine the fit indices 
-glance(partial.rs.2) %>% 
-  select(AIC, BIC, cfi, tli, rmsea, srmr)
-# the effect size is 
-lavaan_dmacs(partial.rs.2, "Clinical")$DMACS[6]
+partial.rs.2$model_fit %>% 
+  filter(model == "intercepts") %>% 
+  dplyr::select(AIC, BIC, cfi, tli, rmsea, srmr)
+
+# effect size model 
+lavaan_dmacs(partial.rs.2$invariance_models$model.intercepts, "Clinical")$DMACS[6]
 ```
@@
 Again, we see about a half-point difference between our clinical and student samples for item 6, which is about drive to achieve.
-The CFI for this model does meet the requirements for partial invariance, `r apa_p(glance(partial.rs.2)$cfi)`.
-The effect size is approximately the same at `r apa_num(lavaan_dmacs(partial.rs.2, "Clinical")$DMACS[6])`.
-Last, we can create our images to view the item non-invariance and the latent means in Figures \@ref(fig:rs6-img) and \@ref(fig:rs7-img).
-
-```{r echo = T, include = T, size = "small"}
-# rebuild the model by constraining item 1 intercept
-# allow the latent variable to be estimated
-model.rs.picture <- "RS =~ RS1+RS2+RS3+RS4+RS5+RS6+RS7+RS8+RS9+RS10+RS11+RS12+RS13+RS14
-RS~1
-RS1~0*1"
-
-# rerun the partial invariance model 
-partial.rs.2.picture <- cfa(model = model.rs, 
-                  data = DF, 
-                  meanstructure = TRUE,
-                  group = "sample", 
-                  meanstructure = T, 
-                  group.equal = c("loadings", "intercepts"),
-                  group.partial = c("RS7~1", "RS6~1"))
-
-# save the coefficients to use in our picture function 
-partial.coef <- tidy(partial.rs.2.picture) %>% 
-  mutate(model = "Scalar")
-```
-
-```{r include = T, echo = T, results = "small", eval = F}
-# plot the image for RS6
-plot_mgcfa(
-  data_coef = partial.coef,
-  model_step = "Scalar", 
-  item_name = "RS6",
-  x_limits = c(-2,2),
+The CFI for this model does meet the requirements for partial invariance, `r apa_p(partial.rs.2$model_fit$cfi[6])`.
+The effect size is approximately the same at $d_{MACS}$ = `r apa_num(lavaan_dmacs(partial.rs.2$invariance_models$model.intercepts, "Clinical")$DMACS[6])`.
+See Figure \@ref(fig:rs6-img) shows the difference between item intercepts and latent means.
+
+```{r plot-RS7, include = T, echo = T, results = "small", eval = F}
+# plot the image for RS7
+plot_mi(
+  data_coef = partial.rs.2$model_coef, 
+  model_step = "intercepts", 
+  item_name = "RS7", 
+  x_limits = c(-1,1),
   y_limits = c(min(DF$RS7), max(DF$RS7)),
-  model_results = partial.rs.2.picture, 
-  ci_level = .95,
+  conf.level = .95, 
+  model_results = partial.rs.2$invariance_models$model.intercepts,
+  # which latent variable do you want 
   lv_name = "RS" 
-)
-```
-
-```{r rs6-img, echo = F, include = T, size = "small", fig.cap="RS6 Item Invariance Visualization"}
-# plot the image for RS6
-plot_mgcfa(
-  data_coef = partial.coef,
-  model_step = "Scalar", 
-  item_name = "RS6",
-  x_limits = c(-2,2),
-  y_limits = c(min(DF$RS7), max(DF$RS7)),
-  model_results = partial.rs.2.picture, 
-  ci_level = .95,
-  lv_name = "RS"
-)
-```
-
-```{r include = T, echo = T, results = "small", eval = F}
-# plot the image for RS7
-plot_mgcfa(
-  data_coef = partial.coef,
-  model_step = "Scalar", 
-  item_name = "RS7",
-  x_limits = c(-2,2),
-  y_limits = c(min(DF$RS7), max(DF$RS7)),
-  model_results = partial.rs.2.picture, 
-  ci_level = .95,
-  lv_name = "RS"
-)
+)$complete
 ```
@@
 # plot the image for RS7
-plot_mgcfa(
-  data_coef = partial.coef,
-  model_step = "Scalar", 
+plot_mi(
+  data_coef = partial.rs.2$model_coef, 
+  model_step = "intercepts", 
   item_name = "RS7", 
-  x_limits = c(-2,2),
+  x_limits = c(-1,1),
   y_limits = c(min(DF$RS7), max(DF$RS7)),
-  model_results = partial.rs.2.picture, 
-  ci_level = .95,
+  conf.level = .95, 
+  model_results = partial.rs.2$invariance_models$model.intercepts,
+  # which latent variable do you want 
   lv_name = "RS" 
-)
-```
-
-The latent mean is calculated "separately" for each group, insomuch as the first group is considered the comparison group, while the second is the difference between groups, like how dummy coded variables in regression are examined.
-Here we see a difference of `r apa_num(partial.coef %>% filter(term == "RS ~1 ") %>% slice_tail() %>% pull(estimate))`, and students show a higher resiliency score.
-However, when all other things are held equivalent, the intercepts on items 6 and 7 show higher scores for clinical populations.
-Additionally, we may see an indication in our student population of a bimodal distribution that may be related to this effect.
+)$complete
+```
+
+```{r plot-RS6, include = T, echo = T, results = "small", eval = F}
+# plot the image for RS6
+plot_mi(
+  data_coef = partial.rs.2$model_coef, 
+  model_step = "intercepts", 
+  item_name = "RS6", 
+  x_limits = c(-1,1),
+  y_limits = c(min(DF$RS6), max(DF$RS6)),
+  conf.level = .95, 
+  model_results = partial.rs.2$invariance_models$model.intercepts,
+  # which latent variable do you want 
+  lv_name = "RS" 
+)$complete
+```
+
+```{r rs6-img, echo = F, include = T, size = "small", fig.cap="RS6 Item Invariance Visualization"}
+plot_mi(
+  data_coef = partial.rs.2$model_coef, 
+  model_step = "intercepts", 
+  item_name = "RS6", 
+  x_limits = c(-1,1),
+  y_limits = c(min(DF$RS6), max(DF$RS6)),
+  conf.level = .95, 
+  model_results = partial.rs.2$invariance_models$model.intercepts,
+  # which latent variable do you want 
+  lv_name = "RS" 
+)$complete
+```
+
+Next, we would examine our replication potential for this model.
+Given our current results, we may not expect our intercepts to replicate.
+Given the order of `group.equal`, the boot function will select the first non-invariant step in the calculation of the effect size for potential replication.
+In our output, we do not see a loadings effect size, and this result occurs when *none* of the bootstrapped or random results are non-invariant.
+Therefore, we would expect the loadings to replicate (and the effect size would be 0 difference between bootstrapped and random, both showing invariance).
+The intercepts show a large (i.e., close to the max possible value) non-invariant effect, and therefore, we should not expect this model to show invariance in a replication.
+
+```{r model-boot-RS, include = T, echo = T, results = "small", eval = F}
+boot.model.rs <- 
+  bootstrap_rr(
+    saved_configural = results.rs$model_configural,
+    data = DF,
+    model = model.rs, 
+    group = "sample", 
+    nboot = 1000, 
+    invariance_index = "cfi",
+    invariance_rule = .01, 
+    group.equal = c("loadings", "intercepts", "residuals")
+)
+```
+
+```{r model-boot-RS-out, include = T, echo = T, results = "small"}
+boot.model.rs
+```
+
+Next, we would examine the strength of the effects of replication on each parameter at the intercept level.
+By examining Table  \@ref(tab:table-boot-effects), it is clear that most of the item means are unlikely to replicate, even though two particular items can be used to create partial invariance.
+Figures \@ref(fig:rs-partial-pic) and \@ref(fig:rs-partial-pic2) display the three plots provided in the `bootstrap_partial()` function.
+In general, we should expect $M_{D}$ = `r apa_num(boot.partial.rs$boot_summary %>% filter(invariant) %>% pull(mean_boot_difference) %>% mean())` when items are invariant and $M_{D}$ = `r apa_num(boot.partial.rs$boot_summary %>% filter(!invariant) %>% pull(mean_boot_difference) %>% mean())` when items are not invariant.
+The effect size of non-invariant items ranges from `r apa_num(boot.partial.rs$boot_summary %>% filter(!invariant) %>% pull(d_boot) %>% min(., na.rm = T))` to `r apa_num(boot.partial.rs$boot_summary %>% filter(!invariant) %>% pull(d_boot) %>% max(., na.rm = T))`.
+
+The density plot shown at the bottom of Figure \@ref(fig:rs-partial-pic) illustrates the likely reasons for the differences found in the top plots.
+It appears that many items show a bimodal distribution within group 1 (Clinical Sample) and when items are invariant, the intercept averages to the same intercept as group 2 (Student Sample).
+In non-invariant estimates, the same bimodal distributions are found, but they are more extreme than the student samples, and therefore, item show different averages due to the presence of two separate means of data.
+Further, some items also appear to show two separate student item averages within the data.
+This result suggests that it would be fruitful to understand a potential predictor of these differences or other confounding variable that separates these samples, creating differences in item averages.
+
+In summary, if one were planning a replication, the prediction would be that item intercepts would likely not replicate, with a large effect size (i.e., it is easy to judge $h_{nmi_p}$ close to the max of one as large).
+While this study found partial invariance by relaxing constraints on two individual items, bootstrapped partial invariance indicates that any item could potentially be problematic with an effect size averaging $d$ ~ 0.50 difference in means.
+While $d_{MACS}$ values represented a "small" effect based on previous publications, this effect may be muted by examining both loadings and intercepts.
+The results here suggest that the effect is driven by intercepts.
+The overall average score on items is high: $M_M$ = `r apa_num(mean(apply(DF[ , -ncol(DF)], 2, mean)))` ($M_{SD}$ = `r apa_num(mean(apply(DF[ , -ncol(DF)], 2, sd)))`).
+Given the mean standard deviation, a $d$ ~ 0.50 represents `r apa_num(mean(apply(DF[ , -ncol(DF)], 2, sd))/2)` or nearly one whole point on the scale.
+A researcher could decide that at least $d$ = 0.33 or at least a third of a standard deviation would be an important change and set that as their smallest effect size of interest for invariance.
+Further, a newly planned study should investigate what variables may predict when and why samples separate into bimodal representations for item means.
+
+```{r partial-boot-RS, include = T, echo = T, results = "small", eval = F}
+boot.partial.rs <- 
+  bootstrap_partial(
+    saved_model = results.rs$invariance_models$model.intercepts,
+    data = DF,
+    model = model.rs, 
+    group = "sample", 
+    nboot = 1000, 
+    invariance_index = "cfi",
+    invariance_rule = .01, 
+    invariance_compare = fitmeasures(results.rs$invariance_models$model.loadings, "cfi"), 
+    partial_step = "intercepts",
+    group.equal = c("loadings", "intercepts")
+)
+```
+
+```{r table-boot-effects, results='asis'}
+apa_table(boot.partial.rs$boot_effects,
+          digits = 3, 
+          caption = "Boot Partial Effects Results for RS-14 Intercepts")
+```
+
+```{r rs-partial-pic, include = T, fig.cap="RS14 scale invariance for item intercepts.
+The left panel indicates the raw score difference between groups and items, while the right panel indicates the effect size for group differences based on invariance."}
+
+plot_grid(
+  boot.partial.rs$invariance_plot,
+  boot.partial.rs$effect_invariance_plot)
+```
+
+```{r rs-partial-pic2, include = T, fig.cap = "RS14 scale invariance density plots, illustrating invariant versus non-invariant bootstrapped and random runs for each parameter."}
+suppressMessages((boot.partial.rs$density_plot))
+```
 
@@
 
-In this tutorial, we examined how to use multiple tools to examine measurement invariance.
-Model fit comparisons and statistics can be paired with newly developed effect size measures, and finally a visualization to examine individual items and the overall latent mean scores.
-This visualization was designed with common graphing elements that researchers often use to display those statistics - intercepts were graphed on the intercept line, slopes were represented as lines of fit, and error terms were represented as distributions.
-Each component can impact the overall model and the eventual latent mean scores, as shown in the simulations holding all other things equal.
+In this tutorial, we examined how to use multiple tools to examine measurement invariance and its potential replication.
+Model fit comparisons and statistics can be paired with the proposed effect size measures, and a visualization to examine individual items and the overall latent mean scores.
+The impact of potential replication was estimated on the overall model and the individual parameters.
 Using real data, the effect of two non-invariant item intercepts was examined and visualized.
-How should one interpret the "discrepancy" between the results (these effect visually appear large) from effect sizes (.30 was proposed as small to medium in @nye2019)?
-
-Effect sizes are notoriously difficult to interpret, which is why we love guidelines, even if @cohen1990 declared we probably shouldn't use his suggestions.
+This tutorial manuscript has provided a concrete way to plan for pre-registration and/or registered reports.
+Researchers could simulate results based on published or previously collected data to determine the likelihood and size of potential replication.
+They could plan and pre-register a smallest effect of interest.
+For example, we may determine that an $h_{nmi_p}$ value above .20 represents an important level of non-invariance for our model overall, while $h_{nmi_p}$ > .30 for any individual parameter warrant caution against invariance for groups.
 Others have begun to discuss the importance of focusing on effects in the scale of the data and their practical importance [@cumming2012; @anvari2021].
-Our interpretation may be that the difference between groups is large, as a `r apa_num(partial.coef %>% filter(term == "RS ~1 ") %>% slice_tail() %>% pull(estimate))` change on a 7 point scale is approximately 10% more resiliency for students when compared to the clinical sample.
+
+From the example, our interpretation may be that the difference between group's latent means is large, as a `r apa_num(partial.rs.2$model_coef %>% filter(term == "RS ~1 ") %>% slice_tail() %>% pull(estimate))` change on a 7 point scale is approximately 10% more resiliency for students when compared to the clinical sample.
 Practically, 10% in resiliency for an area of the United States (Mississippi) often hit with natural disasters (hurricanes, tornadoes, floods) and high levels of poverty would be very important.
@@
 
-What do the results of a study on measurement invariance with these results tell us about replication, generalizability, and validity?
+What do the results of a study on measurement invariance with these results tell us about replication, generalizability, and validity overall?
 If a researcher decides their effects are large, they should likely caution against suggesting that these scores are directly comparable without weighting or other adjustment.
@@
 
-# Appendix
-
-## MGCFA Convenience Function
-
-Please note that any partial invariance is not automatically included in this function.
-This function returns a list with all model summaries, the model coefficients in a tidy dataframe, and the model fit statistics in a tidy dataframe.
-You will need the libraries listed below for this function to work properly.
-
-```{r cfa-append, include = T, echo = T, size = "small"}
-library(lavaan)
-library(dplyr)
-library(broom)
-# CFA function
-mgcfa <- function(data, group, model){
-
-  group_names <- unique(data[ , group])
-  data$group <- data[ , group]
-
-  model.overall <- cfa(model = model, data = data, 
-                       meanstructure = T)
-  model.group1 <- cfa(model = model, 
-                      data = subset(data, group == group_names[1]),
-                      meanstructure = T)
-  model.group2 <- cfa(model = model, 
-                      data = subset(data, group == group_names[2]),
-                      meanstructure = T)
-  model.configural <- cfa(model = model, data = data, 
-                          group = group, meanstructure = T)
-  model.metric <- cfa(model = model, data = data, 
-                      group = group, meanstructure = T,
-                      group.equal = "loadings")
-  model.scalar <- cfa(model = model, data = data, 
-                      group = group, meanstructure = T, 
-                      group.equal = c("loadings", "intercepts"))
-  model.strict <- cfa(model = model, data = data, 
-                      group = group, meanstructure = T, 
-                      group.equal =  c("loadings", "intercepts", "residuals"))
-
-  model_coef <- bind_rows(
-    tidy(model.overall, conf.level = .95) %>% 
-      mutate(model = "Overall"), 
-    tidy(model.group1, conf.level = .95) %>% 
-      mutate(model = "Group 1"), 
-    tidy(model.group2, conf.level = .95) %>% 
-      mutate(model = "Group 2"), 
-    tidy(model.configural, conf.level = .95) %>% 
-      mutate(model = "Configural"), 
-    tidy(model.metric, conf.level = .95) %>% 
-      mutate(model = "Metric"), 
-    tidy(model.scalar, conf.level = .95) %>% 
-      mutate(model = "Scalar"), 
-    tidy(model.strict, conf.level = .95) %>% 
-      mutate(model = "Strict")
-  )
-
-  model_fit <- bind_rows(
-    glance(model.overall) %>% mutate(model = "Overall"), 
-    glance(model.group1) %>% mutate(model = "Group 1"), 
-    glance(model.group2) %>% mutate(model = "Group 2"), 
-    glance(model.configural) %>% mutate(model = "Configural"), 
-    glance(model.metric) %>% mutate(model = "Metric"), 
-    glance(model.scalar) %>% mutate(model = "Scalar"), 
-    glance(model.strict) %>% mutate(model = "Strict")
-    )
-
-  return(list(
-    "model_coef" = model_coef,
-    "model_fit" = model_fit,
-    "model.overall" = model.overall,
-    "model.group1" = model.group1,
-    "model.group2" = model.group2,
-    "model.configural" = model.configural,
-    "model.metric" = model.metric,
-    "model.scalar" = model.scalar,
-    "model.strict" = model.strict
-  ))
-
-}
-```
-
-## Measurement Invariance Plot Function
-
-This function creates the plots shown in the manuscript.
-You will need the libraries listed for this function to work.
-Plots may be modified to rearrange for those who are familiar with `ggplot2`.
-Please note that the function assumes you will use the outputs from the previous `mgcfa` function or a tidy dataframe that includes the coefficients from the model with a column `model` that indicates which step of the MGCFA you are wanting to plot.
-If you have more than two groups, you should first filter the dataframe model coefficient outputs to only include to the two groups you want to compare.
-This code does not plot more than two groups (although, it could be modified for this, but the assumption here is that you only have two, as this is how you would normally proceed in a MGCFA using pairwise comparisons to find where the invariance occurs).
-
-```{r plot-append, include = T, echo = T, size = "small"}
-library(dplyr)
-library(ggplot2)
-library(cowplot)
-library(lavaan)
-# devtools::install_github("psyteachr/introdataviz")
-library(introdataviz)
-# Plot MI MGCFA
-plot_mgcfa <- function(data_coef, # output from model_coef
-                       model_step, # which model
-                       item_name, # name of observed item
-                       x_limits = c(-1,1), # LV limits to graph
-                       y_limits, # Y min and max in data 
-                       ci_level, # what ci do you want
-                       model_results, # what model results do you want 
-                       lv_name # which latent is the observed variable on
-                       ){
-
-  # calculate cutoff
-  cutoff <- qt(p = (1-ci_level)/2, 
-               df = sum(unlist(model_results@Data@nobs)), 
-               lower.tail = F)
-
-  # get group variable
-  group_var <- model_results@Data@group
-  group_labels <- model_results@Data@group.label
-
-  # first get the data
-  graph.data <- data_coef %>% # put in tidy coefficients
-  filter(model == model_step) %>% # pick a model
-  filter(grepl(item_name, term)) %>%  # pick a question
-  mutate(group = factor(group, levels = names(table(data_coef$group)), 
-                        labels = group_labels))
-
-  # make ribbon data y = slope*x + intercept for ci for slopes 
-  ribbondata <- bind_rows(
-    data.frame(
-    x = seq(from = x_limits[1] - 1,  
-            to = x_limits[2] + 1, 
-            by = .05), 
-    group = unique(graph.data$group)[1]
-  ) %>% 
-    mutate(ymin = (graph.data %>% filter(op == "=~") %>% 
-                 slice_head() %>% pull(estimate) * x) - 
-             (cutoff*graph.data %>% filter(op == "=~") %>% 
-                    slice_head() %>% pull(std.error)) +
-             graph.data %>% filter(op == "~1") %>% 
-                 slice_head() %>% pull(estimate), 
-           ymax = (graph.data %>% filter(op == "=~") %>% 
-                 slice_head() %>% pull(estimate) * x) + 
-             (cutoff*graph.data %>% filter(op == "=~") %>% 
-                    slice_head() %>% pull(std.error)) +
-             graph.data %>% filter(op == "~1") %>% 
-                 slice_head() %>% pull(estimate)), 
-    data.frame(
-      x = seq(from = x_limits[1] - 1,  
-              to = x_limits[2] + 1, 
-              by = .05), 
-      group = unique(graph.data$group)[2]
-    ) %>% 
-      mutate(ymin = (graph.data %>% filter(op == "=~") %>% 
-                   slice_tail() %>% pull(estimate) * x) - 
-               (cutoff*graph.data %>% filter(op == "=~") %>% 
-                      slice_tail() %>% pull(std.error)) +
-               graph.data %>% filter(op == "~1") %>% 
-                   slice_tail() %>% pull(estimate), 
-             ymax = (graph.data %>% filter(op == "=~") %>% 
-                   slice_tail() %>% pull(estimate) * x) + 
-               (cutoff*graph.data %>% filter(op == "=~") %>% 
-                      slice_tail() %>% pull(std.error)) +
-               graph.data %>% filter(op == "~1") %>% 
-                   slice_tail() %>% pull(estimate))
-  )
-
-  # make point data to draw on the intercepts 
-  pointdata <- data.frame(
-  x = c(0,0),
-  y = graph.data %>% filter(op == "~1") %>% pull(estimate), 
-  group = graph.data %>% filter(op == "~1") %>% pull(group),
-  ymin = graph.data %>% filter(op == "~1") %>% pull(estimate) - 
-    cutoff * graph.data %>% filter(op == "~1") %>% pull(std.error), 
-  ymax = graph.data %>% filter(op == "~1") %>% pull(estimate) + 
-    cutoff * graph.data %>% filter(op == "~1") %>% pull(std.error)
-  )
-
-  # make the line data to draw on the slopes
-  linedata <- data.frame(
-  slope = graph.data %>% filter(op == "=~") %>% pull(estimate), 
-  intercept = graph.data %>% filter(op == "~1") %>% pull(estimate), 
-  group = graph.data %>% filter(op == "~1") %>% pull(group)
-  )
-
-  # make the distributions for the residuals 
-  violindata <- data.frame(
-  y = c(rnorm(n = 1000, 
-            mean = graph.data %>% filter(op == "~~") %>% 
-              slice_head() %>% pull(estimate), 
-            sd = graph.data %>% filter(op == "~~") %>% 
-              slice_head() %>% pull(std.error)), 
-        rnorm(n = 1000, 
-            mean = graph.data %>% filter(op == "~~") %>% 
-              slice_tail() %>% pull(estimate), 
-            sd = graph.data %>% filter(op == "~~") %>% 
-              slice_tail() %>% pull(std.error))),
-  group = c(rep(graph.data %>% filter(op == "~~") %>% 
-              slice_head() %>% pull(group), 1000),
-            rep(graph.data %>% filter(op == "~~") %>% 
-              slice_tail() %>% pull(group), 1000)), 
-  x = 1
-  )
-
-  # make the latent mean data for right panel
-  latent_means <- lavPredict(model_results, 
-                               type = "lv", 
-                               label = TRUE,
-                               assemble = TRUE, 
-                               append.data = TRUE)
-
-  latent_means$lv <- latent_means[ , lv_name]
-  latent_means$group <- latent_means[ , group_var]
-
-  # make a plot of the variance
-  variance_plot <- 
-  ggplot(violindata, aes(x = 1, y = y, color = group, fill = group)) + 
-  geom_split_violin() + 
-  theme_void() + 
-  theme(legend.position = "none") + 
-  stat_summary(fun = "mean",
-               geom = "crossbar", 
-               width = 0.5,
-               colour = "black")
-
-  # make the plot with intercepts and slopes
-  intercept_plot <- 
-  ggplot() + 
-  # basic set up
-  theme_classic() + 
-  xlab("Latent Variable") + 
-  ylab("Observed Variable") + 
-  coord_cartesian(xlim = x_limits, ylim = y_limits) + 
-  # plot the intercepts 
-  geom_point(data = pointdata, 
-             aes(x = x, y = y, color = group), 
-             inherit.aes = FALSE) + 
-  geom_errorbar(data = pointdata,
-                aes(x = x, ymin = ymin, ymax = ymax, color = group), 
-                inherit.aes = FALSE, width = .10) + 
-  # plot the slopes
-  geom_abline(data = linedata,
-              aes(slope = slope, intercept = intercept, color = group)) + 
-  geom_ribbon(data = ribbondata, 
-              aes(x = x, ymin = ymin, ymax = ymax, fill = group), 
-              inherit.aes = FALSE, alpha = .2) + 
-  scale_color_discrete(name = "Group") + 
-  scale_fill_discrete(name = "Group") + 
-  geom_vline(xintercept = 0) + 
-  theme(axis.line.y = element_blank())
-
-  # make the latent means plot
-  mean_plot <- ggplot(latent_means, aes(x = lv, fill = group)) + 
-    geom_density(alpha = .2) + 
-    theme_classic() + 
-    xlab("Latent Variable") + 
-    ylab("Density") + 
-    geom_vline(data = latent_means %>% group_by(group) %>% summarize(mean = mean(lv)), 
-               aes(xintercept = mean, color = group)) + 
-    theme(legend.position = "none") + 
-    coord_cartesian(xlim = x_limits)
-
-  y_range = abs(y_limits[2] - y_limits[1])
-
-  # line up the two plots 
-  prow <- plot_grid(
-    intercept_plot + 
-      ggtitle("Item Invariance") + 
-      theme(legend.position = "none") + 
-      annotation_custom(ggplotGrob(variance_plot), 
-                        xmin = .25, xmax = 1, 
-                        ymin = y_limits[1], ymax = y_limits[2]-y_range/1.8),
-    mean_plot + 
-      ggtitle("Latent Mean Distribution") + 
-      theme(legend.position = "none"),
-    align = 'vh',
-    hjust = -1,
-    nrow = 1
-  )
-
-  # get the legend
-  legend_b <- get_legend(
-    intercept_plot + 
-      guides(color = guide_legend(nrow = 1)) +
-      theme(legend.position = "bottom")
-  )
-
-  # send out the plot 
-  plot_grid(prow, legend_b, ncol = 1, rel_heights = c(1, .1))
-
-}
-```
-
-## Model Fit Statistics
-
-Model fit statistics are provided for each of the ten model combinations (invariant, three sizes for each ladings, intercepts, and residuals).
-These tables could be used to examine the traditional change in fit statistics cutoff rules of thumb [@cheung2002], such as $\Delta$ CFI or $\Delta$ RMSEA, to the visualizations presented in the manuscript.
-
-```{r tab1, results='asis'}
-apa_table(results.invariant$model_fit %>% 
-            select(model, AIC, BIC, cfi, tli, rmsea, srmr),
-          digits = 3, 
-          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
-          caption = "Model Fit for Invariant Model")
-```
-
-```{r tab2, results='asis'}
-apa_table(results.small.load$model_fit %>% 
-            select(model, AIC, BIC, cfi, tli, rmsea, srmr), 
-          digits = 3, 
-          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
-          caption = "Model Fit for Small Differences in Loadings")
-```
-
-```{r tab3, results='asis'}
-apa_table(results.med.load$model_fit %>% 
-            select(model, AIC, BIC, cfi, tli, rmsea, srmr), 
-          digits = 3, 
-          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
-          caption = "Model Fit for Medium Differences in Loadings")
-```
-
-```{r tab4, results='asis'}
-apa_table(results.large.load$model_fit %>% 
-            select(model, AIC, BIC, cfi, tli, rmsea, srmr),
-          digits = 3, 
-          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
-          caption = "Model Fit for Large Differences in Loadings")
-```
-
-```{r tab5, results='asis'}
-apa_table(results.small.int$model_fit %>% 
-            select(model, AIC, BIC, cfi, tli, rmsea, srmr), 
-          digits = 3, 
-          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
-          caption = "Model Fit for Small Differences in Intercepts")
-```
-
-```{r tab6, results='asis'}
-apa_table(results.med.int$model_fit %>% 
-            select(model, AIC, BIC, cfi, tli, rmsea, srmr),
-          digits = 3, 
-          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
-          caption = "Model Fit for Medium Differences in Intercepts")
-```
-
-```{r tab7, results='asis'}
-apa_table(results.large.int$model_fit %>% 
-            select(model, AIC, BIC, cfi, tli, rmsea, srmr),
-          digits = 3, 
-          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
-          caption = "Model Fit for Large Differences in Intercepts")
-```
-
-```{r tab8, results='asis'}
-apa_table(results.small.res$model_fit %>% 
-            select(model, AIC, BIC, cfi, tli, rmsea, srmr), 
-          digits = 3, 
-          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
-          caption = "Model Fit for Small Differences in Residuals")
-```
-
-```{r tab9, results='asis'}
-apa_table(results.med.res$model_fit %>% 
-            select(model, AIC, BIC, cfi, tli, rmsea, srmr), 
-          digits = 3, 
-          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
-          caption = "Model Fit for Medium Differences in Residuals")
-```
-
-```{r tab10, results='asis'}
-apa_table(results.large.res$model_fit %>% 
-            select(model, AIC, BIC, cfi, tli, rmsea, srmr), 
-          digits = 3, 
-          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
-          caption = "Model Fit for Large Differences in Residuals")
-```
+# (APPENDIX) Appendix {-}
+
+```{r child = "appendix_1.Rmd"}
+```
+
+```{r child = "appendix_2.Rmd"}
+```
+
+```{r child = "appendix_3.Rmd"}
+```
+
+```{r child = "appendix_4.Rmd"}
+```
+
+```{r child = "appendix_5.Rmd"}
+```
+
+```{r child = "appendix_6.Rmd"}
+```

### 2023-10-16 manuscript.tex
all the updates

@@
 \usepackage{amsmath,amssymb}
-\usepackage{lmodern}
 \usepackage{iftex}
@@
 \else % if luatex or xetex
-  \usepackage{unicode-math}
+  \usepackage{unicode-math} % this also loads fontspec
   \defaultfontfeatures{Scale=MatchLowercase}
   \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+\fi
+\usepackage{lmodern}
+\ifPDFTeX\else
+  % xetex/luatex font selection
 \fi
@@
 \newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
+\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
 \newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
@@
 \newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
 \newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
@@
 \newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
-\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
 \newcommand{\ImportTok}[1]{#1}
@@
 \newcommand{\RegionMarkerTok}[1]{#1}
-\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
 \newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
@@
 \IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same} % disable monospaced font for URLs
+\urlstyle{same}
 \hypersetup{
-  pdftitle={Visualizing and Interpreting Multi-Group Confirmatory Factor Analysis},
+  pdftitle={visualizemi: Visualization, Effect Size, and Replication of Measurement Invariance for Registered Reports},
   pdfauthor={Erin M. Buchanan1},
@@
 
-\title{Visualizing and Interpreting Multi-Group Confirmatory Factor Analysis}
+\title{visualizemi: Visualization, Effect Size, and Replication of Measurement Invariance for Registered Reports}
 \author{Erin M. Buchanan\textsuperscript{1}}
@@
 With the rise of the replication crisis and ``psychology's renaissance'' (Nelson et al., 2018), interest in divergence in measurement has increased, often focused on small parameter differences within the latent model.
-This manuscript outlines ways to visualize potential non-invariance, to supplement large numbers of tables that often overwhelm a reader within these published reports.
-Readers will learn how to interpret the impact and size of the proposed non-invariance in models.
-While it is tempting to suggest that problems with replication and generalizability are simply issues with measurement, it is crucial to remember that all models have variability and error, even those models estimating the differences between item functioning, such as multi-group confirmatory factor analysis.
+This manuscript presents \texttt{visualizemi}, an \emph{R} package that provides functionality to calculate multigroup models, partial invariance, visualizations for (non)-invariance, effect sizes for models and parameters, and potential replication rates compared to random models.
+Readers will learn how to interpret the impact and size of the proposed non-invariance in models with a focus on potential replication and how to plan for registered reports.
 }
@@
 
-Measurement invariance is typically analyzed using confirmatory factor analysis, specifically, multi-group confirmatory factor analysis (MGCFA) or less often, with item response theory (Stark et al., 2006; Tay et al., 2015).
-First, the model is examined with the factor structure proposed for the latent and observed variables, and then often these models are assessed for each group separately.
-The two models are then combined together into one nested CFA in order to determine configural invariance (Brown, 2015; Byrne, 2001; Kline, 2016).
-Configural invariance tests if the proposed factor structure is the same between groups.
-In this model, all other estimated parameters are allowed to vary between groups.
-The general approach is to use this model as a baseline for starting a sequential analysis of further restrictions between group parameters (i.e., more restrictive with each step).
-However, models without configural invariance can occur and often point to misspecification for the observed and latent variables within one group (i.e., cross loadings of items onto other latent variables or correlated error terms for one group only).
-
-Next, the estimated parameter between each observed variable and its latent variable are constrained to be equal between groups for metric invariance.
-For example, item 1's factor loading must be equal to item 1's factor loading for each group.
-This test examines if the items represent the same relationship to the latent variable, or if specific items have weaker or stronger relationships in specific groups.
-Finding non-invariance at this stage generally points to items that have different functioning or interpretation for one group.
-At the third model, the item intercepts (i.e., item averages) are restricted across groups for scalar invariance.
-Scalar non-invariance would indicate that items have the same strength of relationship with their latent variable, just one group has a higher overall average on that item.
-Last (although sometimes not used), we may consider constraining error variances for each observed variable to be equal across groups for strict invariance.
-Strict non-invariance can occur when one group has a higher range of values on the observed variable, thus showing a larger variance.
-For example, if using a Likert scale, one group may use the full 1 to 7 range (creating a flatter distribution and larger variance), while the other group shows a ceiling effect of only using 5 to 7.
-
-These concepts have been explored and implemented for the last fifty years (Jöreskog, 1971; Sörbom, 1978) and implemented in the most popular structural equation modeling programs (Boker et al., 2011; Jöreskog \& Sörbom, 2001; Rosseel, 2012).
+Measurement invariance has been explored and implemented for the last fifty years (Jöreskog, 1971; Sörbom, 1978) and implemented in the most popular structural equation modeling programs (Boker et al., 2011; Jöreskog \& Sörbom, 2001; Rosseel, 2012).
 Byrne et al.
@@
 This testing provided an advantage to understand where the potential non-invariance may occur for further study and interpretation guidelines.
-To determine when non-invariance and partial invariance occurred, each model is sequentially compared to the previous model using some form of a difference test.
-Traditionally, since models were nested, a chi-square difference test was used (Cheung \& Rensvold, 2002; Meade et al., 2008); however, given the known issues with chi-square (Thompson \& Daniel, 1996), people have favored empirical cutoffs for differences in fit indices.
 As the field pushes back against favoring cutoff criteria and rules of thumb (Marsh et al., 2004; Putnick \& Bornstein, 2016), an effect size measure for translating ``how much'' non-invariance was developed \(d_{MACS}\) (Nye \& Drasgow, 2011).
@@
 With \(d_{MACS}\) and measurement invariance testing, researchers can begin to quantify how and where their construct measurement may vary between groups.
-However, given the large number of studies that show non-invariance, it is clear that equivalence can be hard to meet.
+Yet, given the large number of studies that show non-invariance, it is clear that equivalence can be hard to meet.
 It is difficult to know if non-invariance occurs because of random sampling error, true population differences, or differences in replication and reproducibility of the construct in a new sample.
-Further, it is important to remember that the parameter estimates that we are testing are just that - estimates.
-All the parameter estimates have measures of standard error to indicate that they are more than likely variable with a new sample or population.
-Given that this information is generally ignored during the examination of measurement invariance, it may be that we are claiming that many scales are non-invariant, when in reality, the differences between loadings or item intercepts are small and unimportant.
-\(d_{MACS}\) provides the opportunity to begin to think about the smallest effect size of interest or the smallest meaningful effect size (Anvari \& Lakens, 2021; Lakens, 2017).
+The field of psychology is increasingly interested in pre-registration (i.e., registering plans for a study before data collection, Nosek et al., 2018) and the promotion of transparency in study design, implementation, and analysis (Mayo-Wilson et al., 2021), in addition to supporting replication studies (Zwaan et al., 2018).
+Registered (replication) reports provide an advantageous avenue for the pre-registration of measurement tests, as they allow a researcher the ability to have their study accepted in principle, regardless of the results of a test of construct validity, reliability, or measurement invariance (Hobson, 2019; Nosek \& Lakens, 2014).
+However, there are few tools that can provide effect size measures for models, individual parameters, or visualization for researchers to plan for future studies.
+\(d_{MACS}\) provides the opportunity to begin to think about the smallest effect size of interest or the smallest meaningful effect size for measurement invariance and replication (Anvari \& Lakens, 2021; i.e., two studies with overlapping confidence intervals ``replicate,'' even if the test of measurement invariance does not, Lakens, 2017).
 As mentioned, \(d_{MACS}\) has only really been explored for a combined intercept and loadings, and while useful, does not necessarily allow a researcher to pinpoint specific issues within an observed variable.
-The purpose of this manuscript is provide readers with a framework for visualization of differences in loadings, intercepts, and variances for each item, and the impact of those differences on the distribution of the latent mean.
+
+Therefore, purpose of this manuscript is describe an \emph{R} package, \texttt{visualizemi}, that provides functionality to calculate multi-group confirmatory factor analysis, partial invariance tests, visualizations of the size of non-invariance, and potential effect sizes for overall models and individual parameters.
 No known visualization techniques have been proposed for measurement invariance.
 By creating panel visualizations, we can supplement a researchers ability to judge the strength of the non-invariance differences and effect size for each item.
+The proposed effect sizes demonstrate the likelihood of replication with a similar sample as compared to a randomly assigned group model, thus, illustrating what type of measurement one might expect to find, and how different that is from random chance.
+Within this technique, the individual parameter effect sizes can calculated: both the group differences within a model as compared to random and the likelihood of a parameter replication compared to random groups.
 Coupled with other indicators (i.e., fit indices differences, \(d_{MACS}\)), we can move toward a better understanding of how much measurement non-invariance is meaningful.
+This tutorial and package will help researchers plan future studies and aid in the ability to estimate a smallest effect of interest for measurement invariance studies, rather than relying on fit indices and rules of thumb alone.
 
@@
 \item
-  Be able to create visualizations for common steps to multi-group confirmatory factor analysis.
-\item
-  Be able to interpret the impact and size of potential non-invariance on measurement.
+  Learn how to use \emph{visualizemi} to analyze multi-group confirmatory factor analysis, examine partial invariance, and create visualizations of parameters.
+\item
+  Learn how to estimate the potential replication of multi-group models and their parameters using bootstrapping compared to a random group model.
+\item
+  Be able to calculate and interpret effect sizes for model and parameter replication, as well as parameter group differences.
 \item
@@
 
+The tutorial will start with simulated data based on known effect sizes using \(d_{MACS}\) and demonstrating the package functions for 1) running the multigroup analysis, 2) running a partial invariance analysis, 3) plotting the partial invariance, 4) estimating replication and effect sizes at the model level, and 5) estimating replication and effect sizes at the parameter level.
+Last, data from Aiena et al.
+(2014) examining the measurement invariance of the RS-14 (Wagnild, 2009) will be used to demonstrate the application of the package on real data.
+The \emph{visualizemi} package vignette includes an additional tutorial walk through.
+
 \hypertarget{method}{%
@@
 Data was simulated using the \texttt{simulateData} function in the \emph{R} package \emph{lavaan} (Rosseel, 2012) assuming multivariate normality using a \(\mu\) of 0 and \(\sigma\) of 1 for the data.
-This function allows you to write \emph{lavaan} syntax for your model with estimated values to generate data for observed variables.
+This function allows you to write \emph{lavaan} syntax for your model with estimated values to generate data for observed variables (see supplemental for examples).
 The data included two groups of individuals (``Group 1'', ``Group 2'') for a multi-group confirmatory factor analysis (\(n_{group}\) = 250, \emph{N} = 500).
-The latent variables were assumed to be continuous normal.
+The latent variables were assumed to be continuous normal (the package functions do not require this assumption).
 The model consisted of five observed items predicted by one latent variable (\texttt{lv\ =\textasciitilde{}\ q1\ +\ q2\ +\ q3\ +\ q4\ +\ q5}); however, the demonstration in this manuscript extends to multiple latent variables and other combinations of observed variables.
-Each item was assumed to be related to the latent variable with loadings approximately equal to .40 to .80, except when cases of non-invariance on the loadings was assumed.
+Each item was assumed to be related to the latent variable with loadings approximately equal to .40 to .80, except when cases of non-invariance on the loadings was simulated.
 
@@
 (2006) suggestions, the visualizations show the impact of loadings and intercepts together.
-The configural model was analyzed nesting both groups into the same CFA model requiring that both groups show the same model structure, but all other parameters are free to vary between groups.
-The metric model constrained the factor loadings of each group to be equal within the model.
-The scalar model then constrained the item intercepts (i.e., item means) to be equal across groups.
-Finally, the strict model constrained the item variances (i.e., error variances) to be equal for each item across groups.
-These models are normally tested sequentially, and a convenience function \texttt{mgcfa} is provided in the supplemental documents for this manuscript.
+A convenience function \texttt{mgcfa} is used for these steps or other measurement invariance test orders and combinations.
 Fit indices for the steps for multi-group models are presented in the appendix for comparison of cutoff rules of thumb (Cheung \& Rensvold, 2002) to effect sizes and visualizations presented in this manuscript.
@@
 Only one item in each model was manipulated from the invariant model to create the non-invariant models.
-
-\hypertarget{results}{%
-\section{Results}\label{results}}
-
-\hypertarget{code-examples}{%
-\subsection{Code Examples}\label{code-examples}}
-
-The complete code for this manuscript can be found at \url{https://osf.io/wev5f/}, and the function code for the convenience function for multi-group models and plots is found in the appendix.
+Given the data was simulated with a \emph{z}-score scaling, the loading values were simulated at .30 points apart (given \(d_{MACS}\) suggestions of .2, .4, .7), the intercepts at .25 points apart, and the residuals at .25 points apart.
+To plan a simulation for your own study, these values can be used to simulate small, medium, and large non-invariance effects by first converting data into \emph{z}-score.
+
+\hypertarget{package-code-examples}{%
+\section{Package Code Examples}\label{package-code-examples}}
+
+The complete code for this manuscript can be found at \url{https://osf.io/wev5f/}.
 This tutorial was registered at \url{https://osf.io/vwf4d}, and the example provided at the end of the manuscript was added after that registration.
+The \emph{R} package and replication/effect sizes was added after the original manuscript submission.
+
+\hypertarget{multi-group-cfa-caculation}{%
+\subsection{Multi-group CFA Caculation}\label{multi-group-cfa-caculation}}
+
 First, we would create our model code in \emph{lavaan} syntax (Rosseel, 2012).
 The \texttt{lv} latent variable predicts the five measured variables, which are present as columns in our \texttt{df.invariant} data set.
-You would include the dataframe in the \texttt{data} argument of our function, the name of the grouping variable in quotes for \texttt{group}, and the \emph{lavaan} model syntax in the \texttt{model} argument.
-The \texttt{mgcfa} function code runs an overall model with all data, regardless of group, each group separately on the model, then the steps described above: configural, metric, scalar, and strict invariance.
+The package does generally require raw data for bootstrapping purposes, and an example of how to simulate data from models and covariance/correlations tables sometimes provided in manuscripts (rather than the raw data) is provided in the supplemental documentation.
 
@@
 In real data, you may wish to run the model steps \emph{without} setting this option, examine the results of a configural or separate models, and then add the option for the values most similar.
-Additionally, you could complete partial invariance steps to determine which value appears most consistent to fix.
+Additionally, you could complete partial invariance steps to determine which value appears most consistent to fix the estimate.
 
@@
 
-\small
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{\# run our mgcfa function to run all models}
-\NormalTok{results.invariant }\OtherTok{\textless{}{-}} \FunctionTok{mgcfa}\NormalTok{(}\AttributeTok{data =}\NormalTok{ df.invariant, }\CommentTok{\#dataframe}
-                           \AttributeTok{group =} \StringTok{"group"}\NormalTok{, }
-                           \AttributeTok{model =}\NormalTok{ model.overall)}
-\CommentTok{\# what is saved for you}
-\FunctionTok{names}\NormalTok{(results.invariant)}
-\end{Highlighting}
-\end{Shaded}
-
-\normalsize
-
-\begin{verbatim}
-## [1] "model_coef"       "model_fit"        "model.overall"    "model.group1"    
-## [5] "model.group2"     "model.configural" "model.metric"     "model.scalar"    
-## [9] "model.strict"
-\end{verbatim}
-
-The results are saved as a list and include the following:
+The \texttt{mgcfa} function is designed to flexibly allow you to leverage \texttt{lavaan}'s package functions to calculate multiple measurement steps at once. You would include:
 
@@
 \item
-  \texttt{model\_coef}: a tidy dataframe with \emph{all} model's coefficients saved from the \emph{lavaan} outputs.
-Note that we can see that the intercept \texttt{\textasciitilde{}1} is set for question 1 but freely estimated for the latent variable.
+  the model syntax in the \texttt{model} argument
+\item
+  the dataframe in the \texttt{data} argument of our function
+\item
+  the name of the grouping variable in quotes for \texttt{group}
+\item
+  and the equality constraints you would like to impose in order in \texttt{group.equal}
+\item
+  \texttt{...} any other \emph{lavaan} arguments you would like to use such as \texttt{meanstructure} or \texttt{estimator}.
+\end{enumerate}
+
+Note: you can also use \texttt{sample.cov}, \texttt{sample.mean}, \texttt{sample.nobs} in this step for estimation of multi-group models, but simulated dataframes are needed for bootstrapping replication estimates.
+
+\small
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\# run our mgcfa function to run all models}
+\NormalTok{results.invariant }\OtherTok{\textless{}{-}} 
+  \CommentTok{\# name of the saved model syntax}
+  \FunctionTok{mgcfa}\NormalTok{(}\AttributeTok{model =}\NormalTok{ model.overall, }
+        \CommentTok{\# name of the dataframe}
+        \AttributeTok{data =}\NormalTok{ df.invariant,}
+        \CommentTok{\# name of the grouping variable}
+        \AttributeTok{group =} \StringTok{"group"}\NormalTok{,}
+        \CommentTok{\# equality constraints to impose in order}
+        \AttributeTok{group.equal =} \FunctionTok{c}\NormalTok{(}\StringTok{"loadings"}\NormalTok{, }\StringTok{"intercepts"}\NormalTok{, }\StringTok{"residuals"}\NormalTok{),}
+        \CommentTok{\# other options to send to lavaan cfa function}
+        \AttributeTok{meanstructure =}\NormalTok{ T)}
+
+\CommentTok{\# what is saved for you}
+\FunctionTok{names}\NormalTok{(results.invariant)}
+\end{Highlighting}
+\end{Shaded}
+
+\normalsize
+
+\begin{verbatim}
+## [1] "model_coef"        "model_fit"         "model_overall"    
+## [4] "group_models"      "model_configural"  "invariance_models"
+\end{verbatim}
+
+The following output is saved:
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi})}
+\tightlist
+\item
+  \texttt{model\_coef}: The parameter estimates for each model with the model step included in a \emph{model} column.
+This set of coefficients can be used for other functions.
+This dataframe is created with \emph{broom}'s \texttt{tidy()} function if you wish to recreate this table without running the \texttt{mgcfa()} function (Robinson et al., 2023).
 \end{enumerate}
@@
 ##    <chr>    <chr>    <dbl>     <dbl>     <dbl>     <dbl>   <dbl>   <dbl>   <dbl>
-##  1 "lv =~ ~ =~      1         0         NA     NA         0.780   0.598   0.598 
-##  2 "lv =~ ~ =~      0.564     0.0864     6.52   6.99e-11  0.440   0.435   0.435 
-##  3 "lv =~ ~ =~      0.748     0.105      7.12   1.09e-12  0.583   0.505   0.505 
-##  4 "lv =~ ~ =~      0.338     0.0804     4.20   2.62e- 5  0.264   0.250   0.250 
-##  5 "lv =~ ~ =~      0.904     0.120      7.52   5.48e-14  0.705   0.613   0.613 
+##  1 "lv =~ ~ =~      1         0         NA     NA         0.803   0.616   0.616 
+##  2 "lv =~ ~ =~      0.655     0.0880     7.44   9.77e-14  0.526   0.493   0.493 
+##  3 "lv =~ ~ =~      0.640     0.0895     7.15   8.83e-13  0.514   0.463   0.463 
+##  4 "lv =~ ~ =~      0.277     0.0749     3.69   2.24e- 4  0.222   0.209   0.209 
+##  5 "lv =~ ~ =~      0.955     0.117      8.13   4.44e-16  0.766   0.656   0.656 
 ##  6 "q1 ~1 " ~1      0         0         NA     NA         0       0       0     
-##  7 "lv ~1 " ~1     -0.0187    0.0584    -0.320  7.49e- 1 -0.0239 -0.0239 -0.0239
-##  8 "q1 ~~ ~ ~~      1.09      0.103     10.6    0         1.09    0.643   0.643 
-##  9 "q2 ~~ ~ ~~      0.828     0.0604    13.7    0         0.828   0.811   0.811 
-## 10 "q3 ~~ ~ ~~      0.997     0.0786    12.7    0         0.997   0.745   0.745 
+##  7 "lv ~1 " ~1     -0.0305    0.0582    -0.524  6.00e- 1 -0.0380 -0.0380 -0.0380
+##  8 "q1 ~~ ~ ~~      1.05      0.0995    10.6    0         1.05    0.620   0.620 
+##  9 "q2 ~~ ~ ~~      0.860     0.0653    13.2    0         0.860   0.757   0.757 
+## 10 "q3 ~~ ~ ~~      0.966     0.0711    13.6    0         0.966   0.785   0.785 
 ## # i 4 more variables: model <chr>, block <int>, group <int>, label <chr>
@@
 \item
-  \texttt{model\_fit}: a tidy dataframe with \emph{all} model's fit indices saved from the \emph{lavaan} outputs.
+  \texttt{model\_fit}: The model fit indices from \texttt{fitmeasures()} to review for overall model fit and invariance judgments. The name of the model is included in a \emph{model} column.
 \end{enumerate}
@@
 ##   <dbl> <dbl> <dbl> <dbl>  <dbl> <dbl>  <dbl>           <dbl>   <dbl> <dbl>
-## 1 0.979 7516. 7579. 0.994  6.37    15 0.0234          0.0697 0.0211 0.988
+## 1 0.998 7516. 7580. 1      0.650    15 0               0      0.00616 1.04 
 ## 2 0.948 3766. 3819. 0.976  7.79     15 0.0473          0.108  0.0312  0.953
-## 3 0.952 3762. 3815. 0.980  7.25    15 0.0424          0.104  0.0322 0.960
-## 4 0.950 7528. 7654. 0.978 15.0     30 0.0449          0.0886 0.0317 0.956
-## 5 0.942 7529. 7639. 0.954 24.7     26 0.0554          0.0905 0.0476 0.934
-## 6 0.952 7523. 7616. 0.964 26.2     22 0.0428          0.0760 0.0488 0.960
+## 3 0.974 3768. 3820. 1      4.48     15 0               0.0831 0.0210  1.01 
+## 4 0.961 7533. 7660. 0.991 12.3      30 0.0301          0.0785 0.0261  0.982
+## 5 0.965 7528. 7638. 0.994 15.4      26 0.0200          0.0660 0.0330  0.992
+## 6 0.969 7522. 7615. 1     17.3      22 0               0.0542 0.0352  1.00 
 ## # i 8 more variables: converged <lgl>, estimator <chr>, ngroups <int>,
@@
 \item
-  Saved \emph{lavaan} fitted objects that you can use the \texttt{summary()}, \texttt{parameterEstimates()}, \texttt{fitIndices()}, etc.
-on.
-Overall model indicates the model without grouping variables testing all data on the proposed model structure.
-This model is then tested separately for each group (\texttt{model.group1}, \texttt{model.group2}).
-The final models follow the Brown (2015) naming convention for sequential steps for testing MGCFA for measurement invariance (\texttt{model.configural}, \texttt{model.metric}, \texttt{model.scalar}, \texttt{model.strict}).
+  \texttt{model\_overall}: A saved \emph{lavaan} fitted model of all groups together without any equality constraints or grouping variables.
+These objects can be used with any function that normally takes a saved model: \texttt{parameterEstimates()}, \texttt{modificationIndices()}, \texttt{semPlot::semPaths()}, and so on (Epskamp, 2022).
+\item
+  \texttt{group\_models}: A list of saved fitted models for each group separately.
+\item
+  \texttt{model\_configural}: A saved fitted model for the configural model that nests together each group into one model with no other constraints.
+\item
+  \texttt{invariance\_models}: A list of saved fitted models that consecutively adds \texttt{group.equal} constraints.
 \end{enumerate}
 
-The results from the \texttt{model\_coef} table can then be used directly in the suggested plotting function. The plot outputs will be described below. First, here are the arguments for the function:
+\hypertarget{visualization-of-invariance}{%
+\subsection{Visualization of Invariance}\label{visualization-of-invariance}}
+
+\hypertarget{package-function}{%
+\subsubsection{Package Function}\label{package-function}}
+
+The results from the \texttt{model\_coef} table can then be used directly in \texttt{plot\_mi()}. The plot outputs will be described below. First, here are the arguments for the function:
 
@@
 \def\labelenumi{\arabic{enumi})}
+\tightlist
 \item
@@
 \item
-  \texttt{ci\_level}: What confidence limit do you want to plot? Use 1 - \(\alpha\).
+  \texttt{conf.level}: What confidence limit do you want to plot? Use 1 - \(\alpha\).
 \item
@@
 If you have items that load onto multiple latent variables, you will need to make multiple plots.
+\item
+  \texttt{plot\_groups}: If you include more than two groups in a multi-group model, the automatic assumption is that you want the first two groups for this visualization.
+If not, include the names of the groups here to plot.
 \end{enumerate}
@@
 \begin{Highlighting}[]
-\FunctionTok{plot\_mgcfa}\NormalTok{(}
-  \AttributeTok{data\_coef =}\NormalTok{ results.invariant}\SpecialCharTok{$}\NormalTok{model\_coef, }\CommentTok{\# output from model\_coef}
-  \AttributeTok{model\_step =} \StringTok{"Configural"}\NormalTok{, }\CommentTok{\# which model do you want to plot}
-  \AttributeTok{item\_name =} \StringTok{"q4"}\NormalTok{, }\CommentTok{\# name of observed item}
-  \AttributeTok{x\_limits =} \FunctionTok{c}\NormalTok{(}\SpecialCharTok{{-}}\DecValTok{1}\NormalTok{,}\DecValTok{1}\NormalTok{), }\CommentTok{\# latent variable limits to graph}
-  \AttributeTok{y\_limits =} \FunctionTok{c}\NormalTok{(}\FunctionTok{min}\NormalTok{(df.invariant}\SpecialCharTok{$}\NormalTok{q4), }\FunctionTok{max}\NormalTok{(df.invariant}\SpecialCharTok{$}\NormalTok{q4)), }\CommentTok{\# Y min and max in data }
-  \AttributeTok{ci\_level =}\NormalTok{ .}\DecValTok{95}\NormalTok{, }\CommentTok{\# what ci do you want}
-  \AttributeTok{model\_results =}\NormalTok{ results.invariant}\SpecialCharTok{$}\NormalTok{model.configural, }\CommentTok{\# what model results do you want }
-  \AttributeTok{lv\_name =} \StringTok{"lv"} \CommentTok{\# which latent variable do you want }
+\NormalTok{invariant.plot }\OtherTok{\textless{}{-}} 
+  \FunctionTok{plot\_mi}\NormalTok{(}
+    \CommentTok{\# output from model\_coef}
+    \AttributeTok{data\_coef =}\NormalTok{ results.invariant}\SpecialCharTok{$}\NormalTok{model\_coef, }
+    \CommentTok{\# which model do you want to plot}
+    \AttributeTok{model\_step =} \StringTok{"Configural"}\NormalTok{, }
+    \CommentTok{\# name of observed item}
+    \AttributeTok{item\_name =} \StringTok{"q4"}\NormalTok{, }
+    \CommentTok{\# latent variable limits to graph}
+    \AttributeTok{x\_limits =} \FunctionTok{c}\NormalTok{(}\SpecialCharTok{{-}}\DecValTok{1}\NormalTok{,}\DecValTok{1}\NormalTok{), }
+    \CommentTok{\# Y min and max in data }
+    \AttributeTok{y\_limits =} \FunctionTok{c}\NormalTok{(}\FunctionTok{min}\NormalTok{(df.invariant}\SpecialCharTok{$}\NormalTok{q4), }\FunctionTok{max}\NormalTok{(df.invariant}\SpecialCharTok{$}\NormalTok{q4)),}
+    \CommentTok{\# what ci do you want}
+    \AttributeTok{conf.level =}\NormalTok{ .}\DecValTok{95}\NormalTok{, }
+    \CommentTok{\# what model results do you want }
+    \AttributeTok{model\_results =}\NormalTok{ results.invariant}\SpecialCharTok{$}\NormalTok{model\_configural,}
+    \CommentTok{\# which latent variable do you want }
+    \AttributeTok{lv\_name =} \StringTok{"lv"} 
 \NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\normalsize
-
-\hypertarget{visualization-of-invariance}{%
-\subsection{Visualization of Invariance}\label{visualization-of-invariance}}
-
-The output from this model can be found in Figure \ref{fig:invariant-pic}.
+
+\FunctionTok{names}\NormalTok{(invariant.plot)}
+\end{Highlighting}
+\end{Shaded}
+
+\normalsize
+
+\begin{verbatim}
+## [1] "complete"  "intercept" "mean"      "variance"
+\end{verbatim}
+
+The output from this function are several \emph{ggplot2} objects that can be edited or saved directly using \emph{ggplot2} functionality (Wickham, 2016).
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi})}
+\tightlist
+\item
+  \texttt{complete}: The output from this model can be found in Figure \ref{fig:invariant-pic}.
 On the left hand side, the item invariance is plotted, and on the right hand side, the latent mean distributions for the two groups are plotted.
@@
 All parameter estimates are plotted on the unstandardized estimates and their confidence interval based on the standard error of the estimate.
-All plots are made with \emph{ggplot2} (Wickham, 2016) and \emph{cowplot} (Wilke, 2020).
-
-\hypertarget{loadings}{%
-\subsubsection{Loadings}\label{loadings}}
-
+All plots are made with \emph{ggplot2} and \emph{cowplot} (Wilke, 2020).
+\end{enumerate}
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/invariant-pic-1.pdf}
+\caption{\label{fig:invariant-pic}Invariant Model Visualization}
+\end{figure}
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi})}
+\setcounter{enumi}{1}
+\tightlist
+\item
+  \texttt{intercept}: Only the left hand side of the complete plot designed to represent intercepts and factor loadings.
 Factor loadings represent the slope of the regression equation for the latent variable predicting the scores on the observed variable (\(\hat{Y} \sim b_0 + b_1X + \epsilon\)).
-Therefore, the latent variable is shown on the x-axis using standardized values (i.e., \emph{z}-scores) where -1 indicates one standard deviation below the mean for the latent variable, 0 indicates the mean for the latent variable and so on.
 The y-axis indicates the observed variable scores, and here, the plot includes the entire range of the scale of the data for item four.
-The coefficient (\(b_1\)) for group 1 was 0.40, while the coefficient for group 2 was 0.34.
+The coefficient (\(b_1\)) for group 1 was 0.40, while the coefficient for group 2 was 0.21.
 The ribbon bands around the plotted slopes indicate the confidence interval for that estimate.
 In this plot, while the coefficients for each group are not literally equal, the overlapping and parallel slope bands indicate they are not different practically.
-
-\hypertarget{intercepts}{%
-\subsubsection{Intercepts}\label{intercepts}}
+\end{enumerate}
 
@@
 
-\hypertarget{residuals}{%
-\subsubsection{Residuals}\label{residuals}}
-
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi})}
+\setcounter{enumi}{2}
+\item
+  \texttt{mean}: The right hand side of the complete plot graphing the latent variable means and density from the data.
+The latent variable is shown on the x-axis using standardized values (i.e., \emph{z}-scores) where -1 indicates one standard deviation below the mean for the latent variable, 0 indicates the mean for the latent variable and so on.
+The lines indicate the means of the latent variables from the simulated dataset.
+Group labels are represented in the figure caption on the bottom.
+Group 1 is usually the group that is alphabetically first in the data set or whichever group is the first that appears when using the \texttt{levels()} command.
+\item
+  \texttt{variance}: A split geom violin plot indicating the variance distribution of the plotted item.
 Residuals are trickier to plot, as they are the left over error when predicting the observed variables \(\epsilon\).
@@
 Therefore, residuals are represented in the inset picture at the bottom right of the item invariance plot.
-The black bars represent the estimated residual for each group (group 1: 0.91, group 2: 1.16).
+The black bars represent the estimated residual for each group (group 1: 0.91, group 2: 1.22).
 The distributions are plotted to represent the normal spread of values using the standard error of the residuals.
@@
 Note that the placement has nothing to do with the x or y-axis and is designed to always show in the same location, regardless of size/value.
-
-\hypertarget{latent-means}{%
-\subsubsection{Latent Means}\label{latent-means}}
-
-The overall impact of differences on the latent means can be found in the right hand visualization.
-The latent means are calculated by using the \texttt{lavPredict} function and then plotted as overlapping histograms.
-The vertical colored lines represent the mean for each group, and the spread of the distribution can be examined using the density coloring.
-Finally, group labels are represented in the figure caption on the bottom.
-Group 1 is usually the group that is alphabetically first in the data set or whichever group is the first that appears when using the \texttt{levels()} command.
-
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/invariant-pic-1.pdf}
-\caption{\label{fig:invariant-pic}Invariant Model Visualization}
-\end{figure}
-
-\hypertarget{graphing-effect-size}{%
-\subsubsection{Graphing Effect Size}\label{graphing-effect-size}}
-
-The \(d_{MACS}\) value for item 4 in the invariant model was 0.06, representing a nil or unimportant difference in this manuscript.
+The plots are included separately so they can be arranged in a different fashion if desired.
+\end{enumerate}
+
+\hypertarget{simulated-results}{%
+\subsubsection{Simulated Results}\label{simulated-results}}
+
+The \(d_{MACS}\) value for item 4 in the invariant model was 0.16, representing a nil or unimportant difference in this manuscript.
 It is important to note that while Nye et al.
 (2019) suggests specific sizes for small, medium, and large, each researcher should determine for themselves what effects represent.
-Figure \ref{fig:small-load-pic} displays the results from the small (\(d_{MACS}\) = 0.12) difference in loadings, while Figure \ref{fig:med-load-pic} displays the results from the medium (\(d_{MACS}\) = 0.43) difference in loadings, and Figure \ref{fig:large-load-pic} shows the large (\(d_{MACS}\) = 0.63) differences.
+Figure \ref{fig:small-load-pic} displays the results from the small (\(d_{MACS}\) = 0.27) difference in loadings, while Figure \ref{fig:med-load-pic} displays the results from the medium (\(d_{MACS}\) = 0.53) difference in loadings, and Figure \ref{fig:large-load-pic} shows the large (\(d_{MACS}\) = 0.68) differences.
 When investigating the slope values, we can clearly see the change in the loading for the second group (the only manipulated variable, although random data set generation may also change intercepts and residuals slightly).
@@
 Additionally, consider that we set the scaling of the model to 0.
-The estimate for the lv mean in the large loading model was group 1: 0.00, and group 2: -0.04, which results in 0.04 difference in group means.
+The estimate for the lv mean in the large loading model was group 1: 0.00, and group 2: -0.06, which results in 0.06 difference in group means.
 The practical implications of this difference will depend on the research and interpretations of the researcher.
@@
 
-For intercepts, the small (Figure \ref{fig:small-int-pic}), medium (Figure \ref{fig:med-int-pic}), and large (Figure \ref{fig:large-int-pic}) depictions represent \(d_{MACS}\) values of 0.29, 0.52, and 0.76, respectively.
+For intercepts, the small (Figure \ref{fig:small-int-pic}), medium (Figure \ref{fig:med-int-pic}), and large (Figure \ref{fig:large-int-pic}) depictions represent \(d_{MACS}\) values of 0.26, 0.47, and 0.70, respectively.
 Intercept differences can be clearly seen represented by the spacing out of the intercept locations (and thus, the overall line as well).
@@
 Last, the effect of the residuals is plotted in small (Figure \ref{fig:small-res-pic}), medium (Figure \ref{fig:med-res-pic}), and large (Figure \ref{fig:large-res-pic}) formats.
-While \(d_{MACS}\) values are not technically available for the residuals, our models showed 0.20, 0.14, and 0.11, respectively.
+While \(d_{MACS}\) values are not technically available for the residuals, our models showed 0.19, 0.19, and 0.16, respectively.
 These differences in values are variable due to the random generation of data sets for each measurement invariance manipulation.
@@
 
+\hypertarget{partial-invariance-calculation}{%
+\subsection{Partial Invariance Calculation}\label{partial-invariance-calculation}}
+
+\hypertarget{package-function-1}{%
+\subsubsection{Package Function}\label{package-function-1}}
+
+The results of the simulated models are presented in the appendix, demonstrating that each simulated dataset shows partial invariance if item four is allowed to vary between groups.
+The function takes the following arguments:
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi})}
+\tightlist
+\item
+  \texttt{saved\_model}: The saved \emph{lavaan} model with the equality constraints at the level of measurement invariance you would like to examine for partial invariance.
+\item
+  \texttt{data}: The dataframe where the model was estimated.
+\item
+  \texttt{model}: The model syntax for the overall model.
+\item
+  \texttt{group}: The grouping variable column in the dataframe.
+\item
+  \texttt{group.equal}: The equality constraints including in your original multi-group tests.
+\item
+  \texttt{partial\_step}: The level of partial invariance you wish to test.
+\end{enumerate}
+
+\small
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{partial.invariant }\OtherTok{\textless{}{-}}
+  \FunctionTok{partial\_mi}\NormalTok{(}
+    \CommentTok{\# saved model output with constraints}
+    \AttributeTok{saved\_model =}\NormalTok{ results.invariant}\SpecialCharTok{$}\NormalTok{invariance\_models}\SpecialCharTok{$}\NormalTok{model.residuals,}
+    \CommentTok{\# dataframe from model }
+    \AttributeTok{data =}\NormalTok{ df.invariant,}
+    \CommentTok{\# model syntax }
+    \AttributeTok{model =}\NormalTok{ model.overall,}
+    \CommentTok{\# group column name }
+    \AttributeTok{group =} \StringTok{"group"}\NormalTok{,}
+    \CommentTok{\# group equality constraints from your mgcfa}
+    \AttributeTok{group.equal =} \FunctionTok{c}\NormalTok{(}\StringTok{"loadings"}\NormalTok{, }\StringTok{"intercepts"}\NormalTok{, }\StringTok{"residuals"}\NormalTok{),}
+    \CommentTok{\# which step you want to examine for partial invariance}
+    \AttributeTok{partial\_step =} \StringTok{"residuals"}
+\NormalTok{    )}
+
+\FunctionTok{names}\NormalTok{(partial.invariant)}
+\end{Highlighting}
+\end{Shaded}
+
+\normalsize
+
+\begin{verbatim}
+## [1] "models"    "fit_table"
+\end{verbatim}
+
+In this function, each parameter with the appropriate \emph{lavaan} syntax is relaxed individually (i.e., \texttt{\textasciitilde{}1} for intercepts, \texttt{\textasciitilde{}\textasciitilde{}} for residuals, etc.).
+The fitted models are saved in the \texttt{models} output, and the \texttt{fit\_table} output includes all fit indices for each model to investigate potential areas of partial invariance based on the researcher's desired criterion.
+Note: the \texttt{partial\_step} function is used to determine which types of \texttt{op} or operators to freely estimate between groups.
+If one chooses residuals, you will also freely estimate the residual for the latent variable or any other residuals found in the model.
+These items may be ignored if they were not meant to be included.
+
+\small
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{head}\NormalTok{(partial.invariant}\SpecialCharTok{$}\NormalTok{fit\_table }\SpecialCharTok{\%\textgreater{}\%} 
+\NormalTok{       dplyr}\SpecialCharTok{::}\FunctionTok{select}\NormalTok{(free.parameter, cfi, rmsea))}
+\end{Highlighting}
+\end{Shaded}
+
+\normalsize
+
+\begin{verbatim}
+## # A tibble: 6 x 3
+##   free.parameter cfi        rmsea     
+##   <chr>          <lvn.vctr> <lvn.vctr>
+## 1 q1 ~~ q1       0.9902679  0.02108648
+## 2 q2 ~~ q2       0.9868905  0.02447336
+## 3 q3 ~~ q3       0.9958241  0.01381266
+## 4 q4 ~~ q4       1.0000000  0.00000000
+## 5 q5 ~~ q5       0.9868088  0.02454944
+## 6 lv ~~ lv       0.9906154  0.02025143
+\end{verbatim}
+
+\hypertarget{replication-and-effect-size-model}{%
+\subsection{Replication and Effect Size: Model}\label{replication-and-effect-size-model}}
+
+\hypertarget{package-function-2}{%
+\subsubsection{Package Function}\label{package-function-2}}
+
+The \texttt{bootstrap\_rr} function in \emph{visualizemi} was designed to estimate the likely replication of overall model invariance with the assumption that the data used for the estimation represents the larger population.
+The following arguments are used:
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi})}
+\tightlist
+\item
+  \texttt{saved\_configural}: a saved fitted model at the configural level with no equality constraints.
+This model should include all other \emph{lavaan} settings you would like to use, such as \texttt{estimator} or \texttt{ordered}.
+\end{enumerate}
+
+\small
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{boot.model.invariant }\OtherTok{\textless{}{-}} 
+  \FunctionTok{bootstrap\_rr}\NormalTok{(}
+    \CommentTok{\# saved configural model }
+    \AttributeTok{saved\_configural =}\NormalTok{ results.invariant}\SpecialCharTok{$}\NormalTok{model\_configural,}
+    \CommentTok{\# dataframe}
+    \AttributeTok{data =}\NormalTok{ df.invariant,}
+    \CommentTok{\# model syntax}
+    \AttributeTok{model =}\NormalTok{ model.overall, }
+    \CommentTok{\# group variable column in dataframe}
+    \AttributeTok{group =} \StringTok{"group"}\NormalTok{,}
+    \CommentTok{\# number of bootstraps}
+    \AttributeTok{nboot =} \DecValTok{1000}\NormalTok{, }
+    \CommentTok{\# which fit index you would like to use}
+    \AttributeTok{invariance\_index =} \StringTok{"cfi"}\NormalTok{,}
+    \CommentTok{\# what is your criterion for that fit index}
+    \AttributeTok{invariance\_rule =}\NormalTok{ .}\DecValTok{01}\NormalTok{,}
+    \CommentTok{\# what equality constraints are you testing }
+    \AttributeTok{group.equal =} \FunctionTok{c}\NormalTok{(}\StringTok{"loadings"}\NormalTok{, }\StringTok{"intercepts"}\NormalTok{, }\StringTok{"residuals"}\NormalTok{)}
+\NormalTok{  )}
+\end{Highlighting}
+\end{Shaded}
+
+\normalsize
+
+The data included in this function will be sampled, with replacement, at the same size as the current dataset, and the included invariance equality constraints are estimated.
+Each step will be compared to the previous step using the invariance index and comparison rule entered.
+The output is a dataframe of the proportion of non-invariant bootstraps from the real data and the same bootstrapped dataset with the group labels randomly assigned.
+The effect size comparison of proportions, \(h\), for non-invariant comparisons:
+
+\[h_{nmi} = 2 \times (asin\sqrt{p_{data}} - asin\sqrt{p_{random}})\]
+The alternative, \(h_{mi}\), for effect size of measurement invariance replication would simply be the inverse sign of \(h_{nmi}\) and is also included in the table.
+Two additional columns \(h_{nmi_p}\) and \(h_{nmi_p}\) represent the \(h\) values divided by the upper bound of \(h\) (i.e., \(\pi\)), to help with interpretation of the effect size (thus, bounding \(h\) to -1 to 1).
+
+\hypertarget{simulated-results-1}{%
+\subsubsection{Simulated Results}\label{simulated-results-1}}
+
+Figure \ref{fig:boot-rr-pic} portrays the \(h_{nmi_p}\) values by simulated non-invariance, strength of non-invariance, and type of equality constraint.
+This image represents 100 simulations of data by 1000 bootstrapped runs (averaged) to explore the expected pattern of results.
+The bars are arranged to show what a researcher might inspect when thinking about replication possibilities and their effect sizes (i.e., only three bars for each equality constraint would be calculated).
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/boot-rr-pic-1.pdf}
+\caption{\label{fig:boot-rr-pic}Visualization of the effect size of bootstrapped replication proportions on simulated data.
+Each panel indicates the simulated data type, colors represent the differences in the strength of the non-invariance, and the bars on the x-axis represent the effect size for the equality constraint.}
+\end{figure}
+
+In the data that was simulated to be invariant between groups, effect sizes are still non-zero (loadings \(h_{nmi_p}\) = 0.28, intercepts = \(h_{nmi_p}\) = 0.06, \(h_{nmi_p}\) = 0.00).
+This result mirrors the effects found in the literature - that often, many models fail to show invariance, and potentially not because measurement is poor but because of natural random variation in parameter estimates.
+This result also indicates the need to be able to identify if specific parameters are driving the differences, which is shown in the next section.
+
+Next, Figure \ref{fig:boot-rr-pic} demonstrates the patterns one might find for small, medium, and large effects at each type of invariance when data is simulated with \emph{one} difference.
+For loadings, the pattern shows a larger effect for loadings with zero or negative effect sizes for other effect sizes.
+The intercept simulations show non-zero effect sizes in the loadings and intercepts, likely for the same reasons \(d_{MACS}\) is interpreted as a combined effect size.
+When intercepts are changed, loadings may naturally shift with those means.
+Last, the residual results present an unexpected pattern, wherein the effect is primarily seen in the loadings, rather than the residuals step.
+However, when distributions of error variance are different, one may expect that those effects are pushed toward the loadings as well (as values can vary more, thus potentially weakening the relationship between observed and latent variable).
+
+An example of interpretation on real data is given in a later section.
+From a research study, only one effect size for each equality constraint would be calculated.
+The interpretation will often be up to the researcher's smallest effect of interest, and this simulation gives some guidance that the values should not be interpreted with traditional rules of thumb.
+The pattern of effects is potentially the most useful information: 1) positive effects on the loadings with negative or very close to zero effects on the other parameters may indicate a non-replication in loadings, 2) equal effects on loadings and intercepts with smaller or negative effects may indicate intercepts may be an issue, and 3) residuals may be determined by the same pattern as loadings but with a smaller ratio of loadings to residuals effect (i.e., loadings \(h_{nmi}\) / residuals \(h_{nmi}\).
+The ``size'' could be determined by the ratio of effect sizes for each constraint.
+Of course, this represents one simulation study, and results from many studies in a meta-analysis would be fruitful for future work.
+
+\hypertarget{replication-and-effect-size-parameters}{%
+\subsection{Replication and Effect Size: Parameters}\label{replication-and-effect-size-parameters}}
+
+\hypertarget{package-function-3}{%
+\subsubsection{Package Function}\label{package-function-3}}
+
+After examining the overall model potential replication effect size, the individual parameters within a model can be bootstrapped for partial invariance to with that parameter relaxed (overall partial model statistics) and the difference in group parameter estimates (parameter effect size).
+This function uses arguments seen in other functions, so they will not be repeated here.
+The general setup consists of using the model you think could be partially invariant in the \texttt{saved\_model} argument and the fit index for comparison for the model with less constraints in \texttt{invariance\_compare}.
+This example examines the loadings in the invariant model, so \texttt{saved\_model} uses the \texttt{mgcfa} output for equality constraints present on the loadings and compares that model to the configural model with no equality constraints on the loadings.
+The \texttt{partial\_step} argument will be used to determine which operation syntax (i.e.~\texttt{=\textasciitilde{}} for loadings) to relax for modeling.
+
+\small
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{boot.partial.invariant }\OtherTok{\textless{}{-}} 
+      \FunctionTok{bootstrap\_partial}\NormalTok{(}
+        \CommentTok{\# saved model you want to examine the partial loadings for }
+        \AttributeTok{saved\_model =}\NormalTok{ results.invariant}\SpecialCharTok{$}\NormalTok{invariance\_models}\SpecialCharTok{$}\NormalTok{model.loadings,}
+        \CommentTok{\# the dataset }
+        \AttributeTok{data =}\NormalTok{ df.invariant, }
+        \CommentTok{\# the model }
+        \AttributeTok{model =}\NormalTok{ model.overall,}
+        \CommentTok{\# the group variable in the dataset}
+        \AttributeTok{group =} \StringTok{"group"}\NormalTok{, }
+        \CommentTok{\# number of bootstraps}
+        \AttributeTok{nboot =} \DecValTok{1000}\NormalTok{,}
+        \CommentTok{\# which fit index you would like to use to determine partial invariance}
+        \AttributeTok{invariance\_index =} \StringTok{"cfi"}\NormalTok{, }
+        \CommentTok{\# what is the invariance rule }
+        \AttributeTok{invariance\_rule =}\NormalTok{ .}\DecValTok{01}\NormalTok{, }
+        \CommentTok{\# what are we comparing the saved model fit index to }
+        \AttributeTok{invariance\_compare =} \FunctionTok{fitmeasures}\NormalTok{(results.invariant}\SpecialCharTok{$}\NormalTok{model\_configural, }\StringTok{"cfi"}\NormalTok{), }
+        \CommentTok{\# what step are we using for invariance}
+        \AttributeTok{partial\_step =} \StringTok{"loadings"}\NormalTok{, }
+        \CommentTok{\# what equality constraints should be imposed }
+        \AttributeTok{group.equal =} \FunctionTok{c}\NormalTok{(}\StringTok{"loadings"}\NormalTok{)}
+\NormalTok{      )}
+\end{Highlighting}
+\end{Shaded}
+
+\normalsize
+
+\small
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{names}\NormalTok{(boot.partial.invariant)}
+\end{Highlighting}
+\end{Shaded}
+
+\normalsize
+
+\begin{verbatim}
+## [1] "invariance_plot"        "effect_invariance_plot" "density_plot"          
+## [4] "boot_DF"                "boot_summary"           "boot_effects"
+\end{verbatim}
+
+The saved output includes several dataframes and plots.
+The first is the \texttt{boot\_DF} which the summary of each run in a dataframe for plotting or summarization.
+This dataframe includes the estimate for each paramter (\texttt{term}) separated by group and type (\texttt{boot\_1}, \texttt{boot\_2} are the bootstrapped estimates for group 1 and group 2, while the same \texttt{random} columns indicate the randomly assigned groups).
+The fit index used to determine invariance is included for bootstrapped and random estimates, and then the differences between groups and if they were ``invariant'' or not given the researcher supplied rule.
+
+\small
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{head}\NormalTok{(boot.partial.invariant}\SpecialCharTok{$}\NormalTok{boot\_DF)}
+\end{Highlighting}
+\end{Shaded}
+
+\normalsize
+
+\begin{verbatim}
+##       term    boot_1     boot_2  random_1  random_2  boot_fit random_fit
+## 1 lv =~ q1 0.4548783 0.49928877 0.4627486 0.4651391 0.9296990  1.0000000
+## 2 lv =~ q2 0.3599017 0.56241016 0.4100874 0.4980215 0.9441125  1.0000000
+## 3 lv =~ q3 0.4254283 0.33640233 0.4274329 0.3422124 0.9377130  1.0000000
+## 4 lv =~ q4 0.3930716 0.03320619 0.1380833 0.2628802 0.9750274  1.0000000
+## 5 lv =~ q5 0.7306414 0.73512673 0.7093891 0.7532471 0.9266587  1.0000000
+## 6 lv =~ q1 0.5537083 0.57086815 0.5732166 0.5475714 0.8958929  0.9814658
+##   boot_difference random_difference boot_index_difference
+## 1    -0.044410454      -0.002390463                 FALSE
+## 2    -0.202508484      -0.087934027                 FALSE
+## 3     0.089025927       0.085220565                 FALSE
+## 4     0.359865463      -0.124796846                 FALSE
+## 5    -0.004485377      -0.043857947                 FALSE
+## 6    -0.017159815       0.025645271                 FALSE
+##   random_index_difference
+## 1                    TRUE
+## 2                    TRUE
+## 3                    TRUE
+## 4                    TRUE
+## 5                    TRUE
+## 6                    TRUE
+\end{verbatim}
+
+Next, the \texttt{boot\_summary} includes a summarized form of the bootstrapped results from separated by bootstrapping versus random and invariant/non-invariant.
+The \(d_s\) for between groups Cohen's \(d\) is shown below, and the non-central confidence interval is included.
+Effect sizes are only calculated when the number of bootstrapped estimates is at least 10\% of the data - therefore, you would not receive effect sizes with almost no bootstrapped runs.
+This dataframe should be used to determine which parameter may be different and at what size between groups in a replication of the study.
+
+\small
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{boot.partial.invariant}\SpecialCharTok{$}\NormalTok{boot\_summary }\SpecialCharTok{\%\textgreater{}\%} 
+\NormalTok{  dplyr}\SpecialCharTok{::}\FunctionTok{select}\NormalTok{(term, d\_boot, d\_random)}
+\end{Highlighting}
+\end{Shaded}
+
+\normalsize
+
+\begin{verbatim}
+## # A tibble: 10 x 4
+## # Groups:   term, invariant [10]
+##    invariant term       d_boot d_random
+##    <lgl>     <chr>       <dbl>    <dbl>
+##  1 FALSE     lv =~ q1 -0.0299   0.0583 
+##  2 TRUE      lv =~ q1  0.0337   0.0116 
+##  3 FALSE     lv =~ q2 -0.0326   0.0933 
+##  4 TRUE      lv =~ q2  0.146    0.0309 
+##  5 FALSE     lv =~ q3 -0.0463   0.113  
+##  6 TRUE      lv =~ q3 -0.148    0.0743 
+##  7 FALSE     lv =~ q4  0.00785 -0.0668 
+##  8 TRUE      lv =~ q4 -0.0157   0.0389 
+##  9 FALSE     lv =~ q5 -0.00129 -0.169  
+## 10 TRUE      lv =~ q5  0.122   -0.00853
+\end{verbatim}
+
+The \texttt{boot\_effects} table creates a summary similar to the overall model replication table based on the proportion of runs that were considered invariant versus not for each parameter.
+Note that the effects match the overall results, such that simulated invariant data appears to still show the likelihood that loadings may not replicate in a similar dataset.
+
+\small
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{boot.partial.invariant}\SpecialCharTok{$}\NormalTok{boot\_effects}
+\end{Highlighting}
+\end{Shaded}
+
+\normalsize
+
+\begin{verbatim}
+## # A tibble: 5 x 7
+##   term     non_invariant random_non_invariant h_nmi  h_mi h_nmi_p h_mi_p
+##   <chr>            <dbl>                <dbl> <dbl> <dbl>   <dbl>  <dbl>
+## 1 lv =~ q1         0.853                0.236  1.34 -1.34   0.427 -0.427
+## 2 lv =~ q2         0.858                0.237  1.35 -1.35   0.430 -0.430
+## 3 lv =~ q3         0.851                0.23   1.35 -1.35   0.429 -0.429
+## 4 lv =~ q4         0.84                 0.229  1.32 -1.32   0.420 -0.420
+## 5 lv =~ q5         0.819                0.237  1.25 -1.25   0.397 -0.397
+\end{verbatim}
+
+Plots of the results from dataframes can be found within the \texttt{bootstrap\_partial()} function.
+Figure \ref{fig:invariance-partial-fig} shows the difference between parameters for groups in the bootstrapped and randomly assigned group runs.
+Figure \ref{fig:density-partial-fig} shows the density plot of the estimates for each group organized by bootstrapped and randomly assigned groups and the invariance decision for each bootstrapped run.
+Last, Figure \ref{fig:effect-partial-fig} indicates the \(d_s\) value between groups with an indication of the number of data points in each estimate (i.e., dot size).
+These visualizations should allow a researcher to understand the likelihood of replication for each parameter, as well as the potential size of the differences.
+Therefore, one could indicate a specific smallest effect size of interest, rather than a invariance cut-off rule of thumb when planning a replication or registered report.
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/invariance-partial-fig-1.pdf}
+\caption{\label{fig:invariance-partial-fig}Visualization of the difference score between groups by parameter for invariant and non-invariant bootstrapped and randomly assigned group data.}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/density-partial-fig-1.pdf}
+\caption{\label{fig:density-partial-fig}Visualization of the number of estimates for each group by bootstrapped and randomly assigned group runs by their invariance decision.}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/effect-partial-fig-1.pdf}
+\caption{\label{fig:effect-partial-fig}Visualization of effect size between groups by parameter for invariant and non-invariant bootstrapped and randomly assigned group data.
+The size of the dots indicate the number of data points for that estimate.}
+\end{figure}
+
+\hypertarget{simulated-results-2}{%
+\subsubsection{Simulated Results}\label{simulated-results-2}}
+
+Figure \ref{fig:effect-large-loading-pic} shows the effect size differences within large loadings simulations.
+The results demonstrate that most of the loadings were considered non-invariant in the bootstrapped models (while holdings all others equal).
+This result is partially due to simulating very good data, so small changes in loadings results in a drop in fit for our chosen invariance index.
+However, we can use this graph to show that question four shows a possible effect size ranging from -0.07 to 0.13.
+The \(h_{nmi_p}\) value for question four was 0.27, representing about a quarter of a possible total effect.
+Last, the density plot in Figure \ref{fig:density-large-loading-pic} shows the separation of the two different groups loadings in item four, thus, illustrating group differences in the findings for their loadings.
+Each of the other combination of plots can be found in the supplemental materials.
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/effect-large-loading-pic-1.pdf}
+\caption{\label{fig:effect-large-loading-pic}Bootstrapped and Random Group effect size differences in loadings for the Large Loading difference simulation.
+The size of the point reprensents the number of data points included in that calculation.}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/density-large-loading-pic-1.pdf}
+\caption{\label{fig:density-large-loading-pic}Bootstrapped and Random density plots for invariant and non-invariant bootstrapped partial effects examining only large loadings.}
+\end{figure}
+
 \hypertarget{an-example-analysis}{%
@@
 \begin{Highlighting}[]
-\CommentTok{\# load the data}
-\FunctionTok{load}\NormalTok{(}\StringTok{"RS14.Rdata"}\NormalTok{)}
+\CommentTok{\# load the data, it is called DF}
+\FunctionTok{load}\NormalTok{(}\StringTok{"manu\_data/RS14.Rdata"}\NormalTok{)}
 
@@
 \CommentTok{\# run the multi{-}group CFA}
-\NormalTok{results.rs }\OtherTok{\textless{}{-}} \FunctionTok{mgcfa}\NormalTok{(}\AttributeTok{data =}\NormalTok{ DF, }
+\NormalTok{results.rs }\OtherTok{\textless{}{-}} \FunctionTok{mgcfa}\NormalTok{(}
+  \AttributeTok{model =}\NormalTok{ model.rs,}
+  \AttributeTok{data =}\NormalTok{ DF, }
   \AttributeTok{group =} \StringTok{"sample"}\NormalTok{, }
-                    \AttributeTok{model =}\NormalTok{ model.rs)}
+  \AttributeTok{group.equal =} \FunctionTok{c}\NormalTok{(}\StringTok{"loadings"}\NormalTok{, }\StringTok{"intercepts"}\NormalTok{, }\StringTok{"residuals"}\NormalTok{)}
+\NormalTok{  )}
 \end{Highlighting}
@@
 \NormalTok{results.rs}\SpecialCharTok{$}\NormalTok{model\_fit }\SpecialCharTok{\%\textgreater{}\%} 
-        \FunctionTok{select}\NormalTok{(model, AIC, BIC, cfi, tli, rmsea, srmr)}
+\NormalTok{        dplyr}\SpecialCharTok{::}\FunctionTok{select}\NormalTok{(model, AIC, BIC, cfi, tli, rmsea, srmr)}
 \end{Highlighting}
@@
 \midrule
-Overall & 126,750.491 & 126,999.816 & 0.934 & 0.923 & 0.094 & 0.033\\
-Group 1 & 52,989.421 & 53,196.870 & 0.919 & 0.904 & 0.090 & 0.041\\
-Group 2 & 69,128.985 & 69,358.973 & 0.928 & 0.915 & 0.108 & 0.033\\
+Overall & 126,722.491 & 126,888.707 & 0.934 & 0.923 & 0.094 & 0.036\\
+Group Clinical & 52,961.421 & 53,099.720 & 0.919 & 0.904 & 0.090 & 0.044\\
+Group Student & 69,100.985 & 69,254.310 & 0.928 & 0.915 & 0.108 & 0.035\\
 Configural & 122,118.406 & 122,617.055 & 0.926 & 0.912 & 0.102 & 0.036\\
-Metric & 122,144.532 & 122,566.010 & 0.925 & 0.918 & 0.098 & 0.043\\
-Scalar & 122,544.109 & 122,888.415 & 0.911 & 0.910 & 0.103 & 0.052\\
-Strict & 126,466.241 & 126,727.438 & 0.780 & 0.793 & 0.156 & 0.086\\
+loadings & 122,144.532 & 122,566.010 & 0.925 & 0.918 & 0.098 & 0.043\\
+intercepts & 122,544.109 & 122,888.415 & 0.911 & 0.910 & 0.103 & 0.052\\
+residuals & 126,466.241 & 126,727.438 & 0.780 & 0.793 & 0.156 & 0.086\\
 \bottomrule
@@
 
-Table \ref{fig:invariant-pic} indicates the results after running the one-factor model.
+Table \ref{tab:rs-table} indicates the results after running the one-factor model.
 There are several guidelines for assessing assessing a degradation in model fit (Cao \& Liang, 2022; Cheung \& Rensvold, 2002; Counsell et al., 2020; Jin, 2020; Putnick \& Bornstein, 2016) but for the purposes of this illustration \(\Delta\)CFI \textgreater{} .01 will be used.
-Table \ref{fig:invariant-pic} indicates that fit was degraded when the constraint on equal item intercepts was added.
+Table \ref{tab:rs-table} indicates that fit was degraded when the constraint on equal item intercepts was added.
 The code below provides an example of testing each item individually by relaxing the constraints and recalculating the CFI.
@@
 \begin{Highlighting}[]
-\CommentTok{\# write out the partial invariance codes for intercepts \textasciitilde{}1}
-\NormalTok{partial\_syntax }\OtherTok{\textless{}{-}} \FunctionTok{paste}\NormalTok{(}\FunctionTok{colnames}\NormalTok{(DF)[}\DecValTok{1}\SpecialCharTok{:}\DecValTok{14}\NormalTok{], }\StringTok{"\textasciitilde{}1"}\NormalTok{) }
-\NormalTok{partial\_syntax}
+\NormalTok{partial.rs }\OtherTok{\textless{}{-}}
+  \FunctionTok{partial\_mi}\NormalTok{(}
+    \AttributeTok{saved\_model =}\NormalTok{ results.rs}\SpecialCharTok{$}\NormalTok{invariance\_models}\SpecialCharTok{$}\NormalTok{model.intercepts,}
+    \AttributeTok{data =}\NormalTok{ DF,}
+    \AttributeTok{model =}\NormalTok{ model.rs,}
+    \AttributeTok{group =} \StringTok{"sample"}\NormalTok{,}
+    \CommentTok{\# be sure to do only up to the step you are interested in}
+    \AttributeTok{group.equal =} \FunctionTok{c}\NormalTok{(}\StringTok{"loadings"}\NormalTok{, }\StringTok{"intercepts"}\NormalTok{),}
+    \AttributeTok{partial\_step =} \StringTok{"intercepts"}\NormalTok{)}
+
+\NormalTok{partial.rs}\SpecialCharTok{$}\NormalTok{fit\_table }\SpecialCharTok{\%\textgreater{}\%} 
+\NormalTok{  dplyr}\SpecialCharTok{::}\FunctionTok{select}\NormalTok{(free.parameter, cfi)}
 \end{Highlighting}
@@
 \begin{verbatim}
-##  [1] "RS1 ~1"  "RS2 ~1"  "RS3 ~1"  "RS4 ~1"  "RS5 ~1"  "RS6 ~1"  "RS7 ~1" 
-##  [8] "RS8 ~1"  "RS9 ~1"  "RS10 ~1" "RS11 ~1" "RS12 ~1" "RS13 ~1" "RS14 ~1"
+## # A tibble: 15 x 2
+##    free.parameter cfi       
+##    <chr>          <lvn.vctr>
+##  1 "RS1 ~1 "      0.9116914 
+##  2 "RS2 ~1 "      0.9129976 
+##  3 "RS3 ~1 "      0.9117235 
+##  4 "RS4 ~1 "      0.9111212 
+##  5 "RS5 ~1 "      0.9126742 
+##  6 "RS6 ~1 "      0.9133618 
+##  7 "RS7 ~1 "      0.9139287 
+##  8 "RS8 ~1 "      0.9111397 
+##  9 "RS9 ~1 "      0.9119702 
+## 10 "RS10 ~1 "     0.9118309 
+## 11 "RS11 ~1 "     0.9110574 
+## 12 "RS12 ~1 "     0.9112309 
+## 13 "RS13 ~1 "     0.9112367 
+## 14 "RS14 ~1 "     0.9112015 
+## 15 "RS ~1 "       0.9108805
 \end{verbatim}
 
-\small
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{\# create a place to save the CFIs for each item separately}
-\NormalTok{CFI\_list  }\OtherTok{\textless{}{-}} \DecValTok{1}\SpecialCharTok{:}\FunctionTok{length}\NormalTok{(partial\_syntax)}
-\FunctionTok{names}\NormalTok{(CFI\_list) }\OtherTok{\textless{}{-}}\NormalTok{ partial\_syntax}
-\CommentTok{\# loop over the items and calculate CFI }
-\CommentTok{\# with that item freely estimated}
-\ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{1}\SpecialCharTok{:}\FunctionTok{length}\NormalTok{(partial\_syntax))\{}
-
-\NormalTok{  temp }\OtherTok{\textless{}{-}} \FunctionTok{cfa}\NormalTok{(}\AttributeTok{model =}\NormalTok{ model.rs, }
-              \AttributeTok{data =}\NormalTok{ DF,}
-              \AttributeTok{meanstructure =} \ConstantTok{TRUE}\NormalTok{,}
-              \AttributeTok{group =} \StringTok{"sample"}\NormalTok{,}
-              \AttributeTok{group.equal =} \FunctionTok{c}\NormalTok{(}\StringTok{"loadings"}\NormalTok{, }\StringTok{"intercepts"}\NormalTok{),}
-              \AttributeTok{group.partial =}\NormalTok{ partial\_syntax[i])}
-
-\NormalTok{  CFI\_list[i] }\OtherTok{\textless{}{-}} \FunctionTok{fitmeasures}\NormalTok{(temp, }\StringTok{"cfi"}\NormalTok{)}
-\NormalTok{\}}
-\CommentTok{\# look at the new CFIs}
-\NormalTok{CFI\_list}
-\end{Highlighting}
-\end{Shaded}
-
-\normalsize
-
-\begin{verbatim}
-##    RS1 ~1    RS2 ~1    RS3 ~1    RS4 ~1    RS5 ~1    RS6 ~1    RS7 ~1    RS8 ~1 
-## 0.9116914 0.9129976 0.9117235 0.9111212 0.9126742 0.9133618 0.9139287 0.9111397 
-##    RS9 ~1   RS10 ~1   RS11 ~1   RS12 ~1   RS13 ~1   RS14 ~1 
-## 0.9119702 0.9118309 0.9110574 0.9112309 0.9112367 0.9112015
-\end{verbatim}
-
-The output indicates that RS6 and RS7 are potential items that could be relaxed to improve model fit and create a partial scalar invariant model.
+The output indicates that RS6 and RS7 are potential items that could be relaxed to improve model fit and create a partial scalar invariant model (i.e., by picking the largest CFI values).
 The code below show to check the addition of these items, which are added one at a time.
 You use the \texttt{group.partial} open to ``relax'' or freely estimate that parameter for each group separately.
-Once that model is saved, you can use the \texttt{tidy} function from \emph{broom} to arrange the estimates from the model, which is used in our plotting function.
-The \texttt{glance} function will create a tidy dataframe of the fit indices for easy review.
 
@@
 \CommentTok{\# run the partially invariant model with group.partial}
-\NormalTok{partial.rs }\OtherTok{\textless{}{-}} \FunctionTok{cfa}\NormalTok{(}\AttributeTok{model =}\NormalTok{ model.rs, }
+\NormalTok{partial.rs}\FloatTok{.1} \OtherTok{\textless{}{-}} \FunctionTok{mgcfa}\NormalTok{(}\AttributeTok{model =}\NormalTok{ model.rs, }
                   \AttributeTok{data =}\NormalTok{ DF, }
-                  \AttributeTok{meanstructure =} \ConstantTok{TRUE}\NormalTok{,}
                   \AttributeTok{group =} \StringTok{"sample"}\NormalTok{, }
-                  \AttributeTok{meanstructure =}\NormalTok{ T, }
                   \AttributeTok{group.equal =} \FunctionTok{c}\NormalTok{(}\StringTok{"loadings"}\NormalTok{, }\StringTok{"intercepts"}\NormalTok{),}
-                  \AttributeTok{group.partial =} \FunctionTok{c}\NormalTok{(}\StringTok{"RS7\textasciitilde{}1"}\NormalTok{))}
+                  \AttributeTok{group.partial =} \FunctionTok{c}\NormalTok{(}\StringTok{"RS7\textasciitilde{}1"}\NormalTok{),}
+                  \AttributeTok{meanstructure =} \ConstantTok{TRUE}\NormalTok{)}
 
 \CommentTok{\# examine the loadings }
-\FunctionTok{tidy}\NormalTok{(partial.rs) }\SpecialCharTok{\%\textgreater{}\%} 
+\NormalTok{partial.rs}\FloatTok{.1}\SpecialCharTok{$}\NormalTok{model\_coef }\SpecialCharTok{\%\textgreater{}\%} 
   \FunctionTok{filter}\NormalTok{(term }\SpecialCharTok{==} \StringTok{"RS7 \textasciitilde{}1 "}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
-  \FunctionTok{select}\NormalTok{(term, group, estimate, std.error)}
+  \FunctionTok{filter}\NormalTok{(model }\SpecialCharTok{==} \StringTok{"intercepts"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
+\NormalTok{  dplyr}\SpecialCharTok{::}\FunctionTok{select}\NormalTok{(term, group, estimate, std.error)}
 \end{Highlighting}
@@
 \CommentTok{\# examine the fit indices }
-\FunctionTok{glance}\NormalTok{(partial.rs) }\SpecialCharTok{\%\textgreater{}\%} 
-  \FunctionTok{select}\NormalTok{(AIC, BIC, cfi, tli, rmsea, srmr)}
+\NormalTok{partial.rs}\FloatTok{.1}\SpecialCharTok{$}\NormalTok{model\_fit }\SpecialCharTok{\%\textgreater{}\%} 
+  \FunctionTok{filter}\NormalTok{(model }\SpecialCharTok{==} \StringTok{"intercepts"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
+\NormalTok{  dplyr}\SpecialCharTok{::}\FunctionTok{select}\NormalTok{(AIC, BIC, cfi, tli, rmsea, srmr)}
 \end{Highlighting}
@@
 \CommentTok{\# effect size model }
-\FunctionTok{lavaan\_dmacs}\NormalTok{(partial.rs, }\StringTok{"Clinical"}\NormalTok{)}\SpecialCharTok{$}\NormalTok{DMACS[}\DecValTok{7}\NormalTok{]}
+\FunctionTok{lavaan\_dmacs}\NormalTok{(partial.rs}\FloatTok{.1}\SpecialCharTok{$}\NormalTok{invariance\_models}\SpecialCharTok{$}\NormalTok{model.intercepts, }\StringTok{"Clinical"}\NormalTok{)}\SpecialCharTok{$}\NormalTok{DMACS[}\DecValTok{7}\NormalTok{]}
 \end{Highlighting}
@@
 Item seven covers perseverance after hardship, and all items can be found in the user manual for the scale at www.resiliencecenter.com.
-The effect size from \(d_{DMACS}\) suggests a small to medium effect, 0.28.
+The effect size from \(d_{MACS}\) suggests a small to medium effect, 0.28.
 In this next code section, we repeat this process for the RS6, as the CFI for our model with only RS7 does not achieve the levels of partial invariance for our \(\Delta\)CFI criterion (i.e., \textless= .01 downward change in fit: metric CFI = .925, partial scalar CFI = .914).
+See Figure \ref{fig:rs7-img} for the difference between item intercepts and latent means.
 
@@
 \CommentTok{\# add the second intercept}
-\NormalTok{partial.rs}\FloatTok{.2} \OtherTok{\textless{}{-}} \FunctionTok{cfa}\NormalTok{(}\AttributeTok{model =}\NormalTok{ model.rs, }
+\NormalTok{partial.rs}\FloatTok{.2} \OtherTok{\textless{}{-}} \FunctionTok{mgcfa}\NormalTok{(}\AttributeTok{model =}\NormalTok{ model.rs, }
                   \AttributeTok{data =}\NormalTok{ DF, }
-                  \AttributeTok{meanstructure =} \ConstantTok{TRUE}\NormalTok{,}
                   \AttributeTok{group =} \StringTok{"sample"}\NormalTok{, }
-                  \AttributeTok{meanstructure =}\NormalTok{ T, }
                   \AttributeTok{group.equal =} \FunctionTok{c}\NormalTok{(}\StringTok{"loadings"}\NormalTok{, }\StringTok{"intercepts"}\NormalTok{),}
-                  \AttributeTok{group.partial =} \FunctionTok{c}\NormalTok{(}\StringTok{"RS7\textasciitilde{}1"}\NormalTok{, }\StringTok{"RS6\textasciitilde{}1"}\NormalTok{))}
+                  \AttributeTok{group.partial =} \FunctionTok{c}\NormalTok{(}\StringTok{"RS7\textasciitilde{}1"}\NormalTok{, }\StringTok{"RS6\textasciitilde{}1"}\NormalTok{),}
+                  \AttributeTok{meanstructure =} \ConstantTok{TRUE}\NormalTok{)}
 
 \CommentTok{\# examine the loadings }
-\FunctionTok{tidy}\NormalTok{(partial.rs}\FloatTok{.2}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
+\NormalTok{partial.rs}\FloatTok{.2}\SpecialCharTok{$}\NormalTok{model\_coef }\SpecialCharTok{\%\textgreater{}\%} 
   \FunctionTok{filter}\NormalTok{(term }\SpecialCharTok{==} \StringTok{"RS6 \textasciitilde{}1 "}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
-  \FunctionTok{select}\NormalTok{(term, group, estimate, std.error)}
+  \FunctionTok{filter}\NormalTok{(model }\SpecialCharTok{==} \StringTok{"intercepts"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
+\NormalTok{  dplyr}\SpecialCharTok{::}\FunctionTok{select}\NormalTok{(term, group, estimate, std.error)}
 \end{Highlighting}
@@
 \CommentTok{\# examine the fit indices }
-\FunctionTok{glance}\NormalTok{(partial.rs}\FloatTok{.2}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
-  \FunctionTok{select}\NormalTok{(AIC, BIC, cfi, tli, rmsea, srmr)}
+\NormalTok{partial.rs}\FloatTok{.2}\SpecialCharTok{$}\NormalTok{model\_fit }\SpecialCharTok{\%\textgreater{}\%} 
+  \FunctionTok{filter}\NormalTok{(model }\SpecialCharTok{==} \StringTok{"intercepts"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
+\NormalTok{  dplyr}\SpecialCharTok{::}\FunctionTok{select}\NormalTok{(AIC, BIC, cfi, tli, rmsea, srmr)}
 \end{Highlighting}
@@
 \begin{Highlighting}[]
-\CommentTok{\# the effect size is }
-\FunctionTok{lavaan\_dmacs}\NormalTok{(partial.rs}\FloatTok{.2}\NormalTok{, }\StringTok{"Clinical"}\NormalTok{)}\SpecialCharTok{$}\NormalTok{DMACS[}\DecValTok{6}\NormalTok{]}
+\CommentTok{\# effect size model }
+\FunctionTok{lavaan\_dmacs}\NormalTok{(partial.rs}\FloatTok{.2}\SpecialCharTok{$}\NormalTok{invariance\_models}\SpecialCharTok{$}\NormalTok{model.intercepts, }\StringTok{"Clinical"}\NormalTok{)}\SpecialCharTok{$}\NormalTok{DMACS[}\DecValTok{6}\NormalTok{]}
 \end{Highlighting}
@@
 The CFI for this model does meet the requirements for partial invariance, .917.
-The effect size is approximately the same at 0.28.
-Last, we can create our images to view the item non-invariance and the latent means in Figures \ref{fig:rs6-img} and \ref{fig:rs7-img}.
-
-\small
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{\# rebuild the model by constraining item 1 intercept}
-\CommentTok{\# allow the latent variable to be estimated}
-\NormalTok{model.rs.picture }\OtherTok{\textless{}{-}} \StringTok{"RS =\textasciitilde{} RS1+RS2+RS3+RS4+RS5+RS6+RS7+RS8+RS9+RS10+RS11+RS12+RS13+RS14}
-\StringTok{RS\textasciitilde{}1}
-\StringTok{RS1\textasciitilde{}0*1"}
-
-\CommentTok{\# rerun the partial invariance model }
-\NormalTok{partial.rs.}\FloatTok{2.}\NormalTok{picture }\OtherTok{\textless{}{-}} \FunctionTok{cfa}\NormalTok{(}\AttributeTok{model =}\NormalTok{ model.rs, }
-                  \AttributeTok{data =}\NormalTok{ DF, }
-                  \AttributeTok{meanstructure =} \ConstantTok{TRUE}\NormalTok{,}
-                  \AttributeTok{group =} \StringTok{"sample"}\NormalTok{, }
-                  \AttributeTok{meanstructure =}\NormalTok{ T, }
-                  \AttributeTok{group.equal =} \FunctionTok{c}\NormalTok{(}\StringTok{"loadings"}\NormalTok{, }\StringTok{"intercepts"}\NormalTok{),}
-                  \AttributeTok{group.partial =} \FunctionTok{c}\NormalTok{(}\StringTok{"RS7\textasciitilde{}1"}\NormalTok{, }\StringTok{"RS6\textasciitilde{}1"}\NormalTok{))}
-
-\CommentTok{\# save the coefficients to use in our picture function }
-\NormalTok{partial.coef }\OtherTok{\textless{}{-}} \FunctionTok{tidy}\NormalTok{(partial.rs.}\FloatTok{2.}\NormalTok{picture) }\SpecialCharTok{\%\textgreater{}\%} 
-  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{model =} \StringTok{"Scalar"}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\normalsize
+The effect size is approximately the same at \(d_{MACS}\) = 0.28.
+See Figure \ref{fig:rs6-img} shows the difference between item intercepts and latent means.
+
+\normalsize
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\# plot the image for RS7}
+\FunctionTok{plot\_mi}\NormalTok{(}
+  \AttributeTok{data\_coef =}\NormalTok{ partial.rs}\FloatTok{.2}\SpecialCharTok{$}\NormalTok{model\_coef, }
+  \AttributeTok{model\_step =} \StringTok{"intercepts"}\NormalTok{, }
+  \AttributeTok{item\_name =} \StringTok{"RS7"}\NormalTok{, }
+  \AttributeTok{x\_limits =} \FunctionTok{c}\NormalTok{(}\SpecialCharTok{{-}}\DecValTok{1}\NormalTok{,}\DecValTok{1}\NormalTok{),}
+  \AttributeTok{y\_limits =} \FunctionTok{c}\NormalTok{(}\FunctionTok{min}\NormalTok{(DF}\SpecialCharTok{$}\NormalTok{RS7), }\FunctionTok{max}\NormalTok{(DF}\SpecialCharTok{$}\NormalTok{RS7)),}
+  \AttributeTok{conf.level =}\NormalTok{ .}\DecValTok{95}\NormalTok{, }
+  \AttributeTok{model\_results =}\NormalTok{ partial.rs}\FloatTok{.2}\SpecialCharTok{$}\NormalTok{invariance\_models}\SpecialCharTok{$}\NormalTok{model.intercepts,}
+  \CommentTok{\# which latent variable do you want }
+  \AttributeTok{lv\_name =} \StringTok{"RS"} 
+\NormalTok{)}\SpecialCharTok{$}\NormalTok{complete}
+\end{Highlighting}
+\end{Shaded}
+
+\normalsize
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/rs7-img-1.pdf}
+\caption{\label{fig:rs7-img}RS7 Item Invariance Visualization}
+\end{figure}
 
@@
 \CommentTok{\# plot the image for RS6}
-\FunctionTok{plot\_mgcfa}\NormalTok{(}
-  \AttributeTok{data\_coef =}\NormalTok{ partial.coef,}
-  \AttributeTok{model\_step =} \StringTok{"Scalar"}\NormalTok{, }
-  \AttributeTok{item\_name =} \StringTok{"RS6"}\NormalTok{,}
-  \AttributeTok{x\_limits =} \FunctionTok{c}\NormalTok{(}\SpecialCharTok{{-}}\DecValTok{2}\NormalTok{,}\DecValTok{2}\NormalTok{),}
-  \AttributeTok{y\_limits =} \FunctionTok{c}\NormalTok{(}\FunctionTok{min}\NormalTok{(DF}\SpecialCharTok{$}\NormalTok{RS7), }\FunctionTok{max}\NormalTok{(DF}\SpecialCharTok{$}\NormalTok{RS7)),}
-  \AttributeTok{model\_results =}\NormalTok{ partial.rs.}\FloatTok{2.}\NormalTok{picture, }
-  \AttributeTok{ci\_level =}\NormalTok{ .}\DecValTok{95}\NormalTok{,}
+\FunctionTok{plot\_mi}\NormalTok{(}
+  \AttributeTok{data\_coef =}\NormalTok{ partial.rs}\FloatTok{.2}\SpecialCharTok{$}\NormalTok{model\_coef, }
+  \AttributeTok{model\_step =} \StringTok{"intercepts"}\NormalTok{, }
+  \AttributeTok{item\_name =} \StringTok{"RS6"}\NormalTok{, }
+  \AttributeTok{x\_limits =} \FunctionTok{c}\NormalTok{(}\SpecialCharTok{{-}}\DecValTok{1}\NormalTok{,}\DecValTok{1}\NormalTok{),}
+  \AttributeTok{y\_limits =} \FunctionTok{c}\NormalTok{(}\FunctionTok{min}\NormalTok{(DF}\SpecialCharTok{$}\NormalTok{RS6), }\FunctionTok{max}\NormalTok{(DF}\SpecialCharTok{$}\NormalTok{RS6)),}
+  \AttributeTok{conf.level =}\NormalTok{ .}\DecValTok{95}\NormalTok{, }
+  \AttributeTok{model\_results =}\NormalTok{ partial.rs}\FloatTok{.2}\SpecialCharTok{$}\NormalTok{invariance\_models}\SpecialCharTok{$}\NormalTok{model.intercepts,}
+  \CommentTok{\# which latent variable do you want }
   \AttributeTok{lv\_name =} \StringTok{"RS"} 
-\NormalTok{)}
+\NormalTok{)}\SpecialCharTok{$}\NormalTok{complete}
 \end{Highlighting}
@@
 
-\normalsize
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{\# plot the image for RS7}
-\FunctionTok{plot\_mgcfa}\NormalTok{(}
-  \AttributeTok{data\_coef =}\NormalTok{ partial.coef,}
-  \AttributeTok{model\_step =} \StringTok{"Scalar"}\NormalTok{, }
-  \AttributeTok{item\_name =} \StringTok{"RS7"}\NormalTok{,}
-  \AttributeTok{x\_limits =} \FunctionTok{c}\NormalTok{(}\SpecialCharTok{{-}}\DecValTok{2}\NormalTok{,}\DecValTok{2}\NormalTok{),}
-  \AttributeTok{y\_limits =} \FunctionTok{c}\NormalTok{(}\FunctionTok{min}\NormalTok{(DF}\SpecialCharTok{$}\NormalTok{RS7), }\FunctionTok{max}\NormalTok{(DF}\SpecialCharTok{$}\NormalTok{RS7)),}
-  \AttributeTok{model\_results =}\NormalTok{ partial.rs.}\FloatTok{2.}\NormalTok{picture, }
-  \AttributeTok{ci\_level =}\NormalTok{ .}\DecValTok{95}\NormalTok{,}
-  \AttributeTok{lv\_name =} \StringTok{"RS"}
+Next, we would examine our replication potential for this model.
+Given our current results, we may not expect our intercepts to replicate.
+Given the order of \texttt{group.equal}, the boot function will select the first non-invariant step in the calculation of the effect size for potential replication.
+In our output, we do not see a loadings effect size, and this result occurs when \emph{none} of the bootstrapped or random results are non-invariant.
+Therefore, we would expect the loadings to replicate (and the effect size would be 0 difference between bootstrapped and random, both showing invariance).
+The intercepts show a large (i.e., close to the max possible value) non-invariant effect, and therefore, we should not expect this model to show invariance in a replication.
+
+\normalsize
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{boot.model.rs }\OtherTok{\textless{}{-}} 
+  \FunctionTok{bootstrap\_rr}\NormalTok{(}
+    \AttributeTok{saved\_configural =}\NormalTok{ results.rs}\SpecialCharTok{$}\NormalTok{model\_configural,}
+    \AttributeTok{data =}\NormalTok{ DF,}
+    \AttributeTok{model =}\NormalTok{ model.rs, }
+    \AttributeTok{group =} \StringTok{"sample"}\NormalTok{, }
+    \AttributeTok{nboot =} \DecValTok{1000}\NormalTok{, }
+    \AttributeTok{invariance\_index =} \StringTok{"cfi"}\NormalTok{,}
+    \AttributeTok{invariance\_rule =}\NormalTok{ .}\DecValTok{01}\NormalTok{, }
+    \AttributeTok{group.equal =} \FunctionTok{c}\NormalTok{(}\StringTok{"loadings"}\NormalTok{, }\StringTok{"intercepts"}\NormalTok{, }\StringTok{"residuals"}\NormalTok{)}
 \NormalTok{)}
@@
 \normalsize
+
+\normalsize
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{boot.model.rs}
+\end{Highlighting}
+\end{Shaded}
+
+\normalsize
+
+\begin{verbatim}
+## # A tibble: 2 x 7
+##   model      non_invariant random_non_invariant  h_nmi    h_mi h_nmi_p  h_mi_p
+##   <chr>              <dbl>                <dbl>  <dbl>   <dbl>   <dbl>   <dbl>
+## 1 intercepts         0.998                    0 3.05   -3.05    0.972  -0.972 
+## 2 residuals          0.002                    0 0.0895 -0.0895  0.0285 -0.0285
+\end{verbatim}
+
+Next, we would examine the strength of the effects of replication on each parameter at the intercept level.
+By examining \ref{tab:table-boot-effects}, it is clear that most of the item means are unlikely to replicate, even though two particular items can be used to create partial invariance.
+Figures \ref{fig:rs-partial-pic} and \ref{fig:rs-partial-pic2} display the three plots provided in the \texttt{bootstrap\_partial()} function.
+In general, we should expect \(M_{D}\) = 0.23 when items are invariant and \(M_{D}\) = 0.26 when items are not invariant.
+The effect size of non-invariant items ranges from 0.43 to 0.62.
+
+The density plot shown at the bottom of Figure \ref{fig:rs-partial-pic} illustrates the likely reasons for the differences found in the top plots.
+It appears that many items show a bimodal distribution within group 1 (Clinical Sample) and when items are invariant, the intercept averages to the same intercept as group 2 (Student Sample).
+In non-invariant estimates, the same bimodal distributions are found, but they are more extreme than the student samples, and therefore, item show different averages due to the presence of two separate means of data.
+Further, some items also appear to show two separate student item averages within the data.
+This result suggests that it would be fruitful to understand a potential predictor of these differences or other confounding variable that separates these samples, creating differences in item averages.
+
+In summary, if one were planning a replication, the prediction would be that item intercepts would likely not replicate, with a large effect size (i.e., it is easy to judge \(h_{nmi_p}\) close to the max of one as large).
+While this study found partial invariance by relaxing constraints on two individual items, bootstrapped partial invariance indicates that any item could potentially be problematic with an effect size averaging \(d\) \textasciitilde{} 0.50 difference in means.
+While \(d_{MACS}\) values represented a ``small'' effect based on previous publications, this effect may be muted by examining both loadings and intercepts.
+The results here suggest that the effect is driven by intercepts.
+The overall average score on items is high: \(M_M\) = 5.04 (\(M_{SD}\) = 1.72).
+Given the mean standard deviation, a \(d\) \textasciitilde{} 0.50 represents 0.86 or nearly one whole point on the scale.
+A researcher could decide that at least \(d\) = 0.33 or at least a third of a standard deviation would be an important change and set that as their smallest effect size of interest for invariance.
+Further, a newly planned study should investigate what variables may predict when and why samples separate into bimodal representations for item means.
+
+\normalsize
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{boot.partial.rs }\OtherTok{\textless{}{-}} 
+  \FunctionTok{bootstrap\_partial}\NormalTok{(}
+    \AttributeTok{saved\_model =}\NormalTok{ results.rs}\SpecialCharTok{$}\NormalTok{invariance\_models}\SpecialCharTok{$}\NormalTok{model.intercepts,}
+    \AttributeTok{data =}\NormalTok{ DF,}
+    \AttributeTok{model =}\NormalTok{ model.rs, }
+    \AttributeTok{group =} \StringTok{"sample"}\NormalTok{, }
+    \AttributeTok{nboot =} \DecValTok{1000}\NormalTok{, }
+    \AttributeTok{invariance\_index =} \StringTok{"cfi"}\NormalTok{,}
+    \AttributeTok{invariance\_rule =}\NormalTok{ .}\DecValTok{01}\NormalTok{, }
+    \AttributeTok{invariance\_compare =} \FunctionTok{fitmeasures}\NormalTok{(results.rs}\SpecialCharTok{$}\NormalTok{invariance\_models}\SpecialCharTok{$}\NormalTok{model.loadings, }\StringTok{"cfi"}\NormalTok{), }
+    \AttributeTok{partial\_step =} \StringTok{"intercepts"}\NormalTok{,}
+    \AttributeTok{group.equal =} \FunctionTok{c}\NormalTok{(}\StringTok{"loadings"}\NormalTok{, }\StringTok{"intercepts"}\NormalTok{)}
+\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\normalsize
+
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:table-boot-effects}Boot Partial Effects Results for RS-14 Intercepts}
+
+\begin{tabular}{lllllll}
+\toprule
+term & \multicolumn{1}{c}{non\_invariant} & \multicolumn{1}{c}{random\_non\_invariant} & \multicolumn{1}{c}{h\_nmi} & \multicolumn{1}{c}{h\_mi} & \multicolumn{1}{c}{h\_nmi\_p} & \multicolumn{1}{c}{h\_mi\_p}\\
+\midrule
+RS \textasciitilde{}1 & 0.991 & 0.007 & 2.784 & -2.784 & 0.886 & -0.886\\
+RS1 \textasciitilde{}1 & 0.989 & 0.007 & 2.764 & -2.764 & 0.880 & -0.880\\
+RS10 \textasciitilde{}1 & 0.988 & 0.007 & 2.755 & -2.755 & 0.877 & -0.877\\
+RS11 \textasciitilde{}1 & 0.991 & 0.007 & 2.784 & -2.784 & 0.886 & -0.886\\
+RS12 \textasciitilde{}1 & 0.991 & 0.007 & 2.784 & -2.784 & 0.886 & -0.886\\
+RS13 \textasciitilde{}1 & 0.991 & 0.007 & 2.784 & -2.784 & 0.886 & -0.886\\
+RS14 \textasciitilde{}1 & 0.990 & 0.007 & 2.774 & -2.774 & 0.883 & -0.883\\
+RS2 \textasciitilde{}1 & 0.985 & 0.007 & 2.728 & -2.728 & 0.869 & -0.869\\
+RS3 \textasciitilde{}1 & 0.988 & 0.007 & 2.755 & -2.755 & 0.877 & -0.877\\
+RS4 \textasciitilde{}1 & 0.990 & 0.007 & 2.774 & -2.774 & 0.883 & -0.883\\
+RS5 \textasciitilde{}1 & 0.984 & 0.007 & 2.720 & -2.720 & 0.866 & -0.866\\
+RS6 \textasciitilde{}1 & 0.979 & 0.007 & 2.683 & -2.683 & 0.854 & -0.854\\
+RS7 \textasciitilde{}1 & 0.974 & 0.007 & 2.650 & -2.650 & 0.844 & -0.844\\
+RS8 \textasciitilde{}1 & 0.991 & 0.007 & 2.784 & -2.784 & 0.886 & -0.886\\
+RS9 \textasciitilde{}1 & 0.987 & 0.007 & 2.746 & -2.746 & 0.874 & -0.874\\
+\bottomrule
+\end{tabular}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
 
@@
 \centering
-\includegraphics{manuscript_files/figure-latex/rs7-img-1.pdf}
-\caption{\label{fig:rs7-img}RS7 Item Invariance Visualization}
+\includegraphics{manuscript_files/figure-latex/rs-partial-pic-1.pdf}
+\caption{\label{fig:rs-partial-pic}RS14 scale invariance for item intercepts.
+The left panel indicates the raw score difference between groups and items, while the right panel indicates the effect size for group differences based on invariance.}
 \end{figure}
 
-The latent mean is calculated ``separately'' for each group, insomuch as the first group is considered the comparison group, while the second is the difference between groups, like how dummy coded variables in regression are examined.
-Here we see a difference of 0.72, and students show a higher resiliency score.
-However, when all other things are held equivalent, the intercepts on items 6 and 7 show higher scores for clinical populations.
-Additionally, we may see an indication in our student population of a bimodal distribution that may be related to this effect.
+\begin{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/rs-partial-pic2-1.pdf}
+\caption{\label{fig:rs-partial-pic2}RS14 scale invariance density plots, illustrating invariant versus non-invariant bootstrapped and random runs for each parameter.}
+\end{figure}
 
@@
 
-In this tutorial, we examined how to use multiple tools to examine measurement invariance.
-Model fit comparisons and statistics can be paired with newly developed effect size measures, and finally a visualization to examine individual items and the overall latent mean scores.
-This visualization was designed with common graphing elements that researchers often use to display those statistics - intercepts were graphed on the intercept line, slopes were represented as lines of fit, and error terms were represented as distributions.
-Each component can impact the overall model and the eventual latent mean scores, as shown in the simulations holding all other things equal.
+In this tutorial, we examined how to use multiple tools to examine measurement invariance and its potential replication.
+Model fit comparisons and statistics can be paired with the proposed effect size measures, and a visualization to examine individual items and the overall latent mean scores.
+The impact of potential replication was estimated on the overall model and the individual parameters.
 Using real data, the effect of two non-invariant item intercepts was examined and visualized.
-How should one interpret the ``discrepancy'' between the results (these effect visually appear large) from effect sizes (.30 was proposed as small to medium in Nye et al.
-(2019))?
-
-Effect sizes are notoriously difficult to interpret, which is why we love guidelines, even if Cohen (1990) declared we probably shouldn't use his suggestions.
+This tutorial manuscript has provided a concrete way to plan for pre-registration and/or registered reports.
+Researchers could simulate results based on published or previously collected data to determine the likelihood and size of potential replication.
+They could plan and pre-register a smallest effect of interest.
+For example, we may determine that an \(h_{nmi_p}\) value above .20 represents an important level of non-invariance for our model overall, while \(h_{nmi_p}\) \textgreater{} .30 for any individual parameter warrant caution against invariance for groups.
 Others have begun to discuss the importance of focusing on effects in the scale of the data and their practical importance (Anvari \& Lakens, 2021; Cumming, 2012).
-Our interpretation may be that the difference between groups is large, as a 0.72 change on a 7 point scale is approximately 10\% more resiliency for students when compared to the clinical sample.
+
+From the example, our interpretation may be that the difference between group's latent means is large, as a 0.72 change on a 7 point scale is approximately 10\% more resiliency for students when compared to the clinical sample.
 Practically, 10\% in resiliency for an area of the United States (Mississippi) often hit with natural disasters (hurricanes, tornadoes, floods) and high levels of poverty would be very important.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-byrne2001}{}}%
-Byrne, B.
-M.
-(2001).
-Structural Equation Modeling With AMOS, EQS, and LISREL: Comparative Approaches to Testing for the Factorial Validity of a Measuring Instrument.
-\emph{International Journal of Testing}, \emph{1}(1), 55--86.
-\url{https://doi.org/10.1207/S15327574IJT0101_4}
-
 \leavevmode\vadjust pre{\hypertarget{ref-byrne1989}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-cohen1990}{}}%
-Cohen, J. (1990). Things I have learned (so far). \emph{American Psychologist}, \emph{45}(12), 1304--1312. \url{https://doi.org/10.1037/0003-066X.45.12.1304}
-
 \leavevmode\vadjust pre{\hypertarget{ref-cohen2003}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-epskamp2022}{}}%
+Epskamp, S. (2022). \emph{semPlot: Path diagrams and visual analysis of various SEM packages' output}. \url{https://CRAN.R-project.org/package=semPlot}
+
 \leavevmode\vadjust pre{\hypertarget{ref-flake2020}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-hobson2019}{}}%
+Hobson, H. (2019). Registered reports are an ally to early career researchers. \emph{Nature Human Behaviour}, \emph{3}(10), 1010--1010. \url{https://doi.org/10.1038/s41562-019-0701-8}
+
 \leavevmode\vadjust pre{\hypertarget{ref-jin2020}{}}%
@@
 Jöreskog, K. G., \& Sörbom, D. (2001). \emph{LISREL 8: user's reference guide} (2. ed., updated to LISREL 8). SSI Scientific Software Internat.
-
-\leavevmode\vadjust pre{\hypertarget{ref-kline2016}{}}%
-Kline, R. B. (2016). \emph{Principles and practice of structural equation modeling} (Fourth edition). The Guilford Press.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-meade2008}{}}%
-Meade, A.
-W., Johnson, E.
-C., \& Braddy, P.
-W.
-(2008).
-Power and sensitivity of alternative fit indices in tests of measurement invariance.
-\emph{Journal of Applied Psychology}, \emph{93}(3), 568--592.
-\url{https://doi.org/10.1037/0021-9010.93.3.568}
+\leavevmode\vadjust pre{\hypertarget{ref-mayo-wilson2021}{}}%
+Mayo-Wilson, E., Grant, S., Supplee, L., Kianersi, S., Amin, A., DeHaven, A., \& Mellor, D.
+(2021).
+Evaluating implementation of the transparency and openness promotion~(TOP) guidelines:~The TRUST process for rating journal policies, procedures, and practices.
+\emph{Research Integrity and Peer Review}, \emph{6}(1), 9.
+\url{https://doi.org/10.1186/s41073-021-00112-8}
 
@@
 Nelson, L. D., Simmons, J., \& Simonsohn, U. (2018). Psychology's renaissance. \emph{Annual Review of Psychology}, \emph{69}(1), 511--534. \url{https://doi.org/10.1146/annurev-psych-122216-011836}
+
+\leavevmode\vadjust pre{\hypertarget{ref-nosek2018}{}}%
+Nosek, B.
+A., Ebersole, C.
+R., DeHaven, A.
+C., \& Mellor, D.
+T.
+(2018).
+The preregistration revolution.
+\emph{Proceedings of the National Academy of Sciences of the United States of America}, \emph{115}(11), 2600--2606.
+\url{https://doi.org/10.1073/pnas.1708274114}
+
+\leavevmode\vadjust pre{\hypertarget{ref-nosek2014}{}}%
+Nosek, B.
+A., \& Lakens, D.
+(2014).
+Registered Reports: A Method to Increase the Credibility of Published Results.
+\emph{Social Psychology}, \emph{45}(3), 137--141.
+\url{https://doi.org/10.1027/1864-9335/a000192}
 
@@
 \url{https://doi.org/10.1207/s15327906mbr2502_4}
-
-\leavevmode\vadjust pre{\hypertarget{ref-tay2015}{}}%
-Tay, L., Meade, A.
-W., \& Cao, M.
-(2015).
-An Overview and Practical Guide to IRT Measurement Equivalence Analysis.
-\emph{Organizational Research Methods}, \emph{18}(1), 3--46.
-\url{https://doi.org/10.1177/1094428114553062}
-
-\leavevmode\vadjust pre{\hypertarget{ref-thompson1996}{}}%
-Thompson, B., \& Daniel, L.
-G.
-(1996).
-Factor Analytic Evidence for the Construct Validity of Scores: A Historical Overview and Some Guidelines.
-\emph{Educational and Psychological Measurement}, \emph{56}(2), 197--208.
-\url{https://doi.org/10.1177/0013164496056002001}
 
@@
 
-\hypertarget{appendix}{%
-\section{Appendix}\label{appendix}}
-
-\hypertarget{mgcfa-convenience-function}{%
-\subsection{MGCFA Convenience Function}\label{mgcfa-convenience-function}}
-
-Please note that any partial invariance is not automatically included in this function.
-This function returns a list with all model summaries, the model coefficients in a tidy dataframe, and the model fit statistics in a tidy dataframe.
-You will need the libraries listed below for this function to work properly.
+\hypertarget{appendix-appendix}{%
+\appendix}
+
+\hypertarget{simulating-from-models}{%
+\subsection{Simulating from models}\label{simulating-from-models}}
+
+Here's an example of how to simulate directly from a \texttt{lavaan} model:
 
@@
 \begin{Highlighting}[]
-\FunctionTok{library}\NormalTok{(lavaan)}
-\FunctionTok{library}\NormalTok{(dplyr)}
-\FunctionTok{library}\NormalTok{(broom)}
-\CommentTok{\# CFA function}
-\NormalTok{mgcfa }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(data, group, model)\{}
-
-\NormalTok{  group\_names }\OtherTok{\textless{}{-}} \FunctionTok{unique}\NormalTok{(data[ , group])}
-\NormalTok{  data}\SpecialCharTok{$}\NormalTok{group }\OtherTok{\textless{}{-}}\NormalTok{ data[ , group]}
-
-\NormalTok{  model.overall }\OtherTok{\textless{}{-}} \FunctionTok{cfa}\NormalTok{(}\AttributeTok{model =}\NormalTok{ model, }\AttributeTok{data =}\NormalTok{ data, }
-                       \AttributeTok{meanstructure =}\NormalTok{ T)}
-\NormalTok{  model.group1 }\OtherTok{\textless{}{-}} \FunctionTok{cfa}\NormalTok{(}\AttributeTok{model =}\NormalTok{ model, }
-                      \AttributeTok{data =} \FunctionTok{subset}\NormalTok{(data, group }\SpecialCharTok{==}\NormalTok{ group\_names[}\DecValTok{1}\NormalTok{]),}
-                      \AttributeTok{meanstructure =}\NormalTok{ T)}
-\NormalTok{  model.group2 }\OtherTok{\textless{}{-}} \FunctionTok{cfa}\NormalTok{(}\AttributeTok{model =}\NormalTok{ model, }
-                      \AttributeTok{data =} \FunctionTok{subset}\NormalTok{(data, group }\SpecialCharTok{==}\NormalTok{ group\_names[}\DecValTok{2}\NormalTok{]),}
-                      \AttributeTok{meanstructure =}\NormalTok{ T)}
-\NormalTok{  model.configural }\OtherTok{\textless{}{-}} \FunctionTok{cfa}\NormalTok{(}\AttributeTok{model =}\NormalTok{ model, }\AttributeTok{data =}\NormalTok{ data, }
-                          \AttributeTok{group =}\NormalTok{ group, }\AttributeTok{meanstructure =}\NormalTok{ T)}
-\NormalTok{  model.metric }\OtherTok{\textless{}{-}} \FunctionTok{cfa}\NormalTok{(}\AttributeTok{model =}\NormalTok{ model, }\AttributeTok{data =}\NormalTok{ data, }
-                      \AttributeTok{group =}\NormalTok{ group, }\AttributeTok{meanstructure =}\NormalTok{ T,}
-                      \AttributeTok{group.equal =} \StringTok{"loadings"}\NormalTok{)}
-\NormalTok{  model.scalar }\OtherTok{\textless{}{-}} \FunctionTok{cfa}\NormalTok{(}\AttributeTok{model =}\NormalTok{ model, }\AttributeTok{data =}\NormalTok{ data, }
-                      \AttributeTok{group =}\NormalTok{ group, }\AttributeTok{meanstructure =}\NormalTok{ T, }
-                      \AttributeTok{group.equal =} \FunctionTok{c}\NormalTok{(}\StringTok{"loadings"}\NormalTok{, }\StringTok{"intercepts"}\NormalTok{))}
-\NormalTok{  model.strict }\OtherTok{\textless{}{-}} \FunctionTok{cfa}\NormalTok{(}\AttributeTok{model =}\NormalTok{ model, }\AttributeTok{data =}\NormalTok{ data, }
-                      \AttributeTok{group =}\NormalTok{ group, }\AttributeTok{meanstructure =}\NormalTok{ T, }
-                      \AttributeTok{group.equal =}  \FunctionTok{c}\NormalTok{(}\StringTok{"loadings"}\NormalTok{, }\StringTok{"intercepts"}\NormalTok{, }\StringTok{"residuals"}\NormalTok{))}
-
-\NormalTok{  model\_coef }\OtherTok{\textless{}{-}} \FunctionTok{bind\_rows}\NormalTok{(}
-    \FunctionTok{tidy}\NormalTok{(model.overall, }\AttributeTok{conf.level =}\NormalTok{ .}\DecValTok{95}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
-      \FunctionTok{mutate}\NormalTok{(}\AttributeTok{model =} \StringTok{"Overall"}\NormalTok{), }
-    \FunctionTok{tidy}\NormalTok{(model.group1, }\AttributeTok{conf.level =}\NormalTok{ .}\DecValTok{95}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
-      \FunctionTok{mutate}\NormalTok{(}\AttributeTok{model =} \StringTok{"Group 1"}\NormalTok{), }
-    \FunctionTok{tidy}\NormalTok{(model.group2, }\AttributeTok{conf.level =}\NormalTok{ .}\DecValTok{95}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
-      \FunctionTok{mutate}\NormalTok{(}\AttributeTok{model =} \StringTok{"Group 2"}\NormalTok{), }
-    \FunctionTok{tidy}\NormalTok{(model.configural, }\AttributeTok{conf.level =}\NormalTok{ .}\DecValTok{95}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
-      \FunctionTok{mutate}\NormalTok{(}\AttributeTok{model =} \StringTok{"Configural"}\NormalTok{), }
-    \FunctionTok{tidy}\NormalTok{(model.metric, }\AttributeTok{conf.level =}\NormalTok{ .}\DecValTok{95}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
-      \FunctionTok{mutate}\NormalTok{(}\AttributeTok{model =} \StringTok{"Metric"}\NormalTok{), }
-    \FunctionTok{tidy}\NormalTok{(model.scalar, }\AttributeTok{conf.level =}\NormalTok{ .}\DecValTok{95}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
-      \FunctionTok{mutate}\NormalTok{(}\AttributeTok{model =} \StringTok{"Scalar"}\NormalTok{), }
-    \FunctionTok{tidy}\NormalTok{(model.strict, }\AttributeTok{conf.level =}\NormalTok{ .}\DecValTok{95}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
-      \FunctionTok{mutate}\NormalTok{(}\AttributeTok{model =} \StringTok{"Strict"}\NormalTok{)}
-\NormalTok{  )}
-
-\NormalTok{  model\_fit }\OtherTok{\textless{}{-}} \FunctionTok{bind\_rows}\NormalTok{(}
-    \FunctionTok{glance}\NormalTok{(model.overall) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{mutate}\NormalTok{(}\AttributeTok{model =} \StringTok{"Overall"}\NormalTok{), }
-    \FunctionTok{glance}\NormalTok{(model.group1) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{mutate}\NormalTok{(}\AttributeTok{model =} \StringTok{"Group 1"}\NormalTok{), }
-    \FunctionTok{glance}\NormalTok{(model.group2) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{mutate}\NormalTok{(}\AttributeTok{model =} \StringTok{"Group 2"}\NormalTok{), }
-    \FunctionTok{glance}\NormalTok{(model.configural) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{mutate}\NormalTok{(}\AttributeTok{model =} \StringTok{"Configural"}\NormalTok{), }
-    \FunctionTok{glance}\NormalTok{(model.metric) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{mutate}\NormalTok{(}\AttributeTok{model =} \StringTok{"Metric"}\NormalTok{), }
-    \FunctionTok{glance}\NormalTok{(model.scalar) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{mutate}\NormalTok{(}\AttributeTok{model =} \StringTok{"Scalar"}\NormalTok{), }
-    \FunctionTok{glance}\NormalTok{(model.strict) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{mutate}\NormalTok{(}\AttributeTok{model =} \StringTok{"Strict"}\NormalTok{)}
-\NormalTok{    )}
-
-  \FunctionTok{return}\NormalTok{(}\FunctionTok{list}\NormalTok{(}
-    \StringTok{"model\_coef"} \OtherTok{=}\NormalTok{ model\_coef,}
-    \StringTok{"model\_fit"} \OtherTok{=}\NormalTok{ model\_fit,}
-    \StringTok{"model.overall"} \OtherTok{=}\NormalTok{ model.overall,}
-    \StringTok{"model.group1"} \OtherTok{=}\NormalTok{ model.group1,}
-    \StringTok{"model.group2"} \OtherTok{=}\NormalTok{ model.group2,}
-    \StringTok{"model.configural"} \OtherTok{=}\NormalTok{ model.configural,}
-    \StringTok{"model.metric"} \OtherTok{=}\NormalTok{ model.metric,}
-    \StringTok{"model.scalar"} \OtherTok{=}\NormalTok{ model.scalar,}
-    \StringTok{"model.strict"} \OtherTok{=}\NormalTok{ model.strict}
-\NormalTok{  ))}
-
-\NormalTok{\}}
-\end{Highlighting}
-\end{Shaded}
-
-\normalsize
-
-\hypertarget{measurement-invariance-plot-function}{%
-\subsection{Measurement Invariance Plot Function}\label{measurement-invariance-plot-function}}
-
-This function creates the plots shown in the manuscript.
-You will need the libraries listed for this function to work.
-Plots may be modified to rearrange for those who are familiar with \texttt{ggplot2}.
-Please note that the function assumes you will use the outputs from the previous \texttt{mgcfa} function or a tidy dataframe that includes the coefficients from the model with a column \texttt{model} that indicates which step of the MGCFA you are wanting to plot.
-If you have more than two groups, you should first filter the dataframe model coefficient outputs to only include to the two groups you want to compare.
-This code does not plot more than two groups (although, it could be modified for this, but the assumption here is that you only have two, as this is how you would normally proceed in a MGCFA using pairwise comparisons to find where the invariance occurs).
+\CommentTok{\# first build your model}
+\CommentTok{\# this example is separate for each group}
+\NormalTok{model.invariant.g1 }\OtherTok{\textless{}{-}} \StringTok{"}
+\StringTok{\# loadings}
+\StringTok{lv =\textasciitilde{} .8*q1 + .4*q2 + .6*q3 + .3*q4 + .6*q5 }
+\StringTok{\# set the residual for invariance on q4}
+\StringTok{q4 \textasciitilde{}\textasciitilde{} 1*q4}
+\StringTok{\# set the intercept for invariance on q4}
+\StringTok{q4 \textasciitilde{} 0*1}
+\StringTok{\# set the intercept to zero for df purposes}
+\StringTok{q1 \textasciitilde{} 0*1}
+\StringTok{\# allow the latent mean to be estimated }
+\StringTok{lv \textasciitilde{} 1"}
+\NormalTok{model.invariant.g2 }\OtherTok{\textless{}{-}} \StringTok{"lv =\textasciitilde{} .77*q1 + .43*q2 + .58*q3 + .3*q4 + .61*q5}
+\StringTok{q4 \textasciitilde{}\textasciitilde{} 1*q4}
+\StringTok{q4 \textasciitilde{} 0*1}
+\StringTok{q1 \textasciitilde{} 0*1}
+\StringTok{lv \textasciitilde{} 1"}
+
+\CommentTok{\# simulate data invariant separately for each group}
+\NormalTok{df.invariant }\OtherTok{\textless{}{-}} \FunctionTok{bind\_rows}\NormalTok{(}
+  \CommentTok{\# lavaan function }
+  \FunctionTok{simulateData}\NormalTok{(}
+    \CommentTok{\# model with estimates }
+    \AttributeTok{model =}\NormalTok{ model.invariant.g1, }
+    \CommentTok{\# how many data points}
+    \AttributeTok{sample.nobs =} \DecValTok{250}\NormalTok{, }
+    \CommentTok{\# mean structure for mgcfa models }
+    \AttributeTok{meanstructure =}\NormalTok{ T, }
+    \CommentTok{\# model type}
+    \AttributeTok{model.type =} \StringTok{"cfa"}\NormalTok{,}
+    \CommentTok{\# set seed for reproducibility }
+    \AttributeTok{seed =} \DecValTok{1234}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
+    \CommentTok{\# add a group label to the data }
+    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{group =} \StringTok{"Group 1"}\NormalTok{), }
+  \FunctionTok{simulateData}\NormalTok{(}
+    \AttributeTok{model =}\NormalTok{ model.invariant.g2, }
+    \AttributeTok{sample.nobs =} \DecValTok{250}\NormalTok{, }
+    \AttributeTok{meanstructure =}\NormalTok{ T, }
+    \AttributeTok{model.type =} \StringTok{"cfa"}\NormalTok{,}
+    \AttributeTok{seed =} \DecValTok{1234}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
+    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{group =} \StringTok{"Group 2"}\NormalTok{) }
+\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\normalsize
+
+\newpage
+
+\hypertarget{simulating-from-matrices}{%
+\subsection{Simulating from matrices}\label{simulating-from-matrices}}
+
+Here's an example of how to simulate using \texttt{MASS} and covariance or correlation matrices.
 
@@
 \begin{Highlighting}[]
-\FunctionTok{library}\NormalTok{(dplyr)}
-\FunctionTok{library}\NormalTok{(ggplot2)}
-\FunctionTok{library}\NormalTok{(cowplot)}
-\FunctionTok{library}\NormalTok{(lavaan)}
-\CommentTok{\# devtools::install\_github("psyteachr/introdataviz")}
-\FunctionTok{library}\NormalTok{(introdataviz)}
-\CommentTok{\# Plot MI MGCFA}
-\NormalTok{plot\_mgcfa }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(data\_coef, }\CommentTok{\# output from model\_coef}
-\NormalTok{                       model\_step, }\CommentTok{\# which model}
-\NormalTok{                       item\_name, }\CommentTok{\# name of observed item}
-                       \AttributeTok{x\_limits =} \FunctionTok{c}\NormalTok{(}\SpecialCharTok{{-}}\DecValTok{1}\NormalTok{,}\DecValTok{1}\NormalTok{), }\CommentTok{\# LV limits to graph}
-\NormalTok{                       y\_limits, }\CommentTok{\# Y min and max in data }
-\NormalTok{                       ci\_level, }\CommentTok{\# what ci do you want}
-\NormalTok{                       model\_results, }\CommentTok{\# what model results do you want }
-\NormalTok{                       lv\_name }\CommentTok{\# which latent is the observed variable on}
-\NormalTok{                       )\{}
-
-  \CommentTok{\# calculate cutoff}
-\NormalTok{  cutoff }\OtherTok{\textless{}{-}} \FunctionTok{qt}\NormalTok{(}\AttributeTok{p =}\NormalTok{ (}\DecValTok{1}\SpecialCharTok{{-}}\NormalTok{ci\_level)}\SpecialCharTok{/}\DecValTok{2}\NormalTok{, }
-               \AttributeTok{df =} \FunctionTok{sum}\NormalTok{(}\FunctionTok{unlist}\NormalTok{(model\_results}\SpecialCharTok{@}\NormalTok{Data}\SpecialCharTok{@}\NormalTok{nobs)), }
-               \AttributeTok{lower.tail =}\NormalTok{ F)}
-
-  \CommentTok{\# get group variable}
-\NormalTok{  group\_var }\OtherTok{\textless{}{-}}\NormalTok{ model\_results}\SpecialCharTok{@}\NormalTok{Data}\SpecialCharTok{@}\NormalTok{group}
-\NormalTok{  group\_labels }\OtherTok{\textless{}{-}}\NormalTok{ model\_results}\SpecialCharTok{@}\NormalTok{Data}\SpecialCharTok{@}\NormalTok{group.label}
-
-  \CommentTok{\# first get the data}
-\NormalTok{  graph.data }\OtherTok{\textless{}{-}}\NormalTok{ data\_coef }\SpecialCharTok{\%\textgreater{}\%} \CommentTok{\# put in tidy coefficients}
-  \FunctionTok{filter}\NormalTok{(model }\SpecialCharTok{==}\NormalTok{ model\_step) }\SpecialCharTok{\%\textgreater{}\%} \CommentTok{\# pick a model}
-  \FunctionTok{filter}\NormalTok{(}\FunctionTok{grepl}\NormalTok{(item\_name, term)) }\SpecialCharTok{\%\textgreater{}\%}  \CommentTok{\# pick a question}
-  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{group =} \FunctionTok{factor}\NormalTok{(group, }\AttributeTok{levels =} \FunctionTok{names}\NormalTok{(}\FunctionTok{table}\NormalTok{(data\_coef}\SpecialCharTok{$}\NormalTok{group)), }
-                        \AttributeTok{labels =}\NormalTok{ group\_labels)) }
-
-  \CommentTok{\# make ribbon data y = slope*x + intercept for ci for slopes }
-\NormalTok{  ribbondata }\OtherTok{\textless{}{-}} \FunctionTok{bind\_rows}\NormalTok{(}
-    \FunctionTok{data.frame}\NormalTok{(}
-    \AttributeTok{x =} \FunctionTok{seq}\NormalTok{(}\AttributeTok{from =}\NormalTok{ x\_limits[}\DecValTok{1}\NormalTok{] }\SpecialCharTok{{-}} \DecValTok{1}\NormalTok{,  }
-            \AttributeTok{to =}\NormalTok{ x\_limits[}\DecValTok{2}\NormalTok{] }\SpecialCharTok{+} \DecValTok{1}\NormalTok{, }
-            \AttributeTok{by =}\NormalTok{ .}\DecValTok{05}\NormalTok{), }
-    \AttributeTok{group =} \FunctionTok{unique}\NormalTok{(graph.data}\SpecialCharTok{$}\NormalTok{group)[}\DecValTok{1}\NormalTok{]}
-\NormalTok{  ) }\SpecialCharTok{\%\textgreater{}\%} 
-    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{ymin =}\NormalTok{ (graph.data }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(op }\SpecialCharTok{==} \StringTok{"=\textasciitilde{}"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
-                 \FunctionTok{slice\_head}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{pull}\NormalTok{(estimate) }\SpecialCharTok{*}\NormalTok{ x) }\SpecialCharTok{{-}} 
-\NormalTok{             (cutoff}\SpecialCharTok{*}\NormalTok{graph.data }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(op }\SpecialCharTok{==} \StringTok{"=\textasciitilde{}"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
-                    \FunctionTok{slice\_head}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{pull}\NormalTok{(std.error)) }\SpecialCharTok{+}
-\NormalTok{             graph.data }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(op }\SpecialCharTok{==} \StringTok{"\textasciitilde{}1"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
-                 \FunctionTok{slice\_head}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{pull}\NormalTok{(estimate), }
-           \AttributeTok{ymax =}\NormalTok{ (graph.data }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(op }\SpecialCharTok{==} \StringTok{"=\textasciitilde{}"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
-                 \FunctionTok{slice\_head}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{pull}\NormalTok{(estimate) }\SpecialCharTok{*}\NormalTok{ x) }\SpecialCharTok{+} 
-\NormalTok{             (cutoff}\SpecialCharTok{*}\NormalTok{graph.data }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(op }\SpecialCharTok{==} \StringTok{"=\textasciitilde{}"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
-                    \FunctionTok{slice\_head}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{pull}\NormalTok{(std.error)) }\SpecialCharTok{+}
-\NormalTok{             graph.data }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(op }\SpecialCharTok{==} \StringTok{"\textasciitilde{}1"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
-                 \FunctionTok{slice\_head}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{pull}\NormalTok{(estimate)), }
-    \FunctionTok{data.frame}\NormalTok{(}
-      \AttributeTok{x =} \FunctionTok{seq}\NormalTok{(}\AttributeTok{from =}\NormalTok{ x\_limits[}\DecValTok{1}\NormalTok{] }\SpecialCharTok{{-}} \DecValTok{1}\NormalTok{,  }
-              \AttributeTok{to =}\NormalTok{ x\_limits[}\DecValTok{2}\NormalTok{] }\SpecialCharTok{+} \DecValTok{1}\NormalTok{, }
-              \AttributeTok{by =}\NormalTok{ .}\DecValTok{05}\NormalTok{), }
-      \AttributeTok{group =} \FunctionTok{unique}\NormalTok{(graph.data}\SpecialCharTok{$}\NormalTok{group)[}\DecValTok{2}\NormalTok{]}
-\NormalTok{    ) }\SpecialCharTok{\%\textgreater{}\%} 
-      \FunctionTok{mutate}\NormalTok{(}\AttributeTok{ymin =}\NormalTok{ (graph.data }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(op }\SpecialCharTok{==} \StringTok{"=\textasciitilde{}"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
-                   \FunctionTok{slice\_tail}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{pull}\NormalTok{(estimate) }\SpecialCharTok{*}\NormalTok{ x) }\SpecialCharTok{{-}} 
-\NormalTok{               (cutoff}\SpecialCharTok{*}\NormalTok{graph.data }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(op }\SpecialCharTok{==} \StringTok{"=\textasciitilde{}"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
-                      \FunctionTok{slice\_tail}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{pull}\NormalTok{(std.error)) }\SpecialCharTok{+}
-\NormalTok{               graph.data }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(op }\SpecialCharTok{==} \StringTok{"\textasciitilde{}1"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
-                   \FunctionTok{slice\_tail}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{pull}\NormalTok{(estimate), }
-             \AttributeTok{ymax =}\NormalTok{ (graph.data }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(op }\SpecialCharTok{==} \StringTok{"=\textasciitilde{}"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
-                   \FunctionTok{slice\_tail}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{pull}\NormalTok{(estimate) }\SpecialCharTok{*}\NormalTok{ x) }\SpecialCharTok{+} 
-\NormalTok{               (cutoff}\SpecialCharTok{*}\NormalTok{graph.data }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(op }\SpecialCharTok{==} \StringTok{"=\textasciitilde{}"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
-                      \FunctionTok{slice\_tail}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{pull}\NormalTok{(std.error)) }\SpecialCharTok{+}
-\NormalTok{               graph.data }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(op }\SpecialCharTok{==} \StringTok{"\textasciitilde{}1"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
-                   \FunctionTok{slice\_tail}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{pull}\NormalTok{(estimate))}
-\NormalTok{  )}
-
-  \CommentTok{\# make point data to draw on the intercepts }
-\NormalTok{  pointdata }\OtherTok{\textless{}{-}} \FunctionTok{data.frame}\NormalTok{(}
-  \AttributeTok{x =} \FunctionTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{,}\DecValTok{0}\NormalTok{),}
-  \AttributeTok{y =}\NormalTok{ graph.data }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(op }\SpecialCharTok{==} \StringTok{"\textasciitilde{}1"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{pull}\NormalTok{(estimate), }
-  \AttributeTok{group =}\NormalTok{ graph.data }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(op }\SpecialCharTok{==} \StringTok{"\textasciitilde{}1"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{pull}\NormalTok{(group),}
-  \AttributeTok{ymin =}\NormalTok{ graph.data }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(op }\SpecialCharTok{==} \StringTok{"\textasciitilde{}1"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{pull}\NormalTok{(estimate) }\SpecialCharTok{{-}}
-\NormalTok{    cutoff }\SpecialCharTok{*}\NormalTok{ graph.data }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(op }\SpecialCharTok{==} \StringTok{"\textasciitilde{}1"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{pull}\NormalTok{(std.error), }
-  \AttributeTok{ymax =}\NormalTok{ graph.data }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(op }\SpecialCharTok{==} \StringTok{"\textasciitilde{}1"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{pull}\NormalTok{(estimate) }\SpecialCharTok{+}
-\NormalTok{    cutoff }\SpecialCharTok{*}\NormalTok{ graph.data }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(op }\SpecialCharTok{==} \StringTok{"\textasciitilde{}1"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{pull}\NormalTok{(std.error)}
-\NormalTok{  )}
-
-  \CommentTok{\# make the line data to draw on the slopes}
-\NormalTok{  linedata }\OtherTok{\textless{}{-}} \FunctionTok{data.frame}\NormalTok{(}
-  \AttributeTok{slope =}\NormalTok{ graph.data }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(op }\SpecialCharTok{==} \StringTok{"=\textasciitilde{}"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{pull}\NormalTok{(estimate), }
-  \AttributeTok{intercept =}\NormalTok{ graph.data }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(op }\SpecialCharTok{==} \StringTok{"\textasciitilde{}1"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{pull}\NormalTok{(estimate), }
-  \AttributeTok{group =}\NormalTok{ graph.data }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(op }\SpecialCharTok{==} \StringTok{"\textasciitilde{}1"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{pull}\NormalTok{(group)}
-\NormalTok{  )}
-
-  \CommentTok{\# make the distributions for the residuals }
-\NormalTok{  violindata }\OtherTok{\textless{}{-}} \FunctionTok{data.frame}\NormalTok{(}
-  \AttributeTok{y =} \FunctionTok{c}\NormalTok{(}\FunctionTok{rnorm}\NormalTok{(}\AttributeTok{n =} \DecValTok{1000}\NormalTok{, }
-            \AttributeTok{mean =}\NormalTok{ graph.data }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(op }\SpecialCharTok{==} \StringTok{"\textasciitilde{}\textasciitilde{}"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
-              \FunctionTok{slice\_head}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{pull}\NormalTok{(estimate), }
-            \AttributeTok{sd =}\NormalTok{ graph.data }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(op }\SpecialCharTok{==} \StringTok{"\textasciitilde{}\textasciitilde{}"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
-              \FunctionTok{slice\_head}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{pull}\NormalTok{(std.error)), }
-        \FunctionTok{rnorm}\NormalTok{(}\AttributeTok{n =} \DecValTok{1000}\NormalTok{, }
-            \AttributeTok{mean =}\NormalTok{ graph.data }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(op }\SpecialCharTok{==} \StringTok{"\textasciitilde{}\textasciitilde{}"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
-              \FunctionTok{slice\_tail}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{pull}\NormalTok{(estimate), }
-            \AttributeTok{sd =}\NormalTok{ graph.data }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(op }\SpecialCharTok{==} \StringTok{"\textasciitilde{}\textasciitilde{}"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
-              \FunctionTok{slice\_tail}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{pull}\NormalTok{(std.error))),}
-  \AttributeTok{group =} \FunctionTok{c}\NormalTok{(}\FunctionTok{rep}\NormalTok{(graph.data }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(op }\SpecialCharTok{==} \StringTok{"\textasciitilde{}\textasciitilde{}"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
-              \FunctionTok{slice\_head}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{pull}\NormalTok{(group), }\DecValTok{1000}\NormalTok{),}
-            \FunctionTok{rep}\NormalTok{(graph.data }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(op }\SpecialCharTok{==} \StringTok{"\textasciitilde{}\textasciitilde{}"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
-              \FunctionTok{slice\_tail}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{pull}\NormalTok{(group), }\DecValTok{1000}\NormalTok{)), }
-  \AttributeTok{x =} \DecValTok{1}
-\NormalTok{  )}
-
-  \CommentTok{\# make the latent mean data for right panel}
-\NormalTok{  latent\_means }\OtherTok{\textless{}{-}} \FunctionTok{lavPredict}\NormalTok{(model\_results, }
-                               \AttributeTok{type =} \StringTok{"lv"}\NormalTok{, }
-                               \AttributeTok{label =} \ConstantTok{TRUE}\NormalTok{,}
-                               \AttributeTok{assemble =} \ConstantTok{TRUE}\NormalTok{, }
-                               \AttributeTok{append.data =} \ConstantTok{TRUE}\NormalTok{)}
-
-\NormalTok{  latent\_means}\SpecialCharTok{$}\NormalTok{lv }\OtherTok{\textless{}{-}}\NormalTok{ latent\_means[ , lv\_name]}
-\NormalTok{  latent\_means}\SpecialCharTok{$}\NormalTok{group }\OtherTok{\textless{}{-}}\NormalTok{ latent\_means[ , group\_var]}
-
-  \CommentTok{\# make a plot of the variance}
-\NormalTok{  variance\_plot }\OtherTok{\textless{}{-}} 
-  \FunctionTok{ggplot}\NormalTok{(violindata, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =} \DecValTok{1}\NormalTok{, }\AttributeTok{y =}\NormalTok{ y, }\AttributeTok{color =}\NormalTok{ group, }\AttributeTok{fill =}\NormalTok{ group)) }\SpecialCharTok{+}
-  \FunctionTok{geom\_split\_violin}\NormalTok{() }\SpecialCharTok{+} 
-  \FunctionTok{theme\_void}\NormalTok{() }\SpecialCharTok{+} 
-  \FunctionTok{theme}\NormalTok{(}\AttributeTok{legend.position =} \StringTok{"none"}\NormalTok{) }\SpecialCharTok{+} 
-  \FunctionTok{stat\_summary}\NormalTok{(}\AttributeTok{fun =} \StringTok{"mean"}\NormalTok{,}
-               \AttributeTok{geom =} \StringTok{"crossbar"}\NormalTok{, }
-               \AttributeTok{width =} \FloatTok{0.5}\NormalTok{,}
-               \AttributeTok{colour =} \StringTok{"black"}\NormalTok{)}
-
-  \CommentTok{\# make the plot with intercepts and slopes}
-\NormalTok{  intercept\_plot }\OtherTok{\textless{}{-}} 
-  \FunctionTok{ggplot}\NormalTok{() }\SpecialCharTok{+} 
-  \CommentTok{\# basic set up}
-  \FunctionTok{theme\_classic}\NormalTok{() }\SpecialCharTok{+} 
-  \FunctionTok{xlab}\NormalTok{(}\StringTok{"Latent Variable"}\NormalTok{) }\SpecialCharTok{+} 
-  \FunctionTok{ylab}\NormalTok{(}\StringTok{"Observed Variable"}\NormalTok{) }\SpecialCharTok{+} 
-  \FunctionTok{coord\_cartesian}\NormalTok{(}\AttributeTok{xlim =}\NormalTok{ x\_limits, }\AttributeTok{ylim =}\NormalTok{ y\_limits) }\SpecialCharTok{+} 
-  \CommentTok{\# plot the intercepts }
-  \FunctionTok{geom\_point}\NormalTok{(}\AttributeTok{data =}\NormalTok{ pointdata, }
-             \FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ x, }\AttributeTok{y =}\NormalTok{ y, }\AttributeTok{color =}\NormalTok{ group), }
-             \AttributeTok{inherit.aes =} \ConstantTok{FALSE}\NormalTok{) }\SpecialCharTok{+} 
-  \FunctionTok{geom\_errorbar}\NormalTok{(}\AttributeTok{data =}\NormalTok{ pointdata,}
-                \FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ x, }\AttributeTok{ymin =}\NormalTok{ ymin, }\AttributeTok{ymax =}\NormalTok{ ymax, }\AttributeTok{color =}\NormalTok{ group), }
-                \AttributeTok{inherit.aes =} \ConstantTok{FALSE}\NormalTok{, }\AttributeTok{width =}\NormalTok{ .}\DecValTok{10}\NormalTok{) }\SpecialCharTok{+} 
-  \CommentTok{\# plot the slopes}
-  \FunctionTok{geom\_abline}\NormalTok{(}\AttributeTok{data =}\NormalTok{ linedata,}
-              \FunctionTok{aes}\NormalTok{(}\AttributeTok{slope =}\NormalTok{ slope, }\AttributeTok{intercept =}\NormalTok{ intercept, }\AttributeTok{color =}\NormalTok{ group)) }\SpecialCharTok{+} 
-  \FunctionTok{geom\_ribbon}\NormalTok{(}\AttributeTok{data =}\NormalTok{ ribbondata, }
-              \FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ x, }\AttributeTok{ymin =}\NormalTok{ ymin, }\AttributeTok{ymax =}\NormalTok{ ymax, }\AttributeTok{fill =}\NormalTok{ group), }
-              \AttributeTok{inherit.aes =} \ConstantTok{FALSE}\NormalTok{, }\AttributeTok{alpha =}\NormalTok{ .}\DecValTok{2}\NormalTok{) }\SpecialCharTok{+} 
-  \FunctionTok{scale\_color\_discrete}\NormalTok{(}\AttributeTok{name =} \StringTok{"Group"}\NormalTok{) }\SpecialCharTok{+} 
-  \FunctionTok{scale\_fill\_discrete}\NormalTok{(}\AttributeTok{name =} \StringTok{"Group"}\NormalTok{) }\SpecialCharTok{+} 
-  \FunctionTok{geom\_vline}\NormalTok{(}\AttributeTok{xintercept =} \DecValTok{0}\NormalTok{) }\SpecialCharTok{+} 
-  \FunctionTok{theme}\NormalTok{(}\AttributeTok{axis.line.y =} \FunctionTok{element\_blank}\NormalTok{())}
-
-  \CommentTok{\# make the latent means plot}
-\NormalTok{  mean\_plot }\OtherTok{\textless{}{-}} \FunctionTok{ggplot}\NormalTok{(latent\_means, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ lv, }\AttributeTok{fill =}\NormalTok{ group)) }\SpecialCharTok{+}
-    \FunctionTok{geom\_density}\NormalTok{(}\AttributeTok{alpha =}\NormalTok{ .}\DecValTok{2}\NormalTok{) }\SpecialCharTok{+} 
-    \FunctionTok{theme\_classic}\NormalTok{() }\SpecialCharTok{+} 
-    \FunctionTok{xlab}\NormalTok{(}\StringTok{"Latent Variable"}\NormalTok{) }\SpecialCharTok{+} 
-    \FunctionTok{ylab}\NormalTok{(}\StringTok{"Density"}\NormalTok{) }\SpecialCharTok{+} 
-    \FunctionTok{geom\_vline}\NormalTok{(}\AttributeTok{data =}\NormalTok{ latent\_means }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{group\_by}\NormalTok{(group) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{summarize}\NormalTok{(}\AttributeTok{mean =} \FunctionTok{mean}\NormalTok{(lv)), }
-               \FunctionTok{aes}\NormalTok{(}\AttributeTok{xintercept =}\NormalTok{ mean, }\AttributeTok{color =}\NormalTok{ group)) }\SpecialCharTok{+} 
-    \FunctionTok{theme}\NormalTok{(}\AttributeTok{legend.position =} \StringTok{"none"}\NormalTok{) }\SpecialCharTok{+} 
-    \FunctionTok{coord\_cartesian}\NormalTok{(}\AttributeTok{xlim =}\NormalTok{ x\_limits)}
-
-\NormalTok{  y\_range }\OtherTok{=} \FunctionTok{abs}\NormalTok{(y\_limits[}\DecValTok{2}\NormalTok{] }\SpecialCharTok{{-}}\NormalTok{ y\_limits[}\DecValTok{1}\NormalTok{])}
-
-  \CommentTok{\# line up the two plots }
-\NormalTok{  prow }\OtherTok{\textless{}{-}} \FunctionTok{plot\_grid}\NormalTok{(}
-\NormalTok{    intercept\_plot }\SpecialCharTok{+} 
-      \FunctionTok{ggtitle}\NormalTok{(}\StringTok{"Item Invariance"}\NormalTok{) }\SpecialCharTok{+} 
-      \FunctionTok{theme}\NormalTok{(}\AttributeTok{legend.position =} \StringTok{"none"}\NormalTok{) }\SpecialCharTok{+} 
-      \FunctionTok{annotation\_custom}\NormalTok{(}\FunctionTok{ggplotGrob}\NormalTok{(variance\_plot), }
-                        \AttributeTok{xmin =}\NormalTok{ .}\DecValTok{25}\NormalTok{, }\AttributeTok{xmax =} \DecValTok{1}\NormalTok{, }
-                        \AttributeTok{ymin =}\NormalTok{ y\_limits[}\DecValTok{1}\NormalTok{], }\AttributeTok{ymax =}\NormalTok{ y\_limits[}\DecValTok{2}\NormalTok{]}\SpecialCharTok{{-}}\NormalTok{y\_range}\SpecialCharTok{/}\FloatTok{1.8}\NormalTok{),}
-\NormalTok{    mean\_plot }\SpecialCharTok{+} 
-      \FunctionTok{ggtitle}\NormalTok{(}\StringTok{"Latent Mean Distribution"}\NormalTok{) }\SpecialCharTok{+} 
-      \FunctionTok{theme}\NormalTok{(}\AttributeTok{legend.position =} \StringTok{"none"}\NormalTok{),}
-    \AttributeTok{align =} \StringTok{\textquotesingle{}vh\textquotesingle{}}\NormalTok{,}
-    \AttributeTok{hjust =} \SpecialCharTok{{-}}\DecValTok{1}\NormalTok{,}
-    \AttributeTok{nrow =} \DecValTok{1}
-\NormalTok{  )}
-
-  \CommentTok{\# get the legend}
-\NormalTok{  legend\_b }\OtherTok{\textless{}{-}} \FunctionTok{get\_legend}\NormalTok{(}
-\NormalTok{    intercept\_plot }\SpecialCharTok{+} 
-      \FunctionTok{guides}\NormalTok{(}\AttributeTok{color =} \FunctionTok{guide\_legend}\NormalTok{(}\AttributeTok{nrow =} \DecValTok{1}\NormalTok{)) }\SpecialCharTok{+}
-      \FunctionTok{theme}\NormalTok{(}\AttributeTok{legend.position =} \StringTok{"bottom"}\NormalTok{)}
-\NormalTok{  )}
-
-  \CommentTok{\# send out the plot }
-  \FunctionTok{plot\_grid}\NormalTok{(prow, legend\_b, }\AttributeTok{ncol =} \DecValTok{1}\NormalTok{, }\AttributeTok{rel\_heights =} \FunctionTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{, .}\DecValTok{1}\NormalTok{))}
-
-\NormalTok{\}}
-\end{Highlighting}
-\end{Shaded}
-
-\normalsize
-
-\hypertarget{model-fit-statistics}{%
-\subsection{Model Fit Statistics}\label{model-fit-statistics}}
+\FunctionTok{library}\NormalTok{(MASS)}
+
+\CommentTok{\# covariance matrix}
+\NormalTok{university.cov }\OtherTok{\textless{}{-}} \FunctionTok{lav\_matrix\_lower2full}\NormalTok{(}
+    \FunctionTok{c}\NormalTok{(}\FloatTok{169.00}\NormalTok{, }
+      \FloatTok{73.710}\NormalTok{, }\FloatTok{182.2500}\NormalTok{,}
+      \FloatTok{73.229}\NormalTok{, }\FloatTok{88.4250}\NormalTok{, }\FloatTok{171.6100}\NormalTok{,}
+      \FloatTok{63.375}\NormalTok{, }\FloatTok{72.5625}\NormalTok{, }\FloatTok{127.7250}\NormalTok{, }\FloatTok{156.2500}\NormalTok{,}
+      \FloatTok{42.120}\NormalTok{, }\FloatTok{67.4325}\NormalTok{, }\FloatTok{122.0265}\NormalTok{, }\FloatTok{123.1875}\NormalTok{, }\FloatTok{182.2500}\NormalTok{,}
+      \FloatTok{57.226}\NormalTok{, }\FloatTok{63.2610}\NormalTok{, }\FloatTok{117.1926}\NormalTok{, }\FloatTok{154.4250}\NormalTok{, }\FloatTok{138.0240}\NormalTok{, }\FloatTok{201.6400}\NormalTok{,}
+      \FloatTok{30.875}\NormalTok{, }\FloatTok{32.0625}\NormalTok{, }\FloatTok{60.9805}\NormalTok{, }\FloatTok{62.9375}\NormalTok{, }\FloatTok{76.9500}\NormalTok{, }\FloatTok{79.5910}\NormalTok{, }\FloatTok{90.2500}\NormalTok{,}
+      \FloatTok{36.075}\NormalTok{, }\FloatTok{38.9610}\NormalTok{, }\FloatTok{61.0722}\NormalTok{, }\FloatTok{58.2750}\NormalTok{, }\FloatTok{65.9340}\NormalTok{, }\FloatTok{70.9290}\NormalTok{, }\FloatTok{81.1965}\NormalTok{, }\FloatTok{123.2100}\NormalTok{,}
+      \FloatTok{18.096}\NormalTok{, }\FloatTok{21.1410}\NormalTok{, }\FloatTok{26.2131}\NormalTok{, }\FloatTok{39.1500}\NormalTok{, }\FloatTok{44.6310}\NormalTok{, }\FloatTok{46.9452}\NormalTok{, }\FloatTok{48.7635}\NormalTok{, }\FloatTok{56.0106}\NormalTok{, }\FloatTok{75.6900}\NormalTok{))}
+
+\CommentTok{\# give it names}
+\FunctionTok{rownames}\NormalTok{(university.cov) }\OtherTok{\textless{}{-}}
+    \FunctionTok{colnames}\NormalTok{(university.cov) }\OtherTok{\textless{}{-}}
+    \FunctionTok{c}\NormalTok{(}\StringTok{"class"}\NormalTok{, }\StringTok{"social"}\NormalTok{, }\StringTok{"learn"}\NormalTok{, }\StringTok{"chronic"}\NormalTok{, }\StringTok{"physical"}\NormalTok{, }\StringTok{"sex"}\NormalTok{, }
+      \StringTok{"depression"}\NormalTok{, }\StringTok{"anxiety"}\NormalTok{, }\StringTok{"stress"}\NormalTok{)}
+
+\CommentTok{\# means {-} you need standard deviation if you only have a correlation matrix }
+\NormalTok{university.means }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\FloatTok{3.4}\NormalTok{, }\FloatTok{4.3}\NormalTok{, }\FloatTok{3.7}\NormalTok{, }\FloatTok{3.2}\NormalTok{, }\FloatTok{4.5}\NormalTok{, }\FloatTok{1.2}\NormalTok{, }\FloatTok{4.0}\NormalTok{, }\FloatTok{3.5}\NormalTok{, }\FloatTok{4.2}\NormalTok{)}
+
+\CommentTok{\# use mass function}
+\NormalTok{DF }\OtherTok{\textless{}{-}} \FunctionTok{mvrnorm}\NormalTok{(}\AttributeTok{n =} \DecValTok{200}\NormalTok{, }\AttributeTok{mu =}\NormalTok{ university.means, }\AttributeTok{Sigma =}\NormalTok{ university.cov)}
+
+\FunctionTok{head}\NormalTok{(DF)}
+\end{Highlighting}
+\end{Shaded}
+
+\normalsize
+
+\begin{verbatim}
+##          class      social     learn   chronic    physical         sex
+## [1,] 12.085294 26.83043663 13.895103 20.634374  16.7903295  30.5468832
+## [2,]  3.939545 10.93624431  3.093025  8.316128  -7.2199148   9.3579991
+## [3,] 15.659627  0.22811723  5.205657  5.224293  -1.4425219  -1.2710662
+## [4,] 23.086133 12.43649966  1.891769 -5.913170 -19.4937389 -13.5922410
+## [5,] 10.856492 23.30887194 17.124064 11.438840   2.4659294   1.7330709
+## [6,] -4.328380  0.07907149 -1.000636 -1.654947  -0.7365838  -0.3958833
+##      depression    anxiety      stress
+## [1,]  14.174374   8.001766  13.6534279
+## [2,]   3.940819  -6.598153  -7.9229552
+## [3,]  -8.927508 -10.335571  -2.8100779
+## [4,]  -0.149840   6.475669 -15.5300195
+## [5,]  -6.492809 -12.524601   0.4924153
+## [6,]  11.917631   3.433587   8.1456346
+\end{verbatim}
+
+\hypertarget{mgcfa-model-fit-statistics}{%
+\subsection{MGCFA Model Fit Statistics}\label{mgcfa-model-fit-statistics}}
 
@@
 \midrule
-Overall & 7,515.723 & 7,578.942 & 0.994 & 0.988 & 0.023 & 0.021\\
-Group 1 & 3,765.749 & 3,818.571 & 0.976 & 0.953 & 0.047 & 0.031\\
-Group 2 & 3,761.952 & 3,814.774 & 0.980 & 0.960 & 0.042 & 0.032\\
-Configural & 7,527.701 & 7,654.140 & 0.978 & 0.956 & 0.045 & 0.032\\
-Metric & 7,529.390 & 7,638.970 & 0.954 & 0.934 & 0.055 & 0.048\\
-Scalar & 7,522.896 & 7,615.617 & 0.964 & 0.960 & 0.043 & 0.049\\
-Strict & 7,519.512 & 7,591.160 & 0.957 & 0.963 & 0.041 & 0.059\\
+Overall & 7,516.454 & 7,579.673 & 1.000 & 1.036 & 0.000 & 0.006\\
+Group Group 1 & 3,765.749 & 3,818.571 & 0.976 & 0.953 & 0.047 & 0.031\\
+Group Group 2 & 3,767.599 & 3,820.421 & 1.000 & 1.008 & 0.000 & 0.021\\
+Configural & 7,533.348 & 7,659.786 & 0.991 & 0.982 & 0.030 & 0.026\\
+loadings & 7,528.476 & 7,638.056 & 0.994 & 0.992 & 0.020 & 0.033\\
+intercepts & 7,522.397 & 7,615.118 & 1.000 & 1.003 & 0.000 & 0.035\\
+residuals & 7,520.435 & 7,592.083 & 0.991 & 0.992 & 0.020 & 0.046\\
 \bottomrule
@@
 \midrule
-Overall & 7,537.668 & 7,600.888 & 0.981 & 0.962 & 0.044 & 0.024\\
-Group 1 & 3,765.749 & 3,818.571 & 0.976 & 0.953 & 0.047 & 0.031\\
-Group 2 & 3,777.833 & 3,830.655 & 0.978 & 0.956 & 0.050 & 0.032\\
-Configural & 7,543.582 & 7,670.020 & 0.977 & 0.955 & 0.048 & 0.032\\
-Metric & 7,548.898 & 7,658.477 & 0.941 & 0.916 & 0.066 & 0.056\\
-Scalar & 7,541.810 & 7,634.531 & 0.953 & 0.948 & 0.052 & 0.056\\
-Strict & 7,541.658 & 7,613.307 & 0.935 & 0.943 & 0.054 & 0.071\\
+Overall & 7,530.321 & 7,593.540 & 0.977 & 0.955 & 0.049 & 0.025\\
+Group Group 1 & 3,765.749 & 3,818.571 & 0.976 & 0.953 & 0.047 & 0.031\\
+Group Group 2 & 3,785.242 & 3,838.064 & 0.979 & 0.958 & 0.050 & 0.029\\
+Configural & 7,550.991 & 7,677.430 & 0.978 & 0.956 & 0.048 & 0.030\\
+loadings & 7,550.133 & 7,659.713 & 0.966 & 0.952 & 0.051 & 0.047\\
+intercepts & 7,542.675 & 7,635.397 & 0.979 & 0.977 & 0.035 & 0.047\\
+residuals & 7,534.091 & 7,605.739 & 0.993 & 0.994 & 0.019 & 0.054\\
 \bottomrule
@@
 \midrule
-Overall & 7,554.550 & 7,617.769 & 0.972 & 0.945 & 0.052 & 0.027\\
-Group 1 & 3,765.749 & 3,818.571 & 0.976 & 0.953 & 0.047 & 0.031\\
-Group 2 & 3,784.923 & 3,837.745 & 0.998 & 0.996 & 0.016 & 0.025\\
-Configural & 7,550.672 & 7,677.110 & 0.988 & 0.976 & 0.035 & 0.028\\
-Metric & 7,562.714 & 7,672.294 & 0.926 & 0.894 & 0.074 & 0.063\\
-Scalar & 7,556.859 & 7,649.580 & 0.933 & 0.926 & 0.062 & 0.064\\
-Strict & 7,558.054 & 7,629.703 & 0.909 & 0.921 & 0.064 & 0.079\\
+Overall & 7,598.681 & 7,661.900 & 0.946 & 0.893 & 0.078 & 0.035\\
+Group Group 1 & 3,765.749 & 3,818.571 & 0.976 & 0.953 & 0.047 & 0.031\\
+Group Group 2 & 3,820.090 & 3,872.912 & 0.969 & 0.938 & 0.067 & 0.034\\
+Configural & 7,585.839 & 7,712.277 & 0.972 & 0.944 & 0.058 & 0.033\\
+loadings & 7,613.434 & 7,723.014 & 0.865 & 0.807 & 0.107 & 0.079\\
+intercepts & 7,606.648 & 7,699.370 & 0.874 & 0.860 & 0.091 & 0.079\\
+residuals & 7,600.057 & 7,671.705 & 0.880 & 0.895 & 0.079 & 0.091\\
 \bottomrule
@@
 \midrule
-Overall & 7,662.989 & 7,726.209 & 0.984 & 0.969 & 0.045 & 0.022\\
-Group 1 & 3,765.749 & 3,818.571 & 0.976 & 0.953 & 0.047 & 0.031\\
-Group 2 & 3,857.210 & 3,910.032 & 0.968 & 0.936 & 0.076 & 0.033\\
-Configural & 7,622.959 & 7,749.397 & 0.971 & 0.942 & 0.063 & 0.032\\
-Metric & 7,659.191 & 7,768.771 & 0.854 & 0.792 & 0.120 & 0.085\\
-Scalar & 7,652.603 & 7,745.325 & 0.862 & 0.846 & 0.103 & 0.085\\
-Strict & 7,660.626 & 7,732.274 & 0.824 & 0.847 & 0.103 & 0.119\\
+Overall & 7,684.982 & 7,748.201 & 0.987 & 0.973 & 0.040 & 0.023\\
+Group Group 1 & 3,765.749 & 3,818.571 & 0.976 & 0.953 & 0.047 & 0.031\\
+Group Group 2 & 3,857.143 & 3,909.965 & 0.992 & 0.984 & 0.037 & 0.029\\
+Configural & 7,622.892 & 7,749.330 & 0.986 & 0.972 & 0.042 & 0.030\\
+loadings & 7,674.188 & 7,783.767 & 0.817 & 0.738 & 0.131 & 0.095\\
+intercepts & 7,667.682 & 7,760.403 & 0.824 & 0.805 & 0.113 & 0.096\\
+residuals & 7,683.177 & 7,754.825 & 0.762 & 0.793 & 0.116 & 0.138\\
 \bottomrule
@@
 \midrule
-Overall & 7,519.687 & 7,582.906 & 0.996 & 0.992 & 0.020 & 0.021\\
-Group 1 & 3,765.749 & 3,818.571 & 0.976 & 0.953 & 0.047 & 0.031\\
-Group 2 & 3,770.411 & 3,823.233 & 0.932 & 0.865 & 0.081 & 0.041\\
-Configural & 7,536.160 & 7,662.598 & 0.954 & 0.908 & 0.066 & 0.036\\
-Metric & 7,531.359 & 7,640.939 & 0.957 & 0.939 & 0.054 & 0.041\\
-Scalar & 7,531.343 & 7,624.064 & 0.941 & 0.934 & 0.056 & 0.049\\
-Strict & 7,523.535 & 7,595.184 & 0.952 & 0.959 & 0.045 & 0.052\\
+Overall & 7,520.471 & 7,583.690 & 1.000 & 1.035 & 0.000 & 0.007\\
+Group Group 1 & 3,765.749 & 3,818.571 & 0.976 & 0.953 & 0.047 & 0.031\\
+Group Group 2 & 3,767.599 & 3,820.421 & 1.000 & 1.008 & 0.000 & 0.021\\
+Configural & 7,533.348 & 7,659.786 & 0.991 & 0.982 & 0.030 & 0.026\\
+loadings & 7,528.476 & 7,638.056 & 0.994 & 0.992 & 0.020 & 0.033\\
+intercepts & 7,526.312 & 7,619.034 & 0.987 & 0.986 & 0.027 & 0.040\\
+residuals & 7,524.356 & 7,596.005 & 0.975 & 0.978 & 0.033 & 0.050\\
 \bottomrule
@@
 \midrule
-Overall & 7,542.771 & 7,605.990 & 0.998 & 0.996 & 0.014 & 0.020\\
-Group 1 & 3,765.749 & 3,818.571 & 0.976 & 0.953 & 0.047 & 0.031\\
-Group 2 & 3,770.411 & 3,823.233 & 0.932 & 0.865 & 0.081 & 0.041\\
-Configural & 7,536.160 & 7,662.598 & 0.954 & 0.908 & 0.066 & 0.036\\
-Metric & 7,531.359 & 7,640.939 & 0.957 & 0.939 & 0.054 & 0.041\\
-Scalar & 7,554.199 & 7,646.920 & 0.845 & 0.828 & 0.091 & 0.070\\
-Strict & 7,546.383 & 7,618.032 & 0.857 & 0.876 & 0.077 & 0.071\\
+Overall & 7,538.375 & 7,601.594 & 1.000 & 1.033 & 0.000 & 0.008\\
+Group Group 1 & 3,765.749 & 3,818.571 & 0.976 & 0.953 & 0.047 & 0.031\\
+Group Group 2 & 3,767.599 & 3,820.421 & 1.000 & 1.008 & 0.000 & 0.021\\
+Configural & 7,533.348 & 7,659.786 & 0.991 & 0.982 & 0.030 & 0.026\\
+loadings & 7,528.476 & 7,638.056 & 0.994 & 0.992 & 0.020 & 0.033\\
+intercepts & 7,544.002 & 7,636.724 & 0.917 & 0.907 & 0.068 & 0.059\\
+residuals & 7,542.064 & 7,613.712 & 0.905 & 0.917 & 0.065 & 0.067\\
 \bottomrule
@@
 \midrule
-Overall & 7,579.167 & 7,642.386 & 1.000 & 1.000 & 0.000 & 0.019\\
-Group 1 & 3,765.749 & 3,818.571 & 0.976 & 0.953 & 0.047 & 0.031\\
-Group 2 & 3,770.411 & 3,823.233 & 0.932 & 0.865 & 0.081 & 0.041\\
-Configural & 7,536.160 & 7,662.598 & 0.954 & 0.908 & 0.066 & 0.036\\
-Metric & 7,531.359 & 7,640.939 & 0.957 & 0.939 & 0.054 & 0.041\\
-Scalar & 7,590.291 & 7,683.013 & 0.695 & 0.661 & 0.128 & 0.097\\
-Strict & 7,582.468 & 7,654.117 & 0.707 & 0.745 & 0.111 & 0.098\\
+Overall & 7,568.748 & 7,631.967 & 1.000 & 1.032 & 0.000 & 0.008\\
+Group Group 1 & 3,765.749 & 3,818.571 & 0.976 & 0.953 & 0.047 & 0.031\\
+Group Group 2 & 3,767.599 & 3,820.421 & 1.000 & 1.008 & 0.000 & 0.021\\
+Configural & 7,533.348 & 7,659.786 & 0.991 & 0.982 & 0.030 & 0.026\\
+loadings & 7,528.476 & 7,638.056 & 0.994 & 0.992 & 0.020 & 0.033\\
+intercepts & 7,574.054 & 7,666.776 & 0.797 & 0.775 & 0.106 & 0.084\\
+residuals & 7,572.174 & 7,643.823 & 0.785 & 0.813 & 0.097 & 0.090\\
 \bottomrule
@@
 \midrule
-Overall & 7,449.492 & 7,512.711 & 1.000 & 1.008 & 0.000 & 0.014\\
-Group 1 & 3,765.749 & 3,818.571 & 0.976 & 0.953 & 0.047 & 0.031\\
-Group 2 & 3,693.319 & 3,746.141 & 1.000 & 1.009 & 0.000 & 0.022\\
-Configural & 7,459.068 & 7,585.507 & 0.991 & 0.983 & 0.030 & 0.026\\
-Metric & 7,461.406 & 7,570.986 & 0.966 & 0.952 & 0.049 & 0.049\\
-Scalar & 7,455.854 & 7,548.575 & 0.972 & 0.969 & 0.039 & 0.051\\
-Strict & 7,453.476 & 7,525.124 & 0.962 & 0.967 & 0.041 & 0.051\\
+Overall & 7,462.007 & 7,525.226 & 1.000 & 1.020 & 0.000 & 0.013\\
+Group Group 1 & 3,765.749 & 3,818.571 & 0.976 & 0.953 & 0.047 & 0.031\\
+Group Group 2 & 3,703.797 & 3,756.619 & 0.962 & 0.924 & 0.061 & 0.037\\
+Configural & 7,469.546 & 7,595.984 & 0.969 & 0.938 & 0.054 & 0.034\\
+loadings & 7,471.637 & 7,581.217 & 0.944 & 0.920 & 0.062 & 0.049\\
+intercepts & 7,465.722 & 7,558.443 & 0.952 & 0.946 & 0.051 & 0.051\\
+residuals & 7,465.986 & 7,537.635 & 0.930 & 0.939 & 0.054 & 0.065\\
 \bottomrule
@@
 \midrule
-Overall & 7,378.566 & 7,441.785 & 1.000 & 1.004 & 0.000 & 0.016\\
-Group 1 & 3,765.749 & 3,818.571 & 0.976 & 0.953 & 0.047 & 0.031\\
-Group 2 & 3,597.774 & 3,650.596 & 1.000 & 1.026 & 0.000 & 0.018\\
-Configural & 7,363.523 & 7,489.961 & 0.997 & 0.994 & 0.018 & 0.025\\
-Metric & 7,366.629 & 7,476.209 & 0.971 & 0.958 & 0.048 & 0.047\\
-Scalar & 7,360.147 & 7,452.869 & 0.980 & 0.978 & 0.035 & 0.048\\
-Strict & 7,382.532 & 7,454.180 & 0.879 & 0.895 & 0.076 & 0.072\\
+Overall & 7,382.013 & 7,445.232 & 0.997 & 0.995 & 0.016 & 0.018\\
+Group Group 1 & 3,765.749 & 3,818.571 & 0.976 & 0.953 & 0.047 & 0.031\\
+Group Group 2 & 3,602.905 & 3,655.727 & 1.000 & 1.013 & 0.000 & 0.023\\
+Configural & 7,368.654 & 7,495.092 & 0.992 & 0.983 & 0.028 & 0.027\\
+loadings & 7,364.904 & 7,474.483 & 0.990 & 0.986 & 0.025 & 0.036\\
+intercepts & 7,358.503 & 7,451.224 & 1.000 & 1.001 & 0.000 & 0.037\\
+residuals & 7,385.958 & 7,457.607 & 0.864 & 0.881 & 0.075 & 0.098\\
 \bottomrule
@@
 \midrule
-Overall & 7,294.214 & 7,357.433 & 1.000 & 1.009 & 0.000 & 0.015\\
-Group 1 & 3,765.749 & 3,818.571 & 0.976 & 0.953 & 0.047 & 0.031\\
-Group 2 & 3,453.472 & 3,506.294 & 0.950 & 0.900 & 0.073 & 0.035\\
-Configural & 7,219.221 & 7,345.659 & 0.962 & 0.925 & 0.061 & 0.033\\
-Metric & 7,216.378 & 7,325.957 & 0.958 & 0.940 & 0.055 & 0.043\\
-Scalar & 7,210.650 & 7,303.372 & 0.965 & 0.961 & 0.044 & 0.045\\
-Strict & 7,297.887 & 7,369.535 & 0.595 & 0.648 & 0.133 & 0.176\\
+Overall & 7,300.856 & 7,364.075 & 0.998 & 0.995 & 0.015 & 0.018\\
+Group Group 1 & 3,765.749 & 3,818.571 & 0.976 & 0.953 & 0.047 & 0.031\\
+Group Group 2 & 3,453.099 & 3,505.921 & 0.954 & 0.908 & 0.069 & 0.035\\
+Configural & 7,218.848 & 7,345.287 & 0.965 & 0.929 & 0.059 & 0.033\\
+loadings & 7,217.332 & 7,326.912 & 0.955 & 0.935 & 0.056 & 0.045\\
+intercepts & 7,211.566 & 7,304.287 & 0.962 & 0.958 & 0.046 & 0.047\\
+residuals & 7,304.566 & 7,376.215 & 0.562 & 0.619 & 0.137 & 0.189\\
 \bottomrule
@@
 
+\hypertarget{simulated-parital-invariance-results}{%
+\subsection{Simulated Parital Invariance Results}\label{simulated-parital-invariance-results}}
+
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:p-tab11}Fit Estimates for Partial Invariance Residuals on Invariant Data}
+
+\begin{tabular}{lll}
+\toprule
+Estimated Parameter & CFI & RSMEA\\
+\midrule
+q1 \textasciitilde{}\textasciitilde{} q1 & 0.990 & 0.021\\
+q2 \textasciitilde{}\textasciitilde{} q2 & 0.987 & 0.024\\
+q3 \textasciitilde{}\textasciitilde{} q3 & 0.996 & 0.014\\
+q4 \textasciitilde{}\textasciitilde{} q4 & 1.000 & 0.000\\
+q5 \textasciitilde{}\textasciitilde{} q5 & 0.987 & 0.025\\
+lv \textasciitilde{}\textasciitilde{} lv & 0.991 & 0.020\\
+\bottomrule
+\end{tabular}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:p-tab12}Fit Estimates for Partial Invariance Loadings for Small Loading Data}
+
+\begin{tabular}{lll}
+\toprule
+Estimated Parameter & CFI & RSMEA\\
+\midrule
+lv =\textasciitilde{} q1 & 0.993 & 0.019\\
+lv =\textasciitilde{} q2 & 0.989 & 0.023\\
+lv =\textasciitilde{} q3 & 0.989 & 0.023\\
+lv =\textasciitilde{} q4 & 1.000 & 0.000\\
+lv =\textasciitilde{} q5 & 0.994 & 0.017\\
+\bottomrule
+\end{tabular}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:p-tab13}Fit Estimates for Partial Invariance Loadings for Medium Loading Data}
+
+\begin{tabular}{lll}
+\toprule
+Estimated Parameter & CFI & RSMEA\\
+\midrule
+lv =\textasciitilde{} q1 & 0.880 & 0.079\\
+lv =\textasciitilde{} q2 & 0.898 & 0.074\\
+lv =\textasciitilde{} q3 & 0.878 & 0.081\\
+lv =\textasciitilde{} q4 & 0.962 & 0.045\\
+lv =\textasciitilde{} q5 & 0.907 & 0.071\\
+\bottomrule
+\end{tabular}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:p-tab14}Fit Estimates for Partial Invariance Loadings for Large Loading Data}
+
+\begin{tabular}{lll}
+\toprule
+Estimated Parameter & CFI & RSMEA\\
+\midrule
+lv =\textasciitilde{} q1 & 0.762 & 0.116\\
+lv =\textasciitilde{} q2 & 0.770 & 0.117\\
+lv =\textasciitilde{} q3 & 0.762 & 0.119\\
+lv =\textasciitilde{} q4 & 0.971 & 0.041\\
+lv =\textasciitilde{} q5 & 0.842 & 0.097\\
+\bottomrule
+\end{tabular}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:p-tab15}Fit Estimates for Partial Invariance Loadings for Small Intercept Data}
+
+\begin{tabular}{lll}
+\toprule
+Estimated Parameter & CFI & RSMEA\\
+\midrule
+q1 \textasciitilde{}1 & 0.975 & 0.033\\
+lv \textasciitilde{}1 & 0.975 & 0.033\\
+q2 \textasciitilde{}1 & 0.972 & 0.035\\
+q3 \textasciitilde{}1 & 0.972 & 0.036\\
+q4 \textasciitilde{}1 & 0.988 & 0.023\\
+q5 \textasciitilde{}1 & 0.971 & 0.036\\
+\bottomrule
+\end{tabular}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:p-tab16}Fit Estimates for Partial Invariance Loadings for Medium Intercept Data}
+
+\begin{tabular}{lll}
+\toprule
+Estimated Parameter & CFI & RSMEA\\
+\midrule
+q1 \textasciitilde{}1 & 0.905 & 0.065\\
+lv \textasciitilde{}1 & 0.905 & 0.065\\
+q2 \textasciitilde{}1 & 0.901 & 0.067\\
+q3 \textasciitilde{}1 & 0.901 & 0.067\\
+q4 \textasciitilde{}1 & 0.988 & 0.023\\
+q5 \textasciitilde{}1 & 0.902 & 0.067\\
+\bottomrule
+\end{tabular}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:p-tab17}Fit Estimates for Partial Invariance Loadings for Large Intercept Data}
+
+\begin{tabular}{lll}
+\toprule
+Estimated Parameter & CFI & RSMEA\\
+\midrule
+q1 \textasciitilde{}1 & 0.785 & 0.097\\
+lv \textasciitilde{}1 & 0.785 & 0.097\\
+q2 \textasciitilde{}1 & 0.781 & 0.100\\
+q3 \textasciitilde{}1 & 0.781 & 0.100\\
+q4 \textasciitilde{}1 & 0.988 & 0.023\\
+q5 \textasciitilde{}1 & 0.784 & 0.099\\
+\bottomrule
+\end{tabular}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:p-tab18}Fit Estimates for Partial Invariance Loadings for Small Residual Data}
+
+\begin{tabular}{lll}
+\toprule
+Estimated Parameter & CFI & RSMEA\\
+\midrule
+q1 \textasciitilde{}\textasciitilde{} q1 & 0.928 & 0.056\\
+q2 \textasciitilde{}\textasciitilde{} q2 & 0.936 & 0.053\\
+q3 \textasciitilde{}\textasciitilde{} q3 & 0.926 & 0.057\\
+q4 \textasciitilde{}\textasciitilde{} q4 & 0.955 & 0.044\\
+q5 \textasciitilde{}\textasciitilde{} q5 & 0.926 & 0.057\\
+lv \textasciitilde{}\textasciitilde{} lv & 0.930 & 0.054\\
+\bottomrule
+\end{tabular}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:p-tab19}Fit Estimates for Partial Invariance Loadings for Medium Residual Data}
+
+\begin{tabular}{lll}
+\toprule
+Estimated Parameter & CFI & RSMEA\\
+\midrule
+q1 \textasciitilde{}\textasciitilde{} q1 & 0.869 & 0.075\\
+q2 \textasciitilde{}\textasciitilde{} q2 & 0.860 & 0.078\\
+q3 \textasciitilde{}\textasciitilde{} q3 & 0.870 & 0.075\\
+q4 \textasciitilde{}\textasciitilde{} q4 & 0.994 & 0.016\\
+q5 \textasciitilde{}\textasciitilde{} q5 & 0.862 & 0.077\\
+lv \textasciitilde{}\textasciitilde{} lv & 0.864 & 0.075\\
+\bottomrule
+\end{tabular}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:p-tab20}Fit Estimates for Partial Invariance Loadings for Large Residual Data}
+
+\begin{tabular}{lll}
+\toprule
+Estimated Parameter & CFI & RSMEA\\
+\midrule
+q1 \textasciitilde{}\textasciitilde{} q1 & 0.558 & 0.140\\
+q2 \textasciitilde{}\textasciitilde{} q2 & 0.559 & 0.140\\
+q3 \textasciitilde{}\textasciitilde{} q3 & 0.560 & 0.140\\
+q4 \textasciitilde{}\textasciitilde{} q4 & 0.972 & 0.035\\
+q5 \textasciitilde{}\textasciitilde{} q5 & 0.559 & 0.140\\
+lv \textasciitilde{}\textasciitilde{} lv & 0.562 & 0.137\\
+\bottomrule
+\end{tabular}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\newpage
+
+\hypertarget{invariance-plots-difference-scores-by-condition}{%
+\subsection{Invariance Plots Difference Scores by Condition}\label{invariance-plots-difference-scores-by-condition}}
+
+\includegraphics{manuscript_files/figure-latex/inv-plots-condition-1.pdf} \includegraphics{manuscript_files/figure-latex/inv-plots-condition-2.pdf} \includegraphics{manuscript_files/figure-latex/inv-plots-condition-3.pdf} \includegraphics{manuscript_files/figure-latex/inv-plots-condition-4.pdf} \includegraphics{manuscript_files/figure-latex/inv-plots-condition-5.pdf} \includegraphics{manuscript_files/figure-latex/inv-plots-condition-6.pdf} \includegraphics{manuscript_files/figure-latex/inv-plots-condition-7.pdf} \includegraphics{manuscript_files/figure-latex/inv-plots-condition-8.pdf} \includegraphics{manuscript_files/figure-latex/inv-plots-condition-9.pdf} \includegraphics{manuscript_files/figure-latex/inv-plots-condition-10.pdf}
+
+\hypertarget{invariance-plots-effect-sizes-by-condition}{%
+\subsection{Invariance Plots Effect Sizes by Condition}\label{invariance-plots-effect-sizes-by-condition}}
+
+\includegraphics{manuscript_files/figure-latex/inv-effect-condition-1.pdf} \includegraphics{manuscript_files/figure-latex/inv-effect-condition-2.pdf} \includegraphics{manuscript_files/figure-latex/inv-effect-condition-3.pdf} \includegraphics{manuscript_files/figure-latex/inv-effect-condition-4.pdf} \includegraphics{manuscript_files/figure-latex/inv-effect-condition-5.pdf} \includegraphics{manuscript_files/figure-latex/inv-effect-condition-6.pdf} \includegraphics{manuscript_files/figure-latex/inv-effect-condition-7.pdf} \includegraphics{manuscript_files/figure-latex/inv-effect-condition-8.pdf} \includegraphics{manuscript_files/figure-latex/inv-effect-condition-9.pdf} \includegraphics{manuscript_files/figure-latex/inv-effect-condition-10.pdf}
+
+\hypertarget{density-plots-by-condition}{%
+\subsection{Density Plots by Condition}\label{density-plots-by-condition}}
+
+\includegraphics{manuscript_files/figure-latex/density-effects-condition-1.pdf} \includegraphics{manuscript_files/figure-latex/density-effects-condition-2.pdf} \includegraphics{manuscript_files/figure-latex/density-effects-condition-3.pdf} \includegraphics{manuscript_files/figure-latex/density-effects-condition-4.pdf} \includegraphics{manuscript_files/figure-latex/density-effects-condition-5.pdf} \includegraphics{manuscript_files/figure-latex/density-effects-condition-6.pdf} \includegraphics{manuscript_files/figure-latex/density-effects-condition-7.pdf} \includegraphics{manuscript_files/figure-latex/density-effects-condition-8.pdf} \includegraphics{manuscript_files/figure-latex/density-effects-condition-9.pdf} \includegraphics{manuscript_files/figure-latex/density-effects-condition-10.pdf}
+
 \end{document}

### 2023-10-16 simulate_combine.Rmd
all the updates

---
title: "Put Together Simulations"
author: "Erin M. Buchanan"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Libraries

```{r}
library(rio)
library(dplyr)
```

## Boot RR Simulations

```{r}
full_boot <- 
  bind_rows(  
    import("data/boot_rr_DF_1a_mac.csv") %>% mutate(computer = paste0("computer1_", run_number)),
    import("data/boot_rr_DF_37_mac.csv") %>% mutate(computer = paste0("computer2_", run_number)),
    import("data/boot_rr_DF_5_sim1.csv") %>% mutate(computer = paste0("computer3_", run_number)), 
    import("data/boot_rr_DF_5_sim2.csv") %>% mutate(computer = paste0("computer4_", run_number)),
    import("data/boot_rr_DF_5_sim3.csv") %>% mutate(computer = paste0("computer5_", run_number)),
    import("data/boot_rr_DF_5_sim4.csv") %>% mutate(computer = paste0("computer6_", run_number)),
    import("data/boot_rr_DF_5_sim5.csv") %>% mutate(computer = paste0("computer7_", run_number)),
    import("data/boot_rr_DF_5_sim6.csv") %>% mutate(computer = paste0("computer8_", run_number)),
    import("data/boot_rr_DF_5_sim7.csv") %>% mutate(computer = paste0("computer9_", run_number)),
    import("data/boot_rr_DF_5_sim8.csv") %>% mutate(computer = paste0("computer10_", run_number)),
    import("data/boot_rr_DF_5_sim9.csv") %>% mutate(computer = paste0("computer11_", run_number)),
    import("data/boot_rr_DF_18_sim10.csv") %>% mutate(computer = paste0("computer12_", run_number)),
    import("data/boot_rr_DF_1_sim10.csv") %>% mutate(computer = paste0("computer13_", run_number)),
    import("data/boot_rr_DF_1_erin.csv") %>% mutate(computer = paste0("computer14_", run_number)),
    import("data/boot_rr_DF_2_erin.csv") %>% mutate(computer = paste0("computer15_", run_number)),
    import("data/boot_rr_DF_16_erin.csv") %>% mutate(computer = paste0("computer16_", run_number))
    )

nrow(full_boot)/30

length(table(full_boot$computer))

export(full_boot, "manu_data/boot_rr_DF.csv", row.names = F)
```

## Boot Partial Simulations

```{r}
boot_DF_full <- bind_rows(
  import("data/boot_DF_DF_sim11.csv") %>% mutate(computer = "computer11"),
  import("data/boot_DF_DF_sim12.csv") %>% mutate(computer = "computer12"),
  import("data/boot_DF_DF_sim13.csv") %>% mutate(computer = "computer13"),
  import("data/boot_DF_DF_sim14.csv") %>% mutate(computer = "computer14"),
  import("data/boot_DF_DF_sim15.csv") %>% mutate(computer = "computer15"),
  import("data/boot_DF_DF_sim16.csv") %>% mutate(computer = "computer16"),
  import("data/boot_DF_DF_sim17.csv") %>% mutate(computer = "computer17"),
  import("data/boot_DF_DF_sim18.csv") %>% mutate(computer = "computer18"),
  import("data/boot_DF_DF_sim19.csv") %>% mutate(computer = "computer19"),
  import("data/boot_DF_DF_sim20.csv") %>% mutate(computer = "computer20")
  )

export(boot_DF_full, "manu_data/boot_DF_full.csv", row.names = F)

boot_effects_summary_DF_full <- bind_rows(
  import("data/boot_effects_summary_DF_sim11.csv") %>% mutate(computer = "computer11"),
  import("data/boot_effects_summary_DF_sim12.csv") %>% mutate(computer = "computer12"),
  import("data/boot_effects_summary_DF_sim13.csv") %>% mutate(computer = "computer13"),
  import("data/boot_effects_summary_DF_sim14.csv") %>% mutate(computer = "computer14"),
  import("data/boot_effects_summary_DF_sim15.csv") %>% mutate(computer = "computer15"),
  import("data/boot_effects_summary_DF_sim16.csv") %>% mutate(computer = "computer16"),
  import("data/boot_effects_summary_DF_sim17.csv") %>% mutate(computer = "computer17"),
  import("data/boot_effects_summary_DF_sim18.csv") %>% mutate(computer = "computer18"),
  import("data/boot_effects_summary_DF_sim19.csv") %>% mutate(computer = "computer19"),
  import("data/boot_effects_summary_DF_sim20.csv") %>% mutate(computer = "computer20")
  )

export(boot_effects_summary_DF_full, "manu_data/boot_effects_summary_DF_full.csv", row.names = F)

boot_partial_summary_full <- bind_rows(
  import("data/boot_partial_summary_DF_sim11.csv") %>% mutate(computer = "computer11"),
  import("data/boot_partial_summary_DF_sim12.csv") %>% mutate(computer = "computer12"),
  import("data/boot_partial_summary_DF_sim13.csv") %>% mutate(computer = "computer13"),
  import("data/boot_partial_summary_DF_sim14.csv") %>% mutate(computer = "computer14"),
  import("data/boot_partial_summary_DF_sim15.csv") %>% mutate(computer = "computer15"),
  import("data/boot_partial_summary_DF_sim16.csv") %>% mutate(computer = "computer16"),
  import("data/boot_partial_summary_DF_sim17.csv") %>% mutate(computer = "computer17"),
  import("data/boot_partial_summary_DF_sim18.csv") %>% mutate(computer = "computer18"),
  import("data/boot_partial_summary_DF_sim19.csv") %>% mutate(computer = "computer19"),
  import("data/boot_partial_summary_DF_sim20.csv") %>% mutate(computer = "computer20")
  )

export(boot_partial_summary_full, "manu_data/boot_partial_summary_DF_full.csv", row.names = F)
```

### 2023-10-17 appendix_2.Rmd
making figures

@@
 
-## MGCFA Model Fit Statistics
+# MGCFA Model Fit Statistics
 
-Model fit statistics are provided for each of the ten model combinations (invariant, three sizes for each ladings, intercepts, and residuals).
+Model fit statistics are provided for each of the ten model combinations (invariant, three sizes for each loadings, intercepts, and residuals).
 These tables could be used to examine the traditional change in fit statistics cutoff rules of thumb [@cheung2002], such as $\Delta$ CFI or $\Delta$ RMSEA, to the visualizations presented in the manuscript.
@@
 apa_table(results.invariant$model_fit %>% 
-            dplyr::select(model, AIC, BIC, cfi, tli, rmsea, srmr),
+            dplyr::select(model, AIC, BIC, cfi, tli, rmsea, srmr) %>% 
+            mutate(model = tools::toTitleCase(model)),
           digits = 3, 
@@
 apa_table(results.small.load$model_fit %>% 
-            dplyr::select(model, AIC, BIC, cfi, tli, rmsea, srmr), 
+            dplyr::select(model, AIC, BIC, cfi, tli, rmsea, srmr) %>% 
+            mutate(model = tools::toTitleCase(model)), 
           digits = 3, 
@@
 apa_table(results.med.load$model_fit %>% 
-            dplyr::select(model, AIC, BIC, cfi, tli, rmsea, srmr), 
+            dplyr::select(model, AIC, BIC, cfi, tli, rmsea, srmr) %>% 
+            mutate(model = tools::toTitleCase(model)), 
           digits = 3, 
@@
 apa_table(results.large.load$model_fit %>% 
-            dplyr::select(model, AIC, BIC, cfi, tli, rmsea, srmr),
+            dplyr::select(model, AIC, BIC, cfi, tli, rmsea, srmr) %>% 
+            mutate(model = tools::toTitleCase(model)),
           digits = 3, 
@@
 apa_table(results.small.int$model_fit %>% 
-            dplyr::select(model, AIC, BIC, cfi, tli, rmsea, srmr), 
+            dplyr::select(model, AIC, BIC, cfi, tli, rmsea, srmr) %>% 
+            mutate(model = tools::toTitleCase(model)), 
           digits = 3, 
@@
 apa_table(results.med.int$model_fit %>% 
-            dplyr::select(model, AIC, BIC, cfi, tli, rmsea, srmr),
+            dplyr::select(model, AIC, BIC, cfi, tli, rmsea, srmr) %>% 
+            mutate(model = tools::toTitleCase(model)),
           digits = 3, 
@@
 apa_table(results.large.int$model_fit %>% 
-            dplyr::select(model, AIC, BIC, cfi, tli, rmsea, srmr),
+            dplyr::select(model, AIC, BIC, cfi, tli, rmsea, srmr) %>% 
+            mutate(model = tools::toTitleCase(model)),
           digits = 3, 
@@
 apa_table(results.small.res$model_fit %>% 
-            dplyr::select(model, AIC, BIC, cfi, tli, rmsea, srmr), 
+            dplyr::select(model, AIC, BIC, cfi, tli, rmsea, srmr) %>% 
+            mutate(model = tools::toTitleCase(model)), 
           digits = 3, 
@@
 apa_table(results.med.res$model_fit %>% 
-            dplyr::select(model, AIC, BIC, cfi, tli, rmsea, srmr), 
+            dplyr::select(model, AIC, BIC, cfi, tli, rmsea, srmr) %>% 
+            mutate(model = tools::toTitleCase(model)), 
           digits = 3, 
@@
 apa_table(results.large.res$model_fit %>% 
-            dplyr::select(model, AIC, BIC, cfi, tli, rmsea, srmr), 
+            dplyr::select(model, AIC, BIC, cfi, tli, rmsea, srmr) %>% 
+            mutate(model = tools::toTitleCase(model)), 
           digits = 3, 

### 2023-10-17 manuscript.Rmd
making figures

@@
 library(visualizemi)
+library(patchwork)
 
@@
 
-The output from this function are several *ggplot2* objects that can be edited or saved directly using *ggplot2* functionality [@R-ggplot2].
+The outputs from this function are several *ggplot2* objects that can be edited or saved directly using *ggplot2* functionality [@R-ggplot2].
 
@@
 invariant.plot$complete
+
+ggsave("figures/invariant-visual.png", dpi = 300, 
+       width = 8, 
+       units = "in")
 ```
@@
 )$complete
+
+ggsave("figures/small-load-visual.png", dpi = 300, 
+       width = 8, 
+       units = "in")
 ```
@@
 )$complete
+
+ggsave("figures/med-load-visual.png", dpi = 300, 
+       width = 8, 
+       units = "in")
 ```
@@
 )$complete
+
+ggsave("figures/large-load-visual.png", dpi = 300, 
+       width = 8, 
+       units = "in")
 ```
@@
 )$complete
+
+ggsave("figures/small-int-visual.png", dpi = 300, 
+       width = 8, 
+       units = "in")
 ```
@@
 )$complete
+
+ggsave("figures/med-int-visual.png", dpi = 300, 
+       width = 8, 
+       units = "in")
 ```
@@
 )$complete
+
+ggsave("figures/large-int-visual.png", dpi = 300, 
+       width = 8, 
+       units = "in")
 ```
@@
 )$complete
+
+ggsave("figures/small-res-visual.png", dpi = 300, 
+       width = 8, 
+       units = "in")
 ```
@@
 )$complete
+
+ggsave("figures/med-res-visual.png", dpi = 300, 
+       width = 8, 
+       units = "in")
 ```
@@
 )$complete
+
+ggsave("figures/large-res-visual.png", dpi = 300, 
+       width = 8, 
+       units = "in")
 ```
@@
 1) `saved_configural`: a saved fitted model at the configural level with no equality constraints.
-This model should include all other *lavaan* settings you would like to use, such as `estimator` or `ordered`.
+This model should include all other lavaan settings you would like to use, such as estimator or ordered.
+2) `data`: The dataframe where the model was estimated. 
+3) `model`: The model syntax for the overall model.
+4) `group`: The grouping variable column in the dataframe. 
+5) `nboot`: The number of bootstraps to run. 
+6) `invariance_index`: The fit index you would like to use to determine invariance. Please use options and labeling from *lavaan* - see `fitmeasures()` for options. 
+7) `invariance_rule`: The invariance difference score you would like to use as your rule. 
+8) `group.equal`: The equality constraints including in your original multi-group tests.
 
@@
 means_invariant <- boot_rr_DF %>% filter(type == "Invariant") %>% group_by(model) %>% summarize(mean_h = mean(h_nmi_p))
+
+ggsave("figures/prop-boot-rr.png", dpi = 300, 
+       width = 8, 
+       units = "in")
 ```
@@
 boot.partial.invariant$invariance_plot
+
+ggsave("figures/boot-partial-invariance.png", dpi = 300, 
+       width = 8, 
+       units = "in")
 ```
@@
 suppressMessages(boot.partial.invariant$density_plot)
+
+ggsave("figures/boot-partial-density.png", dpi = 300, 
+       width = 8, 
+       units = "in")
 ```
@@
 boot.partial.invariant$effect_invariance_plot
+
+ggsave("figures/boot-partial-effects.png", dpi = 300, 
+       width = 8, 
+       units = "in")
 ```
@@
 suppressWarnings(effect_invariance_plot)
+
+ggsave("figures/partial-large-loading-effect.png", dpi = 300, 
+       width = 8, 
+       units = "in")
 ```
@@
 suppressMessages(density_plot)
+
+ggsave("figures/partial-large-loading-density.png", dpi = 300, 
+       width = 8, 
+       units = "in")
 ```
@@
 apa_table(results.rs$model_fit %>% 
-        dplyr::select(model, AIC, BIC, cfi, tli, rmsea, srmr), 
+        dplyr::select(model, AIC, BIC, cfi, tli, rmsea, srmr) %>% 
+          mutate(model = tools::toTitleCase(model)), 
         digits = 3, 
@@
 By examining our estimates, we can see that item seven on the RS-14 is estimated at nearly 5 points for the clinical sample, while the student sample has a lower mean around 4.5 points.
-Generally, students show higher means on the items of the RS14, but when all loadings and other intercepts are constrained to be equal, and this one item is relaxed, this pattern flips so that clinical groups show higher item intercepts.
+Generally, students show higher means on the items of the RS-14, but when all loadings and other intercepts are constrained to be equal, and this one item is relaxed, this pattern flips so that clinical groups show higher item intercepts.
 Given the scale is a 1-7 Likert type scale, .5 a point represents a potentially sizable change on the scale.
@@
 )$complete
+
+ggsave("figures/rs7-visual.png", dpi = 300, 
+       width = 8, 
+       units = "in")
 ```
@@
 )$complete
+
+ggsave("figures/rs6-visual.png", dpi = 300, 
+       width = 8, 
+       units = "in")
 ```
@@
 ```{r table-boot-effects, results='asis'}
-apa_table(boot.partial.rs$boot_effects,
+apa_table(boot.partial.rs$boot_effects %>% 
+            dplyr::select(term, non_invariant, random_non_invariant, h_nmi, h_nmi_p) %>% 
+            mutate(term = gsub("~1", " Intercept", term)),
+          col.names = c("Term", "Non-Invariant", "Random Non-Invariant", 
+                        "$h_{nmi}$", "$h_{nmi_p}$"),
+          escape = F,
           digits = 3, 
@@
 
-```{r rs-partial-pic, include = T, fig.cap="RS14 scale invariance for item intercepts.
+```{r rs-partial-pic, include = T, fig.cap="RS-14 scale invariance for item intercepts.
 The left panel indicates the raw score difference between groups and items, while the right panel indicates the effect size for group differences based on invariance."}
 
-plot_grid(
-  boot.partial.rs$invariance_plot,
-  boot.partial.rs$effect_invariance_plot)
-```
-
-```{r rs-partial-pic2, include = T, fig.cap = "RS14 scale invariance density plots, illustrating invariant versus non-invariant bootstrapped and random runs for each parameter."}
+legend_all <- get_legend(boot.partial.rs$effect_invariance_plot +
+                           theme(legend.direction = "horizontal",
+                                 legend.justification="center",
+                                 legend.box.just = "bottom"))
+
+(boot.partial.rs$invariance_plot + theme(legend.position = "none") + boot.partial.rs$effect_invariance_plot + theme(legend.position = "none")) /  
+  legend_all
+
+ggsave("figures/rs-boot-partial.png", dpi = 300, 
+       width = 8, 
+       units = "in")
+```
+
+```{r rs-partial-pic2, include = T, fig.cap = "RS-14 scale invariance density plots, illustrating invariant versus non-invariant bootstrapped and random runs for each parameter."}
 suppressMessages((boot.partial.rs$density_plot))
+
+ggsave("figures/rs-boot-density.png", dpi = 300, 
+       width = 8, 
+       units = "in")
 ```

### 2023-10-17 manuscript.tex
making figures

@@
 
-The output from this function are several \emph{ggplot2} objects that can be edited or saved directly using \emph{ggplot2} functionality (Wickham, 2016).
+The outputs from this function are several \emph{ggplot2} objects that can be edited or saved directly using \emph{ggplot2} functionality (Wickham, 2016).
 
@@
   \texttt{saved\_configural}: a saved fitted model at the configural level with no equality constraints.
-This model should include all other \emph{lavaan} settings you would like to use, such as \texttt{estimator} or \texttt{ordered}.
+This model should include all other lavaan settings you would like to use, such as estimator or ordered.
+\item
+  \texttt{data}: The dataframe where the model was estimated.
+\item
+  \texttt{model}: The model syntax for the overall model.
+\item
+  \texttt{group}: The grouping variable column in the dataframe.
+\item
+  \texttt{nboot}: The number of bootstraps to run.
+\item
+  \texttt{invariance\_index}: The fit index you would like to use to determine invariance. Please use options and labeling from \emph{lavaan} - see \texttt{fitmeasures()} for options.
+\item
+  \texttt{invariance\_rule}: The invariance difference score you would like to use as your rule.
+\item
+  \texttt{group.equal}: The equality constraints including in your original multi-group tests.
 \end{enumerate}
@@
 Configural & 122,118.406 & 122,617.055 & 0.926 & 0.912 & 0.102 & 0.036\\
-loadings & 122,144.532 & 122,566.010 & 0.925 & 0.918 & 0.098 & 0.043\\
-intercepts & 122,544.109 & 122,888.415 & 0.911 & 0.910 & 0.103 & 0.052\\
-residuals & 126,466.241 & 126,727.438 & 0.780 & 0.793 & 0.156 & 0.086\\
+Loadings & 122,144.532 & 122,566.010 & 0.925 & 0.918 & 0.098 & 0.043\\
+Intercepts & 122,544.109 & 122,888.415 & 0.911 & 0.910 & 0.103 & 0.052\\
+Residuals & 126,466.241 & 126,727.438 & 0.780 & 0.793 & 0.156 & 0.086\\
 \bottomrule
@@
 Next, we would examine the strength of the effects of replication on each parameter at the intercept level.
-By examining \ref{tab:table-boot-effects}, it is clear that most of the item means are unlikely to replicate, even though two particular items can be used to create partial invariance.
+By examining Table \ref{tab:table-boot-effects}, it is clear that most of the item means are unlikely to replicate, even though two particular items can be used to create partial invariance.
 Figures \ref{fig:rs-partial-pic} and \ref{fig:rs-partial-pic2} display the three plots provided in the \texttt{bootstrap\_partial()} function.
@@
 
-\begin{tabular}{lllllll}
+\begin{tabular}{lllll}
 \toprule
-term & \multicolumn{1}{c}{non\_invariant} & \multicolumn{1}{c}{random\_non\_invariant} & \multicolumn{1}{c}{h\_nmi} & \multicolumn{1}{c}{h\_mi} & \multicolumn{1}{c}{h\_nmi\_p} & \multicolumn{1}{c}{h\_mi\_p}\\
+Term & Non-Invariant & Random Non-Invariant & $h_{nmi}$ & $h_{nmi_p}$\\
 \midrule
-RS \textasciitilde{}1 & 0.991 & 0.007 & 2.784 & -2.784 & 0.886 & -0.886\\
-RS1 \textasciitilde{}1 & 0.989 & 0.007 & 2.764 & -2.764 & 0.880 & -0.880\\
-RS10 \textasciitilde{}1 & 0.988 & 0.007 & 2.755 & -2.755 & 0.877 & -0.877\\
-RS11 \textasciitilde{}1 & 0.991 & 0.007 & 2.784 & -2.784 & 0.886 & -0.886\\
-RS12 \textasciitilde{}1 & 0.991 & 0.007 & 2.784 & -2.784 & 0.886 & -0.886\\
-RS13 \textasciitilde{}1 & 0.991 & 0.007 & 2.784 & -2.784 & 0.886 & -0.886\\
-RS14 \textasciitilde{}1 & 0.990 & 0.007 & 2.774 & -2.774 & 0.883 & -0.883\\
-RS2 \textasciitilde{}1 & 0.985 & 0.007 & 2.728 & -2.728 & 0.869 & -0.869\\
-RS3 \textasciitilde{}1 & 0.988 & 0.007 & 2.755 & -2.755 & 0.877 & -0.877\\
-RS4 \textasciitilde{}1 & 0.990 & 0.007 & 2.774 & -2.774 & 0.883 & -0.883\\
-RS5 \textasciitilde{}1 & 0.984 & 0.007 & 2.720 & -2.720 & 0.866 & -0.866\\
-RS6 \textasciitilde{}1 & 0.979 & 0.007 & 2.683 & -2.683 & 0.854 & -0.854\\
-RS7 \textasciitilde{}1 & 0.974 & 0.007 & 2.650 & -2.650 & 0.844 & -0.844\\
-RS8 \textasciitilde{}1 & 0.991 & 0.007 & 2.784 & -2.784 & 0.886 & -0.886\\
-RS9 \textasciitilde{}1 & 0.987 & 0.007 & 2.746 & -2.746 & 0.874 & -0.874\\
+RS  Intercept & 0.991 & 0.007 & 2.784 & 0.886\\
+RS1  Intercept & 0.989 & 0.007 & 2.764 & 0.880\\
+RS10  Intercept & 0.988 & 0.007 & 2.755 & 0.877\\
+RS11  Intercept & 0.991 & 0.007 & 2.784 & 0.886\\
+RS12  Intercept & 0.991 & 0.007 & 2.784 & 0.886\\
+RS13  Intercept & 0.991 & 0.007 & 2.784 & 0.886\\
+RS14  Intercept & 0.990 & 0.007 & 2.774 & 0.883\\
+RS2  Intercept & 0.985 & 0.007 & 2.728 & 0.869\\
+RS3  Intercept & 0.988 & 0.007 & 2.755 & 0.877\\
+RS4  Intercept & 0.990 & 0.007 & 2.774 & 0.883\\
+RS5  Intercept & 0.984 & 0.007 & 2.720 & 0.866\\
+RS6  Intercept & 0.979 & 0.007 & 2.683 & 0.854\\
+RS7  Intercept & 0.974 & 0.007 & 2.650 & 0.844\\
+RS8  Intercept & 0.991 & 0.007 & 2.784 & 0.886\\
+RS9  Intercept & 0.987 & 0.007 & 2.746 & 0.874\\
 \bottomrule
@@
 \includegraphics{manuscript_files/figure-latex/rs-partial-pic-1.pdf}
-\caption{\label{fig:rs-partial-pic}RS14 scale invariance for item intercepts.
+\caption{\label{fig:rs-partial-pic}RS-14 scale invariance for item intercepts.
 The left panel indicates the raw score difference between groups and items, while the right panel indicates the effect size for group differences based on invariance.}
@@
 \includegraphics{manuscript_files/figure-latex/rs-partial-pic2-1.pdf}
-\caption{\label{fig:rs-partial-pic2}RS14 scale invariance density plots, illustrating invariant versus non-invariant bootstrapped and random runs for each parameter.}
+\caption{\label{fig:rs-partial-pic2}RS-14 scale invariance density plots, illustrating invariant versus non-invariant bootstrapped and random runs for each parameter.}
 \end{figure}
@@
 \hypertarget{simulating-from-models}{%
-\subsection{Simulating from models}\label{simulating-from-models}}
+\section{Simulating from models}\label{simulating-from-models}}
 
@@
 \hypertarget{simulating-from-matrices}{%
-\subsection{Simulating from matrices}\label{simulating-from-matrices}}
+\section{Simulating from matrices}\label{simulating-from-matrices}}
 
@@
 \hypertarget{mgcfa-model-fit-statistics}{%
-\subsection{MGCFA Model Fit Statistics}\label{mgcfa-model-fit-statistics}}
-
-Model fit statistics are provided for each of the ten model combinations (invariant, three sizes for each ladings, intercepts, and residuals).
+\section{MGCFA Model Fit Statistics}\label{mgcfa-model-fit-statistics}}
+
+Model fit statistics are provided for each of the ten model combinations (invariant, three sizes for each loadings, intercepts, and residuals).
 These tables could be used to examine the traditional change in fit statistics cutoff rules of thumb (Cheung \& Rensvold, 2002), such as \(\Delta\) CFI or \(\Delta\) RMSEA, to the visualizations presented in the manuscript.
@@
 Configural & 7,533.348 & 7,659.786 & 0.991 & 0.982 & 0.030 & 0.026\\
-loadings & 7,528.476 & 7,638.056 & 0.994 & 0.992 & 0.020 & 0.033\\
-intercepts & 7,522.397 & 7,615.118 & 1.000 & 1.003 & 0.000 & 0.035\\
-residuals & 7,520.435 & 7,592.083 & 0.991 & 0.992 & 0.020 & 0.046\\
+Loadings & 7,528.476 & 7,638.056 & 0.994 & 0.992 & 0.020 & 0.033\\
+Intercepts & 7,522.397 & 7,615.118 & 1.000 & 1.003 & 0.000 & 0.035\\
+Residuals & 7,520.435 & 7,592.083 & 0.991 & 0.992 & 0.020 & 0.046\\
 \bottomrule
@@
 Configural & 7,550.991 & 7,677.430 & 0.978 & 0.956 & 0.048 & 0.030\\
-loadings & 7,550.133 & 7,659.713 & 0.966 & 0.952 & 0.051 & 0.047\\
-intercepts & 7,542.675 & 7,635.397 & 0.979 & 0.977 & 0.035 & 0.047\\
-residuals & 7,534.091 & 7,605.739 & 0.993 & 0.994 & 0.019 & 0.054\\
+Loadings & 7,550.133 & 7,659.713 & 0.966 & 0.952 & 0.051 & 0.047\\
+Intercepts & 7,542.675 & 7,635.397 & 0.979 & 0.977 & 0.035 & 0.047\\
+Residuals & 7,534.091 & 7,605.739 & 0.993 & 0.994 & 0.019 & 0.054\\
 \bottomrule
@@
 Configural & 7,585.839 & 7,712.277 & 0.972 & 0.944 & 0.058 & 0.033\\
-loadings & 7,613.434 & 7,723.014 & 0.865 & 0.807 & 0.107 & 0.079\\
-intercepts & 7,606.648 & 7,699.370 & 0.874 & 0.860 & 0.091 & 0.079\\
-residuals & 7,600.057 & 7,671.705 & 0.880 & 0.895 & 0.079 & 0.091\\
+Loadings & 7,613.434 & 7,723.014 & 0.865 & 0.807 & 0.107 & 0.079\\
+Intercepts & 7,606.648 & 7,699.370 & 0.874 & 0.860 & 0.091 & 0.079\\
+Residuals & 7,600.057 & 7,671.705 & 0.880 & 0.895 & 0.079 & 0.091\\
 \bottomrule
@@
 Configural & 7,622.892 & 7,749.330 & 0.986 & 0.972 & 0.042 & 0.030\\
-loadings & 7,674.188 & 7,783.767 & 0.817 & 0.738 & 0.131 & 0.095\\
-intercepts & 7,667.682 & 7,760.403 & 0.824 & 0.805 & 0.113 & 0.096\\
-residuals & 7,683.177 & 7,754.825 & 0.762 & 0.793 & 0.116 & 0.138\\
+Loadings & 7,674.188 & 7,783.767 & 0.817 & 0.738 & 0.131 & 0.095\\
+Intercepts & 7,667.682 & 7,760.403 & 0.824 & 0.805 & 0.113 & 0.096\\
+Residuals & 7,683.177 & 7,754.825 & 0.762 & 0.793 & 0.116 & 0.138\\
 \bottomrule
@@
 Configural & 7,533.348 & 7,659.786 & 0.991 & 0.982 & 0.030 & 0.026\\
-loadings & 7,528.476 & 7,638.056 & 0.994 & 0.992 & 0.020 & 0.033\\
-intercepts & 7,526.312 & 7,619.034 & 0.987 & 0.986 & 0.027 & 0.040\\
-residuals & 7,524.356 & 7,596.005 & 0.975 & 0.978 & 0.033 & 0.050\\
+Loadings & 7,528.476 & 7,638.056 & 0.994 & 0.992 & 0.020 & 0.033\\
+Intercepts & 7,526.312 & 7,619.034 & 0.987 & 0.986 & 0.027 & 0.040\\
+Residuals & 7,524.356 & 7,596.005 & 0.975 & 0.978 & 0.033 & 0.050\\
 \bottomrule
@@
 Configural & 7,533.348 & 7,659.786 & 0.991 & 0.982 & 0.030 & 0.026\\
-loadings & 7,528.476 & 7,638.056 & 0.994 & 0.992 & 0.020 & 0.033\\
-intercepts & 7,544.002 & 7,636.724 & 0.917 & 0.907 & 0.068 & 0.059\\
-residuals & 7,542.064 & 7,613.712 & 0.905 & 0.917 & 0.065 & 0.067\\
+Loadings & 7,528.476 & 7,638.056 & 0.994 & 0.992 & 0.020 & 0.033\\
+Intercepts & 7,544.002 & 7,636.724 & 0.917 & 0.907 & 0.068 & 0.059\\
+Residuals & 7,542.064 & 7,613.712 & 0.905 & 0.917 & 0.065 & 0.067\\
 \bottomrule
@@
 Configural & 7,533.348 & 7,659.786 & 0.991 & 0.982 & 0.030 & 0.026\\
-loadings & 7,528.476 & 7,638.056 & 0.994 & 0.992 & 0.020 & 0.033\\
-intercepts & 7,574.054 & 7,666.776 & 0.797 & 0.775 & 0.106 & 0.084\\
-residuals & 7,572.174 & 7,643.823 & 0.785 & 0.813 & 0.097 & 0.090\\
+Loadings & 7,528.476 & 7,638.056 & 0.994 & 0.992 & 0.020 & 0.033\\
+Intercepts & 7,574.054 & 7,666.776 & 0.797 & 0.775 & 0.106 & 0.084\\
+Residuals & 7,572.174 & 7,643.823 & 0.785 & 0.813 & 0.097 & 0.090\\
 \bottomrule
@@
 Configural & 7,469.546 & 7,595.984 & 0.969 & 0.938 & 0.054 & 0.034\\
-loadings & 7,471.637 & 7,581.217 & 0.944 & 0.920 & 0.062 & 0.049\\
-intercepts & 7,465.722 & 7,558.443 & 0.952 & 0.946 & 0.051 & 0.051\\
-residuals & 7,465.986 & 7,537.635 & 0.930 & 0.939 & 0.054 & 0.065\\
+Loadings & 7,471.637 & 7,581.217 & 0.944 & 0.920 & 0.062 & 0.049\\
+Intercepts & 7,465.722 & 7,558.443 & 0.952 & 0.946 & 0.051 & 0.051\\
+Residuals & 7,465.986 & 7,537.635 & 0.930 & 0.939 & 0.054 & 0.065\\
 \bottomrule
@@
 Configural & 7,368.654 & 7,495.092 & 0.992 & 0.983 & 0.028 & 0.027\\
-loadings & 7,364.904 & 7,474.483 & 0.990 & 0.986 & 0.025 & 0.036\\
-intercepts & 7,358.503 & 7,451.224 & 1.000 & 1.001 & 0.000 & 0.037\\
-residuals & 7,385.958 & 7,457.607 & 0.864 & 0.881 & 0.075 & 0.098\\
+Loadings & 7,364.904 & 7,474.483 & 0.990 & 0.986 & 0.025 & 0.036\\
+Intercepts & 7,358.503 & 7,451.224 & 1.000 & 1.001 & 0.000 & 0.037\\
+Residuals & 7,385.958 & 7,457.607 & 0.864 & 0.881 & 0.075 & 0.098\\
 \bottomrule
@@
 Configural & 7,218.848 & 7,345.287 & 0.965 & 0.929 & 0.059 & 0.033\\
-loadings & 7,217.332 & 7,326.912 & 0.955 & 0.935 & 0.056 & 0.045\\
-intercepts & 7,211.566 & 7,304.287 & 0.962 & 0.958 & 0.046 & 0.047\\
-residuals & 7,304.566 & 7,376.215 & 0.562 & 0.619 & 0.137 & 0.189\\
+Loadings & 7,217.332 & 7,326.912 & 0.955 & 0.935 & 0.056 & 0.045\\
+Intercepts & 7,211.566 & 7,304.287 & 0.962 & 0.958 & 0.046 & 0.047\\
+Residuals & 7,304.566 & 7,376.215 & 0.562 & 0.619 & 0.137 & 0.189\\
 \bottomrule
@@
 
-\hypertarget{simulated-parital-invariance-results}{%
-\subsection{Simulated Parital Invariance Results}\label{simulated-parital-invariance-results}}
+\hypertarget{simulated-partial-invariance-results}{%
+\section{Simulated Partial Invariance Results}\label{simulated-partial-invariance-results}}
 
@@
 
-\newpage
-
 \hypertarget{invariance-plots-difference-scores-by-condition}{%
-\subsection{Invariance Plots Difference Scores by Condition}\label{invariance-plots-difference-scores-by-condition}}
+\section{Invariance Plots Difference Scores by Condition}\label{invariance-plots-difference-scores-by-condition}}
 
@@
 \hypertarget{invariance-plots-effect-sizes-by-condition}{%
-\subsection{Invariance Plots Effect Sizes by Condition}\label{invariance-plots-effect-sizes-by-condition}}
+\section{Invariance Plots Effect Sizes by Condition}\label{invariance-plots-effect-sizes-by-condition}}
 
@@
 \hypertarget{density-plots-by-condition}{%
-\subsection{Density Plots by Condition}\label{density-plots-by-condition}}
+\section{Density Plots by Condition}\label{density-plots-by-condition}}
 

### 2024-03-08 appendix_7.Rmd
revision 2

---
appendix: "appendix_7.Rmd"
---

## Replication Test

```{r setup}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

```{r libraries-appendix7, message = FALSE}
set.seed(890343)
library(rio)
library(dplyr)
library(visualizemi)
library(papaja)
library(tidyr)
library(dmacs)
library(ggplot2)
library(scales)
library(introdataviz)
library(lavaan)
```

## Data

```{r}
# our data
load("manu_data/RS14.Rdata")

DF <- DF

# take only interesting columns and give a label
DF <- DF %>% 
  # make it comparable by only testing students
  filter(DF$sample == "Student") %>% 
  mutate(group = "Schulenberg") %>% 
  dplyr::select(RS1:RS14, group)

# Chen et al.
DF.pone <- import("manu_data/data1-RS14.dta")
# take only interesting columns and give a label
DF.pone <- DF.pone %>% 
  dplyr::select(starts_with("rs")) %>% 
  mutate(group = "Chen")
# match column style
colnames(DF.pone)[1:14] <- toupper(colnames(DF.pone)[1:14])

# create one dataset
DF.combo <- bind_rows(DF, DF.pone)

DF.combo %>% 
  group_by(group) %>% 
  summarize(sample = n())
```

## MGCFA

```{r}
# build the one-factor model 
model.rs <- "RS =~ RS1+RS2+RS3+RS4+RS5+RS6+RS7+RS8+RS9+RS10+RS11+RS12+RS13+RS14"

# run the multi-group CFA
results.rs <- mgcfa(
  model = model.rs,
  data = DF.combo, 
  group = "group", 
  group.equal = c("loadings", "intercepts", "residuals")
  )

# examine the results
results.rs$model_fit %>% 
        dplyr::select(model, AIC, BIC, cfi, tli, rmsea, srmr)
```

Overall, the one-factor model fits the data well. Each group also shows adequate model fit. If we use $\Delta$CFI <= .01, we find that the loadings would be considered invariant across the English and Chinese samples. The intercepts were not invariant.

## Partial Invariance

```{r}
partial.rs <-
  partial_mi(
    saved_model = results.rs$invariance_models$model.intercepts,
    data = DF.combo,
    model = model.rs,
    group = "group",
    # be sure to do only up to the step you are interested in
    group.equal = c("loadings", "intercepts"),
    partial_step = "intercepts")

partial.rs$fit_table %>% 
  dplyr::select(free.parameter, cfi) %>% 
  arrange(-cfi)
```

Examining partial invariance reveals several potential candidates for partial invariance. In this next section, we relaxed group constraints until we achieved partial invariance (i.e., $\Delta$CFI <= .01). We will need to find our CFI as at least `r results.rs$model_fit %>% filter(model == "Configural") %>% pull(cfi) %>% apa_num() %>% as.numeric() - .01`. More than half the items are necessary to achieve "partial" invariance (which really implies no invariance is likely possible).

```{r}
# run the partially invariant model with group.partial
partial.rs.1 <- mgcfa(model = model.rs, 
                  data = DF.combo, 
                  group = "group", 
                  group.equal = c("loadings", "intercepts"),
                  group.partial = c("RS2 ~1", "RS11 ~1",
                                    "RS4 ~1", "RS12 ~1",
                                    "RS14 ~1", "RS1 ~1",
                                    "RS10 ~1", "RS3 ~ 1"),
                  meanstructure = TRUE)

# examine the fit indices 
partial.rs.1$model_fit %>% 
  filter(model == "intercepts") %>% 
  dplyr::select(AIC, BIC, cfi, tli, rmsea, srmr)

# examine the intercepts 
partial.rs.1$model_coef %>% 
  filter(model == "intercepts") %>% 
  dplyr::select(term, group, estimate) %>% 
  pivot_wider(id_cols = c("term"), 
              names_from = "group", 
              values_from = "estimate") %>% 
  dplyr::rename(English = `1`, 
                Chinese = `2`) %>% 
  filter(term %in% c("RS1 ~1 ", "RS12 ~1 ",
                     "RS7 ~1 ", "RS4 ~1 ",
                     "RS5 ~1 ", "RS3 ~1 "))

# effect size model 
round(lavaan_dmacs(partial.rs.1$invariance_models$model.intercepts, "Chen")$DMACS, 2)
```

## Visualize Invariance

```{r}
for (i in c("RS2", "RS11",
            "RS4", "RS12",
            "RS14", "RS1",
            "RS10", "RS3")){
  cat(paste0("Plot for ", i, "\n"))
  print(plot_mi(
    # output from model_coef
    data_coef = partial.rs.1$model_coef, 
    # which model do you want to plot
    model_step = "intercepts", 
    # name of observed item
    item_name = i, 
    # latent variable limits to graph
    x_limits = c(-1,1), 
    # Y min and max in data 
    y_limits = c(min(DF.combo[ , i]), max(DF.combo[ , i])),
    # what ci do you want
    conf.level = .95, 
    # what model results do you want 
    model_results = partial.rs.1$invariance_models$model.intercepts,
    # which latent variable do you want 
    lv_name = "RS" 
)$complete)

  ggsave(paste0("figures/rs14-chinese-", i, ".png"), 
         dpi = 300, 
         width = 8, 
         units = "in")

  cat(paste0("-------\n"))

}

```

## Bootstrap Model

```{r eval = F}
boot.model.rs <- 
  bootstrap_model(
    saved_configural = results.rs$model_configural,
    data = DF.combo,
    model = model.rs, 
    group = "group", 
    nboot = 1000, 
    invariance_index = "cfi",
    invariance_rule = .01, 
    group.equal = c("loadings", "intercepts")
)

boot.model.rs
```

```{r echo = F}
boot.model.rs <- import("manu_data/boot.model.rs.appendix7.csv")
boot.model.rs
```

In this case, we do not see loadings print out. That implies that all models in both real data and randomized data are invariant because the function only calculates information for non-invariance. We see that the intercepts are unlikely to ever replicate across Chinese and English samples. This result is not surprising given the large number of relaxed parameters required to achieve partial invariance.

## Bootstrap Partial Invariance

```{r eval = F, message = F}
boot.partial.rs <- 
  bootstrap_partial(
    saved_model = results.rs$invariance_models$model.intercepts,
    data = DF.combo,
    model = model.rs, 
    group = "group", 
    nboot = 1000, 
    invariance_index = "cfi",
    invariance_rule = .01, 
    invariance_compare = fitmeasures(results.rs$invariance_models$model.loadings, "cfi"), 
    partial_step = "intercepts",
    group.equal = c("loadings", "intercepts")
)
```

```{r echo = F}
load("manu_data/boot.partial.rs.appendix7.Rdata")
boot.partial.rs <- list(
  "boot_DF" = boot_DF,
  "boot_summary" = boot_summary,
  "density_plot" = density_plot, 
  "invariance_plot" = invariance_plot, 
  "boot_effects" = boot_effects, 
  "effect_invariance_plot" = effect_invariance_plot
)
```

### Each Parameter on the Overall Model Invariance

```{r}
boot.partial.rs$boot_effects
```

In this output, we see that all the bootstrapped runs of the real data are non-invariant, even when each parameter is relaxed individually. A few runs of the random data are *non*-invariant (meaning most are actually invariant when randomized). This indicates that no one parameter is likely the reason for non-invariance, as they all show large non-replication effects. If we use the `boot_summary`, we can see the effect size for each parameter when the two intercepts are compared to each other (as the chart above shows the overall model invariance effect).

### Each Parameter's Standardized Difference Score

```{r}
boot.partial.rs$boot_summary
```

With the bootstrap summary, we see that no invariant intercept runs are found. Note that the `RS~1` does not calculate *d* because the *sd* is zero (thus, this would cause an error as *sd* is part of the denominator). The random runs also do not show a *d* score because the effect size is only calculated when at least 10% of the runs in `n_boot` or `n_random` are found. Since we only have 10 or 11 in that column, no effect size is calculated. The differences in the intercepts for the real data (`boot` columns) appear to be medium to large, showing *d* scores from 0.3 to 0.6. Therefore, we might expect that the English and Chinese samples have different average endorsement levels of the RS14.

```{r}
boot.partial.rs$density_plot

ggsave(paste0("figures/rs14-chinese-density_plot.png"), 
       dpi = 300, 
       width = 8, 
       units = "in")
```

The examination of the density plot shows how group 1 (Schulenberg English) tends to show lower average scores than group 2 (Chen Chinese) for most but not all items.

We can view the mean difference or standardized mean difference by using:

```{r}
boot.partial.rs$invariance_plot

ggsave(paste0("figures/rs14-chinese-invariance_plot.png"), 
       dpi = 300, 
       width = 8, 
       units = "in")

boot.partial.rs$effect_invariance_plot

ggsave(paste0("figures/rs14-chinese-effect_invariance_plot.png"), 
       dpi = 300, 
       width = 8, 
       units = "in")
```

When effects are non-invariant in the randomized data, the mean difference is still fairly small, but we see large mean differences in intercepts when the bootstrapped data is non-invariant. In the effect size graph, we can see that this effect is medium to large for all the parameters.

### 2024-03-08 manuscript.Rmd
revision 2

@@
   - "appendix_6.Rmd"
+  - "appendix_7.Rmd"
 ---
@@
 
-The `bootstrap_rr` function in *visualizemi* was designed to estimate the likely replication of overall model invariance with the assumption that the data used for the estimation represents the larger population.
+The `bootstrap_model` function in *visualizemi* was designed to estimate the likely replication of overall model invariance with the assumption that the data used for the estimation represents the larger population.
 The following arguments are used:
@@
 boot.model.invariant <- 
-  bootstrap_rr(
+  bootstrap_model(
     # saved configural model 
@@
 $$h_{nmi} = 2 \times (asin\sqrt{p_{data}} - asin\sqrt{p_{random}})$$
+
 The alternative, $h_{mi}$, for effect size of measurement invariance replication would simply be the inverse sign of $h_{nmi}$ and is also included in the table.
@@
 partial.rs.2$model_coef %>% 
-  filter(term == "RS6 ~1 ") %>% 
+  filter(term == "RS6 ~1") %>% 
   filter(model == "intercepts") %>% 
@@
 boot.model.rs <- 
-  bootstrap_rr(
+  bootstrap_model(
     saved_configural = results.rs$model_configural,
@@
 In summary, if one were planning a replication, the prediction would be that item intercepts would likely not replicate, with a large effect size (i.e., it is easy to judge $h_{nmi_p}$ close to the max of one as large).
-While this study found partial invariance by relaxing constraints on two individual items, bootstrapped partial invariance indicates that any item could potentially be problematic with an effect size averaging $d$ ~ 0.50 difference in means.
+While this study found partial invariance by relaxing constraints on two individual items, bootstrapped partial invariance indicates that any item could potentially be problematic with an effect size averaging $d$ \~ 0.50 difference in means.
 While $d_{MACS}$ values represented a "small" effect based on previous publications, this effect may be muted by examining both loadings and intercepts.
@@
 The overall average score on items is high: $M_M$ = `r apa_num(mean(apply(DF[ , -ncol(DF)], 2, mean)))` ($M_{SD}$ = `r apa_num(mean(apply(DF[ , -ncol(DF)], 2, sd)))`).
-Given the mean standard deviation, a $d$ ~ 0.50 represents `r apa_num(mean(apply(DF[ , -ncol(DF)], 2, sd))/2)` or nearly one whole point on the scale.
+Given the mean standard deviation, a $d$ \~ 0.50 represents `r apa_num(mean(apply(DF[ , -ncol(DF)], 2, sd))/2)` or nearly one whole point on the scale.
 A researcher could decide that at least $d$ = 0.33 or at least a third of a standard deviation would be an important change and set that as their smallest effect size of interest for invariance.
@@
 
+## An Example Extension
+
+One benefit of the open science movement on scale development is the publication of datasets or covariance tables with published articles.
+We can extend our examination of potential replication on other variables that may effect assessment of underlying phenomena.
+For example, scale translation across languages is not only impacted by the literal conversion of concepts from one language to another, but also the cultural and societal norms of the target population [@cha2007; @yu2004; @chang1999].
+The RS14 was tested in Chinese speaking samples in @chen2020 across five different large samples and determined that the scale showed good psychometric properties for use within Chinese speaking samples as a one-factor model of resiliency.
+Given these results, another researcher may assume that the models would be comparable between English speaking (i.e., likely United States) and Chinese speaking samples.
+With the published data, we can use `visualizemi` to determine if the RS14 is invariant across language/culture, and if the results would likely replicate if tested on a new set of samples, and what, if any, effect size differences are found in parameters.
+The code used for this analysis is presented in Appendix 7.
+
+The @aiena2014 data used in our previous example was first filtered to only college students, as we have already noted that clinical samples show slightly different intercepts for at least two of the items from student samples.
+The @chen2020 data also included college students, which allows us to test a comparable sample that varies on translation and culture.
+The test of measurement invariance indicated that the factor structure and loadings were invariant across groups.
+Much like our test of clinical versus student samples, the results indicated that the intercepts were not consistent across groups.
+Within the English clinical/student sample, partial invariance could be achieved by relaxing two item intercept constraints (item 6 and 7).
+To achieve "partial" invariance between the Chinese and English speaking samples, we would need to relax more than half of the items (specifically, eight items: 1, 2, 3, 4, 10, 11, 12, 14), and it would be difficult to suggest partial invariance given this finding.
+$d_{MACS}$ values range from 0.26 to 0.32 for the eight items which could be interpreted a small to medium given @nye2019's simulation study.
+Figure \@ref(fig:rs14-chinese-pic) portrays the results from the second item on the RS14 (*life accomplishments*).
+
+The results of model bootstrapping indicated that the effect of the loadings was likely to replicate (only invariant results were found), but the intercepts were never found to be invariant compared to a randomized sample ($h_{nmi_p}$ = 1).
+Therefore, we would expect that these differences are persistent, either due to the adaptation or cultural differences in resiliency across samples.
+The bootstrapped partial invariance demonstrates that each item intercept has a medium to large difference between the two samples as shown in Figure \@ref(fig:rs14-chinese-effect-pic), which may explain why full or partial invariance cannot be achieved.
+This result does not invalidate either version of the scale, but informs researchers of potential baseline differences in item responding for the two samples.
+Therefore, careful interpretation should be made when comparing these two samples in other instances, as differences in latent means may be the default finding, but with these results one may determine if their results are different from expectations of general scale responding.
+
+```{r rs14-chinese-pic, include = T, fig.cap = "The differences in intercepts for the second item on the Rs14 by language sample.
+The differences between intercepts are shown on the left hand side with a clear separation between lines.
+The latent means also show a clear difference between groups where the English group appears to have lower scores overall than the Chinese group."}
+knitr::include_graphics("figures/rs14-chinese-RS2.png")
+```
+
+```{r rs14-chinese-effect-pic, include = T, fig.cap = ""}
+knitr::include_graphics("figures/rs14-chinese-effect_invariance_plot.png")
+```
+
 # Discussion
@@
 They could plan and pre-register a smallest effect of interest.
-For example, we may determine that an $h_{nmi_p}$ value above .20 represents an important level of non-invariance for our model overall, while $h_{nmi_p}$ > .30 for any individual parameter warrant caution against invariance for groups.
+For example, we may determine that an $h_{nmi_p}$ value above .20 represents an important level of non-invariance for our model overall, while $h_{nmi_p}$ \> .30 for any individual parameter warrant caution against invariance for groups.
 Others have begun to discuss the importance of focusing on effects in the scale of the data and their practical importance [@cumming2012; @anvari2021].
@@
 Even the smaller difference of .5 point on each individual item could translate into increases in resiliency, and these results may elucidate avenues for further exploration into areas of focus within resiliency, given the items.
+The secondary example showed that we can extend these results to other samples to examine other potentially impactful variables on assessment.
+The findings replicate in the sense that the scale shows the same invariant issues with intercepts on a Chinese versus English sample comparison.
+However, in this analysis, it is clear that the differences in items averages are much larger and across all items, rather than a few.
 
@@
 However, if both the effect size and a visual inspection of the invariance indicates a small difference, we may decide to lessen the practical importance of those results, much like "just significant" *p*-values with small effect sizes are treated now.
+The results from our Chinese versus English comparison show us the other scenario: non-invariant results that clearly indicate differences with a large effect size on both replication and item average differences.
 Given that the goal of measurement invariance is to compare *estimates*, we should expect some differences across samples due to the nature of sampling and estimation.
 It may be that many of the published models presented represent these effects - small variations between groups due to sampling error or other small crud - but do not represent a fundamental problem with the measurement or generalizability of the results.
+The `visualizemi` package is one useful tool to help sort out if findings are this small sampling error or differences in samples due to other variables.
 
@@
 
-# (APPENDIX) Appendix {-}
+# (APPENDIX) Appendix {.unnumbered}
 
@@
 ```
+
+```{r child = "appendix_7.Rmd"}
+
+```

### 2024-03-08 manuscript.tex
revision 2

@@
 
-The \texttt{bootstrap\_rr} function in \emph{visualizemi} was designed to estimate the likely replication of overall model invariance with the assumption that the data used for the estimation represents the larger population.
+The \texttt{bootstrap\_model} function in \emph{visualizemi} was designed to estimate the likely replication of overall model invariance with the assumption that the data used for the estimation represents the larger population.
 The following arguments are used:
@@
 \NormalTok{boot.model.invariant }\OtherTok{\textless{}{-}} 
-  \FunctionTok{bootstrap\_rr}\NormalTok{(}
+  \FunctionTok{bootstrap\_model}\NormalTok{(}
     \CommentTok{\# saved configural model }
@@
 \[h_{nmi} = 2 \times (asin\sqrt{p_{data}} - asin\sqrt{p_{random}})\]
+
 The alternative, \(h_{mi}\), for effect size of measurement invariance replication would simply be the inverse sign of \(h_{nmi}\) and is also included in the table.
@@
 \NormalTok{partial.rs}\FloatTok{.2}\SpecialCharTok{$}\NormalTok{model\_coef }\SpecialCharTok{\%\textgreater{}\%} 
-  \FunctionTok{filter}\NormalTok{(term }\SpecialCharTok{==} \StringTok{"RS6 \textasciitilde{}1 "}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
+  \FunctionTok{filter}\NormalTok{(term }\SpecialCharTok{==} \StringTok{"RS6 \textasciitilde{}1"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
   \FunctionTok{filter}\NormalTok{(model }\SpecialCharTok{==} \StringTok{"intercepts"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
@@
 \begin{verbatim}
-## # A tibble: 2 x 4
-##   term      group estimate std.error
-##   <chr>     <int>    <dbl>     <dbl>
-## 1 "RS6 ~1 "     1     5.00    0.0605
-## 2 "RS6 ~1 "     2     4.54    0.0533
+## # A tibble: 0 x 4
+## # i 4 variables: term <chr>, group <int>, estimate <dbl>, std.error <dbl>
 \end{verbatim}
@@
 \NormalTok{boot.model.rs }\OtherTok{\textless{}{-}} 
-  \FunctionTok{bootstrap\_rr}\NormalTok{(}
+  \FunctionTok{bootstrap\_model}\NormalTok{(}
     \AttributeTok{saved\_configural =}\NormalTok{ results.rs}\SpecialCharTok{$}\NormalTok{model\_configural,}
@@
 
+\hypertarget{an-example-extension}{%
+\subsection{An Example Extension}\label{an-example-extension}}
+
+One benefit of the open science movement on scale development is the publication of datasets or covariance tables with published articles.
+We can extend our examination of potential replication on other variables that may effect assessment of underlying phenomena.
+For example, scale translation across languages is not only impacted by the literal conversion of concepts from one language to another, but also the cultural and societal norms of the target population (Cha et al., 2007; Chang et al., 1999; Yu et al., 2004).
+The RS14 was tested in Chinese speaking samples in Chen et al.
+(2020) across five different large samples and determined that the scale showed good psychometric properties for use within Chinese speaking samples as a one-factor model of resiliency.
+Given these results, another researcher may assume that the models would be comparable between English speaking (i.e., likely United States) and Chinese speaking samples.
+With the published data, we can use \texttt{visualizemi} to determine if the RS14 is invariant across language/culture, and if the results would likely replicate if tested on a new set of samples, and what, if any, effect size differences are found in parameters.
+The code used for this analysis is presented in Appendix 7.
+
+The Aiena et al.
+(2014) data used in our previous example was first filtered to only college students, as we have already noted that clinical samples show slightly different intercepts for at least two of the items from student samples.
+The Chen et al.
+(2020) data also included college students, which allows us to test a comparable sample that varies on translation and culture.
+The test of measurement invariance indicated that the factor structure and loadings were invariant across groups.
+Much like our test of clinical versus student samples, the results indicated that the intercepts were not consistent across groups.
+Within the English clinical/student sample, partial invariance could be achieved by relaxing two item intercept constraints (item 6 and 7).
+To achieve ``partial'' invariance between the Chinese and English speaking samples, we would need to relax more than half of the items (specifically, eight items: 1, 2, 3, 4, 10, 11, 12, 14), and it would be difficult to suggest partial invariance given this finding.
+\(d_{MACS}\) values range from 0.26 to 0.32 for the eight items which could be interpreted a small to medium given Nye et al.
+(2019)'s simulation study.
+Figure \ref{fig:rs14-chinese-pic} portrays the results from the second item on the RS14 (\emph{life accomplishments}).
+
+The results of model bootstrapping indicated that the effect of the loadings was likely to replicate (only invariant results were found), but the intercepts were never found to be invariant compared to a randomized sample (\(h_{nmi_p}\) = 1).
+Therefore, we would expect that these differences are persistent, either due to the adaptation or cultural differences in resiliency across samples.
+The bootstrapped partial invariance demonstrates that each item intercept has a medium to large difference between the two samples as shown in Figure \ref{fig:rs14-chinese-effect-pic}, which may explain why full or partial invariance cannot be achieved.
+This result does not invalidate either version of the scale, but informs researchers of potential baseline differences in item responding for the two samples.
+Therefore, careful interpretation should be made when comparing these two samples in other instances, as differences in latent means may be the default finding, but with these results one may determine if their results are different from expectations of general scale responding.
+
+\begin{figure}
+\includegraphics[width=8in]{figures/rs14-chinese-RS2} \caption{The differences in intercepts for the second item on the Rs14 by language sample.
+The differences between intercepts are shown on the left hand side with a clear separation between lines.
+The latent means also show a clear difference between groups where the English group appears to have lower scores overall than the Chinese group.}\label{fig:rs14-chinese-pic}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=8in]{figures/rs14-chinese-effect_invariance_plot} \end{figure}
+
 \hypertarget{discussion}{%
@@
 However, if both the effect size and a visual inspection of the invariance indicates a small difference, we may decide to lessen the practical importance of those results, much like ``just significant'' \emph{p}-values with small effect sizes are treated now.
+The results from our Chinese versus English comparison show us the other scenario: non-invariant results that clearly indicate differences with a large effect size on both replication and item average differences.
 Given that the goal of measurement invariance is to compare \emph{estimates}, we should expect some differences across samples due to the nature of sampling and estimation.
 It may be that many of the published models presented represent these effects - small variations between groups due to sampling error or other small crud - but do not represent a fundamental problem with the measurement or generalizability of the results.
+The \texttt{visualizemi} package is one useful tool to help sort out if findings are this small sampling error or differences in samples due to other variables.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-cha2007}{}}%
+Cha, E.-S., Kim, K.
+H., \& Erlen, J.
+A.
+(2007).
+Translation of scales in cross{-}cultural research: issues and techniques.
+\emph{Journal of Advanced Nursing}, \emph{58}(4), 386--395.
+\url{https://doi.org/10.1111/j.1365-2648.2007.04242.x}
+
+\leavevmode\vadjust pre{\hypertarget{ref-chang1999}{}}%
+Chang, A.
+M., Chau, J.
+P.
+C., \& Holroyd, E.
+(1999).
+Translation of questionnaires and issues of equivalence.
+\emph{Journal of Advanced Nursing}, \emph{29}(2), 316--322.
+\url{https://doi.org/10.1046/j.1365-2648.1999.00891.x}
+
+\leavevmode\vadjust pre{\hypertarget{ref-chen2020}{}}%
+Chen, W., Xie, E., Tian, X., \& Zhang, G.
+(2020).
+Psychometric properties of the Chinese version of the Resilience Scale (RS-14): Preliminary results.
+\emph{PLOS ONE}, \emph{15}(10), e0241606.
+\url{https://doi.org/10.1371/journal.pone.0241606}
+
 \leavevmode\vadjust pre{\hypertarget{ref-cheung2002}{}}%
@@
 Wilke, C. O. (2020). \emph{Cowplot: Streamlined plot theme and plot annotations for 'ggplot2'}. \url{https://CRAN.R-project.org/package=cowplot}
+
+\leavevmode\vadjust pre{\hypertarget{ref-yu2004}{}}%
+Yu, D.
+S.
+F., Lee, D.
+T.
+F., \& Woo, J.
+(2004).
+Issues and Challenges of Instrument Translation.
+\emph{Western Journal of Nursing Research}, \emph{26}(3), 307--320.
+\url{https://doi.org/10.1177/0193945903260554}
 
@@
 
+\hypertarget{replication-test}{%
+\subsection{Replication Test}\label{replication-test}}
+
+\hypertarget{data}{%
+\subsection{Data}\label{data}}
+
+\begin{verbatim}
+## # A tibble: 2 x 2
+##   group       sample
+##   <chr>        <int>
+## 1 Chen          1010
+## 2 Schulenberg   1765
+\end{verbatim}
+
+\hypertarget{mgcfa}{%
+\subsection{MGCFA}\label{mgcfa}}
+
+\begin{verbatim}
+## # A tibble: 7 x 7
+##   model                 AIC     BIC   cfi   tli  rmsea   srmr
+##   <chr>               <dbl>   <dbl> <dbl> <dbl>  <dbl>  <dbl>
+## 1 Overall           113442. 113608. 0.939 0.928 0.0890 0.0344
+## 2 Group Schulenberg  69101.  69254. 0.928 0.915 0.108  0.0353
+## 3 Group Chen         42603.  42741. 0.929 0.916 0.0766 0.0399
+## 4 Configural        111760. 112258. 0.929 0.916 0.0975 0.0347
+## 5 loadings          111789. 112210. 0.927 0.921 0.0946 0.0427
+## 6 intercepts        112785. 113129. 0.892 0.891 0.111  0.0599
+## 7 residuals         113318. 113579. 0.873 0.880 0.116  0.0661
+\end{verbatim}
+
+Overall, the one-factor model fits the data well.
+Each group also shows adequate model fit.
+If we use \(\Delta\)CFI \textless= .01, we find that the loadings would be considered invariant across the English and Chinese samples.
+The intercepts were not invariant.
+
+\hypertarget{partial-invariance}{%
+\subsection{Partial Invariance}\label{partial-invariance}}
+
+\begin{verbatim}
+## # A tibble: 15 x 2
+##    free.parameter cfi       
+##    <chr>          <lvn.vctr>
+##  1 "RS2 ~1 "      0.8970997 
+##  2 "RS11 ~1 "     0.8963948 
+##  3 "RS4 ~1 "      0.8961938 
+##  4 "RS12 ~1 "     0.8960095 
+##  5 "RS14 ~1 "     0.8954496 
+##  6 "RS1 ~1 "      0.8954215 
+##  7 "RS10 ~1 "     0.8953395 
+##  8 "RS3 ~1 "      0.8948455 
+##  9 "RS5 ~1 "      0.8945236 
+## 10 "RS7 ~1 "      0.8941450 
+## 11 "RS8 ~1 "      0.8920022 
+## 12 "RS13 ~1 "     0.8919491 
+## 13 "RS9 ~1 "      0.8919293 
+## 14 "RS ~1 "       0.8917757 
+## 15 "RS6 ~1 "      0.8917604
+\end{verbatim}
+
+Examining partial invariance reveals several potential candidates for partial invariance.
+In this next section, we relaxed group constraints until we achieved partial invariance (i.e., \(\Delta\)CFI \textless= .01).
+We will need to find our CFI as at least 0.92.
+More than half the items are necessary to achieve ``partial'' invariance (which really implies no invariance is likely possible).
+
+\begin{verbatim}
+## # A tibble: 1 x 6
+##       AIC     BIC   cfi   tli  rmsea   srmr
+##     <dbl>   <dbl> <dbl> <dbl>  <dbl>  <dbl>
+## 1 111935. 112326. 0.922 0.917 0.0966 0.0462
+\end{verbatim}
+
+\begin{verbatim}
+## # A tibble: 6 x 3
+##   term       English Chinese
+##   <chr>        <dbl>   <dbl>
+## 1 "RS1 ~1 "     5.24    4.78
+## 2 "RS3 ~1 "     5.14    5.46
+## 3 "RS4 ~1 "     5.29    5.71
+## 4 "RS5 ~1 "     5.13    5.13
+## 5 "RS7 ~1 "     5.26    5.26
+## 6 "RS12 ~1 "    5.57    5.16
+\end{verbatim}
+
+\begin{verbatim}
+##  RS1  RS2  RS3  RS4  RS5  RS6  RS7  RS8  RS9 RS10 RS11 RS12 RS13 RS14 
+## 0.32 0.29 0.23 0.30 0.00 0.00 0.00 0.00 0.00 0.29 0.27 0.29 0.00 0.26
+\end{verbatim}
+
+\hypertarget{visualize-invariance}{%
+\subsection{Visualize Invariance}\label{visualize-invariance}}
+
+\begin{verbatim}
+## Plot for RS2
+\end{verbatim}
+
+\includegraphics{manuscript_files/figure-latex/unnamed-chunk-103-1.pdf}
+
+\begin{verbatim}
+## -------
+## Plot for RS11
+\end{verbatim}
+
+\includegraphics{manuscript_files/figure-latex/unnamed-chunk-103-2.pdf}
+
+\begin{verbatim}
+## -------
+## Plot for RS4
+\end{verbatim}
+
+\includegraphics{manuscript_files/figure-latex/unnamed-chunk-103-3.pdf}
+
+\begin{verbatim}
+## -------
+## Plot for RS12
+\end{verbatim}
+
+\includegraphics{manuscript_files/figure-latex/unnamed-chunk-103-4.pdf}
+
+\begin{verbatim}
+## -------
+## Plot for RS14
+\end{verbatim}
+
+\includegraphics{manuscript_files/figure-latex/unnamed-chunk-103-5.pdf}
+
+\begin{verbatim}
+## -------
+## Plot for RS1
+\end{verbatim}
+
+\includegraphics{manuscript_files/figure-latex/unnamed-chunk-103-6.pdf}
+
+\begin{verbatim}
+## -------
+## Plot for RS10
+\end{verbatim}
+
+\includegraphics{manuscript_files/figure-latex/unnamed-chunk-103-7.pdf}
+
+\begin{verbatim}
+## -------
+## Plot for RS3
+\end{verbatim}
+
+\includegraphics{manuscript_files/figure-latex/unnamed-chunk-103-8.pdf}
+
+\begin{verbatim}
+## -------
+\end{verbatim}
+
+\hypertarget{bootstrap-model}{%
+\subsection{Bootstrap Model}\label{bootstrap-model}}
+
+\begin{verbatim}
+##        model non_invariant random_non_invariant    h_nmi      h_mi h_nmi_p
+## 1 intercepts             1                    0 3.141593 -3.141593       1
+##   h_mi_p
+## 1     -1
+\end{verbatim}
+
+In this case, we do not see loadings print out.
+That implies that all models in both real data and randomized data are invariant because the function only calculates information for non-invariance.
+We see that the intercepts are unlikely to ever replicate across Chinese and English samples.
+This result is not surprising given the large number of relaxed parameters required to achieve partial invariance.
+
+\hypertarget{bootstrap-partial-invariance}{%
+\subsection{Bootstrap Partial Invariance}\label{bootstrap-partial-invariance}}
+
+\hypertarget{each-parameter-on-the-overall-model-invariance}{%
+\subsubsection{Each Parameter on the Overall Model Invariance}\label{each-parameter-on-the-overall-model-invariance}}
+
+\begin{verbatim}
+## # A tibble: 15 x 7
+##    term       non_invariant random_non_invariant h_nmi  h_mi h_nmi_p h_mi_p
+##    <chr>              <dbl>                <dbl> <dbl> <dbl>   <dbl>  <dbl>
+##  1 "RS ~1 "           0.991                0.007  2.78 -2.78   0.886 -0.886
+##  2 "RS1 ~1 "          0.989                0.007  2.76 -2.76   0.880 -0.880
+##  3 "RS10 ~1 "         0.988                0.007  2.75 -2.75   0.877 -0.877
+##  4 "RS11 ~1 "         0.991                0.007  2.78 -2.78   0.886 -0.886
+##  5 "RS12 ~1 "         0.991                0.007  2.78 -2.78   0.886 -0.886
+##  6 "RS13 ~1 "         0.991                0.007  2.78 -2.78   0.886 -0.886
+##  7 "RS14 ~1 "         0.99                 0.007  2.77 -2.77   0.883 -0.883
+##  8 "RS2 ~1 "          0.985                0.007  2.73 -2.73   0.869 -0.869
+##  9 "RS3 ~1 "          0.988                0.007  2.75 -2.75   0.877 -0.877
+## 10 "RS4 ~1 "          0.99                 0.007  2.77 -2.77   0.883 -0.883
+## 11 "RS5 ~1 "          0.984                0.007  2.72 -2.72   0.866 -0.866
+## 12 "RS6 ~1 "          0.979                0.007  2.68 -2.68   0.854 -0.854
+## 13 "RS7 ~1 "          0.974                0.007  2.65 -2.65   0.844 -0.844
+## 14 "RS8 ~1 "          0.991                0.007  2.78 -2.78   0.886 -0.886
+## 15 "RS9 ~1 "          0.987                0.007  2.75 -2.75   0.874 -0.874
+\end{verbatim}
+
+In this output, we see that all the bootstrapped runs of the real data are non-invariant, even when each parameter is relaxed individually.
+A few runs of the random data are \emph{non}-invariant (meaning most are actually invariant when randomized).
+This indicates that no one parameter is likely the reason for non-invariance, as they all show large non-replication effects.
+If we use the \texttt{boot\_summary}, we can see the effect size for each parameter when the two intercepts are compared to each other (as the chart above shows the overall model invariance effect).
+
+\hypertarget{each-parameters-standardized-difference-score}{%
+\subsubsection{Each Parameter's Standardized Difference Score}\label{each-parameters-standardized-difference-score}}
+
+\begin{verbatim}
+## # A tibble: 30 x 26
+## # Groups:   term, invariant [30]
+##    term       invariant mean_boot_1 mean_boot_2 sd_boot_1 sd_boot_2
+##    <chr>      <lgl>           <dbl>       <dbl>     <dbl>     <dbl>
+##  1 "RS ~1 "   FALSE            0        -0.121      0        0.623 
+##  2 "RS ~1 "   TRUE             0        -0.0110     0        0.680 
+##  3 "RS1 ~1 "  FALSE            3.33      3.11       0.529    0.123 
+##  4 "RS1 ~1 "  TRUE             3.34      3.07       0.550    0.112 
+##  5 "RS10 ~1 " FALSE            3.35      3.01       0.740    0.286 
+##  6 "RS10 ~1 " TRUE             3.37      2.95       0.725    0.268 
+##  7 "RS11 ~1 " FALSE            2.88      2.70       0.489    0.0510
+##  8 "RS11 ~1 " TRUE             2.79      2.68       0.528    0.0281
+##  9 "RS12 ~1 " FALSE            3.42      3.12       0.657    0.197 
+## 10 "RS12 ~1 " TRUE             3.30      3.08       0.733    0.183 
+## # i 20 more rows
+## # i 20 more variables: mean_boot_difference <dbl>, sd_boot_difference <dbl>,
+## #   mean_boot_fit <dbl>, sd_boot_fit <dbl>, n_boot <int>, mean_random_1 <dbl>,
+## #   mean_random_2 <dbl>, sd_random_1 <dbl>, sd_random_2 <dbl>,
+## #   mean_random_difference <dbl>, sd_random_difference <dbl>,
+## #   mean_random_fit <dbl>, sd_random_fit <dbl>, n_random <int>,
+## #   d_boot_low <dbl>, d_boot <dbl>, d_boot_high <dbl>, d_random_low <dbl>, ...
+\end{verbatim}
+
+With the bootstrap summary, we see that no invariant intercept runs are found.
+Note that the \texttt{RS\textasciitilde{}1} does not calculate \emph{d} because the \emph{sd} is zero (thus, this would cause an error as \emph{sd} is part of the denominator).
+The random runs also do not show a \emph{d} score because the effect size is only calculated when at least 10\% of the runs in \texttt{n\_boot} or \texttt{n\_random} are found.
+Since we only have 10 or 11 in that column, no effect size is calculated.
+The differences in the intercepts for the real data (\texttt{boot} columns) appear to be medium to large, showing \emph{d} scores from 0.3 to 0.6.
+Therefore, we might expect that the English and Chinese samples have different average endorsement levels of the RS14.
+
+\includegraphics{manuscript_files/figure-latex/unnamed-chunk-110-1.pdf}
+
+The examination of the density plot shows how group 1 (Schulenberg English) tends to show lower average scores than group 2 (Chen Chinese) for most but not all items.
+
+We can view the mean difference or standardized mean difference by using:
+
+\includegraphics{manuscript_files/figure-latex/unnamed-chunk-111-1.pdf} \includegraphics{manuscript_files/figure-latex/unnamed-chunk-111-2.pdf}
+
+When effects are non-invariant in the randomized data, the mean difference is still fairly small, but we see large mean differences in intercepts when the bootstrapped data is non-invariant.
+In the effect size graph, we can see that this effect is medium to large for all the parameters.
+
 \end{document}

### 2024-03-08 appendix_7.Rmd
whew

@@
 ```{r setup}
-knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
+knitr::opts_chunk$set(echo = TRUE, include = TRUE,
+                      message = FALSE, warning = FALSE, size = "small")
 ```
@@
 boot.model.rs <- import("manu_data/boot.model.rs.appendix7.csv")
-boot.model.rs
+boot.model.rs %>% 
+  dplyr::select(model, non_invariant, random_non_invariant, 
+         h_nmi, h_nmi_p)
 ```
@@
 ```{r}
-boot.partial.rs$boot_effects
+boot.partial.rs$boot_effects %>% 
+  dplyr::select(term, non_invariant, random_non_invariant, 
+         h_nmi, h_nmi_p)
 ```
@@
 ```{r}
-boot.partial.rs$boot_summary
+boot.partial.rs$boot_summary %>% 
+  dplyr::select(term, invariant, n_boot, d_boot)
+
+boot.partial.rs$boot_summary %>% 
+  dplyr::select(term, invariant, n_random, d_random)
 ```
 
-With the bootstrap summary, we see that no invariant intercept runs are found.
+With the bootstrap summary, we see that no invariant intercept runs are found (not all columns shown to save space).
 Note that the `RS~1` does not calculate *d* because the *sd* is zero (thus, this would cause an error as *sd* is part of the denominator).
 The random runs also do not show a *d* score because the effect size is only calculated when at least 10% of the runs in `n_boot` or `n_random` are found.
-Since we only have 10 or 11 in that column, no effect size is calculated.
+Since we only have a few in that column, no effect size is calculated.
 The differences in the intercepts for the real data (`boot` columns) appear to be medium to large, showing *d* scores from 0.3 to 0.6.

### 2024-03-08 manuscript.Rmd
whew

@@
 
-```{r rs14-chinese-pic, include = T, fig.cap = "The differences in intercepts for the second item on the Rs14 by language sample.
+```{r rs14-chinese-pic, include = T, fig.cap = "The differences in intercepts for the second item on the RS14 by language sample.
 The differences between intercepts are shown on the left hand side with a clear separation between lines.
 The latent means also show a clear difference between groups where the English group appears to have lower scores overall than the Chinese group."}
-knitr::include_graphics("figures/rs14-chinese-RS2.png")
-```
-
-```{r rs14-chinese-effect-pic, include = T, fig.cap = ""}
-knitr::include_graphics("figures/rs14-chinese-effect_invariance_plot.png")
+load("manu_data/fig-chinese-rs2.Rdata")
+complete
+```
+
+```{r rs14-chinese-effect-pic, fig.width = 6, include = T, fig.cap = "Effect size differences for item intercepts on the English versus Chinese samples for the RS14.", warnings = FALSE, message = FALSE}
+load("manu_data/boot.partial.rs.appendix7.Rdata")
+effect_invariance_plot
 ```
@@
 ```{r child = "appendix_7.Rmd"}
-
-```
+```

### 2024-03-08 manuscript.tex
whew

@@
 \begin{figure}
-\includegraphics[width=8in]{figures/rs14-chinese-RS2} \caption{The differences in intercepts for the second item on the Rs14 by language sample.
+\centering
+\includegraphics{manuscript_files/figure-latex/rs14-chinese-pic-1.pdf}
+\caption{\label{fig:rs14-chinese-pic}The differences in intercepts for the second item on the RS14 by language sample.
 The differences between intercepts are shown on the left hand side with a clear separation between lines.
-The latent means also show a clear difference between groups where the English group appears to have lower scores overall than the Chinese group.}\label{fig:rs14-chinese-pic}
+The latent means also show a clear difference between groups where the English group appears to have lower scores overall than the Chinese group.}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=8in]{figures/rs14-chinese-effect_invariance_plot} \end{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/rs14-chinese-effect-pic-1.pdf}
+\caption{\label{fig:rs14-chinese-effect-pic}Effect size differences for item intercepts on the English versus Chinese samples for the RS14.}
+\end{figure}
 
@@
 \begin{verbatim}
-##        model non_invariant random_non_invariant    h_nmi      h_mi h_nmi_p
-## 1 intercepts             1                    0 3.141593 -3.141593       1
-##   h_mi_p
-## 1     -1
+##        model non_invariant random_non_invariant    h_nmi h_nmi_p
+## 1 intercepts             1                    0 3.141593       1
 \end{verbatim}
@@
 \begin{verbatim}
-## # A tibble: 15 x 7
-##    term       non_invariant random_non_invariant h_nmi  h_mi h_nmi_p h_mi_p
-##    <chr>              <dbl>                <dbl> <dbl> <dbl>   <dbl>  <dbl>
-##  1 "RS ~1 "           0.991                0.007  2.78 -2.78   0.886 -0.886
-##  2 "RS1 ~1 "          0.989                0.007  2.76 -2.76   0.880 -0.880
-##  3 "RS10 ~1 "         0.988                0.007  2.75 -2.75   0.877 -0.877
-##  4 "RS11 ~1 "         0.991                0.007  2.78 -2.78   0.886 -0.886
-##  5 "RS12 ~1 "         0.991                0.007  2.78 -2.78   0.886 -0.886
-##  6 "RS13 ~1 "         0.991                0.007  2.78 -2.78   0.886 -0.886
-##  7 "RS14 ~1 "         0.99                 0.007  2.77 -2.77   0.883 -0.883
-##  8 "RS2 ~1 "          0.985                0.007  2.73 -2.73   0.869 -0.869
-##  9 "RS3 ~1 "          0.988                0.007  2.75 -2.75   0.877 -0.877
-## 10 "RS4 ~1 "          0.99                 0.007  2.77 -2.77   0.883 -0.883
-## 11 "RS5 ~1 "          0.984                0.007  2.72 -2.72   0.866 -0.866
-## 12 "RS6 ~1 "          0.979                0.007  2.68 -2.68   0.854 -0.854
-## 13 "RS7 ~1 "          0.974                0.007  2.65 -2.65   0.844 -0.844
-## 14 "RS8 ~1 "          0.991                0.007  2.78 -2.78   0.886 -0.886
-## 15 "RS9 ~1 "          0.987                0.007  2.75 -2.75   0.874 -0.874
+##        term non_invariant random_non_invariant    h_nmi  h_nmi_p
+## 1    RS ~1              1                0.002 3.052120 0.971520
+## 2   RS1 ~1              1                0.001 3.078337 0.979865
+## 3  RS10 ~1              1                0.002 3.052120 0.971520
+## 4  RS11 ~1              1                0.002 3.052120 0.971520
+## 5  RS12 ~1              1                0.002 3.052120 0.971520
+## 6  RS13 ~1              1                0.002 3.052120 0.971520
+## 7  RS14 ~1              1                0.002 3.052120 0.971520
+## 8   RS2 ~1              1                0.002 3.052120 0.971520
+## 9   RS3 ~1              1                0.002 3.052120 0.971520
+## 10  RS4 ~1              1                0.002 3.052120 0.971520
+## 11  RS5 ~1              1                0.002 3.052120 0.971520
+## 12  RS6 ~1              1                0.002 3.052120 0.971520
+## 13  RS7 ~1              1                0.001 3.078337 0.979865
+## 14  RS8 ~1              1                0.002 3.052120 0.971520
+## 15  RS9 ~1              1                0.002 3.052120 0.971520
 \end{verbatim}
@@
 \begin{verbatim}
-## # A tibble: 30 x 26
-## # Groups:   term, invariant [30]
-##    term       invariant mean_boot_1 mean_boot_2 sd_boot_1 sd_boot_2
-##    <chr>      <lgl>           <dbl>       <dbl>     <dbl>     <dbl>
-##  1 "RS ~1 "   FALSE            0        -0.121      0        0.623 
-##  2 "RS ~1 "   TRUE             0        -0.0110     0        0.680 
-##  3 "RS1 ~1 "  FALSE            3.33      3.11       0.529    0.123 
-##  4 "RS1 ~1 "  TRUE             3.34      3.07       0.550    0.112 
-##  5 "RS10 ~1 " FALSE            3.35      3.01       0.740    0.286 
-##  6 "RS10 ~1 " TRUE             3.37      2.95       0.725    0.268 
-##  7 "RS11 ~1 " FALSE            2.88      2.70       0.489    0.0510
-##  8 "RS11 ~1 " TRUE             2.79      2.68       0.528    0.0281
-##  9 "RS12 ~1 " FALSE            3.42      3.12       0.657    0.197 
-## 10 "RS12 ~1 " TRUE             3.30      3.08       0.733    0.183 
-## # i 20 more rows
-## # i 20 more variables: mean_boot_difference <dbl>, sd_boot_difference <dbl>,
-## #   mean_boot_fit <dbl>, sd_boot_fit <dbl>, n_boot <int>, mean_random_1 <dbl>,
-## #   mean_random_2 <dbl>, sd_random_1 <dbl>, sd_random_2 <dbl>,
-## #   mean_random_difference <dbl>, sd_random_difference <dbl>,
-## #   mean_random_fit <dbl>, sd_random_fit <dbl>, n_random <int>,
-## #   d_boot_low <dbl>, d_boot <dbl>, d_boot_high <dbl>, d_random_low <dbl>, ...
-\end{verbatim}
-
-With the bootstrap summary, we see that no invariant intercept runs are found.
+##        term invariant n_boot     d_boot
+## 1    RS ~1      FALSE   1000         NA
+## 2   RS1 ~1      FALSE   1000  0.2913872
+## 3  RS10 ~1      FALSE   1000  0.3596961
+## 4  RS11 ~1      FALSE   1000 -0.6589317
+## 5  RS12 ~1      FALSE   1000 -0.3010202
+## 6  RS13 ~1      FALSE   1000 -0.4005088
+## 7  RS14 ~1      FALSE   1000 -0.5665988
+## 8   RS2 ~1      FALSE   1000 -0.5540349
+## 9   RS3 ~1      FALSE   1000 -0.6218628
+## 10  RS4 ~1      FALSE   1000 -0.6245830
+## 11  RS5 ~1      FALSE   1000 -0.3334520
+## 12  RS6 ~1      FALSE   1000 -0.5014247
+## 13  RS7 ~1      FALSE   1000 -0.2381644
+## 14  RS8 ~1      FALSE   1000 -0.6333750
+## 15  RS9 ~1      FALSE   1000 -0.5986866
+\end{verbatim}
+
+\begin{verbatim}
+##        term invariant n_random d_random
+## 1    RS ~1      FALSE        2       NA
+## 2   RS1 ~1      FALSE        1       NA
+## 3  RS10 ~1      FALSE        2       NA
+## 4  RS11 ~1      FALSE        2       NA
+## 5  RS12 ~1      FALSE        2       NA
+## 6  RS13 ~1      FALSE        2       NA
+## 7  RS14 ~1      FALSE        2       NA
+## 8   RS2 ~1      FALSE        2       NA
+## 9   RS3 ~1      FALSE        2       NA
+## 10  RS4 ~1      FALSE        2       NA
+## 11  RS5 ~1      FALSE        2       NA
+## 12  RS6 ~1      FALSE        2       NA
+## 13  RS7 ~1      FALSE        1       NA
+## 14  RS8 ~1      FALSE        2       NA
+## 15  RS9 ~1      FALSE        2       NA
+\end{verbatim}
+
+With the bootstrap summary, we see that no invariant intercept runs are found (not all columns shown to save space).
 Note that the \texttt{RS\textasciitilde{}1} does not calculate \emph{d} because the \emph{sd} is zero (thus, this would cause an error as \emph{sd} is part of the denominator).
 The random runs also do not show a \emph{d} score because the effect size is only calculated when at least 10\% of the runs in \texttt{n\_boot} or \texttt{n\_random} are found.
-Since we only have 10 or 11 in that column, no effect size is calculated.
+Since we only have a few in that column, no effect size is calculated.
 The differences in the intercepts for the real data (\texttt{boot} columns) appear to be medium to large, showing \emph{d} scores from 0.3 to 0.6.

### 2024-03-09 manuscript.Rmd
finalizing paper

@@
 
-Therefore, purpose of this manuscript is describe an *R* package, `visualizemi`, that provides functionality to calculate multi-group confirmatory factor analysis, partial invariance tests, visualizations of the size of non-invariance, and potential effect sizes for overall models and individual parameters.
+Therefore, purpose of this manuscript is to describe an *R* package, `visualizemi`, that provides functionality to calculate multi-group confirmatory factor analysis, partial invariance tests, visualizations of the size of non-invariance, and potential effect sizes for overall models and individual parameters.
 No known visualization techniques have been proposed for measurement invariance.
-By creating panel visualizations, we can supplement a researchers ability to judge the strength of the non-invariance differences and effect size for each item.
+By creating panel visualizations, we can supplement a researcher's ability to judge the strength of the non-invariance differences and effect size for each item.
 The proposed effect sizes demonstrate the likelihood of replication with a similar sample as compared to a randomly assigned group model, thus, illustrating what type of measurement one might expect to find, and how different that is from random chance.
-Within this technique, the individual parameter effect sizes can calculated: both the group differences within a model as compared to random and the likelihood of a parameter replication compared to random groups.
+Within this technique, the individual parameter effect sizes can be calculated: both the group differences within a model as compared to random and the likelihood of a parameter replication compared to random groups.
 Coupled with other indicators (i.e., fit indices differences, $d_{MACS}$), we can move toward a better understanding of how much measurement non-invariance is meaningful.
@@
 
-1.  Learn how to use *visualizemi* to analyze multi-group confirmatory factor analysis, examine partial invariance, and create visualizations of parameters.
+1.  Learn how to use *visualizemi* to analyze multi-group confirmatory factor analysis, examine partial for invariance, and create visualizations of parameters.
 2.  Learn how to estimate the potential replication of multi-group models and their parameters using bootstrapping compared to a random group model.
@@
 1)  `complete`: The output from this model can be found in Figure \@ref(fig:invariant-pic).
-On the left hand side, the item invariance is plotted, and on the right hand side, the latent mean distributions for the two groups are plotted.
+On the left-hand side, the item invariance is plotted, and on the right-hand side, the latent mean distributions for the two groups are plotted.
 In the item invariance sub-plot, the visualization includes all three components traditionally seen in MGCFA testing steps: loadings, intercepts, and residuals.
@@
 
-2)  `intercept`: Only the left hand side of the complete plot designed to represent intercepts and factor loadings.
+2)  `intercept`: Only the left-hand side of the complete plot designed to represent intercepts and factor loadings.
 Factor loadings represent the slope of the regression equation for the latent variable predicting the scores on the observed variable ($\hat{Y} \sim b_0 + b_1X + \epsilon$).
@@
 
-3)  `mean`: The right hand side of the complete plot graphing the latent variable means and density from the data.
+3)  `mean`: The right-hand side of the complete plot graphing the latent variable means and density from the data.
 The latent variable is shown on the x-axis using standardized values (i.e., *z*-scores) where -1 indicates one standard deviation below the mean for the latent variable, 0 indicates the mean for the latent variable and so on.
@@
     # what equality constraints are you testing 
-    group.equal = c("loadings", "intercepts", "residuals")
+    group.equal = c("loadings", "intercepts", "resduals")
   )
@@
 
+```{r echo = F, eval = F}
+saveRDS(boot.partial.invariant, "manu_data/boot.partial.invariant.RData")
+```
+
 ```{r partial-boot-print, echo = T, size = "small"}
@@
 partial.rs.2$model_coef %>% 
-  filter(term == "RS6 ~1") %>% 
+  filter(term == "RS6 ~1 ") %>% 
   filter(model == "intercepts") %>% 
@@
 
+```{r}
+# saveRDS(boot.partial.rs, "manu_data/boot.partial.rs.RData")
+boot.partial.rs <- readRDS("manu_data/boot.partial.rs.RData")
+```
+
 ```{r table-boot-effects, results='asis'}
@@
 
+get_legend <- function(plot, legend = NULL) {
+
+    gt <- ggplotGrob(plot)
+
+    pattern <- "guide-box"
+    if (!is.null(legend)) {
+      pattern <- paste0(pattern, "-", legend)
+    }
+
+    indices <- grep(pattern, gt$layout$name)
+
+    not_empty <- !vapply(
+      gt$grobs[indices],
+      inherits, what = "zeroGrob",
+      FUN.VALUE = logical(1)
+    )
+    indices <- indices[not_empty]
+
+    if (length(indices) > 0) {
+      return(gt$grobs[[indices[1]]])
+    }
+    return(NULL)
+  }
+
 legend_all <- get_legend(boot.partial.rs$effect_invariance_plot +
@@
 ```{r rs14-chinese-pic, include = T, fig.cap = "The differences in intercepts for the second item on the RS14 by language sample.
-The differences between intercepts are shown on the left hand side with a clear separation between lines.
+The differences between intercepts are shown on the left-hand side with a clear separation between lines.
 The latent means also show a clear difference between groups where the English group appears to have lower scores overall than the Chinese group."}

### 2024-03-09 manuscript.tex
finalizing paper

@@
 
-Therefore, purpose of this manuscript is describe an \emph{R} package, \texttt{visualizemi}, that provides functionality to calculate multi-group confirmatory factor analysis, partial invariance tests, visualizations of the size of non-invariance, and potential effect sizes for overall models and individual parameters.
+Therefore, purpose of this manuscript is to describe an \emph{R} package, \texttt{visualizemi}, that provides functionality to calculate multi-group confirmatory factor analysis, partial invariance tests, visualizations of the size of non-invariance, and potential effect sizes for overall models and individual parameters.
 No known visualization techniques have been proposed for measurement invariance.
-By creating panel visualizations, we can supplement a researchers ability to judge the strength of the non-invariance differences and effect size for each item.
+By creating panel visualizations, we can supplement a researcher's ability to judge the strength of the non-invariance differences and effect size for each item.
 The proposed effect sizes demonstrate the likelihood of replication with a similar sample as compared to a randomly assigned group model, thus, illustrating what type of measurement one might expect to find, and how different that is from random chance.
-Within this technique, the individual parameter effect sizes can calculated: both the group differences within a model as compared to random and the likelihood of a parameter replication compared to random groups.
+Within this technique, the individual parameter effect sizes can be calculated: both the group differences within a model as compared to random and the likelihood of a parameter replication compared to random groups.
 Coupled with other indicators (i.e., fit indices differences, \(d_{MACS}\)), we can move toward a better understanding of how much measurement non-invariance is meaningful.
@@
 \item
-  Learn how to use \emph{visualizemi} to analyze multi-group confirmatory factor analysis, examine partial invariance, and create visualizations of parameters.
+  Learn how to use \emph{visualizemi} to analyze multi-group confirmatory factor analysis, examine partial for invariance, and create visualizations of parameters.
 \item
@@
   \texttt{complete}: The output from this model can be found in Figure \ref{fig:invariant-pic}.
-On the left hand side, the item invariance is plotted, and on the right hand side, the latent mean distributions for the two groups are plotted.
+On the left-hand side, the item invariance is plotted, and on the right-hand side, the latent mean distributions for the two groups are plotted.
 In the item invariance sub-plot, the visualization includes all three components traditionally seen in MGCFA testing steps: loadings, intercepts, and residuals.
@@
 \item
-  \texttt{intercept}: Only the left hand side of the complete plot designed to represent intercepts and factor loadings.
+  \texttt{intercept}: Only the left-hand side of the complete plot designed to represent intercepts and factor loadings.
 Factor loadings represent the slope of the regression equation for the latent variable predicting the scores on the observed variable (\(\hat{Y} \sim b_0 + b_1X + \epsilon\)).
@@
 \item
-  \texttt{mean}: The right hand side of the complete plot graphing the latent variable means and density from the data.
+  \texttt{mean}: The right-hand side of the complete plot graphing the latent variable means and density from the data.
 The latent variable is shown on the x-axis using standardized values (i.e., \emph{z}-scores) where -1 indicates one standard deviation below the mean for the latent variable, 0 indicates the mean for the latent variable and so on.
@@
 (2019) suggests specific sizes for small, medium, and large, each researcher should determine for themselves what effects represent.
-Figure \ref{fig:small-load-pic} displays the results from the small (\(d_{MACS}\) = 0.27) difference in loadings, while Figure \ref{fig:med-load-pic} displays the results from the medium (\(d_{MACS}\) = 0.53) difference in loadings, and Figure \ref{fig:large-load-pic} shows the large (\(d_{MACS}\) = 0.68) differences.
+Figure \ref{fig:small-load-pic} displays the results from the small (\(d_{MACS}\) = 0.27) difference in loadings, while Figure \ref{fig:med-load-pic} displays the results from the medium (\(d_{MACS}\) = 0.61) difference in loadings, and Figure \ref{fig:large-load-pic} shows the large (\(d_{MACS}\) = 0.66) differences.
 When investigating the slope values, we can clearly see the change in the loading for the second group (the only manipulated variable, although random data set generation may also change intercepts and residuals slightly).
@@
 Last, the effect of the residuals is plotted in small (Figure \ref{fig:small-res-pic}), medium (Figure \ref{fig:med-res-pic}), and large (Figure \ref{fig:large-res-pic}) formats.
-While \(d_{MACS}\) values are not technically available for the residuals, our models showed 0.19, 0.19, and 0.16, respectively.
+While \(d_{MACS}\) values are not technically available for the residuals, our models showed 0.19, 0.10, and 0.16, respectively.
 These differences in values are variable due to the random generation of data sets for each measurement invariance manipulation.
@@
     \CommentTok{\# what equality constraints are you testing }
-    \AttributeTok{group.equal =} \FunctionTok{c}\NormalTok{(}\StringTok{"loadings"}\NormalTok{, }\StringTok{"intercepts"}\NormalTok{, }\StringTok{"residuals"}\NormalTok{)}
+    \AttributeTok{group.equal =} \FunctionTok{c}\NormalTok{(}\StringTok{"loadings"}\NormalTok{, }\StringTok{"intercepts"}\NormalTok{, }\StringTok{"resduals"}\NormalTok{)}
 \NormalTok{  )}
@@
 \NormalTok{partial.rs}\FloatTok{.2}\SpecialCharTok{$}\NormalTok{model\_coef }\SpecialCharTok{\%\textgreater{}\%} 
-  \FunctionTok{filter}\NormalTok{(term }\SpecialCharTok{==} \StringTok{"RS6 \textasciitilde{}1"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
+  \FunctionTok{filter}\NormalTok{(term }\SpecialCharTok{==} \StringTok{"RS6 \textasciitilde{}1 "}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
   \FunctionTok{filter}\NormalTok{(model }\SpecialCharTok{==} \StringTok{"intercepts"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
@@
 \begin{verbatim}
-## # A tibble: 0 x 4
-## # i 4 variables: term <chr>, group <int>, estimate <dbl>, std.error <dbl>
+## # A tibble: 2 x 4
+##   term      group estimate std.error
+##   <chr>     <int>    <dbl>     <dbl>
+## 1 "RS6 ~1 "     1     5.00    0.0605
+## 2 "RS6 ~1 "     2     4.54    0.0533
 \end{verbatim}
@@
 Figures \ref{fig:rs-partial-pic} and \ref{fig:rs-partial-pic2} display the three plots provided in the \texttt{bootstrap\_partial()} function.
-In general, we should expect \(M_{D}\) = 0.23 when items are invariant and \(M_{D}\) = 0.26 when items are not invariant.
-The effect size of non-invariant items ranges from 0.43 to 0.62.
+In general, we should expect \(M_{D}\) = 0.11 when items are invariant and \(M_{D}\) = 0.25 when items are not invariant.
+The effect size of non-invariant items ranges from 0.43 to 0.59.
 
@@
 \caption{\label{fig:rs14-chinese-pic}The differences in intercepts for the second item on the RS14 by language sample.
-The differences between intercepts are shown on the left hand side with a clear separation between lines.
+The differences between intercepts are shown on the left-hand side with a clear separation between lines.
 The latent means also show a clear difference between groups where the English group appears to have lower scores overall than the Chinese group.}
@@
 \midrule
-Overall & 7,598.681 & 7,661.900 & 0.946 & 0.893 & 0.078 & 0.035\\
+Overall & 7,595.822 & 7,659.041 & 1.000 & 1.017 & 0.000 & 0.012\\
 Group Group 1 & 3,765.749 & 3,818.571 & 0.976 & 0.953 & 0.047 & 0.031\\
-Group Group 2 & 3,820.090 & 3,872.912 & 0.969 & 0.938 & 0.067 & 0.034\\
-Configural & 7,585.839 & 7,712.277 & 0.972 & 0.944 & 0.058 & 0.033\\
-Loadings & 7,613.434 & 7,723.014 & 0.865 & 0.807 & 0.107 & 0.079\\
-Intercepts & 7,606.648 & 7,699.370 & 0.874 & 0.860 & 0.091 & 0.079\\
-Residuals & 7,600.057 & 7,671.705 & 0.880 & 0.895 & 0.079 & 0.091\\
+Group Group 2 & 3,815.314 & 3,868.136 & 0.996 & 0.991 & 0.025 & 0.023\\
+Configural & 7,581.063 & 7,707.501 & 0.988 & 0.976 & 0.038 & 0.027\\
+Loadings & 7,609.348 & 7,718.928 & 0.878 & 0.826 & 0.101 & 0.079\\
+Intercepts & 7,601.550 & 7,694.271 & 0.891 & 0.879 & 0.084 & 0.079\\
+Residuals & 7,596.811 & 7,668.459 & 0.890 & 0.905 & 0.075 & 0.096\\
 \bottomrule
@@
 \midrule
-Overall & 7,684.982 & 7,748.201 & 0.987 & 0.973 & 0.040 & 0.023\\
+Overall & 7,665.760 & 7,728.979 & 1.000 & 1.022 & 0.000 & 0.010\\
 Group Group 1 & 3,765.749 & 3,818.571 & 0.976 & 0.953 & 0.047 & 0.031\\
-Group Group 2 & 3,857.143 & 3,909.965 & 0.992 & 0.984 & 0.037 & 0.029\\
-Configural & 7,622.892 & 7,749.330 & 0.986 & 0.972 & 0.042 & 0.030\\
-Loadings & 7,674.188 & 7,783.767 & 0.817 & 0.738 & 0.131 & 0.095\\
-Intercepts & 7,667.682 & 7,760.403 & 0.824 & 0.805 & 0.113 & 0.096\\
-Residuals & 7,683.177 & 7,754.825 & 0.762 & 0.793 & 0.116 & 0.138\\
+Group Group 2 & 3,855.953 & 3,908.775 & 0.997 & 0.995 & 0.020 & 0.023\\
+Configural & 7,621.702 & 7,748.140 & 0.989 & 0.978 & 0.036 & 0.027\\
+Loadings & 7,659.690 & 7,769.270 & 0.852 & 0.789 & 0.114 & 0.088\\
+Intercepts & 7,652.360 & 7,745.081 & 0.863 & 0.848 & 0.097 & 0.088\\
+Residuals & 7,664.853 & 7,736.502 & 0.806 & 0.832 & 0.102 & 0.135\\
 \bottomrule
@@
 \midrule
-Overall & 7,382.013 & 7,445.232 & 0.997 & 0.995 & 0.016 & 0.018\\
+Overall & 7,382.876 & 7,446.095 & 0.992 & 0.985 & 0.028 & 0.020\\
 Group Group 1 & 3,765.749 & 3,818.571 & 0.976 & 0.953 & 0.047 & 0.031\\
-Group Group 2 & 3,602.905 & 3,655.727 & 1.000 & 1.013 & 0.000 & 0.023\\
-Configural & 7,368.654 & 7,495.092 & 0.992 & 0.983 & 0.028 & 0.027\\
-Loadings & 7,364.904 & 7,474.483 & 0.990 & 0.986 & 0.025 & 0.036\\
-Intercepts & 7,358.503 & 7,451.224 & 1.000 & 1.001 & 0.000 & 0.037\\
-Residuals & 7,385.958 & 7,457.607 & 0.864 & 0.881 & 0.075 & 0.098\\
+Group Group 2 & 3,601.920 & 3,654.742 & 1.000 & 1.023 & 0.000 & 0.018\\
+Configural & 7,367.669 & 7,494.108 & 0.996 & 0.992 & 0.020 & 0.025\\
+Loadings & 7,371.027 & 7,480.607 & 0.969 & 0.956 & 0.049 & 0.046\\
+Intercepts & 7,364.724 & 7,457.446 & 0.977 & 0.975 & 0.037 & 0.047\\
+Residuals & 7,386.854 & 7,458.502 & 0.877 & 0.893 & 0.076 & 0.076\\
 \bottomrule
@@
 \midrule
-Overall & 7,300.856 & 7,364.075 & 0.998 & 0.995 & 0.015 & 0.018\\
+Overall & 7,301.897 & 7,365.116 & 0.993 & 0.986 & 0.026 & 0.019\\
 Group Group 1 & 3,765.749 & 3,818.571 & 0.976 & 0.953 & 0.047 & 0.031\\
-Group Group 2 & 3,453.099 & 3,505.921 & 0.954 & 0.908 & 0.069 & 0.035\\
-Configural & 7,218.848 & 7,345.287 & 0.965 & 0.929 & 0.059 & 0.033\\
-Loadings & 7,217.332 & 7,326.912 & 0.955 & 0.935 & 0.056 & 0.045\\
-Intercepts & 7,211.566 & 7,304.287 & 0.962 & 0.958 & 0.046 & 0.047\\
-Residuals & 7,304.566 & 7,376.215 & 0.562 & 0.619 & 0.137 & 0.189\\
+Group Group 2 & 3,454.309 & 3,507.131 & 0.945 & 0.889 & 0.075 & 0.036\\
+Configural & 7,220.058 & 7,346.496 & 0.960 & 0.920 & 0.063 & 0.034\\
+Loadings & 7,218.878 & 7,328.458 & 0.948 & 0.926 & 0.060 & 0.046\\
+Intercepts & 7,213.011 & 7,305.732 & 0.956 & 0.951 & 0.049 & 0.048\\
+Residuals & 7,305.660 & 7,377.309 & 0.559 & 0.617 & 0.137 & 0.189\\
 \bottomrule
@@
 \midrule
-lv =\textasciitilde{} q1 & 0.880 & 0.079\\
-lv =\textasciitilde{} q2 & 0.898 & 0.074\\
-lv =\textasciitilde{} q3 & 0.878 & 0.081\\
-lv =\textasciitilde{} q4 & 0.962 & 0.045\\
-lv =\textasciitilde{} q5 & 0.907 & 0.071\\
+lv =\textasciitilde{} q1 & 0.890 & 0.075\\
+lv =\textasciitilde{} q2 & 0.904 & 0.072\\
+lv =\textasciitilde{} q3 & 0.887 & 0.078\\
+lv =\textasciitilde{} q4 & 1.000 & 0.000\\
+lv =\textasciitilde{} q5 & 0.914 & 0.068\\
 \bottomrule
@@
 \midrule
-lv =\textasciitilde{} q1 & 0.762 & 0.116\\
-lv =\textasciitilde{} q2 & 0.770 & 0.117\\
-lv =\textasciitilde{} q3 & 0.762 & 0.119\\
-lv =\textasciitilde{} q4 & 0.971 & 0.041\\
-lv =\textasciitilde{} q5 & 0.842 & 0.097\\
+lv =\textasciitilde{} q1 & 0.806 & 0.102\\
+lv =\textasciitilde{} q2 & 0.812 & 0.102\\
+lv =\textasciitilde{} q3 & 0.813 & 0.102\\
+lv =\textasciitilde{} q4 & 1.000 & 0.000\\
+lv =\textasciitilde{} q5 & 0.861 & 0.088\\
 \bottomrule
@@
 \midrule
-q1 \textasciitilde{}\textasciitilde{} q1 & 0.869 & 0.075\\
-q2 \textasciitilde{}\textasciitilde{} q2 & 0.860 & 0.078\\
-q3 \textasciitilde{}\textasciitilde{} q3 & 0.870 & 0.075\\
-q4 \textasciitilde{}\textasciitilde{} q4 & 0.994 & 0.016\\
-q5 \textasciitilde{}\textasciitilde{} q5 & 0.862 & 0.077\\
-lv \textasciitilde{}\textasciitilde{} lv & 0.864 & 0.075\\
+q1 \textasciitilde{}\textasciitilde{} q1 & 0.879 & 0.077\\
+q2 \textasciitilde{}\textasciitilde{} q2 & 0.873 & 0.079\\
+q3 \textasciitilde{}\textasciitilde{} q3 & 0.878 & 0.077\\
+q4 \textasciitilde{}\textasciitilde{} q4 & 0.980 & 0.031\\
+q5 \textasciitilde{}\textasciitilde{} q5 & 0.873 & 0.079\\
+lv \textasciitilde{}\textasciitilde{} lv & 0.877 & 0.076\\
 \bottomrule
@@
 \midrule
-q1 \textasciitilde{}\textasciitilde{} q1 & 0.558 & 0.140\\
-q2 \textasciitilde{}\textasciitilde{} q2 & 0.559 & 0.140\\
-q3 \textasciitilde{}\textasciitilde{} q3 & 0.560 & 0.140\\
-q4 \textasciitilde{}\textasciitilde{} q4 & 0.972 & 0.035\\
-q5 \textasciitilde{}\textasciitilde{} q5 & 0.559 & 0.140\\
-lv \textasciitilde{}\textasciitilde{} lv & 0.562 & 0.137\\
+q1 \textasciitilde{}\textasciitilde{} q1 & 0.555 & 0.141\\
+q2 \textasciitilde{}\textasciitilde{} q2 & 0.556 & 0.141\\
+q3 \textasciitilde{}\textasciitilde{} q3 & 0.556 & 0.141\\
+q4 \textasciitilde{}\textasciitilde{} q4 & 0.967 & 0.039\\
+q5 \textasciitilde{}\textasciitilde{} q5 & 0.557 & 0.141\\
+lv \textasciitilde{}\textasciitilde{} lv & 0.559 & 0.137\\
 \bottomrule
@@
 
-\includegraphics{manuscript_files/figure-latex/unnamed-chunk-103-1.pdf}
+\includegraphics{manuscript_files/figure-latex/unnamed-chunk-107-1.pdf}
 
@@
 
-\includegraphics{manuscript_files/figure-latex/unnamed-chunk-103-2.pdf}
+\includegraphics{manuscript_files/figure-latex/unnamed-chunk-107-2.pdf}
 
@@
 
-\includegraphics{manuscript_files/figure-latex/unnamed-chunk-103-3.pdf}
+\includegraphics{manuscript_files/figure-latex/unnamed-chunk-107-3.pdf}
 
@@
 
-\includegraphics{manuscript_files/figure-latex/unnamed-chunk-103-4.pdf}
+\includegraphics{manuscript_files/figure-latex/unnamed-chunk-107-4.pdf}
 
@@
 
-\includegraphics{manuscript_files/figure-latex/unnamed-chunk-103-5.pdf}
+\includegraphics{manuscript_files/figure-latex/unnamed-chunk-107-5.pdf}
 
@@
 
-\includegraphics{manuscript_files/figure-latex/unnamed-chunk-103-6.pdf}
+\includegraphics{manuscript_files/figure-latex/unnamed-chunk-107-6.pdf}
 
@@
 
-\includegraphics{manuscript_files/figure-latex/unnamed-chunk-103-7.pdf}
+\includegraphics{manuscript_files/figure-latex/unnamed-chunk-107-7.pdf}
 
@@
 
-\includegraphics{manuscript_files/figure-latex/unnamed-chunk-103-8.pdf}
+\includegraphics{manuscript_files/figure-latex/unnamed-chunk-107-8.pdf}
 
@@
 
-\includegraphics{manuscript_files/figure-latex/unnamed-chunk-110-1.pdf}
+\includegraphics{manuscript_files/figure-latex/unnamed-chunk-114-1.pdf}
 
@@
 
-\includegraphics{manuscript_files/figure-latex/unnamed-chunk-111-1.pdf} \includegraphics{manuscript_files/figure-latex/unnamed-chunk-111-2.pdf}
+\includegraphics{manuscript_files/figure-latex/unnamed-chunk-115-1.pdf} \includegraphics{manuscript_files/figure-latex/unnamed-chunk-115-2.pdf}
 

### 2024-07-29 appendix_1.Rmd
making figures
updated manuscript

@@
 
-## Simulating from models
+# Code Examples
+
+```{r create-models, echo = F, message = F}
+# overall model
+model.overall <- "lv =~ q1 + q2 + q3 + q4 + q5
+q1 ~ 0*1
+lv ~ 1"
+
+# build invariant model one factor
+model.invariant.g1 <- "lv =~ .8*q1 + .4*q2 + .6*q3 + .3*q4 + .6*q5 
+q4 ~~ 1*q4
+q4 ~ 0*1
+q1 ~ 0*1
+lv ~ 1"
+model.invariant.g2 <- "lv =~ .81*q1 + .41*q2 + .61*q3 + .31*q4 + .61*q5
+q4 ~~ 1*q4
+q4 ~ 0*1
+q1 ~ 0*1
+lv ~ 1"
+
+# loadings .5, .8, 1.1
+model.small.load.g2 <- "lv =~ .81*q1 + .41*q2 + .61*q3 + .5*q4 + .61*q5
+q1 ~ 0*1
+lv ~ 1"
+model.med.load.g2 <- "lv =~ .81*q1 + .41*q2 + .61*q3 + .8*q4 + .61*q5
+q1 ~ 0*1
+lv ~ 1"
+model.large.load.g2 <- "lv =~ .81*q1 + .41*q2 + .61*q3 + 1.1*q4 + .61*q5
+q1 ~ 0*1
+lv ~ 1"
+
+# build invariance on intercepts .25, .50, and .75
+model.small.int.g2 <- "lv =~ .81*q1 + .41*q2 + .61*q3 + .31*q4 + .61*q5
+q4 ~ .25*1
+q1 ~ 0*1
+lv ~ 1"
+model.med.int.g2 <- "lv =~ .81*q1 + .41*q2 + .61*q3 + .31*q4 + .61*q5
+q4 ~ .5*1
+q1 ~ 0*1
+lv ~ 1"
+model.large.int.g2 <- "lv =~ .81*q1 + .41*q2 + .61*q3 + .31*q4 + .61*q5
+q4 ~ .75*1
+q1 ~ 0*1
+lv ~ 1"
+
+# build invariance on residuals .25, .50, and .75
+model.small.res.g2 <- "lv =~ .81*q1 + .41*q2 + .61*q3 + .31*q4 + .61*q5
+q4 ~~ .75*q4
+q1 ~ 0*1
+lv ~ 1"
+model.med.res.g2 <- "lv =~ .81*q1 + .41*q2 + .61*q3 + .31*q4 + .61*q5
+q4 ~~ .5*q4
+q1 ~ 0*1
+lv ~ 1"
+model.large.res.g2 <- "lv =~ .81*q1 + .41*q2 + .61*q3 + .31*q4 + .61*q5
+q4 ~~ .25*q4
+q1 ~ 0*1
+lv ~ 1"
+```
+
+```{r create-data, echo = F, message = F}
+# simulate data invariant
+df.invariant <- bind_rows(
+  simulateData(model.invariant.g1, sample.nobs = 250, 
+               meanstructure = T, model.type = "cfa",
+               seed = 1234) %>% 
+    mutate(group = "Group 1"), 
+  simulateData(model.invariant.g2, sample.nobs = 250, 
+               meanstructure = T, model.type = "cfa",
+               seed = 1234) %>% 
+    mutate(group = "Group 2") 
+)
+
+# simulate data small load
+df.small.load <- bind_rows(
+  simulateData(model.invariant.g1, sample.nobs = 250, 
+               meanstructure = T, model.type = "cfa",
+               seed = 1234) %>% 
+    mutate(group = "Group 1"), 
+  simulateData(model.small.load.g2, sample.nobs = 250, 
+               meanstructure = T, model.type = "cfa",
+               seed = 1234) %>% 
+    mutate(group = "Group 2") 
+)
+
+# simulate data med load
+df.med.load <- bind_rows(
+  simulateData(model.invariant.g1, sample.nobs = 250, 
+               meanstructure = T, model.type = "cfa",
+               seed = 1234) %>% 
+    mutate(group = "Group 1"), 
+  simulateData(model.med.load.g2, sample.nobs = 250, 
+               meanstructure = T, model.type = "cfa",
+               seed = 1234) %>% 
+    mutate(group = "Group 2") 
+)
+
+# simulate data large load
+df.large.load <- bind_rows(
+  simulateData(model.invariant.g1, sample.nobs = 250, 
+               meanstructure = T, model.type = "cfa",
+               seed = 1234) %>% 
+    mutate(group = "Group 1"), 
+  simulateData(model.large.load.g2, sample.nobs = 250, 
+               meanstructure = T, model.type = "cfa",
+               seed = 1234) %>% 
+    mutate(group = "Group 2") 
+)
+
+# simulate data small int
+df.small.int <- bind_rows(
+  simulateData(model.invariant.g1, sample.nobs = 250, 
+               meanstructure = T, model.type = "cfa",
+               seed = 1234) %>% 
+    mutate(group = "Group 1"), 
+  simulateData(model.small.int.g2, sample.nobs = 250, 
+               meanstructure = T, model.type = "cfa",
+               seed = 1234) %>% 
+    mutate(group = "Group 2") 
+)
+
+# simulate data med int
+df.med.int <- bind_rows(
+  simulateData(model.invariant.g1, sample.nobs = 250, 
+               meanstructure = T, model.type = "cfa",
+               seed = 1234) %>% 
+    mutate(group = "Group 1"), 
+  simulateData(model.med.int.g2, sample.nobs = 250, 
+               meanstructure = T, model.type = "cfa",
+               seed = 1234) %>% 
+    mutate(group = "Group 2") 
+)
+
+# simulate data large int
+df.large.int <- bind_rows(
+  simulateData(model.invariant.g1, sample.nobs = 250, 
+               meanstructure = T, model.type = "cfa",
+               seed = 1234) %>% 
+    mutate(group = "Group 1"), 
+  simulateData(model.large.int.g2, sample.nobs = 250, 
+               meanstructure = T, model.type = "cfa",
+               seed = 1234) %>% 
+    mutate(group = "Group 2") 
+)
+
+# simulate data small res
+df.small.res <- bind_rows(
+  simulateData(model.invariant.g1, sample.nobs = 250, 
+               meanstructure = T, model.type = "cfa",
+               seed = 1234) %>% 
+    mutate(group = "Group 1"), 
+  simulateData(model.small.res.g2, sample.nobs = 250, 
+               meanstructure = T, model.type = "cfa",
+               seed = 1234) %>% 
+    mutate(group = "Group 2") 
+)
+
+# simulate data med res
+df.med.res <- bind_rows(
+  simulateData(model.invariant.g1, sample.nobs = 250, 
+               meanstructure = T, model.type = "cfa",
+               seed = 1234) %>% 
+    mutate(group = "Group 1"), 
+  simulateData(model.med.res.g2, sample.nobs = 250, 
+               meanstructure = T, model.type = "cfa",
+               seed = 1234) %>% 
+    mutate(group = "Group 2") 
+)
+
+# simulate data large res
+df.large.res <- bind_rows(
+  simulateData(model.invariant.g1, sample.nobs = 250, 
+               meanstructure = T, model.type = "cfa",
+               seed = 1234) %>% 
+    mutate(group = "Group 1"), 
+  simulateData(model.large.res.g2, sample.nobs = 250, 
+               meanstructure = T, model.type = "cfa",
+               seed = 1234) %>% 
+    mutate(group = "Group 2") 
+)
+```
+
+```{r run-cfa, echo = F, message = F}
+# invariant CFA
+results.invariant <- 
+  mgcfa(model = model.overall, 
+        data = df.invariant,
+        group = "group",
+        group.equal = c("loadings", "intercepts", "residuals"),
+        meanstructure = T)
+
+d_invariant <- lavaan_dmacs(
+  results.invariant$model_configural, 
+  RefGroup = "Group 1")
+
+# loadings
+results.small.load <- 
+  mgcfa(model = model.overall, 
+        data = df.small.load,
+        group = "group",
+        group.equal = c("loadings", "intercepts", "residuals"),
+        meanstructure = T)
+
+results.med.load <- 
+  mgcfa(model = model.overall, 
+        data = df.med.load,
+        group = "group",
+        group.equal = c("loadings", "intercepts", "residuals"),
+        meanstructure = T)
+results.large.load <- 
+  mgcfa(model = model.overall, 
+        data = df.large.load,
+        group = "group",
+        group.equal = c("loadings", "intercepts", "residuals"),
+        meanstructure = T)
+
+d_small_load <- 
+  lavaan_dmacs(results.small.load$model_configural, 
+               RefGroup = "Group 1")
+d_med_load <- 
+  lavaan_dmacs(results.med.load$model_configural, 
+               RefGroup = "Group 1")
+d_large_load <- 
+  lavaan_dmacs(results.large.load$model_configural, 
+               RefGroup = "Group 1")
+
+# intercepts
+results.small.int <- 
+  mgcfa(model = model.overall, 
+        data = df.small.int,
+        group = "group",
+        group.equal = c("loadings", "intercepts", "residuals"),
+        meanstructure = T)
+results.med.int <- 
+  mgcfa(model = model.overall, 
+        data = df.med.int,
+        group = "group",
+        group.equal = c("loadings", "intercepts", "residuals"),
+        meanstructure = T)
+results.large.int <- 
+  mgcfa(model = model.overall, 
+        data = df.large.int,
+        group = "group",
+        group.equal = c("loadings", "intercepts", "residuals"),
+        meanstructure = T)
+
+d_small_int <- 
+  lavaan_dmacs(results.small.int$model_configural, 
+               RefGroup = "Group 1")
+d_med_int <- 
+  lavaan_dmacs(results.med.int$model_configural, 
+               RefGroup = "Group 1")
+d_large_int <- 
+  lavaan_dmacs(results.large.int$model_configural, 
+               RefGroup = "Group 1")
+
+# residuals
+results.small.res <-
+  mgcfa(model = model.overall, 
+        data = df.small.res,
+        group = "group",
+        group.equal = c("loadings", "intercepts", "residuals"),
+        meanstructure = T)
+results.med.res <- 
+  mgcfa(model = model.overall, 
+        data = df.med.res,
+        group = "group",
+        group.equal = c("loadings", "intercepts", "residuals"),
+        meanstructure = T)
+results.large.res <- 
+  mgcfa(model = model.overall, 
+        data = df.large.res,
+        group = "group",
+        group.equal = c("loadings", "intercepts", "residuals"),
+        meanstructure = T)
+
+d_small_res <- 
+  lavaan_dmacs(results.small.res$model_configural, 
+               RefGroup = "Group 1")
+d_med_res <- 
+  lavaan_dmacs(results.med.res$model_configural,
+               RefGroup = "Group 1")
+d_large_res <- 
+  lavaan_dmacs(results.large.res$model_configural, 
+               RefGroup = "Group 1")
+```
+
+## Simulating from Models
 
@@
 
-## Simulating from matrices
+## Simulating from Matrices
 
@@
 ```
+
+\newpage
+
+## MGCFA: `mgcfa()` Function
+
+In this example, we make our example model using *lavaan* syntax. The `lv` latent variable predicts the five measured variables, which are present as columns in our `df.invariant` data set.
+
+ *lavaan* automatically sets the mean (i.e., the intercept) for latent variables to zero.
+If we wish to visualize the impact of the changes in parameter estimates across groups on the latent means, we need to allow the latent mean estimation with `lv ~ 1`.
+However, adding this estimation into our model will create a non-identified model.
+To solve this problem, you can set one of the intercepts of another variable to a value to scale the model.
+Here we will set the scale of the model by using `q1 ~ 0*1`, thus, scaling the expected means to zero.
+With simulation, this step is easy to know which variable to pick - we set the intercept on the variable we know did not show differences.
+In real data, you may wish to run the model steps *without* setting this option, examine the results of a configural or separate models, and then add the option for the values most similar.
+Additionally, you could complete partial invariance steps to determine which value appears most consistent to fix the estimate.
+
+```{r model-example-app, eval = T, include = T, echo = T, size = "small"}
+# create lavaan model
+model.overall <- "
+# overall one-factor model
+lv =~ q1 + q2 + q3 + q4 + q5
+# set the intercept (mean) of q1 to zero
+q1 ~ 0*1
+# allow the lv intercept to be freely estimated
+lv ~ 1"
+# look at the data
+head(df.invariant)
+```
+
+The `mgcfa()` function is designed to flexibly allow you to leverage *lavaan*'s package functions to calculate multiple measurement steps at once. You would include:
+
+1)  the model syntax in the `model` argument
+2)  the dataframe in the `data` argument of our function
+3)  the name of the grouping variable in quotes for `group`
+4)  and the equality constraints you would like to impose in order in `group.equal`
+5)  `...` any other *lavaan* arguments you would like to use such as `meanstructure` or `estimator`.
+
+Note: you can also use `sample.cov`, `sample.mean`, `sample.nobs` in this step for estimation of multigroup models, but simulated dataframes are needed for bootstrapping replication estimates.
+
+```{r mgcfa-example-app, echo = T, size = "small"}
+# run our mgcfa function to run all models
+results.invariant <- 
+  # name of the saved model syntax
+  mgcfa(model = model.overall, 
+        # name of the dataframe
+        data = df.invariant,
+        # name of the grouping variable
+        group = "group",
+        # equality constraints to impose in order
+        group.equal = c("loadings", "intercepts", "residuals"),
+        # other options to send to lavaan cfa function
+        meanstructure = T)
+
+# what is saved for you
+names(results.invariant)
+```
+
+1)  `model_coef`: The parameter estimates for each model with the model step included in a *model* column.
+This set of coefficients can be used for other functions.
+This dataframe is created with *broom*'s `tidy()` function if you wish to recreate this table without running the `mgcfa()` function [@robinson2023].
+
+```{r mgcfa-output1-app, echo = T, include = T, size = "small"}
+results.invariant$model_coef[1:10 , ]
+```
+
+2)  `model_fit`: The model fit indices from `fitmeasures()` to review for overall model fit and invariance judgments. The name of the model is included in a *model* column.
+
+```{r mgcfa-output2-app, echo = T, include = T, size = "small"}
+head(results.invariant$model_fit)
+```
+
+3)  `model_overall`: A saved *lavaan* fitted model of all groups together without any equality constraints or grouping variables.
+These objects can be used with any function that normally takes a saved model: `parameterEstimates()`, `modificationIndices()`, `semPlot::semPaths()`, and so on [@epskamp2022].
+
+```{r mgcfa-output3-app, echo = T, include = T, size = "small"}
+class(results.invariant$model_overall)
+```
+
+4)  `group_models`: A list of saved fitted models for each group separately.
+
+```{r mgcfa-output4-app, echo = T, include = T, size = "small"}
+names(results.invariant$group_models)
+```
+
+5)  `model_configural`: A saved fitted model for the configural model that nests together each group into one model with no other constraints.
+
+```{r mgcfa-output5-app, echo = T, include = T, size = "small"}
+class(results.invariant$model_configural)
+```
+
+6)  `invariance_models`: A list of saved fitted models that consecutively adds `group.equal` constraints.
+
+```{r mgcfa-output6-app, echo = T, include = T, size = "small"}
+names(results.invariant$invariance_models)
+```
+
+\newpage
+
+## Partial Invariance: `partial_mi()` Function
+
+The `partial_mi()` function aids in the calculation of partial invariance for a specific step of the MGCFA process. The function includes the following arguments:
+
+1)  `saved_model`: The saved *lavaan* model with the equality constraints at the level of measurement invariance you would like to examine for partial invariance.
+2)  `data`: The dataframe where the model was estimated.
+3)  `model`: The model syntax for the overall model.
+4)  `group`: The grouping variable column in the dataframe.
+5)  `group.equal`: The equality constraints including in your original multigroup tests.
+6)  `partial_step`: The level of partial invariance you wish to test.
+
+```{r partial-example-app, echo = T, size = "small"}
+partial.invariant <-
+  partial_mi(
+    # saved model output with constraints
+    saved_model = results.invariant$invariance_models$model.residuals,
+    # dataframe from model 
+    data = df.invariant,
+    # model syntax 
+    model = model.overall,
+    # group column name 
+    group = "group",
+    # group equality constraints from your mgcfa
+    group.equal = c("loadings", "intercepts", "residuals"),
+    # which step you want to examine for partial invariance
+    partial_step = "residuals"
+    )
+
+names(partial.invariant)
+```
+
+In this function, each parameter with the appropriate *lavaan* syntax is relaxed individually (i.e., `~1` for intercepts, `~~` for residuals, etc.).
+The fitted models are saved in the `models` output, and the `fit_table` output includes all fit indices for each model to investigate potential areas of partial invariance based on the researcher's desired criterion.
+
+```{r partial-example1-app, echo = T, size = "small"}
+names(partial.invariant$models)
+```
+
+```{r partial-example2-app, echo = T, size = "small"}
+head(partial.invariant$fit_table %>% 
+       dplyr::select(free.parameter, cfi, rmsea))
+```
+
+Note: the `partial_step` function is used to determine which types of `op` or operators to freely estimate between groups.
+If one chooses residuals, you will also freely estimate the residual for the latent variable or any other residuals found in the model.
+These items may be ignored if they were not meant to be included.
+
+\newpage
+
+## Visualization of Invariance: `plot_mi()` Functions
+
+Once we know which items are non-invariant, the `model_coef` output from the `mgcfa()` can be used directly in `plot_mi()`.
+The plot outputs will be described below.
+First, here are the arguments for the function:
+
+1)  `data_coef`: A tidy dataframe of the parameter estimates from the models.
+This function assumes you have used `broom::tidy()` on the saved model from *lavaan* and added a column called "model" with the name of the model step [@robinson2023].
+This function will only run for models that have used the grouping function (i.e., configural, metric, scalar, and strict or other combinations/steps you wish to examine).
+2)  `model_step`: Which model do you want to plot? You should match this name to the one you want to extract from your model column in the `data_coef`.
+3)  `item_name`: Which observed variable from your model syntax do you want to plot? Please list this variable name exactly how it appears in the model.
+4)  `x_limits`: What do you want the x-axis limits to be for your invariance plot?
+The default option is to assume the latent variable is standardized, and therefore, -1 to 1 is recommended.
+Use only two numbers, a lower and upper limit.
+This value also constrains the latent mean diagram to help zoom in on group differences because the scale of latent means is usually centered over zero.
+You can use this parameter to zoom out to a more traditional histogram using `c(-2, 2)`.
+5)  `y_limits`: What do you want the y-axis limits to be for your invariance plot?
+Given that the latent variable is used to predict the observed values in the data, you could use the minimum and maximum values found in the data.
+If that range is large, consider reducing this value to be able to visualize the results (i.e., otherwise it may be too zoomed out to judge group differences).
+Use only two numbers, a lower and upper limit.
+6)  `conf.level`: What confidence limit do you want to plot? Use 1 - $\alpha$.
+7)  `model_results`: In this argument, include the saved *lavaan* output for the model listed in the `model_step` argument.
+8)  `lv_name`: Include the name of the latent variable, exactly how it is listed in your *lavaan* syntax.
+You should plot the latent variable that the `item_name` is linked to.
+If you have items that load onto multiple latent variables, you will need to make multiple plots.
+9)  `plot_groups`: If you include more than two groups in a multigroup model, the automatic assumption is that you want the first two groups for this visualization.
+If not, include the names of the groups here to plot.
+
+```{r plot-example-app, eval = T, echo = T, include = T, size = "small"}
+invariant.plot <- 
+  plot_mi(
+    # output from model_coef
+    data_coef = results.invariant$model_coef, 
+    # which model do you want to plot
+    model_step = "Configural", 
+    # name of observed item
+    item_name = "q4", 
+    # latent variable limits to graph
+    x_limits = c(-1,1), 
+    # Y min and max in data 
+    y_limits = c(min(df.invariant$q4), max(df.invariant$q4)),
+    # what ci do you want
+    conf.level = .95, 
+    # what model results do you want 
+    model_results = results.invariant$model_configural,
+    # which latent variable do you want 
+    lv_name = "lv" 
+)
+
+names(invariant.plot)
+```
+
+The outputs from this function are several *ggplot2* objects that can be edited or saved directly using *ggplot2* functionality [@R-ggplot2].
+
+1)  `complete`: The output from this model can be found in Figure \@ref(fig:invariant-pic).
+On the left-hand side, the item invariance is plotted, and on the right-hand side, the latent mean distributions for the two groups are plotted.
+In the item invariance sub-plot, the visualization includes all three components traditionally seen in MGCFA testing steps: loadings, intercepts, and residuals.
+Each visualization element was designed to match the traditional visualization for that type of output.
+All parameter estimates are plotted on the unstandardized estimates and their confidence interval based on the standard error of the estimate.
+All plots are made with *ggplot2* and *cowplot* [@wilke2020].
+
+```{r invariant-pic-app, include = T, fig.cap = "Invariant Model Visualization"}
+invariant.plot$complete
+
+ggsave("figures/invariant-visual.png", dpi = 300, 
+       width = 8, 
+       units = "in")
+```
+
+2)  `intercept`: Only the left-hand side of the complete plot designed to represent intercepts and factor loadings.
+Factor loadings represent the slope of the regression equation for the latent variable predicting the scores on the observed variable ($\hat{Y} \sim b_0 + b_1X + \epsilon$).
+The y-axis indicates the observed variable scores, and here, the plot includes the entire range of the scale of the data for item four.
+The coefficient ($b_1$) for group 1 was `r apa_num(results.invariant$model_coef %>% filter(model == "Configural") %>% filter(grepl("q4", term)) %>% filter(op == "=~") %>% slice_head() %>% pull(estimate))`, while the coefficient for group 2 was `r apa_num(results.invariant$model_coef %>% filter(model == "Configural") %>% filter(grepl("q4", term)) %>% filter(op == "=~") %>% slice_tail() %>% pull(estimate))`.
+The ribbon bands around the plotted slopes indicate the confidence interval for that estimate.
+In this plot, while the coefficients for each group are not literally equal, the overlapping and parallel slope bands indicate they are not different practically.
+
+The item intercepts ($b_0$) are plotted on the middle line where they would cross the y-axis at a latent variable score of zero.
+These are represented by a dot with a set of confidence error bars around the point.
+The intercept for group 1 was `r apa_num(results.invariant$model_coef %>% filter(model == "Configural") %>% filter(grepl("q4", term)) %>% filter(op == "~1") %>% slice_head() %>% pull(estimate))`, while the coefficient for group 2 was `r apa_num(results.invariant$model_coef %>% filter(model == "Configural") %>% filter(grepl("q4", term)) %>% filter(op == "~1") %>% slice_tail() %>% pull(estimate))`.
+In this invariant depiction, the overlap in the intercepts is clear, indicating they are not different.
+You can use `y_limits` to zoom in on the graph if these are too small to be distinguishable.
+
+3)  `mean`: The right-hand side of the complete plot graphing the latent variable means and density from the data.
+The latent variable is shown on the x-axis using standardized values (i.e., *z*-scores) where -1 indicates one standard deviation below the mean for the latent variable, 0 indicates the mean for the latent variable and so on.
+The lines indicate the means of the latent variables from the simulated dataset.
+Group labels are represented in the figure caption on the bottom.
+Group 1 is usually the group that is alphabetically first in the data set or whichever group is the first that appears when using the `levels()` command.
+
+4)  `variance`: A split geom violin plot indicating the variance distribution of the plotted item.
+Residuals are trickier to plot, as they are the left over error when predicting the observed variables $\epsilon$.
+It is tempting to plot this value as the confidence band around the slope, however, that defeats the purpose of understanding that the slopes are estimated separately from the residuals, and both have an associated variability around their parameter estimate.
+Therefore, residuals are represented in the inset picture at the bottom right of the item invariance plot.
+The black bars represent the estimated residual for each group (group 1: `r apa_num(results.invariant$model_coef %>% filter(model == "Configural") %>% filter(grepl("q4", term)) %>% filter(op == "~~") %>% slice_head() %>% pull(estimate))`, group 2: `r apa_num(results.invariant$model_coef %>% filter(model == "Configural") %>% filter(grepl("q4", term)) %>% filter(op == "~~") %>% slice_tail() %>% pull(estimate))`).
+The distributions are plotted to represent the normal spread of values using the standard error of the residuals.
+The violin plot allows for direct comparison of those residuals and their potential distributions.
+Note that the placement has nothing to do with the x or y-axis and is designed to always show in the same location, regardless of size/value.
+The plots are included separately so they can be arranged in a different fashion if desired.
+
+\newpage
+
+## Model Replication and Effect Sizes: `bootstrap_model()` Function
+
+The `bootstrap_model` function in *visualizemi* was designed to estimate the likely replication of overall model invariance with the assumption that the data used for the estimation represents the larger population.
+The following arguments are used:
+
+1)  `saved_configural`: a saved fitted model at the configural level with no equality constraints.
+This model should include all other lavaan settings you would like to use, such as estimator or ordered.
+2)  `data`: The dataframe where the model was estimated.
+3)  `model`: The model syntax for the overall model.
+4)  `group`: The grouping variable column in the dataframe.
+5)  `nboot`: The number of bootstraps to run.
+6)  `invariance_index`: The fit index you would like to use to determine invariance. Please use options and labeling from *lavaan* - see `fitmeasures()` for options.
+7)  `invariance_rule`: The invariance difference score you would like to use as your rule.
+8)  `group.equal`: The equality constraints including in your original multigroup tests.
+
+```{r boot-rr-app, echo = T, eval = F, size = "small"}
+boot.model.invariant <- 
+  bootstrap_model(
+    # saved configural model 
+    saved_configural = results.invariant$model_configural,
+    # dataframe
+    data = df.invariant,
+    # model syntax
+    model = model.overall, 
+    # group variable column in dataframe
+    group = "group",
+    # number of bootstraps
+    nboot = 1000, 
+    # which fit index you would like to use
+    invariance_index = "cfi",
+    # what is your criterion for that fit index
+    invariance_rule = .01,
+    # what equality constraints are you testing 
+    group.equal = c("loadings", "intercepts", "resduals")
+  )
+```
+
+The data included in this function will be sampled, with replacement, at the same size as the current dataset, and the included invariance equality constraints are estimated.
+Each step will be compared to the previous step using the invariance index and comparison rule entered.
+The output is a dataframe of the proportion of non-invariant bootstraps from the real data and the same bootstrapped dataset with the group labels randomly assigned.
+The effect size comparison of proportions, $h$, for non-invariant comparisons:
+
+$$h_{nmi} = 2 \times (asin\sqrt{p_{data}} - asin\sqrt{p_{random}})$$
+
+The alternative, $h_{mi}$, for effect size of measurement invariance replication would simply be the inverse sign of $h_{nmi}$ and is also included in the table.
+Two additional columns $h_{nmi_p}$ and $h_{nmi_p}$ represent the $h$ values divided by the upper bound of $h$ (i.e., $\pi$), to help with interpretation of the effect size (thus, bounding $h$ to -1 to 1).
+
+\newpage
+
+## Parameter Replication and Effect Sizes: `bootstrap_partial()` Function
+
+After examining the overall model potential replication effect size, the individual parameters within a model can be bootstrapped for partial invariance to with that parameter relaxed (overall partial model statistics) and the difference in group parameter estimates (parameter effect size).
+This function uses arguments seen in other functions, so they will not be repeated here.
+The general setup consists of using the model you think could be partially invariant in the `saved_model` argument and the fit index for comparison for the model with less constraints in `invariance_compare`.
+This example examines the loadings in the invariant model, so `saved_model` uses the `mgcfa` output for equality constraints present on the loadings and compares that model to the configural model with no equality constraints on the loadings.
+The `partial_step` argument will be used to determine which operation syntax (i.e.
+`=~` for loadings) to relax for modeling.
+
+```{r boot-partial-app, echo = T, size = "small", eval = F}
+boot.partial.invariant <- 
+      bootstrap_partial(
+        # saved model you want to examine the partial loadings for 
+        saved_model = results.invariant$invariance_models$model.loadings,
+        # the dataset 
+        data = df.invariant, 
+        # the model 
+        model = model.overall,
+        # the group variable in the dataset
+        group = "group", 
+        # number of bootstraps
+        nboot = 1000,
+        # which fit index you would like to use to determine partial invariance
+        invariance_index = "cfi", 
+        # what is the invariance rule 
+        invariance_rule = .01, 
+        # what are we comparing the saved model fit index to 
+        invariance_compare = fitmeasures(results.invariant$model_configural, "cfi"), 
+        # what step are we using for invariance
+        partial_step = "loadings", 
+        # what equality constraints should be imposed 
+        group.equal = c("loadings")
+      )
+```
+
+```{r echo = F, eval = F}
+saveRDS(boot.partial.invariant, "manu_data/boot.partial.invariant.RData")
+```
+
+```{r partial-boot-print-app, echo = T, size = "small"}
+names(boot.partial.invariant)
+```
+
+The saved output includes several dataframes and plots.
+The first is the `boot_DF` which the summary of each run in a dataframe for plotting or summarization.
+This dataframe includes the estimate for each parameter (`term`) separated by group and type (`boot_1`, `boot_2` are the bootstrapped estimates for group 1 and group 2, while the same `random` columns indicate the randomly assigned groups).
+The fit index used to determine invariance is included for bootstrapped and random estimates, and then the differences between groups and if they were "invariant" or not given the researcher supplied rule.
+
+```{r boot-partial-DF-app, echo = T, size = "small"}
+head(boot.partial.invariant$boot_DF)
+```
+
+Next, the `boot_summary` includes a summarized form of the bootstrapped results from separated by bootstrapping versus random and invariant/non-invariant.
+The $d_s$ for between groups Cohen's $d$ is shown below, and the non-central confidence interval is included.
+Effect sizes are only calculated when the number of bootstrapped estimates is at least 10% of the data - therefore, you would not receive effect sizes with almost no bootstrapped runs.
+This dataframe should be used to determine which parameter may be different and at what size between groups in a replication of the study.
+
+```{r boot-summary-DF-app, echo = T, size = "small"}
+boot.partial.invariant$boot_summary %>% 
+  dplyr::select(term, d_boot, d_random)
+```
+
+The `boot_effects` table creates a summary similar to the overall model replication table based on the proportion of runs that were considered invariant versus not for each parameter.
+Note that the effects match the overall results, such that simulated invariant data appears to still show the likelihood that loadings may not replicate in a similar dataset.
+
+```{r boot-effects-DF-app, echo = T, size = "small"}
+boot.partial.invariant$boot_effects
+```
+
+Plots of the results from dataframes can be found within the `bootstrap_partial()` function.
+Figure \@ref(fig:invariance-partial-fig) shows the difference between parameters for groups in the bootstrapped and randomly assigned group runs.
+Figure \@ref(fig:density-partial-fig) shows the density plot of the estimates for each group organized by bootstrapped and randomly assigned groups and the invariance decision for each bootstrapped run.
+Last, Figure \@ref(fig:effect-partial-fig) indicates the $d_s$ value between groups with an indication of the number of data points in each estimate (i.e., dot size).
+These visualizations should allow a researcher to understand the likelihood of replication for each parameter, as well as the potential size of the differences.
+Therefore, one could indicate a specific smallest effect size of interest, rather than a invariance cut-off rule of thumb when planning a replication or registered report.
+
+```{r invariance-partial-fig-app, include = T, fig.cap = "Visualization of the difference score between groups by parameter for invariant and non-invariant bootstrapped and randomly assigned group data."}
+boot.partial.invariant$invariance_plot
+
+ggsave("figures/boot-partial-invariance.png", dpi = 300, 
+       width = 8, 
+       units = "in")
+```
+
+```{r density-partial-fig-app, include = T, fig.cap = "Visualization of the number of estimates for each group by bootstrapped and randomly assigned group runs by their invariance decision."}
+suppressMessages(boot.partial.invariant$density_plot)
+
+ggsave("figures/boot-partial-density.png", dpi = 300, 
+       width = 8, 
+       units = "in")
+```
+
+```{r effect-partial-fig-app, include = T, fig.cap = "Visualization of effect size between groups by parameter for invariant and non-invariant bootstrapped and randomly assigned group data.
+The size of the dots indicate the number of data points for that estimate."}
+boot.partial.invariant$effect_invariance_plot
+
+ggsave("figures/boot-partial-effects.png", dpi = 300, 
+       width = 8, 
+       units = "in")
+```

### 2024-07-29 appendix_2.Rmd
updated manuscript

@@
 
-# MGCFA Model Fit Statistics
+# Simulation Study
+
+The code for building and running simulations can be found in *simulate_boot_rr.Rmd*, *simulate_boot_partial.Rmd*, and *simulate_combine.Rmd*.
+
+## Design and Analysis
+
+Data was simulated using the `simulateData` function in the *R* package *lavaan* [@rosseel2012] assuming multivariate normality using a $\mu$ of 0 and $\sigma$ of 1 for the data.
+This function allows you to write *lavaan* syntax for your model with estimated values to generate data for observed variables (see supplemental for examples).
+The data included two groups of individuals ("Group 1", "Group 2") for a multigroup confirmatory factor analysis ($n_{group}$ = 250, *N* = 500).
+The latent variables were assumed to be continuous normal (the package functions do not require this assumption).
+The model consisted of five observed items predicted by one latent variable (`lv =~ q1 + q2 + q3 + q4 + q5`); however, the demonstration in this manuscript extends to multiple latent variables and other combinations of observed variables.
+Each item was assumed to be related to the latent variable with loadings approximately equal to .40 to .80, except when cases of non-invariance on the loadings was simulated.
+
+The @brown2015 steps of testing measurement invariance are demonstrated in this manuscript for illustration purposes, but in line with @stark2006 suggestions, the visualizations show the impact of loadings and intercepts together.
+A convenience function `mgcfa` is used for these steps or other measurement invariance test orders and combinations.
+Fit indices for the steps for multigroup models are presented in the appendix for comparison of cutoff rules of thumb [@cheung2002] to effect sizes and visualizations presented in this manuscript.
+Fit indices include Akaike Information Criterion [AIC, @akaike1998], Bayesian Information Criterion [BIC, @schwarz1978], Comparative Fit Index [CFI, @bentler1990], Tucker Lewis Index [TLI, @tucker1973], root mean squared error of approximation RMSEA [@steiger1990], and standardized root mean square residual [SRMR, @bentler1995].
+
+The data was then simulated to represent invariance across all model steps, small, medium, and large invariance using $d_{MACS}$ estimated sizes from @nye2019.
+While $d_{MACS}$ is used primarily for an effect size of the (non)-invariance for intercepts and loadings together, a similar approach was taken for the estimation of small, medium, and large effects on the residuals.
+The effect size is presented for all models, calculated from the *dmacs* package [@dueber2023; @nye2011].
+Only one item in each model was manipulated from the invariant model to create the non-invariant models.
+Given the data was simulated with a *z*-score scaling, the loading values were simulated at .30 points apart (given $d_{MACS}$ suggestions of .2, .4, .7), the intercepts at .25 points apart, and the residuals at .25 points apart.
+To plan a simulation for your own study, these values can be used to simulate small, medium, and large non-invariance effects by first converting data into *z*-score.
+
+## Visualize Parameter Differences
+
+The $d_{MACS}$ value for item 4 in the invariant model was `r apa_num(d_invariant)$DMACS[4]`, representing a nil or unimportant difference in this manuscript.
+It is important to note that while @nye2019 suggests specific sizes for small, medium, and large, each researcher should determine for themselves what effects represent.
+Figure \@ref(fig:small-load-pic) displays the results from the small ($d_{MACS}$ = `r apa_num(d_small_load)$DMACS[4]`) difference in loadings, while Figure \@ref(fig:med-load-pic) displays the results from the medium ($d_{MACS}$ = `r apa_num(d_med_load)$DMACS[4]`) difference in loadings, and Figure \@ref(fig:large-load-pic) shows the large ($d_{MACS}$ = `r apa_num(d_large_load)$DMACS[4]`) differences.
+When investigating the slope values, we can clearly see the change in the loading for the second group (the only manipulated variable, although random data set generation may also change intercepts and residuals slightly).
+At the medium effect size, we see that the confidence bands do not overlap (at the edges), and at the large effect size, we can see a clear separation of two lines.
+Note that the intercepts in this model are estimated as equal so the loading representation will not literally separate, but the steepness of the lines is the indicator of the difference between the slopes.
+You can imagine these lines are interpreted like a simple slopes analysis for interactions in regression [@cohen2003].
+When simple slopes for interactions are plotted, if they are parallel, there is no interaction, and if they cross, then there is an interaction.
+Here, we can use this same logic.
+If they are parallel, there is likely invariance (they are the same), and the further from parallel they become, the larger the effect size for the differences between group loadings.
+
+The latent means in Figure \@ref(fig:large-load-pic) do appear to show differences, albeit visually small.
+The latent means diagram shows the impact of any group differences that aren't constrained, and this image shows the configural model (as the metric model would force them to be equal).
+In the simulated model, the *only* manipulated parameter is question 4's loading.
+In real models, the differences may be larger due to other variation found in the parameter estimates.
+Therefore, once you discover items you believe would make a model "partially" invariant, you may wish to estimate that model and graph the item again using the partially invariant model to see only the effect of the non-invariant items.
+Additionally, consider that we set the scaling of the model to 0.
+The estimate for the lv mean in the large loading model was group 1: `r apa_num(results.invariant$model_coef %>% filter(model == "Configural") %>% filter(grepl("lv", term)) %>% filter(op == "~1") %>% slice_head() %>% pull(estimate))`, and group 2: `r apa_num(results.invariant$model_coef %>% filter(model == "Configural") %>% filter(grepl("lv", term)) %>% filter(op == "~1") %>% slice_tail() %>% pull(estimate))`, which results in `r apa_num(results.invariant$model_coef %>% filter(model == "Configural") %>% filter(grepl("lv", term)) %>% filter(op == "~1") %>% slice_head() %>% pull(estimate) - results.invariant$model_coef %>% filter(model == "Configural") %>% filter(grepl("lv", term)) %>% filter(op == "~1") %>% slice_tail() %>% pull(estimate))` difference in group means.
+The practical implications of this difference will depend on the research and interpretations of the researcher.
+
+```{r small-load-pic, include = T, fig.cap = "Small Loadings Model Visualization"}
+plot_mi(
+  data_coef = results.small.load$model_coef, # output from model_coef
+  model_step = "Configural", # which model
+  item_name = "q4", # name of observed item
+  x_limits = c(-1,1), # LV limits to graph
+  y_limits = c(min(df.small.load$q4), max(df.small.load$q4)), # Y min and max in data 
+  conf.level = .95, # what ci do you want
+  model_results = results.small.load$model_configural, # what model results do you want 
+  lv_name = "lv"
+)$complete
+
+ggsave("figures/small-load-visual.png", dpi = 300, 
+       width = 8, 
+       units = "in")
+```
+
+```{r med-load-pic, include = T, fig.cap = "Medium Loadings Model Visualization"}
+plot_mi(
+  data_coef = results.med.load$model_coef, # output from model_coef
+  model_step = "Configural", # which model
+  item_name = "q4", # name of observed item
+  x_limits = c(-1,1), # LV limits to graph
+  y_limits = c(min(df.med.load$q4), max(df.med.load$q4)), # Y min and max in data 
+  conf.level = .95, # what ci do you want
+  model_results = results.med.load$model_configural, # what model results do you want 
+  lv_name = "lv"
+)$complete
+
+ggsave("figures/med-load-visual.png", dpi = 300, 
+       width = 8, 
+       units = "in")
+```
+
+```{r large-load-pic, include = T, fig.cap = "Large Loadings Model Visualization"}
+plot_mi(
+  data_coef = results.large.load$model_coef, # output from model_coef
+  model_step = "Configural", # which model
+  item_name = "q4", # name of observed item
+  x_limits = c(-1,1), # LV limits to graph
+  y_limits = c(min(df.large.load$q4), max(df.large.load$q4)), # Y min and max in data 
+  conf.level = .95, # what ci do you want
+  model_results = results.large.load$model_configural, # what model results do you want 
+  lv_name = "lv"
+)$complete
+
+ggsave("figures/large-load-visual.png", dpi = 300, 
+       width = 8, 
+       units = "in")
+```
+
+For intercepts, the small (Figure \@ref(fig:small-int-pic)), medium (Figure \@ref(fig:med-int-pic)), and large (Figure \@ref(fig:large-int-pic)) depictions represent $d_{MACS}$ values of `r apa_num(d_small_int)$DMACS[4]`, `r apa_num(d_med_int)$DMACS[4]`, and `r apa_num(d_large_int)$DMACS[4]`, respectively.
+Intercept differences can be clearly seen represented by the spacing out of the intercept locations (and thus, the overall line as well).
+While the changes in intercept do not appear to change the latent means, the caveat to this simulation is that only item four was manipulated.
+An example is provided below that demonstrates large changes in latent means.
+
+```{r small-int-pic, include = T, fig.cap = "Small Intercepts Model Visualization"}
+plot_mi(
+  data_coef = results.small.int$model_coef, # output from model_coef
+  model_step = "loadings", # which model
+  item_name = "q4", # name of observed item
+  x_limits = c(-1,1), # LV limits to graph
+  y_limits = c(min(df.small.int$q4), max(df.small.int$q4)), # Y min and max in data 
+  conf.level = .95, # what ci do you want
+  model_results = results.small.int$invariance_models$model.loadings, # what model results do you want 
+  lv_name = "lv"
+)$complete
+
+ggsave("figures/small-int-visual.png", dpi = 300, 
+       width = 8, 
+       units = "in")
+```
+
+```{r med-int-pic, include = T, fig.cap = "Medium Intercepts Model Visualization"}
+plot_mi(
+  data_coef = results.med.int$model_coef, # output from model_coef
+  model_step = "loadings", # which model
+  item_name = "q4", # name of observed item
+  x_limits = c(-1,1), # LV limits to graph
+  y_limits = c(min(df.med.int$q4), max(df.med.int$q4)), # Y min and max in data 
+  conf.level = .95, # what ci do you want
+  model_results = results.med.int$invariance_models$model.loadings, # what model results do you want 
+  lv_name = "lv"
+)$complete
+
+ggsave("figures/med-int-visual.png", dpi = 300, 
+       width = 8, 
+       units = "in")
+```
+
+```{r large-int-pic, include = T, fig.cap = "Large Intercepts Model Visualization"}
+plot_mi(
+  data_coef = results.large.int$model_coef, # output from model_coef
+  model_step = "loadings", # which model
+  item_name = "q4", # name of observed item
+  x_limits = c(-1,1), # LV limits to graph
+  y_limits = c(min(df.large.int$q4), max(df.large.int$q4)), # Y min and max in data 
+  conf.level = .95, # what ci do you want
+  model_results = results.large.int$invariance_models$model.loadings, # what model results do you want 
+  lv_name = "lv"
+)$complete
+
+ggsave("figures/large-int-visual.png", dpi = 300, 
+       width = 8, 
+       units = "in")
+```
+
+Last, the effect of the residuals is plotted in small (Figure \@ref(fig:small-res-pic)), medium (Figure \@ref(fig:med-res-pic)), and large (Figure \@ref(fig:large-res-pic)) formats.
+While $d_{MACS}$ values are not technically available for the residuals, our models showed `r apa_num(d_small_res)$DMACS[4]`, `r apa_num(d_med_res)$DMACS[4]`, and `r apa_num(d_large_res)$DMACS[4]`, respectively.
+These differences in values are variable due to the random generation of data sets for each measurement invariance manipulation.
+At first glance, the differences in the small chart may seem large, because the black lines are not touching, but notice that the distributions overlap, indicating a likely small difference.
+The medium and large differences better illustrate differences in residuals across groups.
+Further, the impact of the residuals on the shape of the latent mean distribution can also been seen (and unintentionally, in the first figures as well due to random variation).
+The impact is due to the standard error of the residuals, as smaller standard errors represent lepokurtic distributions (taller), and larger standard errors represent platykurtic distributions (flatter).
+The effect size difference of the residuals does not appear to change the effects in the latent means.
+
+```{r small-res-pic, include = T, fig.cap = "Small Residuals Model Visualization"}
+plot_mi(
+  data_coef = results.small.res$model_coef, # output from model_coef
+  model_step = "intercepts", # which model
+  item_name = "q4", # name of observed item
+  x_limits = c(-1,1), # LV limits to graph
+  y_limits = c(min(df.small.res$q4), max(df.small.res$q4)), # Y min and max in data 
+  conf.level = .95, # what ci do you want
+  model_results = results.small.res$invariance_models$model.intercepts, # what model results do you want 
+  lv_name = "lv"
+)$complete
+
+ggsave("figures/small-res-visual.png", dpi = 300, 
+       width = 8, 
+       units = "in")
+```
+
+```{r med-res-pic, include = T, fig.cap = "Medium Residuals Model Visualization"}
+plot_mi(
+  data_coef = results.med.res$model_coef, # output from model_coef
+  model_step = "intercepts", # which model
+  item_name = "q4", # name of observed item
+  x_limits = c(-1,1), # LV limits to graph
+  y_limits = c(min(df.med.res$q4), max(df.med.res$q4)), # Y min and max in data 
+  conf.level = .95, # what ci do you want
+  model_results = results.med.res$invariance_models$model.intercepts, # what model results do you want 
+  lv_name = "lv"
+)$complete
+
+ggsave("figures/med-res-visual.png", dpi = 300, 
+       width = 8, 
+       units = "in")
+```
+
+```{r large-res-pic, include = T, fig.cap = "Large Residuals Model Visualization"}
+plot_mi(
+  data_coef = results.large.res$model_coef, # output from model_coef
+  model_step = "intercepts", # which model
+  item_name = "q4", # name of observed item
+  x_limits = c(-1,1), # LV limits to graph
+  y_limits = c(min(df.large.res$q4), max(df.large.res$q4)), # Y min and max in data 
+  conf.level = .95, # what ci do you want
+  model_results = results.large.res$invariance_models$model.intercepts, # what model results do you want 
+  lv_name = "lv"
+)$complete
+
+ggsave("figures/large-res-visual.png", dpi = 300, 
+       width = 8, 
+       units = "in")
+```
+
+## Model Replication and Effect Size
+
+Figure \@ref(fig:boot-rr-pic) portrays the $h_{nmi_p}$ values by simulated non-invariance, strength of non-invariance, and type of equality constraint.
+This image represents 100 simulations of data by 1000 bootstrapped runs (averaged) to explore the expected pattern of results.
+The bars are arranged to show what a researcher might inspect when thinking about replication possibilities and their effect sizes (i.e., only three bars for each equality constraint would be calculated).
+
+```{r boot-rr-pic, include = T, fig.cap = "Visualization of the effect size of bootstrapped replication proportions on simulated data.
+Each panel indicates the simulated data type, colors represent the differences in the strength of the non-invariance, and the bars on the x-axis represent the effect size for the equality constraint.
+"}
+
+boot_rr_DF <- boot_rr_DF %>% 
+  mutate(type_size = ifelse(
+    type == "Invariant", "None", ifelse(
+      grepl("Small", type), "Small", ifelse(
+        grepl("Medium", type), "Medium", "Large"
+      )
+    )
+  ),
+  type_type = ifelse(
+    type == "Invariant", "Invariant", ifelse(
+      grepl("Loadings", type), "Loadings", ifelse(
+        grepl("Intercepts", type), "Intercepts", "Residuals"
+      )
+    ) 
+  ),
+  model = factor(model, 
+                 levels = c("loadings", "intercepts", "residuals"),
+                 labels = c("Loadings", "Intercepts", "Residuals")),
+  type_size = factor(type_size, 
+                     levels = c("None", "Small", "Medium", "Large")),
+  type_type = factor(type_type, 
+                     levels = c("Invariant", "Loadings", "Intercepts", "Residuals")))
+
+prop_boot_rr <- ggplot(boot_rr_DF %>% 
+                         filter(type_type != "Invariant"), 
+                       aes(x = model, 
+                       y = h_nmi_p,
+                       fill = type_size)) + 
+  stat_summary(fun = "mean", 
+               position = "dodge", 
+               geom = "bar") + 
+  stat_summary(fun.data = "mean_cl_normal",
+               geom = "errorbar", 
+               position = position_dodge(width = .9),
+               width = .2) + 
+  theme_classic() + 
+  facet_grid(type_type~type_size) + 
+  scale_fill_discrete(name = "Size of Non-Invariance") + 
+  xlab("Equality Constraints") + 
+  ylab("Normalized Effect Size") + 
+  theme(legend.position = "bottom") + 
+  geom_hline(yintercept = 0) +
+  # geom_hline(yintercept = 1) + 
+  NULL
+
+prop_boot_rr
+
+means_invariant <- boot_rr_DF %>% filter(type == "Invariant") %>% group_by(model) %>% summarize(mean_h = mean(h_nmi_p))
+
+ggsave("figures/prop-boot-rr.png", dpi = 300, 
+       width = 8, 
+       units = "in")
+```
+
+In the data that was simulated to be invariant between groups, effect sizes are still non-zero (loadings $h_{nmi_p}$ = `r apa_num(means_invariant$mean_h[1])`, intercepts = $h_{nmi_p}$ = `r apa_num(means_invariant$mean_h[2])`, $h_{nmi_p}$ = `r apa_num(means_invariant$mean_h[3])`).
+This result mirrors the effects found in the literature - that often, many models fail to show invariance, and potentially not because measurement is poor but because of natural random variation in parameter estimates.
+This result also indicates the need to be able to identify if specific parameters are driving the differences, which is shown in the next section.
+
+Next, Figure \@ref(fig:boot-rr-pic) demonstrates the patterns one might find for small, medium, and large effects at each type of invariance when data is simulated with *one* difference.
+For loadings, the pattern shows a larger effect for loadings with zero or negative effect sizes for other effect sizes.
+The intercept simulations show non-zero effect sizes in the loadings and intercepts, likely for the same reasons $d_{MACS}$ is interpreted as a combined effect size.
+When intercepts are changed, loadings may naturally shift with those means.
+Last, the residual results present an unexpected pattern, wherein the effect is primarily seen in the loadings, rather than the residuals step.
+However, when distributions of error variance are different, one may expect that those effects are pushed toward the loadings as well (as values can vary more, thus potentially weakening the relationship between observed and latent variable).
+
+An example of interpretation on real data is given in a later section.
+From a research study, only one effect size for each equality constraint would be calculated.
+The interpretation will often be up to the researcher's smallest effect of interest, and this simulation gives some guidance that the values should not be interpreted with traditional rules of thumb.
+The pattern of effects is potentially the most useful information: 1) positive effects on the loadings with negative or very close to zero effects on the other parameters may indicate a non-replication in loadings, 2) equal effects on loadings and intercepts with smaller or negative effects may indicate intercepts may be an issue, and 3) residuals may be determined by the same pattern as loadings but with a smaller ratio of loadings to residuals effect (i.e., loadings $h_{nmi}$ / residuals $h_{nmi}$.
+The "size" could be determined by the ratio of effect sizes for each constraint.
+Of course, this represents one simulation study, and results from many studies in a meta-analysis would be fruitful for future work.
+
+## Parameter Replication and Effect Size
+
+```{r create-plot-partial, echo = F, message = F}
+# make all the graphs boot long ----
+boot_long <- 
+  bind_rows(boot.df.full %>% 
+              dplyr::select(term, boot_difference, boot_index_difference, type) %>% 
+              rename(difference = boot_difference, index_difference = boot_index_difference) %>%
+              mutate(type_estimate = "Bootstrapped"), 
+            boot.df.full %>% 
+              dplyr::select(term, random_difference, random_index_difference, type) %>% 
+              rename(difference = random_difference, index_difference = random_index_difference) %>% 
+              mutate(type_estimate = "Random")) %>% 
+  mutate(type_together = paste0(type, " " , type_estimate ))
+
+label_graph <- c(`TRUE` = "Invariant", `FALSE` = "Non-Invariant")
+
+# make all the graphs summary long ----
+# summarize the overall
+boot.partial.summary <- boot.partial.summary.full %>% 
+  dplyr::select(-run_number, computer) %>% 
+  group_by(term, invariant, type) %>% 
+  summarize(across(c(mean_boot_1:d_random_high), ~mean(., na.rm = TRUE)))
+
+boot_summary_long <- 
+  bind_rows(boot.partial.summary %>% 
+              dplyr::select(term, invariant, n_boot, type, starts_with("d_boot")) %>% 
+              rename(n = n_boot, 
+                     d_low = d_boot_low, 
+                     d = d_boot, 
+                     d_high = d_boot_high) %>% 
+              mutate(type_estimate = "Bootstrapped"), 
+            boot.partial.summary %>% 
+              dplyr::select(term, invariant, n_random, type,
+                                    starts_with("d_random")) %>% 
+              rename(n = n_random, 
+                     d_low = d_random_low, 
+                     d = d_random, 
+                     d_high = d_random_high) %>% 
+              mutate(type_estimate = "Random"))
+
+## make all the graphs effects long ----
+# summarize the effects
+boot.effects.summary <- boot.effects.summary.full %>% 
+  dplyr::select(-run_number, -computer) %>% 
+  group_by(term, type) %>% 
+  summarize(across(c(non_invariant:h_mi_p), ~mean(., na.rm = TRUE)))
+
+density_long <- 
+  bind_rows(
+    boot.df.full %>% 
+      dplyr::select(term, boot_index_difference, boot_1, boot_2, type) %>% 
+      pivot_longer(cols = c(boot_1, boot_2), 
+                   names_to = "group", 
+                   values_to = "estimate") %>% 
+      rename(invariant = boot_index_difference) %>% 
+      mutate(type_estimate = "Bootstrapped"), 
+    boot.df.full %>% 
+      dplyr::select(term, random_index_difference, random_1, random_2, type) %>% 
+      pivot_longer(cols = c(random_1, random_2), 
+                   names_to = "group", values_to = "estimate") %>% 
+      rename(invariant = random_index_difference) %>% 
+      mutate(type_estimate = "Random")) %>% 
+  mutate(group = gsub("boot_1|random_1", "Group 1", group), 
+         group = gsub("boot_2|random_2", "Group 2", group), 
+         invariant = factor(invariant, 
+                            levels = c("TRUE", "FALSE"), 
+                            labels = c("Invariant", "Non-Invariant")))
+
+```
+
+Figure \@ref(fig:effect-large-loading-pic) shows the effect size differences within large loadings simulations.
+The results demonstrate that most of the loadings were considered non-invariant in the bootstrapped models (while holdings all others equal).
+This result is partially due to simulating very good data, so small changes in loadings results in a drop in fit for our chosen invariance index.
+However, we can use this graph to show that question four shows a possible effect size ranging from `r boot_summary_long %>% filter(type == "Large Loadings") %>% filter(invariant == FALSE) %>% filter(term == "lv =~ q4") %>% filter(type_estimate == "Bootstrapped") %>% pull(d_low) %>% apa_num()` to `r boot_summary_long %>% filter(type == "Large Loadings") %>% filter(invariant == FALSE) %>% filter(term == "lv =~ q4") %>% filter(type_estimate == "Bootstrapped") %>% pull(d_high) %>% apa_num()`.
+The $h_{nmi_p}$ value for question four was `r boot.effects.summary %>% filter(type == "Large Loadings") %>% filter(term == "lv =~ q4") %>% pull(h_nmi_p) %>% apa_num()`, representing about a quarter of a possible total effect.
+Last, the density plot in Figure \@ref(fig:density-large-loading-pic) shows the separation of the two different groups loadings in item four, thus, illustrating group differences in the findings for their loadings.
+Each of the other combination of plots can be found in the supplemental materials.
+
+```{r effect-large-loading-pic, include = T, fig.cap="Bootstrapped and Random Group effect size differences in loadings for the Large Loading difference simulation.
+The size of the point reprensents the number of data points included in that calculation."}
+effect_invariance_plot <- 
+  ggplot(boot_summary_long %>% 
+           filter(type == "Large Loadings"), 
+         aes(term, d, color = type_estimate)) + 
+  theme_classic() + 
+  facet_wrap(~invariant, labeller = as_labeller(label_graph)) +
+  scale_color_discrete(name = "Type of Estimate") + 
+  geom_point(aes(size = n)) + 
+  geom_errorbar(aes(ymin = d_low, ymax = d_high), width = 0.2) + 
+  xlab("Estimated Item") + 
+  ylab("Group Effect Size") + 
+  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1), 
+        legend.position = "bottom") + 
+  geom_hline(yintercept = 0) + 
+  coord_flip()
+
+suppressWarnings(effect_invariance_plot)
+
+ggsave("figures/partial-large-loading-effect.png", dpi = 300, 
+       width = 8, 
+       units = "in")
+```
+
+```{r density-large-loading-pic, include = T,  fig.cap="Bootstrapped and Random density plots for invariant and non-invariant bootstrapped partial effects examining only large loadings."}
+density_plot <- ggplot(density_long %>% 
+                        filter(type == "Large Loadings"), 
+                       aes(x = estimate, y = term, fill = group)) + 
+  geom_density_ridges(alpha = 0.7, scale = 0.9) + 
+  facet_grid(invariant ~ type_estimate) + 
+  theme_classic() + 
+  xlab("Estimated Score") + 
+  ylab("Parameter") + 
+  scale_fill_discrete(name = "Group")
+
+suppressMessages(density_plot)
+
+ggsave("figures/partial-large-loading-density.png", dpi = 300, 
+       width = 8, 
+       units = "in")
+```
+
+## MGCFA Model Fit Statistics
 

### 2024-07-29 appendix_7.Rmd
updated manuscript

@@
   filter(DF$sample == "Student") %>% 
-  mutate(group = "Schulenberg") %>% 
+  mutate(group = "Aiena") %>% 
   dplyr::select(RS1:RS14, group)
@@
 
+# export(boot.model.rs, "manu_data/boot.model.rs.appendix7.csv")
+
 boot.model.rs
@@
 )
+
+saveRDS(boot.partial.rs, "manu_data/boot.partial.rs.appendix7.Rdata")
 ```
@@
 
-The examination of the density plot shows how group 1 (Schulenberg English) tends to show lower average scores than group 2 (Chen Chinese) for most but not all items.
+The examination of the density plot shows how group 1 (Aiena English) tends to show lower average scores than group 2 (Chen Chinese) for most but not all items.
 

### 2024-07-29 manuscript.Rmd
updated manuscript

@@
 ---
-title             : "visualizemi: Visualization, Effect Size, and Replication of Measurement Invariance for Registered Reports"
-shorttitle        : "VISUAL MGCFA"
+title: "visualizemi: Visualization, Effect Size, and Replication of Measurement Invariance for Registered Reports"
+shorttitle: "VISUAL MGCFA"
 
 author: 
-  - name          : "Erin M. Buchanan"
-    affiliation   : "1"
-    corresponding : yes    # Define only one corresponding author
-    address       : "326 Market St., Harrisburg, PA, USA"
-    email         : "ebuchanan@harrisburgu.edu"
+  - name: "Erin M. Buchanan"
+    affiliation: "1"
+    corresponding: yes    # Define only one corresponding author
+    address: "326 Market St., Harrisburg, PA, USA"
+    email: "ebuchanan@harrisburgu.edu"
 
 affiliation:
-  - id            : "1"
-    institution   : "Harrisburg University of Science and Technology"
+  - id: "1"
+    institution: "Harrisburg University of Science and Technology"
 
@@
 Journals such as *Assessment* regularly publish articles supporting measures of latent constructs wherein a measurement model is established.
-Confirmatory factor analysis can be used to investigate the replicability and generalizability of the measurement model in new samples, while multi-group confirmatory factor analysis is used to examine the measurement model across groups within samples [@brown2015].
+Confirmatory factor analysis can be used to investigate the replicability and generalizability of the measurement model in new samples, while multigroup confirmatory factor analysis is used to examine the measurement model across groups within samples [@brown2015].
 With the rise of the replication crisis and "psychology's renaissance" [@nelson2018], interest in divergence in measurement has increased, often focused on small parameter differences within the latent model.
@@
 
-keywords          : "multigroup confirmatory factor analysis, measurement invariance, visualization, effect size"
-
-floatsintext      : no
-linenumbers       : yes
-draft             : no
-mask              : no
-
-figurelist        : no
-tablelist         : no
-footnotelist      : no
-
-classoption       : "man"
+keywords: "multigroup confirmatory factor analysis, measurement invariance, visualization, effect size"
+
+floatsintext: no
+linenumbers: yes
+draft: no
+mask: no
+
+figurelist: no
+tablelist: no
+footnotelist: no
+
+classoption: "man"
 bibliography: includes/references.bib
@@
 Measurement invariance has been explored and implemented for the last fifty years [@jöreskog1971; @sörbom1978] and implemented in the most popular structural equation modeling programs [@jöreskog2001; @rosseel2012; @boker2011].
-@byrne1989 extended the ideas of multi-group testing by suggesting partial invariance [followed by @meredith1993].
+@byrne1989 extended the ideas of multigroup testing by suggesting partial invariance [followed by @meredith1993].
 Partial invariance occurs when non-invariance is found but can be attributed to only a few parameter estimate differences between groups (i.e., items 1 and 2 have different factor loadings but all others are the same).
@@
 
-Therefore, purpose of this manuscript is to describe an *R* package, `visualizemi`, that provides functionality to calculate multi-group confirmatory factor analysis, partial invariance tests, visualizations of the size of non-invariance, and potential effect sizes for overall models and individual parameters.
+Therefore, purpose of this manuscript is to describe an *R* package, `visualizemi`, that provides functionality to calculate multigroup confirmatory factor analysis, partial invariance tests, visualizations of the size of non-invariance, and potential effect sizes for overall models and individual parameters.
 No known visualization techniques have been proposed for measurement invariance.
@@
 
-1.  Learn how to use *visualizemi* to analyze multi-group confirmatory factor analysis, examine partial for invariance, and create visualizations of parameters.
-2.  Learn how to estimate the potential replication of multi-group models and their parameters using bootstrapping compared to a random group model.
+1.  Learn how to use *visualizemi* to analyze multigroup confirmatory factor analysis, examine partial for invariance, and create visualizations of parameters.
+2.  Learn how to estimate the potential replication of multigroup models and their parameters using bootstrapping compared to a random group model.
 3.  Be able to calculate and interpret effect sizes for model and parameter replication, as well as parameter group differences.
@@
 
-The tutorial will start with simulated data based on known effect sizes using $d_{MACS}$ and demonstrating the package functions for 1) running the multigroup analysis, 2) running a partial invariance analysis, 3) plotting the partial invariance, 4) estimating replication and effect sizes at the model level, and 5) estimating replication and effect sizes at the parameter level.
-Last, data from @aiena2014 examining the measurement invariance of the RS-14 [@wagnild2009] will be used to demonstrate the application of the package on real data.
+The tutorial will start with a general overview of relevant topics to orient readers to invariance testing and MGCFA effect sizes.
+Next, the reader will learn about the `visualizemi` package functions for 1) running the multigroup analysis, 2) running a partial invariance analysis, 3) plotting the partial invariance, 4) estimating replication and effect sizes at the model level, and 5) estimating replication and effect sizes at the parameter level.
+Last, data from @aiena2014 and @chen2020 examining the measurement invariance of the RS-14 [@wagnild2009] will be used to demonstrate the application of the package on real data.
 The *visualizemi* package vignette includes an additional tutorial walk through.
 
-# Method
-
-## Design and Analysis
-
-Data was simulated using the `simulateData` function in the *R* package *lavaan* [@rosseel2012] assuming multivariate normality using a $\mu$ of 0 and $\sigma$ of 1 for the data.
-This function allows you to write *lavaan* syntax for your model with estimated values to generate data for observed variables (see supplemental for examples).
-The data included two groups of individuals ("Group 1", "Group 2") for a multi-group confirmatory factor analysis ($n_{group}$ = 250, *N* = 500).
-The latent variables were assumed to be continuous normal (the package functions do not require this assumption).
-The model consisted of five observed items predicted by one latent variable (`lv =~ q1 + q2 + q3 + q4 + q5`); however, the demonstration in this manuscript extends to multiple latent variables and other combinations of observed variables.
-Each item was assumed to be related to the latent variable with loadings approximately equal to .40 to .80, except when cases of non-invariance on the loadings was simulated.
-
-The @brown2015 steps of testing measurement invariance are demonstrated in this manuscript for illustration purposes, but in line with @stark2006 suggestions, the visualizations show the impact of loadings and intercepts together.
-A convenience function `mgcfa` is used for these steps or other measurement invariance test orders and combinations.
-Fit indices for the steps for multi-group models are presented in the appendix for comparison of cutoff rules of thumb [@cheung2002] to effect sizes and visualizations presented in this manuscript.
-Fit indices include Akaike Information Criterion [AIC, @akaike1998], Bayesian Information Criterion [BIC, @schwarz1978], Comparative Fit Index [CFI, @bentler1990], Tucker Lewis Index [TLI, @tucker1973], root mean squared error of approximation RMSEA [@steiger1990], and standardized root mean square residual [SRMR, @bentler1995].
-
-The data was then simulated to represent invariance across all model steps, small, medium, and large invariance using $d_{MACS}$ estimated sizes from @nye2019.
-While $d_{MACS}$ is used primarily for an effect size of the (non)-invariance for intercepts and loadings together, a similar approach was taken for the estimation of small, medium, and large effects on the residuals.
-The effect size is presented for all models, calculated from the *dmacs* package [@dueber2023; @nye2011].
-Only one item in each model was manipulated from the invariant model to create the non-invariant models.
-Given the data was simulated with a *z*-score scaling, the loading values were simulated at .30 points apart (given $d_{MACS}$ suggestions of .2, .4, .7), the intercepts at .25 points apart, and the residuals at .25 points apart.
-To plan a simulation for your own study, these values can be used to simulate small, medium, and large non-invariance effects by first converting data into *z*-score.
-
-# Package Code Examples
-
-The complete code for this manuscript can be found at <https://osf.io/wev5f/>.
+# Terminology
+
+## MGCFA
+
+Multigroup confirmatory factor analysis (MGCFA) was proposed as a method to examine differences in scale functioning across groups [@brown2015] using structural equation modeling and confirmatory factor analysis (CFA).
+The goal of MGCFA is to determine if groups are invariant or show the same response patterns on the scale.
+MGCFA is often performed in sequential steps to determine the location and impact of potential non-invariance.
+The most common procedure starts by examining overall scale structure for each group individually to show that the groups can be combined into one nested model (i.e., both models at least converge).
+The combined model, often described as the *configural* model, creates one CFA for both groups that allows each group's estimated parameters to vary.
+Equality constraints between group parameters are then added sequentially to the model [@brown2015].
+If parameters are found to be equivalent between groups, these models are considered "invariant", suggesting that any subtle differences in the parameter estimate should not effect overall scoring and assessment.
+
+The first equality constraint added is usually the item factor loadings (*metric* model) which requires items to be related to the latent variable at the same strength across groups.
+The intercepts are then constrained to be equal across groups (*scalar* model) to determine the invariance of item averages.
+The item variances (*strict* model) can then be examined to determine if the general variation in item answers are equal across groups.
+Other parameter equality constraints can be set at the latent variable level (latent means, variance, covariances), but the focus is generally on the observable variables and their parameter estimations.
+Non-invariance is determined by examining differences in fit indices between models with constraints versus without [@cheung2002].
+
+## Partial Invariance
+
+If a specific step within the MGCFA testing framework shows non-invariance, partial invariance is often used to investigate where and "how much" invariance occurs [@meredith1993; @byrne1989].
+Similar to *post hoc* follow up tests in ANOVA, each equality constraint for that model is examined one at a time by allowing groups to vary.
+If the model fit improves when groups are allowed to have separate parameter estimations, the item parameter estimate is considered non-invariant.
+When only a few parameters are found that impact invariance, models are considered partially invariant, implying that most, but not all parameters are equal across groups.
+The researcher then interprets the impact of those items and parameters on overall scores and assessment usefulness.
+Partial invariance investigation is a useful tool for finding specific items that vary between groups, but does not fully explain the effect size of the difference between groups and the impact on the overall model.
+
+## Effect Size: $d_{MACS}$
+
+$d_{MACS}$ was developed from Differential Item Functioning (DIF) measurement in Item Response Theory [IRT, @stark2004] wherein the effect size (DIF) portrays the group differences that lead to overall item score differences.
+Item scores can be mathematically defined as:
+
+$$
+\hat{X}_{iR} = \tau_{iR} + \lambda_{iR}\xi
+$$
+
+*i* indicates an individual item, and *R* indicates the reference group [@nye2011].
+Therefore, an individual score is predicted by the intercept of the item ($\tau$) added to the item loading ($\lambda$) times the latent variable score ($\xi$).
+@nye2011 demonstrated that the terminology from IRT and DIF can be used to create a measure of item functioning differences within CFA, $d_{MACS}$.
+$d_{MACS}$ is then the difference of reference group versus focal group (e.g., group 1 versus group 2) divided by a pooled standard deviation similar to formulas for *d* proposed by @cohen2013.
+Therefore, if $\tau$ or $\lambda$ are individually (or both) different across groups, it will impact all the predicted $X_{iR}$ scores, and thus, impact $d_{MACS}$ values.
+While $d_{MACS}$ represents a necessary step for development of effect sizes within CFA, it does not separate the differences in parameters between groups in a way that can be paired with traditional MGCFA testing and partial invariance.
+In addition to the missing effect sizes at model and parameter levels, no effect size to date gives the researcher a feeling for potential replication of the invariant or non-invariant items.
+Last, in line with general suggestions by @cumming2012 and @cumming2016, the visualization of effect sizes in MGCFA would be an added tool for researchers to gauge the size of group differences.
+
+# Package Functions
+
+The %>% code for this manuscript can be found at <https://osf.io/wev5f/>.
 This tutorial was registered at <https://osf.io/vwf4d>, and the example provided at the end of the manuscript was added after that registration.
 The *R* package and replication/effect sizes was added after the original manuscript submission.
-
-```{r create-models}
-# overall model
-model.overall <- "lv =~ q1 + q2 + q3 + q4 + q5
-q1 ~ 0*1
-lv ~ 1"
-
-# build invariant model one factor
-model.invariant.g1 <- "lv =~ .8*q1 + .4*q2 + .6*q3 + .3*q4 + .6*q5 
-q4 ~~ 1*q4
-q4 ~ 0*1
-q1 ~ 0*1
-lv ~ 1"
-model.invariant.g2 <- "lv =~ .81*q1 + .41*q2 + .61*q3 + .31*q4 + .61*q5
-q4 ~~ 1*q4
-q4 ~ 0*1
-q1 ~ 0*1
-lv ~ 1"
-
-# loadings .5, .8, 1.1
-model.small.load.g2 <- "lv =~ .81*q1 + .41*q2 + .61*q3 + .5*q4 + .61*q5
-q1 ~ 0*1
-lv ~ 1"
-model.med.load.g2 <- "lv =~ .81*q1 + .41*q2 + .61*q3 + .8*q4 + .61*q5
-q1 ~ 0*1
-lv ~ 1"
-model.large.load.g2 <- "lv =~ .81*q1 + .41*q2 + .61*q3 + 1.1*q4 + .61*q5
-q1 ~ 0*1
-lv ~ 1"
-
-# build invariance on intercepts .25, .50, and .75
-model.small.int.g2 <- "lv =~ .81*q1 + .41*q2 + .61*q3 + .31*q4 + .61*q5
-q4 ~ .25*1
-q1 ~ 0*1
-lv ~ 1"
-model.med.int.g2 <- "lv =~ .81*q1 + .41*q2 + .61*q3 + .31*q4 + .61*q5
-q4 ~ .5*1
-q1 ~ 0*1
-lv ~ 1"
-model.large.int.g2 <- "lv =~ .81*q1 + .41*q2 + .61*q3 + .31*q4 + .61*q5
-q4 ~ .75*1
-q1 ~ 0*1
-lv ~ 1"
-
-# build invariance on residuals .25, .50, and .75
-model.small.res.g2 <- "lv =~ .81*q1 + .41*q2 + .61*q3 + .31*q4 + .61*q5
-q4 ~~ .75*q4
-q1 ~ 0*1
-lv ~ 1"
-model.med.res.g2 <- "lv =~ .81*q1 + .41*q2 + .61*q3 + .31*q4 + .61*q5
-q4 ~~ .5*q4
-q1 ~ 0*1
-lv ~ 1"
-model.large.res.g2 <- "lv =~ .81*q1 + .41*q2 + .61*q3 + .31*q4 + .61*q5
-q4 ~~ .25*q4
-q1 ~ 0*1
-lv ~ 1"
-```
-
-```{r create-data}
-# simulate data invariant
-df.invariant <- bind_rows(
-  simulateData(model.invariant.g1, sample.nobs = 250, 
-               meanstructure = T, model.type = "cfa",
-               seed = 1234) %>% 
-    mutate(group = "Group 1"), 
-  simulateData(model.invariant.g2, sample.nobs = 250, 
-               meanstructure = T, model.type = "cfa",
-               seed = 1234) %>% 
-    mutate(group = "Group 2") 
-)
-
-# simulate data small load
-df.small.load <- bind_rows(
-  simulateData(model.invariant.g1, sample.nobs = 250, 
-               meanstructure = T, model.type = "cfa",
-               seed = 1234) %>% 
-    mutate(group = "Group 1"), 
-  simulateData(model.small.load.g2, sample.nobs = 250, 
-               meanstructure = T, model.type = "cfa",
-               seed = 1234) %>% 
-    mutate(group = "Group 2") 
-)
-
-# simulate data med load
-df.med.load <- bind_rows(
-  simulateData(model.invariant.g1, sample.nobs = 250, 
-               meanstructure = T, model.type = "cfa",
-               seed = 1234) %>% 
-    mutate(group = "Group 1"), 
-  simulateData(model.med.load.g2, sample.nobs = 250, 
-               meanstructure = T, model.type = "cfa",
-               seed = 1234) %>% 
-    mutate(group = "Group 2") 
-)
-
-# simulate data large load
-df.large.load <- bind_rows(
-  simulateData(model.invariant.g1, sample.nobs = 250, 
-               meanstructure = T, model.type = "cfa",
-               seed = 1234) %>% 
-    mutate(group = "Group 1"), 
-  simulateData(model.large.load.g2, sample.nobs = 250, 
-               meanstructure = T, model.type = "cfa",
-               seed = 1234) %>% 
-    mutate(group = "Group 2") 
-)
-
-# simulate data small int
-df.small.int <- bind_rows(
-  simulateData(model.invariant.g1, sample.nobs = 250, 
-               meanstructure = T, model.type = "cfa",
-               seed = 1234) %>% 
-    mutate(group = "Group 1"), 
-  simulateData(model.small.int.g2, sample.nobs = 250, 
-               meanstructure = T, model.type = "cfa",
-               seed = 1234) %>% 
-    mutate(group = "Group 2") 
-)
-
-# simulate data med int
-df.med.int <- bind_rows(
-  simulateData(model.invariant.g1, sample.nobs = 250, 
-               meanstructure = T, model.type = "cfa",
-               seed = 1234) %>% 
-    mutate(group = "Group 1"), 
-  simulateData(model.med.int.g2, sample.nobs = 250, 
-               meanstructure = T, model.type = "cfa",
-               seed = 1234) %>% 
-    mutate(group = "Group 2") 
-)
-
-# simulate data large int
-df.large.int <- bind_rows(
-  simulateData(model.invariant.g1, sample.nobs = 250, 
-               meanstructure = T, model.type = "cfa",
-               seed = 1234) %>% 
-    mutate(group = "Group 1"), 
-  simulateData(model.large.int.g2, sample.nobs = 250, 
-               meanstructure = T, model.type = "cfa",
-               seed = 1234) %>% 
-    mutate(group = "Group 2") 
-)
-
-# simulate data small res
-df.small.res <- bind_rows(
-  simulateData(model.invariant.g1, sample.nobs = 250, 
-               meanstructure = T, model.type = "cfa",
-               seed = 1234) %>% 
-    mutate(group = "Group 1"), 
-  simulateData(model.small.res.g2, sample.nobs = 250, 
-               meanstructure = T, model.type = "cfa",
-               seed = 1234) %>% 
-    mutate(group = "Group 2") 
-)
-
-# simulate data med res
-df.med.res <- bind_rows(
-  simulateData(model.invariant.g1, sample.nobs = 250, 
-               meanstructure = T, model.type = "cfa",
-               seed = 1234) %>% 
-    mutate(group = "Group 1"), 
-  simulateData(model.med.res.g2, sample.nobs = 250, 
-               meanstructure = T, model.type = "cfa",
-               seed = 1234) %>% 
-    mutate(group = "Group 2") 
-)
-
-# simulate data large res
-df.large.res <- bind_rows(
-  simulateData(model.invariant.g1, sample.nobs = 250, 
-               meanstructure = T, model.type = "cfa",
-               seed = 1234) %>% 
-    mutate(group = "Group 1"), 
-  simulateData(model.large.res.g2, sample.nobs = 250, 
-               meanstructure = T, model.type = "cfa",
-               seed = 1234) %>% 
-    mutate(group = "Group 2") 
-)
-```
-
-```{r run-cfa}
-# invariant CFA
-results.invariant <- 
-  mgcfa(model = model.overall, 
-        data = df.invariant,
-        group = "group",
-        group.equal = c("loadings", "intercepts", "residuals"),
-        meanstructure = T)
-
-d_invariant <- lavaan_dmacs(
-  results.invariant$model_configural, 
-  RefGroup = "Group 1")
-
-# loadings
-results.small.load <- 
-  mgcfa(model = model.overall, 
-        data = df.small.load,
-        group = "group",
-        group.equal = c("loadings", "intercepts", "residuals"),
-        meanstructure = T)
-
-results.med.load <- 
-  mgcfa(model = model.overall, 
-        data = df.med.load,
-        group = "group",
-        group.equal = c("loadings", "intercepts", "residuals"),
-        meanstructure = T)
-results.large.load <- 
-  mgcfa(model = model.overall, 
-        data = df.large.load,
-        group = "group",
-        group.equal = c("loadings", "intercepts", "residuals"),
-        meanstructure = T)
-
-d_small_load <- 
-  lavaan_dmacs(results.small.load$model_configural, 
-               RefGroup = "Group 1")
-d_med_load <- 
-  lavaan_dmacs(results.med.load$model_configural, 
-               RefGroup = "Group 1")
-d_large_load <- 
-  lavaan_dmacs(results.large.load$model_configural, 
-               RefGroup = "Group 1")
-
-# intercepts
-results.small.int <- 
-  mgcfa(model = model.overall, 
-        data = df.small.int,
-        group = "group",
-        group.equal = c("loadings", "intercepts", "residuals"),
-        meanstructure = T)
-results.med.int <- 
-  mgcfa(model = model.overall, 
-        data = df.med.int,
-        group = "group",
-        group.equal = c("loadings", "intercepts", "residuals"),
-        meanstructure = T)
-results.large.int <- 
-  mgcfa(model = model.overall, 
-        data = df.large.int,
-        group = "group",
-        group.equal = c("loadings", "intercepts", "residuals"),
-        meanstructure = T)
-
-d_small_int <- 
-  lavaan_dmacs(results.small.int$model_configural, 
-               RefGroup = "Group 1")
-d_med_int <- 
-  lavaan_dmacs(results.med.int$model_configural, 
-               RefGroup = "Group 1")
-d_large_int <- 
-  lavaan_dmacs(results.large.int$model_configural, 
-               RefGroup = "Group 1")
-
-# residuals
-results.small.res <-
-  mgcfa(model = model.overall, 
-        data = df.small.res,
-        group = "group",
-        group.equal = c("loadings", "intercepts", "residuals"),
-        meanstructure = T)
-results.med.res <- 
-  mgcfa(model = model.overall, 
-        data = df.med.res,
-        group = "group",
-        group.equal = c("loadings", "intercepts", "residuals"),
-        meanstructure = T)
-results.large.res <- 
-  mgcfa(model = model.overall, 
-        data = df.large.res,
-        group = "group",
-        group.equal = c("loadings", "intercepts", "residuals"),
-        meanstructure = T)
-
-d_small_res <- 
-  lavaan_dmacs(results.small.res$model_configural, 
-               RefGroup = "Group 1")
-d_med_res <- 
-  lavaan_dmacs(results.med.res$model_configural,
-               RefGroup = "Group 1")
-d_large_res <- 
-  lavaan_dmacs(results.large.res$model_configural, 
-               RefGroup = "Group 1")
-```
-
-## Multi-group CFA Caculation
+The simulation study used to design plotting functions and test effect sizes can be found in the supplemental materials, along with worked code examples.
+
+## MGCFA: `mgcfa()` Function
 
 First, we would create our model code in *lavaan* syntax [@rosseel2012].
-The `lv` latent variable predicts the five measured variables, which are present as columns in our `df.invariant` data set.
-The package does generally require raw data for bootstrapping purposes, and an example of how to simulate data from models and covariance/correlations tables sometimes provided in manuscripts (rather than the raw data) is provided in the supplemental documentation.
-
-*lavaan* automatically sets the mean (i.e., the intercept) for latent variables to zero.
-If we wish to visualize the impact of the changes in parameter estimates across groups on the latent means, we need to allow the latent mean estimation with `lv ~ 1`.
-However, adding this estimation into our model will create a non-identified model.
-To solve this problem, you can set one of the intercepts of another variable to a value to scale the model.
-Here we will set the scale of the model by using `q1 ~ 0*1`, thus, scaling the expected means to zero.
-With simulation, this step is easy to know which variable to pick - we set the intercept on the variable we know did not show differences.
-In real data, you may wish to run the model steps *without* setting this option, examine the results of a configural or separate models, and then add the option for the values most similar.
-Additionally, you could complete partial invariance steps to determine which value appears most consistent to fix the estimate.
-
-```{r model-example, eval = T, include = T, echo = T, size = "small"}
-# create lavaan model
-model.overall <- "
-# overall one-factor model
-lv =~ q1 + q2 + q3 + q4 + q5
-# set the intercept (mean) of q1 to zero
-q1 ~ 0*1
-# allow the lv intercept to be freely estimated
-lv ~ 1"
-# look at the data
-head(df.invariant)
-```
-
-The `mgcfa` function is designed to flexibly allow you to leverage `lavaan`'s package functions to calculate multiple measurement steps at once. You would include:
-
-1)  the model syntax in the `model` argument
+The *visualizemi* package does generally require raw data for bootstrapping purposes, and an example of how to simulate data from models and covariance/correlations tables that sometimes are provided in manuscripts (rather than the raw data) is provided in the supplemental documentation.
+The `mgcfa()` function is designed to flexibly allow you to leverage *lavaan*'s package functions to calculate multiple measurement steps at once.
+You would include:
+
+1)  the model syntax in the `model` argument.
 2)  the dataframe in the `data` argument of our function
-3)  the name of the grouping variable in quotes for `group`
-4)  and the equality constraints you would like to impose in order in `group.equal`
+3)  the name of the grouping variable in quotes for `group`.
+4)  and the equality constraints you would like to impose in order in `group.equal`.
 5)  `...` any other *lavaan* arguments you would like to use such as `meanstructure` or `estimator`.
-
-Note: you can also use `sample.cov`, `sample.mean`, `sample.nobs` in this step for estimation of multi-group models, but simulated dataframes are needed for bootstrapping replication estimates.
-
-```{r mgcfa-example, echo = T, size = "small"}
-# run our mgcfa function to run all models
-results.invariant <- 
-  # name of the saved model syntax
-  mgcfa(model = model.overall, 
-        # name of the dataframe
-        data = df.invariant,
-        # name of the grouping variable
-        group = "group",
-        # equality constraints to impose in order
-        group.equal = c("loadings", "intercepts", "residuals"),
-        # other options to send to lavaan cfa function
-        meanstructure = T)
-
-# what is saved for you
-names(results.invariant)
-```
 
@@
 This dataframe is created with *broom*'s `tidy()` function if you wish to recreate this table without running the `mgcfa()` function [@robinson2023].
-
-```{r mgcfa-output1, echo = T, include = T, size = "small"}
-results.invariant$model_coef[1:10 , ]
-```
-
 2)  `model_fit`: The model fit indices from `fitmeasures()` to review for overall model fit and invariance judgments. The name of the model is included in a *model* column.
-
-```{r mgcfa-output2, echo = T, include = T, size = "small"}
-head(results.invariant$model_fit)
-```
-
 3)  `model_overall`: A saved *lavaan* fitted model of all groups together without any equality constraints or grouping variables.
@@
 
-## Visualization of Invariance
-
-### Package Function
-
-The results from the `model_coef` table can then be used directly in `plot_mi()`. The plot outputs will be described below. First, here are the arguments for the function:
+## Partial Invariance: `partial_mi()` Function
+
+The `partial_mi()` function aids in the calculation of partial invariance for a specific step of the MGCFA process. The function includes the following arguments:
+
+1)  `saved_model`: The saved *lavaan* model with the equality constraints at the level of measurement invariance you would like to examine for partial invariance.
+2)  `data`: The dataframe where the model was estimated.
+3)  `model`: The model syntax for the overall model.
+4)  `group`: The grouping variable column in the dataframe.
+5)  `group.equal`: The equality constraints including in your original multigroup tests.
+6)  `partial_step`: The level of partial invariance you wish to test.
+
+In this function, each parameter with the appropriate *lavaan* syntax is relaxed individually (i.e., `~1` for intercepts, `~~` for residuals, etc.).
+The fitted models are saved in the `models` output, and the `fit_table` output includes all fit indices for each model to investigate potential areas of partial invariance based on the researcher's desired criterion.
+
+## Visualization of Invariance: `plot_mi()` Function
+
+Once we know which items are non-invariant, the `model_coef` output from the `mgcfa()` can be used directly in `plot_mi()`.
+The plot outputs will be described below.
+First, here are the arguments for the function:
 
@@
 If you have items that load onto multiple latent variables, you will need to make multiple plots.
-9)  `plot_groups`: If you include more than two groups in a multi-group model, the automatic assumption is that you want the first two groups for this visualization.
+9)  `plot_groups`: If you include more than two groups in a multigroup model, the automatic assumption is that you want the first two groups for this visualization.
 If not, include the names of the groups here to plot.
-
-```{r plot-example, eval = T, echo = T, include = T, size = "small"}
-invariant.plot <- 
-  plot_mi(
-    # output from model_coef
-    data_coef = results.invariant$model_coef, 
-    # which model do you want to plot
-    model_step = "Configural", 
-    # name of observed item
-    item_name = "q4", 
-    # latent variable limits to graph
-    x_limits = c(-1,1), 
-    # Y min and max in data 
-    y_limits = c(min(df.invariant$q4), max(df.invariant$q4)),
-    # what ci do you want
-    conf.level = .95, 
-    # what model results do you want 
-    model_results = results.invariant$model_configural,
-    # which latent variable do you want 
-    lv_name = "lv" 
-)
-
-names(invariant.plot)
-```
 
@@
 
-```{r invariant-pic, include = T, fig.cap = "Invariant Model Visualization"}
-invariant.plot$complete
-
-ggsave("figures/invariant-visual.png", dpi = 300, 
-       width = 8, 
-       units = "in")
+```{r invariant-pic, include = T, fig.cap = "Invariant model visualization demonstrating the components of the `plot_mi()` function in *visualizemi*.", fig.height=8}
+knitr::include_graphics("figures/invariant-visual.png")
 ```
@@
 Factor loadings represent the slope of the regression equation for the latent variable predicting the scores on the observed variable ($\hat{Y} \sim b_0 + b_1X + \epsilon$).
-The y-axis indicates the observed variable scores, and here, the plot includes the entire range of the scale of the data for item four.
-The coefficient ($b_1$) for group 1 was `r apa_num(results.invariant$model_coef %>% filter(model == "Configural") %>% filter(grepl("q4", term)) %>% filter(op == "=~") %>% slice_head() %>% pull(estimate))`, while the coefficient for group 2 was `r apa_num(results.invariant$model_coef %>% filter(model == "Configural") %>% filter(grepl("q4", term)) %>% filter(op == "=~") %>% slice_tail() %>% pull(estimate))`.
+The y-axis indicates the observed variable scores, and here, the plot includes the entire range of the scale of the data this simulated item.
 The ribbon bands around the plotted slopes indicate the confidence interval for that estimate.
@@
 These are represented by a dot with a set of confidence error bars around the point.
-The intercept for group 1 was `r apa_num(results.invariant$model_coef %>% filter(model == "Configural") %>% filter(grepl("q4", term)) %>% filter(op == "~1") %>% slice_head() %>% pull(estimate))`, while the coefficient for group 2 was `r apa_num(results.invariant$model_coef %>% filter(model == "Configural") %>% filter(grepl("q4", term)) %>% filter(op == "~1") %>% slice_tail() %>% pull(estimate))`.
 In this invariant depiction, the overlap in the intercepts is clear, indicating they are not different.
@@
 Therefore, residuals are represented in the inset picture at the bottom right of the item invariance plot.
-The black bars represent the estimated residual for each group (group 1: `r apa_num(results.invariant$model_coef %>% filter(model == "Configural") %>% filter(grepl("q4", term)) %>% filter(op == "~~") %>% slice_head() %>% pull(estimate))`, group 2: `r apa_num(results.invariant$model_coef %>% filter(model == "Configural") %>% filter(grepl("q4", term)) %>% filter(op == "~~") %>% slice_tail() %>% pull(estimate))`).
+The black bars represent the estimated residual for each group.
 The distributions are plotted to represent the normal spread of values using the standard error of the residuals.
@@
 
-### Simulated Results
-
-The $d_{MACS}$ value for item 4 in the invariant model was `r apa_num(d_invariant)$DMACS[4]`, representing a nil or unimportant difference in this manuscript.
-It is important to note that while @nye2019 suggests specific sizes for small, medium, and large, each researcher should determine for themselves what effects represent.
-Figure \@ref(fig:small-load-pic) displays the results from the small ($d_{MACS}$ = `r apa_num(d_small_load)$DMACS[4]`) difference in loadings, while Figure \@ref(fig:med-load-pic) displays the results from the medium ($d_{MACS}$ = `r apa_num(d_med_load)$DMACS[4]`) difference in loadings, and Figure \@ref(fig:large-load-pic) shows the large ($d_{MACS}$ = `r apa_num(d_large_load)$DMACS[4]`) differences.
-When investigating the slope values, we can clearly see the change in the loading for the second group (the only manipulated variable, although random data set generation may also change intercepts and residuals slightly).
-At the medium effect size, we see that the confidence bands do not overlap (at the edges), and at the large effect size, we can see a clear separation of two lines.
-Note that the intercepts in this model are estimated as equal so the loading representation will not literally separate, but the steepness of the lines is the indicator of the difference between the slopes.
-You can imagine these lines are interpreted like a simple slopes analysis for interactions in regression [@cohen2003].
-When simple slopes for interactions are plotted, if they are parallel, there is no interaction, and if they cross, then there is an interaction.
-Here, we can use this same logic.
-If they are parallel, there is likely invariance (they are the same), and the further from parallel they become, the larger the effect size for the differences between group loadings.
-
-The latent means in Figure \@ref(fig:large-load-pic) do appear to show differences, albeit visually small.
-The latent means diagram shows the impact of any group differences that aren't constrained, and this image shows the configural model (as the metric model would force them to be equal).
-In the simulated model, the *only* manipulated parameter is question 4's loading.
-In real models, the differences may be larger due to other variation found in the parameter estimates.
-Therefore, once you discover items you believe would make a model "partially" invariant, you may wish to estimate that model and graph the item again using the partially invariant model to see only the effect of the non-invariant items.
-Additionally, consider that we set the scaling of the model to 0.
-The estimate for the lv mean in the large loading model was group 1: `r apa_num(results.invariant$model_coef %>% filter(model == "Configural") %>% filter(grepl("lv", term)) %>% filter(op == "~1") %>% slice_head() %>% pull(estimate))`, and group 2: `r apa_num(results.invariant$model_coef %>% filter(model == "Configural") %>% filter(grepl("lv", term)) %>% filter(op == "~1") %>% slice_tail() %>% pull(estimate))`, which results in `r apa_num(results.invariant$model_coef %>% filter(model == "Configural") %>% filter(grepl("lv", term)) %>% filter(op == "~1") %>% slice_head() %>% pull(estimate) - results.invariant$model_coef %>% filter(model == "Configural") %>% filter(grepl("lv", term)) %>% filter(op == "~1") %>% slice_tail() %>% pull(estimate))` difference in group means.
-The practical implications of this difference will depend on the research and interpretations of the researcher.
-
-```{r small-load-pic, include = T, fig.cap = "Small Loadings Model Visualization"}
-plot_mi(
-  data_coef = results.small.load$model_coef, # output from model_coef
-  model_step = "Configural", # which model
-  item_name = "q4", # name of observed item
-  x_limits = c(-1,1), # LV limits to graph
-  y_limits = c(min(df.small.load$q4), max(df.small.load$q4)), # Y min and max in data 
-  conf.level = .95, # what ci do you want
-  model_results = results.small.load$model_configural, # what model results do you want 
-  lv_name = "lv"
-)$complete
-
-ggsave("figures/small-load-visual.png", dpi = 300, 
-       width = 8, 
-       units = "in")
-```
-
-```{r med-load-pic, include = T, fig.cap = "Medium Loadings Model Visualization"}
-plot_mi(
-  data_coef = results.med.load$model_coef, # output from model_coef
-  model_step = "Configural", # which model
-  item_name = "q4", # name of observed item
-  x_limits = c(-1,1), # LV limits to graph
-  y_limits = c(min(df.med.load$q4), max(df.med.load$q4)), # Y min and max in data 
-  conf.level = .95, # what ci do you want
-  model_results = results.med.load$model_configural, # what model results do you want 
-  lv_name = "lv"
-)$complete
-
-ggsave("figures/med-load-visual.png", dpi = 300, 
-       width = 8, 
-       units = "in")
-```
-
-```{r large-load-pic, include = T, fig.cap = "Large Loadings Model Visualization"}
-plot_mi(
-  data_coef = results.large.load$model_coef, # output from model_coef
-  model_step = "Configural", # which model
-  item_name = "q4", # name of observed item
-  x_limits = c(-1,1), # LV limits to graph
-  y_limits = c(min(df.large.load$q4), max(df.large.load$q4)), # Y min and max in data 
-  conf.level = .95, # what ci do you want
-  model_results = results.large.load$model_configural, # what model results do you want 
-  lv_name = "lv"
-)$complete
-
-ggsave("figures/large-load-visual.png", dpi = 300, 
-       width = 8, 
-       units = "in")
-```
-
-For intercepts, the small (Figure \@ref(fig:small-int-pic)), medium (Figure \@ref(fig:med-int-pic)), and large (Figure \@ref(fig:large-int-pic)) depictions represent $d_{MACS}$ values of `r apa_num(d_small_int)$DMACS[4]`, `r apa_num(d_med_int)$DMACS[4]`, and `r apa_num(d_large_int)$DMACS[4]`, respectively.
-Intercept differences can be clearly seen represented by the spacing out of the intercept locations (and thus, the overall line as well).
-While the changes in intercept do not appear to change the latent means, the caveat to this simulation is that only item four was manipulated.
-An example is provided below that demonstrates large changes in latent means.
-
-```{r small-int-pic, include = T, fig.cap = "Small Intercepts Model Visualization"}
-plot_mi(
-  data_coef = results.small.int$model_coef, # output from model_coef
-  model_step = "loadings", # which model
-  item_name = "q4", # name of observed item
-  x_limits = c(-1,1), # LV limits to graph
-  y_limits = c(min(df.small.int$q4), max(df.small.int$q4)), # Y min and max in data 
-  conf.level = .95, # what ci do you want
-  model_results = results.small.int$invariance_models$model.loadings, # what model results do you want 
-  lv_name = "lv"
-)$complete
-
-ggsave("figures/small-int-visual.png", dpi = 300, 
-       width = 8, 
-       units = "in")
-```
-
-```{r med-int-pic, include = T, fig.cap = "Medium Intercepts Model Visualization"}
-plot_mi(
-  data_coef = results.med.int$model_coef, # output from model_coef
-  model_step = "loadings", # which model
-  item_name = "q4", # name of observed item
-  x_limits = c(-1,1), # LV limits to graph
-  y_limits = c(min(df.med.int$q4), max(df.med.int$q4)), # Y min and max in data 
-  conf.level = .95, # what ci do you want
-  model_results = results.med.int$invariance_models$model.loadings, # what model results do you want 
-  lv_name = "lv"
-)$complete
-
-ggsave("figures/med-int-visual.png", dpi = 300, 
-       width = 8, 
-       units = "in")
-```
-
-```{r large-int-pic, include = T, fig.cap = "Large Intercepts Model Visualization"}
-plot_mi(
-  data_coef = results.large.int$model_coef, # output from model_coef
-  model_step = "loadings", # which model
-  item_name = "q4", # name of observed item
-  x_limits = c(-1,1), # LV limits to graph
-  y_limits = c(min(df.large.int$q4), max(df.large.int$q4)), # Y min and max in data 
-  conf.level = .95, # what ci do you want
-  model_results = results.large.int$invariance_models$model.loadings, # what model results do you want 
-  lv_name = "lv"
-)$complete
-
-ggsave("figures/large-int-visual.png", dpi = 300, 
-       width = 8, 
-       units = "in")
-```
-
-Last, the effect of the residuals is plotted in small (Figure \@ref(fig:small-res-pic)), medium (Figure \@ref(fig:med-res-pic)), and large (Figure \@ref(fig:large-res-pic)) formats.
-While $d_{MACS}$ values are not technically available for the residuals, our models showed `r apa_num(d_small_res)$DMACS[4]`, `r apa_num(d_med_res)$DMACS[4]`, and `r apa_num(d_large_res)$DMACS[4]`, respectively.
-These differences in values are variable due to the random generation of data sets for each measurement invariance manipulation.
-At first glance, the differences in the small chart may seem large, because the black lines are not touching, but notice that the distributions overlap, indicating a likely small difference.
-The medium and large differences better illustrate differences in residuals across groups.
-Further, the impact of the residuals on the shape of the latent mean distribution can also been seen (and unintentionally, in the first figures as well due to random variation).
-The impact is due to the standard error of the residuals, as smaller standard errors represent lepokurtic distributions (taller), and larger standard errors represent platykurtic distributions (flatter).
-The effect size difference of the residuals does not appear to change the effects in the latent means.
-
-```{r small-res-pic, include = T, fig.cap = "Small Residuals Model Visualization"}
-plot_mi(
-  data_coef = results.small.res$model_coef, # output from model_coef
-  model_step = "intercepts", # which model
-  item_name = "q4", # name of observed item
-  x_limits = c(-1,1), # LV limits to graph
-  y_limits = c(min(df.small.res$q4), max(df.small.res$q4)), # Y min and max in data 
-  conf.level = .95, # what ci do you want
-  model_results = results.small.res$invariance_models$model.intercepts, # what model results do you want 
-  lv_name = "lv"
-)$complete
-
-ggsave("figures/small-res-visual.png", dpi = 300, 
-       width = 8, 
-       units = "in")
-```
-
-```{r med-res-pic, include = T, fig.cap = "Medium Residuals Model Visualization"}
-plot_mi(
-  data_coef = results.med.res$model_coef, # output from model_coef
-  model_step = "intercepts", # which model
-  item_name = "q4", # name of observed item
-  x_limits = c(-1,1), # LV limits to graph
-  y_limits = c(min(df.med.res$q4), max(df.med.res$q4)), # Y min and max in data 
-  conf.level = .95, # what ci do you want
-  model_results = results.med.res$invariance_models$model.intercepts, # what model results do you want 
-  lv_name = "lv"
-)$complete
-
-ggsave("figures/med-res-visual.png", dpi = 300, 
-       width = 8, 
-       units = "in")
-```
-
-```{r large-res-pic, include = T, fig.cap = "Large Residuals Model Visualization"}
-plot_mi(
-  data_coef = results.large.res$model_coef, # output from model_coef
-  model_step = "intercepts", # which model
-  item_name = "q4", # name of observed item
-  x_limits = c(-1,1), # LV limits to graph
-  y_limits = c(min(df.large.res$q4), max(df.large.res$q4)), # Y min and max in data 
-  conf.level = .95, # what ci do you want
-  model_results = results.large.res$invariance_models$model.intercepts, # what model results do you want 
-  lv_name = "lv"
-)$complete
-
-ggsave("figures/large-res-visual.png", dpi = 300, 
-       width = 8, 
-       units = "in")
-```
-
-## Partial Invariance Calculation
-
-### Package Function
-
-The results of the simulated models are presented in the appendix, demonstrating that each simulated dataset shows partial invariance if item four is allowed to vary between groups.
-The function takes the following arguments:
-
-1)  `saved_model`: The saved *lavaan* model with the equality constraints at the level of measurement invariance you would like to examine for partial invariance.
-2)  `data`: The dataframe where the model was estimated.
-3)  `model`: The model syntax for the overall model.
-4)  `group`: The grouping variable column in the dataframe.
-5)  `group.equal`: The equality constraints including in your original multi-group tests.
-6)  `partial_step`: The level of partial invariance you wish to test.
-
-```{r partial-example, echo = T, size = "small"}
-partial.invariant <-
-  partial_mi(
-    # saved model output with constraints
-    saved_model = results.invariant$invariance_models$model.residuals,
-    # dataframe from model 
-    data = df.invariant,
-    # model syntax 
-    model = model.overall,
-    # group column name 
-    group = "group",
-    # group equality constraints from your mgcfa
-    group.equal = c("loadings", "intercepts", "residuals"),
-    # which step you want to examine for partial invariance
-    partial_step = "residuals"
-    )
-
-names(partial.invariant)
-```
-
-In this function, each parameter with the appropriate *lavaan* syntax is relaxed individually (i.e., `~1` for intercepts, `~~` for residuals, etc.).
-The fitted models are saved in the `models` output, and the `fit_table` output includes all fit indices for each model to investigate potential areas of partial invariance based on the researcher's desired criterion.
-Note: the `partial_step` function is used to determine which types of `op` or operators to freely estimate between groups.
-If one chooses residuals, you will also freely estimate the residual for the latent variable or any other residuals found in the model.
-These items may be ignored if they were not meant to be included.
-
-```{r partial-example2, echo = T, size = "small"}
-head(partial.invariant$fit_table %>% 
-       dplyr::select(free.parameter, cfi, rmsea))
-```
-
-## Replication and Effect Size: Model
-
-### Package Function
+## Model Replication and Effect Sizes: `bootstrap_model()` Function
 
@@
 7)  `invariance_rule`: The invariance difference score you would like to use as your rule.
-8)  `group.equal`: The equality constraints including in your original multi-group tests.
-
-```{r boot-rr, echo = T, eval = F, size = "small"}
-boot.model.invariant <- 
-  bootstrap_model(
-    # saved configural model 
-    saved_configural = results.invariant$model_configural,
-    # dataframe
-    data = df.invariant,
-    # model syntax
-    model = model.overall, 
-    # group variable column in dataframe
-    group = "group",
-    # number of bootstraps
-    nboot = 1000, 
-    # which fit index you would like to use
-    invariance_index = "cfi",
-    # what is your criterion for that fit index
-    invariance_rule = .01,
-    # what equality constraints are you testing 
-    group.equal = c("loadings", "intercepts", "resduals")
-  )
-```
+8)  `group.equal`: The equality constraints including in your original multigroup tests.
 
@@
 
-### Simulated Results
-
-Figure \@ref(fig:boot-rr-pic) portrays the $h_{nmi_p}$ values by simulated non-invariance, strength of non-invariance, and type of equality constraint.
-This image represents 100 simulations of data by 1000 bootstrapped runs (averaged) to explore the expected pattern of results.
-The bars are arranged to show what a researcher might inspect when thinking about replication possibilities and their effect sizes (i.e., only three bars for each equality constraint would be calculated).
-
-```{r boot-rr-pic, include = T, fig.cap = "Visualization of the effect size of bootstrapped replication proportions on simulated data.
-Each panel indicates the simulated data type, colors represent the differences in the strength of the non-invariance, and the bars on the x-axis represent the effect size for the equality constraint.
-"}
-
-boot_rr_DF <- boot_rr_DF %>% 
-  mutate(type_size = ifelse(
-    type == "Invariant", "None", ifelse(
-      grepl("Small", type), "Small", ifelse(
-        grepl("Medium", type), "Medium", "Large"
-      )
-    )
-  ),
-  type_type = ifelse(
-    type == "Invariant", "Invariant", ifelse(
-      grepl("Loadings", type), "Loadings", ifelse(
-        grepl("Intercepts", type), "Intercepts", "Residuals"
-      )
-    ) 
-  ),
-  model = factor(model, 
-                 levels = c("loadings", "intercepts", "residuals"),
-                 labels = c("Loadings", "Intercepts", "Residuals")),
-  type_size = factor(type_size, 
-                     levels = c("None", "Small", "Medium", "Large")),
-  type_type = factor(type_type, 
-                     levels = c("Invariant", "Loadings", "Intercepts", "Residuals")))
-
-prop_boot_rr <- ggplot(boot_rr_DF %>% 
-                         filter(type_type != "Invariant"), 
-                       aes(x = model, 
-                       y = h_nmi_p,
-                       fill = type_size)) + 
-  stat_summary(fun = "mean", 
-               position = "dodge", 
-               geom = "bar") + 
-  stat_summary(fun.data = "mean_cl_normal",
-               geom = "errorbar", 
-               position = position_dodge(width = .9),
-               width = .2) + 
-  theme_classic() + 
-  facet_grid(type_type~type_size) + 
-  scale_fill_discrete(name = "Size of Non-Invariance") + 
-  xlab("Equality Constraints") + 
-  ylab("Normalized Effect Size") + 
-  theme(legend.position = "bottom") + 
-  geom_hline(yintercept = 0) +
-  # geom_hline(yintercept = 1) + 
-  NULL
-
-prop_boot_rr
-
-means_invariant <- boot_rr_DF %>% filter(type == "Invariant") %>% group_by(model) %>% summarize(mean_h = mean(h_nmi_p))
-
-ggsave("figures/prop-boot-rr.png", dpi = 300, 
-       width = 8, 
-       units = "in")
-```
-
-In the data that was simulated to be invariant between groups, effect sizes are still non-zero (loadings $h_{nmi_p}$ = `r apa_num(means_invariant$mean_h[1])`, intercepts = $h_{nmi_p}$ = `r apa_num(means_invariant$mean_h[2])`, $h_{nmi_p}$ = `r apa_num(means_invariant$mean_h[3])`).
-This result mirrors the effects found in the literature - that often, many models fail to show invariance, and potentially not because measurement is poor but because of natural random variation in parameter estimates.
-This result also indicates the need to be able to identify if specific parameters are driving the differences, which is shown in the next section.
-
-Next, Figure \@ref(fig:boot-rr-pic) demonstrates the patterns one might find for small, medium, and large effects at each type of invariance when data is simulated with *one* difference.
-For loadings, the pattern shows a larger effect for loadings with zero or negative effect sizes for other effect sizes.
-The intercept simulations show non-zero effect sizes in the loadings and intercepts, likely for the same reasons $d_{MACS}$ is interpreted as a combined effect size.
-When intercepts are changed, loadings may naturally shift with those means.
-Last, the residual results present an unexpected pattern, wherein the effect is primarily seen in the loadings, rather than the residuals step.
-However, when distributions of error variance are different, one may expect that those effects are pushed toward the loadings as well (as values can vary more, thus potentially weakening the relationship between observed and latent variable).
-
-An example of interpretation on real data is given in a later section.
-From a research study, only one effect size for each equality constraint would be calculated.
-The interpretation will often be up to the researcher's smallest effect of interest, and this simulation gives some guidance that the values should not be interpreted with traditional rules of thumb.
-The pattern of effects is potentially the most useful information: 1) positive effects on the loadings with negative or very close to zero effects on the other parameters may indicate a non-replication in loadings, 2) equal effects on loadings and intercepts with smaller or negative effects may indicate intercepts may be an issue, and 3) residuals may be determined by the same pattern as loadings but with a smaller ratio of loadings to residuals effect (i.e., loadings $h_{nmi}$ / residuals $h_{nmi}$.
-The "size" could be determined by the ratio of effect sizes for each constraint.
-Of course, this represents one simulation study, and results from many studies in a meta-analysis would be fruitful for future work.
-
-## Replication and Effect Size: Parameters
-
-### Package Function
+## Parameter Replication and Effect Sizes: `bootstrap_partial()` Function
 
@@
 The general setup consists of using the model you think could be partially invariant in the `saved_model` argument and the fit index for comparison for the model with less constraints in `invariance_compare`.
-This example examines the loadings in the invariant model, so `saved_model` uses the `mgcfa` output for equality constraints present on the loadings and compares that model to the configural model with no equality constraints on the loadings.
 The `partial_step` argument will be used to determine which operation syntax (i.e.
@@
 
-```{r boot-partial, echo = T, size = "small", eval = F}
-boot.partial.invariant <- 
-      bootstrap_partial(
-        # saved model you want to examine the partial loadings for 
-        saved_model = results.invariant$invariance_models$model.loadings,
-        # the dataset 
-        data = df.invariant, 
-        # the model 
-        model = model.overall,
-        # the group variable in the dataset
-        group = "group", 
-        # number of bootstraps
-        nboot = 1000,
-        # which fit index you would like to use to determine partial invariance
-        invariance_index = "cfi", 
-        # what is the invariance rule 
-        invariance_rule = .01, 
-        # what are we comparing the saved model fit index to 
-        invariance_compare = fitmeasures(results.invariant$model_configural, "cfi"), 
-        # what step are we using for invariance
-        partial_step = "loadings", 
-        # what equality constraints should be imposed 
-        group.equal = c("loadings")
-      )
-```
-
-```{r echo = F, eval = F}
-saveRDS(boot.partial.invariant, "manu_data/boot.partial.invariant.RData")
-```
-
-```{r partial-boot-print, echo = T, size = "small"}
-names(boot.partial.invariant)
-```
-
 The saved output includes several dataframes and plots.
-The first is the `boot_DF` which the summary of each run in a dataframe for plotting or summarization.
-This dataframe includes the estimate for each paramter (`term`) separated by group and type (`boot_1`, `boot_2` are the bootstrapped estimates for group 1 and group 2, while the same `random` columns indicate the randomly assigned groups).
+The first is the `boot_DF` which is the summary of each bootstrapped run in a dataframe for plotting or summarization.
+This dataframe includes the estimate for each parameter (`term`) separated by group and type (`boot_1`, `boot_2` are the bootstrapped estimates for group 1 and group 2, while the same `random` columns indicate the randomly assigned groups).
 The fit index used to determine invariance is included for bootstrapped and random estimates, and then the differences between groups and if they were "invariant" or not given the researcher supplied rule.
 
-```{r boot-partial-DF, echo = T, size = "small"}
-head(boot.partial.invariant$boot_DF)
-```
-
-Next, the `boot_summary` includes a summarized form of the bootstrapped results from separated by bootstrapping versus random and invariant/non-invariant.
-The $d_s$ for between groups Cohen's $d$ is shown below, and the non-central confidence interval is included.
+Next, the `boot_summary` includes a summarized form of the bootstrapped results separated by bootstrapped data versus randomized data and then invariant/non-invariant outcomes.
+The $d_s$ for between groups Cohen's $d$ is included [@lakens2013].
 Effect sizes are only calculated when the number of bootstrapped estimates is at least 10% of the data - therefore, you would not receive effect sizes with almost no bootstrapped runs.
-This dataframe should be used to determine which parameter may be different and at what size between groups in a replication of the study.
-
-```{r boot-summary-DF, echo = T, size = "small"}
-boot.partial.invariant$boot_summary %>% 
-  dplyr::select(term, d_boot, d_random)
-```
-
+This dataframe should be used to determine which parameter may be different and the effect size potential between groups in a replication of the study.
 The `boot_effects` table creates a summary similar to the overall model replication table based on the proportion of runs that were considered invariant versus not for each parameter.
-Note that the effects match the overall results, such that simulated invariant data appears to still show the likelihood that loadings may not replicate in a similar dataset.
-
-```{r boot-effects-DF, echo = T, size = "small"}
-boot.partial.invariant$boot_effects
-```
 
 Plots of the results from dataframes can be found within the `bootstrap_partial()` function.
-Figure \@ref(fig:invariance-partial-fig) shows the difference between parameters for groups in the bootstrapped and randomly assigned group runs.
+Figure \@ref(fig:invariance-partial-fig) shows the difference between parameters for groups in the bootstrapped and randomly assigned group runs in simulated data.
 Figure \@ref(fig:density-partial-fig) shows the density plot of the estimates for each group organized by bootstrapped and randomly assigned groups and the invariance decision for each bootstrapped run.
@@
 
-```{r invariance-partial-fig, include = T, fig.cap = "Visualization of the difference score between groups by parameter for invariant and non-invariant bootstrapped and randomly assigned group data."}
-boot.partial.invariant$invariance_plot
-
-ggsave("figures/boot-partial-invariance.png", dpi = 300, 
-       width = 8, 
-       units = "in")
-```
-
-```{r density-partial-fig, include = T, fig.cap = "Visualization of the number of estimates for each group by bootstrapped and randomly assigned group runs by their invariance decision."}
-suppressMessages(boot.partial.invariant$density_plot)
-
-ggsave("figures/boot-partial-density.png", dpi = 300, 
-       width = 8, 
-       units = "in")
+```{r invariance-partial-fig, include = T, fig.cap = "Visualization of the difference score between groups by parameter for invariant and non-invariant bootstrapped and randomly assigned group data on simulated data.", fig.height=8}
+knitr::include_graphics("figures/boot-partial-invariance.png")
+```
+
+```{r density-partial-fig, include = T, fig.cap = "Visualization of the number of estimates for each group by bootstrapped and randomly assigned group runs by their invariance decision on simulated data.", fig.height=8}
+knitr::include_graphics("figures/boot-partial-density.png")
 ```
@@
 ```{r effect-partial-fig, include = T, fig.cap = "Visualization of effect size between groups by parameter for invariant and non-invariant bootstrapped and randomly assigned group data.
-The size of the dots indicate the number of data points for that estimate."}
-boot.partial.invariant$effect_invariance_plot
-
-ggsave("figures/boot-partial-effects.png", dpi = 300, 
-       width = 8, 
-       units = "in")
-```
-
-### Simulated Results
-
-```{r create-plot-partial}
-# make all the graphs boot long ----
-boot_long <- 
-  bind_rows(boot.df.full %>% 
-              dplyr::select(term, boot_difference, boot_index_difference, type) %>% 
-              rename(difference = boot_difference, index_difference = boot_index_difference) %>%
-              mutate(type_estimate = "Bootstrapped"), 
-            boot.df.full %>% 
-              dplyr::select(term, random_difference, random_index_difference, type) %>% 
-              rename(difference = random_difference, index_difference = random_index_difference) %>% 
-              mutate(type_estimate = "Random")) %>% 
-  mutate(type_together = paste0(type, " " , type_estimate ))
-
-label_graph <- c(`TRUE` = "Invariant", `FALSE` = "Non-Invariant")
-
-# make all the graps summary long ----
-# summarize the overall
-boot.partial.summary <- boot.partial.summary.full %>% 
-  dplyr::select(-run_number, computer) %>% 
-  group_by(term, invariant, type) %>% 
-  summarize_at(vars(mean_boot_1:d_random_high), mean, na.rm = TRUE)
-
-boot_summary_long <- 
-  bind_rows(boot.partial.summary %>% 
-              dplyr::select(term, invariant, n_boot, type, starts_with("d_boot")) %>% 
-              rename(n = n_boot, 
-                     d_low = d_boot_low, 
-                     d = d_boot, 
-                     d_high = d_boot_high) %>% 
-              mutate(type_estimate = "Bootstrapped"), 
-            boot.partial.summary %>% 
-              dplyr::select(term, invariant, n_random, type,
-                                    starts_with("d_random")) %>% 
-              rename(n = n_random, 
-                     d_low = d_random_low, 
-                     d = d_random, 
-                     d_high = d_random_high) %>% 
-              mutate(type_estimate = "Random"))
-
-## make all the graphs effects long ----
-# summarize the effects
-boot.effects.summary <- boot.effects.summary.full %>% 
-  dplyr::select(-run_number, -computer) %>% 
-  group_by(term, type) %>% 
-  summarize_at(vars(non_invariant:h_mi_p), mean, na.rm = TRUE)
-
-density_long <- 
-  bind_rows(
-    boot.df.full %>% 
-      dplyr::select(term, boot_index_difference, boot_1, boot_2, type) %>% 
-      pivot_longer(cols = c(boot_1, boot_2), 
-                   names_to = "group", 
-                   values_to = "estimate") %>% 
-      rename(invariant = boot_index_difference) %>% 
-      mutate(type_estimate = "Bootstrapped"), 
-    boot.df.full %>% 
-      dplyr::select(term, random_index_difference, random_1, random_2, type) %>% 
-      pivot_longer(cols = c(random_1, random_2), 
-                   names_to = "group", values_to = "estimate") %>% 
-      rename(invariant = random_index_difference) %>% 
-      mutate(type_estimate = "Random")) %>% 
-  mutate(group = gsub("boot_1|random_1", "Group 1", group), 
-         group = gsub("boot_2|random_2", "Group 2", group), 
-         invariant = factor(invariant, 
-                            levels = c("TRUE", "FALSE"), 
-                            labels = c("Invariant", "Non-Invariant")))
-
-```
-
-Figure \@ref(fig:effect-large-loading-pic) shows the effect size differences within large loadings simulations.
-The results demonstrate that most of the loadings were considered non-invariant in the bootstrapped models (while holdings all others equal).
-This result is partially due to simulating very good data, so small changes in loadings results in a drop in fit for our chosen invariance index.
-However, we can use this graph to show that question four shows a possible effect size ranging from `r boot_summary_long %>% filter(type == "Large Loadings") %>% filter(invariant == FALSE) %>% filter(term == "lv =~ q4") %>% filter(type_estimate == "Bootstrapped") %>% pull(d_low) %>% apa_num()` to `r boot_summary_long %>% filter(type == "Large Loadings") %>% filter(invariant == FALSE) %>% filter(term == "lv =~ q4") %>% filter(type_estimate == "Bootstrapped") %>% pull(d_high) %>% apa_num()`.
-The $h_{nmi_p}$ value for question four was `r boot.effects.summary %>% filter(type == "Large Loadings") %>% filter(term == "lv =~ q4") %>% pull(h_nmi_p) %>% apa_num()`, representing about a quarter of a possible total effect.
-Last, the density plot in Figure \@ref(fig:density-large-loading-pic) shows the separation of the two different groups loadings in item four, thus, illustrating group differences in the findings for their loadings.
-Each of the other combination of plots can be found in the supplemental materials.
-
-```{r effect-large-loading-pic, fig.cap="Bootstrapped and Random Group effect size differences in loadings for the Large Loading difference simulation.
-The size of the point reprensents the number of data points included in that calculation."}
-effect_invariance_plot <- 
-  ggplot(boot_summary_long %>% 
-           filter(type == "Large Loadings"), 
-         aes(term, d, color = type_estimate)) + 
-  theme_classic() + 
-  facet_wrap(~invariant, labeller = as_labeller(label_graph)) +
-  scale_color_discrete(name = "Type of Estimate") + 
-  geom_point(aes(size = n)) + 
-  geom_errorbar(aes(ymin = d_low, ymax = d_high), width = 0.2) + 
-  xlab("Estimated Item") + 
-  ylab("Group Effect Size") + 
-  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1), 
-        legend.position = "bottom") + 
-  geom_hline(yintercept = 0) + 
-  coord_flip()
-
-suppressWarnings(effect_invariance_plot)
-
-ggsave("figures/partial-large-loading-effect.png", dpi = 300, 
-       width = 8, 
-       units = "in")
-```
-
-```{r density-large-loading-pic, fig.cap="Bootstrapped and Random density plots for invariant and non-invariant bootstrapped partial effects examining only large loadings."}
-density_plot <- ggplot(density_long %>% 
-                        filter(type == "Large Loadings"), 
-                       aes(x = estimate, y = term, fill = group)) + 
-  geom_density_ridges(alpha = 0.7, scale = 0.9) + 
-  facet_grid(invariant ~ type_estimate) + 
-  theme_classic() + 
-  xlab("Estimated Score") + 
-  ylab("Parameter") + 
-  scale_fill_discrete(name = "Group")
-
-suppressMessages(density_plot)
-
-ggsave("figures/partial-large-loading-density.png", dpi = 300, 
-       width = 8, 
-       units = "in")
-```
-
-## An Example Analysis
+The size of the dots indicate the number of data points for that estimate.", fig.height=8}
+knitr::include_graphics("figures/boot-partial-effects.png")
+```
+
+# An Example Analysis
 
@@
 
-```{r load-RS, echo = T, include = T, size = "small"}
+```{r load-RS, echo = F, include = T, size = "small"}
 # load the data, it is called DF
@@
 model.rs <- "RS =~ RS1+RS2+RS3+RS4+RS5+RS6+RS7+RS8+RS9+RS10+RS11+RS12+RS13+RS14"
-# run the multi-group CFA
+# run the multigroup CFA
 results.rs <- mgcfa(
@@
 
-```{r show-rs-results, eval = F, echo = T, include = T, size = "small"}
+```{r show-rs-results, eval = F, echo = F, include = F, size = "small"}
 # how to get results in table 
@@
 Table \@ref(tab:rs-table) indicates that fit was degraded when the constraint on equal item intercepts was added.
-The code below provides an example of testing each item individually by relaxing the constraints and recalculating the CFI.
+The code online provides an example of testing each item individually by relaxing the constraints and recalculating the CFI.
 If these Items bring the CFI value back up to $\Delta$CFI \<= .01 from the metric model, then the model would be considering partially invariant at the scalar level.
-It seems unlikely that the residuals will show invariance, if partial scalar invariance can be found, as the drop in fit is quite large.
-
-```{r partial-RS, echo = T, include = T, size = "small"}
+It seems unlikely that the residuals will show invariance, even if partial scalar invariance can be found, as the drop in fit on the residual model is quite large.
+
+```{r partial-RS, echo = F, include = F, size = "small"}
 partial.rs <-
@@
 
-The output indicates that RS6 and RS7 are potential items that could be relaxed to improve model fit and create a partial scalar invariant model (i.e., by picking the largest CFI values).
-The code below show to check the addition of these items, which are added one at a time.
-You use the `group.partial` open to "relax" or freely estimate that parameter for each group separately.
-
-```{r partial-RS7, echo = T, include = T, size = "small"}
+```{r partial-RS7, echo = F, include = F, size = "small"}
 # run the partially invariant model with group.partial
@@
 
+The partial invariance results indicated that RS6 and RS7 are potential items that could be relaxed to improve model fit and create a partial scalar invariant model (i.e., by picking the largest CFI values).
 By examining our estimates, we can see that item seven on the RS-14 is estimated at nearly 5 points for the clinical sample, while the student sample has a lower mean around 4.5 points.
@@
 The effect size from $d_{MACS}$ suggests a small to medium effect, `r apa_num(lavaan_dmacs(partial.rs.1$invariance_models$model.intercepts, "Clinical")$DMACS[7])`.
-In this next code section, we repeat this process for the RS6, as the CFI for our model with only RS7 does not achieve the levels of partial invariance for our $\Delta$CFI criterion (i.e., \<= .01 downward change in fit: metric CFI = `r apa_p(results.rs$model_fit$cfi[5])`, partial scalar CFI = `r apa_p(partial.rs.1$model_fit$cfi[6])`).
 See Figure \@ref(fig:rs7-img) for the difference between item intercepts and latent means.
-
-```{r partial-RS6, echo = T, include = T, size = "small"}
+We repeat this process for the RS6, as the CFI for our model with only RS7 does not achieve the levels of partial invariance for our $\Delta$CFI criterion (i.e., \<= .01 downward change in fit: metric CFI = `r apa_p(results.rs$model_fit$cfi[5])`, partial scalar CFI = `r apa_p(partial.rs.1$model_fit$cfi[6])`).
+
+```{r partial-RS6, echo = F, include = F, size = "small"}
 # add the second intercept
@@
 
-```{r plot-RS7, include = T, echo = T, results = "small", eval = F}
+```{r plot-RS7, include = F, echo = F, results = "small", eval = F}
 # plot the image for RS7
@@
 
-```{r rs7-img, echo = F, include = T, size = "small", fig.cap="RS7 Item Invariance Visualization"}
+```{r rs7-img, echo = F, include = T, size = "small", fig.cap="RS7 item non-invariance visualization showing differences in the item intercepts and latent variable.", fig.height=8}
 # plot the image for RS7
@@
 
-```{r plot-RS6, include = T, echo = T, results = "small", eval = F}
+```{r plot-RS6, include = F, echo = F, results = "small", eval = F}
 # plot the image for RS6
@@
 
-```{r rs6-img, echo = F, include = T, size = "small", fig.cap="RS6 Item Invariance Visualization"}
+```{r rs6-img, echo = F, include = T, size = "small", fig.cap="RS6 item non-invariance visualization similar results to RS7 with differences in item intercepts.", fig.height=8}
 plot_mi(
@@
 Given our current results, we may not expect our intercepts to replicate.
-Given the order of `group.equal`, the boot function will select the first non-invariant step in the calculation of the effect size for potential replication.
+Given the order of desired steps in the  `group.equal` argument, the boot function will select the first non-invariant step (as defined by the user) in the calculation of the effect size for potential replication.
 In our output, we do not see a loadings effect size, and this result occurs when *none* of the bootstrapped or random results are non-invariant.
@@
 
-```{r model-boot-RS, include = T, echo = T, results = "small", eval = F}
+```{r model-boot-RS, include = F, echo = F, results = "small", eval = F}
 boot.model.rs <- 
@@
 )
-```
-
-```{r model-boot-RS-out, include = T, echo = T, results = "small"}
+saveRDS(boot.model.rs, "manu_data/boot.model.rs.RData")
+```
+
+```{r model-boot-RS-out, include = F, echo = F, results = "small"}
 boot.model.rs
@@
 
-```{r partial-boot-RS, include = T, echo = T, results = "small", eval = F}
+```{r partial-boot-RS, include = F, echo = F, results = "small", eval = F}
 boot.partial.rs <- 
@@
           digits = 3, 
-          caption = "Boot Partial Effects Results for RS-14 Intercepts")
+          caption = "Boot Partial Effects Results for RS-14 Intercepts",
+          note = "Non-Invariant and Random Non-Invariant columns represent the proportion of non-invariant simulations of out the total simulations, representing our non-replication rate.
+These values are converted into an effect size difference in the final two columns.")
 ```
@@
 
-## An Example Extension
+# An Example Extension
 
@@
 With the published data, we can use `visualizemi` to determine if the RS14 is invariant across language/culture, and if the results would likely replicate if tested on a new set of samples, and what, if any, effect size differences are found in parameters.
-The code used for this analysis is presented in Appendix 7.
+The code used for this analysis is presented in the supplemental materials.
 
@@
 The differences between intercepts are shown on the left-hand side with a clear separation between lines.
-The latent means also show a clear difference between groups where the English group appears to have lower scores overall than the Chinese group."}
-load("manu_data/fig-chinese-rs2.Rdata")
-complete
-```
-
-```{r rs14-chinese-effect-pic, fig.width = 6, include = T, fig.cap = "Effect size differences for item intercepts on the English versus Chinese samples for the RS14.", warnings = FALSE, message = FALSE}
+The latent means also show a clear difference between groups where the English group appears to have lower scores overall than the Chinese group.", fig.height=8}
+knitr::include_graphics("figures/rs14-chinese-RS2.png")
+```
+
+```{r rs14-chinese-effect-pic, include = T, fig.cap = "Effect size differences for item intercepts on the English versus Chinese samples for the RS14.", warnings = FALSE, message = FALSE, fig.height=8}
 load("manu_data/boot.partial.rs.appendix7.Rdata")
@@
 In this tutorial, we examined how to use multiple tools to examine measurement invariance and its potential replication.
-Model fit comparisons and statistics can be paired with the proposed effect size measures, and a visualization to examine individual items and the overall latent mean scores.
+Model fit comparisons and statistics can be paired with the proposed effect size measures, and visualizations to examine individual items and the overall latent mean scores.
 The impact of potential replication was estimated on the overall model and the individual parameters.
@@
 The results from our Chinese versus English comparison show us the other scenario: non-invariant results that clearly indicate differences with a large effect size on both replication and item average differences.
-Given that the goal of measurement invariance is to compare *estimates*, we should expect some differences across samples due to the nature of sampling and estimation.
+Overall, given that the goal of measurement invariance is to compare parameter *estimates*, we should expect some differences across samples due to the nature of sampling and estimation.
 It may be that many of the published models presented represent these effects - small variations between groups due to sampling error or other small crud - but do not represent a fundamental problem with the measurement or generalizability of the results.
@@
 ```{r child = "appendix_1.Rmd"}
+
 ```

### 2024-07-29 manuscript.tex
updated manuscript

@@
 \documentclass[
-  man]{apa7}
+  man,floatsintext]{apa7}
 \usepackage{amsmath,amssymb}
@@
 \makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
-\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
-\makeatother
-% Scale images if necessary, so that they will not overflow the page
-% margins by default, and it is still possible to overwrite the defaults
-% using explicit options in \includegraphics[width, height, ...]{}
-\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+\newsavebox\pandoc@box
+\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
+  \sbox\pandoc@box{#1}%
+  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
+  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
+  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
+  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
+  \else\usebox{\pandoc@box}%
+  \fi%
+}
 % Set default figure placement to htbp
-\makeatletter
 \def\fps@figure{htbp}
@@
 % Make \paragraph and \subparagraph free-standing
+\makeatletter
 \ifx\paragraph\undefined\else
   \let\oldparagraph\paragraph
-  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
+  \renewcommand{\paragraph}{
+    \@ifstar
+      \xxxParagraphStar
+      \xxxParagraphNoStar
+  }
+  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
+  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
 \fi
@@
   \let\oldsubparagraph\subparagraph
-  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
+  \renewcommand{\subparagraph}{
+    \@ifstar
+      \xxxSubParagraphStar
+      \xxxSubParagraphNoStar
+  }
+  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
+  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
 \fi
+\makeatother
+% definitions for citeproc citations
+\NewDocumentCommand\citeproctext{}{}
+\NewDocumentCommand\citeproc{mm}{%
+  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
+\makeatletter
+ % allow citations to break across lines
+ \let\@cite@ofmt\@firstofone
+ % avoid brackets around text for \cite:
+ \def\@biblabel#1{}
+ \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
+\makeatother
 \newlength{\cslhangindent}
@@
 \setlength{\csllabelwidth}{3em}
-\newlength{\cslentryspacingunit} % times entry-spacing
-\setlength{\cslentryspacingunit}{\parskip}
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
+\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
+ {\begin{list}{}{%
+  \setlength{\itemindent}{0pt}
+  \setlength{\leftmargin}{0pt}
+  \setlength{\parsep}{0pt}
   % turn on hanging indent if param 1 is 1
   \ifodd #1
-  \let\oldpar\par
-  \def\par{\hangindent=\cslhangindent\oldpar}
+   \setlength{\leftmargin}{\cslhangindent}
+   \setlength{\itemindent}{-1\cslhangindent}
   \fi
   % set entry spacing
-  \setlength{\parskip}{#2\cslentryspacingunit}
- }%
- {}
+  \setlength{\itemsep}{#2\baselineskip}}}
+ {\end{list}}
 \usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
 \newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
@@
 \def\languageshorthands#1{}
+\ifLuaTeX
+  \usepackage[english]{selnolig} % disable illegal ligatures
+\fi
 % Manuscript styling
@@
 \keywords{multigroup confirmatory factor analysis, measurement invariance, visualization, effect size}
-\DeclareDelayedFloatFlavor{ThreePartTable}{table}
-\DeclareDelayedFloatFlavor{lltable}{table}
-\DeclareDelayedFloatFlavor*{longtable}{table}
-\makeatletter
-\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
-\makeatother
 \usepackage{lineno}
@@
 
-\ifLuaTeX
-  \usepackage{selnolig}  % disable illegal ligatures
-\fi
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\usepackage{bookmark}
 \IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
@@
 Journals such as \emph{Assessment} regularly publish articles supporting measures of latent constructs wherein a measurement model is established.
-Confirmatory factor analysis can be used to investigate the replicability and generalizability of the measurement model in new samples, while multi-group confirmatory factor analysis is used to examine the measurement model across groups within samples (Brown, 2015).
+Confirmatory factor analysis can be used to investigate the replicability and generalizability of the measurement model in new samples, while multigroup confirmatory factor analysis is used to examine the measurement model across groups within samples (Brown, 2015).
 With the rise of the replication crisis and ``psychology's renaissance'' (Nelson et al., 2018), interest in divergence in measurement has increased, often focused on small parameter differences within the latent model.
@@
 Byrne et al.
-(1989) extended the ideas of multi-group testing by suggesting partial invariance (followed by Meredith, 1993).
+(1989) extended the ideas of multigroup testing by suggesting partial invariance (followed by Meredith, 1993).
 Partial invariance occurs when non-invariance is found but can be attributed to only a few parameter estimate differences between groups (i.e., items 1 and 2 have different factor loadings but all others are the same).
@@
 
-Therefore, purpose of this manuscript is to describe an \emph{R} package, \texttt{visualizemi}, that provides functionality to calculate multi-group confirmatory factor analysis, partial invariance tests, visualizations of the size of non-invariance, and potential effect sizes for overall models and individual parameters.
+Therefore, purpose of this manuscript is to describe an \emph{R} package, \texttt{visualizemi}, that provides functionality to calculate multigroup confirmatory factor analysis, partial invariance tests, visualizations of the size of non-invariance, and potential effect sizes for overall models and individual parameters.
 No known visualization techniques have been proposed for measurement invariance.
@@
 \item
-  Learn how to use \emph{visualizemi} to analyze multi-group confirmatory factor analysis, examine partial for invariance, and create visualizations of parameters.
-\item
-  Learn how to estimate the potential replication of multi-group models and their parameters using bootstrapping compared to a random group model.
+  Learn how to use \emph{visualizemi} to analyze multigroup confirmatory factor analysis, examine partial for invariance, and create visualizations of parameters.
+\item
+  Learn how to estimate the potential replication of multigroup models and their parameters using bootstrapping compared to a random group model.
 \item
@@
 
-The tutorial will start with simulated data based on known effect sizes using \(d_{MACS}\) and demonstrating the package functions for 1) running the multigroup analysis, 2) running a partial invariance analysis, 3) plotting the partial invariance, 4) estimating replication and effect sizes at the model level, and 5) estimating replication and effect sizes at the parameter level.
+The tutorial will start with a general overview of relevant topics to orient readers to invariance testing and MGCFA effect sizes.
+Next, the reader will learn about the \texttt{visualizemi} package functions for 1) running the multigroup analysis, 2) running a partial invariance analysis, 3) plotting the partial invariance, 4) estimating replication and effect sizes at the model level, and 5) estimating replication and effect sizes at the parameter level.
 Last, data from Aiena et al.
-(2014) examining the measurement invariance of the RS-14 (Wagnild, 2009) will be used to demonstrate the application of the package on real data.
+(2014) and Chen et al.
+(2020) examining the measurement invariance of the RS-14 (Wagnild, 2009) will be used to demonstrate the application of the package on real data.
 The \emph{visualizemi} package vignette includes an additional tutorial walk through.
 
-\hypertarget{method}{%
-\section{Method}\label{method}}
-
-\hypertarget{design-and-analysis}{%
-\subsection{Design and Analysis}\label{design-and-analysis}}
-
-Data was simulated using the \texttt{simulateData} function in the \emph{R} package \emph{lavaan} (Rosseel, 2012) assuming multivariate normality using a \(\mu\) of 0 and \(\sigma\) of 1 for the data.
-This function allows you to write \emph{lavaan} syntax for your model with estimated values to generate data for observed variables (see supplemental for examples).
-The data included two groups of individuals (``Group 1'', ``Group 2'') for a multi-group confirmatory factor analysis (\(n_{group}\) = 250, \emph{N} = 500).
-The latent variables were assumed to be continuous normal (the package functions do not require this assumption).
-The model consisted of five observed items predicted by one latent variable (\texttt{lv\ =\textasciitilde{}\ q1\ +\ q2\ +\ q3\ +\ q4\ +\ q5}); however, the demonstration in this manuscript extends to multiple latent variables and other combinations of observed variables.
-Each item was assumed to be related to the latent variable with loadings approximately equal to .40 to .80, except when cases of non-invariance on the loadings was simulated.
-
-The Brown (2015) steps of testing measurement invariance are demonstrated in this manuscript for illustration purposes, but in line with Stark et al.
-(2006) suggestions, the visualizations show the impact of loadings and intercepts together.
-A convenience function \texttt{mgcfa} is used for these steps or other measurement invariance test orders and combinations.
-Fit indices for the steps for multi-group models are presented in the appendix for comparison of cutoff rules of thumb (Cheung \& Rensvold, 2002) to effect sizes and visualizations presented in this manuscript.
-Fit indices include Akaike Information Criterion (AIC, Akaike, 1998), Bayesian Information Criterion (BIC, Schwarz, 1978), Comparative Fit Index (CFI, Bentler, 1990), Tucker Lewis Index (TLI, Tucker \& Lewis, 1973), root mean squared error of approximation RMSEA (Steiger, 1990), and standardized root mean square residual (SRMR, Bentler, 1995).
-
-The data was then simulated to represent invariance across all model steps, small, medium, and large invariance using \(d_{MACS}\) estimated sizes from Nye et al.
-(2019).
-While \(d_{MACS}\) is used primarily for an effect size of the (non)-invariance for intercepts and loadings together, a similar approach was taken for the estimation of small, medium, and large effects on the residuals.
-The effect size is presented for all models, calculated from the \emph{dmacs} package (Dueber, 2023; Nye \& Drasgow, 2011).
-Only one item in each model was manipulated from the invariant model to create the non-invariant models.
-Given the data was simulated with a \emph{z}-score scaling, the loading values were simulated at .30 points apart (given \(d_{MACS}\) suggestions of .2, .4, .7), the intercepts at .25 points apart, and the residuals at .25 points apart.
-To plan a simulation for your own study, these values can be used to simulate small, medium, and large non-invariance effects by first converting data into \emph{z}-score.
-
-\hypertarget{package-code-examples}{%
-\section{Package Code Examples}\label{package-code-examples}}
+\section{Terminology}\label{terminology}
+
+\subsection{MGCFA}\label{mgcfa}
+
+Multigroup confirmatory factor analysis (MGCFA) was proposed as a method to examine differences in scale functioning across groups (Brown, 2015) using structural equation modeling and confirmatory factor analysis (CFA).
+The goal of MGCFA is to determine if groups are invariant or show the same response patterns on the scale.
+MGCFA is often performed in sequential steps to determine the location and impact of potential non-invariance.
+The most common procedure starts by examining overall scale structure for each group individually to show that the groups can be combined into one nested model (i.e., both models at least converge).
+The combined model, often described as the \emph{configural} model, creates one CFA for both groups that allows each group's estimated parameters to vary.
+Equality constraints between group parameters are then added sequentially to the model (Brown, 2015).
+If parameters are found to be equivalent between groups, these models are considered ``invariant'', suggesting that any subtle differences in the parameter estimate should not effect overall scoring and assessment.
+
+The first equality constraint added is usually the item factor loadings (\emph{metric} model) which requires items to be related to the latent variable at the same strength across groups.
+The intercepts are then constrained to be equal across groups (\emph{scalar} model) to determine the invariance of item averages.
+The item variances (\emph{strict} model) can then be examined to determine if the general variation in item answers are equal across groups.
+Other parameter equality constraints can be set at the latent variable level (latent means, variance, covariances), but the focus is generally on the observable variables and their parameter estimations.
+Non-invariance is determined by examining differences in fit indices between models with constraints versus without (Cheung \& Rensvold, 2002).
+
+\subsection{Partial Invariance}\label{partial-invariance}
+
+If a specific step within the MGCFA testing framework shows non-invariance, partial invariance is often used to investigate where and ``how much'' invariance occurs (Byrne et al., 1989; Meredith, 1993).
+Similar to \emph{post hoc} follow up tests in ANOVA, each equality constraint for that model is examined one at a time by allowing groups to vary.
+If the model fit improves when groups are allowed to have separate parameter estimations, the item parameter estimate is considered non-invariant.
+When only a few parameters are found that impact invariance, models are considered partially invariant, implying that most, but not all parameters are equal across groups.
+The researcher then interprets the impact of those items and parameters on overall scores and assessment usefulness.
+Partial invariance investigation is a useful tool for finding specific items that vary between groups, but does not fully explain the effect size of the difference between groups and the impact on the overall model.
+
+\subsection{\texorpdfstring{Effect Size: \(d_{MACS}\)}{Effect Size: d\_\{MACS\}}}\label{effect-size-d_macs}
+
+\(d_{MACS}\) was developed from Differential Item Functioning (DIF) measurement in Item Response Theory (IRT, Stark et al., 2004) wherein the effect size (DIF) portrays the group differences that lead to overall item score differences.
+Item scores can be mathematically defined as:
+
+\[
+\hat{X}_{iR} = \tau_{iR} + \lambda_{iR}\xi
+\]
+
+\emph{i} indicates an individual item, and \emph{R} indicates the reference group (Nye \& Drasgow, 2011).
+Therefore, an individual score is predicted by the intercept of the item (\(\tau\)) added to the item loading (\(\lambda\)) times the latent variable score (\(\xi\)).
+Nye and Drasgow (2011) demonstrated that the terminology from IRT and DIF can be used to create a measure of item functioning differences within CFA, \(d_{MACS}\).
+\(d_{MACS}\) is then the difference of reference group versus focal group (e.g., group 1 versus group 2) divided by a pooled standard deviation similar to formulas for \emph{d} proposed by Cohen (2013).
+Therefore, if \(\tau\) or \(\lambda\) are individually (or both) different across groups, it will impact all the predicted \(X_{iR}\) scores, and thus, impact \(d_{MACS}\) values.
+While \(d_{MACS}\) represents a necessary step for development of effect sizes within CFA, it does not separate the differences in parameters between groups in a way that can be paired with traditional MGCFA testing and partial invariance.
+In addition to the missing effect sizes at model and parameter levels, no effect size to date gives the researcher a feeling for potential replication of the invariant or non-invariant items.
+Last, in line with general suggestions by Cumming (2012) and Cumming and Calin-Jageman (2016), the visualization of effect sizes in MGCFA would be an added tool for researchers to gauge the size of group differences.
+
+\section{Package Functions}\label{package-functions}
 
@@
 The \emph{R} package and replication/effect sizes was added after the original manuscript submission.
-
-\hypertarget{multi-group-cfa-caculation}{%
-\subsection{Multi-group CFA Caculation}\label{multi-group-cfa-caculation}}
+The simulation study used to design plotting functions and test effect sizes can be found in the supplemental materials, along with worked code examples.
+
+\subsection{\texorpdfstring{MGCFA: \texttt{mgcfa()} Function}{MGCFA: mgcfa() Function}}\label{mgcfa-mgcfa-function}
 
 First, we would create our model code in \emph{lavaan} syntax (Rosseel, 2012).
+The \emph{visualizemi} package does generally require raw data for bootstrapping purposes, and an example of how to simulate data from models and covariance/correlations tables that sometimes are provided in manuscripts (rather than the raw data) is provided in the supplemental documentation.
+The \texttt{mgcfa()} function is designed to flexibly allow you to leverage \emph{lavaan}'s package functions to calculate multiple measurement steps at once.
+You would include:
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi})}
+\tightlist
+\item
+  the model syntax in the \texttt{model} argument.
+\item
+  the dataframe in the \texttt{data} argument of our functionl
+\item
+  the name of the grouping variable in quotes for \texttt{group}.
+\item
+  and the equality constraints you would like to impose in order in \texttt{group.equal}.
+\item
+  \texttt{...} any other \emph{lavaan} arguments you would like to use such as \texttt{meanstructure} or \texttt{estimator}.
+\end{enumerate}
+
+The following output is saved:
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi})}
+\tightlist
+\item
+  \texttt{model\_coef}: The parameter estimates for each model with the model step included in a \emph{model} column.
+This set of coefficients can be used for other functions.
+This dataframe is created with \emph{broom}'s \texttt{tidy()} function if you wish to recreate this table without running the \texttt{mgcfa()} function (Robinson et al., 2023).
+\item
+  \texttt{model\_fit}: The model fit indices from \texttt{fitmeasures()} to review for overall model fit and invariance judgments. The name of the model is included in a \emph{model} column.
+\item
+  \texttt{model\_overall}: A saved \emph{lavaan} fitted model of all groups together without any equality constraints or grouping variables.
+These objects can be used with any function that normally takes a saved model: \texttt{parameterEstimates()}, \texttt{modificationIndices()}, \texttt{semPlot::semPaths()}, and so on (Epskamp, 2022).
+\item
+  \texttt{group\_models}: A list of saved fitted models for each group separately.
+\item
+  \texttt{model\_configural}: A saved fitted model for the configural model that nests together each group into one model with no other constraints.
+\item
+  \texttt{invariance\_models}: A list of saved fitted models that consecutively adds \texttt{group.equal} constraints.
+\end{enumerate}
+
+\subsection{\texorpdfstring{Partial Invariance: \texttt{partial\_mi()} Function}{Partial Invariance: partial\_mi() Function}}\label{partial-invariance-partial_mi-function}
+
+The \texttt{partial\_mi()} function aids in the calculation of partial invariance for a specific step of the MGCFA process. The function includes the following arguments:
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi})}
+\tightlist
+\item
+  \texttt{saved\_model}: The saved \emph{lavaan} model with the equality constraints at the level of measurement invariance you would like to examine for partial invariance.
+\item
+  \texttt{data}: The dataframe where the model was estimated.
+\item
+  \texttt{model}: The model syntax for the overall model.
+\item
+  \texttt{group}: The grouping variable column in the dataframe.
+\item
+  \texttt{group.equal}: The equality constraints including in your original multigroup tests.
+\item
+  \texttt{partial\_step}: The level of partial invariance you wish to test.
+\end{enumerate}
+
+In this function, each parameter with the appropriate \emph{lavaan} syntax is relaxed individually (i.e., \texttt{\textasciitilde{}1} for intercepts, \texttt{\textasciitilde{}\textasciitilde{}} for residuals, etc.).
+The fitted models are saved in the \texttt{models} output, and the \texttt{fit\_table} output includes all fit indices for each model to investigate potential areas of partial invariance based on the researcher's desired criterion.
+
+\subsection{\texorpdfstring{Visualization of Invariance: \texttt{plot\_mi()} Function}{Visualization of Invariance: plot\_mi() Function}}\label{visualization-of-invariance-plot_mi-function}
+
+Once we know which items are non-invariant, the \texttt{model\_coef} output from the \texttt{mgcfa()} can be used directly in \texttt{plot\_mi()}.
+The plot outputs will be described below.
+First, here are the arguments for the function:
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi})}
+\tightlist
+\item
+  \texttt{data\_coef}: A tidy dataframe of the parameter estimates from the models.
+This function assumes you have used \texttt{broom::tidy()} on the saved model from \emph{lavaan} and added a column called ``model'' with the name of the model step (Robinson et al., 2023).
+This function will only run for models that have used the grouping function (i.e., configural, metric, scalar, and strict or other combinations/steps you wish to examine).
+\item
+  \texttt{model\_step}: Which model do you want to plot? You should match this name to the one you want to extract from your model column in the \texttt{data\_coef}.
+\item
+  \texttt{item\_name}: Which observed variable from your model syntax do you want to plot? Please list this variable name exactly how it appears in the model.
+\item
+  \texttt{x\_limits}: What do you want the x-axis limits to be for your invariance plot?
+The default option is to assume the latent variable is standardized, and therefore, -1 to 1 is recommended.
+Use only two numbers, a lower and upper limit.
+This value also constrains the latent mean diagram to help zoom in on group differences because the scale of latent means is usually centered over zero.
+You can use this parameter to zoom out to a more traditional histogram using \texttt{c(-2,\ 2)}.
+\item
+  \texttt{y\_limits}: What do you want the y-axis limits to be for your invariance plot?
+Given that the latent variable is used to predict the observed values in the data, you could use the minimum and maximum values found in the data.
+If that range is large, consider reducing this value to be able to visualize the results (i.e., otherwise it may be too zoomed out to judge group differences).
+Use only two numbers, a lower and upper limit.
+\item
+  \texttt{conf.level}: What confidence limit do you want to plot? Use 1 - \(\alpha\).
+\item
+  \texttt{model\_results}: In this argument, include the saved \emph{lavaan} output for the model listed in the \texttt{model\_step} argument.
+\item
+  \texttt{lv\_name}: Include the name of the latent variable, exactly how it is listed in your \emph{lavaan} syntax.
+You should plot the latent variable that the \texttt{item\_name} is linked to.
+If you have items that load onto multiple latent variables, you will need to make multiple plots.
+\item
+  \texttt{plot\_groups}: If you include more than two groups in a multigroup model, the automatic assumption is that you want the first two groups for this visualization.
+If not, include the names of the groups here to plot.
+\end{enumerate}
+
+The outputs from this function are several \emph{ggplot2} objects that can be edited or saved directly using \emph{ggplot2} functionality (Wickham, 2016).
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi})}
+\tightlist
+\item
+  \texttt{complete}: The output from this model can be found in Figure \ref{fig:invariant-pic}.
+On the left-hand side, the item invariance is plotted, and on the right-hand side, the latent mean distributions for the two groups are plotted.
+In the item invariance sub-plot, the visualization includes all three components traditionally seen in MGCFA testing steps: loadings, intercepts, and residuals.
+Each visualization element was designed to match the traditional visualization for that type of output.
+All parameter estimates are plotted on the unstandardized estimates and their confidence interval based on the standard error of the estimate.
+All plots are made with \emph{ggplot2} and \emph{cowplot} (Wilke, 2020).
+\end{enumerate}
+
+\begin{figure}
+\centering
+\pandocbounded{\includegraphics[keepaspectratio]{figures/invariant-visual.png}}
+\caption{\label{fig:invariant-pic}Invariant model visualization demonstrating the components of the \texttt{plot\_mi()} function in \emph{visualizemi}.}
+\end{figure}
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi})}
+\setcounter{enumi}{1}
+\tightlist
+\item
+  \texttt{intercept}: Only the left-hand side of the complete plot designed to represent intercepts and factor loadings.
+Factor loadings represent the slope of the regression equation for the latent variable predicting the scores on the observed variable (\(\hat{Y} \sim b_0 + b_1X + \epsilon\)).
+The y-axis indicates the observed variable scores, and here, the plot includes the entire range of the scale of the data this simulated item.
+The ribbon bands around the plotted slopes indicate the confidence interval for that estimate.
+In this plot, while the coefficients for each group are not literally equal, the overlapping and parallel slope bands indicate they are not different practically.
+\end{enumerate}
+
+The item intercepts (\(b_0\)) are plotted on the middle line where they would cross the y-axis at a latent variable score of zero.
+These are represented by a dot with a set of confidence error bars around the point.
+In this invariant depiction, the overlap in the intercepts is clear, indicating they are not different.
+You can use \texttt{y\_limits} to zoom in on the graph if these are too small to be distinguishable.
+3) \texttt{mean}: The right-hand side of the complete plot graphing the latent variable means and density from the data.
+The latent variable is shown on the x-axis using standardized values (i.e., \emph{z}-scores) where -1 indicates one standard deviation below the mean for the latent variable, 0 indicates the mean for the latent variable and so on.
+The lines indicate the means of the latent variables from the simulated dataset.
+Group labels are represented in the figure caption on the bottom.
+Group 1 is usually the group that is alphabetically first in the data set or whichever group is the first that appears when using the \texttt{levels()} command.
+4) \texttt{variance}: A split geom violin plot indicating the variance distribution of the plotted item.
+Residuals are trickier to plot, as they are the left over error when predicting the observed variables \(\epsilon\).
+It is tempting to plot this value as the confidence band around the slope, however, that defeats the purpose of understanding that the slopes are estimated separately from the residuals, and both have an associated variability around their parameter estimate.
+Therefore, residuals are represented in the inset picture at the bottom right of the item invariance plot.
+The black bars represent the estimated residual for each group.
+The distributions are plotted to represent the normal spread of values using the standard error of the residuals.
+The violin plot allows for direct comparison of those residuals and their potential distributions.
+Note that the placement has nothing to do with the x or y-axis and is designed to always show in the same location, regardless of size/value.
+The plots are included separately so they can be arranged in a different fashion if desired.
+
+\subsection{\texorpdfstring{Model Replication and Effect Sizes: \texttt{bootstrap\_model()} Function}{Model Replication and Effect Sizes: bootstrap\_model() Function}}\label{model-replication-and-effect-sizes-bootstrap_model-function}
+
+The \texttt{bootstrap\_model} function in \emph{visualizemi} was designed to estimate the likely replication of overall model invariance with the assumption that the data used for the estimation represents the larger population.
+The following arguments are used:
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi})}
+\tightlist
+\item
+  \texttt{saved\_configural}: a saved fitted model at the configural level with no equality constraints.
+This model should include all other lavaan settings you would like to use, such as estimator or ordered.
+\item
+  \texttt{data}: The dataframe where the model was estimated.
+\item
+  \texttt{model}: The model syntax for the overall model.
+\item
+  \texttt{group}: The grouping variable column in the dataframe.
+\item
+  \texttt{nboot}: The number of bootstraps to run.
+\item
+  \texttt{invariance\_index}: The fit index you would like to use to determine invariance. Please use options and labeling from \emph{lavaan} - see \texttt{fitmeasures()} for options.
+\item
+  \texttt{invariance\_rule}: The invariance difference score you would like to use as your rule.
+\item
+  \texttt{group.equal}: The equality constraints including in your original multigroup tests.
+\end{enumerate}
+
+The data included in this function will be sampled, with replacement, at the same size as the current dataset, and the included invariance equality constraints are estimated.
+Each step will be compared to the previous step using the invariance index and comparison rule entered.
+The output is a dataframe of the proportion of non-invariant bootstraps from the real data and the same bootstrapped dataset with the group labels randomly assigned.
+The effect size comparison of proportions, \(h\), for non-invariant comparisons:
+
+\[h_{nmi} = 2 \times (asin\sqrt{p_{data}} - asin\sqrt{p_{random}})\]
+
+The alternative, \(h_{mi}\), for effect size of measurement invariance replication would simply be the inverse sign of \(h_{nmi}\) and is also included in the table.
+Two additional columns \(h_{nmi_p}\) and \(h_{nmi_p}\) represent the \(h\) values divided by the upper bound of \(h\) (i.e., \(\pi\)), to help with interpretation of the effect size (thus, bounding \(h\) to -1 to 1).
+
+\subsection{\texorpdfstring{Parameter Replication and Effect Sizes: \texttt{bootstrap\_partial()} Function}{Parameter Replication and Effect Sizes: bootstrap\_partial() Function}}\label{parameter-replication-and-effect-sizes-bootstrap_partial-function}
+
+After examining the overall model potential replication effect size, the individual parameters within a model can be bootstrapped for partial invariance to with that parameter relaxed (overall partial model statistics) and the difference in group parameter estimates (parameter effect size).
+This function uses arguments seen in other functions, so they will not be repeated here.
+The general setup consists of using the model you think could be partially invariant in the \texttt{saved\_model} argument and the fit index for comparison for the model with less constraints in \texttt{invariance\_compare}.
+The \texttt{partial\_step} argument will be used to determine which operation syntax (i.e.~\texttt{=\textasciitilde{}} for loadings) to relax for modeling.
+
+The saved output includes several dataframes and plots.
+The first is the \texttt{boot\_DF} which the summary of each run in a dataframe for plotting or summarization.
+This dataframe includes the estimate for each paramter (\texttt{term}) separated by group and type (\texttt{boot\_1}, \texttt{boot\_2} are the bootstrapped estimates for group 1 and group 2, while the same \texttt{random} columns indicate the randomly assigned groups).
+The fit index used to determine invariance is included for bootstrapped and random estimates, and then the differences between groups and if they were ``invariant'' or not given the researcher supplied rule.
+
+Next, the \texttt{boot\_summary} includes a summarized form of the bootstrapped results from separated by bootstrapping versus random and invariant/non-invariant.
+The \(d_s\) for between groups Cohen's \(d\) is included.
+Effect sizes are only calculated when the number of bootstrapped estimates is at least 10\% of the data - therefore, you would not receive effect sizes with almost no bootstrapped runs.
+This dataframe should be used to determine which parameter may be different and at what size between groups in a replication of the study.
+The \texttt{boot\_effects} table creates a summary similar to the overall model replication table based on the proportion of runs that were considered invariant versus not for each parameter.
+
+Plots of the results from dataframes can be found within the \texttt{bootstrap\_partial()} function.
+Figure \ref{fig:invariance-partial-fig} shows the difference between parameters for groups in the bootstrapped and randomly assigned group runs in simulated data.
+Figure \ref{fig:density-partial-fig} shows the density plot of the estimates for each group organized by bootstrapped and randomly assigned groups and the invariance decision for each bootstrapped run.
+Last, Figure \ref{fig:effect-partial-fig} indicates the \(d_s\) value between groups with an indication of the number of data points in each estimate (i.e., dot size).
+These visualizations should allow a researcher to understand the likelihood of replication for each parameter, as well as the potential size of the differences.
+Therefore, one could indicate a specific smallest effect size of interest, rather than a invariance cut-off rule of thumb when planning a replication or registered report.
+
+\begin{figure}
+\centering
+\pandocbounded{\includegraphics[keepaspectratio]{figures/boot-partial-invariance.png}}
+\caption{\label{fig:invariance-partial-fig}Visualization of the difference score between groups by parameter for invariant and non-invariant bootstrapped and randomly assigned group data.}
+\end{figure}
+
+\begin{figure}
+\centering
+\pandocbounded{\includegraphics[keepaspectratio]{figures/boot-partial-density.png}}
+\caption{\label{fig:density-partial-fig}Visualization of the number of estimates for each group by bootstrapped and randomly assigned group runs by their invariance decision.}
+\end{figure}
+
+\begin{figure}
+\centering
+\pandocbounded{\includegraphics[keepaspectratio]{figures/boot-partial-effects.png}}
+\caption{\label{fig:effect-partial-fig}Visualization of effect size between groups by parameter for invariant and non-invariant bootstrapped and randomly assigned group data.
+The size of the dots indicate the number of data points for that estimate.}
+\end{figure}
+
+\section{An Example Analysis}\label{an-example-analysis}
+
+Aiena et al.
+(2014) examined the RS-14 (Wagnild, 2009) exploring the factor structure of the Resiliency Scale in a clinical sample receiving treatment services and a college student sample.
+Measurement invariance was calculated for differences separately for these samples for gender and race finding a partially invariant models with a few item intercepts or residuals that differed between groups.
+Aiena et al.
+(2014) did not compare the clinical to the student sample for measurement invariance, and it is reasonable to expect potential differences in these two populations.
+This example will demonstrate the procedure for researchers who wish to use partial invariance steps and how to interpret real, messy data.
+
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:rs-table}Model Fit for RS-14 Example}
+
+\begin{tabular}{lllllll}
+\toprule
+Model & AIC & BIC & CFI & TLI & RMSEA & SRMR\\
+\midrule
+Overall & 126,722.491 & 126,888.707 & 0.934 & 0.923 & 0.094 & 0.036\\
+Group Clinical & 52,961.421 & 53,099.720 & 0.919 & 0.904 & 0.090 & 0.044\\
+Group Student & 69,100.985 & 69,254.310 & 0.928 & 0.915 & 0.108 & 0.035\\
+Configural & 122,118.406 & 122,617.055 & 0.926 & 0.912 & 0.102 & 0.036\\
+Loadings & 122,144.532 & 122,566.010 & 0.925 & 0.918 & 0.098 & 0.043\\
+Intercepts & 122,544.109 & 122,888.415 & 0.911 & 0.910 & 0.103 & 0.052\\
+Residuals & 126,466.241 & 126,727.438 & 0.780 & 0.793 & 0.156 & 0.086\\
+\bottomrule
+\end{tabular}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+Table \ref{tab:rs-table} indicates the results after running the one-factor model.
+There are several guidelines for assessing assessing a degradation in model fit (Cao \& Liang, 2022; Cheung \& Rensvold, 2002; Counsell et al., 2020; Jin, 2020; Putnick \& Bornstein, 2016) but for the purposes of this illustration \(\Delta\)CFI \textgreater{} .01 will be used.
+Table \ref{tab:rs-table} indicates that fit was degraded when the constraint on equal item intercepts was added.
+The code below provides an example of testing each item individually by relaxing the constraints and recalculating the CFI.
+If these Items bring the CFI value back up to \(\Delta\)CFI \textless= .01 from the metric model, then the model would be considering partially invariant at the scalar level.
+It seems unlikely that the residuals will show invariance, if partial scalar invariance can be found, as the drop in fit is quite large.
+
+The output indicates that RS6 and RS7 are potential items that could be relaxed to improve model fit and create a partial scalar invariant model (i.e., by picking the largest CFI values).
+The code below show to check the addition of these items, which are added one at a time.
+You use the \texttt{group.partial} open to ``relax'' or freely estimate that parameter for each group separately.
+
+By examining our estimates, we can see that item seven on the RS-14 is estimated at nearly 5 points for the clinical sample, while the student sample has a lower mean around 4.5 points.
+Generally, students show higher means on the items of the RS-14, but when all loadings and other intercepts are constrained to be equal, and this one item is relaxed, this pattern flips so that clinical groups show higher item intercepts.
+Given the scale is a 1-7 Likert type scale, .5 a point represents a potentially sizable change on the scale.
+Item seven covers perseverance after hardship, and all items can be found in the user manual for the scale at www.resiliencecenter.com.
+The effect size from \(d_{MACS}\) suggests a small to medium effect, 0.28.
+In this next code section, we repeat this process for the RS6, as the CFI for our model with only RS7 does not achieve the levels of partial invariance for our \(\Delta\)CFI criterion (i.e., \textless= .01 downward change in fit: metric CFI = .925, partial scalar CFI = .914).
+See Figure \ref{fig:rs7-img} for the difference between item intercepts and latent means.
+
+Again, we see about a half-point difference between our clinical and student samples for item 6, which is about drive to achieve.
+The CFI for this model does meet the requirements for partial invariance, .917.
+The effect size is approximately the same at \(d_{MACS}\) = 0.28.
+See Figure \ref{fig:rs6-img} shows the difference between item intercepts and latent means.
+
+\begin{figure}
+\centering
+\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/rs7-img-1.pdf}}
+\caption{\label{fig:rs7-img}RS7 Item Invariance Visualization}
+\end{figure}
+
+\begin{figure}
+\centering
+\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/rs6-img-1.pdf}}
+\caption{\label{fig:rs6-img}RS6 Item Invariance Visualization}
+\end{figure}
+
+Next, we would examine our replication potential for this model.
+Given our current results, we may not expect our intercepts to replicate.
+Given the order of \texttt{group.equal}, the boot function will select the first non-invariant step in the calculation of the effect size for potential replication.
+In our output, we do not see a loadings effect size, and this result occurs when \emph{none} of the bootstrapped or random results are non-invariant.
+Therefore, we would expect the loadings to replicate (and the effect size would be 0 difference between bootstrapped and random, both showing invariance).
+The intercepts show a large (i.e., close to the max possible value) non-invariant effect, and therefore, we should not expect this model to show invariance in a replication.
+
+Next, we would examine the strength of the effects of replication on each parameter at the intercept level.
+By examining Table \ref{tab:table-boot-effects}, it is clear that most of the item means are unlikely to replicate, even though two particular items can be used to create partial invariance.
+Figures \ref{fig:rs-partial-pic} and \ref{fig:rs-partial-pic2} display the three plots provided in the \texttt{bootstrap\_partial()} function.
+In general, we should expect \(M_{D}\) = 0.11 when items are invariant and \(M_{D}\) = 0.25 when items are not invariant.
+The effect size of non-invariant items ranges from 0.43 to 0.59.
+
+The density plot shown at the bottom of Figure \ref{fig:rs-partial-pic} illustrates the likely reasons for the differences found in the top plots.
+It appears that many items show a bimodal distribution within group 1 (Clinical Sample) and when items are invariant, the intercept averages to the same intercept as group 2 (Student Sample).
+In non-invariant estimates, the same bimodal distributions are found, but they are more extreme than the student samples, and therefore, item show different averages due to the presence of two separate means of data.
+Further, some items also appear to show two separate student item averages within the data.
+This result suggests that it would be fruitful to understand a potential predictor of these differences or other confounding variable that separates these samples, creating differences in item averages.
+
+In summary, if one were planning a replication, the prediction would be that item intercepts would likely not replicate, with a large effect size (i.e., it is easy to judge \(h_{nmi_p}\) close to the max of one as large).
+While this study found partial invariance by relaxing constraints on two individual items, bootstrapped partial invariance indicates that any item could potentially be problematic with an effect size averaging \(d\) \textasciitilde{} 0.50 difference in means.
+While \(d_{MACS}\) values represented a ``small'' effect based on previous publications, this effect may be muted by examining both loadings and intercepts.
+The results here suggest that the effect is driven by intercepts.
+The overall average score on items is high: \(M_M\) = 5.04 (\(M_{SD}\) = 1.72).
+Given the mean standard deviation, a \(d\) \textasciitilde{} 0.50 represents 0.86 or nearly one whole point on the scale.
+A researcher could decide that at least \(d\) = 0.33 or at least a third of a standard deviation would be an important change and set that as their smallest effect size of interest for invariance.
+Further, a newly planned study should investigate what variables may predict when and why samples separate into bimodal representations for item means.
+
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:table-boot-effects}Boot Partial Effects Results for RS-14 Intercepts}
+
+\begin{tabular}{lllll}
+\toprule
+Term & Non-Invariant & Random Non-Invariant & $h_{nmi}$ & $h_{nmi_p}$\\
+\midrule
+RS  Intercept & 0.989 & 0.013 & 2.703 & 0.860\\
+RS1  Intercept & 0.979 & 0.013 & 2.622 & 0.835\\
+RS10  Intercept & 0.981 & 0.013 & 2.636 & 0.839\\
+RS11  Intercept & 0.988 & 0.013 & 2.694 & 0.857\\
+RS12  Intercept & 0.986 & 0.013 & 2.676 & 0.852\\
+RS13  Intercept & 0.984 & 0.013 & 2.659 & 0.847\\
+RS14  Intercept & 0.986 & 0.013 & 2.676 & 0.852\\
+RS2  Intercept & 0.971 & 0.012 & 2.580 & 0.821\\
+RS3  Intercept & 0.981 & 0.012 & 2.646 & 0.842\\
+RS4  Intercept & 0.989 & 0.012 & 2.712 & 0.863\\
+RS5  Intercept & 0.976 & 0.013 & 2.602 & 0.828\\
+RS6  Intercept & 0.970 & 0.013 & 2.565 & 0.816\\
+RS7  Intercept & 0.961 & 0.013 & 2.515 & 0.801\\
+RS8  Intercept & 0.986 & 0.013 & 2.676 & 0.852\\
+RS9  Intercept & 0.978 & 0.013 & 2.615 & 0.832\\
+\bottomrule
+\end{tabular}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\begin{figure}
+\centering
+\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/rs-partial-pic-1.pdf}}
+\caption{\label{fig:rs-partial-pic}RS-14 scale invariance for item intercepts.
+The left panel indicates the raw score difference between groups and items, while the right panel indicates the effect size for group differences based on invariance.}
+\end{figure}
+
+\begin{figure}
+\centering
+\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/rs-partial-pic2-1.pdf}}
+\caption{\label{fig:rs-partial-pic2}RS-14 scale invariance density plots, illustrating invariant versus non-invariant bootstrapped and random runs for each parameter.}
+\end{figure}
+
+\section{An Example Extension}\label{an-example-extension}
+
+One benefit of the open science movement on scale development is the publication of datasets or covariance tables with published articles.
+We can extend our examination of potential replication on other variables that may effect assessment of underlying phenomena.
+For example, scale translation across languages is not only impacted by the literal conversion of concepts from one language to another, but also the cultural and societal norms of the target population (Cha et al., 2007; Chang et al., 1999; Yu et al., 2004).
+The RS14 was tested in Chinese speaking samples in Chen et al.
+(2020) across five different large samples and determined that the scale showed good psychometric properties for use within Chinese speaking samples as a one-factor model of resiliency.
+Given these results, another researcher may assume that the models would be comparable between English speaking (i.e., likely United States) and Chinese speaking samples.
+With the published data, we can use \texttt{visualizemi} to determine if the RS14 is invariant across language/culture, and if the results would likely replicate if tested on a new set of samples, and what, if any, effect size differences are found in parameters.
+The code used for this analysis is presented in Appendix 7.
+
+The Aiena et al.
+(2014) data used in our previous example was first filtered to only college students, as we have already noted that clinical samples show slightly different intercepts for at least two of the items from student samples.
+The Chen et al.
+(2020) data also included college students, which allows us to test a comparable sample that varies on translation and culture.
+The test of measurement invariance indicated that the factor structure and loadings were invariant across groups.
+Much like our test of clinical versus student samples, the results indicated that the intercepts were not consistent across groups.
+Within the English clinical/student sample, partial invariance could be achieved by relaxing two item intercept constraints (item 6 and 7).
+To achieve ``partial'' invariance between the Chinese and English speaking samples, we would need to relax more than half of the items (specifically, eight items: 1, 2, 3, 4, 10, 11, 12, 14), and it would be difficult to suggest partial invariance given this finding.
+\(d_{MACS}\) values range from 0.26 to 0.32 for the eight items which could be interpreted a small to medium given Nye et al.
+(2019)'s simulation study.
+Figure \ref{fig:rs14-chinese-pic} portrays the results from the second item on the RS14 (\emph{life accomplishments}).
+
+The results of model bootstrapping indicated that the effect of the loadings was likely to replicate (only invariant results were found), but the intercepts were never found to be invariant compared to a randomized sample (\(h_{nmi_p}\) = 1).
+Therefore, we would expect that these differences are persistent, either due to the adaptation or cultural differences in resiliency across samples.
+The bootstrapped partial invariance demonstrates that each item intercept has a medium to large difference between the two samples as shown in Figure \ref{fig:rs14-chinese-effect-pic}, which may explain why full or partial invariance cannot be achieved.
+This result does not invalidate either version of the scale, but informs researchers of potential baseline differences in item responding for the two samples.
+Therefore, careful interpretation should be made when comparing these two samples in other instances, as differences in latent means may be the default finding, but with these results one may determine if their results are different from expectations of general scale responding.
+
+\begin{figure}
+\centering
+\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/rs14-chinese-pic-1.pdf}}
+\caption{\label{fig:rs14-chinese-pic}The differences in intercepts for the second item on the RS14 by language sample.
+The differences between intercepts are shown on the left-hand side with a clear separation between lines.
+The latent means also show a clear difference between groups where the English group appears to have lower scores overall than the Chinese group.}
+\end{figure}
+
+\begin{figure}
+\centering
+\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/rs14-chinese-effect-pic-1.pdf}}
+\caption{\label{fig:rs14-chinese-effect-pic}Effect size differences for item intercepts on the English versus Chinese samples for the RS14.}
+\end{figure}
+
+\section{Discussion}\label{discussion}
+
+In this tutorial, we examined how to use multiple tools to examine measurement invariance and its potential replication.
+Model fit comparisons and statistics can be paired with the proposed effect size measures, and a visualization to examine individual items and the overall latent mean scores.
+The impact of potential replication was estimated on the overall model and the individual parameters.
+Using real data, the effect of two non-invariant item intercepts was examined and visualized.
+This tutorial manuscript has provided a concrete way to plan for pre-registration and/or registered reports.
+Researchers could simulate results based on published or previously collected data to determine the likelihood and size of potential replication.
+They could plan and pre-register a smallest effect of interest.
+For example, we may determine that an \(h_{nmi_p}\) value above .20 represents an important level of non-invariance for our model overall, while \(h_{nmi_p}\) \textgreater{} .30 for any individual parameter warrant caution against invariance for groups.
+Others have begun to discuss the importance of focusing on effects in the scale of the data and their practical importance (Anvari \& Lakens, 2021; Cumming, 2012).
+
+From the example, our interpretation may be that the difference between group's latent means is large, as a 0.72 change on a 7 point scale is approximately 10\% more resiliency for students when compared to the clinical sample.
+Practically, 10\% in resiliency for an area of the United States (Mississippi) often hit with natural disasters (hurricanes, tornadoes, floods) and high levels of poverty would be very important.
+Even the smaller difference of .5 point on each individual item could translate into increases in resiliency, and these results may elucidate avenues for further exploration into areas of focus within resiliency, given the items.
+The secondary example showed that we can extend these results to other samples to examine other potentially impactful variables on assessment.
+The findings replicate in the sense that the scale shows the same invariant issues with intercepts on a Chinese versus English sample comparison.
+However, in this analysis, it is clear that the differences in items averages are much larger and across all items, rather than a few.
+
+What do the results of a study on measurement invariance with these results tell us about replication, generalizability, and validity overall?
+If a researcher decides their effects are large, they should likely caution against suggesting that these scores are directly comparable without weighting or other adjustment.
+Let's consider a scenario wherein the change metric between models picked (i.e., \(\Delta\)CFI, \(\Delta\)RMSEA) indicates a ``significant'' change in model fit.
+However, if both the effect size and a visual inspection of the invariance indicates a small difference, we may decide to lessen the practical importance of those results, much like ``just significant'' \emph{p}-values with small effect sizes are treated now.
+The results from our Chinese versus English comparison show us the other scenario: non-invariant results that clearly indicate differences with a large effect size on both replication and item average differences.
+Given that the goal of measurement invariance is to compare \emph{estimates}, we should expect some differences across samples due to the nature of sampling and estimation.
+It may be that many of the published models presented represent these effects - small variations between groups due to sampling error or other small crud - but do not represent a fundamental problem with the measurement or generalizability of the results.
+The \texttt{visualizemi} package is one useful tool to help sort out if findings are this small sampling error or differences in samples due to other variables.
+
+\newpage
+
+\section{References}\label{references}
+
+\phantomsection\label{refs}
+\begin{CSLReferences}{1}{0}
+\bibitem[\citeproctext]{ref-aiena2014}
+Aiena, B.
+J., Baczwaski, B.
+J., Schulenberg, S.
+E., \& Buchanan, E.
+M.
+(2014).
+Measuring Resilience With the RS{\textendash}14: A Tale of Two Samples.
+\emph{Journal of Personality Assessment}, \emph{97}(3), 291--300.
+\url{https://doi.org/10.1080/00223891.2014.951445}
+
+\bibitem[\citeproctext]{ref-akaike1998}
+Akaike, H.
+(1998).
+\emph{Information theory and an extension of the maximum likelihood principle} (E.
+Parzen, K.
+Tanabe, \& G.
+Kitagawa, Eds.; pp.
+199--213).
+Springer New York.
+\url{http://link.springer.com/10.1007/978-1-4612-1694-0_15}
+
+\bibitem[\citeproctext]{ref-anvari2021}
+Anvari, F., \& Lakens, D.
+(2021).
+Using anchor-based methods to determine the smallest effect size of interest.
+\emph{Journal of Experimental Social Psychology}, \emph{96}, 104159.
+\url{https://doi.org/10.1016/j.jesp.2021.104159}
+
+\bibitem[\citeproctext]{ref-barry2014}
+Barry, A.
+E., Chaney, B., Piazza-Gardner, A.
+K., \& Chavarria, E.
+A.
+(2014).
+Validity and Reliability Reporting Practices in the Field of Health Education and Behavior: A Review of Seven Journals.
+\emph{Health Education \& Behavior}, \emph{41}(1), 12--18.
+\url{https://doi.org/10.1177/1090198113483139}
+
+\bibitem[\citeproctext]{ref-beaujean2014}
+Beaujean, A. A. (2014). \emph{Latent variable modeling using r: A step by step guide}. Routledge/Taylor \& Francis Group.
+
+\bibitem[\citeproctext]{ref-bentler1990}
+Bentler, P. M. (1990). Comparative fit indexes in structural models. \emph{Psychological Bulletin}, \emph{107}(2), 238--246. \url{https://doi.org/10.1037/0033-2909.107.2.238}
+
+\bibitem[\citeproctext]{ref-bentler1995}
+Bentler, P. M. (1995). \emph{EQS structural equations program manual}.
+
+\bibitem[\citeproctext]{ref-boker2011}
+Boker, S., Neale, M., Maes, H., Wilde, M., Spiegel, M., Brick, T., Spies, J., Estabrook, R., Kenny, S., Bates, T., Mehta, P., \& Fox, J.
+(2011).
+OpenMx: An Open Source Extended Structural Equation Modeling Framework.
+\emph{Psychometrika}, \emph{76}(2), 306--317.
+\url{https://doi.org/10.1007/s11336-010-9200-6}
+
+\bibitem[\citeproctext]{ref-brown2015}
+Brown, T. A. (2015). \emph{Confirmatory factor analysis for applied research} (Second edition). The Guilford Press.
+
+\bibitem[\citeproctext]{ref-byrne1989}
+Byrne, B.
+M., Shavelson, R.
+J., \& Muthén, B.
+(1989).
+Testing for the equivalence of factor covariance and mean structures: The issue of partial measurement invariance.
+\emph{Psychological Bulletin}, \emph{105}(3), 456--466.
+\url{https://doi.org/10.1037/0033-2909.105.3.456}
+
+\bibitem[\citeproctext]{ref-cao2022}
+Cao, C., \& Liang, X.
+(2022).
+The impact of model size on the sensitivity of fit measures in measurement invariance testing.
+\emph{Structural Equation Modeling: A Multidisciplinary Journal}, \emph{29}(5), 744--754.
+\url{https://doi.org/10.1080/10705511.2022.2056893}
+
+\bibitem[\citeproctext]{ref-cha2007}
+Cha, E.-S., Kim, K.
+H., \& Erlen, J.
+A.
+(2007).
+Translation of scales in cross{-}cultural research: issues and techniques.
+\emph{Journal of Advanced Nursing}, \emph{58}(4), 386--395.
+\url{https://doi.org/10.1111/j.1365-2648.2007.04242.x}
+
+\bibitem[\citeproctext]{ref-chang1999}
+Chang, A.
+M., Chau, J.
+P.
+C., \& Holroyd, E.
+(1999).
+Translation of questionnaires and issues of equivalence.
+\emph{Journal of Advanced Nursing}, \emph{29}(2), 316--322.
+\url{https://doi.org/10.1046/j.1365-2648.1999.00891.x}
+
+\bibitem[\citeproctext]{ref-chen2020}
+Chen, W., Xie, E., Tian, X., \& Zhang, G.
+(2020).
+Psychometric properties of the Chinese version of the Resilience Scale (RS-14): Preliminary results.
+\emph{PLOS ONE}, \emph{15}(10), e0241606.
+\url{https://doi.org/10.1371/journal.pone.0241606}
+
+\bibitem[\citeproctext]{ref-cheung2002}
+Cheung, G.
+W., \& Rensvold, R.
+B.
+(2002).
+Evaluating Goodness-of-Fit Indexes for Testing Measurement Invariance.
+\emph{Structural Equation Modeling: A Multidisciplinary Journal}, \emph{9}(2), 233--255.
+\url{https://doi.org/10.1207/s15328007sem0902_5}
+
+\bibitem[\citeproctext]{ref-chorpita2000}
+Chorpita, B.
+F., Yim, L., Moffitt, C., Umemoto, L.
+A., \& Francis, S.
+E.
+(2000).
+Assessment of symptoms of DSM-IV anxiety and depression in children: a revised child anxiety and depression scale.
+\emph{Behaviour Research and Therapy}, \emph{38}(8), 835--855.
+\url{https://doi.org/10.1016/S0005-7967(99)00130-8}
+
+\bibitem[\citeproctext]{ref-cohen2013}
+Cohen, J. (2013). \emph{Statistical Power Analysis for the Behavioral Sciences}. Routledge. \url{https://doi.org/10.4324/9780203771587}
+
+\bibitem[\citeproctext]{ref-cohen2003}
+Cohen, J., Cohen, P., West, S. G., \& Aiken, L. (2003). \emph{Applied multiple regression / correlation analysis for the behavioral sciences} (3rd ed.). Lawrence Erlbaum Associates.
+
+\bibitem[\citeproctext]{ref-counsell2020}
+Counsell, A., Cribbie, R.
+A., \& Flora, D.
+B.
+(2020).
+Evaluating equivalence testing methods for measurement invariance.
+\emph{Multivariate Behavioral Research}, \emph{55}(2), 312--328.
+\url{https://doi.org/10.1080/00273171.2019.1633617}
+
+\bibitem[\citeproctext]{ref-cumming2012}
+Cumming, G. (2012). \emph{Understanding the new statistics: Effect sizes, confidence intervals, and meta-analysis}. Routledge.
+
+\bibitem[\citeproctext]{ref-cumming2016}
+Cumming, G., \& Calin-Jageman, R. (2016). \emph{Introduction to the New Statistics} (0th ed.). Routledge. \url{https://doi.org/10.4324/9781315708607}
+
+\bibitem[\citeproctext]{ref-devellis2022}
+DeVellis, R. F., \& Thorpe, C. T. (2022). \emph{Scale development: Theory and applications} (Fifth edition). SAGE Publications, Inc.
+
+\bibitem[\citeproctext]{ref-dueber2023}
+Dueber, D. (2023). \emph{Dmacs}. \url{https://github.com/ddueber/dmacs}
+
+\bibitem[\citeproctext]{ref-epskamp2022}
+Epskamp, S. (2022). \emph{semPlot: Path diagrams and visual analysis of various SEM packages' output}. \url{https://CRAN.R-project.org/package=semPlot}
+
+\bibitem[\citeproctext]{ref-flake2020}
+Flake, J.
+K., \& Fried, E.
+I.
+(2020).
+Measurement Schmeasurement: Questionable Measurement Practices and How to Avoid Them.
+\emph{Advances in Methods and Practices in Psychological Science}, \emph{3}(4), 456--465.
+\url{https://doi.org/10.1177/2515245920952393}
+
+\bibitem[\citeproctext]{ref-hobson2019}
+Hobson, H. (2019). Registered reports are an ally to early career researchers. \emph{Nature Human Behaviour}, \emph{3}(10), 1010--1010. \url{https://doi.org/10.1038/s41562-019-0701-8}
+
+\bibitem[\citeproctext]{ref-jin2020}
+Jin, Y.
+(2020).
+A note on the cutoff values of alternative fit indices to evaluate measurement invariance for ESEM models.
+\emph{International Journal of Behavioral Development}, \emph{44}(2), 166--174.
+\url{https://doi.org/10.1177/0165025419866911}
+
+\bibitem[\citeproctext]{ref-juxf6reskog1971}
+Jöreskog, K. G. (1971). Simultaneous factor analysis in several populations. \emph{Psychometrika}, \emph{36}(4), 409--426. \url{https://doi.org/10.1007/BF02291366}
+
+\bibitem[\citeproctext]{ref-juxf6reskog2001}
+Jöreskog, K. G., \& Sörbom, D. (2001). \emph{LISREL 8: user's reference guide} (2. ed., updated to LISREL 8). SSI Scientific Software Internat.
+
+\bibitem[\citeproctext]{ref-lakens2017}
+Lakens, D. (2017). Equivalence Tests. \emph{Social Psychological and Personality Science}, \emph{8}(4), 355--362. \url{https://doi.org/10.1177/1948550617697177}
+
+\bibitem[\citeproctext]{ref-makel2014}
+Makel, M.
+C., \& Plucker, J.
+A.
+(2014).
+Facts Are More Important Than Novelty: Replication in the Education Sciences.
+\emph{Educational Researcher}, \emph{43}(6), 304--316.
+\url{https://doi.org/10.3102/0013189X14545513}
+
+\bibitem[\citeproctext]{ref-makel2012}
+Makel, M.
+C., Plucker, J.
+A., \& Hegarty, B.
+(2012).
+Replications in Psychology Research: How Often Do They Really Occur?
+\emph{Perspectives on Psychological Science}, \emph{7}(6), 537--542.
+\url{https://doi.org/10.1177/1745691612460688}
+
+\bibitem[\citeproctext]{ref-marsh2004}
+Marsh, H.
+W., Hau, K.-T., \& Wen, Z.
+(2004).
+In search of golden rules: Comment on hypothesis-testing approaches to setting cutoff values for fit indexes and dangers in overgeneralizing hu and bentler's (1999) findings.
+\emph{Structural Equation Modeling: A Multidisciplinary Journal}, \emph{11}(3), 320--341.
+\url{https://doi.org/10.1207/s15328007sem1103_2}
+
+\bibitem[\citeproctext]{ref-mayo-wilson2021}
+Mayo-Wilson, E., Grant, S., Supplee, L., Kianersi, S., Amin, A., DeHaven, A., \& Mellor, D.
+(2021).
+Evaluating implementation of the transparency and openness promotion~(TOP) guidelines:~The TRUST process for rating journal policies, procedures, and practices.
+\emph{Research Integrity and Peer Review}, \emph{6}(1), 9.
+\url{https://doi.org/10.1186/s41073-021-00112-8}
+
+\bibitem[\citeproctext]{ref-meredith1993}
+Meredith, W. (1993). Measurement invariance, factor analysis and factorial invariance. \emph{Psychometrika}, \emph{58}(4), 525--543. \url{https://doi.org/10.1007/BF02294825}
+
+\bibitem[\citeproctext]{ref-nelson2018}
+Nelson, L. D., Simmons, J., \& Simonsohn, U. (2018). Psychology's renaissance. \emph{Annual Review of Psychology}, \emph{69}(1), 511--534. \url{https://doi.org/10.1146/annurev-psych-122216-011836}
+
+\bibitem[\citeproctext]{ref-nosek2018}
+Nosek, B.
+A., Ebersole, C.
+R., DeHaven, A.
+C., \& Mellor, D.
+T.
+(2018).
+The preregistration revolution.
+\emph{Proceedings of the National Academy of Sciences of the United States of America}, \emph{115}(11), 2600--2606.
+\url{https://doi.org/10.1073/pnas.1708274114}
+
+\bibitem[\citeproctext]{ref-nosek2014}
+Nosek, B.
+A., \& Lakens, D.
+(2014).
+Registered Reports: A Method to Increase the Credibility of Published Results.
+\emph{Social Psychology}, \emph{45}(3), 137--141.
+\url{https://doi.org/10.1027/1864-9335/a000192}
+
+\bibitem[\citeproctext]{ref-nye2019}
+Nye, C.
+D., Bradburn, J., Olenick, J., Bialko, C., \& Drasgow, F.
+(2019).
+How Big Are My Effects?
+Examining the Magnitude of Effect Sizes in Studies of Measurement Equivalence.
+\emph{Organizational Research Methods}, \emph{22}(3), 678--709.
+\url{https://doi.org/10.1177/1094428118761122}
+
+\bibitem[\citeproctext]{ref-nye2011}
+Nye, C.
+D., \& Drasgow, F.
+(2011).
+Effect size indices for analyses of measurement equivalence: Understanding the practical importance of differences between groups.
+\emph{Journal of Applied Psychology}, \emph{96}(5), 966--980.
+\url{https://doi.org/10.1037/a0022955}
+
+\bibitem[\citeproctext]{ref-putnick2016}
+Putnick, D.
+L., \& Bornstein, M.
+H.
+(2016).
+Measurement invariance conventions and reporting: The state of the art and future directions for psychological research.
+\emph{Developmental Review}, \emph{41}, 71--90.
+\url{https://doi.org/10.1016/j.dr.2016.06.004}
+
+\bibitem[\citeproctext]{ref-robinson2023}
+Robinson, D., Hayes, A., Couch {[}aut, S., cre, Software, P., PBC, Patil, I., Chiu, D., Gomez, M., Demeshev, B., Menne, D., Nutter, B., Johnston, L., Bolker, B., Briatte, F., Arnold, J., Gabry, J., Selzer, L., Simpson, G., \ldots{} Reinhart, A.
+(2023).
+\emph{Broom: Convert statistical objects into tidy tibbles}.
+\url{https://CRAN.R-project.org/package=broom}
+
+\bibitem[\citeproctext]{ref-rosseel2012}
+Rosseel, Y. (2012). Lavaan: An r package for structural equation modeling. \emph{Journal of Statistical Software}, \emph{48}(1), 1--36. \url{https://doi.org/10.18637/jss.v048.i02}
+
+\bibitem[\citeproctext]{ref-schwarz1978}
+Schwarz, G. (1978). Estimating the dimension of a model. \emph{The Annals of Statistics}, \emph{6}(2), 461--464. \url{https://www.jstor.org/stable/2958889}
+
+\bibitem[\citeproctext]{ref-shadish2001}
+Shadish, W. R., Cook, T. D., \& Campbell, D. T. (2001). \emph{Experimental and quasi-experimental designs for generalized causal inference}. Houghton Mifflin.
+
+\bibitem[\citeproctext]{ref-suxf6rbom1978}
+Sörbom, D. (1978). An alternative to the methodology for analysis of covariance. \emph{Psychometrika}, \emph{43}(3), 381--396. \url{https://doi.org/10.1007/BF02293647}
+
+\bibitem[\citeproctext]{ref-stark2004}
+Stark, S., Chernyshenko, O.
+S., \& Drasgow, F.
+(2004).
+Examining the Effects of Differential Item (Functioning and Differential) Test Functioning on Selection Decisions: When Are Statistically Significant Effects Practically Important?
+\emph{Journal of Applied Psychology}, \emph{89}(3), 497--508.
+\url{https://doi.org/10.1037/0021-9010.89.3.497}
+
+\bibitem[\citeproctext]{ref-stark2006}
+Stark, S., Chernyshenko, O.
+S., \& Drasgow, F.
+(2006).
+Detecting differential item functioning with confirmatory factor analysis and item response theory: Toward a unified strategy.
+\emph{Journal of Applied Psychology}, \emph{91}(6), 1292--1306.
+\url{https://doi.org/10.1037/0021-9010.91.6.1292}
+
+\bibitem[\citeproctext]{ref-steiger1990}
+Steiger, J.
+H.
+(1990).
+Structural model evaluation and modification: An interval estimation approach.
+\emph{Multivariate Behavioral Research}, \emph{25}(2), 173--180.
+\url{https://doi.org/10.1207/s15327906mbr2502_4}
+
+\bibitem[\citeproctext]{ref-trent2013}
+Trent, L.
+R., Buchanan, E., Ebesutani, C., Ale, C.
+M., Heiden, L., Hight, T.
+L., Damon, J.
+D., \& Young, J.
+(2013).
+A measurement invariance examination of the revised child anxiety and depression scale in a southern sample: Differential item functioning between african american and caucasian youth.
+\emph{Assessment}, \emph{20}(2), 175--187.
+\url{https://doi.org/10.1177/1073191112450907}
+
+\bibitem[\citeproctext]{ref-tucker1973}
+Tucker, L. R., \& Lewis, C. (1973). A reliability coefficient for maximum likelihood factor analysis. \emph{Psychometrika}, \emph{38}(1), 1--10. \url{https://doi.org/10.1007/BF02291170}
+
+\bibitem[\citeproctext]{ref-vandeschoot2015}
+Van De Schoot, R., Schmidt, P., De Beuckelaer, A., Lek, K., \& Zondervan-Zwijnenburg, M.
+(2015).
+Editorial: Measurement invariance.
+\emph{Frontiers in Psychology}, \emph{6}.
+\url{https://www.frontiersin.org/articles/10.3389/fpsyg.2015.01064}
+
+\bibitem[\citeproctext]{ref-vazire2022}
+Vazire, S., Schiavone, S.
+R., \& Bottesini, J.
+G.
+(2022).
+Credibility Beyond Replicability: Improving the Four Validities in Psychological Science.
+\emph{Current Directions in Psychological Science}, \emph{31}(2), 162--168.
+\url{https://doi.org/10.1177/09637214211067779}
+
+\bibitem[\citeproctext]{ref-wagnild2009}
+Wagnild, G. (2009). A review of the resilience scale. \emph{Journal of Nursing Measurement}, \emph{17}(2), 105--113. \url{https://doi.org/10.1891/1061-3749.17.2.105}
+
+\bibitem[\citeproctext]{ref-weidman2017}
+Weidman, A.
+C., Steckler, C.
+M., \& Tracy, J.
+L.
+(2017).
+The jingle and jangle of emotion assessment: Imprecise measurement, casual scale usage, and conceptual fuzziness in emotion research.
+\emph{Emotion}, \emph{17}(2), 267--295.
+\url{https://doi.org/10.1037/emo0000226}
+
+\bibitem[\citeproctext]{ref-R-ggplot2}
+Wickham, H. (2016). \emph{ggplot2: Elegant graphics for data analysis}. Springer-Verlag New York. \url{https://ggplot2.tidyverse.org}
+
+\bibitem[\citeproctext]{ref-wilke2020}
+Wilke, C. O. (2020). \emph{Cowplot: Streamlined plot theme and plot annotations for 'ggplot2'}. \url{https://CRAN.R-project.org/package=cowplot}
+
+\bibitem[\citeproctext]{ref-yu2004}
+Yu, D.
+S.
+F., Lee, D.
+T.
+F., \& Woo, J.
+(2004).
+Issues and Challenges of Instrument Translation.
+\emph{Western Journal of Nursing Research}, \emph{26}(3), 307--320.
+\url{https://doi.org/10.1177/0193945903260554}
+
+\bibitem[\citeproctext]{ref-zwaan2018}
+Zwaan, R. A., Etz, A., Lucas, R. E., \& Donnellan, M. B. (2018). Making replication mainstream. \emph{Behavioral and Brain Sciences}, \emph{41}, e120. \url{https://doi.org/10.1017/S0140525X17001972}
+
+\end{CSLReferences}
+
+\newpage
+
+\appendix
+
+\section{Code Examples}\label{code-examples}
+
+\subsection{Simulating from Models}\label{simulating-from-models}
+
+Here's an example of how to simulate directly from a \texttt{lavaan} model:
+
+\small
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\# first build your model}
+\CommentTok{\# this example is separate for each group}
+\NormalTok{model.invariant.g1 }\OtherTok{\textless{}{-}} \StringTok{"}
+\StringTok{\# loadings}
+\StringTok{lv =\textasciitilde{} .8*q1 + .4*q2 + .6*q3 + .3*q4 + .6*q5 }
+\StringTok{\# set the residual for invariance on q4}
+\StringTok{q4 \textasciitilde{}\textasciitilde{} 1*q4}
+\StringTok{\# set the intercept for invariance on q4}
+\StringTok{q4 \textasciitilde{} 0*1}
+\StringTok{\# set the intercept to zero for df purposes}
+\StringTok{q1 \textasciitilde{} 0*1}
+\StringTok{\# allow the latent mean to be estimated }
+\StringTok{lv \textasciitilde{} 1"}
+\NormalTok{model.invariant.g2 }\OtherTok{\textless{}{-}} \StringTok{"lv =\textasciitilde{} .77*q1 + .43*q2 + .58*q3 + .3*q4 + .61*q5}
+\StringTok{q4 \textasciitilde{}\textasciitilde{} 1*q4}
+\StringTok{q4 \textasciitilde{} 0*1}
+\StringTok{q1 \textasciitilde{} 0*1}
+\StringTok{lv \textasciitilde{} 1"}
+
+\CommentTok{\# simulate data invariant separately for each group}
+\NormalTok{df.invariant }\OtherTok{\textless{}{-}} \FunctionTok{bind\_rows}\NormalTok{(}
+  \CommentTok{\# lavaan function }
+  \FunctionTok{simulateData}\NormalTok{(}
+    \CommentTok{\# model with estimates }
+    \AttributeTok{model =}\NormalTok{ model.invariant.g1, }
+    \CommentTok{\# how many data points}
+    \AttributeTok{sample.nobs =} \DecValTok{250}\NormalTok{, }
+    \CommentTok{\# mean structure for mgcfa models }
+    \AttributeTok{meanstructure =}\NormalTok{ T, }
+    \CommentTok{\# model type}
+    \AttributeTok{model.type =} \StringTok{"cfa"}\NormalTok{,}
+    \CommentTok{\# set seed for reproducibility }
+    \AttributeTok{seed =} \DecValTok{1234}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
+    \CommentTok{\# add a group label to the data }
+    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{group =} \StringTok{"Group 1"}\NormalTok{), }
+  \FunctionTok{simulateData}\NormalTok{(}
+    \AttributeTok{model =}\NormalTok{ model.invariant.g2, }
+    \AttributeTok{sample.nobs =} \DecValTok{250}\NormalTok{, }
+    \AttributeTok{meanstructure =}\NormalTok{ T, }
+    \AttributeTok{model.type =} \StringTok{"cfa"}\NormalTok{,}
+    \AttributeTok{seed =} \DecValTok{1234}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
+    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{group =} \StringTok{"Group 2"}\NormalTok{) }
+\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\normalsize
+
+\newpage
+
+\subsection{Simulating from Matrices}\label{simulating-from-matrices}
+
+Here's an example of how to simulate using \texttt{MASS} and covariance or correlation matrices.
+
+\small
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{library}\NormalTok{(MASS)}
+
+\CommentTok{\# covariance matrix}
+\NormalTok{university.cov }\OtherTok{\textless{}{-}} \FunctionTok{lav\_matrix\_lower2full}\NormalTok{(}
+    \FunctionTok{c}\NormalTok{(}\FloatTok{169.00}\NormalTok{, }
+      \FloatTok{73.710}\NormalTok{, }\FloatTok{182.2500}\NormalTok{,}
+      \FloatTok{73.229}\NormalTok{, }\FloatTok{88.4250}\NormalTok{, }\FloatTok{171.6100}\NormalTok{,}
+      \FloatTok{63.375}\NormalTok{, }\FloatTok{72.5625}\NormalTok{, }\FloatTok{127.7250}\NormalTok{, }\FloatTok{156.2500}\NormalTok{,}
+      \FloatTok{42.120}\NormalTok{, }\FloatTok{67.4325}\NormalTok{, }\FloatTok{122.0265}\NormalTok{, }\FloatTok{123.1875}\NormalTok{, }\FloatTok{182.2500}\NormalTok{,}
+      \FloatTok{57.226}\NormalTok{, }\FloatTok{63.2610}\NormalTok{, }\FloatTok{117.1926}\NormalTok{, }\FloatTok{154.4250}\NormalTok{, }\FloatTok{138.0240}\NormalTok{, }\FloatTok{201.6400}\NormalTok{,}
+      \FloatTok{30.875}\NormalTok{, }\FloatTok{32.0625}\NormalTok{, }\FloatTok{60.9805}\NormalTok{, }\FloatTok{62.9375}\NormalTok{, }\FloatTok{76.9500}\NormalTok{, }\FloatTok{79.5910}\NormalTok{, }\FloatTok{90.2500}\NormalTok{,}
+      \FloatTok{36.075}\NormalTok{, }\FloatTok{38.9610}\NormalTok{, }\FloatTok{61.0722}\NormalTok{, }\FloatTok{58.2750}\NormalTok{, }\FloatTok{65.9340}\NormalTok{, }\FloatTok{70.9290}\NormalTok{, }\FloatTok{81.1965}\NormalTok{, }\FloatTok{123.2100}\NormalTok{,}
+      \FloatTok{18.096}\NormalTok{, }\FloatTok{21.1410}\NormalTok{, }\FloatTok{26.2131}\NormalTok{, }\FloatTok{39.1500}\NormalTok{, }\FloatTok{44.6310}\NormalTok{, }\FloatTok{46.9452}\NormalTok{, }\FloatTok{48.7635}\NormalTok{, }\FloatTok{56.0106}\NormalTok{, }\FloatTok{75.6900}\NormalTok{))}
+
+\CommentTok{\# give it names}
+\FunctionTok{rownames}\NormalTok{(university.cov) }\OtherTok{\textless{}{-}}
+    \FunctionTok{colnames}\NormalTok{(university.cov) }\OtherTok{\textless{}{-}}
+    \FunctionTok{c}\NormalTok{(}\StringTok{"class"}\NormalTok{, }\StringTok{"social"}\NormalTok{, }\StringTok{"learn"}\NormalTok{, }\StringTok{"chronic"}\NormalTok{, }\StringTok{"physical"}\NormalTok{, }\StringTok{"sex"}\NormalTok{, }
+      \StringTok{"depression"}\NormalTok{, }\StringTok{"anxiety"}\NormalTok{, }\StringTok{"stress"}\NormalTok{)}
+
+\CommentTok{\# means {-} you need standard deviation if you only have a correlation matrix }
+\NormalTok{university.means }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\FloatTok{3.4}\NormalTok{, }\FloatTok{4.3}\NormalTok{, }\FloatTok{3.7}\NormalTok{, }\FloatTok{3.2}\NormalTok{, }\FloatTok{4.5}\NormalTok{, }\FloatTok{1.2}\NormalTok{, }\FloatTok{4.0}\NormalTok{, }\FloatTok{3.5}\NormalTok{, }\FloatTok{4.2}\NormalTok{)}
+
+\CommentTok{\# use mass function}
+\NormalTok{DF }\OtherTok{\textless{}{-}} \FunctionTok{mvrnorm}\NormalTok{(}\AttributeTok{n =} \DecValTok{200}\NormalTok{, }\AttributeTok{mu =}\NormalTok{ university.means, }\AttributeTok{Sigma =}\NormalTok{ university.cov)}
+
+\FunctionTok{head}\NormalTok{(DF)}
+\end{Highlighting}
+\end{Shaded}
+
+\normalsize
+
+\begin{verbatim}
+##           class     social      learn   chronic   physical        sex
+## [1,]   9.332202  6.7442501   8.001600  6.771713 -10.833804  -3.837477
+## [2,]   4.873877 -0.1368433  11.690145 14.572699  13.356779  22.699918
+## [3,]  13.650244 -5.5841743  -2.295967 -3.914620  -6.552379 -11.711882
+## [4,]   7.644520 -1.6201790 -15.075033  4.010138   4.741793  11.704179
+## [5,] -10.491240 14.6367273   2.951522 10.934949   1.153787   3.637487
+## [6,]   3.188521 -0.2078648 -11.655781 -8.085560 -12.482893 -18.914448
+##       depression    anxiety     stress
+## [1,]  -9.2071866 -9.0853468 -10.016408
+## [2,]  -5.7266089 -5.1086786  -3.757830
+## [3,] -12.3350189 -9.5855529 -10.855687
+## [4,]  -0.8850695 -8.8631134  -1.046865
+## [5,]  -3.4707411 -0.1493184  -2.300569
+## [6,]  -9.1500394  0.3167367   5.590050
+\end{verbatim}
+
+\newpage
+
+\subsection{\texorpdfstring{MGCFA: \texttt{mgcfa()} Function}{MGCFA: mgcfa() Function}}\label{mgcfa-mgcfa-function-1}
+
+In this example, we make our example model using \emph{lavaan} syntax.
 The \texttt{lv} latent variable predicts the five measured variables, which are present as columns in our \texttt{df.invariant} data set.
-The package does generally require raw data for bootstrapping purposes, and an example of how to simulate data from models and covariance/correlations tables sometimes provided in manuscripts (rather than the raw data) is provided in the supplemental documentation.
 
@@
 
-The \texttt{mgcfa} function is designed to flexibly allow you to leverage \texttt{lavaan}'s package functions to calculate multiple measurement steps at once. You would include:
+The \texttt{mgcfa()} function is designed to flexibly allow you to leverage \emph{lavaan}'s package functions to calculate multiple measurement steps at once. You would include:
 
@@
 
-Note: you can also use \texttt{sample.cov}, \texttt{sample.mean}, \texttt{sample.nobs} in this step for estimation of multi-group models, but simulated dataframes are needed for bootstrapping replication estimates.
+Note: you can also use \texttt{sample.cov}, \texttt{sample.mean}, \texttt{sample.nobs} in this step for estimation of multigroup models, but simulated dataframes are needed for bootstrapping replication estimates.
 
@@
 
-The following output is saved:
-
 \begin{enumerate}
@@
 \begin{verbatim}
-## # A tibble: 10 x 13
-##    term     op    estimate std.error statistic   p.value  std.lv std.all std.nox
-##    <chr>    <chr>    <dbl>     <dbl>     <dbl>     <dbl>   <dbl>   <dbl>   <dbl>
-##  1 "lv =~ ~ =~      1         0         NA     NA         0.803   0.616   0.616 
-##  2 "lv =~ ~ =~      0.655     0.0880     7.44   9.77e-14  0.526   0.493   0.493 
-##  3 "lv =~ ~ =~      0.640     0.0895     7.15   8.83e-13  0.514   0.463   0.463 
-##  4 "lv =~ ~ =~      0.277     0.0749     3.69   2.24e- 4  0.222   0.209   0.209 
-##  5 "lv =~ ~ =~      0.955     0.117      8.13   4.44e-16  0.766   0.656   0.656 
-##  6 "q1 ~1 " ~1      0         0         NA     NA         0       0       0     
-##  7 "lv ~1 " ~1     -0.0305    0.0582    -0.524  6.00e- 1 -0.0380 -0.0380 -0.0380
-##  8 "q1 ~~ ~ ~~      1.05      0.0995    10.6    0         1.05    0.620   0.620 
-##  9 "q2 ~~ ~ ~~      0.860     0.0653    13.2    0         0.860   0.757   0.757 
-## 10 "q3 ~~ ~ ~~      0.966     0.0711    13.6    0         0.966   0.785   0.785 
-## # i 4 more variables: model <chr>, block <int>, group <int>, label <chr>
+## # A tibble: 10 x 12
+##    term       op    estimate std.error statistic   p.value  std.lv std.all model
+##    <chr>      <chr>    <dbl>     <dbl>     <dbl>     <dbl>   <dbl>   <dbl> <chr>
+##  1 "lv =~ q1" =~      1         0         NA     NA         0.803   0.616  Over~
+##  2 "lv =~ q2" =~      0.655     0.0880     7.44   9.77e-14  0.526   0.493  Over~
+##  3 "lv =~ q3" =~      0.640     0.0895     7.15   8.83e-13  0.514   0.463  Over~
+##  4 "lv =~ q4" =~      0.277     0.0749     3.69   2.24e- 4  0.222   0.209  Over~
+##  5 "lv =~ q5" =~      0.955     0.117      8.13   4.44e-16  0.766   0.656  Over~
+##  6 "q1 ~1 "   ~1      0         0         NA     NA         0       0      Over~
+##  7 "lv ~1 "   ~1     -0.0305    0.0582    -0.524  6.00e- 1 -0.0380 -0.0380 Over~
+##  8 "q1 ~~ q1" ~~      1.05      0.0995    10.6    0         1.05    0.620  Over~
+##  9 "q2 ~~ q2" ~~      0.860     0.0653    13.2    0         0.860   0.757  Over~
+## 10 "q3 ~~ q3" ~~      0.966     0.0711    13.6    0         0.966   0.785  Over~
+## # i 3 more variables: block <int>, group <int>, label <chr>
 \end{verbatim}
@@
 These objects can be used with any function that normally takes a saved model: \texttt{parameterEstimates()}, \texttt{modificationIndices()}, \texttt{semPlot::semPaths()}, and so on (Epskamp, 2022).
+\end{enumerate}
+
+\small
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{class}\NormalTok{(results.invariant}\SpecialCharTok{$}\NormalTok{model\_overall)}
+\end{Highlighting}
+\end{Shaded}
+
+\normalsize
+
+\begin{verbatim}
+## [1] "lavaan"
+## attr(,"package")
+## [1] "lavaan"
+\end{verbatim}
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi})}
+\setcounter{enumi}{3}
+\tightlist
 \item
   \texttt{group\_models}: A list of saved fitted models for each group separately.
+\end{enumerate}
+
+\small
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{names}\NormalTok{(results.invariant}\SpecialCharTok{$}\NormalTok{group\_models)}
+\end{Highlighting}
+\end{Shaded}
+
+\normalsize
+
+\begin{verbatim}
+## [1] "model.Group 1" "model.Group 2"
+\end{verbatim}
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi})}
+\setcounter{enumi}{4}
+\tightlist
 \item
   \texttt{model\_configural}: A saved fitted model for the configural model that nests together each group into one model with no other constraints.
+\end{enumerate}
+
+\small
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{class}\NormalTok{(results.invariant}\SpecialCharTok{$}\NormalTok{model\_configural)}
+\end{Highlighting}
+\end{Shaded}
+
+\normalsize
+
+\begin{verbatim}
+## [1] "lavaan"
+## attr(,"package")
+## [1] "lavaan"
+\end{verbatim}
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi})}
+\setcounter{enumi}{5}
+\tightlist
 \item
@@
 
-\hypertarget{visualization-of-invariance}{%
-\subsection{Visualization of Invariance}\label{visualization-of-invariance}}
-
-\hypertarget{package-function}{%
-\subsubsection{Package Function}\label{package-function}}
-
-The results from the \texttt{model\_coef} table can then be used directly in \texttt{plot\_mi()}. The plot outputs will be described below. First, here are the arguments for the function:
+\small
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{names}\NormalTok{(results.invariant}\SpecialCharTok{$}\NormalTok{invariance\_models)}
+\end{Highlighting}
+\end{Shaded}
+
+\normalsize
+
+\begin{verbatim}
+## [1] "model.loadings"   "model.intercepts" "model.residuals"
+\end{verbatim}
+
+\newpage
+
+\subsection{\texorpdfstring{Partial Invariance: \texttt{partial\_mi()} Function}{Partial Invariance: partial\_mi() Function}}\label{partial-invariance-partial_mi-function-1}
+
+The \texttt{partial\_mi()} function aids in the calculation of partial invariance for a specific step of the MGCFA process. The function includes the following arguments:
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi})}
+\tightlist
+\item
+  \texttt{saved\_model}: The saved \emph{lavaan} model with the equality constraints at the level of measurement invariance you would like to examine for partial invariance.
+\item
+  \texttt{data}: The dataframe where the model was estimated.
+\item
+  \texttt{model}: The model syntax for the overall model.
+\item
+  \texttt{group}: The grouping variable column in the dataframe.
+\item
+  \texttt{group.equal}: The equality constraints including in your original multigroup tests.
+\item
+  \texttt{partial\_step}: The level of partial invariance you wish to test.
+\end{enumerate}
+
+\small
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{partial.invariant }\OtherTok{\textless{}{-}}
+  \FunctionTok{partial\_mi}\NormalTok{(}
+    \CommentTok{\# saved model output with constraints}
+    \AttributeTok{saved\_model =}\NormalTok{ results.invariant}\SpecialCharTok{$}\NormalTok{invariance\_models}\SpecialCharTok{$}\NormalTok{model.residuals,}
+    \CommentTok{\# dataframe from model }
+    \AttributeTok{data =}\NormalTok{ df.invariant,}
+    \CommentTok{\# model syntax }
+    \AttributeTok{model =}\NormalTok{ model.overall,}
+    \CommentTok{\# group column name }
+    \AttributeTok{group =} \StringTok{"group"}\NormalTok{,}
+    \CommentTok{\# group equality constraints from your mgcfa}
+    \AttributeTok{group.equal =} \FunctionTok{c}\NormalTok{(}\StringTok{"loadings"}\NormalTok{, }\StringTok{"intercepts"}\NormalTok{, }\StringTok{"residuals"}\NormalTok{),}
+    \CommentTok{\# which step you want to examine for partial invariance}
+    \AttributeTok{partial\_step =} \StringTok{"residuals"}
+\NormalTok{    )}
+
+\FunctionTok{names}\NormalTok{(partial.invariant)}
+\end{Highlighting}
+\end{Shaded}
+
+\normalsize
+
+\begin{verbatim}
+## [1] "models"    "fit_table"
+\end{verbatim}
+
+In this function, each parameter with the appropriate \emph{lavaan} syntax is relaxed individually (i.e., \texttt{\textasciitilde{}1} for intercepts, \texttt{\textasciitilde{}\textasciitilde{}} for residuals, etc.).
+The fitted models are saved in the \texttt{models} output, and the \texttt{fit\_table} output includes all fit indices for each model to investigate potential areas of partial invariance based on the researcher's desired criterion.
+
+\small
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{names}\NormalTok{(partial.invariant}\SpecialCharTok{$}\NormalTok{models)}
+\end{Highlighting}
+\end{Shaded}
+
+\normalsize
+
+\begin{verbatim}
+## [1] "q1 ~~ q1" "q2 ~~ q2" "q3 ~~ q3" "q4 ~~ q4" "q5 ~~ q5" "lv ~~ lv"
+\end{verbatim}
+
+\small
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{head}\NormalTok{(partial.invariant}\SpecialCharTok{$}\NormalTok{fit\_table }\SpecialCharTok{\%\textgreater{}\%} 
+\NormalTok{       dplyr}\SpecialCharTok{::}\FunctionTok{select}\NormalTok{(free.parameter, cfi, rmsea))}
+\end{Highlighting}
+\end{Shaded}
+
+\normalsize
+
+\begin{verbatim}
+## # A tibble: 6 x 3
+##   free.parameter cfi        rmsea     
+##   <chr>          <lvn.vctr> <lvn.vctr>
+## 1 q1 ~~ q1       0.9902679  0.02108648
+## 2 q2 ~~ q2       0.9868905  0.02447336
+## 3 q3 ~~ q3       0.9958241  0.01381266
+## 4 q4 ~~ q4       1.0000000  0.00000000
+## 5 q5 ~~ q5       0.9868088  0.02454944
+## 6 lv ~~ lv       0.9906154  0.02025143
+\end{verbatim}
+
+Note: the \texttt{partial\_step} function is used to determine which types of \texttt{op} or operators to freely estimate between groups.
+If one chooses residuals, you will also freely estimate the residual for the latent variable or any other residuals found in the model.
+These items may be ignored if they were not meant to be included.
+
+\newpage
+
+\subsection{\texorpdfstring{Visualization of Invariance: \texttt{plot\_mi()} Functions}{Visualization of Invariance: plot\_mi() Functions}}\label{visualization-of-invariance-plot_mi-functions}
+
+Once we know which items are non-invariant, the \texttt{model\_coef} output from the \texttt{mgcfa()} can be used directly in \texttt{plot\_mi()}.
+The plot outputs will be described below.
+First, here are the arguments for the function:
 
@@
 \item
-  \texttt{plot\_groups}: If you include more than two groups in a multi-group model, the automatic assumption is that you want the first two groups for this visualization.
+  \texttt{plot\_groups}: If you include more than two groups in a multigroup model, the automatic assumption is that you want the first two groups for this visualization.
 If not, include the names of the groups here to plot.
@@
 \centering
-\includegraphics{manuscript_files/figure-latex/invariant-pic-1.pdf}
-\caption{\label{fig:invariant-pic}Invariant Model Visualization}
+\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/invariant-pic-app-1.pdf}}
+\caption{\label{fig:invariant-pic-app}Invariant Model Visualization}
 \end{figure}
@@
 
-\hypertarget{simulated-results}{%
-\subsubsection{Simulated Results}\label{simulated-results}}
-
-The \(d_{MACS}\) value for item 4 in the invariant model was 0.16, representing a nil or unimportant difference in this manuscript.
-It is important to note that while Nye et al.
-(2019) suggests specific sizes for small, medium, and large, each researcher should determine for themselves what effects represent.
-Figure \ref{fig:small-load-pic} displays the results from the small (\(d_{MACS}\) = 0.27) difference in loadings, while Figure \ref{fig:med-load-pic} displays the results from the medium (\(d_{MACS}\) = 0.61) difference in loadings, and Figure \ref{fig:large-load-pic} shows the large (\(d_{MACS}\) = 0.66) differences.
-When investigating the slope values, we can clearly see the change in the loading for the second group (the only manipulated variable, although random data set generation may also change intercepts and residuals slightly).
-At the medium effect size, we see that the confidence bands do not overlap (at the edges), and at the large effect size, we can see a clear separation of two lines.
-Note that the intercepts in this model are estimated as equal so the loading representation will not literally separate, but the steepness of the lines is the indicator of the difference between the slopes.
-You can imagine these lines are interpreted like a simple slopes analysis for interactions in regression (Cohen et al., 2003).
-When simple slopes for interactions are plotted, if they are parallel, there is no interaction, and if they cross, then there is an interaction.
-Here, we can use this same logic.
-If they are parallel, there is likely invariance (they are the same), and the further from parallel they become, the larger the effect size for the differences between group loadings.
-
-The latent means in Figure \ref{fig:large-load-pic} do appear to show differences, albeit visually small.
-The latent means diagram shows the impact of any group differences that aren't constrained, and this image shows the configural model (as the metric model would force them to be equal).
-In the simulated model, the \emph{only} manipulated parameter is question 4's loading.
-In real models, the differences may be larger due to other variation found in the parameter estimates.
-Therefore, once you discover items you believe would make a model ``partially'' invariant, you may wish to estimate that model and graph the item again using the partially invariant model to see only the effect of the non-invariant items.
-Additionally, consider that we set the scaling of the model to 0.
-The estimate for the lv mean in the large loading model was group 1: 0.00, and group 2: -0.06, which results in 0.06 difference in group means.
-The practical implications of this difference will depend on the research and interpretations of the researcher.
-
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/small-load-pic-1.pdf}
-\caption{\label{fig:small-load-pic}Small Loadings Model Visualization}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/med-load-pic-1.pdf}
-\caption{\label{fig:med-load-pic}Medium Loadings Model Visualization}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/large-load-pic-1.pdf}
-\caption{\label{fig:large-load-pic}Large Loadings Model Visualization}
-\end{figure}
-
-For intercepts, the small (Figure \ref{fig:small-int-pic}), medium (Figure \ref{fig:med-int-pic}), and large (Figure \ref{fig:large-int-pic}) depictions represent \(d_{MACS}\) values of 0.26, 0.47, and 0.70, respectively.
-Intercept differences can be clearly seen represented by the spacing out of the intercept locations (and thus, the overall line as well).
-While the changes in intercept do not appear to change the latent means, the caveat to this simulation is that only item four was manipulated.
-An example is provided below that demonstrates large changes in latent means.
-
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/small-int-pic-1.pdf}
-\caption{\label{fig:small-int-pic}Small Intercepts Model Visualization}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/med-int-pic-1.pdf}
-\caption{\label{fig:med-int-pic}Medium Intercepts Model Visualization}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/large-int-pic-1.pdf}
-\caption{\label{fig:large-int-pic}Large Intercepts Model Visualization}
-\end{figure}
-
-Last, the effect of the residuals is plotted in small (Figure \ref{fig:small-res-pic}), medium (Figure \ref{fig:med-res-pic}), and large (Figure \ref{fig:large-res-pic}) formats.
-While \(d_{MACS}\) values are not technically available for the residuals, our models showed 0.19, 0.10, and 0.16, respectively.
-These differences in values are variable due to the random generation of data sets for each measurement invariance manipulation.
-At first glance, the differences in the small chart may seem large, because the black lines are not touching, but notice that the distributions overlap, indicating a likely small difference.
-The medium and large differences better illustrate differences in residuals across groups.
-Further, the impact of the residuals on the shape of the latent mean distribution can also been seen (and unintentionally, in the first figures as well due to random variation).
-The impact is due to the standard error of the residuals, as smaller standard errors represent lepokurtic distributions (taller), and larger standard errors represent platykurtic distributions (flatter).
-The effect size difference of the residuals does not appear to change the effects in the latent means.
-
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/small-res-pic-1.pdf}
-\caption{\label{fig:small-res-pic}Small Residuals Model Visualization}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/med-res-pic-1.pdf}
-\caption{\label{fig:med-res-pic}Medium Residuals Model Visualization}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/large-res-pic-1.pdf}
-\caption{\label{fig:large-res-pic}Large Residuals Model Visualization}
-\end{figure}
-
-\hypertarget{partial-invariance-calculation}{%
-\subsection{Partial Invariance Calculation}\label{partial-invariance-calculation}}
-
-\hypertarget{package-function-1}{%
-\subsubsection{Package Function}\label{package-function-1}}
-
-The results of the simulated models are presented in the appendix, demonstrating that each simulated dataset shows partial invariance if item four is allowed to vary between groups.
-The function takes the following arguments:
+\newpage
+
+\subsection{\texorpdfstring{Model Replication and Effect Sizes: \texttt{bootstrap\_model()} Function}{Model Replication and Effect Sizes: bootstrap\_model() Function}}\label{model-replication-and-effect-sizes-bootstrap_model-function-1}
+
+The \texttt{bootstrap\_model} function in \emph{visualizemi} was designed to estimate the likely replication of overall model invariance with the assumption that the data used for the estimation represents the larger population.
+The following arguments are used:
 
@@
 \item
-  \texttt{saved\_model}: The saved \emph{lavaan} model with the equality constraints at the level of measurement invariance you would like to examine for partial invariance.
-\item
-  \texttt{data}: The dataframe where the model was estimated.
-\item
-  \texttt{model}: The model syntax for the overall model.
-\item
-  \texttt{group}: The grouping variable column in the dataframe.
-\item
-  \texttt{group.equal}: The equality constraints including in your original multi-group tests.
-\item
-  \texttt{partial\_step}: The level of partial invariance you wish to test.
-\end{enumerate}
-
-\small
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{partial.invariant }\OtherTok{\textless{}{-}}
-  \FunctionTok{partial\_mi}\NormalTok{(}
-    \CommentTok{\# saved model output with constraints}
-    \AttributeTok{saved\_model =}\NormalTok{ results.invariant}\SpecialCharTok{$}\NormalTok{invariance\_models}\SpecialCharTok{$}\NormalTok{model.residuals,}
-    \CommentTok{\# dataframe from model }
-    \AttributeTok{data =}\NormalTok{ df.invariant,}
-    \CommentTok{\# model syntax }
-    \AttributeTok{model =}\NormalTok{ model.overall,}
-    \CommentTok{\# group column name }
-    \AttributeTok{group =} \StringTok{"group"}\NormalTok{,}
-    \CommentTok{\# group equality constraints from your mgcfa}
-    \AttributeTok{group.equal =} \FunctionTok{c}\NormalTok{(}\StringTok{"loadings"}\NormalTok{, }\StringTok{"intercepts"}\NormalTok{, }\StringTok{"residuals"}\NormalTok{),}
-    \CommentTok{\# which step you want to examine for partial invariance}
-    \AttributeTok{partial\_step =} \StringTok{"residuals"}
-\NormalTok{    )}
-
-\FunctionTok{names}\NormalTok{(partial.invariant)}
-\end{Highlighting}
-\end{Shaded}
-
-\normalsize
-
-\begin{verbatim}
-## [1] "models"    "fit_table"
-\end{verbatim}
-
-In this function, each parameter with the appropriate \emph{lavaan} syntax is relaxed individually (i.e., \texttt{\textasciitilde{}1} for intercepts, \texttt{\textasciitilde{}\textasciitilde{}} for residuals, etc.).
-The fitted models are saved in the \texttt{models} output, and the \texttt{fit\_table} output includes all fit indices for each model to investigate potential areas of partial invariance based on the researcher's desired criterion.
-Note: the \texttt{partial\_step} function is used to determine which types of \texttt{op} or operators to freely estimate between groups.
-If one chooses residuals, you will also freely estimate the residual for the latent variable or any other residuals found in the model.
-These items may be ignored if they were not meant to be included.
-
-\small
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\FunctionTok{head}\NormalTok{(partial.invariant}\SpecialCharTok{$}\NormalTok{fit\_table }\SpecialCharTok{\%\textgreater{}\%} 
-\NormalTok{       dplyr}\SpecialCharTok{::}\FunctionTok{select}\NormalTok{(free.parameter, cfi, rmsea))}
-\end{Highlighting}
-\end{Shaded}
-
-\normalsize
-
-\begin{verbatim}
-## # A tibble: 6 x 3
-##   free.parameter cfi        rmsea     
-##   <chr>          <lvn.vctr> <lvn.vctr>
-## 1 q1 ~~ q1       0.9902679  0.02108648
-## 2 q2 ~~ q2       0.9868905  0.02447336
-## 3 q3 ~~ q3       0.9958241  0.01381266
-## 4 q4 ~~ q4       1.0000000  0.00000000
-## 5 q5 ~~ q5       0.9868088  0.02454944
-## 6 lv ~~ lv       0.9906154  0.02025143
-\end{verbatim}
-
-\hypertarget{replication-and-effect-size-model}{%
-\subsection{Replication and Effect Size: Model}\label{replication-and-effect-size-model}}
-
-\hypertarget{package-function-2}{%
-\subsubsection{Package Function}\label{package-function-2}}
-
-The \texttt{bootstrap\_model} function in \emph{visualizemi} was designed to estimate the likely replication of overall model invariance with the assumption that the data used for the estimation represents the larger population.
-The following arguments are used:
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi})}
-\tightlist
-\item
   \texttt{saved\_configural}: a saved fitted model at the configural level with no equality constraints.
@@
 \item
-  \texttt{group.equal}: The equality constraints including in your original multi-group tests.
+  \texttt{group.equal}: The equality constraints including in your original multigroup tests.
 \end{enumerate}
@@
 
-\hypertarget{simulated-results-1}{%
-\subsubsection{Simulated Results}\label{simulated-results-1}}
-
-Figure \ref{fig:boot-rr-pic} portrays the \(h_{nmi_p}\) values by simulated non-invariance, strength of non-invariance, and type of equality constraint.
-This image represents 100 simulations of data by 1000 bootstrapped runs (averaged) to explore the expected pattern of results.
-The bars are arranged to show what a researcher might inspect when thinking about replication possibilities and their effect sizes (i.e., only three bars for each equality constraint would be calculated).
-
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/boot-rr-pic-1.pdf}
-\caption{\label{fig:boot-rr-pic}Visualization of the effect size of bootstrapped replication proportions on simulated data.
-Each panel indicates the simulated data type, colors represent the differences in the strength of the non-invariance, and the bars on the x-axis represent the effect size for the equality constraint.}
-\end{figure}
-
-In the data that was simulated to be invariant between groups, effect sizes are still non-zero (loadings \(h_{nmi_p}\) = 0.28, intercepts = \(h_{nmi_p}\) = 0.06, \(h_{nmi_p}\) = 0.00).
-This result mirrors the effects found in the literature - that often, many models fail to show invariance, and potentially not because measurement is poor but because of natural random variation in parameter estimates.
-This result also indicates the need to be able to identify if specific parameters are driving the differences, which is shown in the next section.
-
-Next, Figure \ref{fig:boot-rr-pic} demonstrates the patterns one might find for small, medium, and large effects at each type of invariance when data is simulated with \emph{one} difference.
-For loadings, the pattern shows a larger effect for loadings with zero or negative effect sizes for other effect sizes.
-The intercept simulations show non-zero effect sizes in the loadings and intercepts, likely for the same reasons \(d_{MACS}\) is interpreted as a combined effect size.
-When intercepts are changed, loadings may naturally shift with those means.
-Last, the residual results present an unexpected pattern, wherein the effect is primarily seen in the loadings, rather than the residuals step.
-However, when distributions of error variance are different, one may expect that those effects are pushed toward the loadings as well (as values can vary more, thus potentially weakening the relationship between observed and latent variable).
-
-An example of interpretation on real data is given in a later section.
-From a research study, only one effect size for each equality constraint would be calculated.
-The interpretation will often be up to the researcher's smallest effect of interest, and this simulation gives some guidance that the values should not be interpreted with traditional rules of thumb.
-The pattern of effects is potentially the most useful information: 1) positive effects on the loadings with negative or very close to zero effects on the other parameters may indicate a non-replication in loadings, 2) equal effects on loadings and intercepts with smaller or negative effects may indicate intercepts may be an issue, and 3) residuals may be determined by the same pattern as loadings but with a smaller ratio of loadings to residuals effect (i.e., loadings \(h_{nmi}\) / residuals \(h_{nmi}\).
-The ``size'' could be determined by the ratio of effect sizes for each constraint.
-Of course, this represents one simulation study, and results from many studies in a meta-analysis would be fruitful for future work.
-
-\hypertarget{replication-and-effect-size-parameters}{%
-\subsection{Replication and Effect Size: Parameters}\label{replication-and-effect-size-parameters}}
-
-\hypertarget{package-function-3}{%
-\subsubsection{Package Function}\label{package-function-3}}
+\newpage
+
+\subsection{\texorpdfstring{Parameter Replication and Effect Sizes: \texttt{bootstrap\_partial()} Function}{Parameter Replication and Effect Sizes: bootstrap\_partial() Function}}\label{parameter-replication-and-effect-sizes-bootstrap_partial-function-1}
 
@@
 \begin{verbatim}
-## # A tibble: 10 x 4
-## # Groups:   term, invariant [10]
-##    invariant term       d_boot d_random
-##    <lgl>     <chr>       <dbl>    <dbl>
-##  1 FALSE     lv =~ q1 -0.0299   0.0583 
-##  2 TRUE      lv =~ q1  0.0337   0.0116 
-##  3 FALSE     lv =~ q2 -0.0326   0.0933 
-##  4 TRUE      lv =~ q2  0.146    0.0309 
-##  5 FALSE     lv =~ q3 -0.0463   0.113  
-##  6 TRUE      lv =~ q3 -0.148    0.0743 
-##  7 FALSE     lv =~ q4  0.00785 -0.0668 
-##  8 TRUE      lv =~ q4 -0.0157   0.0389 
-##  9 FALSE     lv =~ q5 -0.00129 -0.169  
-## 10 TRUE      lv =~ q5  0.122   -0.00853
+##        term       d_boot     d_random
+## 1  lv =~ q1 -0.029853316  0.058271662
+## 2  lv =~ q1  0.033742666  0.011640524
+## 3  lv =~ q2 -0.032613505  0.093288563
+## 4  lv =~ q2  0.146200211  0.030925365
+## 5  lv =~ q3 -0.046329761  0.112823117
+## 6  lv =~ q3 -0.148330246  0.074265298
+## 7  lv =~ q4  0.007851687 -0.066844445
+## 8  lv =~ q4 -0.015702705  0.038884725
+## 9  lv =~ q5 -0.001285809 -0.169307690
+## 10 lv =~ q5  0.122405579 -0.008526218
 \end{verbatim}
@@
 \begin{verbatim}
-## # A tibble: 5 x 7
-##   term     non_invariant random_non_invariant h_nmi  h_mi h_nmi_p h_mi_p
-##   <chr>            <dbl>                <dbl> <dbl> <dbl>   <dbl>  <dbl>
-## 1 lv =~ q1         0.853                0.236  1.34 -1.34   0.427 -0.427
-## 2 lv =~ q2         0.858                0.237  1.35 -1.35   0.430 -0.430
-## 3 lv =~ q3         0.851                0.23   1.35 -1.35   0.429 -0.429
-## 4 lv =~ q4         0.84                 0.229  1.32 -1.32   0.420 -0.420
-## 5 lv =~ q5         0.819                0.237  1.25 -1.25   0.397 -0.397
+##       term non_invariant random_non_invariant    h_nmi      h_mi   h_nmi_p
+## 1 lv =~ q1         0.853                0.236 1.340078 -1.340078 0.4265601
+## 2 lv =~ q2         0.858                0.237 1.351946 -1.351946 0.4303378
+## 3 lv =~ q3         0.851                0.230 1.348639 -1.348639 0.4292851
+## 4 lv =~ q4         0.840                0.229 1.320578 -1.320578 0.4203530
+## 5 lv =~ q5         0.819                0.237 1.245789 -1.245789 0.3965468
+##       h_mi_p
+## 1 -0.4265601
+## 2 -0.4303378
+## 3 -0.4292851
+## 4 -0.4203530
+## 5 -0.3965468
 \end{verbatim}
@@
 \centering
-\includegraphics{manuscript_files/figure-latex/invariance-partial-fig-1.pdf}
-\caption{\label{fig:invariance-partial-fig}Visualization of the difference score between groups by parameter for invariant and non-invariant bootstrapped and randomly assigned group data.}
+\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/invariance-partial-fig-app-1.pdf}}
+\caption{\label{fig:invariance-partial-fig-app}Visualization of the difference score between groups by parameter for invariant and non-invariant bootstrapped and randomly assigned group data.}
 \end{figure}
@@
 \centering
-\includegraphics{manuscript_files/figure-latex/density-partial-fig-1.pdf}
-\caption{\label{fig:density-partial-fig}Visualization of the number of estimates for each group by bootstrapped and randomly assigned group runs by their invariance decision.}
+\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/density-partial-fig-app-1.pdf}}
+\caption{\label{fig:density-partial-fig-app}Visualization of the number of estimates for each group by bootstrapped and randomly assigned group runs by their invariance decision.}
 \end{figure}
@@
 \centering
-\includegraphics{manuscript_files/figure-latex/effect-partial-fig-1.pdf}
-\caption{\label{fig:effect-partial-fig}Visualization of effect size between groups by parameter for invariant and non-invariant bootstrapped and randomly assigned group data.
+\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/effect-partial-fig-app-1.pdf}}
+\caption{\label{fig:effect-partial-fig-app}Visualization of effect size between groups by parameter for invariant and non-invariant bootstrapped and randomly assigned group data.
 The size of the dots indicate the number of data points for that estimate.}
@@
 
-\hypertarget{simulated-results-2}{%
-\subsubsection{Simulated Results}\label{simulated-results-2}}
+\section{Simulation Study}\label{simulation-study}
+
+\subsection{Design and Analysis}\label{design-and-analysis}
+
+Data was simulated using the \texttt{simulateData} function in the \emph{R} package \emph{lavaan} (Rosseel, 2012) assuming multivariate normality using a \(\mu\) of 0 and \(\sigma\) of 1 for the data.
+This function allows you to write \emph{lavaan} syntax for your model with estimated values to generate data for observed variables (see supplemental for examples).
+The data included two groups of individuals (``Group 1'', ``Group 2'') for a multigroup confirmatory factor analysis (\(n_{group}\) = 250, \emph{N} = 500).
+The latent variables were assumed to be continuous normal (the package functions do not require this assumption).
+The model consisted of five observed items predicted by one latent variable (\texttt{lv\ =\textasciitilde{}\ q1\ +\ q2\ +\ q3\ +\ q4\ +\ q5}); however, the demonstration in this manuscript extends to multiple latent variables and other combinations of observed variables.
+Each item was assumed to be related to the latent variable with loadings approximately equal to .40 to .80, except when cases of non-invariance on the loadings was simulated.
+
+The Brown (2015) steps of testing measurement invariance are demonstrated in this manuscript for illustration purposes, but in line with Stark et al.
+(2006) suggestions, the visualizations show the impact of loadings and intercepts together.
+A convenience function \texttt{mgcfa} is used for these steps or other measurement invariance test orders and combinations.
+Fit indices for the steps for multigroup models are presented in the appendix for comparison of cutoff rules of thumb (Cheung \& Rensvold, 2002) to effect sizes and visualizations presented in this manuscript.
+Fit indices include Akaike Information Criterion (AIC, Akaike, 1998), Bayesian Information Criterion (BIC, Schwarz, 1978), Comparative Fit Index (CFI, Bentler, 1990), Tucker Lewis Index (TLI, Tucker \& Lewis, 1973), root mean squared error of approximation RMSEA (Steiger, 1990), and standardized root mean square residual (SRMR, Bentler, 1995).
+
+The data was then simulated to represent invariance across all model steps, small, medium, and large invariance using \(d_{MACS}\) estimated sizes from Nye et al.
+(2019).
+While \(d_{MACS}\) is used primarily for an effect size of the (non)-invariance for intercepts and loadings together, a similar approach was taken for the estimation of small, medium, and large effects on the residuals.
+The effect size is presented for all models, calculated from the \emph{dmacs} package (Dueber, 2023; Nye \& Drasgow, 2011).
+Only one item in each model was manipulated from the invariant model to create the non-invariant models.
+Given the data was simulated with a \emph{z}-score scaling, the loading values were simulated at .30 points apart (given \(d_{MACS}\) suggestions of .2, .4, .7), the intercepts at .25 points apart, and the residuals at .25 points apart.
+To plan a simulation for your own study, these values can be used to simulate small, medium, and large non-invariance effects by first converting data into \emph{z}-score.
+
+\subsection{Visualize Parameter Differences}\label{visualize-parameter-differences}
+
+The \(d_{MACS}\) value for item 4 in the invariant model was 0.16, representing a nil or unimportant difference in this manuscript.
+It is important to note that while Nye et al.
+(2019) suggests specific sizes for small, medium, and large, each researcher should determine for themselves what effects represent.
+Figure \ref{fig:small-load-pic} displays the results from the small (\(d_{MACS}\) = 0.27) difference in loadings, while Figure \ref{fig:med-load-pic} displays the results from the medium (\(d_{MACS}\) = 0.61) difference in loadings, and Figure \ref{fig:large-load-pic} shows the large (\(d_{MACS}\) = 0.66) differences.
+When investigating the slope values, we can clearly see the change in the loading for the second group (the only manipulated variable, although random data set generation may also change intercepts and residuals slightly).
+At the medium effect size, we see that the confidence bands do not overlap (at the edges), and at the large effect size, we can see a clear separation of two lines.
+Note that the intercepts in this model are estimated as equal so the loading representation will not literally separate, but the steepness of the lines is the indicator of the difference between the slopes.
+You can imagine these lines are interpreted like a simple slopes analysis for interactions in regression (Cohen et al., 2003).
+When simple slopes for interactions are plotted, if they are parallel, there is no interaction, and if they cross, then there is an interaction.
+Here, we can use this same logic.
+If they are parallel, there is likely invariance (they are the same), and the further from parallel they become, the larger the effect size for the differences between group loadings.
+
+The latent means in Figure \ref{fig:large-load-pic} do appear to show differences, albeit visually small.
+The latent means diagram shows the impact of any group differences that aren't constrained, and this image shows the configural model (as the metric model would force them to be equal).
+In the simulated model, the \emph{only} manipulated parameter is question 4's loading.
+In real models, the differences may be larger due to other variation found in the parameter estimates.
+Therefore, once you discover items you believe would make a model ``partially'' invariant, you may wish to estimate that model and graph the item again using the partially invariant model to see only the effect of the non-invariant items.
+Additionally, consider that we set the scaling of the model to 0.
+The estimate for the lv mean in the large loading model was group 1: 0.00, and group 2: -0.06, which results in 0.06 difference in group means.
+The practical implications of this difference will depend on the research and interpretations of the researcher.
+
+\begin{figure}
+\centering
+\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/small-load-pic-1.pdf}}
+\caption{\label{fig:small-load-pic}Small Loadings Model Visualization}
+\end{figure}
+
+\begin{figure}
+\centering
+\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/med-load-pic-1.pdf}}
+\caption{\label{fig:med-load-pic}Medium Loadings Model Visualization}
+\end{figure}
+
+\begin{figure}
+\centering
+\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/large-load-pic-1.pdf}}
+\caption{\label{fig:large-load-pic}Large Loadings Model Visualization}
+\end{figure}
+
+For intercepts, the small (Figure \ref{fig:small-int-pic}), medium (Figure \ref{fig:med-int-pic}), and large (Figure \ref{fig:large-int-pic}) depictions represent \(d_{MACS}\) values of 0.26, 0.47, and 0.70, respectively.
+Intercept differences can be clearly seen represented by the spacing out of the intercept locations (and thus, the overall line as well).
+While the changes in intercept do not appear to change the latent means, the caveat to this simulation is that only item four was manipulated.
+An example is provided below that demonstrates large changes in latent means.
+
+\begin{figure}
+\centering
+\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/small-int-pic-1.pdf}}
+\caption{\label{fig:small-int-pic}Small Intercepts Model Visualization}
+\end{figure}
+
+\begin{figure}
+\centering
+\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/med-int-pic-1.pdf}}
+\caption{\label{fig:med-int-pic}Medium Intercepts Model Visualization}
+\end{figure}
+
+\begin{figure}
+\centering
+\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/large-int-pic-1.pdf}}
+\caption{\label{fig:large-int-pic}Large Intercepts Model Visualization}
+\end{figure}
+
+Last, the effect of the residuals is plotted in small (Figure \ref{fig:small-res-pic}), medium (Figure \ref{fig:med-res-pic}), and large (Figure \ref{fig:large-res-pic}) formats.
+While \(d_{MACS}\) values are not technically available for the residuals, our models showed 0.19, 0.10, and 0.16, respectively.
+These differences in values are variable due to the random generation of data sets for each measurement invariance manipulation.
+At first glance, the differences in the small chart may seem large, because the black lines are not touching, but notice that the distributions overlap, indicating a likely small difference.
+The medium and large differences better illustrate differences in residuals across groups.
+Further, the impact of the residuals on the shape of the latent mean distribution can also been seen (and unintentionally, in the first figures as well due to random variation).
+The impact is due to the standard error of the residuals, as smaller standard errors represent lepokurtic distributions (taller), and larger standard errors represent platykurtic distributions (flatter).
+The effect size difference of the residuals does not appear to change the effects in the latent means.
+
+\begin{figure}
+\centering
+\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/small-res-pic-1.pdf}}
+\caption{\label{fig:small-res-pic}Small Residuals Model Visualization}
+\end{figure}
+
+\begin{figure}
+\centering
+\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/med-res-pic-1.pdf}}
+\caption{\label{fig:med-res-pic}Medium Residuals Model Visualization}
+\end{figure}
+
+\begin{figure}
+\centering
+\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/large-res-pic-1.pdf}}
+\caption{\label{fig:large-res-pic}Large Residuals Model Visualization}
+\end{figure}
+
+\subsection{Model Replication and Effect Size}\label{model-replication-and-effect-size}
+
+Figure \ref{fig:boot-rr-pic} portrays the \(h_{nmi_p}\) values by simulated non-invariance, strength of non-invariance, and type of equality constraint.
+This image represents 100 simulations of data by 1000 bootstrapped runs (averaged) to explore the expected pattern of results.
+The bars are arranged to show what a researcher might inspect when thinking about replication possibilities and their effect sizes (i.e., only three bars for each equality constraint would be calculated).
+
+\begin{figure}
+\centering
+\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/boot-rr-pic-1.pdf}}
+\caption{\label{fig:boot-rr-pic}Visualization of the effect size of bootstrapped replication proportions on simulated data.
+Each panel indicates the simulated data type, colors represent the differences in the strength of the non-invariance, and the bars on the x-axis represent the effect size for the equality constraint.}
+\end{figure}
+
+In the data that was simulated to be invariant between groups, effect sizes are still non-zero (loadings \(h_{nmi_p}\) = 0.28, intercepts = \(h_{nmi_p}\) = 0.06, \(h_{nmi_p}\) = 0.00).
+This result mirrors the effects found in the literature - that often, many models fail to show invariance, and potentially not because measurement is poor but because of natural random variation in parameter estimates.
+This result also indicates the need to be able to identify if specific parameters are driving the differences, which is shown in the next section.
+
+Next, Figure \ref{fig:boot-rr-pic} demonstrates the patterns one might find for small, medium, and large effects at each type of invariance when data is simulated with \emph{one} difference.
+For loadings, the pattern shows a larger effect for loadings with zero or negative effect sizes for other effect sizes.
+The intercept simulations show non-zero effect sizes in the loadings and intercepts, likely for the same reasons \(d_{MACS}\) is interpreted as a combined effect size.
+When intercepts are changed, loadings may naturally shift with those means.
+Last, the residual results present an unexpected pattern, wherein the effect is primarily seen in the loadings, rather than the residuals step.
+However, when distributions of error variance are different, one may expect that those effects are pushed toward the loadings as well (as values can vary more, thus potentially weakening the relationship between observed and latent variable).
+
+An example of interpretation on real data is given in a later section.
+From a research study, only one effect size for each equality constraint would be calculated.
+The interpretation will often be up to the researcher's smallest effect of interest, and this simulation gives some guidance that the values should not be interpreted with traditional rules of thumb.
+The pattern of effects is potentially the most useful information: 1) positive effects on the loadings with negative or very close to zero effects on the other parameters may indicate a non-replication in loadings, 2) equal effects on loadings and intercepts with smaller or negative effects may indicate intercepts may be an issue, and 3) residuals may be determined by the same pattern as loadings but with a smaller ratio of loadings to residuals effect (i.e., loadings \(h_{nmi}\) / residuals \(h_{nmi}\).
+The ``size'' could be determined by the ratio of effect sizes for each constraint.
+Of course, this represents one simulation study, and results from many studies in a meta-analysis would be fruitful for future work.
+
+\subsection{Parameter Replication and Effect Size}\label{parameter-replication-and-effect-size}
 
@@
 \centering
-\includegraphics{manuscript_files/figure-latex/effect-large-loading-pic-1.pdf}
+\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/effect-large-loading-pic-1.pdf}}
 \caption{\label{fig:effect-large-loading-pic}Bootstrapped and Random Group effect size differences in loadings for the Large Loading difference simulation.
@@
 \centering
-\includegraphics{manuscript_files/figure-latex/density-large-loading-pic-1.pdf}
+\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/density-large-loading-pic-1.pdf}}
 \caption{\label{fig:density-large-loading-pic}Bootstrapped and Random density plots for invariant and non-invariant bootstrapped partial effects examining only large loadings.}
@@
 
-\hypertarget{an-example-analysis}{%
-\subsection{An Example Analysis}\label{an-example-analysis}}
-
-Aiena et al.
-(2014) examined the RS-14 (Wagnild, 2009) exploring the factor structure of the Resiliency Scale in a clinical sample receiving treatment services and a college student sample.
-Measurement invariance was calculated for differences separately for these samples for gender and race finding a partially invariant models with a few item intercepts or residuals that differed between groups.
-Aiena et al.
-(2014) did not compare the clinical to the student sample for measurement invariance, and it is reasonable to expect potential differences in these two populations.
-This example will demonstrate the procedure for researchers who wish to use partial invariance steps and how to interpret real, messy data.
-
-\small
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{\# load the data, it is called DF}
-\FunctionTok{load}\NormalTok{(}\StringTok{"manu\_data/RS14.Rdata"}\NormalTok{)}
-
-\CommentTok{\# build the one{-}factor model }
-\NormalTok{model.rs }\OtherTok{\textless{}{-}} \StringTok{"RS =\textasciitilde{} RS1+RS2+RS3+RS4+RS5+RS6+RS7+RS8+RS9+RS10+RS11+RS12+RS13+RS14"}
-\CommentTok{\# run the multi{-}group CFA}
-\NormalTok{results.rs }\OtherTok{\textless{}{-}} \FunctionTok{mgcfa}\NormalTok{(}
-  \AttributeTok{model =}\NormalTok{ model.rs,}
-  \AttributeTok{data =}\NormalTok{ DF, }
-  \AttributeTok{group =} \StringTok{"sample"}\NormalTok{, }
-  \AttributeTok{group.equal =} \FunctionTok{c}\NormalTok{(}\StringTok{"loadings"}\NormalTok{, }\StringTok{"intercepts"}\NormalTok{, }\StringTok{"residuals"}\NormalTok{)}
-\NormalTok{  )}
-\end{Highlighting}
-\end{Shaded}
-
-\normalsize
-
-\small
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{\# how to get results in table }
-\NormalTok{results.rs}\SpecialCharTok{$}\NormalTok{model\_fit }\SpecialCharTok{\%\textgreater{}\%} 
-\NormalTok{        dplyr}\SpecialCharTok{::}\FunctionTok{select}\NormalTok{(model, AIC, BIC, cfi, tli, rmsea, srmr)}
-\end{Highlighting}
-\end{Shaded}
-
-\normalsize
-
-\begin{table}[tbp]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:rs-table}Model Fit for RS-14 Example}
-
-\begin{tabular}{lllllll}
-\toprule
-Model & AIC & BIC & CFI & TLI & RMSEA & SRMR\\
-\midrule
-Overall & 126,722.491 & 126,888.707 & 0.934 & 0.923 & 0.094 & 0.036\\
-Group Clinical & 52,961.421 & 53,099.720 & 0.919 & 0.904 & 0.090 & 0.044\\
-Group Student & 69,100.985 & 69,254.310 & 0.928 & 0.915 & 0.108 & 0.035\\
-Configural & 122,118.406 & 122,617.055 & 0.926 & 0.912 & 0.102 & 0.036\\
-Loadings & 122,144.532 & 122,566.010 & 0.925 & 0.918 & 0.098 & 0.043\\
-Intercepts & 122,544.109 & 122,888.415 & 0.911 & 0.910 & 0.103 & 0.052\\
-Residuals & 126,466.241 & 126,727.438 & 0.780 & 0.793 & 0.156 & 0.086\\
-\bottomrule
-\end{tabular}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-Table \ref{tab:rs-table} indicates the results after running the one-factor model.
-There are several guidelines for assessing assessing a degradation in model fit (Cao \& Liang, 2022; Cheung \& Rensvold, 2002; Counsell et al., 2020; Jin, 2020; Putnick \& Bornstein, 2016) but for the purposes of this illustration \(\Delta\)CFI \textgreater{} .01 will be used.
-Table \ref{tab:rs-table} indicates that fit was degraded when the constraint on equal item intercepts was added.
-The code below provides an example of testing each item individually by relaxing the constraints and recalculating the CFI.
-If these Items bring the CFI value back up to \(\Delta\)CFI \textless= .01 from the metric model, then the model would be considering partially invariant at the scalar level.
-It seems unlikely that the residuals will show invariance, if partial scalar invariance can be found, as the drop in fit is quite large.
-
-\small
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{partial.rs }\OtherTok{\textless{}{-}}
-  \FunctionTok{partial\_mi}\NormalTok{(}
-    \AttributeTok{saved\_model =}\NormalTok{ results.rs}\SpecialCharTok{$}\NormalTok{invariance\_models}\SpecialCharTok{$}\NormalTok{model.intercepts,}
-    \AttributeTok{data =}\NormalTok{ DF,}
-    \AttributeTok{model =}\NormalTok{ model.rs,}
-    \AttributeTok{group =} \StringTok{"sample"}\NormalTok{,}
-    \CommentTok{\# be sure to do only up to the step you are interested in}
-    \AttributeTok{group.equal =} \FunctionTok{c}\NormalTok{(}\StringTok{"loadings"}\NormalTok{, }\StringTok{"intercepts"}\NormalTok{),}
-    \AttributeTok{partial\_step =} \StringTok{"intercepts"}\NormalTok{)}
-
-\NormalTok{partial.rs}\SpecialCharTok{$}\NormalTok{fit\_table }\SpecialCharTok{\%\textgreater{}\%} 
-\NormalTok{  dplyr}\SpecialCharTok{::}\FunctionTok{select}\NormalTok{(free.parameter, cfi)}
-\end{Highlighting}
-\end{Shaded}
-
-\normalsize
-
-\begin{verbatim}
-## # A tibble: 15 x 2
-##    free.parameter cfi       
-##    <chr>          <lvn.vctr>
-##  1 "RS1 ~1 "      0.9116914 
-##  2 "RS2 ~1 "      0.9129976 
-##  3 "RS3 ~1 "      0.9117235 
-##  4 "RS4 ~1 "      0.9111212 
-##  5 "RS5 ~1 "      0.9126742 
-##  6 "RS6 ~1 "      0.9133618 
-##  7 "RS7 ~1 "      0.9139287 
-##  8 "RS8 ~1 "      0.9111397 
-##  9 "RS9 ~1 "      0.9119702 
-## 10 "RS10 ~1 "     0.9118309 
-## 11 "RS11 ~1 "     0.9110574 
-## 12 "RS12 ~1 "     0.9112309 
-## 13 "RS13 ~1 "     0.9112367 
-## 14 "RS14 ~1 "     0.9112015 
-## 15 "RS ~1 "       0.9108805
-\end{verbatim}
-
-The output indicates that RS6 and RS7 are potential items that could be relaxed to improve model fit and create a partial scalar invariant model (i.e., by picking the largest CFI values).
-The code below show to check the addition of these items, which are added one at a time.
-You use the \texttt{group.partial} open to ``relax'' or freely estimate that parameter for each group separately.
-
-\small
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{\# run the partially invariant model with group.partial}
-\NormalTok{partial.rs}\FloatTok{.1} \OtherTok{\textless{}{-}} \FunctionTok{mgcfa}\NormalTok{(}\AttributeTok{model =}\NormalTok{ model.rs, }
-                  \AttributeTok{data =}\NormalTok{ DF, }
-                  \AttributeTok{group =} \StringTok{"sample"}\NormalTok{, }
-                  \AttributeTok{group.equal =} \FunctionTok{c}\NormalTok{(}\StringTok{"loadings"}\NormalTok{, }\StringTok{"intercepts"}\NormalTok{),}
-                  \AttributeTok{group.partial =} \FunctionTok{c}\NormalTok{(}\StringTok{"RS7\textasciitilde{}1"}\NormalTok{),}
-                  \AttributeTok{meanstructure =} \ConstantTok{TRUE}\NormalTok{)}
-
-\CommentTok{\# examine the loadings }
-\NormalTok{partial.rs}\FloatTok{.1}\SpecialCharTok{$}\NormalTok{model\_coef }\SpecialCharTok{\%\textgreater{}\%} 
-  \FunctionTok{filter}\NormalTok{(term }\SpecialCharTok{==} \StringTok{"RS7 \textasciitilde{}1 "}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
-  \FunctionTok{filter}\NormalTok{(model }\SpecialCharTok{==} \StringTok{"intercepts"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
-\NormalTok{  dplyr}\SpecialCharTok{::}\FunctionTok{select}\NormalTok{(term, group, estimate, std.error)}
-\end{Highlighting}
-\end{Shaded}
-
-\normalsize
-
-\begin{verbatim}
-## # A tibble: 2 x 4
-##   term      group estimate std.error
-##   <chr>     <int>    <dbl>     <dbl>
-## 1 "RS7 ~1 "     1     4.95    0.0580
-## 2 "RS7 ~1 "     2     4.49    0.0529
-\end{verbatim}
-
-\small
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{\# examine the fit indices }
-\NormalTok{partial.rs}\FloatTok{.1}\SpecialCharTok{$}\NormalTok{model\_fit }\SpecialCharTok{\%\textgreater{}\%} 
-  \FunctionTok{filter}\NormalTok{(model }\SpecialCharTok{==} \StringTok{"intercepts"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
-\NormalTok{  dplyr}\SpecialCharTok{::}\FunctionTok{select}\NormalTok{(AIC, BIC, cfi, tli, rmsea, srmr)}
-\end{Highlighting}
-\end{Shaded}
-
-\normalsize
-
-\begin{verbatim}
-## # A tibble: 1 x 6
-##       AIC     BIC   cfi   tli rmsea   srmr
-##     <dbl>   <dbl> <dbl> <dbl> <dbl>  <dbl>
-## 1 122454. 122804. 0.914 0.912 0.102 0.0502
-\end{verbatim}
-
-\small
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{\# effect size model }
-\FunctionTok{lavaan\_dmacs}\NormalTok{(partial.rs}\FloatTok{.1}\SpecialCharTok{$}\NormalTok{invariance\_models}\SpecialCharTok{$}\NormalTok{model.intercepts, }\StringTok{"Clinical"}\NormalTok{)}\SpecialCharTok{$}\NormalTok{DMACS[}\DecValTok{7}\NormalTok{]}
-\end{Highlighting}
-\end{Shaded}
-
-\normalsize
-
-\begin{verbatim}
-##      RS7 
-## 0.282302
-\end{verbatim}
-
-By examining our estimates, we can see that item seven on the RS-14 is estimated at nearly 5 points for the clinical sample, while the student sample has a lower mean around 4.5 points.
-Generally, students show higher means on the items of the RS-14, but when all loadings and other intercepts are constrained to be equal, and this one item is relaxed, this pattern flips so that clinical groups show higher item intercepts.
-Given the scale is a 1-7 Likert type scale, .5 a point represents a potentially sizable change on the scale.
-Item seven covers perseverance after hardship, and all items can be found in the user manual for the scale at www.resiliencecenter.com.
-The effect size from \(d_{MACS}\) suggests a small to medium effect, 0.28.
-In this next code section, we repeat this process for the RS6, as the CFI for our model with only RS7 does not achieve the levels of partial invariance for our \(\Delta\)CFI criterion (i.e., \textless= .01 downward change in fit: metric CFI = .925, partial scalar CFI = .914).
-See Figure \ref{fig:rs7-img} for the difference between item intercepts and latent means.
-
-\small
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{\# add the second intercept}
-\NormalTok{partial.rs}\FloatTok{.2} \OtherTok{\textless{}{-}} \FunctionTok{mgcfa}\NormalTok{(}\AttributeTok{model =}\NormalTok{ model.rs, }
-                  \AttributeTok{data =}\NormalTok{ DF, }
-                  \AttributeTok{group =} \StringTok{"sample"}\NormalTok{, }
-                  \AttributeTok{group.equal =} \FunctionTok{c}\NormalTok{(}\StringTok{"loadings"}\NormalTok{, }\StringTok{"intercepts"}\NormalTok{),}
-                  \AttributeTok{group.partial =} \FunctionTok{c}\NormalTok{(}\StringTok{"RS7\textasciitilde{}1"}\NormalTok{, }\StringTok{"RS6\textasciitilde{}1"}\NormalTok{),}
-                  \AttributeTok{meanstructure =} \ConstantTok{TRUE}\NormalTok{)}
-
-\CommentTok{\# examine the loadings }
-\NormalTok{partial.rs}\FloatTok{.2}\SpecialCharTok{$}\NormalTok{model\_coef }\SpecialCharTok{\%\textgreater{}\%} 
-  \FunctionTok{filter}\NormalTok{(term }\SpecialCharTok{==} \StringTok{"RS6 \textasciitilde{}1 "}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
-  \FunctionTok{filter}\NormalTok{(model }\SpecialCharTok{==} \StringTok{"intercepts"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
-\NormalTok{  dplyr}\SpecialCharTok{::}\FunctionTok{select}\NormalTok{(term, group, estimate, std.error)}
-\end{Highlighting}
-\end{Shaded}
-
-\normalsize
-
-\begin{verbatim}
-## # A tibble: 2 x 4
-##   term      group estimate std.error
-##   <chr>     <int>    <dbl>     <dbl>
-## 1 "RS6 ~1 "     1     5.00    0.0605
-## 2 "RS6 ~1 "     2     4.54    0.0533
-\end{verbatim}
-
-\small
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{\# examine the fit indices }
-\NormalTok{partial.rs}\FloatTok{.2}\SpecialCharTok{$}\NormalTok{model\_fit }\SpecialCharTok{\%\textgreater{}\%} 
-  \FunctionTok{filter}\NormalTok{(model }\SpecialCharTok{==} \StringTok{"intercepts"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
-\NormalTok{  dplyr}\SpecialCharTok{::}\FunctionTok{select}\NormalTok{(AIC, BIC, cfi, tli, rmsea, srmr)}
-\end{Highlighting}
-\end{Shaded}
-
-\normalsize
-
-\begin{verbatim}
-## # A tibble: 1 x 6
-##       AIC     BIC   cfi   tli rmsea   srmr
-##     <dbl>   <dbl> <dbl> <dbl> <dbl>  <dbl>
-## 1 122363. 122719. 0.917 0.915 0.100 0.0488
-\end{verbatim}
-
-\small
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{\# effect size model }
-\FunctionTok{lavaan\_dmacs}\NormalTok{(partial.rs}\FloatTok{.2}\SpecialCharTok{$}\NormalTok{invariance\_models}\SpecialCharTok{$}\NormalTok{model.intercepts, }\StringTok{"Clinical"}\NormalTok{)}\SpecialCharTok{$}\NormalTok{DMACS[}\DecValTok{6}\NormalTok{]}
-\end{Highlighting}
-\end{Shaded}
-
-\normalsize
-
-\begin{verbatim}
-##       RS6 
-## 0.2796334
-\end{verbatim}
-
-Again, we see about a half-point difference between our clinical and student samples for item 6, which is about drive to achieve.
-The CFI for this model does meet the requirements for partial invariance, .917.
-The effect size is approximately the same at \(d_{MACS}\) = 0.28.
-See Figure \ref{fig:rs6-img} shows the difference between item intercepts and latent means.
-
-\normalsize
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{\# plot the image for RS7}
-\FunctionTok{plot\_mi}\NormalTok{(}
-  \AttributeTok{data\_coef =}\NormalTok{ partial.rs}\FloatTok{.2}\SpecialCharTok{$}\NormalTok{model\_coef, }
-  \AttributeTok{model\_step =} \StringTok{"intercepts"}\NormalTok{, }
-  \AttributeTok{item\_name =} \StringTok{"RS7"}\NormalTok{, }
-  \AttributeTok{x\_limits =} \FunctionTok{c}\NormalTok{(}\SpecialCharTok{{-}}\DecValTok{1}\NormalTok{,}\DecValTok{1}\NormalTok{),}
-  \AttributeTok{y\_limits =} \FunctionTok{c}\NormalTok{(}\FunctionTok{min}\NormalTok{(DF}\SpecialCharTok{$}\NormalTok{RS7), }\FunctionTok{max}\NormalTok{(DF}\SpecialCharTok{$}\NormalTok{RS7)),}
-  \AttributeTok{conf.level =}\NormalTok{ .}\DecValTok{95}\NormalTok{, }
-  \AttributeTok{model\_results =}\NormalTok{ partial.rs}\FloatTok{.2}\SpecialCharTok{$}\NormalTok{invariance\_models}\SpecialCharTok{$}\NormalTok{model.intercepts,}
-  \CommentTok{\# which latent variable do you want }
-  \AttributeTok{lv\_name =} \StringTok{"RS"} 
-\NormalTok{)}\SpecialCharTok{$}\NormalTok{complete}
-\end{Highlighting}
-\end{Shaded}
-
-\normalsize
-
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/rs7-img-1.pdf}
-\caption{\label{fig:rs7-img}RS7 Item Invariance Visualization}
-\end{figure}
-
-\normalsize
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{\# plot the image for RS6}
-\FunctionTok{plot\_mi}\NormalTok{(}
-  \AttributeTok{data\_coef =}\NormalTok{ partial.rs}\FloatTok{.2}\SpecialCharTok{$}\NormalTok{model\_coef, }
-  \AttributeTok{model\_step =} \StringTok{"intercepts"}\NormalTok{, }
-  \AttributeTok{item\_name =} \StringTok{"RS6"}\NormalTok{, }
-  \AttributeTok{x\_limits =} \FunctionTok{c}\NormalTok{(}\SpecialCharTok{{-}}\DecValTok{1}\NormalTok{,}\DecValTok{1}\NormalTok{),}
-  \AttributeTok{y\_limits =} \FunctionTok{c}\NormalTok{(}\FunctionTok{min}\NormalTok{(DF}\SpecialCharTok{$}\NormalTok{RS6), }\FunctionTok{max}\NormalTok{(DF}\SpecialCharTok{$}\NormalTok{RS6)),}
-  \AttributeTok{conf.level =}\NormalTok{ .}\DecValTok{95}\NormalTok{, }
-  \AttributeTok{model\_results =}\NormalTok{ partial.rs}\FloatTok{.2}\SpecialCharTok{$}\NormalTok{invariance\_models}\SpecialCharTok{$}\NormalTok{model.intercepts,}
-  \CommentTok{\# which latent variable do you want }
-  \AttributeTok{lv\_name =} \StringTok{"RS"} 
-\NormalTok{)}\SpecialCharTok{$}\NormalTok{complete}
-\end{Highlighting}
-\end{Shaded}
-
-\normalsize
-
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/rs6-img-1.pdf}
-\caption{\label{fig:rs6-img}RS6 Item Invariance Visualization}
-\end{figure}
-
-Next, we would examine our replication potential for this model.
-Given our current results, we may not expect our intercepts to replicate.
-Given the order of \texttt{group.equal}, the boot function will select the first non-invariant step in the calculation of the effect size for potential replication.
-In our output, we do not see a loadings effect size, and this result occurs when \emph{none} of the bootstrapped or random results are non-invariant.
-Therefore, we would expect the loadings to replicate (and the effect size would be 0 difference between bootstrapped and random, both showing invariance).
-The intercepts show a large (i.e., close to the max possible value) non-invariant effect, and therefore, we should not expect this model to show invariance in a replication.
-
-\normalsize
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{boot.model.rs }\OtherTok{\textless{}{-}} 
-  \FunctionTok{bootstrap\_model}\NormalTok{(}
-    \AttributeTok{saved\_configural =}\NormalTok{ results.rs}\SpecialCharTok{$}\NormalTok{model\_configural,}
-    \AttributeTok{data =}\NormalTok{ DF,}
-    \AttributeTok{model =}\NormalTok{ model.rs, }
-    \AttributeTok{group =} \StringTok{"sample"}\NormalTok{, }
-    \AttributeTok{nboot =} \DecValTok{1000}\NormalTok{, }
-    \AttributeTok{invariance\_index =} \StringTok{"cfi"}\NormalTok{,}
-    \AttributeTok{invariance\_rule =}\NormalTok{ .}\DecValTok{01}\NormalTok{, }
-    \AttributeTok{group.equal =} \FunctionTok{c}\NormalTok{(}\StringTok{"loadings"}\NormalTok{, }\StringTok{"intercepts"}\NormalTok{, }\StringTok{"residuals"}\NormalTok{)}
-\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\normalsize
-
-\normalsize
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{boot.model.rs}
-\end{Highlighting}
-\end{Shaded}
-
-\normalsize
-
-\begin{verbatim}
-## # A tibble: 2 x 7
-##   model      non_invariant random_non_invariant  h_nmi    h_mi h_nmi_p  h_mi_p
-##   <chr>              <dbl>                <dbl>  <dbl>   <dbl>   <dbl>   <dbl>
-## 1 intercepts         0.998                    0 3.05   -3.05    0.972  -0.972 
-## 2 residuals          0.002                    0 0.0895 -0.0895  0.0285 -0.0285
-\end{verbatim}
-
-Next, we would examine the strength of the effects of replication on each parameter at the intercept level.
-By examining Table \ref{tab:table-boot-effects}, it is clear that most of the item means are unlikely to replicate, even though two particular items can be used to create partial invariance.
-Figures \ref{fig:rs-partial-pic} and \ref{fig:rs-partial-pic2} display the three plots provided in the \texttt{bootstrap\_partial()} function.
-In general, we should expect \(M_{D}\) = 0.11 when items are invariant and \(M_{D}\) = 0.25 when items are not invariant.
-The effect size of non-invariant items ranges from 0.43 to 0.59.
-
-The density plot shown at the bottom of Figure \ref{fig:rs-partial-pic} illustrates the likely reasons for the differences found in the top plots.
-It appears that many items show a bimodal distribution within group 1 (Clinical Sample) and when items are invariant, the intercept averages to the same intercept as group 2 (Student Sample).
-In non-invariant estimates, the same bimodal distributions are found, but they are more extreme than the student samples, and therefore, item show different averages due to the presence of two separate means of data.
-Further, some items also appear to show two separate student item averages within the data.
-This result suggests that it would be fruitful to understand a potential predictor of these differences or other confounding variable that separates these samples, creating differences in item averages.
-
-In summary, if one were planning a replication, the prediction would be that item intercepts would likely not replicate, with a large effect size (i.e., it is easy to judge \(h_{nmi_p}\) close to the max of one as large).
-While this study found partial invariance by relaxing constraints on two individual items, bootstrapped partial invariance indicates that any item could potentially be problematic with an effect size averaging \(d\) \textasciitilde{} 0.50 difference in means.
-While \(d_{MACS}\) values represented a ``small'' effect based on previous publications, this effect may be muted by examining both loadings and intercepts.
-The results here suggest that the effect is driven by intercepts.
-The overall average score on items is high: \(M_M\) = 5.04 (\(M_{SD}\) = 1.72).
-Given the mean standard deviation, a \(d\) \textasciitilde{} 0.50 represents 0.86 or nearly one whole point on the scale.
-A researcher could decide that at least \(d\) = 0.33 or at least a third of a standard deviation would be an important change and set that as their smallest effect size of interest for invariance.
-Further, a newly planned study should investigate what variables may predict when and why samples separate into bimodal representations for item means.
-
-\normalsize
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{boot.partial.rs }\OtherTok{\textless{}{-}} 
-  \FunctionTok{bootstrap\_partial}\NormalTok{(}
-    \AttributeTok{saved\_model =}\NormalTok{ results.rs}\SpecialCharTok{$}\NormalTok{invariance\_models}\SpecialCharTok{$}\NormalTok{model.intercepts,}
-    \AttributeTok{data =}\NormalTok{ DF,}
-    \AttributeTok{model =}\NormalTok{ model.rs, }
-    \AttributeTok{group =} \StringTok{"sample"}\NormalTok{, }
-    \AttributeTok{nboot =} \DecValTok{1000}\NormalTok{, }
-    \AttributeTok{invariance\_index =} \StringTok{"cfi"}\NormalTok{,}
-    \AttributeTok{invariance\_rule =}\NormalTok{ .}\DecValTok{01}\NormalTok{, }
-    \AttributeTok{invariance\_compare =} \FunctionTok{fitmeasures}\NormalTok{(results.rs}\SpecialCharTok{$}\NormalTok{invariance\_models}\SpecialCharTok{$}\NormalTok{model.loadings, }\StringTok{"cfi"}\NormalTok{), }
-    \AttributeTok{partial\_step =} \StringTok{"intercepts"}\NormalTok{,}
-    \AttributeTok{group.equal =} \FunctionTok{c}\NormalTok{(}\StringTok{"loadings"}\NormalTok{, }\StringTok{"intercepts"}\NormalTok{)}
-\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\normalsize
-
-\begin{table}[tbp]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:table-boot-effects}Boot Partial Effects Results for RS-14 Intercepts}
-
-\begin{tabular}{lllll}
-\toprule
-Term & Non-Invariant & Random Non-Invariant & $h_{nmi}$ & $h_{nmi_p}$\\
-\midrule
-RS  Intercept & 0.991 & 0.007 & 2.784 & 0.886\\
-RS1  Intercept & 0.989 & 0.007 & 2.764 & 0.880\\
-RS10  Intercept & 0.988 & 0.007 & 2.755 & 0.877\\
-RS11  Intercept & 0.991 & 0.007 & 2.784 & 0.886\\
-RS12  Intercept & 0.991 & 0.007 & 2.784 & 0.886\\
-RS13  Intercept & 0.991 & 0.007 & 2.784 & 0.886\\
-RS14  Intercept & 0.990 & 0.007 & 2.774 & 0.883\\
-RS2  Intercept & 0.985 & 0.007 & 2.728 & 0.869\\
-RS3  Intercept & 0.988 & 0.007 & 2.755 & 0.877\\
-RS4  Intercept & 0.990 & 0.007 & 2.774 & 0.883\\
-RS5  Intercept & 0.984 & 0.007 & 2.720 & 0.866\\
-RS6  Intercept & 0.979 & 0.007 & 2.683 & 0.854\\
-RS7  Intercept & 0.974 & 0.007 & 2.650 & 0.844\\
-RS8  Intercept & 0.991 & 0.007 & 2.784 & 0.886\\
-RS9  Intercept & 0.987 & 0.007 & 2.746 & 0.874\\
-\bottomrule
-\end{tabular}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/rs-partial-pic-1.pdf}
-\caption{\label{fig:rs-partial-pic}RS-14 scale invariance for item intercepts.
-The left panel indicates the raw score difference between groups and items, while the right panel indicates the effect size for group differences based on invariance.}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/rs-partial-pic2-1.pdf}
-\caption{\label{fig:rs-partial-pic2}RS-14 scale invariance density plots, illustrating invariant versus non-invariant bootstrapped and random runs for each parameter.}
-\end{figure}
-
-\hypertarget{an-example-extension}{%
-\subsection{An Example Extension}\label{an-example-extension}}
-
-One benefit of the open science movement on scale development is the publication of datasets or covariance tables with published articles.
-We can extend our examination of potential replication on other variables that may effect assessment of underlying phenomena.
-For example, scale translation across languages is not only impacted by the literal conversion of concepts from one language to another, but also the cultural and societal norms of the target population (Cha et al., 2007; Chang et al., 1999; Yu et al., 2004).
-The RS14 was tested in Chinese speaking samples in Chen et al.
-(2020) across five different large samples and determined that the scale showed good psychometric properties for use within Chinese speaking samples as a one-factor model of resiliency.
-Given these results, another researcher may assume that the models would be comparable between English speaking (i.e., likely United States) and Chinese speaking samples.
-With the published data, we can use \texttt{visualizemi} to determine if the RS14 is invariant across language/culture, and if the results would likely replicate if tested on a new set of samples, and what, if any, effect size differences are found in parameters.
-The code used for this analysis is presented in Appendix 7.
-
-The Aiena et al.
-(2014) data used in our previous example was first filtered to only college students, as we have already noted that clinical samples show slightly different intercepts for at least two of the items from student samples.
-The Chen et al.
-(2020) data also included college students, which allows us to test a comparable sample that varies on translation and culture.
-The test of measurement invariance indicated that the factor structure and loadings were invariant across groups.
-Much like our test of clinical versus student samples, the results indicated that the intercepts were not consistent across groups.
-Within the English clinical/student sample, partial invariance could be achieved by relaxing two item intercept constraints (item 6 and 7).
-To achieve ``partial'' invariance between the Chinese and English speaking samples, we would need to relax more than half of the items (specifically, eight items: 1, 2, 3, 4, 10, 11, 12, 14), and it would be difficult to suggest partial invariance given this finding.
-\(d_{MACS}\) values range from 0.26 to 0.32 for the eight items which could be interpreted a small to medium given Nye et al.
-(2019)'s simulation study.
-Figure \ref{fig:rs14-chinese-pic} portrays the results from the second item on the RS14 (\emph{life accomplishments}).
-
-The results of model bootstrapping indicated that the effect of the loadings was likely to replicate (only invariant results were found), but the intercepts were never found to be invariant compared to a randomized sample (\(h_{nmi_p}\) = 1).
-Therefore, we would expect that these differences are persistent, either due to the adaptation or cultural differences in resiliency across samples.
-The bootstrapped partial invariance demonstrates that each item intercept has a medium to large difference between the two samples as shown in Figure \ref{fig:rs14-chinese-effect-pic}, which may explain why full or partial invariance cannot be achieved.
-This result does not invalidate either version of the scale, but informs researchers of potential baseline differences in item responding for the two samples.
-Therefore, careful interpretation should be made when comparing these two samples in other instances, as differences in latent means may be the default finding, but with these results one may determine if their results are different from expectations of general scale responding.
-
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/rs14-chinese-pic-1.pdf}
-\caption{\label{fig:rs14-chinese-pic}The differences in intercepts for the second item on the RS14 by language sample.
-The differences between intercepts are shown on the left-hand side with a clear separation between lines.
-The latent means also show a clear difference between groups where the English group appears to have lower scores overall than the Chinese group.}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/rs14-chinese-effect-pic-1.pdf}
-\caption{\label{fig:rs14-chinese-effect-pic}Effect size differences for item intercepts on the English versus Chinese samples for the RS14.}
-\end{figure}
-
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
-
-In this tutorial, we examined how to use multiple tools to examine measurement invariance and its potential replication.
-Model fit comparisons and statistics can be paired with the proposed effect size measures, and a visualization to examine individual items and the overall latent mean scores.
-The impact of potential replication was estimated on the overall model and the individual parameters.
-Using real data, the effect of two non-invariant item intercepts was examined and visualized.
-This tutorial manuscript has provided a concrete way to plan for pre-registration and/or registered reports.
-Researchers could simulate results based on published or previously collected data to determine the likelihood and size of potential replication.
-They could plan and pre-register a smallest effect of interest.
-For example, we may determine that an \(h_{nmi_p}\) value above .20 represents an important level of non-invariance for our model overall, while \(h_{nmi_p}\) \textgreater{} .30 for any individual parameter warrant caution against invariance for groups.
-Others have begun to discuss the importance of focusing on effects in the scale of the data and their practical importance (Anvari \& Lakens, 2021; Cumming, 2012).
-
-From the example, our interpretation may be that the difference between group's latent means is large, as a 0.72 change on a 7 point scale is approximately 10\% more resiliency for students when compared to the clinical sample.
-Practically, 10\% in resiliency for an area of the United States (Mississippi) often hit with natural disasters (hurricanes, tornadoes, floods) and high levels of poverty would be very important.
-Even the smaller difference of .5 point on each individual item could translate into increases in resiliency, and these results may elucidate avenues for further exploration into areas of focus within resiliency, given the items.
-The secondary example showed that we can extend these results to other samples to examine other potentially impactful variables on assessment.
-The findings replicate in the sense that the scale shows the same invariant issues with intercepts on a Chinese versus English sample comparison.
-However, in this analysis, it is clear that the differences in items averages are much larger and across all items, rather than a few.
-
-What do the results of a study on measurement invariance with these results tell us about replication, generalizability, and validity overall?
-If a researcher decides their effects are large, they should likely caution against suggesting that these scores are directly comparable without weighting or other adjustment.
-Let's consider a scenario wherein the change metric between models picked (i.e., \(\Delta\)CFI, \(\Delta\)RMSEA) indicates a ``significant'' change in model fit.
-However, if both the effect size and a visual inspection of the invariance indicates a small difference, we may decide to lessen the practical importance of those results, much like ``just significant'' \emph{p}-values with small effect sizes are treated now.
-The results from our Chinese versus English comparison show us the other scenario: non-invariant results that clearly indicate differences with a large effect size on both replication and item average differences.
-Given that the goal of measurement invariance is to compare \emph{estimates}, we should expect some differences across samples due to the nature of sampling and estimation.
-It may be that many of the published models presented represent these effects - small variations between groups due to sampling error or other small crud - but do not represent a fundamental problem with the measurement or generalizability of the results.
-The \texttt{visualizemi} package is one useful tool to help sort out if findings are this small sampling error or differences in samples due to other variables.
-
-\newpage
-
-\hypertarget{references}{%
-\section{References}\label{references}}
-
-\hypertarget{refs}{}
-\begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-aiena2014}{}}%
-Aiena, B.
-J., Baczwaski, B.
-J., Schulenberg, S.
-E., \& Buchanan, E.
-M.
-(2014).
-Measuring Resilience With the RS{\textendash}14: A Tale of Two Samples.
-\emph{Journal of Personality Assessment}, \emph{97}(3), 291--300.
-\url{https://doi.org/10.1080/00223891.2014.951445}
-
-\leavevmode\vadjust pre{\hypertarget{ref-akaike1998}{}}%
-Akaike, H.
-(1998).
-\emph{Information theory and an extension of the maximum likelihood principle} (E.
-Parzen, K.
-Tanabe, \& G.
-Kitagawa, Eds.; pp.
-199--213).
-Springer New York.
-\url{http://link.springer.com/10.1007/978-1-4612-1694-0_15}
-
-\leavevmode\vadjust pre{\hypertarget{ref-anvari2021}{}}%
-Anvari, F., \& Lakens, D.
-(2021).
-Using anchor-based methods to determine the smallest effect size of interest.
-\emph{Journal of Experimental Social Psychology}, \emph{96}, 104159.
-\url{https://doi.org/10.1016/j.jesp.2021.104159}
-
-\leavevmode\vadjust pre{\hypertarget{ref-barry2014}{}}%
-Barry, A.
-E., Chaney, B., Piazza-Gardner, A.
-K., \& Chavarria, E.
-A.
-(2014).
-Validity and Reliability Reporting Practices in the Field of Health Education and Behavior: A Review of Seven Journals.
-\emph{Health Education \& Behavior}, \emph{41}(1), 12--18.
-\url{https://doi.org/10.1177/1090198113483139}
-
-\leavevmode\vadjust pre{\hypertarget{ref-beaujean2014}{}}%
-Beaujean, A. A. (2014). \emph{Latent variable modeling using r: A step by step guide}. Routledge/Taylor \& Francis Group.
-
-\leavevmode\vadjust pre{\hypertarget{ref-bentler1990}{}}%
-Bentler, P. M. (1990). Comparative fit indexes in structural models. \emph{Psychological Bulletin}, \emph{107}(2), 238--246. \url{https://doi.org/10.1037/0033-2909.107.2.238}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bentler1995}{}}%
-Bentler, P. M. (1995). \emph{EQS structural equations program manual}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-boker2011}{}}%
-Boker, S., Neale, M., Maes, H., Wilde, M., Spiegel, M., Brick, T., Spies, J., Estabrook, R., Kenny, S., Bates, T., Mehta, P., \& Fox, J.
-(2011).
-OpenMx: An Open Source Extended Structural Equation Modeling Framework.
-\emph{Psychometrika}, \emph{76}(2), 306--317.
-\url{https://doi.org/10.1007/s11336-010-9200-6}
-
-\leavevmode\vadjust pre{\hypertarget{ref-brown2015}{}}%
-Brown, T. A. (2015). \emph{Confirmatory factor analysis for applied research} (Second edition). The Guilford Press.
-
-\leavevmode\vadjust pre{\hypertarget{ref-byrne1989}{}}%
-Byrne, B.
-M., Shavelson, R.
-J., \& Muthén, B.
-(1989).
-Testing for the equivalence of factor covariance and mean structures: The issue of partial measurement invariance.
-\emph{Psychological Bulletin}, \emph{105}(3), 456--466.
-\url{https://doi.org/10.1037/0033-2909.105.3.456}
-
-\leavevmode\vadjust pre{\hypertarget{ref-cao2022}{}}%
-Cao, C., \& Liang, X.
-(2022).
-The impact of model size on the sensitivity of fit measures in measurement invariance testing.
-\emph{Structural Equation Modeling: A Multidisciplinary Journal}, \emph{29}(5), 744--754.
-\url{https://doi.org/10.1080/10705511.2022.2056893}
-
-\leavevmode\vadjust pre{\hypertarget{ref-cha2007}{}}%
-Cha, E.-S., Kim, K.
-H., \& Erlen, J.
-A.
-(2007).
-Translation of scales in cross{-}cultural research: issues and techniques.
-\emph{Journal of Advanced Nursing}, \emph{58}(4), 386--395.
-\url{https://doi.org/10.1111/j.1365-2648.2007.04242.x}
-
-\leavevmode\vadjust pre{\hypertarget{ref-chang1999}{}}%
-Chang, A.
-M., Chau, J.
-P.
-C., \& Holroyd, E.
-(1999).
-Translation of questionnaires and issues of equivalence.
-\emph{Journal of Advanced Nursing}, \emph{29}(2), 316--322.
-\url{https://doi.org/10.1046/j.1365-2648.1999.00891.x}
-
-\leavevmode\vadjust pre{\hypertarget{ref-chen2020}{}}%
-Chen, W., Xie, E., Tian, X., \& Zhang, G.
-(2020).
-Psychometric properties of the Chinese version of the Resilience Scale (RS-14): Preliminary results.
-\emph{PLOS ONE}, \emph{15}(10), e0241606.
-\url{https://doi.org/10.1371/journal.pone.0241606}
-
-\leavevmode\vadjust pre{\hypertarget{ref-cheung2002}{}}%
-Cheung, G.
-W., \& Rensvold, R.
-B.
-(2002).
-Evaluating Goodness-of-Fit Indexes for Testing Measurement Invariance.
-\emph{Structural Equation Modeling: A Multidisciplinary Journal}, \emph{9}(2), 233--255.
-\url{https://doi.org/10.1207/s15328007sem0902_5}
-
-\leavevmode\vadjust pre{\hypertarget{ref-chorpita2000}{}}%
-Chorpita, B.
-F., Yim, L., Moffitt, C., Umemoto, L.
-A., \& Francis, S.
-E.
-(2000).
-Assessment of symptoms of DSM-IV anxiety and depression in children: a revised child anxiety and depression scale.
-\emph{Behaviour Research and Therapy}, \emph{38}(8), 835--855.
-\url{https://doi.org/10.1016/S0005-7967(99)00130-8}
-
-\leavevmode\vadjust pre{\hypertarget{ref-cohen2003}{}}%
-Cohen, J., Cohen, P., West, S. G., \& Aiken, L. (2003). \emph{Applied multiple regression / correlation analysis for the behavioral sciences} (3rd ed.). Lawrence Erlbaum Associates.
-
-\leavevmode\vadjust pre{\hypertarget{ref-counsell2020}{}}%
-Counsell, A., Cribbie, R.
-A., \& Flora, D.
-B.
-(2020).
-Evaluating equivalence testing methods for measurement invariance.
-\emph{Multivariate Behavioral Research}, \emph{55}(2), 312--328.
-\url{https://doi.org/10.1080/00273171.2019.1633617}
-
-\leavevmode\vadjust pre{\hypertarget{ref-cumming2012}{}}%
-Cumming, G. (2012). \emph{Understanding the new statistics: Effect sizes, confidence intervals, and meta-analysis}. Routledge.
-
-\leavevmode\vadjust pre{\hypertarget{ref-devellis2022}{}}%
-DeVellis, R. F., \& Thorpe, C. T. (2022). \emph{Scale development: Theory and applications} (Fifth edition). SAGE Publications, Inc.
-
-\leavevmode\vadjust pre{\hypertarget{ref-dueber2023}{}}%
-Dueber, D. (2023). \emph{Dmacs}. \url{https://github.com/ddueber/dmacs}
-
-\leavevmode\vadjust pre{\hypertarget{ref-epskamp2022}{}}%
-Epskamp, S. (2022). \emph{semPlot: Path diagrams and visual analysis of various SEM packages' output}. \url{https://CRAN.R-project.org/package=semPlot}
-
-\leavevmode\vadjust pre{\hypertarget{ref-flake2020}{}}%
-Flake, J.
-K., \& Fried, E.
-I.
-(2020).
-Measurement Schmeasurement: Questionable Measurement Practices and How to Avoid Them.
-\emph{Advances in Methods and Practices in Psychological Science}, \emph{3}(4), 456--465.
-\url{https://doi.org/10.1177/2515245920952393}
-
-\leavevmode\vadjust pre{\hypertarget{ref-hobson2019}{}}%
-Hobson, H. (2019). Registered reports are an ally to early career researchers. \emph{Nature Human Behaviour}, \emph{3}(10), 1010--1010. \url{https://doi.org/10.1038/s41562-019-0701-8}
-
-\leavevmode\vadjust pre{\hypertarget{ref-jin2020}{}}%
-Jin, Y.
-(2020).
-A note on the cutoff values of alternative fit indices to evaluate measurement invariance for ESEM models.
-\emph{International Journal of Behavioral Development}, \emph{44}(2), 166--174.
-\url{https://doi.org/10.1177/0165025419866911}
-
-\leavevmode\vadjust pre{\hypertarget{ref-juxf6reskog1971}{}}%
-Jöreskog, K. G. (1971). Simultaneous factor analysis in several populations. \emph{Psychometrika}, \emph{36}(4), 409--426. \url{https://doi.org/10.1007/BF02291366}
-
-\leavevmode\vadjust pre{\hypertarget{ref-juxf6reskog2001}{}}%
-Jöreskog, K. G., \& Sörbom, D. (2001). \emph{LISREL 8: user's reference guide} (2. ed., updated to LISREL 8). SSI Scientific Software Internat.
-
-\leavevmode\vadjust pre{\hypertarget{ref-lakens2017}{}}%
-Lakens, D. (2017). Equivalence Tests. \emph{Social Psychological and Personality Science}, \emph{8}(4), 355--362. \url{https://doi.org/10.1177/1948550617697177}
-
-\leavevmode\vadjust pre{\hypertarget{ref-makel2014}{}}%
-Makel, M.
-C., \& Plucker, J.
-A.
-(2014).
-Facts Are More Important Than Novelty: Replication in the Education Sciences.
-\emph{Educational Researcher}, \emph{43}(6), 304--316.
-\url{https://doi.org/10.3102/0013189X14545513}
-
-\leavevmode\vadjust pre{\hypertarget{ref-makel2012}{}}%
-Makel, M.
-C., Plucker, J.
-A., \& Hegarty, B.
-(2012).
-Replications in Psychology Research: How Often Do They Really Occur?
-\emph{Perspectives on Psychological Science}, \emph{7}(6), 537--542.
-\url{https://doi.org/10.1177/1745691612460688}
-
-\leavevmode\vadjust pre{\hypertarget{ref-marsh2004}{}}%
-Marsh, H.
-W., Hau, K.-T., \& Wen, Z.
-(2004).
-In search of golden rules: Comment on hypothesis-testing approaches to setting cutoff values for fit indexes and dangers in overgeneralizing hu and bentler's (1999) findings.
-\emph{Structural Equation Modeling: A Multidisciplinary Journal}, \emph{11}(3), 320--341.
-\url{https://doi.org/10.1207/s15328007sem1103_2}
-
-\leavevmode\vadjust pre{\hypertarget{ref-mayo-wilson2021}{}}%
-Mayo-Wilson, E., Grant, S., Supplee, L., Kianersi, S., Amin, A., DeHaven, A., \& Mellor, D.
-(2021).
-Evaluating implementation of the transparency and openness promotion~(TOP) guidelines:~The TRUST process for rating journal policies, procedures, and practices.
-\emph{Research Integrity and Peer Review}, \emph{6}(1), 9.
-\url{https://doi.org/10.1186/s41073-021-00112-8}
-
-\leavevmode\vadjust pre{\hypertarget{ref-meredith1993}{}}%
-Meredith, W. (1993). Measurement invariance, factor analysis and factorial invariance. \emph{Psychometrika}, \emph{58}(4), 525--543. \url{https://doi.org/10.1007/BF02294825}
-
-\leavevmode\vadjust pre{\hypertarget{ref-nelson2018}{}}%
-Nelson, L. D., Simmons, J., \& Simonsohn, U. (2018). Psychology's renaissance. \emph{Annual Review of Psychology}, \emph{69}(1), 511--534. \url{https://doi.org/10.1146/annurev-psych-122216-011836}
-
-\leavevmode\vadjust pre{\hypertarget{ref-nosek2018}{}}%
-Nosek, B.
-A., Ebersole, C.
-R., DeHaven, A.
-C., \& Mellor, D.
-T.
-(2018).
-The preregistration revolution.
-\emph{Proceedings of the National Academy of Sciences of the United States of America}, \emph{115}(11), 2600--2606.
-\url{https://doi.org/10.1073/pnas.1708274114}
-
-\leavevmode\vadjust pre{\hypertarget{ref-nosek2014}{}}%
-Nosek, B.
-A., \& Lakens, D.
-(2014).
-Registered Reports: A Method to Increase the Credibility of Published Results.
-\emph{Social Psychology}, \emph{45}(3), 137--141.
-\url{https://doi.org/10.1027/1864-9335/a000192}
-
-\leavevmode\vadjust pre{\hypertarget{ref-nye2019}{}}%
-Nye, C.
-D., Bradburn, J., Olenick, J., Bialko, C., \& Drasgow, F.
-(2019).
-How Big Are My Effects?
-Examining the Magnitude of Effect Sizes in Studies of Measurement Equivalence.
-\emph{Organizational Research Methods}, \emph{22}(3), 678--709.
-\url{https://doi.org/10.1177/1094428118761122}
-
-\leavevmode\vadjust pre{\hypertarget{ref-nye2011}{}}%
-Nye, C.
-D., \& Drasgow, F.
-(2011).
-Effect size indices for analyses of measurement equivalence: Understanding the practical importance of differences between groups.
-\emph{Journal of Applied Psychology}, \emph{96}(5), 966--980.
-\url{https://doi.org/10.1037/a0022955}
-
-\leavevmode\vadjust pre{\hypertarget{ref-putnick2016}{}}%
-Putnick, D.
-L., \& Bornstein, M.
-H.
-(2016).
-Measurement invariance conventions and reporting: The state of the art and future directions for psychological research.
-\emph{Developmental Review}, \emph{41}, 71--90.
-\url{https://doi.org/10.1016/j.dr.2016.06.004}
-
-\leavevmode\vadjust pre{\hypertarget{ref-robinson2023}{}}%
-Robinson, D., Hayes, A., Couch {[}aut, S., cre, Software, P., PBC, Patil, I., Chiu, D., Gomez, M., Demeshev, B., Menne, D., Nutter, B., Johnston, L., Bolker, B., Briatte, F., Arnold, J., Gabry, J., Selzer, L., Simpson, G., \ldots{} Reinhart, A.
-(2023).
-\emph{Broom: Convert statistical objects into tidy tibbles}.
-\url{https://CRAN.R-project.org/package=broom}
-
-\leavevmode\vadjust pre{\hypertarget{ref-rosseel2012}{}}%
-Rosseel, Y. (2012). Lavaan: An r package for structural equation modeling. \emph{Journal of Statistical Software}, \emph{48}(1), 1--36. \url{https://doi.org/10.18637/jss.v048.i02}
-
-\leavevmode\vadjust pre{\hypertarget{ref-schwarz1978}{}}%
-Schwarz, G. (1978). Estimating the dimension of a model. \emph{The Annals of Statistics}, \emph{6}(2), 461--464. \url{https://www.jstor.org/stable/2958889}
-
-\leavevmode\vadjust pre{\hypertarget{ref-shadish2001}{}}%
-Shadish, W. R., Cook, T. D., \& Campbell, D. T. (2001). \emph{Experimental and quasi-experimental designs for generalized causal inference}. Houghton Mifflin.
-
-\leavevmode\vadjust pre{\hypertarget{ref-suxf6rbom1978}{}}%
-Sörbom, D. (1978). An alternative to the methodology for analysis of covariance. \emph{Psychometrika}, \emph{43}(3), 381--396. \url{https://doi.org/10.1007/BF02293647}
-
-\leavevmode\vadjust pre{\hypertarget{ref-stark2006}{}}%
-Stark, S., Chernyshenko, O.
-S., \& Drasgow, F.
-(2006).
-Detecting differential item functioning with confirmatory factor analysis and item response theory: Toward a unified strategy.
-\emph{Journal of Applied Psychology}, \emph{91}(6), 1292--1306.
-\url{https://doi.org/10.1037/0021-9010.91.6.1292}
-
-\leavevmode\vadjust pre{\hypertarget{ref-steiger1990}{}}%
-Steiger, J.
-H.
-(1990).
-Structural model evaluation and modification: An interval estimation approach.
-\emph{Multivariate Behavioral Research}, \emph{25}(2), 173--180.
-\url{https://doi.org/10.1207/s15327906mbr2502_4}
-
-\leavevmode\vadjust pre{\hypertarget{ref-trent2013}{}}%
-Trent, L.
-R., Buchanan, E., Ebesutani, C., Ale, C.
-M., Heiden, L., Hight, T.
-L., Damon, J.
-D., \& Young, J.
-(2013).
-A measurement invariance examination of the revised child anxiety and depression scale in a southern sample: Differential item functioning between african american and caucasian youth.
-\emph{Assessment}, \emph{20}(2), 175--187.
-\url{https://doi.org/10.1177/1073191112450907}
-
-\leavevmode\vadjust pre{\hypertarget{ref-tucker1973}{}}%
-Tucker, L. R., \& Lewis, C. (1973). A reliability coefficient for maximum likelihood factor analysis. \emph{Psychometrika}, \emph{38}(1), 1--10. \url{https://doi.org/10.1007/BF02291170}
-
-\leavevmode\vadjust pre{\hypertarget{ref-vandeschoot2015}{}}%
-Van De Schoot, R., Schmidt, P., De Beuckelaer, A., Lek, K., \& Zondervan-Zwijnenburg, M.
-(2015).
-Editorial: Measurement invariance.
-\emph{Frontiers in Psychology}, \emph{6}.
-\url{https://www.frontiersin.org/articles/10.3389/fpsyg.2015.01064}
-
-\leavevmode\vadjust pre{\hypertarget{ref-vazire2022}{}}%
-Vazire, S., Schiavone, S.
-R., \& Bottesini, J.
-G.
-(2022).
-Credibility Beyond Replicability: Improving the Four Validities in Psychological Science.
-\emph{Current Directions in Psychological Science}, \emph{31}(2), 162--168.
-\url{https://doi.org/10.1177/09637214211067779}
-
-\leavevmode\vadjust pre{\hypertarget{ref-wagnild2009}{}}%
-Wagnild, G. (2009). A review of the resilience scale. \emph{Journal of Nursing Measurement}, \emph{17}(2), 105--113. \url{https://doi.org/10.1891/1061-3749.17.2.105}
-
-\leavevmode\vadjust pre{\hypertarget{ref-weidman2017}{}}%
-Weidman, A.
-C., Steckler, C.
-M., \& Tracy, J.
-L.
-(2017).
-The jingle and jangle of emotion assessment: Imprecise measurement, casual scale usage, and conceptual fuzziness in emotion research.
-\emph{Emotion}, \emph{17}(2), 267--295.
-\url{https://doi.org/10.1037/emo0000226}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-ggplot2}{}}%
-Wickham, H. (2016). \emph{ggplot2: Elegant graphics for data analysis}. Springer-Verlag New York. \url{https://ggplot2.tidyverse.org}
-
-\leavevmode\vadjust pre{\hypertarget{ref-wilke2020}{}}%
-Wilke, C. O. (2020). \emph{Cowplot: Streamlined plot theme and plot annotations for 'ggplot2'}. \url{https://CRAN.R-project.org/package=cowplot}
-
-\leavevmode\vadjust pre{\hypertarget{ref-yu2004}{}}%
-Yu, D.
-S.
-F., Lee, D.
-T.
-F., \& Woo, J.
-(2004).
-Issues and Challenges of Instrument Translation.
-\emph{Western Journal of Nursing Research}, \emph{26}(3), 307--320.
-\url{https://doi.org/10.1177/0193945903260554}
-
-\leavevmode\vadjust pre{\hypertarget{ref-zwaan2018}{}}%
-Zwaan, R. A., Etz, A., Lucas, R. E., \& Donnellan, M. B. (2018). Making replication mainstream. \emph{Behavioral and Brain Sciences}, \emph{41}, e120. \url{https://doi.org/10.1017/S0140525X17001972}
-
-\end{CSLReferences}
-
-\newpage
-
-\hypertarget{appendix-appendix}{%
-\appendix}
-
-\hypertarget{simulating-from-models}{%
-\section{Simulating from models}\label{simulating-from-models}}
-
-Here's an example of how to simulate directly from a \texttt{lavaan} model:
-
-\small
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{\# first build your model}
-\CommentTok{\# this example is separate for each group}
-\NormalTok{model.invariant.g1 }\OtherTok{\textless{}{-}} \StringTok{"}
-\StringTok{\# loadings}
-\StringTok{lv =\textasciitilde{} .8*q1 + .4*q2 + .6*q3 + .3*q4 + .6*q5 }
-\StringTok{\# set the residual for invariance on q4}
-\StringTok{q4 \textasciitilde{}\textasciitilde{} 1*q4}
-\StringTok{\# set the intercept for invariance on q4}
-\StringTok{q4 \textasciitilde{} 0*1}
-\StringTok{\# set the intercept to zero for df purposes}
-\StringTok{q1 \textasciitilde{} 0*1}
-\StringTok{\# allow the latent mean to be estimated }
-\StringTok{lv \textasciitilde{} 1"}
-\NormalTok{model.invariant.g2 }\OtherTok{\textless{}{-}} \StringTok{"lv =\textasciitilde{} .77*q1 + .43*q2 + .58*q3 + .3*q4 + .61*q5}
-\StringTok{q4 \textasciitilde{}\textasciitilde{} 1*q4}
-\StringTok{q4 \textasciitilde{} 0*1}
-\StringTok{q1 \textasciitilde{} 0*1}
-\StringTok{lv \textasciitilde{} 1"}
-
-\CommentTok{\# simulate data invariant separately for each group}
-\NormalTok{df.invariant }\OtherTok{\textless{}{-}} \FunctionTok{bind\_rows}\NormalTok{(}
-  \CommentTok{\# lavaan function }
-  \FunctionTok{simulateData}\NormalTok{(}
-    \CommentTok{\# model with estimates }
-    \AttributeTok{model =}\NormalTok{ model.invariant.g1, }
-    \CommentTok{\# how many data points}
-    \AttributeTok{sample.nobs =} \DecValTok{250}\NormalTok{, }
-    \CommentTok{\# mean structure for mgcfa models }
-    \AttributeTok{meanstructure =}\NormalTok{ T, }
-    \CommentTok{\# model type}
-    \AttributeTok{model.type =} \StringTok{"cfa"}\NormalTok{,}
-    \CommentTok{\# set seed for reproducibility }
-    \AttributeTok{seed =} \DecValTok{1234}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
-    \CommentTok{\# add a group label to the data }
-    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{group =} \StringTok{"Group 1"}\NormalTok{), }
-  \FunctionTok{simulateData}\NormalTok{(}
-    \AttributeTok{model =}\NormalTok{ model.invariant.g2, }
-    \AttributeTok{sample.nobs =} \DecValTok{250}\NormalTok{, }
-    \AttributeTok{meanstructure =}\NormalTok{ T, }
-    \AttributeTok{model.type =} \StringTok{"cfa"}\NormalTok{,}
-    \AttributeTok{seed =} \DecValTok{1234}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
-    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{group =} \StringTok{"Group 2"}\NormalTok{) }
-\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\normalsize
-
-\newpage
-
-\hypertarget{simulating-from-matrices}{%
-\section{Simulating from matrices}\label{simulating-from-matrices}}
-
-Here's an example of how to simulate using \texttt{MASS} and covariance or correlation matrices.
-
-\small
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\FunctionTok{library}\NormalTok{(MASS)}
-
-\CommentTok{\# covariance matrix}
-\NormalTok{university.cov }\OtherTok{\textless{}{-}} \FunctionTok{lav\_matrix\_lower2full}\NormalTok{(}
-    \FunctionTok{c}\NormalTok{(}\FloatTok{169.00}\NormalTok{, }
-      \FloatTok{73.710}\NormalTok{, }\FloatTok{182.2500}\NormalTok{,}
-      \FloatTok{73.229}\NormalTok{, }\FloatTok{88.4250}\NormalTok{, }\FloatTok{171.6100}\NormalTok{,}
-      \FloatTok{63.375}\NormalTok{, }\FloatTok{72.5625}\NormalTok{, }\FloatTok{127.7250}\NormalTok{, }\FloatTok{156.2500}\NormalTok{,}
-      \FloatTok{42.120}\NormalTok{, }\FloatTok{67.4325}\NormalTok{, }\FloatTok{122.0265}\NormalTok{, }\FloatTok{123.1875}\NormalTok{, }\FloatTok{182.2500}\NormalTok{,}
-      \FloatTok{57.226}\NormalTok{, }\FloatTok{63.2610}\NormalTok{, }\FloatTok{117.1926}\NormalTok{, }\FloatTok{154.4250}\NormalTok{, }\FloatTok{138.0240}\NormalTok{, }\FloatTok{201.6400}\NormalTok{,}
-      \FloatTok{30.875}\NormalTok{, }\FloatTok{32.0625}\NormalTok{, }\FloatTok{60.9805}\NormalTok{, }\FloatTok{62.9375}\NormalTok{, }\FloatTok{76.9500}\NormalTok{, }\FloatTok{79.5910}\NormalTok{, }\FloatTok{90.2500}\NormalTok{,}
-      \FloatTok{36.075}\NormalTok{, }\FloatTok{38.9610}\NormalTok{, }\FloatTok{61.0722}\NormalTok{, }\FloatTok{58.2750}\NormalTok{, }\FloatTok{65.9340}\NormalTok{, }\FloatTok{70.9290}\NormalTok{, }\FloatTok{81.1965}\NormalTok{, }\FloatTok{123.2100}\NormalTok{,}
-      \FloatTok{18.096}\NormalTok{, }\FloatTok{21.1410}\NormalTok{, }\FloatTok{26.2131}\NormalTok{, }\FloatTok{39.1500}\NormalTok{, }\FloatTok{44.6310}\NormalTok{, }\FloatTok{46.9452}\NormalTok{, }\FloatTok{48.7635}\NormalTok{, }\FloatTok{56.0106}\NormalTok{, }\FloatTok{75.6900}\NormalTok{))}
-
-\CommentTok{\# give it names}
-\FunctionTok{rownames}\NormalTok{(university.cov) }\OtherTok{\textless{}{-}}
-    \FunctionTok{colnames}\NormalTok{(university.cov) }\OtherTok{\textless{}{-}}
-    \FunctionTok{c}\NormalTok{(}\StringTok{"class"}\NormalTok{, }\StringTok{"social"}\NormalTok{, }\StringTok{"learn"}\NormalTok{, }\StringTok{"chronic"}\NormalTok{, }\StringTok{"physical"}\NormalTok{, }\StringTok{"sex"}\NormalTok{, }
-      \StringTok{"depression"}\NormalTok{, }\StringTok{"anxiety"}\NormalTok{, }\StringTok{"stress"}\NormalTok{)}
-
-\CommentTok{\# means {-} you need standard deviation if you only have a correlation matrix }
-\NormalTok{university.means }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\FloatTok{3.4}\NormalTok{, }\FloatTok{4.3}\NormalTok{, }\FloatTok{3.7}\NormalTok{, }\FloatTok{3.2}\NormalTok{, }\FloatTok{4.5}\NormalTok{, }\FloatTok{1.2}\NormalTok{, }\FloatTok{4.0}\NormalTok{, }\FloatTok{3.5}\NormalTok{, }\FloatTok{4.2}\NormalTok{)}
-
-\CommentTok{\# use mass function}
-\NormalTok{DF }\OtherTok{\textless{}{-}} \FunctionTok{mvrnorm}\NormalTok{(}\AttributeTok{n =} \DecValTok{200}\NormalTok{, }\AttributeTok{mu =}\NormalTok{ university.means, }\AttributeTok{Sigma =}\NormalTok{ university.cov)}
-
-\FunctionTok{head}\NormalTok{(DF)}
-\end{Highlighting}
-\end{Shaded}
-
-\normalsize
-
-\begin{verbatim}
-##          class      social     learn   chronic    physical         sex
-## [1,] 12.085294 26.83043663 13.895103 20.634374  16.7903295  30.5468832
-## [2,]  3.939545 10.93624431  3.093025  8.316128  -7.2199148   9.3579991
-## [3,] 15.659627  0.22811723  5.205657  5.224293  -1.4425219  -1.2710662
-## [4,] 23.086133 12.43649966  1.891769 -5.913170 -19.4937389 -13.5922410
-## [5,] 10.856492 23.30887194 17.124064 11.438840   2.4659294   1.7330709
-## [6,] -4.328380  0.07907149 -1.000636 -1.654947  -0.7365838  -0.3958833
-##      depression    anxiety      stress
-## [1,]  14.174374   8.001766  13.6534279
-## [2,]   3.940819  -6.598153  -7.9229552
-## [3,]  -8.927508 -10.335571  -2.8100779
-## [4,]  -0.149840   6.475669 -15.5300195
-## [5,]  -6.492809 -12.524601   0.4924153
-## [6,]  11.917631   3.433587   8.1456346
-\end{verbatim}
-
-\hypertarget{mgcfa-model-fit-statistics}{%
-\section{MGCFA Model Fit Statistics}\label{mgcfa-model-fit-statistics}}
+\subsection{MGCFA Model Fit Statistics}\label{mgcfa-model-fit-statistics}
 
@@
 
-\hypertarget{simulated-partial-invariance-results}{%
-\section{Simulated Partial Invariance Results}\label{simulated-partial-invariance-results}}
+\section{Simulated Partial Invariance Results}\label{simulated-partial-invariance-results}
 
@@
 
-\hypertarget{invariance-plots-difference-scores-by-condition}{%
-\section{Invariance Plots Difference Scores by Condition}\label{invariance-plots-difference-scores-by-condition}}
-
-\includegraphics{manuscript_files/figure-latex/inv-plots-condition-1.pdf} \includegraphics{manuscript_files/figure-latex/inv-plots-condition-2.pdf} \includegraphics{manuscript_files/figure-latex/inv-plots-condition-3.pdf} \includegraphics{manuscript_files/figure-latex/inv-plots-condition-4.pdf} \includegraphics{manuscript_files/figure-latex/inv-plots-condition-5.pdf} \includegraphics{manuscript_files/figure-latex/inv-plots-condition-6.pdf} \includegraphics{manuscript_files/figure-latex/inv-plots-condition-7.pdf} \includegraphics{manuscript_files/figure-latex/inv-plots-condition-8.pdf} \includegraphics{manuscript_files/figure-latex/inv-plots-condition-9.pdf} \includegraphics{manuscript_files/figure-latex/inv-plots-condition-10.pdf}
-
-\hypertarget{invariance-plots-effect-sizes-by-condition}{%
-\section{Invariance Plots Effect Sizes by Condition}\label{invariance-plots-effect-sizes-by-condition}}
-
-\includegraphics{manuscript_files/figure-latex/inv-effect-condition-1.pdf} \includegraphics{manuscript_files/figure-latex/inv-effect-condition-2.pdf} \includegraphics{manuscript_files/figure-latex/inv-effect-condition-3.pdf} \includegraphics{manuscript_files/figure-latex/inv-effect-condition-4.pdf} \includegraphics{manuscript_files/figure-latex/inv-effect-condition-5.pdf} \includegraphics{manuscript_files/figure-latex/inv-effect-condition-6.pdf} \includegraphics{manuscript_files/figure-latex/inv-effect-condition-7.pdf} \includegraphics{manuscript_files/figure-latex/inv-effect-condition-8.pdf} \includegraphics{manuscript_files/figure-latex/inv-effect-condition-9.pdf} \includegraphics{manuscript_files/figure-latex/inv-effect-condition-10.pdf}
-
-\hypertarget{density-plots-by-condition}{%
-\section{Density Plots by Condition}\label{density-plots-by-condition}}
-
-\includegraphics{manuscript_files/figure-latex/density-effects-condition-1.pdf} \includegraphics{manuscript_files/figure-latex/density-effects-condition-2.pdf} \includegraphics{manuscript_files/figure-latex/density-effects-condition-3.pdf} \includegraphics{manuscript_files/figure-latex/density-effects-condition-4.pdf} \includegraphics{manuscript_files/figure-latex/density-effects-condition-5.pdf} \includegraphics{manuscript_files/figure-latex/density-effects-condition-6.pdf} \includegraphics{manuscript_files/figure-latex/density-effects-condition-7.pdf} \includegraphics{manuscript_files/figure-latex/density-effects-condition-8.pdf} \includegraphics{manuscript_files/figure-latex/density-effects-condition-9.pdf} \includegraphics{manuscript_files/figure-latex/density-effects-condition-10.pdf}
-
-\hypertarget{replication-test}{%
-\subsection{Replication Test}\label{replication-test}}
-
-\hypertarget{data}{%
-\subsection{Data}\label{data}}
+\section{Invariance Plots Difference Scores by Condition}\label{invariance-plots-difference-scores-by-condition}
+
+\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/inv-plots-condition-1.pdf}} \pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/inv-plots-condition-2.pdf}} \pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/inv-plots-condition-3.pdf}} \pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/inv-plots-condition-4.pdf}} \pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/inv-plots-condition-5.pdf}} \pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/inv-plots-condition-6.pdf}} \pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/inv-plots-condition-7.pdf}} \pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/inv-plots-condition-8.pdf}} \pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/inv-plots-condition-9.pdf}} \pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/inv-plots-condition-10.pdf}}
+
+\section{Invariance Plots Effect Sizes by Condition}\label{invariance-plots-effect-sizes-by-condition}
+
+\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/inv-effect-condition-1.pdf}} \pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/inv-effect-condition-2.pdf}} \pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/inv-effect-condition-3.pdf}} \pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/inv-effect-condition-4.pdf}} \pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/inv-effect-condition-5.pdf}} \pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/inv-effect-condition-6.pdf}} \pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/inv-effect-condition-7.pdf}} \pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/inv-effect-condition-8.pdf}} \pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/inv-effect-condition-9.pdf}} \pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/inv-effect-condition-10.pdf}}
+
+\section{Density Plots by Condition}\label{density-plots-by-condition}
+
+\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/density-effects-condition-1.pdf}} \pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/density-effects-condition-2.pdf}} \pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/density-effects-condition-3.pdf}} \pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/density-effects-condition-4.pdf}} \pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/density-effects-condition-5.pdf}} \pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/density-effects-condition-6.pdf}} \pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/density-effects-condition-7.pdf}} \pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/density-effects-condition-8.pdf}} \pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/density-effects-condition-9.pdf}} \pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/density-effects-condition-10.pdf}}
+
+\subsection{Replication Test}\label{replication-test}
+
+\subsection{Data}\label{data}
 
@@
 
-\hypertarget{mgcfa}{%
-\subsection{MGCFA}\label{mgcfa}}
+\subsection{MGCFA}\label{mgcfa-1}
 
@@
 
-\hypertarget{partial-invariance}{%
-\subsection{Partial Invariance}\label{partial-invariance}}
+\subsection{Partial Invariance}\label{partial-invariance-1}
 
@@
 
-\hypertarget{visualize-invariance}{%
-\subsection{Visualize Invariance}\label{visualize-invariance}}
+\subsection{Visualize Invariance}\label{visualize-invariance}
 
@@
 
-\includegraphics{manuscript_files/figure-latex/unnamed-chunk-107-1.pdf}
+\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/unnamed-chunk-116-1.pdf}}
 
@@
 
-\includegraphics{manuscript_files/figure-latex/unnamed-chunk-107-2.pdf}
+\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/unnamed-chunk-116-2.pdf}}
 
@@
 
-\includegraphics{manuscript_files/figure-latex/unnamed-chunk-107-3.pdf}
+\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/unnamed-chunk-116-3.pdf}}
 
@@
 
-\includegraphics{manuscript_files/figure-latex/unnamed-chunk-107-4.pdf}
+\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/unnamed-chunk-116-4.pdf}}
 
@@
 
-\includegraphics{manuscript_files/figure-latex/unnamed-chunk-107-5.pdf}
+\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/unnamed-chunk-116-5.pdf}}
 
@@
 
-\includegraphics{manuscript_files/figure-latex/unnamed-chunk-107-6.pdf}
+\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/unnamed-chunk-116-6.pdf}}
 
@@
 
-\includegraphics{manuscript_files/figure-latex/unnamed-chunk-107-7.pdf}
+\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/unnamed-chunk-116-7.pdf}}
 
@@
 
-\includegraphics{manuscript_files/figure-latex/unnamed-chunk-107-8.pdf}
+\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/unnamed-chunk-116-8.pdf}}
 
@@
 
-\hypertarget{bootstrap-model}{%
-\subsection{Bootstrap Model}\label{bootstrap-model}}
+\subsection{Bootstrap Model}\label{bootstrap-model}
 
@@
 
-\hypertarget{bootstrap-partial-invariance}{%
-\subsection{Bootstrap Partial Invariance}\label{bootstrap-partial-invariance}}
-
-\hypertarget{each-parameter-on-the-overall-model-invariance}{%
-\subsubsection{Each Parameter on the Overall Model Invariance}\label{each-parameter-on-the-overall-model-invariance}}
+\subsection{Bootstrap Partial Invariance}\label{bootstrap-partial-invariance}
+
+\subsubsection{Each Parameter on the Overall Model Invariance}\label{each-parameter-on-the-overall-model-invariance}
 
@@
 
-\hypertarget{each-parameters-standardized-difference-score}{%
-\subsubsection{Each Parameter's Standardized Difference Score}\label{each-parameters-standardized-difference-score}}
+\subsubsection{Each Parameter's Standardized Difference Score}\label{each-parameters-standardized-difference-score}
 
@@
 
-\includegraphics{manuscript_files/figure-latex/unnamed-chunk-114-1.pdf}
+\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/unnamed-chunk-123-1.pdf}}
 
@@
 
-\includegraphics{manuscript_files/figure-latex/unnamed-chunk-115-1.pdf} \includegraphics{manuscript_files/figure-latex/unnamed-chunk-115-2.pdf}
+\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/unnamed-chunk-124-1.pdf}} \pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/unnamed-chunk-124-2.pdf}}
 

### 2024-07-29 manuscript.Rmd
fixing figures

@@
 Equality constraints between group parameters are then added sequentially to the model [@brown2015].
-If parameters are found to be equivalent between groups, these models are considered "invariant", suggesting that any subtle differences in the parameter estimate should not effect overall scoring and assessment.
+If parameters are found to be equivalent between groups, these models are considered "invariant", suggesting that any subtle differences in the parameter estimates should not effect overall scoring and assessment.
 
@@
 Other parameter equality constraints can be set at the latent variable level (latent means, variance, covariances), but the focus is generally on the observable variables and their parameter estimations.
-Non-invariance is determined by examining differences in fit indices between models with constraints versus without [@cheung2002].
+Non-invariance is determined by examining differences in fit indices between models with constraints versus without in sequential order [@cheung2002].
 
@@
 
-If a specific step within the MGCFA testing framework shows non-invariance, partial invariance is often used to investigate where and "how much" invariance occurs [@meredith1993; @byrne1989].
+If a specific step within the MGCFA testing framework shows non-invariance, partial invariance is often used to investigate where and "how much" invariance occurs [i.e., how many items, rather than how big the differences are @byrne1989; @meredith1993].
 Similar to *post hoc* follow up tests in ANOVA, each equality constraint for that model is examined one at a time by allowing groups to vary.
-If the model fit improves when groups are allowed to have separate parameter estimations, the item parameter estimate is considered non-invariant.
+If the model fit improves when groups are allowed to have separate parameter estimates, the item for these groups is considered non-invariant.
 When only a few parameters are found that impact invariance, models are considered partially invariant, implying that most, but not all parameters are equal across groups.
 The researcher then interprets the impact of those items and parameters on overall scores and assessment usefulness.
-Partial invariance investigation is a useful tool for finding specific items that vary between groups, but does not fully explain the effect size of the difference between groups and the impact on the overall model.
+Partial invariance investigation is a useful tool for finding specific items that vary between groups, but does not fully explain the effect size of the difference between groups on those items and the impact on the overall model.
 
@@
 *i* indicates an individual item, and *R* indicates the reference group [@nye2011].
-Therefore, an individual score is predicted by the intercept of the item ($\tau$) added to the item loading ($\lambda$) times the latent variable score ($\xi$).
-@nye2011 demonstrated that the terminology from IRT and DIF can be used to create a measure of item functioning differences within CFA, $d_{MACS}$.
+Therefore, an individual item is predicted by the intercept of the item ($\tau$) added to the item loading ($\lambda$) times the latent variable score ($\xi$).
+@nye2011 demonstrated that the terminology and equations from IRT and DIF can be used to create a measure of item functioning differences within CFA, $d_{MACS}$.
 $d_{MACS}$ is then the difference of reference group versus focal group (e.g., group 1 versus group 2) divided by a pooled standard deviation similar to formulas for *d* proposed by @cohen2013.
 Therefore, if $\tau$ or $\lambda$ are individually (or both) different across groups, it will impact all the predicted $X_{iR}$ scores, and thus, impact $d_{MACS}$ values.
-While $d_{MACS}$ represents a necessary step for development of effect sizes within CFA, it does not separate the differences in parameters between groups in a way that can be paired with traditional MGCFA testing and partial invariance.
+While $d_{MACS}$ represents a necessary step for development of effect sizes within CFA, it does not separate the differences in parameters between groups in a way that can be paired with traditional MGCFA testing steps and partial invariance.
 In addition to the missing effect sizes at model and parameter levels, no effect size to date gives the researcher a feeling for potential replication of the invariant or non-invariant items.
@@
 
-The %>% code for this manuscript can be found at <https://osf.io/wev5f/>.
+The code for this manuscript can be found at <https://osf.io/wev5f/>.
 This tutorial was registered at <https://osf.io/vwf4d>, and the example provided at the end of the manuscript was added after that registration.
@@
 The code online provides an example of testing each item individually by relaxing the constraints and recalculating the CFI.
-If these Items bring the CFI value back up to $\Delta$CFI \<= .01 from the metric model, then the model would be considering partially invariant at the scalar level.
+If these items bring the CFI value back up to $\Delta$CFI \<= .01 from the metric model, then the model would be considering partially invariant at the scalar level.
 It seems unlikely that the residuals will show invariance, even if partial scalar invariance can be found, as the drop in fit on the residual model is quite large.
@@
 
-The partial invariance results indicated that RS6 and RS7 are potential items that could be relaxed to improve model fit and create a partial scalar invariant model (i.e., by picking the largest CFI values).
-By examining our estimates, we can see that item seven on the RS-14 is estimated at nearly 5 points for the clinical sample, while the student sample has a lower mean around 4.5 points.
-Generally, students show higher means on the items of the RS-14, but when all loadings and other intercepts are constrained to be equal, and this one item is relaxed, this pattern flips so that clinical groups show higher item intercepts.
-Given the scale is a 1-7 Likert type scale, .5 a point represents a potentially sizable change on the scale.
-Item seven covers perseverance after hardship, and all items can be found in the user manual for the scale at www.resiliencecenter.com.
-The effect size from $d_{MACS}$ suggests a small to medium effect, `r apa_num(lavaan_dmacs(partial.rs.1$invariance_models$model.intercepts, "Clinical")$DMACS[7])`.
-See Figure \@ref(fig:rs7-img) for the difference between item intercepts and latent means.
-We repeat this process for the RS6, as the CFI for our model with only RS7 does not achieve the levels of partial invariance for our $\Delta$CFI criterion (i.e., \<= .01 downward change in fit: metric CFI = `r apa_p(results.rs$model_fit$cfi[5])`, partial scalar CFI = `r apa_p(partial.rs.1$model_fit$cfi[6])`).
-
 ```{r partial-RS6, echo = F, include = F, size = "small"}
@@
 
+The partial invariance results indicated that RS6 and RS7 are potential items that could be relaxed to improve model fit and create a partial scalar invariant model (i.e., by picking the largest CFI values).
+By examining our estimates, we can see that item seven on the RS-14 is estimated at nearly 5 points for the clinical sample, while the student sample has a lower mean around 4.5 points.
+Generally, students show higher means on the items of the RS-14, but when all loadings and other intercepts are constrained to be equal, and this one item is relaxed, this pattern flips so that clinical groups show higher item intercepts.
+Given the scale is a 1-7 Likert type scale, .5 a point represents a potentially sizable change on the scale.
+Item seven covers perseverance after hardship, and all items can be found in the user manual for the scale at www.resiliencecenter.com.
+The effect size from $d_{MACS}$ suggests a small to medium effect, `r apa_num(lavaan_dmacs(partial.rs.1$invariance_models$model.intercepts, "Clinical")$DMACS[7])`.
+See Figure \@ref(fig:rs7-img) for the difference between item intercepts and latent means.
+We repeat this process for the RS6, as the CFI for our model with only RS7 does not achieve the levels of partial invariance for our $\Delta$CFI criterion (i.e., \<= .01 downward change in fit: metric CFI = `r apa_p(results.rs$model_fit$cfi[5])`, partial scalar CFI = `r apa_p(partial.rs.1$model_fit$cfi[6])`).
 Again, we see about a half-point difference between our clinical and student samples for item 6, which is about drive to achieve.
@@
 Therefore, we would expect the loadings to replicate (and the effect size would be 0 difference between bootstrapped and random, both showing invariance).
-The intercepts show a large (i.e., close to the max possible value) non-invariant effect, and therefore, we should not expect this model to show invariance in a replication.
+The intercepts show a large (i.e., close to the max possible value) non-invariant effect, $h_{nmi}$ = `r apa_num(boot.model.rs$h_nmi[1])` ($h_{mni}_p$ = `r apa_num(boot.model.rs$h_nmi_p[1])`), and therefore, we should not expect this model to show invariance in a replication.
 
@@
 In general, we should expect $M_{D}$ = `r apa_num(boot.partial.rs$boot_summary %>% filter(invariant) %>% pull(mean_boot_difference) %>% mean())` when items are invariant and $M_{D}$ = `r apa_num(boot.partial.rs$boot_summary %>% filter(!invariant) %>% pull(mean_boot_difference) %>% mean())` when items are not invariant.
-The effect size of non-invariant items ranges from `r apa_num(boot.partial.rs$boot_summary %>% filter(!invariant) %>% pull(d_boot) %>% min(., na.rm = T))` to `r apa_num(boot.partial.rs$boot_summary %>% filter(!invariant) %>% pull(d_boot) %>% max(., na.rm = T))`.
+The effect size of non-invariant items ranges from $d_s$ ~ `r apa_num(boot.partial.rs$boot_summary %>% filter(!invariant) %>% pull(d_boot) %>% min(., na.rm = T))` to `r apa_num(boot.partial.rs$boot_summary %>% filter(!invariant) %>% pull(d_boot) %>% max(., na.rm = T))`.
 
@@
 In summary, if one were planning a replication, the prediction would be that item intercepts would likely not replicate, with a large effect size (i.e., it is easy to judge $h_{nmi_p}$ close to the max of one as large).
-While this study found partial invariance by relaxing constraints on two individual items, bootstrapped partial invariance indicates that any item could potentially be problematic with an effect size averaging $d$ \~ 0.50 difference in means.
+While this study found partial invariance by relaxing constraints on two individual items, bootstrapped partial invariance indicates that any item could potentially be problematic with an effect size averaging $d_s$ \~ 0.50 difference in means.
 While $d_{MACS}$ values represented a "small" effect based on previous publications, this effect may be muted by examining both loadings and intercepts.
@@
 The overall average score on items is high: $M_M$ = `r apa_num(mean(apply(DF[ , -ncol(DF)], 2, mean)))` ($M_{SD}$ = `r apa_num(mean(apply(DF[ , -ncol(DF)], 2, sd)))`).
-Given the mean standard deviation, a $d$ \~ 0.50 represents `r apa_num(mean(apply(DF[ , -ncol(DF)], 2, sd))/2)` or nearly one whole point on the scale.
-A researcher could decide that at least $d$ = 0.33 or at least a third of a standard deviation would be an important change and set that as their smallest effect size of interest for invariance.
+Given the mean and standard deviation, a $d_s$ \~ 0.50 represents `r apa_num(mean(apply(DF[ , -ncol(DF)], 2, sd))/2)` or nearly one whole point on the scale.
+A researcher could decide that at least $d_s$ = 0.33 or at least a third of a standard deviation would be an important change and set that as their smallest effect size of interest for invariance replication and extension.
 Further, a newly planned study should investigate what variables may predict when and why samples separate into bimodal representations for item means.
@@
 Given these results, another researcher may assume that the models would be comparable between English speaking (i.e., likely United States) and Chinese speaking samples.
-With the published data, we can use `visualizemi` to determine if the RS14 is invariant across language/culture, and if the results would likely replicate if tested on a new set of samples, and what, if any, effect size differences are found in parameters.
+With the published data, we can use *visualizemi* to determine if the RS14 is invariant across language/culture, and if the results would likely replicate if tested on a new set of samples, and what, if any, effect size differences are found in parameters.
 The code used for this analysis is presented in the supplemental materials.
@@
 ```{r rs14-chinese-effect-pic, include = T, fig.cap = "Effect size differences for item intercepts on the English versus Chinese samples for the RS14.", warnings = FALSE, message = FALSE, fig.height=8}
-load("manu_data/boot.partial.rs.appendix7.Rdata")
-effect_invariance_plot
+knitr::include_graphics("figures/rs14-chinese-effect_invariance_plot.png")
 ```

### 2024-07-29 manuscript.tex
fixing figures

@@
 \documentclass[
-  man,floatsintext]{apa7}
+  man]{apa7}
 \usepackage{amsmath,amssymb}
@@
 \keywords{multigroup confirmatory factor analysis, measurement invariance, visualization, effect size}
+\DeclareDelayedFloatFlavor{ThreePartTable}{table}
+\DeclareDelayedFloatFlavor{lltable}{table}
+\DeclareDelayedFloatFlavor*{longtable}{table}
+\makeatletter
+\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
+\makeatother
 \usepackage{lineno}
@@
 
-The complete code for this manuscript can be found at \url{https://osf.io/wev5f/}.
+The \%\textgreater\% code for this manuscript can be found at \url{https://osf.io/wev5f/}.
 This tutorial was registered at \url{https://osf.io/vwf4d}, and the example provided at the end of the manuscript was added after that registration.
@@
 \item
-  the dataframe in the \texttt{data} argument of our functionl
+  the dataframe in the \texttt{data} argument of our function
 \item
@@
 You can use \texttt{y\_limits} to zoom in on the graph if these are too small to be distinguishable.
-3) \texttt{mean}: The right-hand side of the complete plot graphing the latent variable means and density from the data.
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi})}
+\setcounter{enumi}{2}
+\item
+  \texttt{mean}: The right-hand side of the complete plot graphing the latent variable means and density from the data.
 The latent variable is shown on the x-axis using standardized values (i.e., \emph{z}-scores) where -1 indicates one standard deviation below the mean for the latent variable, 0 indicates the mean for the latent variable and so on.
@@
 Group 1 is usually the group that is alphabetically first in the data set or whichever group is the first that appears when using the \texttt{levels()} command.
-4) \texttt{variance}: A split geom violin plot indicating the variance distribution of the plotted item.
+\item
+  \texttt{variance}: A split geom violin plot indicating the variance distribution of the plotted item.
 Residuals are trickier to plot, as they are the left over error when predicting the observed variables \(\epsilon\).
@@
 The plots are included separately so they can be arranged in a different fashion if desired.
+\end{enumerate}
 
@@
 The saved output includes several dataframes and plots.
-The first is the \texttt{boot\_DF} which the summary of each run in a dataframe for plotting or summarization.
-This dataframe includes the estimate for each paramter (\texttt{term}) separated by group and type (\texttt{boot\_1}, \texttt{boot\_2} are the bootstrapped estimates for group 1 and group 2, while the same \texttt{random} columns indicate the randomly assigned groups).
+The first is the \texttt{boot\_DF} which is the summary of each bootstrapped run in a dataframe for plotting or summarization.
+This dataframe includes the estimate for each parameter (\texttt{term}) separated by group and type (\texttt{boot\_1}, \texttt{boot\_2} are the bootstrapped estimates for group 1 and group 2, while the same \texttt{random} columns indicate the randomly assigned groups).
 The fit index used to determine invariance is included for bootstrapped and random estimates, and then the differences between groups and if they were ``invariant'' or not given the researcher supplied rule.
 
-Next, the \texttt{boot\_summary} includes a summarized form of the bootstrapped results from separated by bootstrapping versus random and invariant/non-invariant.
-The \(d_s\) for between groups Cohen's \(d\) is included.
+Next, the \texttt{boot\_summary} includes a summarized form of the bootstrapped results separated by bootstrapped data versus randomized data and then invariant/non-invariant outcomes.
+The \(d_s\) for between groups Cohen's \(d\) is included (\textbf{lakens2013?}).
 Effect sizes are only calculated when the number of bootstrapped estimates is at least 10\% of the data - therefore, you would not receive effect sizes with almost no bootstrapped runs.
-This dataframe should be used to determine which parameter may be different and at what size between groups in a replication of the study.
+This dataframe should be used to determine which parameter may be different and the effect size potential between groups in a replication of the study.
 The \texttt{boot\_effects} table creates a summary similar to the overall model replication table based on the proportion of runs that were considered invariant versus not for each parameter.
@@
 \pandocbounded{\includegraphics[keepaspectratio]{figures/boot-partial-invariance.png}}
-\caption{\label{fig:invariance-partial-fig}Visualization of the difference score between groups by parameter for invariant and non-invariant bootstrapped and randomly assigned group data.}
+\caption{\label{fig:invariance-partial-fig}Visualization of the difference score between groups by parameter for invariant and non-invariant bootstrapped and randomly assigned group data on simulated data.}
 \end{figure}
@@
 \pandocbounded{\includegraphics[keepaspectratio]{figures/boot-partial-density.png}}
-\caption{\label{fig:density-partial-fig}Visualization of the number of estimates for each group by bootstrapped and randomly assigned group runs by their invariance decision.}
+\caption{\label{fig:density-partial-fig}Visualization of the number of estimates for each group by bootstrapped and randomly assigned group runs by their invariance decision on simulated data.}
 \end{figure}
@@
 Table \ref{tab:rs-table} indicates that fit was degraded when the constraint on equal item intercepts was added.
-The code below provides an example of testing each item individually by relaxing the constraints and recalculating the CFI.
+The code online provides an example of testing each item individually by relaxing the constraints and recalculating the CFI.
 If these Items bring the CFI value back up to \(\Delta\)CFI \textless= .01 from the metric model, then the model would be considering partially invariant at the scalar level.
-It seems unlikely that the residuals will show invariance, if partial scalar invariance can be found, as the drop in fit is quite large.
-
-The output indicates that RS6 and RS7 are potential items that could be relaxed to improve model fit and create a partial scalar invariant model (i.e., by picking the largest CFI values).
-The code below show to check the addition of these items, which are added one at a time.
-You use the \texttt{group.partial} open to ``relax'' or freely estimate that parameter for each group separately.
-
+It seems unlikely that the residuals will show invariance, even if partial scalar invariance can be found, as the drop in fit on the residual model is quite large.
+
+The partial invariance results indicated that RS6 and RS7 are potential items that could be relaxed to improve model fit and create a partial scalar invariant model (i.e., by picking the largest CFI values).
 By examining our estimates, we can see that item seven on the RS-14 is estimated at nearly 5 points for the clinical sample, while the student sample has a lower mean around 4.5 points.
@@
 The effect size from \(d_{MACS}\) suggests a small to medium effect, 0.28.
-In this next code section, we repeat this process for the RS6, as the CFI for our model with only RS7 does not achieve the levels of partial invariance for our \(\Delta\)CFI criterion (i.e., \textless= .01 downward change in fit: metric CFI = .925, partial scalar CFI = .914).
 See Figure \ref{fig:rs7-img} for the difference between item intercepts and latent means.
+We repeat this process for the RS6, as the CFI for our model with only RS7 does not achieve the levels of partial invariance for our \(\Delta\)CFI criterion (i.e., \textless= .01 downward change in fit: metric CFI = .925, partial scalar CFI = .914).
 
@@
 \pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/rs7-img-1.pdf}}
-\caption{\label{fig:rs7-img}RS7 Item Invariance Visualization}
+\caption{\label{fig:rs7-img}RS7 item non-invariance visualization showing differences in the item intercepts and latent variable.}
 \end{figure}
@@
 \pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/rs6-img-1.pdf}}
-\caption{\label{fig:rs6-img}RS6 Item Invariance Visualization}
+\caption{\label{fig:rs6-img}RS6 item non-invariance visualization similar results to RS7 with differences in item intercepts.}
 \end{figure}
@@
 Given our current results, we may not expect our intercepts to replicate.
-Given the order of \texttt{group.equal}, the boot function will select the first non-invariant step in the calculation of the effect size for potential replication.
+Given the order of desired steps in the \texttt{group.equal} argument, the boot function will select the first non-invariant step (as defined by the user) in the calculation of the effect size for potential replication.
 In our output, we do not see a loadings effect size, and this result occurs when \emph{none} of the bootstrapped or random results are non-invariant.
@@
 \bottomrule
+\addlinespace
 \end{tabular}
+
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} Non-Invariant and Random Non-Invariant columns represent the proportion of non-invariant simulations of out the total simulations, representing our non-replication rate.
+These values are converted into an effect size difference in the final two columns.}
+\end{tablenotes}
 
@@
 With the published data, we can use \texttt{visualizemi} to determine if the RS14 is invariant across language/culture, and if the results would likely replicate if tested on a new set of samples, and what, if any, effect size differences are found in parameters.
-The code used for this analysis is presented in Appendix 7.
+The code used for this analysis is presented in the supplemental materials.
 
@@
 \centering
-\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/rs14-chinese-pic-1.pdf}}
+\pandocbounded{\includegraphics[keepaspectratio]{figures/rs14-chinese-RS2.png}}
 \caption{\label{fig:rs14-chinese-pic}The differences in intercepts for the second item on the RS14 by language sample.
@@
 \centering
-\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/rs14-chinese-effect-pic-1.pdf}}
+\pandocbounded{\includegraphics[keepaspectratio]{figures/rs14-chinese-effect_invariance_plot.png}}
 \caption{\label{fig:rs14-chinese-effect-pic}Effect size differences for item intercepts on the English versus Chinese samples for the RS14.}
@@
 The results from our Chinese versus English comparison show us the other scenario: non-invariant results that clearly indicate differences with a large effect size on both replication and item average differences.
-Given that the goal of measurement invariance is to compare \emph{estimates}, we should expect some differences across samples due to the nature of sampling and estimation.
+Overall, given that the goal of measurement invariance is to compare parameter \emph{estimates}, we should expect some differences across samples due to the nature of sampling and estimation.
 It may be that many of the published models presented represent these effects - small variations between groups due to sampling error or other small crud - but do not represent a fundamental problem with the measurement or generalizability of the results.
@@
 The first is the \texttt{boot\_DF} which the summary of each run in a dataframe for plotting or summarization.
-This dataframe includes the estimate for each paramter (\texttt{term}) separated by group and type (\texttt{boot\_1}, \texttt{boot\_2} are the bootstrapped estimates for group 1 and group 2, while the same \texttt{random} columns indicate the randomly assigned groups).
+This dataframe includes the estimate for each parameter (\texttt{term}) separated by group and type (\texttt{boot\_1}, \texttt{boot\_2} are the bootstrapped estimates for group 1 and group 2, while the same \texttt{random} columns indicate the randomly assigned groups).
 The fit index used to determine invariance is included for bootstrapped and random estimates, and then the differences between groups and if they were ``invariant'' or not given the researcher supplied rule.
@@
 
+The code for building and running simulations can be found in \emph{simulate\_boot\_rr.Rmd}, \emph{simulate\_boot\_partial.Rmd}, and \emph{simulate\_combine.Rmd}.
+
 \subsection{Design and Analysis}\label{design-and-analysis}
@@
 ##   <chr>  <int>
-## 1 Chen          1010
-## 2 Schulenberg   1765
+## 1 Aiena   1765
+## 2 Chen    1010
 \end{verbatim}

### 2024-07-29 manuscript.Rmd
manuscript!

@@
 
-```{r rs7-img, echo = F, include = T, size = "small", fig.cap="RS7 item non-invariance visualization showing differences in the item intercepts and latent variable.", fig.height=8}
+```{r rs7-img, echo = F, include = T, size = "small", fig.cap="RS7 item non-invariance visualization showing differences in the item intercepts and latent variable."}
 # plot the image for RS7
@@
        width = 8, 
+       height = 6,
        units = "in")
@@
 
-```{r rs6-img, echo = F, include = T, size = "small", fig.cap="RS6 item non-invariance visualization similar results to RS7 with differences in item intercepts.", fig.height=8}
+```{r rs6-img, echo = F, include = T, size = "small", fig.cap="RS6 item non-invariance visualization similar results to RS7 with differences in item intercepts."}
 plot_mi(
@@
        width = 8, 
+       height = 6, 
        units = "in")
@@
 Therefore, we would expect the loadings to replicate (and the effect size would be 0 difference between bootstrapped and random, both showing invariance).
-The intercepts show a large (i.e., close to the max possible value) non-invariant effect, $h_{nmi}$ = `r apa_num(boot.model.rs$h_nmi[1])` ($h_{mni}_p$ = `r apa_num(boot.model.rs$h_nmi_p[1])`), and therefore, we should not expect this model to show invariance in a replication.
+The intercepts show a large (i.e., close to the max possible value) non-invariant effect, $h_{nmi}$ = `r apa_num(boot.model.rs$h_nmi[1])` ($h_{mni_p}$ = `r apa_num(boot.model.rs$h_nmi_p[1])`), and therefore, we should not expect this model to show invariance in a replication.
 
@@
 In general, we should expect $M_{D}$ = `r apa_num(boot.partial.rs$boot_summary %>% filter(invariant) %>% pull(mean_boot_difference) %>% mean())` when items are invariant and $M_{D}$ = `r apa_num(boot.partial.rs$boot_summary %>% filter(!invariant) %>% pull(mean_boot_difference) %>% mean())` when items are not invariant.
-The effect size of non-invariant items ranges from $d_s$ ~ `r apa_num(boot.partial.rs$boot_summary %>% filter(!invariant) %>% pull(d_boot) %>% min(., na.rm = T))` to `r apa_num(boot.partial.rs$boot_summary %>% filter(!invariant) %>% pull(d_boot) %>% max(., na.rm = T))`.
+The effect size of non-invariant items ranges from $d_s$ \~ `r apa_num(boot.partial.rs$boot_summary %>% filter(!invariant) %>% pull(d_boot) %>% min(., na.rm = T))` to `r apa_num(boot.partial.rs$boot_summary %>% filter(!invariant) %>% pull(d_boot) %>% max(., na.rm = T))`.
 

### 2024-07-29 manuscript.tex
manuscript!

@@
 Equality constraints between group parameters are then added sequentially to the model (Brown, 2015).
-If parameters are found to be equivalent between groups, these models are considered ``invariant'', suggesting that any subtle differences in the parameter estimate should not effect overall scoring and assessment.
+If parameters are found to be equivalent between groups, these models are considered ``invariant'', suggesting that any subtle differences in the parameter estimates should not effect overall scoring and assessment.
 
@@
 Other parameter equality constraints can be set at the latent variable level (latent means, variance, covariances), but the focus is generally on the observable variables and their parameter estimations.
-Non-invariance is determined by examining differences in fit indices between models with constraints versus without (Cheung \& Rensvold, 2002).
+Non-invariance is determined by examining differences in fit indices between models with constraints versus without in sequential order (Cheung \& Rensvold, 2002).
 
@@
 
-If a specific step within the MGCFA testing framework shows non-invariance, partial invariance is often used to investigate where and ``how much'' invariance occurs (Byrne et al., 1989; Meredith, 1993).
+If a specific step within the MGCFA testing framework shows non-invariance, partial invariance is often used to investigate where and ``how much'' invariance occurs (i.e., how many items, rather than how big the differences are Byrne et al., 1989; Meredith, 1993).
 Similar to \emph{post hoc} follow up tests in ANOVA, each equality constraint for that model is examined one at a time by allowing groups to vary.
-If the model fit improves when groups are allowed to have separate parameter estimations, the item parameter estimate is considered non-invariant.
+If the model fit improves when groups are allowed to have separate parameter estimates, the item for these groups is considered non-invariant.
 When only a few parameters are found that impact invariance, models are considered partially invariant, implying that most, but not all parameters are equal across groups.
 The researcher then interprets the impact of those items and parameters on overall scores and assessment usefulness.
-Partial invariance investigation is a useful tool for finding specific items that vary between groups, but does not fully explain the effect size of the difference between groups and the impact on the overall model.
+Partial invariance investigation is a useful tool for finding specific items that vary between groups, but does not fully explain the effect size of the difference between groups on those items and the impact on the overall model.
 
@@
 \emph{i} indicates an individual item, and \emph{R} indicates the reference group (Nye \& Drasgow, 2011).
-Therefore, an individual score is predicted by the intercept of the item (\(\tau\)) added to the item loading (\(\lambda\)) times the latent variable score (\(\xi\)).
-Nye and Drasgow (2011) demonstrated that the terminology from IRT and DIF can be used to create a measure of item functioning differences within CFA, \(d_{MACS}\).
+Therefore, an individual item is predicted by the intercept of the item (\(\tau\)) added to the item loading (\(\lambda\)) times the latent variable score (\(\xi\)).
+Nye and Drasgow (2011) demonstrated that the terminology and equations from IRT and DIF can be used to create a measure of item functioning differences within CFA, \(d_{MACS}\).
 \(d_{MACS}\) is then the difference of reference group versus focal group (e.g., group 1 versus group 2) divided by a pooled standard deviation similar to formulas for \emph{d} proposed by Cohen (2013).
 Therefore, if \(\tau\) or \(\lambda\) are individually (or both) different across groups, it will impact all the predicted \(X_{iR}\) scores, and thus, impact \(d_{MACS}\) values.
-While \(d_{MACS}\) represents a necessary step for development of effect sizes within CFA, it does not separate the differences in parameters between groups in a way that can be paired with traditional MGCFA testing and partial invariance.
+While \(d_{MACS}\) represents a necessary step for development of effect sizes within CFA, it does not separate the differences in parameters between groups in a way that can be paired with traditional MGCFA testing steps and partial invariance.
 In addition to the missing effect sizes at model and parameter levels, no effect size to date gives the researcher a feeling for potential replication of the invariant or non-invariant items.
@@
 
-The \%\textgreater\% code for this manuscript can be found at \url{https://osf.io/wev5f/}.
+The code for this manuscript can be found at \url{https://osf.io/wev5f/}.
 This tutorial was registered at \url{https://osf.io/vwf4d}, and the example provided at the end of the manuscript was added after that registration.
@@
 Next, the \texttt{boot\_summary} includes a summarized form of the bootstrapped results separated by bootstrapped data versus randomized data and then invariant/non-invariant outcomes.
-The \(d_s\) for between groups Cohen's \(d\) is included (\textbf{lakens2013?}).
+The \(d_s\) for between groups Cohen's \(d\) is included (Lakens, 2013).
 Effect sizes are only calculated when the number of bootstrapped estimates is at least 10\% of the data - therefore, you would not receive effect sizes with almost no bootstrapped runs.
@@
 The code online provides an example of testing each item individually by relaxing the constraints and recalculating the CFI.
-If these Items bring the CFI value back up to \(\Delta\)CFI \textless= .01 from the metric model, then the model would be considering partially invariant at the scalar level.
+If these items bring the CFI value back up to \(\Delta\)CFI \textless= .01 from the metric model, then the model would be considering partially invariant at the scalar level.
 It seems unlikely that the residuals will show invariance, even if partial scalar invariance can be found, as the drop in fit on the residual model is quite large.
@@
 We repeat this process for the RS6, as the CFI for our model with only RS7 does not achieve the levels of partial invariance for our \(\Delta\)CFI criterion (i.e., \textless= .01 downward change in fit: metric CFI = .925, partial scalar CFI = .914).
-
 Again, we see about a half-point difference between our clinical and student samples for item 6, which is about drive to achieve.
@@
 Therefore, we would expect the loadings to replicate (and the effect size would be 0 difference between bootstrapped and random, both showing invariance).
-The intercepts show a large (i.e., close to the max possible value) non-invariant effect, and therefore, we should not expect this model to show invariance in a replication.
+The intercepts show a large (i.e., close to the max possible value) non-invariant effect, \(h_{nmi}\) = 3.05 (\(h_{mni_p}\) = 0.97), and therefore, we should not expect this model to show invariance in a replication.
 
@@
 In general, we should expect \(M_{D}\) = 0.11 when items are invariant and \(M_{D}\) = 0.25 when items are not invariant.
-The effect size of non-invariant items ranges from 0.43 to 0.59.
+The effect size of non-invariant items ranges from \(d_s\) \textasciitilde{} 0.43 to 0.59.
 
@@
 In summary, if one were planning a replication, the prediction would be that item intercepts would likely not replicate, with a large effect size (i.e., it is easy to judge \(h_{nmi_p}\) close to the max of one as large).
-While this study found partial invariance by relaxing constraints on two individual items, bootstrapped partial invariance indicates that any item could potentially be problematic with an effect size averaging \(d\) \textasciitilde{} 0.50 difference in means.
+While this study found partial invariance by relaxing constraints on two individual items, bootstrapped partial invariance indicates that any item could potentially be problematic with an effect size averaging \(d_s\) \textasciitilde{} 0.50 difference in means.
 While \(d_{MACS}\) values represented a ``small'' effect based on previous publications, this effect may be muted by examining both loadings and intercepts.
@@
 The overall average score on items is high: \(M_M\) = 5.04 (\(M_{SD}\) = 1.72).
-Given the mean standard deviation, a \(d\) \textasciitilde{} 0.50 represents 0.86 or nearly one whole point on the scale.
-A researcher could decide that at least \(d\) = 0.33 or at least a third of a standard deviation would be an important change and set that as their smallest effect size of interest for invariance.
+Given the mean and standard deviation, a \(d_s\) \textasciitilde{} 0.50 represents 0.86 or nearly one whole point on the scale.
+A researcher could decide that at least \(d_s\) = 0.33 or at least a third of a standard deviation would be an important change and set that as their smallest effect size of interest for invariance replication and extension.
 Further, a newly planned study should investigate what variables may predict when and why samples separate into bimodal representations for item means.
@@
 Given these results, another researcher may assume that the models would be comparable between English speaking (i.e., likely United States) and Chinese speaking samples.
-With the published data, we can use \texttt{visualizemi} to determine if the RS14 is invariant across language/culture, and if the results would likely replicate if tested on a new set of samples, and what, if any, effect size differences are found in parameters.
+With the published data, we can use \emph{visualizemi} to determine if the RS14 is invariant across language/culture, and if the results would likely replicate if tested on a new set of samples, and what, if any, effect size differences are found in parameters.
 The code used for this analysis is presented in the supplemental materials.
@@
 Jöreskog, K. G., \& Sörbom, D. (2001). \emph{LISREL 8: user's reference guide} (2. ed., updated to LISREL 8). SSI Scientific Software Internat.
+
+\bibitem[\citeproctext]{ref-lakens2013}
+Lakens, D.
+(2013).
+Calculating and reporting effect sizes to facilitate cumulative science: A practical primer for t-tests and ANOVAs.
+\emph{Frontiers in Psychology}, \emph{4}.
+\url{https://doi.org/10.3389/fpsyg.2013.00863}
 

### 2024-07-29 manuscript.Rmd
sigh word docs

@@
 documentclass     : "apa7"
-output            : papaja::apa6_pdf
+output            : papaja::apa6_docx
 appendix          :
@@
        width = 8, 
-       height = 6,
        units = "in")
@@
        width = 8, 
-       height = 6, 
        units = "in")

### 2024-10-19 appendix_1_fixrefs.Rmd
fixing supplement

--- 2024-07-29 appendix_1.Rmd
@@
 ---
-appendix: "appendix_1.Rmd"
+appendix: appendix_1.Rmd
+bibliography: includes/references.bib
+output: word_document
+csl: "/Library/Frameworks/R.framework/Versions/4.4-arm64/Resources/library/papaja/rmd/apa7.csl"
 ---
@@
 # Code Examples
+
+```{r echo = F, include = F}
+library(dplyr)
+library(lavaan)
+library(visualizemi)
+library(dmacs)
+library(ggplot2)
+library(papaja)
+```
 
@@
 
+```{r echo = F}
+boot.partial.invariant <- readRDS("manu_data/boot.partial.invariant.RData")
+```
+
 ```{r partial-boot-print-app, echo = T, size = "small"}
@@
 ```
+
+# References
+
+<div id="refs"></div>

### 2024-10-19 appendix_2_fixrefs.Rmd
fixing supplement

--- 2024-07-29 appendix_2.Rmd
@@
 appendix: "appendix_2.Rmd"
+bibliography: includes/references.bib
+output: word_document
+csl: "/Library/Frameworks/R.framework/Versions/4.4-arm64/Resources/library/papaja/rmd/apa7.csl"
 ---
@@
 # Simulation Study
+
+```{r}
+library(dplyr)
+library(lavaan)
+library(visualizemi)
+library(dmacs)
+library(ggplot2)
+library(papaja)
+library(tidyr)
+library(ggridges)
+```
+
+```{r setup, include=FALSE, echo = F}
+knitr::opts_chunk$set(fig.path = as.character("figures/"))
+knitr::knit('appendix_1_fixrefs.Rmd')
+boot_rr_DF <- rio::import("manu_data/boot_rr_DF.csv")
+boot.df.full <- rio::import("manu_data/boot_DF_full.csv")
+boot.partial.summary.full <- rio::import("manu_data/boot_partial_summary_DF_full.csv")
+boot.effects.summary.full <- rio::import("manu_data/boot_effects_summary_DF_full.csv")
+```
 
